### 2022-04-30 manuscript.Rmd
Initial commit and checking synchronisation with RStudio

---
title: "Normalization Reweighting"
author: "Daniel Baker"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Abstract

```{r cars}
summary(cars)
```

## Introduction

## Results

## Discussion

## Methods

### 2022-05-03 manuscript.Rmd
Analysis of pilot data started

@@
 title: "Normalization Reweighting"
-author: "Daniel Baker"
+author: "Daniel H. Baker"
 date: "`r Sys.Date()`"
@@
 ```{r setup, include=FALSE}
+
+runcode <- 1  # this flag chooses whether to run the underlying analysis code (1), or just load in the figures from the last time this was run (0)
+processraw <- 0  # this flag determines whether the raw data are downloaded from OSF and processed - this will require ~30GB of hard drive space and take several hours
+
+# reasonably compact code to check which packages are installed, install the missing ones, and activate all
+packagelist <- c('knitr','remotes','tictoc') # list of CRAN packages
+missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
+if (length(missingpackages)>0){install.packages(missingpackages)}
+if (!'osfr' %in% installed.packages()[,1]){remotes::install_github("centerforopenscience/osfr")}
+if (!'FourierStats' %in% installed.packages()[,1]){remotes::install_github("bakerdh/FourierStats")}
+packagelist <- c(packagelist,'osfr','FourierStats')
+toinstall <- packagelist[which(!packagelist %in% (.packages()))]
+invisible(lapply(toinstall,library,character.only=TRUE))
+
+# helper function to make colours transparent
+addalpha <- function(col, alpha=1){apply(sapply(col, col2rgb)/255, 2, function(x) rgb(x[1], x[2], x[3], alpha=alpha))}
+
 knitr::opts_chunk$set(echo = TRUE)
+
+# check if a directory exists to store data files (ignored by git)
+if (!dir.exists('temp/')){dir.create('temp/')}
+if (!dir.exists('temp/VilidaiteProcessed/')){dir.create('temp/VilidaiteProcessed/')}
+
+targetelectrodes <- c('Oz','POz','O1','O2')
+
 ```
@@
 ## Abstract
-
-```{r cars}
-summary(cars)
-```
 
@@
 
+Figure summarising the Vilidaite reanalysis
+Contrast response functions?
+Waveforms
+Spectra with scalp distributions
+Timecourse for each condition & frequency
+NR for each frequency
+AQ distribution
+Median AQ split
+
+```{r}
+
+samplerate <- 1000
+targetF <- 7
+maskF <- 5
+tindex <- (10*targetF) + 1
+mindex <- (10*maskF) + 1
+duration <- 14
+
+if (processraw==1){
+
+# datadir <- '/Volumes/Seagate/EEG data/UG2014/tar/'
+# tempdir <- '/Volumes/Seagate/EEG data/UG2014/tar/temp/'
+datadir <- 'temp/raw/'
+tempdir <- 'temp/raw/temp/'
+
+hdata <- read.csv('~/Google Drive/Current work/R scripts/EEG analysis/headerfile.csv', header = TRUE)
+legaltriggers <- hdata$Trigger[!is.na(hdata$Trigger)]
+subcounter <- 0
+
+for (s in 1:101) {
+  if (s != 75) {
+    subcounter <- subcounter + 1  
+  if (!file.exists(paste0('temp/VilidaiteProcessed/V',subcounter,'processed.RData'))){
+  print(s)
+
+    condcounter <- (1:20) * 0
+    allsamples <- array(0, dim = c(10,20,64,duration*samplerate))
+    if (s < 10){untar(paste(datadir, 'S0', s, '.tar', sep = ''), exdir = tempdir)}
+    if (s > 9){untar(paste(datadir, 'S', s, '.tar', sep = ''), exdir = tempdir)}
+
+    d <- dir(path = tempdir, pattern = '*.csv.gz')
+
+    for (block in 1:length(d)) {
+      EEGdata <- read.csv(paste(tempdir, d[block], sep = ''), header = TRUE)
+
+      electrodes <- colnames(EEGdata)
+      targetchannels <- match(targetelectrodes, electrodes) - 2
+
+      # epoch the data, Fourier transform and store
+      triggertimes <- (1:40) * 0
+      counter <- 0
+      for (n in 1:nrow(EEGdata)) {
+        if (EEGdata$Trigger[n] %in% legaltriggers) {
+          counter <- counter + 1
+          triggertimes[counter] <- n
+        }
+      }
+
+      for (tr in 1:counter) {
+        cond <- EEGdata$Trigger[triggertimes[tr]] / 10
+        condcounter[cond] <- condcounter[cond] + 1
+        for (ch in 1:64){
+        temp <- as.matrix(EEGdata[(triggertimes[tr]:(triggertimes[tr] + samplerate * duration - 1))-999, ch + 2])
+        temp <- temp - mean(temp[1:1000])   # baseline subtraction to remove DC component
+        allsamples[condcounter[cond],cond,ch,1:(1000*duration)] <- as.vector(rowMeans(temp))
+        }
+      }
+    }
+allsamples[which(is.na(allsamples))] <- 0     # remove any NaN values
+meanwaveforms <- array(0,dim=c(14,64,14000))
+    for (cond in 1:14){
+      for (ch in 1:64){
+        temp <- allsamples[1:condcounter[cond],cond,ch,]
+        allspec <- matrix(0,nrow=condcounter[cond],ncol=10000)
+        for (trial in 1:condcounter[cond]){
+          allspec[trial,] <- fft(temp[trial,2001:12000])/10000
+        }
+        targetresps <- allspec[,tindex]
+        maskresps <- allspec[,mindex]
+      if (sum(abs(targetresps))>0){  
+      tempxy <- data.frame(Re(targetresps),Im(targetresps))
+      D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+      i1 <- (D<3)
+      tempxy <- data.frame(Re(maskresps),Im(maskresps))
+      D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+      i2 <- (D<3)
+      i <- which((i1*i2)>0)
+        meanwaveforms[cond,ch,] <- colMeans(temp[i,])
+      }
+      }
+    }
+
+     save(file = paste0('temp/VilidaiteProcessed/V',subcounter,'processed.RData'), list = c('meanwaveforms','electrodes'))
+
+    for (block in 1:length(d)){file.remove(paste0(tempdir, d[block]))}
+
+  }
+}
+}
+}
+
+if (runcode==1){
+  d <- dir('temp/VilidaiteProcessed/')
+
+  allwaves <- array(0,dim=c(length(d),14,64,14000))
+  for (s in 1:length(d)){
+    load(paste0('temp/VilidaiteProcessed/',d[s]))
+    allwaves[s,,,] <- meanwaveforms
+  }
+
+  meanwaveforms <- array(0,dim=c(14,64,14000))
+  alltarget <- matrix(0,nrow=14,ncol=64)
+  allmask <- matrix(0,nrow=14,ncol=64)
+    for (cond in 1:14){
+      for (ch in 1:64){
+        temp <- allwaves[,cond,ch,]
+        allspec <- matrix(0,nrow=length(d),ncol=10000)
+        for (subj in 1:length(d)){
+          allspec[subj,] <- fft(temp[subj,2001:12000])/10000
+        }
+        targetresps <- allspec[,tindex]
+        maskresps <- allspec[,mindex]
+      if (sum(abs(targetresps))>0){  
+      tempxy <- data.frame(Re(targetresps),Im(targetresps))
+      D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+      i1 <- (D<3)
+      tempxy <- data.frame(Re(maskresps),Im(maskresps))
+      D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+      i2 <- (D<3)
+      i <- which((i1*i2)>0)
+        meanwaveforms[cond,ch,] <- colMeans(temp[i,])
+      }
+        spec <- fft(meanwaveforms[cond,ch,2001:12000])/10000
+        alltarget[cond,ch] <- spec[tindex]
+        allmask[cond,ch] <- spec[mindex]
+      }
+    }
+
+}
+
+targetchannels <- match(targetelectrodes, electrodes) - 2
+
+elecave <- colMeans(meanwaveforms[6,targetchannels,])
+binwidth <- 1000
+f1 <- 7
+tindex <- 1 + f1*(binwidth/1000)
+fspec <- elecave*0
+for (t in 1:(length(elecave)-binwidth)){
+  temp <- elecave[t:(t+binwidth-1)]
+  spec <- fft(temp)/binwidth
+  fspec[t] <- abs(spec[tindex])
+}
+elecave <- colMeans(meanwaveforms[13,targetchannels,])
+binwidth <- 1000
+f1 <- 7
+tindex <- 1 + f1*(binwidth/1000)
+fspec2 <- elecave*0
+for (t in 1:(length(elecave)-binwidth)){
+  temp <- elecave[t:(t+binwidth-1)]
+  spec <- fft(temp)/binwidth
+  fspec2[t] <- abs(spec[tindex])
+}
+
+times <- -499:13500
+plot(times,fspec,type='l',col='red')
+lines(times,fspec2,col='green')
+
+# all electrodes, condition 6 @ 7Hz
+# all electrodes, condition 8 @ 5Hz
+# target electrodes, conditions 1-14 for CRF, 5&7Hz
+# target electrodes, full timecourse at 5 & 7Hz, conditions 6, 8, 13
+# allwaves dimensions: 67 x 14 x 64 x 14000
+
+temp <- allwaves[,6,,2001:12000]
+meantemp <- apply(allwaves,2:3,mean)
+
+f1 <- 7
+f2 <- 5
+    binwidth <- 1000
+    tindex <- 1 + f1*(binwidth/1000)
+    mindex <- 1 + f2*(binwidth/1000)
+condlist <- c(6,8,13)
+targetchannels <- match(targetelectrodes, electrodes) - 2
+d <- dir('temp/VilidaiteProcessed/')
+all7Hz <- array(0,dim=c(length(d),14,64))
+all5Hz <- array(0,dim=c(length(d),14,64))
+timecourse7Hz <- array(0,dim=c(length(d),3,14000))
+timecourse5Hz <- array(0,dim=c(length(d),3,14000))
+
+  for (s in 1:length(d)){
+    tic()
+    load(paste0('temp/VilidaiteProcessed/',d[s]))
+
+    for (cond in 1:14){
+      for (ch in 1:64){
+        temp <- meanwaveforms[cond,ch,2001:12000]
+        spec <- fft(temp)/length(temp)
+        all7Hz[s,cond,ch] <- spec[7*10+1]
+        all5Hz[s,cond,ch] <- spec[5*10+1]
+      }
+    }
+    for (cond in 1:3){
+    temp <- colMeans(meanwaveforms[condlist[cond],targetchannels,])
+
+fspec1 <- temp*0
+fspec2 <- temp*0
+for (t in 1:(length(temp)-binwidth)){
+  spec <- fft(temp[t:(t+binwidth-1)])/binwidth
+  fspec1[t] <- abs(spec[tindex])
+  fspec2[t] <- abs(spec[mindex])
+}
+    timecourse7Hz[s,cond,] <- fspec1
+    timecourse5Hz[s,cond,] <- fspec2
+
+    }
+
+    print(toc())
+
+  }
+
+mean7 <- apply(all7Hz[,,targetchannels],1:2,mean)
+mean5 <- apply(all5Hz[,,targetchannels],1:2,mean)
+inclusionmatrix7 <- matrix(0,nrow=length(d),ncol=length(condlist))
+inclusionmatrix5 <- matrix(0,nrow=length(d),ncol=length(condlist))
+for (cond in 1:3){
+  temp <- mean7[,condlist[cond]]
+        tempxy <- data.frame(Re(temp),Im(temp))
+      D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+      inclusionmatrix7[,cond] <- (D<3)
+   temp <- mean5[,condlist[cond]]
+        tempxy <- data.frame(Re(temp),Im(temp))
+      D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+      inclusionmatrix5[,cond] <- (D<3)
+}
+
+meantime5Hz <- matrix(0,nrow=length(condlist),ncol=14000) 
+meantime7Hz <- matrix(0,nrow=length(condlist),ncol=14000) 
+for (cond in 1:3){
+meantime7Hz[cond,] <- abs(apply(timecourse7Hz[which(inclusionmatrix7[,cond]>0),cond,],2,mean))
+meantime5Hz[cond,] <- abs(apply(timecourse5Hz[which(inclusionmatrix5[,cond]>0),cond,],2,mean))
+}
+
+plot(-499:13500,meantime5Hz[2,],type='l',col='red')
+lines(-499:13500,meantime5Hz[1,],col='black')
+lines(-499:13500,meantime5Hz[3,],col='green')
+
+plot(-499:13500,meantime7Hz[1,],type='l',col='red')
+lines(-499:13500,meantime7Hz[2,],col='black')
+lines(-499:13500,meantime7Hz[3,],col='green')
+
+```
+
+Figure summarising the EEG experiment
+Stimuli?
+Waveforms
+Spectra with scalp distributions
+Timecourse for each condition & frequency
+NR for each frequency, mon & dich
+AQ vs SPQ with distributions on margins
+Median AQ split
+
+Figure summarising the MEG experiment
+Brains showing location of activity and V1 ROI
+Spectra, timecourses
+NR for each frequency, mon & dich, split by group
+
 ## Discussion
@@
 ## Methods
+
+```{r cars}
+summary(cars)
+```

### 2022-05-03 manuscript.Rmd
Update manuscript.Rmd
Fixed weird commit issues

@@
 runcode <- 1  # this flag chooses whether to run the underlying analysis code (1), or just load in the figures from the last time this was run (0)
-processraw <- 0  # this flag determines whether the raw data are downloaded from OSF and processed - this will require ~30GB of hard drive space and take several hours
+processraw <- 1  # this flag determines whether the raw data are downloaded from OSF and processed - this will require ~30GB of hard drive space and take several hours
 
@@
 
+osfnode <- 'y4n5k'    # this is where the pilot data are stored
+osfproject <- osf_retrieve_node(osfnode)
+EEGfiles <- osf_ls_files(osfproject,n_max=300)
+
 # datadir <- '/Volumes/Seagate/EEG data/UG2014/tar/'
@@
   print(s)
+
+    if (s < 10){tarname <- paste0('S0', s, '.tar')}
+    if (s > 9){tarname <- paste0('S', s, '.tar')}
+
+    if (!file.exists(paste0(datadir,tarname))){
+      fid <- which(EEGfiles$name==tarname)
+      osf_download(EEGfiles[fid,],datadir,progress=TRUE)
+    }
+
+    condcounter <- (1:20) * 0
+    allsamples <- array(0, dim = c(10,20,64,duration*samplerate))
+
+    untar(paste0(datadir,tarname),exdir=tempdir)
 
@@
       counter <- 0
+      for (n in 1000:nrow(EEGdata)) {    # ignore triggers starting in the first 1000ms that generate an error
       for (n in 1:nrow(EEGdata)) {
@@
 if (runcode==1){
+#   d <- dir('temp/VilidaiteProcessed/')
+#   
+#   allwaves <- array(0,dim=c(length(d),14,64,14000))
+#   for (s in 1:length(d)){
+#     load(paste0('temp/VilidaiteProcessed/',d[s]))
+#     allwaves[s,,,] <- meanwaveforms
+#   }
+#   
+#   meanwaveforms <- array(0,dim=c(14,64,14000))
+#   alltarget <- matrix(0,nrow=14,ncol=64)
+#   allmask <- matrix(0,nrow=14,ncol=64)
+#     for (cond in 1:14){
+#       for (ch in 1:64){
+#         temp <- allwaves[,cond,ch,]
+#         allspec <- matrix(0,nrow=length(d),ncol=10000)
+#         for (subj in 1:length(d)){
+#           allspec[subj,] <- fft(temp[subj,2001:12000])/10000
+#         }
+#         targetresps <- allspec[,tindex]
+#         maskresps <- allspec[,mindex]
+#       if (sum(abs(targetresps))>0){  
+#       tempxy <- data.frame(Re(targetresps),Im(targetresps))
+#       D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+#       i1 <- (D<3)
+#       tempxy <- data.frame(Re(maskresps),Im(maskresps))
+#       D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+#       i2 <- (D<3)
+#       i <- which((i1*i2)>0)
+#         meanwaveforms[cond,ch,] <- colMeans(temp[i,])
+#       }
+#         spec <- fft(meanwaveforms[cond,ch,2001:12000])/10000
+#         alltarget[cond,ch] <- spec[tindex]
+#         allmask[cond,ch] <- spec[mindex]
+#       }
+#     }
+#   
+# }
+# 
+# targetchannels <- match(targetelectrodes, electrodes) - 2
+# 
+# elecave <- colMeans(meanwaveforms[6,targetchannels,])
+# binwidth <- 1000
+# f1 <- 7
+# tindex <- 1 + f1*(binwidth/1000)
+# fspec <- elecave*0
+# for (t in 1:(length(elecave)-binwidth)){
+#   temp <- elecave[t:(t+binwidth-1)]
+#   spec <- fft(temp)/binwidth
+#   fspec[t] <- abs(spec[tindex])
+# }
+# elecave <- colMeans(meanwaveforms[13,targetchannels,])
+# binwidth <- 1000
+# f1 <- 7
+# tindex <- 1 + f1*(binwidth/1000)
+# fspec2 <- elecave*0
+# for (t in 1:(length(elecave)-binwidth)){
+#   temp <- elecave[t:(t+binwidth-1)]
+#   spec <- fft(temp)/binwidth
+#   fspec2[t] <- abs(spec[tindex])
+# }
+# 
+# times <- -499:13500
+# plot(times,fspec,type='l',col='red')
+# lines(times,fspec2,col='green')
   d <- dir('temp/VilidaiteProcessed/')
@@
 
+# temp <- allwaves[,6,,2001:12000]
+# meantemp <- apply(allwaves,2:3,mean)
+
 temp <- allwaves[,6,,2001:12000]
@@
 condlist <- c(6,8,13)
+
 targetchannels <- match(targetelectrodes, electrodes) - 2
@@
     load(paste0('temp/VilidaiteProcessed/',d[s]))
+
+    targetchannels <- match(targetelectrodes, electrodes) - 2
 
@@
 
+}
+
 ```

### 2022-05-17 manuscript.Rmd
Update manuscript.Rmd
Started writing introduction

--- 2022-05-03 manuscript.Rmd
@@
 ---
-title: "Normalization Reweighting"
-author: "Daniel H. Baker"
+title: "The Dynamics of Normalization Reweighting"
+author: "Daniel H.
+Baker, Daniela Marinova, Richard Aveyard, Lydia Hargreaves, Alice Renton, Ruby Castellani, Phoebe Hall, Miriam Harmens, Georgia Holroyd, Dorian Manning, Beth Nicholson, Emily Williams, Hannah M.
+Hobson & Alex R.
+Wade"
 date: "`r Sys.Date()`"
@@
 
+Suppressive interactions between neurons are ubiquitous in the nervous system, and normalization (or gain control) processes have been proposed as a canonical neuronal computation (Carandini & Heeger).
+Yet the strength of suppression was for decades treated as fixed, largely due to the observation that adapting to one stimulus does not decrease its suppressive potency (refs).
+This orthodoxy was recently challenged by a series of innovative studies showing that normalization can be 'reweighted' by recent history (Westrick, Aschner, Yiltiz).
+Specifically, when pairs of stimuli are repeatedly presented together, they come to suppress each other more strongly.
+This suggests that, far from being fixed, normalization is a dynamic process that is continuously updated by the sensory environment.
+Here, our objectives were to determine if the timecourse of these changes can be measured non-invasively from the human brain, assess if they occur across suppressive pathways, and determine whether they differ across the population as a function of self-reported sensory experience, and autistic traits.
+
+Atypical sensory experience is widely reported by individuals on the autism spectrum, yet the causal mechanisms remain unclear.
+Typical issues include hypersensitivity to intense stimuli such as loud sounds, bright lights and strong odours or flavours.
+Yet fundamental measures of sensitivity such as visual acuity, contrast sensitivity, and audiometric performance (Rosenhall et al.
+1999) are not consistently different from neurotypical controls.
+
+Simmons
+
+Dickinson 2014 oblique effect
+
+Vilidaite summary
+
+Theoretical accounts of sensory differences in autism have long proposed that the balance of inhibition and excitation may be disrupted, and there are isolated results that seem consistent with this.
+For example ...
+However many other studies have failed to find group differences using tasks that are at least superficially dependent on inhibition, such as...
+
+Priors
+
+Suppression itself is not a single process.
+Multiple suppressive pathways have been identified in the visual system, including between stimuli differing in orientation, eye-of-origin and spatial position.
+At present there is evidence of normalization reweighting between stimuli of orthogonal orientations (Aschner, 2018), and adjacent spatial positions (Yiltiz, 2020).
+We also wondered if interocular suppression might be subject to reweighting, and if there are differences in the dynamics across pathways.
+This is possible, given that suppression within and between the eyes has different spatiotemporal tuning (Meese & Baker, 2009), and dichoptic masking can be reduced by adapting to the mask (Baker, 2007 and other studies), unlike within-eye masking.
+Dynamic fluctuations in interocular suppression are a feature of binocular rivalry (Wilson, 2003), for which differences in autism have also been reported (Robertson).
+
+We hypothesised that normalization reweighting might differ as a function of autistic traits.
+The relative novelty of the reweighting framework could explain why any differences have not previously been detected, and why the literature on inhibition in autism is relatively inconclusive.
+In this paper we perform a time-course analysis of a previously published EEG data set, and report two novel pre-registered experiments using EEG and MEG.
+Our data show that suppression increases substantially during the first 4 seconds after stimulus onset, for both monocular and dichoptic masks, and as early as V1.
+Autism ...
+
 ## Results
 
-Figure summarising the Vilidaite reanalysis
-Contrast response functions?
-Waveforms
-Spectra with scalp distributions
-Timecourse for each condition & frequency
-NR for each frequency
-AQ distribution
-Median AQ split
+We began by reanalysing data from a steady-state visually evoked potential (SSVEP) experiment reported by Vilidaite et al (2018).
+Participants viewed arrays of flickering gratings of varying contrasts.
+In some conditions a single grating orientation was present flickering at 7Hz, whereas in other conditions a high contrast 'mask' was added at right angles to the target gratings, and flickering at 5Hz.
+Figure 1a shows contrast response functions with and without the mask - the presence of the mask reduces the 7Hz response to the target.
+Similarly, Figure 1b shows that the 5Hz response to the mask was itself suppressed by the presence of high contrast targets (note that the data from the mask conditions were not reported by Vilidaite et al.).
+At both frequencies, responses were localised to the occipital pole (see insets).
+
+We then performed a novel timecourse analysis, in which we separated each 11-second trial into bins of 1 second duration.
+Figure 1c shows the response at the target frequency (7Hz) to a single stimulus of 32% contrast, and the response at 7Hz when the mask is added.
+For the target alone there is a gradual decline throughout the trial, consistent with traditional adaptation effects.
+The reduction in signal strength when the mask component is added illustrates the masking effect.
+Taking the ratio of the two timecourses reveals that masking increases steeply during the first 4 seconds of stimulus presentation, plateaus for several seconds, and then possibly declines.
+A similar pattern is observed at 5Hz (Figures 1e,f).
+Finally, we split the data set by median AQ score (see Figure 1g).
+Averaging across frequency, the low AQ group showed a strong increase over the first 4 seconds of the trial, whereas the high AQ group showed a much shallower change over the same time period (Figure 1h).
 
@@
 if (processraw==1){
+
+osfnode <- 'y4n5k'    # this is where the pilot data are stored
+osfproject <- osf_retrieve_node(osfnode)
+EEGfiles <- osf_ls_files(osfproject,n_max=300)
 
@@
 }
+}
 
 if (runcode==1){
-  d <- dir('temp/VilidaiteProcessed/')
-
-  allwaves <- array(0,dim=c(length(d),14,64,14000))
-  for (s in 1:length(d)){
-    load(paste0('temp/VilidaiteProcessed/',d[s]))
-    allwaves[s,,,] <- meanwaveforms
-  }
-
-  meanwaveforms <- array(0,dim=c(14,64,14000))
-  alltarget <- matrix(0,nrow=14,ncol=64)
-  allmask <- matrix(0,nrow=14,ncol=64)
-    for (cond in 1:14){
-      for (ch in 1:64){
-        temp <- allwaves[,cond,ch,]
-        allspec <- matrix(0,nrow=length(d),ncol=10000)
-        for (subj in 1:length(d)){
-          allspec[subj,] <- fft(temp[subj,2001:12000])/10000
-        }
-        targetresps <- allspec[,tindex]
-        maskresps <- allspec[,mindex]
-      if (sum(abs(targetresps))>0){  
-      tempxy <- data.frame(Re(targetresps),Im(targetresps))
-      D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
-      i1 <- (D<3)
-      tempxy <- data.frame(Re(maskresps),Im(maskresps))
-      D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
-      i2 <- (D<3)
-      i <- which((i1*i2)>0)
-        meanwaveforms[cond,ch,] <- colMeans(temp[i,])
-      }
-        spec <- fft(meanwaveforms[cond,ch,2001:12000])/10000
-        alltarget[cond,ch] <- spec[tindex]
-        allmask[cond,ch] <- spec[mindex]
-      }
-    }
-
-}
-
-targetchannels <- match(targetelectrodes, electrodes) - 2
-
-elecave <- colMeans(meanwaveforms[6,targetchannels,])
-binwidth <- 1000
-f1 <- 7
-tindex <- 1 + f1*(binwidth/1000)
-fspec <- elecave*0
-for (t in 1:(length(elecave)-binwidth)){
-  temp <- elecave[t:(t+binwidth-1)]
-  spec <- fft(temp)/binwidth
-  fspec[t] <- abs(spec[tindex])
-}
-elecave <- colMeans(meanwaveforms[13,targetchannels,])
-binwidth <- 1000
-f1 <- 7
-tindex <- 1 + f1*(binwidth/1000)
-fspec2 <- elecave*0
-for (t in 1:(length(elecave)-binwidth)){
-  temp <- elecave[t:(t+binwidth-1)]
-  spec <- fft(temp)/binwidth
-  fspec2[t] <- abs(spec[tindex])
-}
-
-times <- -499:13500
-plot(times,fspec,type='l',col='red')
-lines(times,fspec2,col='green')
+#   d <- dir('temp/VilidaiteProcessed/')
+#   
+#   allwaves <- array(0,dim=c(length(d),14,64,14000))
+#   for (s in 1:length(d)){
+#     load(paste0('temp/VilidaiteProcessed/',d[s]))
+#     allwaves[s,,,] <- meanwaveforms
+#   }
+#   
+#   meanwaveforms <- array(0,dim=c(14,64,14000))
+#   alltarget <- matrix(0,nrow=14,ncol=64)
+#   allmask <- matrix(0,nrow=14,ncol=64)
+#     for (cond in 1:14){
+#       for (ch in 1:64){
+#         temp <- allwaves[,cond,ch,]
+#         allspec <- matrix(0,nrow=length(d),ncol=10000)
+#         for (subj in 1:length(d)){
+#           allspec[subj,] <- fft(temp[subj,2001:12000])/10000
+#         }
+#         targetresps <- allspec[,tindex]
+#         maskresps <- allspec[,mindex]
+#       if (sum(abs(targetresps))>0){  
+#       tempxy <- data.frame(Re(targetresps),Im(targetresps))
+#       D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+#       i1 <- (D<3)
+#       tempxy <- data.frame(Re(maskresps),Im(maskresps))
+#       D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+#       i2 <- (D<3)
+#       i <- which((i1*i2)>0)
+#         meanwaveforms[cond,ch,] <- colMeans(temp[i,])
+#       }
+#         spec <- fft(meanwaveforms[cond,ch,2001:12000])/10000
+#         alltarget[cond,ch] <- spec[tindex]
+#         allmask[cond,ch] <- spec[mindex]
+#       }
+#     }
+#   
+# }
+# 
+# targetchannels <- match(targetelectrodes, electrodes) - 2
+# 
+# elecave <- colMeans(meanwaveforms[6,targetchannels,])
+# binwidth <- 1000
+# f1 <- 7
+# tindex <- 1 + f1*(binwidth/1000)
+# fspec <- elecave*0
+# for (t in 1:(length(elecave)-binwidth)){
+#   temp <- elecave[t:(t+binwidth-1)]
+#   spec <- fft(temp)/binwidth
+#   fspec[t] <- abs(spec[tindex])
+# }
+# elecave <- colMeans(meanwaveforms[13,targetchannels,])
+# binwidth <- 1000
+# f1 <- 7
+# tindex <- 1 + f1*(binwidth/1000)
+# fspec2 <- elecave*0
+# for (t in 1:(length(elecave)-binwidth)){
+#   temp <- elecave[t:(t+binwidth-1)]
+#   spec <- fft(temp)/binwidth
+#   fspec2[t] <- abs(spec[tindex])
+# }
+# 
+# times <- -499:13500
+# plot(times,fspec,type='l',col='red')
+# lines(times,fspec2,col='green')
+#   d <- dir('temp/VilidaiteProcessed/')
+#   
+#   allwaves <- array(0,dim=c(length(d),14,64,14000))
+#   for (s in 1:length(d)){
+#     load(paste0('temp/VilidaiteProcessed/',d[s]))
+#     allwaves[s,,,] <- meanwaveforms
+#   }
+#   
+#   meanwaveforms <- array(0,dim=c(14,64,14000))
+#   alltarget <- matrix(0,nrow=14,ncol=64)
+#   allmask <- matrix(0,nrow=14,ncol=64)
+#     for (cond in 1:14){
+#       for (ch in 1:64){
+#         temp <- allwaves[,cond,ch,]
+#         allspec <- matrix(0,nrow=length(d),ncol=10000)
+#         for (subj in 1:length(d)){
+#           allspec[subj,] <- fft(temp[subj,2001:12000])/10000
+#         }
+#         targetresps <- allspec[,tindex]
+#         maskresps <- allspec[,mindex]
+#       if (sum(abs(targetresps))>0){  
+#       tempxy <- data.frame(Re(targetresps),Im(targetresps))
+#       D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+#       i1 <- (D<3)
+#       tempxy <- data.frame(Re(maskresps),Im(maskresps))
+#       D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+#       i2 <- (D<3)
+#       i <- which((i1*i2)>0)
+#         meanwaveforms[cond,ch,] <- colMeans(temp[i,])
+#       }
+#         spec <- fft(meanwaveforms[cond,ch,2001:12000])/10000
+#         alltarget[cond,ch] <- spec[tindex]
+#         allmask[cond,ch] <- spec[mindex]
+#       }
+#     }
+#   
+# }
+# 
+# targetchannels <- match(targetelectrodes, electrodes) - 2
+# 
+# elecave <- colMeans(meanwaveforms[6,targetchannels,])
+# binwidth <- 1000
+# f1 <- 7
+# tindex <- 1 + f1*(binwidth/1000)
+# fspec <- elecave*0
+# for (t in 1:(length(elecave)-binwidth)){
+#   temp <- elecave[t:(t+binwidth-1)]
+#   spec <- fft(temp)/binwidth
+#   fspec[t] <- abs(spec[tindex])
+# }
+# elecave <- colMeans(meanwaveforms[13,targetchannels,])
+# binwidth <- 1000
+# f1 <- 7
+# tindex <- 1 + f1*(binwidth/1000)
+# fspec2 <- elecave*0
+# for (t in 1:(length(elecave)-binwidth)){
+#   temp <- elecave[t:(t+binwidth-1)]
+#   spec <- fft(temp)/binwidth
+#   fspec2[t] <- abs(spec[tindex])
+# }
+# 
+# times <- -499:13500
+# plot(times,fspec,type='l',col='red')
+# lines(times,fspec2,col='green')
 
@@
 
-temp <- allwaves[,6,,2001:12000]
-meantemp <- apply(allwaves,2:3,mean)
+# temp <- allwaves[,6,,2001:12000]
+# meantemp <- apply(allwaves,2:3,mean)
+
+# temp <- allwaves[,6,,2001:12000]
+# meantemp <- apply(allwaves,2:3,mean)
 
@@
 condlist <- c(6,8,13)
-targetchannels <- match(targetelectrodes, electrodes) - 2
+
 d <- dir('temp/VilidaiteProcessed/')
@@
   for (s in 1:length(d)){
-    tic()
+
     load(paste0('temp/VilidaiteProcessed/',d[s]))
+
+    targetchannels <- match(targetelectrodes, electrodes) - 2
 
@@
   spec <- fft(temp[t:(t+binwidth-1)])/binwidth
-  fspec1[t] <- abs(spec[tindex])
-  fspec2[t] <- abs(spec[mindex])
+  fspec1[t] <- spec[tindex]
+  fspec2[t] <- spec[mindex]
 }
@@
     }
-
-    print(toc())
 
@@
 for (cond in 1:3){
-meantime7Hz[cond,] <- abs(apply(timecourse7Hz[which(inclusionmatrix7[,cond]>0),cond,],2,mean))
-meantime5Hz[cond,] <- abs(apply(timecourse5Hz[which(inclusionmatrix5[,cond]>0),cond,],2,mean))
+meantime7Hz[cond,] <- abs(apply(abs(timecourse7Hz[which(inclusionmatrix7[,cond]>0),cond,]),2,mean))
+meantime5Hz[cond,] <- abs(apply(abs(timecourse5Hz[which(inclusionmatrix5[,cond]>0),cond,]),2,mean))
 }
@@
 
+}
+
+abs(colMeans(mean5))
+abs(colMeans(mean7))
+
 ```
+Our initial reanalysis was promising, however the data were noisy despite the large sample size, because each participant contributed only 8 trials to each condition.
+We therefore preregistered two new experiments (see http://) to investigate these effects in greater detail.
+These had a similar overall design to the Vilidaite study, with some small changes intended to optimise the study (see Methods).
+The key differences were that we used shorter trials (because there were few changes in the latter part of the trials shown in Figure 1), and also focussed all trials into a smaller number of conditions, such that each participant contributed 48 repetitions to each of 4 conditions.
+The greater data fidelity afforded by this design allowed us to perform a sliding time window analysis of the results.
 
-Figure summarising the EEG experiment
-Stimuli?
-Waveforms
-Spectra with scalp distributions
-Timecourse for each condition & frequency
-NR for each frequency, mon & dich
-AQ vs SPQ with distributions on margins
-Median AQ split
+Figure 2 summarises the results of an EEG experiment testing 100 neurotypical participants.
+Averaged EEG waveforms showed a strong oscillatory component at each of the two stimulus flicker frequencies (Figure 2a), which slightly lagged the driving signal.
+Signals were well-isolated in the Fourier domain, and localised to occipital electrodes (Figure 2b).
+The timecourse at both frequencies showed an initial onset transient, and were then relatively stable for the 6 seconds of stimulus presentation (Figure 2c,d).
+Responses were weaker in the two masking conditions, and the ratio of target only to target + mask conditions increased over time (Figure 2e,f).
+
+Participants showed a wide range of scores on both the AQ and SPQ scales, which were negatively correlated (Fig 3a; R = , p < ).
+We again performed a median split by AQ on the EEG data, and calculated the timecourse of the EEG response and masking ratios for each group (Figure 3b,c).
+
+Next we repeated the experiment on 20 participants using a 248-channel whole-head cryogenic MEG system.
+Half of the participants had a diagnosis of autism, and the remainder were age and gender-matched controls.
+Source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm (reference) showed strong localisation of steady-state signals at the occipital pole (see Figure 4a,b).
+Responses across V1 showed a similar timecourse to those of the EEG experiment at both frequencies (Figure 4c,d), and showed increasing suppression during the first 4 seconds of stimulus presentation (Figure 4e,f).
 
@@
 ## Methods
-
-```{r cars}
-summary(cars)
-```

### 2022-05-17 manuscript.Rmd
Included MEG analysis code

@@
 # reasonably compact code to check which packages are installed, install the missing ones, and activate all
-packagelist <- c('knitr','remotes','tictoc') # list of CRAN packages
+packagelist <- c('knitr','remotes','tictoc','R.matlab') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
@@
 
-# check if a directory exists to store data files (ignored by git)
+# check if directories exist to store data files (ignored by git)
 if (!dir.exists('temp/')){dir.create('temp/')}
 if (!dir.exists('temp/VilidaiteProcessed/')){dir.create('temp/VilidaiteProcessed/')}
+if (!dir.exists('temp/raw/')){dir.create('temp/raw/')}
+if (!dir.exists('temp/raw/temp/')){dir.create('temp/raw/temp/')}
+if (!dir.exists('temp/MEGdata/')){dir.create('temp/MEGdata/')}
 
@@
 
+```{r}
+
+samplerate <- 1001
+targetF <- 5
+maskF <- 7
+    binwidth <- 1001
+    tindex <- 1 + targetF*(binwidth/1001)
+    mindex <- 1 + maskF*(binwidth/1001)
+
+d <- dir(path = 'temp/MEGdata/', pattern = '*alltrials.mat', full.names=TRUE)
+d2 <- dir(path = 'temp/MEGdata/', pattern = '*alltrials.mat', full.names=FALSE)
+
+allresps <- array(0, dim=c(length(d),4,2,9))
+allspectra <- array(0, dim=c(length(d),4,6006))
+allwaves <- array(0, dim=c(length(d), 4, 9010))
+MEGtimecourse7Hz <- array(0, dim=c(length(d),4,8009))
+MEGtimecourse5Hz <- array(0, dim=c(length(d),4,8009))
+allRnos <- NULL
+for (s in 1:length(d)){
+  allRnos[s] <- substr(d2[s],1,5)
+  data <- readMat(d[s])
+
+  for (cond in 1:4){
+      for (t in 1:9){
+        all1F <- NULL
+        all2F <- NULL
+        for (rep in 1:data$trialcounter[1,cond]){
+          trial <- data$alltrials[cond,rep,]
+
+        sample <- trial[(1+((t-1)*1001)):(t*1001)]
+        fftsample <- fft(sample)/length(sample)
+
+        all1F[rep] <- fftsample[targetF + 1]
+        all2F[rep] <- fftsample[maskF + 1]
+      }
+
+        tempxy <- data.frame(Re(all1F),Im(all1F))
+        D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+        i <- which(D<3)
+        allresps[s,cond,1,t] <- mean(all1F[i])
+
+        tempxy <- data.frame(Re(all2F),Im(all2F))
+        D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+        i <- which(D<3)
+        allresps[s,cond,2,t] <- mean(all2F[i])
+    }
+
+    meanwave <- colMeans(data$alltrials[cond,1:data$trialcounter[1,cond],])
+
+    sample <- meanwave[1001:7006]
+    allspectra[s,cond,] <- fft(sample)/length(sample)
+
+    allwaves[s,cond,] <- meanwave
+
+fspec1 <- NULL
+fspec2 <- NULL
+for (t in 1:(length(meanwave)-binwidth)){
+  spec <- fft(meanwave[t:(t+binwidth-1)])/binwidth
+  fspec1[t] <- spec[tindex]
+  fspec2[t] <- spec[mindex]
+}
+    MEGtimecourse5Hz[s,cond,] <- fspec1
+    MEGtimecourse7Hz[s,cond,] <- fspec2
+
+  }
+}
+
+allresps <- abs(allresps)
+meanspec <- apply(allresps,2:4,mean)
+
+MEGmeantime5Hz <- matrix(0,nrow=4,ncol=8009) 
+MEGmeantime7Hz <- matrix(0,nrow=4,ncol=8009) 
+for (cond in 1:4){
+MEGmeantime7Hz[cond,] <- apply(abs(MEGtimecourse7Hz[,cond,]),2,mean)
+MEGmeantime5Hz[cond,] <- apply(abs(MEGtimecourse5Hz[,cond,]),2,mean)
+}
+
+qdata <- read.csv('~/Google Drive/Current work/Teaching/MSci project 2021/MSci project questionnaires 2021 (Responses) - Form Responses 1.csv')
+qgroup <- as.factor(qdata[,5])
+qRnos <- as.character(qdata[,2])
+qAges <- qdata[,3]
+qRnos[20] <- 'R5860'
+qgroup[20] <- 'Yes'
+qAges[20] <- 19
+
+sortedgroups <- NULL
+for (s in 1:length(allRnos)){sortedgroups[s] <- qgroup[which(qRnos==allRnos[s])]}
+# sortedgroups now codes 1 = control, 2 = ASC in the order of the MEG data
+
+lowAQ <- abs(apply(abs(allresps[which(sortedgroups==1),,,]),c(2,3,4),mean))
+highAQ <- abs(apply(abs(allresps[which(sortedgroups==2),,,]),c(2,3,4),mean))
+
+MEGmeantime5HzCON <- matrix(0,nrow=4,ncol=8009) 
+MEGmeantime7HzCON <- matrix(0,nrow=4,ncol=8009) 
+MEGmeantime5HzASD <- matrix(0,nrow=4,ncol=8009) 
+MEGmeantime7HzASD <- matrix(0,nrow=4,ncol=8009) 
+for (cond in 1:4){
+MEGmeantime7HzCON[cond,] <- apply(abs(MEGtimecourse7Hz[which(sortedgroups==1),cond,]),2,mean)
+MEGmeantime5HzCON[cond,] <- apply(abs(MEGtimecourse5Hz[which(sortedgroups==1),cond,]),2,mean)
+MEGmeantime7HzASD[cond,] <- apply(abs(MEGtimecourse7Hz[which(sortedgroups==2),cond,]),2,mean)
+MEGmeantime5HzASD[cond,] <- apply(abs(MEGtimecourse5Hz[which(sortedgroups==2),cond,]),2,mean)
+}
+
+# par(mfrow=c(2,3))
+
+times <- ((1:8009)-500)/1000
+
+plotlims <- c(-1,8,0,30)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+ticklocsx <- -1:8    # locations of tick marks on x axis
+ticklocsy <- seq(0,30,10)    # locations of tick marks on y axis
+ticklabelsx <- -1:8        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+# lines(times,1000*meanspec[1,1,],lwd=2,col='red')
+# lines(times,1000*meanspec[2,1,],lwd=2,col='green')
+# lines(times,1000*meanspec[3,1,],lwd=2,col='blue')
+# lines(times,1000*meanspec[4,1,],lwd=2,col='orange')
+
+# lines(times,1000*MEGmeantime5Hz[1,],lwd=2,col='red')
+# lines(times,1000*MEGmeantime5Hz[2,],lwd=2,col='green')
+# lines(times,1000*MEGmeantime5Hz[3,],lwd=2,col='blue')
+# lines(times,1000*MEGmeantime5Hz[4,],lwd=2,col='orange')
+spl5a <- smooth.spline(times,1000*MEGmeantime5Hz[1,],df=20)
+lines(spl5a$x,spl5a$y,col='red',lwd=2)
+spl5b <- smooth.spline(times,1000*MEGmeantime5Hz[2,],df=20)
+lines(spl5b$x,spl5b$y,col='green',lwd=2)
+spl5c <- smooth.spline(times,1000*MEGmeantime5Hz[3,],df=20)
+lines(spl5c$x,spl5c$y,col='blue',lwd=2)
+spl5d <- smooth.spline(times,1000*MEGmeantime5Hz[4,],df=20)
+lines(spl5d$x,spl5d$y,col='orange',lwd=2)
+
+# lines(times,1000*MEGmeantime5HzASD[1,],lwd=2,col='red',lty=2)
+# lines(times,1000*MEGmeantime5HzASD[2,],lwd=2,col='green',lty=2)
+# lines(times,1000*MEGmeantime5HzASD[3,],lwd=2,col='blue',lty=2)
+# lines(times,1000*MEGmeantime5HzASD[4,],lwd=2,col='orange',lty=2)
+spl5aASD <- smooth.spline(times,1000*MEGmeantime5HzASD[1,],df=20)
+lines(spl5aASD$x,spl5aASD$y,col='red',lwd=2,lty=2)
+spl5bASD <- smooth.spline(times,1000*MEGmeantime5HzASD[2,],df=20)
+lines(spl5bASD$x,spl5bASD$y,col='green',lwd=2,lty=2)
+spl5cASD <- smooth.spline(times,1000*MEGmeantime5HzASD[3,],df=20)
+lines(spl5cASD$x,spl5cASD$y,col='blue',lwd=2,lty=2)
+spl5dASD <- smooth.spline(times,1000*MEGmeantime5HzASD[4,],df=20)
+lines(spl5dASD$x,spl5dASD$y,col='orange',lwd=2,lty=2)
+
+# lines(times,1000*MEGmeantime5HzCON[1,],lwd=2,col='red',lty=3)
+# lines(times,1000*MEGmeantime5HzCON[2,],lwd=2,col='green',lty=3)
+# lines(times,1000*MEGmeantime5HzCON[3,],lwd=2,col='blue',lty=3)
+# lines(times,1000*MEGmeantime5HzCON[4,],lwd=2,col='orange',lty=3)
+spl5aCON <- smooth.spline(times,1000*MEGmeantime5HzCON[1,],df=20)
+lines(spl5aCON$x,spl5aCON$y,col='red',lwd=2,lty=3)
+spl5bCON <- smooth.spline(times,1000*MEGmeantime5HzCON[2,],df=20)
+lines(spl5bCON$x,spl5bCON$y,col='green',lwd=2,lty=3)
+spl5cCON <- smooth.spline(times,1000*MEGmeantime5HzCON[3,],df=20)
+lines(spl5cCON$x,spl5cCON$y,col='blue',lwd=2,lty=3)
+spl5dCON <- smooth.spline(times,1000*MEGmeantime5HzCON[4,],df=20)
+lines(spl5dCON$x,spl5dCON$y,col='orange',lwd=2,lty=3)
+
+plotlims <- c(-1,8,0,2)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+ticklocsx <- -1:8    # locations of tick marks on x axis
+ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
+ticklabelsx <- -1:8        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+lines(spl5b$x,spl5a$y/spl5c$y,col='blue',lwd=2)
+lines(spl5b$x,spl5a$y/spl5d$y,col='orange',lwd=2)
+
+lines(spl5bASD$x,spl5aASD$y/spl5cASD$y,col='blue',lwd=2,lty=2)
+lines(spl5bASD$x,spl5aASD$y/spl5dASD$y,col='orange',lwd=2,lty=2)
+
+lines(spl5bCON$x,spl5aCON$y/spl5cCON$y,col='blue',lwd=2,lty=3)
+lines(spl5bCON$x,spl5aCON$y/spl5dCON$y,col='orange',lwd=2,lty=3)
+
+plotlims <- c(-1,8,0,30)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+ticklocsx <- -1:8    # locations of tick marks on x axis
+ticklocsy <- seq(0,30,10)    # locations of tick marks on y axis
+ticklabelsx <- -1:8        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+# lines(times,1000*MEGmeantime7Hz[1,],lwd=2,col='red')
+# lines(times,1000*MEGmeantime7Hz[2,],lwd=2,col='green')
+# lines(times,1000*MEGmeantime7Hz[3,],lwd=2,col='blue')
+# lines(times,1000*MEGmeantime7Hz[4,],lwd=2,col='orange')
+spl7a <- smooth.spline(times,1000*MEGmeantime7Hz[1,],df=20)
+lines(spl7a$x,spl7a$y,col='red',lwd=2)
+spl7b <- smooth.spline(times,1000*MEGmeantime7Hz[2,],df=20)
+lines(spl7b$x,spl7b$y,col='green',lwd=2)
+spl7c <- smooth.spline(times,1000*MEGmeantime7Hz[3,],df=20)
+lines(spl7c$x,spl7c$y,col='blue',lwd=2)
+spl7d <- smooth.spline(times,1000*MEGmeantime7Hz[4,],df=20)
+lines(spl7d$x,spl7d$y,col='orange',lwd=2)
+
+# lines(times,1000*MEGmeantime7HzASD[1,],lwd=2,col='red',lty=2)
+# lines(times,1000*MEGmeantime7HzASD[2,],lwd=2,col='green',lty=2)
+# lines(times,1000*MEGmeantime7HzASD[3,],lwd=2,col='blue',lty=2)
+# lines(times,1000*MEGmeantime7HzASD[4,],lwd=2,col='orange',lty=2)
+spl7aASD <- smooth.spline(times,1000*MEGmeantime7HzASD[1,],df=20)
+lines(spl7aASD$x,spl7aASD$y,col='red',lwd=2,lty=2)
+spl7bASD <- smooth.spline(times,1000*MEGmeantime7HzASD[2,],df=20)
+lines(spl7bASD$x,spl7bASD$y,col='green',lwd=2,lty=2)
+spl7cASD <- smooth.spline(times,1000*MEGmeantime7HzASD[3,],df=20)
+lines(spl7cASD$x,spl7cASD$y,col='blue',lwd=2,lty=2)
+spl7dASD <- smooth.spline(times,1000*MEGmeantime7HzASD[4,],df=20)
+lines(spl7dASD$x,spl7dASD$y,col='orange',lwd=2,lty=2)
+
+# lines(times,1000*MEGmeantime7HzCON[1,],lwd=2,col='red',lty=3)
+# lines(times,1000*MEGmeantime7HzCON[2,],lwd=2,col='green',lty=3)
+# lines(times,1000*MEGmeantime7HzCON[3,],lwd=2,col='blue',lty=3)
+# lines(times,1000*MEGmeantime7HzCON[4,],lwd=2,col='orange',lty=3)
+spl7aCON <- smooth.spline(times,1000*MEGmeantime7HzCON[1,],df=20)
+lines(spl7aCON$x,spl7aCON$y,col='red',lwd=2,lty=3)
+spl7bCON <- smooth.spline(times,1000*MEGmeantime7HzCON[2,],df=20)
+lines(spl7bCON$x,spl7bCON$y,col='green',lwd=2,lty=3)
+spl7cCON <- smooth.spline(times,1000*MEGmeantime7HzCON[3,],df=20)
+lines(spl7cCON$x,spl7cCON$y,col='blue',lwd=2,lty=3)
+spl7dCON <- smooth.spline(times,1000*MEGmeantime7HzCON[4,],df=20)
+lines(spl7dCON$x,spl7dCON$y,col='orange',lwd=2,lty=3)
+
+plotlims <- c(-1,8,0,2)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+ticklocsx <- -1:8    # locations of tick marks on x axis
+ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
+ticklabelsx <- -1:8        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+lines(spl7b$x,spl7b$y/spl7c$y,col='blue',lwd=2)
+lines(spl7b$x,spl7b$y/spl7d$y,col='orange',lwd=2)
+
+lines(spl7bASD$x,spl7bASD$y/spl7cASD$y,col='blue',lwd=2,lty=2)
+lines(spl7bASD$x,spl7bASD$y/spl7dASD$y,col='orange',lwd=2,lty=2)
+
+lines(spl7bCON$x,spl7bCON$y/spl7cCON$y,col='blue',lwd=2,lty=3)
+lines(spl7bCON$x,spl7bCON$y/spl7dCON$y,col='orange',lwd=2,lty=3)
+
+# lines(times,1000*meanspec[1,2,],lwd=2,lty=2,col='red')
+# lines(times,1000*meanspec[2,2,],lwd=2,lty=2,col='green')
+# lines(times,1000*meanspec[3,2,],lwd=2,lty=2,col='blue')
+# lines(times,1000*meanspec[4,2,],lwd=2,lty=2,col='orange')
+
+# text(-0.5,3.8,paste0('N=',length(allRnos)),cex=2)
+# condlist <- c('5Hz target only','5Hz mask only','5Hz mon','5Hz dich','7Hz target only','7Hz mask only','7Hz mon','7Hz dich')
+# if (outputplot>0){legend(0,4,condlist,col=c('red','green','blue','orange'),lty=c(1,1,1,1,2,2,2,2),lwd=2,box.lwd=2)}
+
+```
+
 Figure summarising the MEG experiment

### 2022-05-17 manuscript.Rmd
Included MEG analysis code

@@
 
-MEGmeantime5HzCON <- matrix(0,nrow=4,ncol=8009) 
-MEGmeantime7HzCON <- matrix(0,nrow=4,ncol=8009) 
-MEGmeantime5HzASD <- matrix(0,nrow=4,ncol=8009) 
-MEGmeantime7HzASD <- matrix(0,nrow=4,ncol=8009) 
-for (cond in 1:4){
-MEGmeantime7HzCON[cond,] <- apply(abs(MEGtimecourse7Hz[which(sortedgroups==1),cond,]),2,mean)
-MEGmeantime5HzCON[cond,] <- apply(abs(MEGtimecourse5Hz[which(sortedgroups==1),cond,]),2,mean)
-MEGmeantime7HzASD[cond,] <- apply(abs(MEGtimecourse7Hz[which(sortedgroups==2),cond,]),2,mean)
-MEGmeantime5HzASD[cond,] <- apply(abs(MEGtimecourse5Hz[which(sortedgroups==2),cond,]),2,mean)
-}
-
 # par(mfrow=c(2,3))
@@
 
-# lines(times,1000*MEGmeantime5Hz[1,],lwd=2,col='red')
-# lines(times,1000*MEGmeantime5Hz[2,],lwd=2,col='green')
-# lines(times,1000*MEGmeantime5Hz[3,],lwd=2,col='blue')
-# lines(times,1000*MEGmeantime5Hz[4,],lwd=2,col='orange')
+lines(times,1000*MEGmeantime5Hz[1,],lwd=2,col='red')
+lines(times,1000*MEGmeantime5Hz[2,],lwd=2,col='green')
+lines(times,1000*MEGmeantime5Hz[3,],lwd=2,col='blue')
+lines(times,1000*MEGmeantime5Hz[4,],lwd=2,col='orange')
 spl5a <- smooth.spline(times,1000*MEGmeantime5Hz[1,],df=20)
@@
 lines(spl5d$x,spl5d$y,col='orange',lwd=2)
-
-# lines(times,1000*MEGmeantime5HzASD[1,],lwd=2,col='red',lty=2)
-# lines(times,1000*MEGmeantime5HzASD[2,],lwd=2,col='green',lty=2)
-# lines(times,1000*MEGmeantime5HzASD[3,],lwd=2,col='blue',lty=2)
-# lines(times,1000*MEGmeantime5HzASD[4,],lwd=2,col='orange',lty=2)
-spl5aASD <- smooth.spline(times,1000*MEGmeantime5HzASD[1,],df=20)
-lines(spl5aASD$x,spl5aASD$y,col='red',lwd=2,lty=2)
-spl5bASD <- smooth.spline(times,1000*MEGmeantime5HzASD[2,],df=20)
-lines(spl5bASD$x,spl5bASD$y,col='green',lwd=2,lty=2)
-spl5cASD <- smooth.spline(times,1000*MEGmeantime5HzASD[3,],df=20)
-lines(spl5cASD$x,spl5cASD$y,col='blue',lwd=2,lty=2)
-spl5dASD <- smooth.spline(times,1000*MEGmeantime5HzASD[4,],df=20)
-lines(spl5dASD$x,spl5dASD$y,col='orange',lwd=2,lty=2)
-
-# lines(times,1000*MEGmeantime5HzCON[1,],lwd=2,col='red',lty=3)
-# lines(times,1000*MEGmeantime5HzCON[2,],lwd=2,col='green',lty=3)
-# lines(times,1000*MEGmeantime5HzCON[3,],lwd=2,col='blue',lty=3)
-# lines(times,1000*MEGmeantime5HzCON[4,],lwd=2,col='orange',lty=3)
-spl5aCON <- smooth.spline(times,1000*MEGmeantime5HzCON[1,],df=20)
-lines(spl5aCON$x,spl5aCON$y,col='red',lwd=2,lty=3)
-spl5bCON <- smooth.spline(times,1000*MEGmeantime5HzCON[2,],df=20)
-lines(spl5bCON$x,spl5bCON$y,col='green',lwd=2,lty=3)
-spl5cCON <- smooth.spline(times,1000*MEGmeantime5HzCON[3,],df=20)
-lines(spl5cCON$x,spl5cCON$y,col='blue',lwd=2,lty=3)
-spl5dCON <- smooth.spline(times,1000*MEGmeantime5HzCON[4,],df=20)
-lines(spl5dCON$x,spl5dCON$y,col='orange',lwd=2,lty=3)
 
@@
 
-lines(spl5bASD$x,spl5aASD$y/spl5cASD$y,col='blue',lwd=2,lty=2)
-lines(spl5bASD$x,spl5aASD$y/spl5dASD$y,col='orange',lwd=2,lty=2)
-
-lines(spl5bCON$x,spl5aCON$y/spl5cCON$y,col='blue',lwd=2,lty=3)
-lines(spl5bCON$x,spl5aCON$y/spl5dCON$y,col='orange',lwd=2,lty=3)
-
 plotlims <- c(-1,8,0,30)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
@@
 
-# lines(times,1000*MEGmeantime7Hz[1,],lwd=2,col='red')
-# lines(times,1000*MEGmeantime7Hz[2,],lwd=2,col='green')
-# lines(times,1000*MEGmeantime7Hz[3,],lwd=2,col='blue')
-# lines(times,1000*MEGmeantime7Hz[4,],lwd=2,col='orange')
+lines(times,1000*MEGmeantime7Hz[1,],lwd=2,col='red')
+lines(times,1000*MEGmeantime7Hz[2,],lwd=2,col='green')
+lines(times,1000*MEGmeantime7Hz[3,],lwd=2,col='blue')
+lines(times,1000*MEGmeantime7Hz[4,],lwd=2,col='orange')
 spl7a <- smooth.spline(times,1000*MEGmeantime7Hz[1,],df=20)
@@
 lines(spl7d$x,spl7d$y,col='orange',lwd=2)
-
-# lines(times,1000*MEGmeantime7HzASD[1,],lwd=2,col='red',lty=2)
-# lines(times,1000*MEGmeantime7HzASD[2,],lwd=2,col='green',lty=2)
-# lines(times,1000*MEGmeantime7HzASD[3,],lwd=2,col='blue',lty=2)
-# lines(times,1000*MEGmeantime7HzASD[4,],lwd=2,col='orange',lty=2)
-spl7aASD <- smooth.spline(times,1000*MEGmeantime7HzASD[1,],df=20)
-lines(spl7aASD$x,spl7aASD$y,col='red',lwd=2,lty=2)
-spl7bASD <- smooth.spline(times,1000*MEGmeantime7HzASD[2,],df=20)
-lines(spl7bASD$x,spl7bASD$y,col='green',lwd=2,lty=2)
-spl7cASD <- smooth.spline(times,1000*MEGmeantime7HzASD[3,],df=20)
-lines(spl7cASD$x,spl7cASD$y,col='blue',lwd=2,lty=2)
-spl7dASD <- smooth.spline(times,1000*MEGmeantime7HzASD[4,],df=20)
-lines(spl7dASD$x,spl7dASD$y,col='orange',lwd=2,lty=2)
-
-# lines(times,1000*MEGmeantime7HzCON[1,],lwd=2,col='red',lty=3)
-# lines(times,1000*MEGmeantime7HzCON[2,],lwd=2,col='green',lty=3)
-# lines(times,1000*MEGmeantime7HzCON[3,],lwd=2,col='blue',lty=3)
-# lines(times,1000*MEGmeantime7HzCON[4,],lwd=2,col='orange',lty=3)
-spl7aCON <- smooth.spline(times,1000*MEGmeantime7HzCON[1,],df=20)
-lines(spl7aCON$x,spl7aCON$y,col='red',lwd=2,lty=3)
-spl7bCON <- smooth.spline(times,1000*MEGmeantime7HzCON[2,],df=20)
-lines(spl7bCON$x,spl7bCON$y,col='green',lwd=2,lty=3)
-spl7cCON <- smooth.spline(times,1000*MEGmeantime7HzCON[3,],df=20)
-lines(spl7cCON$x,spl7cCON$y,col='blue',lwd=2,lty=3)
-spl7dCON <- smooth.spline(times,1000*MEGmeantime7HzCON[4,],df=20)
-lines(spl7dCON$x,spl7dCON$y,col='orange',lwd=2,lty=3)
 
@@
 lines(spl7b$x,spl7b$y/spl7d$y,col='orange',lwd=2)
-
-lines(spl7bASD$x,spl7bASD$y/spl7cASD$y,col='blue',lwd=2,lty=2)
-lines(spl7bASD$x,spl7bASD$y/spl7dASD$y,col='orange',lwd=2,lty=2)
-
-lines(spl7bCON$x,spl7bCON$y/spl7cCON$y,col='blue',lwd=2,lty=3)
-lines(spl7bCON$x,spl7bCON$y/spl7dCON$y,col='orange',lwd=2,lty=3)
 

### 2022-05-22 manuscript.Rmd
Updates to analysis code

--- 2022-05-17 manuscript.Rmd
@@
 ---
-title: "The Dynamics of Normalization Reweighting"
+title: "The Dynamics of Normalization Reweighting (target journal: Neuron)"
 author: "Daniel H.
@@
 if (!dir.exists('temp/MEGdata/')){dir.create('temp/MEGdata/')}
+if (!dir.exists('temp/EEGprocessed/')){dir.create('temp/EEGprocessed/')}
 
@@
 
+```{r}
+
+samplerate <- 1000
+targetF <- 5
+maskF <- 7
+    binwidth <- 1000
+    tindex <- 1 + targetF*(binwidth/samplerate)
+    mindex <- 1 + maskF*(binwidth/samplerate)
+
+d <- dir(path = 'temp/EEGprocessed', pattern = '*.RData', full.names=TRUE)
+
+groupmeans <- array(0,dim=c(length(d),4,4,10))
+groupspec <- array(0,dim=c(length(d),4,64,121))
+groupspecplot <- array(0,dim=c(length(d),4,121))
+groupwaveforms <- array(0,dim=c(length(d),4,8000))
+EEGtimecourse5Hz <- array(0,dim=c(length(d),4,7000))
+EEGtimecourse7Hz <- array(0,dim=c(length(d),4,7000))
+
+for (s in 1:length(d)){
+  load(d[s])
+
+  # remove any NaN values
+  chanspec[which(is.na(chanspec))] <- 0
+  allspec[which(is.na(allspec))] <- 0
+  allsamples[which(is.na(allsamples))] <- 0
+
+  ch <- match(toupper(targetelectrodes),toupper(electrodes),nomatch=0)
+
+  meanchanspec <- (apply(chanspec,2:4,mean))
+  spectoplot <- (apply(chanspec[,,ch,],c(2,4),mean))
+
+  meanspec <- (apply(allspec,2:4,mean))
+  for (f in 1:4){
+    for (cond in 1:4){
+      for (t in 1:10){
+        temp <- allspec[,f,cond,t]
+        tempxy <- data.frame(Re(temp),Im(temp))
+        D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+        i <- which(D<3)
+        meanspec[f,cond,t] <- (mean(temp[i]))
+      }
+    }
+  }
+  meanwaves <- apply(allsamples,2:3,mean)
+
+  for (cond in 1:4){
+   fspec1 <- NULL
+fspec2 <- NULL
+for (t in 1:(8000-binwidth)){
+  spec <- fft(meanwaves[cond,t:(t+binwidth-1)])/binwidth
+  fspec1[t] <- spec[tindex]
+  fspec2[t] <- spec[mindex]
+}
+    EEGtimecourse5Hz[s,cond,] <- fspec1
+    EEGtimecourse7Hz[s,cond,] <- fspec2 
+  }
+
+  meanwaves <- meanwaves - mean(meanwaves)
+  meanwaves <- meanwaves / max(abs(meanwaves))
+  groupmeans[s,,,] <- meanspec
+  groupspec[s,,,] <- meanchanspec
+  groupspecplot[s,,] <- spectoplot
+  groupwaveforms[s,,] <- meanwaves
+
+}
+
+meanspec <- abs(apply(groupmeans,c(2,3,4),mean))
+spectoplot <- abs(apply(groupspecplot,c(2,3),mean))
+meanwaves <- apply(groupwaveforms,c(2,3),mean)
+meanchanspec <- abs(apply(groupspec,c(2,3,4),mean))
+
+EEGmeantime5Hz <- matrix(0,nrow=4,ncol=7000) 
+EEGmeantime7Hz <- matrix(0,nrow=4,ncol=7000) 
+for (cond in 1:4){
+EEGmeantime7Hz[cond,] <- apply(abs(EEGtimecourse7Hz[,cond,]),2,mean)
+EEGmeantime5Hz[cond,] <- apply(abs(EEGtimecourse5Hz[,cond,]),2,mean)
+}
+
+par(mfrow=c(2,2))
+
+times <- ((1:7000)-500)/1000
+
+plotlims <- c(-1,8,0,1)
+ticklocsx <- -1:8    # locations of tick marks on x axis
+ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
+ticklabelsx <- -1:8        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+lines(times,EEGmeantime5Hz[1,],lwd=2,col='red')
+lines(times,EEGmeantime5Hz[2,],lwd=2,col='green')
+lines(times,EEGmeantime5Hz[3,],lwd=2,col='blue')
+lines(times,EEGmeantime5Hz[4,],lwd=2,col='orange')
+
+spl5a <- smooth.spline(times,EEGmeantime5Hz[1,],df=20)
+lines(spl5a$x,spl5a$y,col='red',lwd=2)
+spl5b <- smooth.spline(times,EEGmeantime5Hz[2,],df=20)
+lines(spl5b$x,spl5b$y,col='green',lwd=2)
+spl5c <- smooth.spline(times,EEGmeantime5Hz[3,],df=20)
+lines(spl5c$x,spl5c$y,col='blue',lwd=2)
+spl5d <- smooth.spline(times,EEGmeantime5Hz[4,],df=20)
+lines(spl5d$x,spl5d$y,col='orange',lwd=2)
+
+plotlims <- c(-1,8,0,2) 
+ticklocsx <- -1:8    # locations of tick marks on x axis
+ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
+ticklabelsx <- -1:8        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+lines(times,EEGmeantime5Hz[1,]/EEGmeantime5Hz[3,],col='blue',lwd=2)
+lines(times,EEGmeantime5Hz[1,]/EEGmeantime5Hz[4,],col='orange',lwd=2)
+
+lines(spl5a$x,spl5a$y/spl5c$y,col='blue',lwd=2)
+lines(spl5a$x,spl5a$y/spl5d$y,col='orange',lwd=2)
+
+plotlims <- c(-1,8,0,1) 
+ticklocsx <- -1:8    # locations of tick marks on x axis
+ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+lines(times,EEGmeantime7Hz[1,],lwd=2,col='red')
+lines(times,EEGmeantime7Hz[2,],lwd=2,col='green')
+lines(times,EEGmeantime7Hz[3,],lwd=2,col='blue')
+lines(times,EEGmeantime7Hz[4,],lwd=2,col='orange')
+
+spl7a <- smooth.spline(times,EEGmeantime7Hz[1,],df=20)
+lines(spl7a$x,spl7a$y,col='red',lwd=2)
+spl7b <- smooth.spline(times,EEGmeantime7Hz[2,],df=20)
+lines(spl7b$x,spl7b$y,col='green',lwd=2)
+spl7c <- smooth.spline(times,EEGmeantime7Hz[3,],df=20)
+lines(spl7c$x,spl7c$y,col='blue',lwd=2)
+spl7d <- smooth.spline(times,EEGmeantime7Hz[4,],df=20)
+lines(spl7d$x,spl7d$y,col='orange',lwd=2)
+
+plotlims <- c(-1,8,0,2) 
+ticklocsx <- -1:8    # locations of tick marks on x axis
+ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
+ticklabelsx <- -1:8        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+lines(times,EEGmeantime7Hz[2,]/EEGmeantime7Hz[3,],col='blue',lwd=2)
+lines(times,EEGmeantime7Hz[2,]/EEGmeantime7Hz[4,],col='orange',lwd=2)
+
+lines(spl7b$x,spl7b$y/spl7c$y,col='blue',lwd=2)
+lines(spl7b$x,spl7b$y/spl7d$y,col='orange',lwd=2)
+
+```
+
 Participants showed a wide range of scores on both the AQ and SPQ scales, which were negatively correlated (Fig 3a; R = , p < ).
@@
     binwidth <- 1001
-    tindex <- 1 + targetF*(binwidth/1001)
-    mindex <- 1 + maskF*(binwidth/1001)
+    tindex <- 1 + targetF*(binwidth/samplerate)
+    mindex <- 1 + maskF*(binwidth/samplerate)
 
+# d <- dir(path = 'temp/V2/', pattern = '*alltrialsV2.mat', full.names=TRUE)
+# d2 <- dir(path = 'temp/V2/', pattern = '*alltrialsV2.mat', full.names=FALSE)
 d <- dir(path = 'temp/MEGdata/', pattern = '*alltrials.mat', full.names=TRUE)
@@
 
-# par(mfrow=c(2,3))
+par(mfrow=c(2,2))
 

### 2022-05-22 manuscript.Rmd
Update manuscript.Rmd

@@
 ---
-title: "The Dynamics of Normalization Reweighting (target journal: Neuron)"
-author: "Daniel H.
-Baker, Daniela Marinova, Richard Aveyard, Lydia Hargreaves, Alice Renton, Ruby Castellani, Phoebe Hall, Miriam Harmens, Georgia Holroyd, Dorian Manning, Beth Nicholson, Emily Williams, Hannah M.
-Hobson & Alex R.
-Wade"
+title: 'The Dynamics of Normalization Reweighting (target journal: Neuron)'
+author: Daniel H. Baker, Daniela Marinova, Richard Aveyard, Lydia Hargreaves, Alice
+  Renton, Ruby Castellani, Phoebe Hall, Miriam Harmens, Georgia Holroyd, Dorian Manning,
+  Beth Nicholson, Emily Williams, Hannah M. Hobson & Alex R. Wade
 date: "`r Sys.Date()`"
-output: html_document
+output:
+  bookdown::pdf_document2:
+    fig_caption: yes 
+    toc: false   
+    keep_tex: true
+  word_document: default
+  html_document: default
 ---
@@
 runcode <- 1  # this flag chooses whether to run the underlying analysis code (1), or just load in the figures from the last time this was run (0)
-processraw <- 0  # this flag determines whether the raw data are downloaded from OSF and processed - this will require ~30GB of hard drive space and take several hours
+processraw <- 1  # this flag determines whether the raw data are downloaded from OSF and processed - this will require ~30GB of hard drive space and take several hours
 
 # reasonably compact code to check which packages are installed, install the missing ones, and activate all
-packagelist <- c('knitr','remotes','tictoc','R.matlab') # list of CRAN packages
+packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
@@
 if (!dir.exists('temp/')){dir.create('temp/')}
+if (!dir.exists('temp/figures/')){dir.create('temp/figures/')}
 if (!dir.exists('temp/VilidaiteProcessed/')){dir.create('temp/VilidaiteProcessed/')}
@@
 targetelectrodes <- c('Oz','POz','O1','O2')
+# targetelectrodes <- c('PO8','PO6','PO5','PO7')
 
@@
 
-```{r}
+```{r include=FALSE, results='hide'}
 
@@
 
-abs(colMeans(mean5))
-abs(colMeans(mean7))
-
 ```
@@
     mindex <- 1 + maskF*(binwidth/samplerate)
+
+ if (processraw==1){
 
@@
 
-  ch <- match(toupper(targetelectrodes),toupper(electrodes),nomatch=0)
+  ch <- match(targetelectrodes, electrodes) - 2
 
@@
 
+save(file='temp/EEGsummary.RData',list=c('groupmeans','groupspecplot','groupwaveforms','groupspec','EEGtimecourse5Hz','EEGtimecourse7Hz','electrodes'))
+
+ }
+
+if (runcode==1){
+load('temp/EEGsummary.RData')
+
 meanspec <- abs(apply(groupmeans,c(2,3,4),mean))
@@
 }
+
+pdf("temp/figures/Fig3.pdf", bg="transparent", height = 10, width = 10)
 
@@
 
+dev.off()
+
+}
+
+```
+
+```{r EEGdata, fig.cap="E.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('temp/figures/Fig3.pdf')
+
 ```
@@
 
-```{r}
+```{r include=FALSE, results='hide'}
+
+if (processraw==1){
 
@@
 
+save(file='temp/MEGsummary.RData',list=c('allspectra','allresps','allwaves','MEGtimecourse5Hz','MEGtimecourse7Hz','allRnos'))
+}
+
+if (runcode==1){
+
+  load('temp/MEGsummary.RData')
+
 allresps <- abs(allresps)
@@
 }
+
+pdf("temp/figures/Fig4.pdf", bg="transparent", height = 10, width = 10)
 
@@
 
+dev.off()
+}
+
+```
+
+```{r MEGdata, fig.cap="E.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('temp/figures/Fig4.pdf')
+
 ```

### 2022-05-23 renameandupload.R
Added renameandupload.R

@@ -1,0 +1,83 @@
+# script to rename raw EEG files to preserve participant anonymity
+# also re-orders by AQ score, and uploads data to OSF
+# DHB 23/5/22
+
+packagelist <- c('remotes','tictoc','utils')
+missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
+if (length(missingpackages)>0){install.packages(missingpackages)}
+if (packagelist[!'osfr' %in% installed.packages()[,1]]){remotes::install_github("centerforopenscience/osfr")}
+packagelist <- c(packagelist,'osfr')
+toinstall <- packagelist[which(!packagelist %in% (.packages()))]
+invisible(lapply(toinstall,library,character.only=TRUE))
+
+
+osf_auth(token = '3dEYuhZNmwWbG3xuhRIiVRo0T2oniOkEP3Ip8i1LPG4PNjeTRln54eGNAG7oyTT9xozWwJ')
+osfproject <- osf_retrieve_node("ab3yv")
+componentlist <- osf_ls_nodes(osfproject)
+EEGID <- pmatch('Raw EEG data 1',as.character(unlist(componentlist[,1])))
+EEGtokenLow <- componentlist[EEGID,2]
+EEGfilesLow <- osf_ls_files(EEGtokenLow,n_max=300)
+EEGID <- pmatch('Raw EEG data 2',as.character(unlist(componentlist[,1])))
+EEGtokenHi <- componentlist[EEGID,2]
+EEGfilesHi <- osf_ls_files(EEGtokenHi,n_max=300)
+
+rawdata <- read.csv('~/Google Drive/Current work/Teaching/BSc projects 2021/ASD/BSc project questionnaires 2021 (Responses) - Form Responses 1.csv')
+
+IDnos <- readMat('~/Google Drive/Current work/Research/normalization/IDnos.mat')
+uniqueID <- unlist(IDnos$allU)
+load('~/Google Drive/Current work/Research/normalization/questionnairedata.RData')
+QIDs <- as.character(qdata$ID)
+
+# fix duplicate ID numbers
+uniqueID[12] <- '2001b'
+QIDs[12] <- '2001b'
+uniqueID[46] <- '2001c'
+QIDs[46] <- '2001c'
+uniqueID[56] <- '1357b'
+QIDs[55] <- '1357b'
+uniqueID[70] <- '1234b'
[…]

### 2022-05-24 manuscript.Rmd
Update manuscript.Rmd

@@
 
+hdata <- read.csv('~/Google Drive/Current work/R scripts/EEG analysis/headerfile.csv', header = TRUE)
+
 ```
@@
 maskF <- 7
+duration <- 6
     binwidth <- 1000
@@
     mindex <- 1 + maskF*(binwidth/samplerate)
+    legaltriggers <- c(210,211,220,221,230,231,240,241)
 
  if (processraw==1){
+
+osfproject <- osf_retrieve_node("ab3yv")
+componentlist <- osf_ls_nodes(osfproject)
+EEGID <- pmatch('Raw EEG data 1',as.character(unlist(componentlist[,1])))
+EEGID[2] <- pmatch('Raw EEG data 2',as.character(unlist(componentlist[,1])))
+
+subjcounter <- 0
+for (datahalf in 1:length(EEGID)){
+  EEGtoken <- componentlist[EEGID[datahalf],2]
+  EEGfiles <- osf_ls_files(EEGtoken,n_max=300)
+  for (f in 1:nrow(EEGfiles)){
+    subjcounter <- subcounter + 1
+
+    # first check if we have this participant's data
+    if (!file.exists(paste0('temp/EEGprocessed/S',subjcounter,'data.RData'))){
+      # if we haven't processed the data, check if we need to download the raw data
+      if (!dir.exists(paste0('temp/raw/S',subjcounter))){
+        if (!file.exists(paste0('temp/raw/S',subjcounter,'.zip'))){
+          osf_download(EEGfiles[f,], path='temp/raw/',progress=TRUE)
+        }
+          unzip(paste0('temp/raw/S',subjcounter,'.zip'),exdir='temp/raw/')
+          file.remove(paste0('temp/raw/S',subjcounter,'.zip'))
+      }
+    # if necessary, process the data for this participant
+
+      d <- dir(paste0('temp/raw/S',subjcounter), pattern='*.csv.gz',full.names=TRUE)
+      condcounter <- (1:4) * 0
+      alltrials <- array(0,dim=c(50,4,9000,64))
+      subjwaves <- array(0,dim=c(4,9000,64))
+      trialsincluded <- matrix(0,nrow=4,ncol=64)
+
+      for (block in 1:length(d)){
+      EEGdata <- read.csv(d[block], header = TRUE)
+      electrodes <- colnames(EEGdata)
+
+     triggertimes <- (1:64) * 0
+    counter <- 0
+    for (n in 1:nrow(EEGdata)) {
+      if (EEGdata$Trigger[n] %in% legaltriggers) {
+        counter <- counter + 1
+        triggertimes[counter] <- n
+      }
+    }
+
+     for (tr in 1:counter) {
+      cond <- which(legaltriggers == EEGdata$Trigger[triggertimes[tr]])
+      cond <- ceiling(cond/2)
+      condcounter[cond] <- condcounter[cond] + 1
+
+      # # horrible hack to fix one trial for P227
+      # if (33-samplerate+(triggertimes[tr])<0){
+      #   if (pno == 227){triggertimes[tr] <- triggertimes[tr] + 150}
+      #   if (pno == 279){triggertimes[tr] <- triggertimes[tr] + 150}
+      #  }
+    for (ch in 1:64){     
+      alltrials[condcounter[cond],cond,,ch] <- as.matrix(EEGdata[33-(1.5*samplerate)+(triggertimes[tr]:(triggertimes[tr] + samplerate * (3+duration) - 1)), ch+3])}
+
+     }
+
+      }
+
+      for (cond in 1:4){
+        for (ch in 1:64){
+
+          temp <- alltrials[1:condcounter[cond],cond,,ch]
+
+          spec5 <- NULL
+          spec7 <- NULL
+          for (t in 1:condcounter[cond]){
+            spec <- fft(temp[t,1501:7500])
+            spec5[t] <- spec[6*5+1]
+            spec7[t] <- spec[7*5+1]
+          }
+        spec5[which(is.na(spec5))] <- 0
+        spec7[which(is.na(spec7))] <- 0
+      if (sum(abs(spec5))>0){  
+      tempxy <- data.frame(Re(spec5),Im(spec5))
+      D5 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+      tempxy <- data.frame(Re(spec7),Im(spec7))
+      D7 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))      
+      i <- which(D5<3 & D7<3)
+      trialsincluded[cond,ch] <- length(i)
+      subjwaves[cond,,ch] <- colMeans(temp[i,])
+      }   
+        }
+      }
+
+      qdatasubj <- read.csv(paste0('temp/raw/S',subjcounter,'/questionnairedata.csv'))
+      save(file=paste0('temp/EEGprocessed/S',subjcounter,'data.RData'),list=c('qdatasubj','condcounter','trialsincluded','subjwaves'))
+    }
+
+ }
+}
 

### 2022-05-24 renameandupload.R
Update renameandupload.R

@@ -2,7 +2,7 @@
 # also re-orders by AQ score, and uploads data to OSF
 # DHB 23/5/22
 
-packagelist <- c('remotes','tictoc','utils')
+packagelist <- c('remotes','tictoc','utils','R.matlab')
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
 if (length(missingpackages)>0){install.packages(missingpackages)}
 if (packagelist[!'osfr' %in% installed.packages()[,1]]){remotes::install_github("centerforopenscience/osfr")}
@@ -10,8 +10,9 @@ packagelist <- c(packagelist,'osfr')
 toinstall <- packagelist[which(!packagelist %in% (.packages()))]
 invisible(lapply(toinstall,library,character.only=TRUE))
 
+my_wd <- getwd()
 
-osf_auth(token = '3dEYuhZNmwWbG3xuhRIiVRo0T2oniOkEP3Ip8i1LPG4PNjeTRln54eGNAG7oyTT9xozWwJ')
+osf_auth(token = '')
 osfproject <- osf_retrieve_node("ab3yv")
 componentlist <- osf_ls_nodes(osfproject)
 EEGID <- pmatch('Raw EEG data 1',as.character(unlist(componentlist[,1])))
@@ -20,6 +21,8 @@ EEGfilesLow <- osf_ls_files(EEGtokenLow,n_max=300)
 EEGID <- pmatch('Raw EEG data 2',as.character(unlist(componentlist[,1])))
 EEGtokenHi <- componentlist[EEGID,2]
 EEGfilesHi <- osf_ls_files(EEGtokenHi,n_max=300)
+
+rawdatadir <- '~/Desktop/UG2021/'
 
 rawdata <- read.csv('~/Google Drive/Current work/Teaching/BSc projects 2021/ASD/BSc project questionnaires 2021 (Responses) - Form Responses 1.csv')
 
@@ -43,41 +46,63 @@ uniqueID[85] <- '2705b'
 QIDs[83] <- '2705b'
 QIDs[53] <- '5417'
 
-IDmatching <- data.frame(uniqueID,QIDs)
-
-# these are the indices in the questionnaire data for each EEG dataset
-Qindices <- NULL
-for (n in 1:nrow(IDmatching)){
-  Qindices[n] <- match(IDmatching[n,1],IDmatching[,2])
-}
-
-Eindices <- which(!is.na(Qindices))
-orderedAQ <- qdata$AQ[Qindices]
-
[…]

### 2022-05-24 manuscript.Rmd
Preprocessing for main EEG experiment

@@
 
+osf_auth(token = '3dEYuhZNmwWbG3xuhRIiVRo0T2oniOkEP3Ip8i1LPG4PNjeTRln54eGNAG7oyTT9xozWwJ')
+
 # helper function to make colours transparent
@@
 legaltriggers <- hdata$Trigger[!is.na(hdata$Trigger)]
-subcounter <- 0
+subjcounter <- 0
 
@@
   if (s != 75) {
-    subcounter <- subcounter + 1  
-  if (!file.exists(paste0('temp/VilidaiteProcessed/V',subcounter,'processed.RData'))){
+    subjcounter <- subjcounter + 1  
+  if (!file.exists(paste0('temp/VilidaiteProcessed/V',subjcounter,'processed.RData'))){
   print(s)
@@
 
-     save(file = paste0('temp/VilidaiteProcessed/V',subcounter,'processed.RData'), list = c('meanwaveforms','electrodes'))
+     save(file = paste0('temp/VilidaiteProcessed/V',subjcounter,'processed.RData'), list = c('meanwaveforms','electrodes'))
 
@@
   for (f in 1:nrow(EEGfiles)){
-    subjcounter <- subcounter + 1
-
+    subjcounter <- subjcounter + 1
+    print(subjcounter)
     # first check if we have this participant's data
@@
 
-     triggertimes <- (1:64) * 0
+    triggertimes <- NULL
     counter <- 0
@@
 
-     for (tr in 1:counter) {
+    # remove the first trial if there is not sufficient pre-trial baseline time
+    if (triggertimes[1]<1500){triggertimes <- triggertimes[2:counter]}
+
+     for (tr in 1:length(triggertimes)) {
       cond <- which(legaltriggers == EEGdata$Trigger[triggertimes[tr]])
@@
             spec <- fft(temp[t,1501:7500])
-            spec5[t] <- spec[6*5+1]
-            spec7[t] <- spec[7*5+1]
+            spec5[t] <- spec[targetF*duration+1]
+            spec7[t] <- spec[maskF*duration+1]
           }
@@
         spec7[which(is.na(spec7))] <- 0
-      if (sum(abs(spec5))>0){  
+      if (length(which(abs(spec5)>0))>2){  
       tempxy <- data.frame(Re(spec5),Im(spec5))
@@
 
-d <- dir(path = 'temp/EEGprocessed', pattern = '*.RData', full.names=TRUE)
-
-groupmeans <- array(0,dim=c(length(d),4,4,10))
-groupspec <- array(0,dim=c(length(d),4,64,121))
-groupspecplot <- array(0,dim=c(length(d),4,121))
-groupwaveforms <- array(0,dim=c(length(d),4,8000))
-EEGtimecourse5Hz <- array(0,dim=c(length(d),4,7000))
-EEGtimecourse7Hz <- array(0,dim=c(length(d),4,7000))
-
-for (s in 1:length(d)){
-  load(d[s])
-
-  # remove any NaN values
-  chanspec[which(is.na(chanspec))] <- 0
-  allspec[which(is.na(allspec))] <- 0
-  allsamples[which(is.na(allsamples))] <- 0
-
-  ch <- match(targetelectrodes, electrodes) - 2
-
-  meanchanspec <- (apply(chanspec,2:4,mean))
-  spectoplot <- (apply(chanspec[,,ch,],c(2,4),mean))
-
-  meanspec <- (apply(allspec,2:4,mean))
-  for (f in 1:4){
-    for (cond in 1:4){
-      for (t in 1:10){
-        temp <- allspec[,f,cond,t]
-        tempxy <- data.frame(Re(temp),Im(temp))
-        D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
-        i <- which(D<3)
-        meanspec[f,cond,t] <- (mean(temp[i]))
-      }
-    }
-  }
-  meanwaves <- apply(allsamples,2:3,mean)
-
-  for (cond in 1:4){
-   fspec1 <- NULL
-fspec2 <- NULL
-for (t in 1:(8000-binwidth)){
-  spec <- fft(meanwaves[cond,t:(t+binwidth-1)])/binwidth
-  fspec1[t] <- spec[tindex]
-  fspec2[t] <- spec[mindex]
-}
-    EEGtimecourse5Hz[s,cond,] <- fspec1
-    EEGtimecourse7Hz[s,cond,] <- fspec2 
-  }
-
-  meanwaves <- meanwaves - mean(meanwaves)
-  meanwaves <- meanwaves / max(abs(meanwaves))
-  groupmeans[s,,,] <- meanspec
-  groupspec[s,,,] <- meanchanspec
-  groupspecplot[s,,] <- spectoplot
-  groupwaveforms[s,,] <- meanwaves
-
-}
-
-save(file='temp/EEGsummary.RData',list=c('groupmeans','groupspecplot','groupwaveforms','groupspec','EEGtimecourse5Hz','EEGtimecourse7Hz','electrodes'))
-
- }
-
-if (runcode==1){
-load('temp/EEGsummary.RData')
-
-meanspec <- abs(apply(groupmeans,c(2,3,4),mean))
-spectoplot <- abs(apply(groupspecplot,c(2,3),mean))
-meanwaves <- apply(groupwaveforms,c(2,3),mean)
-meanchanspec <- abs(apply(groupspec,c(2,3,4),mean))
-
-EEGmeantime5Hz <- matrix(0,nrow=4,ncol=7000) 
-EEGmeantime7Hz <- matrix(0,nrow=4,ncol=7000) 
-for (cond in 1:4){
-EEGmeantime7Hz[cond,] <- apply(abs(EEGtimecourse7Hz[,cond,]),2,mean)
-EEGmeantime5Hz[cond,] <- apply(abs(EEGtimecourse5Hz[,cond,]),2,mean)
-}
-
-pdf("temp/figures/Fig3.pdf", bg="transparent", height = 10, width = 10)
-
-par(mfrow=c(2,2))
-
-times <- ((1:7000)-500)/1000
-
-plotlims <- c(-1,8,0,1)
-ticklocsx <- -1:8    # locations of tick marks on x axis
-ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
-ticklabelsx <- -1:8        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-lines(times,EEGmeantime5Hz[1,],lwd=2,col='red')
-lines(times,EEGmeantime5Hz[2,],lwd=2,col='green')
-lines(times,EEGmeantime5Hz[3,],lwd=2,col='blue')
-lines(times,EEGmeantime5Hz[4,],lwd=2,col='orange')
-
-spl5a <- smooth.spline(times,EEGmeantime5Hz[1,],df=20)
-lines(spl5a$x,spl5a$y,col='red',lwd=2)
-spl5b <- smooth.spline(times,EEGmeantime5Hz[2,],df=20)
-lines(spl5b$x,spl5b$y,col='green',lwd=2)
-spl5c <- smooth.spline(times,EEGmeantime5Hz[3,],df=20)
-lines(spl5c$x,spl5c$y,col='blue',lwd=2)
-spl5d <- smooth.spline(times,EEGmeantime5Hz[4,],df=20)
-lines(spl5d$x,spl5d$y,col='orange',lwd=2)
-
-plotlims <- c(-1,8,0,2) 
-ticklocsx <- -1:8    # locations of tick marks on x axis
-ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
-ticklabelsx <- -1:8        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-lines(times,EEGmeantime5Hz[1,]/EEGmeantime5Hz[3,],col='blue',lwd=2)
-lines(times,EEGmeantime5Hz[1,]/EEGmeantime5Hz[4,],col='orange',lwd=2)
-
-lines(spl5a$x,spl5a$y/spl5c$y,col='blue',lwd=2)
-lines(spl5a$x,spl5a$y/spl5d$y,col='orange',lwd=2)
-
-plotlims <- c(-1,8,0,1) 
-ticklocsx <- -1:8    # locations of tick marks on x axis
-ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-lines(times,EEGmeantime7Hz[1,],lwd=2,col='red')
-lines(times,EEGmeantime7Hz[2,],lwd=2,col='green')
-lines(times,EEGmeantime7Hz[3,],lwd=2,col='blue')
-lines(times,EEGmeantime7Hz[4,],lwd=2,col='orange')
-
-spl7a <- smooth.spline(times,EEGmeantime7Hz[1,],df=20)
-lines(spl7a$x,spl7a$y,col='red',lwd=2)
-spl7b <- smooth.spline(times,EEGmeantime7Hz[2,],df=20)
-lines(spl7b$x,spl7b$y,col='green',lwd=2)
-spl7c <- smooth.spline(times,EEGmeantime7Hz[3,],df=20)
-lines(spl7c$x,spl7c$y,col='blue',lwd=2)
-spl7d <- smooth.spline(times,EEGmeantime7Hz[4,],df=20)
-lines(spl7d$x,spl7d$y,col='orange',lwd=2)
-
-plotlims <- c(-1,8,0,2) 
-ticklocsx <- -1:8    # locations of tick marks on x axis
-ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
-ticklabelsx <- -1:8        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-lines(times,EEGmeantime7Hz[2,]/EEGmeantime7Hz[3,],col='blue',lwd=2)
-lines(times,EEGmeantime7Hz[2,]/EEGmeantime7Hz[4,],col='orange',lwd=2)
-
-lines(spl7b$x,spl7b$y/spl7c$y,col='blue',lwd=2)
-lines(spl7b$x,spl7b$y/spl7d$y,col='orange',lwd=2)
-
-dev.off()
-
+# d <- dir(path = 'temp/EEGprocessed', pattern = '*.RData', full.names=TRUE)
+# 
+# groupmeans <- array(0,dim=c(length(d),4,4,10))
+# groupspec <- array(0,dim=c(length(d),4,64,121))
+# groupspecplot <- array(0,dim=c(length(d),4,121))
+# groupwaveforms <- array(0,dim=c(length(d),4,8000))
+# EEGtimecourse5Hz <- array(0,dim=c(length(d),4,7000))
+# EEGtimecourse7Hz <- array(0,dim=c(length(d),4,7000))
+# 
+# for (s in 1:length(d)){
+#   load(d[s])
+#   
+#   # remove any NaN values
+#   chanspec[which(is.na(chanspec))] <- 0
+#   allspec[which(is.na(allspec))] <- 0
+#   allsamples[which(is.na(allsamples))] <- 0
+#   
+#   ch <- match(targetelectrodes, electrodes) - 2
+#   
+#   meanchanspec <- (apply(chanspec,2:4,mean))
+#   spectoplot <- (apply(chanspec[,,ch,],c(2,4),mean))
+#   
+#   meanspec <- (apply(allspec,2:4,mean))
+#   for (f in 1:4){
+#     for (cond in 1:4){
+#       for (t in 1:10){
+#         temp <- allspec[,f,cond,t]
+#         tempxy <- data.frame(Re(temp),Im(temp))
+#         D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+#         i <- which(D<3)
+#         meanspec[f,cond,t] <- (mean(temp[i]))
+#       }
+#     }
+#   }
+#   meanwaves <- apply(allsamples,2:3,mean)
+#   
+#   for (cond in 1:4){
+#    fspec1 <- NULL
+# fspec2 <- NULL
+# for (t in 1:(8000-binwidth)){
+#   spec <- fft(meanwaves[cond,t:(t+binwidth-1)])/binwidth
+#   fspec1[t] <- spec[tindex]
+#   fspec2[t] <- spec[mindex]
+# }
+#     EEGtimecourse5Hz[s,cond,] <- fspec1
+#     EEGtimecourse7Hz[s,cond,] <- fspec2 
+#   }
+#   
+#   meanwaves <- meanwaves - mean(meanwaves)
+#   meanwaves <- meanwaves / max(abs(meanwaves))
+#   groupmeans[s,,,] <- meanspec
+#   groupspec[s,,,] <- meanchanspec
+#   groupspecplot[s,,] <- spectoplot
+#   groupwaveforms[s,,] <- meanwaves
+#   
+# }
+# 
+# save(file='temp/EEGsummary.RData',list=c('groupmeans','groupspecplot','groupwaveforms','groupspec','EEGtimecourse5Hz','EEGtimecourse7Hz','electrodes'))
+# 
+#  }
+#     
+# if (runcode==1){
+# load('temp/EEGsummary.RData')
+#     
+# meanspec <- abs(apply(groupmeans,c(2,3,4),mean))
+# spectoplot <- abs(apply(groupspecplot,c(2,3),mean))
+# meanwaves <- apply(groupwaveforms,c(2,3),mean)
+# meanchanspec <- abs(apply(groupspec,c(2,3,4),mean))
+# 
+# EEGmeantime5Hz <- matrix(0,nrow=4,ncol=7000) 
+# EEGmeantime7Hz <- matrix(0,nrow=4,ncol=7000) 
+# for (cond in 1:4){
+# EEGmeantime7Hz[cond,] <- apply(abs(EEGtimecourse7Hz[,cond,]),2,mean)
+# EEGmeantime5Hz[cond,] <- apply(abs(EEGtimecourse5Hz[,cond,]),2,mean)
+# }
+# 
+# pdf("temp/figures/Fig3.pdf", bg="transparent", height = 10, width = 10)
+# 
+# par(mfrow=c(2,2))
+# 
+# times <- ((1:7000)-500)/1000
+# 
+# plotlims <- c(-1,8,0,1)
+# ticklocsx <- -1:8    # locations of tick marks on x axis
+# ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
+# ticklabelsx <- -1:8        # set labels for x ticks
+# ticklabelsy <- ticklocsy    # set labels for y ticks
+# plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+# axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
+# axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+# mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
+# mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+# title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+# title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+# 
+# lines(times,EEGmeantime5Hz[1,],lwd=2,col='red')
+# lines(times,EEGmeantime5Hz[2,],lwd=2,col='green')
+# lines(times,EEGmeantime5Hz[3,],lwd=2,col='blue')
+# lines(times,EEGmeantime5Hz[4,],lwd=2,col='orange')
+# 
+# 
+# spl5a <- smooth.spline(times,EEGmeantime5Hz[1,],df=20)
+# lines(spl5a$x,spl5a$y,col='red',lwd=2)
+# spl5b <- smooth.spline(times,EEGmeantime5Hz[2,],df=20)
+# lines(spl5b$x,spl5b$y,col='green',lwd=2)
+# spl5c <- smooth.spline(times,EEGmeantime5Hz[3,],df=20)
+# lines(spl5c$x,spl5c$y,col='blue',lwd=2)
+# spl5d <- smooth.spline(times,EEGmeantime5Hz[4,],df=20)
+# lines(spl5d$x,spl5d$y,col='orange',lwd=2)
+# 
+# 
+# plotlims <- c(-1,8,0,2) 
+# ticklocsx <- -1:8    # locations of tick marks on x axis
+# ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
+# ticklabelsx <- -1:8        # set labels for x ticks
+# ticklabelsy <- ticklocsy    # set labels for y ticks
+# plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+# axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
+# axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+# mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
+# mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+# title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+# title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+# 
+# lines(times,EEGmeantime5Hz[1,]/EEGmeantime5Hz[3,],col='blue',lwd=2)
+# lines(times,EEGmeantime5Hz[1,]/EEGmeantime5Hz[4,],col='orange',lwd=2)
+# 
+# lines(spl5a$x,spl5a$y/spl5c$y,col='blue',lwd=2)
+# lines(spl5a$x,spl5a$y/spl5d$y,col='orange',lwd=2)
+# 
+# 
+# plotlims <- c(-1,8,0,1) 
+# ticklocsx <- -1:8    # locations of tick marks on x axis
+# ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
+# plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+# axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
+# axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+# mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
+# mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+# title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+# title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+# 
+# 
+# lines(times,EEGmeantime7Hz[1,],lwd=2,col='red')
+# lines(times,EEGmeantime7Hz[2,],lwd=2,col='green')
+# lines(times,EEGmeantime7Hz[3,],lwd=2,col='blue')
+# lines(times,EEGmeantime7Hz[4,],lwd=2,col='orange')
+# 
+# 
+# spl7a <- smooth.spline(times,EEGmeantime7Hz[1,],df=20)
+# lines(spl7a$x,spl7a$y,col='red',lwd=2)
+# spl7b <- smooth.spline(times,EEGmeantime7Hz[2,],df=20)
+# lines(spl7b$x,spl7b$y,col='green',lwd=2)
+# spl7c <- smooth.spline(times,EEGmeantime7Hz[3,],df=20)
+# lines(spl7c$x,spl7c$y,col='blue',lwd=2)
+# spl7d <- smooth.spline(times,EEGmeantime7Hz[4,],df=20)
+# lines(spl7d$x,spl7d$y,col='orange',lwd=2)
+# 
+# 
+# plotlims <- c(-1,8,0,2) 
+# ticklocsx <- -1:8    # locations of tick marks on x axis
+# ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
+# ticklabelsx <- -1:8        # set labels for x ticks
+# ticklabelsy <- ticklocsy    # set labels for y ticks
+# plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+# axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
+# axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+# mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
+# mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+# title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+# title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+# 
+# lines(times,EEGmeantime7Hz[2,]/EEGmeantime7Hz[3,],col='blue',lwd=2)
+# lines(times,EEGmeantime7Hz[2,]/EEGmeantime7Hz[4,],col='orange',lwd=2)
+# 
+# lines(spl7b$x,spl7b$y/spl7c$y,col='blue',lwd=2)
+# lines(spl7b$x,spl7b$y/spl7d$y,col='orange',lwd=2)
+# 
+# dev.off()
+# 
 }

### 2022-06-06 manuscript.Rmd
Update manuscript.Rmd

@@
 
+plotsmoothed <- 0 # either plot the raw data (0), or a smoothed spline (1)
+
 # reasonably compact code to check which packages are installed, install the missing ones, and activate all
-packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown') # list of CRAN packages
+packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','tiff') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
@@
 
+v4Interp <- function(df, xo, yo, rmax = .75, gridRes = 67) {
+  ## Create a function to perform Matlab's v4 interpolation.
+  ## Takes as input a data-frame with columns x, y, and z (x co-ordinates, y co-ordinates, and amplitude)
+  ## and variables xo and yo, the co-ordinates which will be use to create a grid for interpolation
+  xo <- matrix(rep(xo,length(yo)),nrow = length(xo),ncol = length(yo))
+  yo <- t(matrix(rep(yo,length(xo)),nrow = length(yo),ncol = length(xo)))
+  xy <- df$x + df$y*sqrt(as.complex(-1))
+  d <- matrix(rep(xy,length(xy)),nrow = length(xy), ncol = length(xy))
+  d <- abs(d - t(d))
+  diag(d) <- 1
+  g <- (d^2) * (log(d)-1)   # Green's function.
+  diag(g) <- 0
+  weights <- qr.solve(g,df$z)
+  xy <- t(xy)
+  outmat <- matrix(nrow = gridRes,ncol = gridRes)
+  for (i in 1:gridRes){
+    for (j in 1:gridRes) {
+      test4 <- abs((xo[i,j] + sqrt(as.complex(-1))*yo[i,j]) - xy)
+      g <- (test4^2) * (log(test4)-1)
+      outmat[i,j] <- g %*% weights}}
+  outDf <- data.frame(x = xo[,1],outmat)
+  names(outDf)[1:length(yo[1,])+1] <- yo[1,]
+  return(outDf)}
+
 knitr::opts_chunk$set(echo = TRUE)
+colpal <- c('#000000','#8783CF','#FE5000','#004731','#603FB3')
 
@@
 targetelectrodes <- c('Oz','POz','O1','O2')
-# targetelectrodes <- c('PO8','PO6','PO5','PO7')
 
@@
 ## Abstract
+
+Our analysis of 220 human M/EEG datasets
 
@@
         for (ch in 1:64){
-        temp <- as.matrix(EEGdata[(triggertimes[tr]:(triggertimes[tr] + samplerate * duration - 1))-999, ch + 2])
-        temp <- temp - mean(temp[1:1000])   # baseline subtraction to remove DC component
+        temp <- as.matrix(EEGdata[(triggertimes[tr]:(triggertimes[tr] + samplerate * duration - 1))-1499, ch + 2])
+        temp <- temp - mean(temp[501:1500])   # baseline subtraction to remove DC component
         allsamples[condcounter[cond],cond,ch,1:(1000*duration)] <- as.vector(rowMeans(temp))
@@
         for (trial in 1:condcounter[cond]){
-          allspec[trial,] <- fft(temp[trial,2001:12000])/10000
+          allspec[trial,] <- fft(temp[trial,2501:12500])/10000
         }
@@
 # times <- -499:13500
-# plot(times,fspec,type='l',col='red')
+# plot(times,fspec,type='l',col=colpal[1])
 # lines(times,fspec2,col='green')
@@
     mindex <- 1 + f2*(binwidth/1000)
+    tindex2 <- 1 + 2*f1*(binwidth/1000)
+    mindex2 <- 1 + 2*f2*(binwidth/1000)
+
 condlist <- c(6,8,13)
 
-d <- dir('temp/VilidaiteProcessed/')
-all7Hz <- array(0,dim=c(length(d),14,64))
-all5Hz <- array(0,dim=c(length(d),14,64))
-timecourse7Hz <- array(0,dim=c(length(d),3,14000))
-timecourse5Hz <- array(0,dim=c(length(d),3,14000))
+d <- dir(path = 'temp/VilidaiteProcessed', pattern = '*.RData', full.names=TRUE)
+EEGtimecourse5Hz <- array(0,dim=c(length(d),3,13000))
+EEGtimecourse7Hz <- array(0,dim=c(length(d),3,13000))
+EEGtimecourse10Hz <- array(0,dim=c(length(d),3,13000))
+EEGtimecourse14Hz <- array(0,dim=c(length(d),3,13000))
 
 for (s in 1:length(d)){
-
-    load(paste0('temp/VilidaiteProcessed/',d[s]))
-
+  load(d[s])
   targetchannels <- match(targetelectrodes, electrodes) - 2
-
-    for (cond in 1:14){
-      for (ch in 1:64){
-        temp <- meanwaveforms[cond,ch,2001:12000]
-        spec <- fft(temp)/length(temp)
-        all7Hz[s,cond,ch] <- spec[7*10+1]
-        all5Hz[s,cond,ch] <- spec[5*10+1]
-      }
-    }
   for (cond in 1:3){
-    temp <- colMeans(meanwaveforms[condlist[cond],targetchannels,])
-
-fspec1 <- temp*0
-fspec2 <- temp*0
-for (t in 1:(length(temp)-binwidth)){
+    temp <- colMeans(meanwaveforms[condlist[cond],targetchannels,],na.rm=TRUE)
+    nainds <- which(is.na(temp))   # find occasional NaN values in the waveform
+    temp[nainds] <- 0   # replace with zeros
+
+fspec1 <- NULL
+fspec2 <- NULL
+fspec3 <- NULL
+fspec4 <- NULL
+for (t in 1:(14000-binwidth)){
   spec <- fft(temp[t:(t+binwidth-1)])/binwidth
@@
   fspec2[t] <- spec[mindex]
-}
-    timecourse7Hz[s,cond,] <- fspec1
-    timecourse5Hz[s,cond,] <- fspec2
-
-    }
-
-  }
-
-mean7 <- apply(all7Hz[,,targetchannels],1:2,mean)
-mean5 <- apply(all5Hz[,,targetchannels],1:2,mean)
-inclusionmatrix7 <- matrix(0,nrow=length(d),ncol=length(condlist))
-inclusionmatrix5 <- matrix(0,nrow=length(d),ncol=length(condlist))
+  fspec3[t] <- spec[tindex2]
+  fspec4[t] <- spec[mindex2]
+
+}
+    EEGtimecourse5Hz[s,cond,] <- fspec1
+    EEGtimecourse7Hz[s,cond,] <- fspec2
+    EEGtimecourse10Hz[s,cond,] <- fspec3
+    EEGtimecourse14Hz[s,cond,] <- fspec4
+
+  }
+
+}
+
+save(file='temp/Pilotsummary.RData',list=c('EEGtimecourse5Hz','EEGtimecourse7Hz','EEGtimecourse10Hz','EEGtimecourse14Hz','electrodes'))
+
+load('temp/Pilotsummary.RData')
+EEGmeantime5Hz <- matrix(0,nrow=3,ncol=13000)
+EEGmeantime7Hz <- matrix(0,nrow=3,ncol=13000)
+EEGmeantime10Hz <- matrix(0,nrow=3,ncol=13000)
+EEGmeantime14Hz <- matrix(0,nrow=3,ncol=13000)
+
 for (cond in 1:3){
-  temp <- mean7[,condlist[cond]]
-        tempxy <- data.frame(Re(temp),Im(temp))
-      D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
-      inclusionmatrix7[,cond] <- (D<3)
-   temp <- mean5[,condlist[cond]]
-        tempxy <- data.frame(Re(temp),Im(temp))
-      D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
-      inclusionmatrix5[,cond] <- (D<3)
-}
-
-meantime5Hz <- matrix(0,nrow=length(condlist),ncol=14000) 
-meantime7Hz <- matrix(0,nrow=length(condlist),ncol=14000) 
-for (cond in 1:3){
-meantime7Hz[cond,] <- abs(apply(abs(timecourse7Hz[which(inclusionmatrix7[,cond]>0),cond,]),2,mean))
-meantime5Hz[cond,] <- abs(apply(abs(timecourse5Hz[which(inclusionmatrix5[,cond]>0),cond,]),2,mean))
-}
-
-plot(-499:13500,meantime5Hz[2,],type='l',col='red')
-lines(-499:13500,meantime5Hz[1,],col='black')
-lines(-499:13500,meantime5Hz[3,],col='green')
-
-plot(-499:13500,meantime7Hz[1,],type='l',col='red')
-lines(-499:13500,meantime7Hz[2,],col='black')
-lines(-499:13500,meantime7Hz[3,],col='green')
+EEGmeantime5Hz[cond,] <- apply(abs(EEGtimecourse5Hz[,cond,]),2,mean,na.rm=TRUE)
+EEGmeantime7Hz[cond,] <- apply(abs(EEGtimecourse7Hz[,cond,]),2,mean,na.rm=TRUE)
+EEGmeantime10Hz[cond,] <- apply(abs(EEGtimecourse10Hz[,cond,]),2,mean,na.rm=TRUE)
+EEGmeantime14Hz[cond,] <- apply(abs(EEGtimecourse14Hz[,cond,]),2,mean,na.rm=TRUE)
+}
+
+EEGmaskindex5 <- colMeans(20*log10(abs(EEGtimecourse5Hz[,1,])/abs(EEGtimecourse5Hz[,3,])))
+EEGmaskindex7 <- colMeans(20*log10(abs(EEGtimecourse7Hz[,2,])/abs(EEGtimecourse7Hz[,3,])))
+EEGmaskindex10 <- colMeans(20*log10(abs(EEGtimecourse10Hz[,1,])/abs(EEGtimecourse10Hz[,3,])))
+EEGmaskindex14 <- colMeans(20*log10(abs(EEGtimecourse14Hz[,2,])/abs(EEGtimecourse14Hz[,3,])))
+
+times <- -499:12500
+
+plot(times,EEGmeantime5Hz[1,],type='l',col=colpal[1],ylim=c(0,1))
+lines(times,EEGmeantime5Hz[2,],col='grey')
+lines(times,EEGmeantime5Hz[3,],col=colpal[2])
+spl5a <- smooth.spline(times,EEGmeantime5Hz[1,],df=20)
+lines(spl5a$x,spl5a$y,col=colpal[1],lwd=2)
+spl5a <- smooth.spline(times,EEGmeantime5Hz[2,],df=20)
+lines(spl5a$x,spl5a$y,col='grey',lwd=2)
+spl5a <- smooth.spline(times,EEGmeantime5Hz[3,],df=20)
+lines(spl5a$x,spl5a$y,col=colpal[2],lwd=2)
+
+plot(times,EEGmeantime7Hz[2,],type='l',col=colpal[1],ylim=c(0,1))
+lines(times,EEGmeantime7Hz[1,],col='grey')
+lines(times,EEGmeantime7Hz[3,],col=colpal[2])
+spl5a <- smooth.spline(times,EEGmeantime7Hz[2,],df=20)
+lines(spl5a$x,spl5a$y,col=colpal[1],lwd=2)
+spl5a <- smooth.spline(times,EEGmeantime7Hz[1,],df=20)
+lines(spl5a$x,spl5a$y,col='grey',lwd=2)
+spl5a <- smooth.spline(times,EEGmeantime7Hz[3,],df=20)
+lines(spl5a$x,spl5a$y,col=colpal[2],lwd=2)
+
+plot(times,EEGmaskindex5,type='l',col=colpal[1],ylim=c(0,6))
+lines(times,EEGmaskindex7,col=colpal[2])
+lines(times,EEGmaskindex10,col=colpal[4])
+lines(times,EEGmaskindex14,col=colpal[5])
+lines(times,(EEGmaskindex5+EEGmaskindex7+EEGmaskindex10+EEGmaskindex14)/4,col=colpal[3])
+
+spl5a <- smooth.spline(times,EEGmaskindex5,df=20)
+lines(spl5a$x,spl5a$y,col=colpal[1],lwd=2)
+spl5a <- smooth.spline(times,EEGmaskindex7,df=20)
+lines(spl5a$x,spl5a$y,col=colpal[2],lwd=2)
+spl5a <- smooth.spline(times,(EEGmaskindex5+EEGmaskindex7+EEGmaskindex10+EEGmaskindex14)/4,df=20)
+lines(spl5a$x,spl5a$y,col=colpal[3],lwd=4)
+
+# f1 <- 7
+# f2 <- 5
+#     binwidth <- 1000
+#     tindex <- 1 + f1*(binwidth/1000)
+#     mindex <- 1 + f2*(binwidth/1000)
+# condlist <- c(6,8,13)
+# 
+# d <- dir('temp/VilidaiteProcessed/')
+# all7Hz <- array(0,dim=c(length(d),14,64))
+# all5Hz <- array(0,dim=c(length(d),14,64))
+# timecourse7Hz <- array(0,dim=c(length(d),3,14000))
+# timecourse5Hz <- array(0,dim=c(length(d),3,14000))
+# 
+#   for (s in 1:length(d)){
+# 
+#     load(paste0('temp/VilidaiteProcessed/',d[s]))
+#     
+#     targetchannels <- match(targetelectrodes, electrodes) - 2
+# 
+#     for (cond in 1:14){
+#       for (ch in 1:64){
+#         temp <- meanwaveforms[cond,ch,2001:12000]
+#         spec <- fft(temp)/length(temp)
+#         all7Hz[s,cond,ch] <- spec[7*10+1]
+#         all5Hz[s,cond,ch] <- spec[5*10+1]
+#       }
+#     }
+#     for (cond in 1:3){
+#     temp <- colMeans(meanwaveforms[condlist[cond],targetchannels,])
+# 
+# fspec1 <- temp*0
+# fspec2 <- temp*0
+# for (t in 1:(length(temp)-binwidth)){
+#   spec <- fft(temp[t:(t+binwidth-1)])/binwidth
+#   fspec1[t] <- spec[tindex]
+#   fspec2[t] <- spec[mindex]
+# }
+#     timecourse7Hz[s,cond,] <- fspec1
+#     timecourse5Hz[s,cond,] <- fspec2
+#     
+#     }
+#     
+#   }
+# 
+# mean7 <- apply(all7Hz[,,targetchannels],1:2,mean)
+# mean5 <- apply(all5Hz[,,targetchannels],1:2,mean)
+# inclusionmatrix7 <- matrix(0,nrow=length(d),ncol=length(condlist))
+# inclusionmatrix5 <- matrix(0,nrow=length(d),ncol=length(condlist))
+# for (cond in 1:3){
+#   temp <- mean7[,condlist[cond]]
+#         tempxy <- data.frame(Re(temp),Im(temp))
+#       D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+#       inclusionmatrix7[,cond] <- (D<3)
+#    temp <- mean5[,condlist[cond]]
+#         tempxy <- data.frame(Re(temp),Im(temp))
+#       D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+#       inclusionmatrix5[,cond] <- (D<3)
+# }
+# 
+# meantime5Hz <- matrix(0,nrow=length(condlist),ncol=14000) 
+# meantime7Hz <- matrix(0,nrow=length(condlist),ncol=14000) 
+# for (cond in 1:3){
+# meantime7Hz[cond,] <- abs(apply(abs(timecourse7Hz[which(inclusionmatrix7[,cond]>0),cond,]),2,mean))
+# meantime5Hz[cond,] <- abs(apply(abs(timecourse5Hz[which(inclusionmatrix5[,cond]>0),cond,]),2,mean))
+# }
+# 
+# plot(-499:13500,meantime5Hz[2,],type='l',col=colpal[1])
+# lines(-499:13500,meantime5Hz[1,],col='grey')
+# lines(-499:13500,meantime5Hz[3,],col=colpal[2])
+# 
+# plot(-499:13500,meantime7Hz[1,],type='l',col=colpal[1])
+# lines(-499:13500,meantime7Hz[2,],col='grey')
+# lines(-499:13500,meantime7Hz[3,],col=colpal[2])
+# 
+# plot(-499:13500,meantime7Hz[1,]/meantime7Hz[3,],type='l',col=colpal[1])
+# lines(-499:13500,meantime5Hz[2,]/meantime5Hz[3,],col=colpal[2])
 
@@
 Our initial reanalysis was promising, however the data were noisy despite the large sample size, because each participant contributed only 8 trials to each condition.
-We therefore preregistered two new experiments (see http://) to investigate these effects in greater detail.
+We therefore preregistered two new experiments (see https://osf.io/4qudc) to investigate these effects in greater detail.
 These had a similar overall design to the Vilidaite study, with some small changes intended to optimise the study (see Methods).
@@
 
-Figure 2 summarises the results of an EEG experiment testing 100 neurotypical participants.
-Averaged EEG waveforms showed a strong oscillatory component at each of the two stimulus flicker frequencies (Figure 2a), which slightly lagged the driving signal.
-Signals were well-isolated in the Fourier domain, and localised to occipital electrodes (Figure 2b).
-The timecourse at both frequencies showed an initial onset transient, and were then relatively stable for the 6 seconds of stimulus presentation (Figure 2c,d).
-Responses were weaker in the two masking conditions, and the ratio of target only to target + mask conditions increased over time (Figure 2e,f).
+Figure \@ref(fig:EEGdata) summarises the results of an EEG experiment testing 100 neurotypical participants.
+Averaged EEG waveforms showed a strong oscillatory component at each of the two stimulus flicker frequencies (Figure \@ref(fig:EEGdata)a), which slightly lagged the driving signal.
+Signals were well-isolated in the Fourier domain, and localised to occipital electrodes (Figure \@ref(fig:EEGdata)b).
+The timecourse at both frequencies showed an initial onset transient, and was then relatively stable for the 6 seconds of stimulus presentation (Figure \@ref(fig:EEGdata)c,d).
+Responses were weaker in the two masking conditions, and the ratio of target only to target + mask conditions increased over time (Figure \@ref(fig:EEGdata)e,f) for both mask types.
+At 5Hz the increase in masking continued over the first 5 seconds of stimulus presentation (Figure \@ref(fig:EEGdata)e), whereas at 7Hz the increase occurred mostly during the first second after onset (Figure \@ref(fig:EEGdata)f).
 
@@
       qdatasubj <- read.csv(paste0('temp/raw/S',subjcounter,'/questionnairedata.csv'))
-      save(file=paste0('temp/EEGprocessed/S',subjcounter,'data.RData'),list=c('qdatasubj','condcounter','trialsincluded','subjwaves'))
-    }
-
- }
-}
-
-# d <- dir(path = 'temp/EEGprocessed', pattern = '*.RData', full.names=TRUE)
-# 
-# groupmeans <- array(0,dim=c(length(d),4,4,10))
-# groupspec <- array(0,dim=c(length(d),4,64,121))
-# groupspecplot <- array(0,dim=c(length(d),4,121))
-# groupwaveforms <- array(0,dim=c(length(d),4,8000))
-# EEGtimecourse5Hz <- array(0,dim=c(length(d),4,7000))
-# EEGtimecourse7Hz <- array(0,dim=c(length(d),4,7000))
-# 
+      save(file=paste0('temp/EEGprocessed/S',subjcounter,'data.RData'),list=c('qdatasubj','condcounter','trialsincluded','subjwaves','electrodes'))
+    }
+
+ }
+}
+
+d <- dir(path = 'temp/EEGprocessed', pattern = '*.RData', full.names=TRUE)
+EEGtimecourse5Hz <- array(0,dim=c(length(d),4,8000))
+EEGtimecourse7Hz <- array(0,dim=c(length(d),4,8000))
+allwaves <- array(0,dim=c(length(d),4,9000))
+allspec <- array(0,dim=c(length(d),4,duration*20))
+allheads5 <- array(0,dim=c(length(d),4,64))
+allheads7 <- array(0,dim=c(length(d),4,64))
+for (s in 1:length(d)){
+  load(d[s])
+  targetchannels <- match(targetelectrodes, electrodes) - 2
+  for (cond in 1:4){
+    temp <- rowMeans(subjwaves[cond,,targetchannels],na.rm=TRUE)
+    nainds <- which(is.na(temp))   # find occasional NaN values in the waveform
+    # temp[nainds] <- (temp[nainds-1] + temp[nainds+1])/2   # interpolate adjacent values
+    temp[nainds] <- 0   # replace with zeros
+    allwaves[s,cond,] <- temp - mean(temp)
+    spec <- fft(temp[1501:7500])/6000
+    allspec[s,cond,] <- spec[1+(1:(duration*20))]
+
+fspec1 <- NULL
+fspec2 <- NULL
+for (t in 1:(9000-binwidth)){
+  spec <- fft(temp[t:(t+binwidth-1)])/binwidth
+  fspec1[t] <- spec[tindex]
+  fspec2[t] <- spec[mindex]
+}
+    EEGtimecourse5Hz[s,cond,] <- fspec1
+    EEGtimecourse7Hz[s,cond,] <- fspec2
+
+  for (ch in 1:64){
+    temp <- fft(subjwaves[cond,1501:7500,ch])/6000
+    allheads5[s,cond,ch] <- temp[1+(duration*targetF)]
+    allheads7[s,cond,ch] <- temp[1+(duration*maskF)]
+  }
+  }
+
+}
+
+save(file='temp/EEGsummary.RData',list=c('allheads5','allheads7','allspec','allwaves','EEGtimecourse5Hz','EEGtimecourse7Hz','electrodes'))
+ }
+
+if (runcode==1){
+load('temp/EEGsummary.RData')
+
+isincluded <- matrix(rep(1,4*dim(allspec)[1]),nrow=4,ncol=dim(allspec)[1])
+for (cond in 1:4){
+  # note that in allspec the DC component has been removed
+  # so we don't need to add 1 to the index
+      tempxy <- data.frame(Re(allspec[,cond,duration*targetF]),Im(allspec[,cond,duration*targetF]))
+      D5 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+      tempxy <- data.frame(Re(allspec[,cond,duration*maskF]),Im(allspec[,cond,duration*maskF]))      
+      D7 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))      
+      isincluded[cond,which(D5>3)] <- 0
+      isincluded[cond,which(D7>3)] <- 0
+   for (s in 1:100){
+     if (max(abs(EEGtimecourse5Hz[s,cond,]))>5){isincluded[cond,s] <- 0}
+   }   
+}
+
+allwaves[which(allwaves<(-100))] <- 0
+allwaves[which(allwaves>100)] <- 0
+
+EEGmeantime5Hz <- matrix(0,nrow=4,ncol=8000)
+EEGmeantime7Hz <- matrix(0,nrow=4,ncol=8000)
+EEGSEtime5Hz <- matrix(0,nrow=4,ncol=8000)
+EEGSEtime7Hz <- matrix(0,nrow=4,ncol=8000)
+meanspec <- matrix(0,nrow=4,ncol=120)
+meanwave <- matrix(0,nrow=4,ncol=9000)
+meanhead5 <- matrix(0,nrow=4,ncol=64)
+meanhead7 <- matrix(0,nrow=4,ncol=64)
+for (cond in 1:4){
+EEGmeantime7Hz[cond,] <- apply(abs(EEGtimecourse7Hz[which(isincluded[cond,]==1),cond,]),2,mean,na.rm=TRUE)
+EEGmeantime5Hz[cond,] <- apply(abs(EEGtimecourse5Hz[which(isincluded[cond,]==1),cond,]),2,mean,na.rm=TRUE)
+
+EEGSEtime7Hz[cond,] <- apply(abs(EEGtimecourse7Hz[which(isincluded[cond,]==1),cond,]),2,sd,na.rm=TRUE)/sqrt(sum(isincluded[cond,]))
+EEGSEtime5Hz[cond,] <- apply(abs(EEGtimecourse5Hz[which(isincluded[cond,]==1),cond,]),2,sd,na.rm=TRUE)/sqrt(sum(isincluded[cond,]))
+
+meanspec[cond,] <- abs(colMeans(allspec[which(isincluded[cond,]==1),cond,],na.rm=TRUE))
+meanwave[cond,] <- colMeans(allwaves[which(isincluded[cond,]==1),cond,],na.rm=TRUE)
+meanhead5[cond,] <- abs(colMeans(allheads5[which(isincluded[cond,]==1),cond,],na.rm=TRUE))
+meanhead7[cond,] <- abs(colMeans(allheads7[which(isincluded[cond,]==1),cond,],na.rm=TRUE))
+}
+
+EEGmaskindex5 <- matrix(0,nrow=2,ncol=8000)
+EEGmaskindexSE5 <- matrix(0,nrow=2,ncol=8000)
+includedboth <- isincluded[1,]*isincluded[3,]
+monratios <- abs(EEGtimecourse5Hz[which(includedboth==1),1,])/abs(EEGtimecourse5Hz[which(includedboth==1),3,])
+EEGmaskindex5[1,] <- colMeans(20*log10(monratios))
+EEGmaskindexSE5[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+includedboth <- isincluded[1,]*isincluded[4,]
+dichratios <- abs(EEGtimecourse5Hz[which(includedboth==1),1,])/abs(EEGtimecourse5Hz[which(includedboth==1),4,])
+EEGmaskindex5[2,] <- colMeans(20*log10(dichratios))
+EEGmaskindexSE5[2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+
+EEGmaskindex7 <- matrix(0,nrow=2,ncol=8000)
+EEGmaskindexSE7 <- matrix(0,nrow=2,ncol=8000)
+includedboth <- isincluded[2,]*isincluded[3,]
+monratios <- abs(EEGtimecourse7Hz[which(includedboth==1),2,])/abs(EEGtimecourse7Hz[which(includedboth==1),3,])
+EEGmaskindex7[1,] <- colMeans(20*log10(monratios))
+EEGmaskindexSE7[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+includedboth <- isincluded[2,]*isincluded[4,]
+dichratios <- abs(EEGtimecourse7Hz[which(includedboth==1),2,])/abs(EEGtimecourse7Hz[which(includedboth==1),4,])
+EEGmaskindex7[2,] <- colMeans(20*log10(dichratios))
+EEGmaskindexSE7[2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+
+# pdf("temp/figures/Fig3.pdf", bg="transparent", height = 10, width = 12)
+# 
+# par(mfrow=c(3,4))
+
+times <- ((1:8000)-1000)/1000
+
+postscript("timecourse1.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,7,0,0.6)
+ticklocsx <- -1:7    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.6,0.1)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocsx, side = 1, at=ticklocsx)
+mtext(text = ticklocsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,6,6,0),c(-0.022,-0.022,0.02,0.02),border=NA,col=rgb(0.5,0.5,0.5))
+
+if (plotsmoothed==0){
+polygon(times[c(1:8000,8000:1)],c(EEGmeantime5Hz[1,]+EEGSEtime5Hz[1,],EEGmeantime5Hz[1,8000:1]-EEGSEtime5Hz[1,8000:1]),col=colpal[1],border=NA)
+polygon(times[c(1:8000,8000:1)],c(EEGmeantime5Hz[3,]+EEGSEtime5Hz[3,],EEGmeantime5Hz[3,8000:1]-EEGSEtime5Hz[3,8000:1]),col=colpal[2],border=NA)
+polygon(times[c(1:8000,8000:1)],c(EEGmeantime5Hz[4,]+EEGSEtime5Hz[4,],EEGmeantime5Hz[4,8000:1]-EEGSEtime5Hz[4,8000:1]),col=colpal[3],border=NA)
+
+lines(times,EEGmeantime5Hz[1,],lwd=2,col=colpal[1])
+# lines(times,EEGmeantime5Hz[2,],lwd=2,col='green')
+lines(times,EEGmeantime5Hz[3,],lwd=2,col=colpal[2])
+lines(times,EEGmeantime5Hz[4,],lwd=2,col=colpal[3])
+}
+
+if (plotsmoothed==1){
+spl5aU <- smooth.spline(times,EEGmeantime5Hz[1,]+EEGSEtime5Hz[1,],df=20)
+spl5aL <- smooth.spline(times,EEGmeantime5Hz[1,]-EEGSEtime5Hz[1,],df=20)
+polygon(times[c(1:8000,8000:1)],c(spl5aU$y,spl5aL$y[8000:1]),col=colpal[1],border=NA)
+
+spl5cU <- smooth.spline(times,EEGmeantime5Hz[3,]+EEGSEtime5Hz[3,],df=20)
+spl5cL <- smooth.spline(times,EEGmeantime5Hz[3,]-EEGSEtime5Hz[3,],df=20)
+polygon(times[c(1:8000,8000:1)],c(spl5cU$y,spl5cL$y[8000:1]),col=colpal[2],border=NA)
+
+spl5dU <- smooth.spline(times,EEGmeantime5Hz[4,]+EEGSEtime5Hz[4,],df=20)
+spl5dL <- smooth.spline(times,EEGmeantime5Hz[4,]-EEGSEtime5Hz[4,],df=20)
+polygon(times[c(1:8000,8000:1)],c(spl5dU$y,spl5dL$y[8000:1]),col=colpal[3],border=NA)
+
+spl5a <- smooth.spline(times,EEGmeantime5Hz[1,],df=20)
+lines(spl5a$x,spl5a$y,col=colpal[1],lwd=2)
+# spl5b <- smooth.spline(times,EEGmeantime5Hz[2,],df=20)
+# lines(spl5b$x,spl5b$y,col='green',lwd=2)
+spl5c <- smooth.spline(times,EEGmeantime5Hz[3,],df=20)
+lines(spl5c$x,spl5c$y,col=colpal[2],lwd=2)
+spl5d <- smooth.spline(times,EEGmeantime5Hz[4,],df=20)
+lines(spl5d$x,spl5d$y,col=colpal[3],lwd=2)
+
+}
+
+dev.off()
+
+postscript("timecourse2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,7,-3,7)
+ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocsx, side = 1, at=ticklocsx)
+mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,6,6,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))
+
+lines(c(-1,7),c(0,0),lty=2)
+
+if (plotsmoothed==0){
+polygon(times[c(1:8000,8000:1)],c(EEGmaskindex5[1,]+EEGmaskindexSE5[1,],EEGmaskindex5[1,8000:1]-EEGmaskindexSE5[1,8000:1]),col=colpal[2],border=NA)
+polygon(times[c(1:8000,8000:1)],c(EEGmaskindex5[2,]+EEGmaskindexSE5[2,],EEGmaskindex5[2,8000:1]-EEGmaskindexSE5[2,8000:1]),col=colpal[3],border=NA)
+
+lines(times,EEGmaskindex5[1,],col=colpal[2],lwd=2)
+lines(times,EEGmaskindex5[2,],col=colpal[3],lwd=2)
+}
+if (plotsmoothed==1){
+U <- smooth.spline(times,EEGmaskindex5[1,]+EEGmaskindexSE5[1,],df=20)
+L <- smooth.spline(times,EEGmaskindex5[1,]-EEGmaskindexSE5[1,],df=20)
+polygon(times[c(1:8000,8000:1)],c(U$y,L$y[8000:1]),col=colpal[2],border=NA)
+
+U <- smooth.spline(times,EEGmaskindex5[2,]+EEGmaskindexSE5[2,],df=20)
+L <- smooth.spline(times,EEGmaskindex5[2,]-EEGmaskindexSE5[2,],df=20)
+polygon(times[c(1:8000,8000:1)],c(U$y,L$y[8000:1]),col=colpal[3],border=NA)
+
+L <- smooth.spline(times,EEGmaskindex5[1,],df=20)
+lines(L$x,L$y,col=colpal[2],lwd=2)
+L <- smooth.spline(times,EEGmaskindex5[2,],df=20)
+lines(L$x,L$y,col=colpal[3],lwd=2)
+}
+
+dev.off()
+
+postscript("timecourse3.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,7,0,0.6)
+ticklocsy <- seq(0,0.6,0.1)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocsx, side = 1, at=ticklocsx)
+mtext(text = ticklocsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,6,6,0),c(-0.022,-0.022,0.02,0.02),border=NA,col=rgb(0.5,0.5,0.5))
+
+if (plotsmoothed==0){
+polygon(times[c(1:8000,8000:1)],c(EEGmeantime7Hz[2,]+EEGSEtime7Hz[2,],EEGmeantime7Hz[2,8000:1]-EEGSEtime7Hz[2,8000:1]),col=colpal[1],border=NA)
+polygon(times[c(1:8000,8000:1)],c(EEGmeantime7Hz[3,]+EEGSEtime7Hz[3,],EEGmeantime7Hz[3,8000:1]-EEGSEtime7Hz[3,8000:1]),col=colpal[2],border=NA)
+polygon(times[c(1:8000,8000:1)],c(EEGmeantime7Hz[4,]+EEGSEtime7Hz[4,],EEGmeantime7Hz[4,8000:1]-EEGSEtime7Hz[4,8000:1]),col=colpal[3],border=NA)
+
+# lines(times,EEGmeantime7Hz[1,],lwd=2,col=colpal[1])
+lines(times,EEGmeantime7Hz[2,],lwd=2,col=colpal[1])
+lines(times,EEGmeantime7Hz[3,],lwd=2,col=colpal[2])
+lines(times,EEGmeantime7Hz[4,],lwd=2,col=colpal[3])
+}
+if (plotsmoothed==1){
+
+spl7bU <- smooth.spline(times,EEGmeantime7Hz[2,]+EEGSEtime7Hz[2,],df=20)
+spl7bL <- smooth.spline(times,EEGmeantime7Hz[2,]-EEGSEtime7Hz[2,],df=20)
+polygon(times[c(1:8000,8000:1)],c(spl7bU$y,spl7bL$y[8000:1]),col=colpal[1],border=NA)
+
+spl7cU <- smooth.spline(times,EEGmeantime7Hz[3,]+EEGSEtime7Hz[3,],df=20)
+spl7cL <- smooth.spline(times,EEGmeantime7Hz[3,]-EEGSEtime7Hz[3,],df=20)
+polygon(times[c(1:8000,8000:1)],c(spl7cU$y,spl7cL$y[8000:1]),col=colpal[2],border=NA)
+
+spl7dU <- smooth.spline(times,EEGmeantime7Hz[4,]+EEGSEtime7Hz[4,],df=20)
+spl7dL <- smooth.spline(times,EEGmeantime7Hz[4,]-EEGSEtime7Hz[4,],df=20)
+polygon(times[c(1:8000,8000:1)],c(spl7dU$y,spl7dL$y[8000:1]),col=colpal[3],border=NA)
+
+# spl7a <- smooth.spline(times,EEGmeantime7Hz[1,],df=20)
+# lines(spl7a$x,spl7a$y,col=colpal[1],lwd=2)
+spl7b <- smooth.spline(times,EEGmeantime7Hz[2,],df=20)
+lines(spl7b$x,spl7b$y,col=colpal[1],lwd=2)
+spl7c <- smooth.spline(times,EEGmeantime7Hz[3,],df=20)
+lines(spl7c$x,spl7c$y,col=colpal[2],lwd=2)
+spl7d <- smooth.spline(times,EEGmeantime7Hz[4,],df=20)
+lines(spl7d$x,spl7d$y,col=colpal[3],lwd=2)
+}
+
+dev.off()
+
+postscript("timecourse4.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,7,-3,6)
+ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocsx, side = 1, at=ticklocsx)
+mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,6,6,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))
+
+lines(c(-1,7),c(0,0),lty=2)
+
+if (plotsmoothed==0){
+polygon(times[c(1:8000,8000:1)],c(EEGmaskindex7[1,]+EEGmaskindexSE7[1,],EEGmaskindex7[1,8000:1]-EEGmaskindexSE7[1,8000:1]),col=colpal[2],border=NA)
+polygon(times[c(1:8000,8000:1)],c(EEGmaskindex7[2,]+EEGmaskindexSE7[2,],EEGmaskindex7[2,8000:1]-EEGmaskindexSE7[2,8000:1]),col=colpal[3],border=NA)
+
+lines(times,EEGmaskindex7[1,],col=colpal[2],lwd=2)
+lines(times,EEGmaskindex7[2,],col=colpal[3],lwd=2)
+}
+
+if (plotsmoothed==1){
+U <- smooth.spline(times,EEGmaskindex7[1,]+EEGmaskindexSE7[1,],df=20)
+L <- smooth.spline(times,EEGmaskindex7[1,]-EEGmaskindexSE7[1,],df=20)
+polygon(times[c(1:8000,8000:1)],c(U$y,L$y[8000:1]),col=colpal[2],border=NA)
+
+U <- smooth.spline(times,EEGmaskindex7[2,]+EEGmaskindexSE7[2,],df=20)
+L <- smooth.spline(times,EEGmaskindex7[2,]-EEGmaskindexSE7[2,],df=20)
+polygon(times[c(1:8000,8000:1)],c(U$y,L$y[8000:1]),col=colpal[3],border=NA)
+
+L <- smooth.spline(times,EEGmaskindex7[1,],df=20)
+lines(L$x,L$y,col=colpal[2],lwd=2)
+L <- smooth.spline(times,EEGmaskindex7[2,],df=20)
+lines(L$x,L$y,col=colpal[3],lwd=2)
+}
+
+dev.off()
+
+freqlist <- seq(1/6,20,length=ncol(meanspec))
+
+postscript("spectrum.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 10)
+
+plotlims <- c(0,20,0,4)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+ticklocsx <- seq(0,20,5)    # locations of tick marks on x axis
+ticklocsy <- c(0,0.4,0.8,1,2,3,4)    # locations of tick marks on y axis
+ticklabelsx <- seq(0,20,5)        # set labels for x ticks
+ticklabelsy <- c(0,0.2,0.4,'','','','')    # set labels for y ticks
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+lines(c(0,20),c(0,0),lty=3)
+lines(c(0,20),c(1,1),lty=3)
+lines(c(0,20),c(2,2),lty=3)
+lines(c(0,20),c(3,3),lty=3)
+
+# lines(c(5,5),c(0,4),col='grey',lwd=2)
+# lines(c(7,7),c(0,4),col='grey',lwd=2)
+
+polygon(c(1/6,freqlist,20),c(0,2*meanspec[1,],0)+3,border=NA,col=colpal[1])
+polygon(c(1/6,freqlist,20),c(0,2*meanspec[2,],0)+2,border=NA,col=colpal[1])
+polygon(c(1/6,freqlist,20),c(0,2*meanspec[3,],0)+1,border=NA,col=colpal[2])
+polygon(c(1/6,freqlist,20),c(0,2*meanspec[4,],0),border=NA,col=colpal[3])
+
+lines(freqlist,2*meanspec[1,]+3,lwd=2,col='black')
+lines(freqlist,2*meanspec[2,]+2,lwd=2,col='black')
+lines(freqlist,2*meanspec[3,]+1,lwd=2,col='black')
+lines(freqlist,2*meanspec[4,],lwd=2,col='black')
+
+text(20,3.5,'5Hz monocular target',pos=2,cex=1.5)
+text(20,2.5,'7Hz monocular target',pos=2,cex=1.5)
+text(20,1.5,'Monocular combination',pos=2,cex=1.5)
+text(20,0.5,'Dichoptic combination',pos=2,cex=1.5)
+
+dev.off()
+
+times <- seq(1/1000,9,1/1000)-1.5
+trigwaveform1 <- -cos(2 * 5 * times * pi)
+trigwaveform2 <- -cos(2 * 7 * times * pi)
+trigwaveform1[1:1500] <- -1
+trigwaveform1[7501:9000] <- -1
+trigwaveform2[1:1500] <- -1
+trigwaveform2[7501:9000] <- -1
+
+postscript("waveform1.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 12)
+
+plotlims <- c(-1,7,-3,2)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+ticklocsx <- seq(-1,7,1)    # locations of tick marks on x axis
+ticklocsy <- seq(-3,2,1)    # locations of tick marks on y axis
+ticklabelsx <- seq(-1,7,1)        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+polygon(c(0,6,6,0,0),c(-3,-3,2,2,-2),col=rgb(0.95,0.95,0.95),border=NA)
+
+lines(times[501:8500],meanwave[1,501:8500],lwd=1,col=colpal[2])
+lines(times[501:8500],(trigwaveform1[501:8500]/2) - 2.5)
+# text(-1,1.8,'5Hz average waveform',pos=4,cex=1.5)
+
+dev.off()
+
+postscript("waveform2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 12)
+
+plotlims <- c(-1,7,-3,2)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+ticklocsx <- seq(-1,7,1)    # locations of tick marks on x axis
+ticklocsy <- seq(-3,2,1)    # locations of tick marks on y axis
+ticklabelsx <- seq(-1,7,1)        # set labels for x ticks
+ticklabelsy <- ticklocsy    # set labels for y ticks
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+polygon(c(0,6,6,0,0),c(-3,-3,2,2,-2),col=rgb(0.95,0.95,0.95),border=NA)
+
+lines(times[501:8500],meanwave[2,501:8500],lwd=1,col=colpal[2])
+lines(times[501:8500],(trigwaveform2[501:8500]/2) - 2.5)
+# text(-1,1.8,'7Hz average waveform',pos=4,cex=1.5)
+
+dev.off()
+
+xpos <- 1:64
+ypos <- 1:64
+montageE <- toupper(as.character(hdata$Electrode))
+for (ch in 1:64){
+  i <- match(toupper(electrodes[ch+2]),montageE)
+  xpos[ch] <- hdata$X_position[i]
+  ypos[ch] <- hdata$Y_position[i]
+}
+
+rmax <- 0.55   #specify a maximum boundary for the grid
+gridRes <- 100 #specify the interpolation grid resolution
+
+datatoplot <- meanhead5[1,]
+datatoplot[which(is.na(datatoplot))] <- 0
+datatoplot[which(datatoplot<0)] <- 0
+datatoplot[which(datatoplot>30)] <- 0
+
+testDat<- data.frame(x = xpos,
+                     y = -ypos,
+                     z = datatoplot)
+
+#Create the interpolation grid
+xo <- seq(min(-rmax, testDat$x), max(rmax, testDat$x), length = gridRes)
+yo <- seq(max(rmax, testDat$y), min(-rmax, testDat$y), length = gridRes)
+
+interpV4 <- v4Interp(testDat, xo, yo, rmax, gridRes)
+
+zo2 <- as.matrix(interpV4[,2:ncol(interpV4)])
+
+xo2 <- matrix(rep(xo,length(yo)),nrow = length(xo),ncol = length(yo))
+yo2 <- t(matrix(rep(yo,length(xo)),nrow = length(yo),ncol = length(xo)))
+outsidecircle <- sqrt(xo2^2 + yo2^2) > 0.51
+zo2[outsidecircle] <- 0
+
+ramp2 <- colorRamp(c("white",colpal[2]))  
+colmatrix2 <- rgb(ramp2(seq(0, 1, length = 101)), max = 255)
+
+tiff('headplot1.tif', height = 600, width = 600, units="px", bg="white")
+
+plotlims <- c(-rmax,rmax,-rmax,rmax)  
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,ann=FALSE, axes=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4]) 
+image(xo,xo,zo2,col=colmatrix2,zlim=c(0,1),add=TRUE,useRaster=FALSE)
+maskx <- c(hdata$OutlineX[1:51]*2.2,hdata$OutlineX[51:1])
+masky <- c(hdata$OutlineY[1:51]*2.2,hdata$OutlineY[51:1])
+polygon(maskx,masky,border=NA,col="white")
+maskx <- c(hdata$OutlineX[51:101]*2.2,hdata$OutlineX[101:51])
+masky <- c(hdata$OutlineY[51:101]*2.2,hdata$OutlineY[101:51])
+polygon(maskx,masky,border=NA,col="white")
+
+blackelectrodes <- match('OZ',toupper(as.character(electrodes[3:66])))
+points(xpos[blackelectrodes],ypos[blackelectrodes],pch=16,col="black",cex=1.6)
+blackelectrodes <- match('POZ',toupper(as.character(electrodes[3:66])))
+points(xpos[blackelectrodes],ypos[blackelectrodes],pch=16,col="black",cex=1.6)
+blackelectrodes <- match('O1',toupper(as.character(electrodes[3:66])))
+points(xpos[blackelectrodes],ypos[blackelectrodes],pch=16,col="black",cex=1.6)
+blackelectrodes <- match('O2',toupper(as.character(electrodes[3:66])))
+points(xpos[blackelectrodes],ypos[blackelectrodes],pch=16,col="black",cex=1.6)
+
+lines(hdata$OutlineX,hdata$OutlineY,col="black",lwd=2)
+lines(hdata$NoseX,hdata$NoseY,col="black",lwd=2)
+lines(hdata$LearX,hdata$LearY,col="black",lwd=2)
+lines(hdata$RearX,hdata$RearY,col="black",lwd=2)
+
+# text(0,-0.55,'5Hz response',cex=1.5,adj=0.5)
+
+dev.off()
+
+datatoplot <- meanhead7[2,]
+datatoplot[which(is.na(datatoplot))] <- 0
+datatoplot[which(datatoplot<0)] <- 0
+datatoplot[which(datatoplot>30)] <- 0
+
+testDat<- data.frame(x = xpos,
+                     y = -ypos,
+                     z = datatoplot)
+
+#Create the interpolation grid
+xo <- seq(min(-rmax, testDat$x), max(rmax, testDat$x), length = gridRes)
+yo <- seq(max(rmax, testDat$y), min(-rmax, testDat$y), length = gridRes)
+
+interpV4 <- v4Interp(testDat, xo, yo, rmax, gridRes)
+
+zo2 <- as.matrix(interpV4[,2:ncol(interpV4)])
+
+xo2 <- matrix(rep(xo,length(yo)),nrow = length(xo),ncol = length(yo))
+yo2 <- t(matrix(rep(yo,length(xo)),nrow = length(yo),ncol = length(xo)))
+outsidecircle <- sqrt(xo2^2 + yo2^2) > 0.51
+zo2[outsidecircle] <- 0
+
+tiff('headplot2.tif', height = 600, width = 600, units="px", bg="white")
+
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,ann=FALSE, axes=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4]) 
+image(xo,xo,zo2,col=colmatrix2,zlim=c(0,1),add=TRUE,useRaster=FALSE)
+maskx <- c(hdata$OutlineX[1:51]*2.2,hdata$OutlineX[51:1])
+masky <- c(hdata$OutlineY[1:51]*2.2,hdata$OutlineY[51:1])
+polygon(maskx,masky,border=NA,col="white")
+maskx <- c(hdata$OutlineX[51:101]*2.2,hdata$OutlineX[101:51])
+masky <- c(hdata$OutlineY[51:101]*2.2,hdata$OutlineY[101:51])
+polygon(maskx,masky,border=NA,col="white")
+
+blackelectrodes <- match('OZ',toupper(as.character(electrodes[3:66])))
+points(xpos[blackelectrodes],ypos[blackelectrodes],pch=16,col="black",cex=1.6)
+blackelectrodes <- match('POZ',toupper(as.character(electrodes[3:66])))
+points(xpos[blackelectrodes],ypos[blackelectrodes],pch=16,col="black",cex=1.6)
+blackelectrodes <- match('O1',toupper(as.character(electrodes[3:66])))
+points(xpos[blackelectrodes],ypos[blackelectrodes],pch=16,col="black",cex=1.6)
+blackelectrodes <- match('O2',toupper(as.character(electrodes[3:66])))
+points(xpos[blackelectrodes],ypos[blackelectrodes],pch=16,col="black",cex=1.6)
+
+lines(hdata$OutlineX,hdata$OutlineY,col="black",lwd=2)
+lines(hdata$NoseX,hdata$NoseY,col="black",lwd=2)
+lines(hdata$LearX,hdata$LearY,col="black",lwd=2)
+lines(hdata$RearX,hdata$RearY,col="black",lwd=2)
+
+# text(0,-0.55,'7Hz response',cex=1.5,adj=0.5)
+
+dev.off()
+
+# baseline <- data.frame(Re(allspec[,1,duration*targetF]),Im(allspec[,1,duration*targetF]))
+# monmask <- data.frame(Re(allspec[,3,duration*targetF]),Im(allspec[,3,duration*targetF]))
+# dichmask <- data.frame(Re(allspec[,4,duration*targetF]),Im(allspec[,4,duration*targetF]))
+# 
+# par(pty="s")  # make axis square
+# plotlims <- c(-1,1,-1,1)
+# plot(x=NULL,y=NULL,ann=FALSE, axes=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4]) 
+# lines(plotlims[1:2],c(0,0))
+# lines(c(0,0),plotlims[1:2])
+# 
+# points(baseline[,1],baseline[,2],pch=16,cex=0.5,col=addalpha(colpal[1],0.2))
+# points(monmask[,1],monmask[,2],pch=16,cex=0.5,col=addalpha(colpal[2],0.2))
+# points(dichmask[,1],dichmask[,2],pch=16,cex=0.5,col=addalpha(colpal[3],0.2))
+# 
+# points(mean(baseline[,1]),mean(baseline[,2]),pch=16,cex=2,col=addalpha(colpal[1],1))
+# points(mean(monmask[,1]),mean(monmask[,2]),pch=16,cex=2,col=addalpha(colpal[2],1))
+# points(mean(dichmask[,1]),mean(dichmask[,2]),pch=16,cex=2,col=addalpha(colpal[3],1))
+# 
+# 
+# 
+# baseline <- data.frame(Re(allspec[,2,duration*maskF]),Im(allspec[,2,duration*maskF]))
+# monmask <- data.frame(Re(allspec[,3,duration*maskF]),Im(allspec[,3,duration*maskF]))
+# dichmask <- data.frame(Re(allspec[,4,duration*maskF]),Im(allspec[,4,duration*maskF]))
+# 
+# par(pty="s")  # make axis square
+# plotlims <- c(-1,1,-1,1)
+# plot(x=NULL,y=NULL,ann=FALSE, axes=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4]) 
+# lines(plotlims[1:2],c(0,0))
+# lines(c(0,0),plotlims[1:2])
+# 
+# points(baseline[,1],baseline[,2],pch=16,cex=0.5,col=addalpha(colpal[1],0.2))
+# points(monmask[,1],monmask[,2],pch=16,cex=0.5,col=addalpha(colpal[2],0.2))
+# points(dichmask[,1],dichmask[,2],pch=16,cex=0.5,col=addalpha(colpal[3],0.2))
+# 
+# points(mean(baseline[,1]),mean(baseline[,2]),pch=16,cex=2,col=addalpha(colpal[1],1))
+# points(mean(monmask[,1]),mean(monmask[,2]),pch=16,cex=2,col=addalpha(colpal[2],1))
+# points(mean(dichmask[,1]),mean(dichmask[,2]),pch=16,cex=2,col=addalpha(colpal[3],1))
+#
+
+  e1 <- readTIFF('headplot1.tif')
+  e2 <- readTIFF('headplot2.tif')
+
+  PostScriptTrace(paste('waveform1.ps',sep=''))
+  e3 <- readPicture('waveform1.ps.xml')
+  PostScriptTrace(paste('waveform2.ps',sep=''))
+  e4 <- readPicture('waveform2.ps.xml')
+
+  PostScriptTrace(paste('spectrum.ps',sep=''))
+  e5 <- readPicture('spectrum.ps.xml')
+  for (n in 1:length(e5@paths)){
+    temp <- class(e5@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e5@paths[n]$path@rgb))<765){e5@paths[n]$path@rgb <- addalpha(e5@paths[n]$path@rgb,alpha=0.2)}}}
+
+   PostScriptTrace(paste('timecourse1.ps',sep=''))
+  e6 <- readPicture('timecourse1.ps.xml')
+  for (n in 1:length(e6@paths)){
+    temp <- class(e6@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e6@paths[n]$path@rgb))<765){e6@paths[n]$path@rgb <- addalpha(e6@paths[n]$path@rgb,alpha=0.2)}}}
+
+   PostScriptTrace(paste('timecourse2.ps',sep=''))
+  e7 <- readPicture('timecourse2.ps.xml')
+  for (n in 1:length(e7@paths)){
+    temp <- class(e7@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e7@paths[n]$path@rgb))<765){e7@paths[n]$path@rgb <- addalpha(e7@paths[n]$path@rgb,alpha=0.2)}}}
+
+     PostScriptTrace(paste('timecourse3.ps',sep=''))
+  e8 <- readPicture('timecourse3.ps.xml')
+  for (n in 1:length(e8@paths)){
+    temp <- class(e8@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e8@paths[n]$path@rgb))<765){e8@paths[n]$path@rgb <- addalpha(e8@paths[n]$path@rgb,alpha=0.2)}}}
+
+     PostScriptTrace(paste('timecourse4.ps',sep=''))
+  e9 <- readPicture('timecourse4.ps.xml')
+  for (n in 1:length(e9@paths)){
+    temp <- class(e9@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e9@paths[n]$path@rgb))<765){e9@paths[n]$path@rgb <- addalpha(e9@paths[n]$path@rgb,alpha=0.2)}}}
+
+  pdf('temp/figures/Fig3.pdf', bg="transparent", height = 6, width = 15)
+  par(mar=c(0.1,0.1,0.1,0.1))
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
+
+  aspratio <- 6/15  # this is the aspect ratio of the output pdf
+  imwidth <- 0.28
+  xstart <- 0.02
+  ystart <- 0.75
+  rasterImage(e1,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth)
+  ystart <- 0.475
+  rasterImage(e2,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth)
+
+  grid.picture(e3,x=0.3,y=0.85,width=0.3,height=1)
+  grid.picture(e4,x=0.3,y=0.6,width=0.3,height=1)
+  grid.picture(e5,x=0.25,y=0.25,width=0.45,height=1)
+
+  grid.picture(e6,x=0.6,y=0.75,width=0.25,height=1)
+  grid.picture(e7,x=0.85,y=0.75,width=0.25,height=1)
+  grid.picture(e8,x=0.6,y=0.25,width=0.25,height=1)
+  grid.picture(e9,x=0.85,y=0.25,width=0.25,height=1)
+
+  text(-0.02,1,'(a)',pos=4,cex=2)
+  text(-0.02,0.45,'(b)',pos=4,cex=2)
+  text(0.515,1,'(c)',pos=4,cex=2)
+  text(0.515,0.46,'(d)',pos=4,cex=2)
+  text(0.785,1,'(e)',pos=4,cex=2)
+  text(0.785,0.46,'(f)',pos=4,cex=2)
+
+  text(-0.02,0.61,'5Hz',pos=4,cex=2)
+  text(-0.02,0.89,'7Hz',pos=4,cex=2)
+
+  dev.off()
+
+  file.remove(c('headplot1.tif','headplot2.tif','spectrum.ps','timecourse1.ps','timecourse2.ps','timecourse3.ps','timecourse4.ps','waveform1.ps','waveform2.ps'))
+  file.remove(c('spectrum.ps.xml','timecourse1.ps.xml','timecourse2.ps.xml','timecourse3.ps.xml','timecourse4.ps.xml','waveform1.ps.xml','waveform2.ps.xml'))
+
+}
+
+```
+
+```{r EEGdata, fig.cap="Summary of EEG results for N=100 neurotypical participants.
+Panel (a) shows scalp topographies and averaged waveforms for 5Hz (top) and 7Hz (bottom) stimuli.
+The black sine wave trace in each panel illustrates the driving contrast modulation, and black points on the scalp topographies indicate electrodes Oz, O1, O2 and POz.
+Panel (b) shows the Fourier amplitude spectrum for each condition, with clear peaks at 5Hz and 7Hz.
+Panels (c,d) show timecourses at each frequency for the baseline condition (black), and the monocular (blue) and dichoptic (red) masking conditions.
+Panels (e,f) show suppression ratios as a function of time for each mask type.
+Light grey rectangles indicate the period of stimulus presentation.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('temp/figures/Fig3.pdf')
+
+```
+
+Participants showed a wide range of scores on both the AQ and SPQ scales, which were negatively correlated (Fig 3a; R = , p < ).
+We again performed a median split by AQ on the EEG data, and calculated the timecourse of the EEG response and suppression ratios for each group (Figure 3b,c).
+
+Next we repeated the experiment on 20 participants using a 248-channel whole-head cryogenic MEG system.
+Half of the participants had a diagnosis of autism, and the remainder were age and gender-matched controls.
+Source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm (reference) showed strong localisation of steady-state signals at the occipital pole (see Figure 4a,b).
+Responses across V1 showed a similar timecourse to those of the EEG experiment at both frequencies (Figure 4c,d), and showed increasing suppression during the first 4 seconds of stimulus presentation (Figure 4e,f).
+
+```{r include=FALSE, results='hide'}
+
+nareas <- 7
+samplerate <- 1001
+targetF <- 5
+maskF <- 7
+duration <- 6
+    binwidth <- 1001
+    tindex <- 1 + targetF*(binwidth/samplerate)
+    mindex <- 1 + maskF*(binwidth/samplerate)
+
+if (processraw==1){
+
+d <- dir(path = 'temp/MEGtrialsWang/', pattern = '*alltrials.mat', full.names=TRUE)
+d2 <- dir(path = 'temp/MEGtrialsWang/', pattern = '*alltrials.mat', full.names=FALSE)
+
+MEGtimecourse5Hz <- array(0,dim=c(length(d),nareas,4,8008))
+MEGtimecourse7Hz <- array(0,dim=c(length(d),nareas,4,8008))
+# allwaves <- array(0,dim=c(length(d),4,9009))
+allspec <- array(0,dim=c(length(d),nareas,4,duration*20))
+allRnos <- NULL
+for (s in 1:length(d)){
+  allRnos[s] <- substr(d2[s],1,5)
+  data <- readMat(d[s])
+  for (area in 1:nareas){
+  for (cond in 1:4){
+    temp <- colMeans(data$alltrials[area,cond,1:data$trialcounter[1,cond],],na.rm=TRUE)
+    nainds <- which(is.na(temp))   # find occasional NaN values in the waveform
+    temp[nainds] <- 0   # replace with zeros
+    # allwaves[s,cond,] <- temp - mean(temp)
+    spec <- fft(temp[1501:7500])/6000
+    allspec[s,area,cond,] <- spec[1+(1:(duration*20))]
+
+fspec1 <- NULL
+fspec2 <- NULL
+for (t in 1:(9009-binwidth)){
+  spec <- fft(temp[t:(t+binwidth-1)])/binwidth
+  fspec1[t] <- spec[tindex]
+  fspec2[t] <- spec[mindex]
+}
+    MEGtimecourse5Hz[s,area,cond,] <- fspec1
+    MEGtimecourse7Hz[s,area,cond,] <- fspec2
+
+  }
+
+}
+}
+
+save(file='temp/MEGsummary.RData',list=c('allspec','MEGtimecourse5Hz','MEGtimecourse7Hz','allRnos'))
+
+load('temp/MEGsummary.RData')
+
+isincluded <- array(1, dim=c(nareas,4,dim(allspec)[1]))
+for (area in 1:nareas){
+for (cond in 1:4){
+  # note that in allspec the DC component has been removed
+  # so we don't need to add 1 to the index
+      tempxy <- data.frame(Re(allspec[,area,cond,duration*targetF]),Im(allspec[,area,cond,duration*targetF]))
+      D5 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+      tempxy <- data.frame(Re(allspec[,area,cond,duration*maskF]),Im(allspec[,area,cond,duration*maskF]))      
+      D7 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))      
+      isincluded[area,cond,which(D5>3)] <- 0
+      isincluded[area,cond,which(D7>3)] <- 0
+   for (s in 1:20){
+     if (max(abs(MEGtimecourse5Hz[s,area,cond,]))>5){isincluded[area,cond,s] <- 0}
+   }   
+}
+}
+
+MEGmeantime5Hz <- array(0,dim=c(nareas,4,8008))
+MEGmeantime7Hz <- array(0,dim=c(nareas,4,8008))
+MEGSEtime5Hz <- array(0,dim=c(nareas,4,8008))
+MEGSEtime7Hz <- array(0,dim=c(nareas,4,8008))
+meanspec <- array(0,dim=c(nareas,4,120))
+for (area in 1:nareas){
+for (cond in 1:4){
+MEGmeantime7Hz[area,cond,] <- apply(abs(MEGtimecourse7Hz[which(isincluded[area,cond,]==1),area,cond,]),2,mean,na.rm=TRUE)
+MEGmeantime5Hz[area,cond,] <- apply(abs(MEGtimecourse5Hz[which(isincluded[area,cond,]==1),area,cond,]),2,mean,na.rm=TRUE)
+
+MEGSEtime7Hz[area,cond,] <- apply(abs(MEGtimecourse7Hz[which(isincluded[area,cond,]==1),area,cond,]),2,sd,na.rm=TRUE)/sqrt(sum(isincluded[area,cond,]))
+MEGSEtime5Hz[area,cond,] <- apply(abs(MEGtimecourse5Hz[which(isincluded[area,cond,]==1),area,cond,]),2,sd,na.rm=TRUE)/sqrt(sum(isincluded[area,cond,]))
+
+meanspec[area,cond,] <- abs(colMeans(allspec[which(isincluded[area,cond,]==1),area,cond,],na.rm=TRUE))
+# meanwave[area,cond,] <- colMeans(allwaves[which(isincluded[area,cond,]==1),area,cond,],na.rm=TRUE)
+}
+}
+
+MEGmaskindex5 <- array(0, dim=c(nareas,2,8008))
+MEGmaskindexSE5 <- array(0, dim=c(nareas,2,8008))
+MEGmaskindex7 <- array(0, dim=c(nareas,2,8008))
+MEGmaskindexSE7 <- array(0, dim=c(nareas,2,8008))
+for (area in 1:nareas){
+includedboth <- isincluded[area,1,]*isincluded[area,3,]
+monratios <- abs(MEGtimecourse5Hz[which(includedboth==1),area,1,])/abs(MEGtimecourse5Hz[which(includedboth==1),area,3,])
+MEGmaskindex5[area,1,] <- colMeans(20*log10(monratios))
+MEGmaskindexSE5[area,1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+includedboth <- isincluded[area,1,]*isincluded[area,4,]
+dichratios <- abs(MEGtimecourse5Hz[which(includedboth==1),area,1,])/abs(MEGtimecourse5Hz[which(includedboth==1),area,4,])
+MEGmaskindex5[area,2,] <- colMeans(20*log10(dichratios))
+MEGmaskindexSE5[area,2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+
+includedboth <- isincluded[area,2,]*isincluded[area,3,]
+monratios <- abs(MEGtimecourse7Hz[which(includedboth==1),area,2,])/abs(MEGtimecourse7Hz[which(includedboth==1),area,3,])
+MEGmaskindex7[area,1,] <- colMeans(20*log10(monratios))
+MEGmaskindexSE7[area,1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+includedboth <- isincluded[area,2,]*isincluded[area,4,]
+dichratios <- abs(MEGtimecourse7Hz[which(includedboth==1),area,2,])/abs(MEGtimecourse7Hz[which(includedboth==1),area,4,])
+MEGmaskindex7[area,2,] <- colMeans(20*log10(dichratios))
+MEGmaskindexSE7[area,2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+}
+
+times <- ((1:8008)-1001)/1001
+
+postscript("timecourse1.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,7,0,0.6)
+ticklocsx <- -1:7    # locations of tick marks on x axis
+ticklocsy <- seq(0,0.6,0.1)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocsx, side = 1, at=ticklocsx)
+mtext(text = ticklocsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,6,6,0),c(-0.022,-0.022,0.02,0.02),border=NA,col=rgb(0.5,0.5,0.5))
+
+if (plotsmoothed==0){
+polygon(times[c(1:8008,8008:1)],10*c(MEGmeantime5Hz[1,]+MEGSEtime5Hz[1,],MEGmeantime5Hz[1,8008:1]-MEGSEtime5Hz[1,8008:1]),col=colpal[1],border=NA)
+polygon(times[c(1:8008,8008:1)],10*c(MEGmeantime5Hz[3,]+MEGSEtime5Hz[3,],MEGmeantime5Hz[3,8008:1]-MEGSEtime5Hz[3,8008:1]),col=colpal[2],border=NA)
+polygon(times[c(1:8008,8008:1)],10*c(MEGmeantime5Hz[4,]+MEGSEtime5Hz[4,],MEGmeantime5Hz[4,8008:1]-MEGSEtime5Hz[4,8008:1]),col=colpal[3],border=NA)
+
+lines(times,10*MEGmeantime5Hz[1,],lwd=2,col=colpal[1])
+# lines(times,MEGmeantime5Hz[2,],lwd=2,col='green')
+lines(times,10*MEGmeantime5Hz[3,],lwd=2,col=colpal[2])
+lines(times,10*MEGmeantime5Hz[4,],lwd=2,col=colpal[3])
+}
+
+if (plotsmoothed==1){
+  for (area in 1:nareas){
+spl5aU <- smooth.spline(times,MEGmeantime5Hz[1,]+MEGSEtime5Hz[1,],df=20)
+spl5aL <- smooth.spline(times,MEGmeantime5Hz[1,]-MEGSEtime5Hz[1,],df=20)
+polygon(times[c(1:8008,8008:1)],c(spl5aU$y,spl5aL$y[8008:1]),col=colpal[1],border=NA)
+
+spl5cU <- smooth.spline(times,MEGmeantime5Hz[3,]+MEGSEtime5Hz[3,],df=20)
+spl5cL <- smooth.spline(times,MEGmeantime5Hz[3,]-MEGSEtime5Hz[3,],df=20)
+polygon(times[c(1:8008,8008:1)],c(spl5cU$y,spl5cL$y[8008:1]),col=colpal[2],border=NA)
+
+spl5dU <- smooth.spline(times,MEGmeantime5Hz[4,]+MEGSEtime5Hz[4,],df=20)
+spl5dL <- smooth.spline(times,MEGmeantime5Hz[4,]-MEGSEtime5Hz[4,],df=20)
+polygon(times[c(1:8008,8008:1)],c(spl5dU$y,spl5dL$y[8008:1]),col=colpal[3],border=NA)
+  }
+  for (area in 1:nareas){  
+spl5a <- smooth.spline(times,10*MEGmeantime5Hz[area,1,],df=20)
+lines(spl5a$x,spl5a$y,col=colpal[1],lwd=2)
+# spl5b <- smooth.spline(times,MEGmeantime5Hz[2,],df=20)
+# lines(spl5b$x,spl5b$y,col='green',lwd=2)
+spl5c <- smooth.spline(times,10*MEGmeantime5Hz[area,3,],df=20)
+lines(spl5c$x,spl5c$y,col=colpal[2],lwd=2)
+spl5d <- smooth.spline(times,10*MEGmeantime5Hz[area,4,],df=20)
+lines(spl5d$x,spl5d$y,col=colpal[3],lwd=2)
+}
+}
+
+dev.off()
+
+postscript("timecourse2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,7,-3,7)
+ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocsx, side = 1, at=ticklocsx)
+mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,6,6,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))
+
+lines(c(-1,7),c(0,0),lty=2)
+
+if (plotsmoothed==0){
+polygon(times[c(1:8008,8008:1)],c(MEGmaskindex5[1,]+MEGmaskindexSE5[1,],MEGmaskindex5[1,8008:1]-MEGmaskindexSE5[1,8008:1]),col=colpal[2],border=NA)
+polygon(times[c(1:8008,8008:1)],c(MEGmaskindex5[2,]+MEGmaskindexSE5[2,],MEGmaskindex5[2,8008:1]-MEGmaskindexSE5[2,8008:1]),col=colpal[3],border=NA)
+
+lines(times,MEGmaskindex5[1,],col=colpal[2],lwd=2)
+lines(times,MEGmaskindex5[2,],col=colpal[3],lwd=2)
+}
+if (plotsmoothed==1){
+U <- smooth.spline(times,MEGmaskindex5[1,]+MEGmaskindexSE5[1,],df=20)
+L <- smooth.spline(times,MEGmaskindex5[1,]-MEGmaskindexSE5[1,],df=20)
+polygon(times[c(1:8008,8008:1)],c(U$y,L$y[8008:1]),col=colpal[2],border=NA)
+
+U <- smooth.spline(times,MEGmaskindex5[2,]+MEGmaskindexSE5[2,],df=20)
+L <- smooth.spline(times,MEGmaskindex5[2,]-MEGmaskindexSE5[2,],df=20)
+polygon(times[c(1:8008,8008:1)],c(U$y,L$y[8008:1]),col=colpal[3],border=NA)
+
+for (area in 1:nareas){ 
+L <- smooth.spline(times,MEGmaskindex5[area,1,],df=20)
+lines(L$x,L$y,col=colpal[2],lwd=2)
+L <- smooth.spline(times,MEGmaskindex5[area,2,],df=20)
+lines(L$x,L$y,col=colpal[3],lwd=2)
+}
+}
+
+dev.off()
+
+postscript("timecourse3.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,7,0,0.6)
+ticklocsy <- seq(0,0.6,0.1)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocsx, side = 1, at=ticklocsx)
+mtext(text = ticklocsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,6,6,0),c(-0.022,-0.022,0.02,0.02),border=NA,col=rgb(0.5,0.5,0.5))
+
+if (plotsmoothed==0){
+polygon(times[c(1:8008,8008:1)],10*c(MEGmeantime7Hz[2,]+MEGSEtime7Hz[2,],MEGmeantime7Hz[2,8008:1]-MEGSEtime7Hz[2,8008:1]),col=colpal[1],border=NA)
+polygon(times[c(1:8008,8008:1)],10*c(MEGmeantime7Hz[3,]+MEGSEtime7Hz[3,],MEGmeantime7Hz[3,8008:1]-MEGSEtime7Hz[3,8008:1]),col=colpal[2],border=NA)
+polygon(times[c(1:8008,8008:1)],10*c(MEGmeantime7Hz[4,]+MEGSEtime7Hz[4,],MEGmeantime7Hz[4,8008:1]-MEGSEtime7Hz[4,8008:1]),col=colpal[3],border=NA)
+
+# lines(times,MEGmeantime7Hz[1,],lwd=2,col=colpal[1])
+lines(times,10*MEGmeantime7Hz[2,],lwd=2,col=colpal[1])
+lines(times,10*MEGmeantime7Hz[3,],lwd=2,col=colpal[2])
+lines(times,10*MEGmeantime7Hz[4,],lwd=2,col=colpal[3])
+}
+if (plotsmoothed==1){
+
+spl7bU <- smooth.spline(times,MEGmeantime7Hz[2,]+MEGSEtime7Hz[2,],df=20)
+spl7bL <- smooth.spline(times,MEGmeantime7Hz[2,]-MEGSEtime7Hz[2,],df=20)
+polygon(times[c(1:8008,8008:1)],c(spl7bU$y,spl7bL$y[8008:1]),col=colpal[1],border=NA)
+
+spl7cU <- smooth.spline(times,MEGmeantime7Hz[3,]+MEGSEtime7Hz[3,],df=20)
+spl7cL <- smooth.spline(times,MEGmeantime7Hz[3,]-MEGSEtime7Hz[3,],df=20)
+polygon(times[c(1:8008,8008:1)],c(spl7cU$y,spl7cL$y[8008:1]),col=colpal[2],border=NA)
+
+spl7dU <- smooth.spline(times,MEGmeantime7Hz[4,]+MEGSEtime7Hz[4,],df=20)
+spl7dL <- smooth.spline(times,MEGmeantime7Hz[4,]-MEGSEtime7Hz[4,],df=20)
+polygon(times[c(1:8008,8008:1)],c(spl7dU$y,spl7dL$y[8008:1]),col=colpal[3],border=NA)
+
+# spl7a <- smooth.spline(times,MEGmeantime7Hz[1,],df=20)
+# lines(spl7a$x,spl7a$y,col=colpal[1],lwd=2)
+  for (area in 1:nareas){ 
+spl7b <- smooth.spline(times,10*MEGmeantime7Hz[area,2,],df=20)
+lines(spl7b$x,spl7b$y,col=colpal[1],lwd=2)
+spl7c <- smooth.spline(times,10*MEGmeantime7Hz[area,3,],df=20)
+lines(spl7c$x,spl7c$y,col=colpal[2],lwd=2)
+spl7d <- smooth.spline(times,10*MEGmeantime7Hz[area,4,],df=20)
+lines(spl7d$x,spl7d$y,col=colpal[3],lwd=2)
+}
+}
+
+dev.off()
+
+postscript("timecourse4.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,7,-3,6)
+ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocsx, side = 1, at=ticklocsx)
+mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,6,6,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))
+
+lines(c(-1,7),c(0,0),lty=2)
+
+if (plotsmoothed==0){
+polygon(times[c(1:8008,8008:1)],c(MEGmaskindex7[1,]+MEGmaskindexSE7[1,],MEGmaskindex7[1,8008:1]-MEGmaskindexSE7[1,8008:1]),col=colpal[2],border=NA)
+polygon(times[c(1:8008,8008:1)],c(MEGmaskindex7[2,]+MEGmaskindexSE7[2,],MEGmaskindex7[2,8008:1]-MEGmaskindexSE7[2,8008:1]),col=colpal[3],border=NA)
+
+lines(times,MEGmaskindex7[1,],col=colpal[2],lwd=2)
+lines(times,MEGmaskindex7[2,],col=colpal[3],lwd=2)
+}
+
+if (plotsmoothed==1){
+U <- smooth.spline(times,MEGmaskindex7[1,]+MEGmaskindexSE7[1,],df=20)
+L <- smooth.spline(times,MEGmaskindex7[1,]-MEGmaskindexSE7[1,],df=20)
+polygon(times[c(1:8008,8008:1)],c(U$y,L$y[8008:1]),col=colpal[2],border=NA)
+
+U <- smooth.spline(times,MEGmaskindex7[2,]+MEGmaskindexSE7[2,],df=20)
+L <- smooth.spline(times,MEGmaskindex7[2,]-MEGmaskindexSE7[2,],df=20)
+polygon(times[c(1:8008,8008:1)],c(U$y,L$y[8008:1]),col=colpal[3],border=NA)
+
+for (area in 1:nareas){
+L <- smooth.spline(times,MEGmaskindex7[area,1,],df=20)
+lines(L$x,L$y,col=colpal[2],lwd=2)
+L <- smooth.spline(times,MEGmaskindex7[area,2,],df=20)
+lines(L$x,L$y,col=colpal[3],lwd=2)
+}
+}
+
+dev.off()
+
+# freqlist <- seq(1/6,20,length=ncol(meanspec))
+# 
+# postscript("spectrum.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 10)
+# 
+# plotlims <- c(0,20,0,4)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+# ticklocsx <- seq(0,20,5)    # locations of tick marks on x axis
+# ticklocsy <- c(0,0.4,0.8,1,2,3,4)    # locations of tick marks on y axis
+# ticklabelsx <- seq(0,20,5)        # set labels for x ticks
+# ticklabelsy <- c(0,0.2,0.4,'','','','')    # set labels for y ticks
+# plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+# axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+# axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+# mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+# mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+# title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+# title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+# 
+# lines(c(0,20),c(0,0),lty=3)
+# lines(c(0,20),c(1,1),lty=3)
+# lines(c(0,20),c(2,2),lty=3)
+# lines(c(0,20),c(3,3),lty=3)
+# 
+# # lines(c(5,5),c(0,4),col='grey',lwd=2)
+# # lines(c(7,7),c(0,4),col='grey',lwd=2)
+# 
+# polygon(c(1/6,freqlist,20),c(0,100*meanspec[1,],0)+3,border=NA,col=colpal[1])
+# polygon(c(1/6,freqlist,20),c(0,100*meanspec[2,],0)+2,border=NA,col=colpal[1])
+# polygon(c(1/6,freqlist,20),c(0,100*meanspec[3,],0)+1,border=NA,col=colpal[2])
+# polygon(c(1/6,freqlist,20),c(0,100*meanspec[4,],0),border=NA,col=colpal[3])
+# 
+# lines(freqlist,100*meanspec[1,]+3,lwd=2,col='black')
+# lines(freqlist,100*meanspec[2,]+2,lwd=2,col='black')
+# lines(freqlist,100*meanspec[3,]+1,lwd=2,col='black')
+# lines(freqlist,100*meanspec[4,],lwd=2,col='black')
+# 
+# text(20,3.5,'5Hz monocular target',pos=2,cex=1.5)
+# text(20,2.5,'7Hz monocular target',pos=2,cex=1.5)
+# text(20,1.5,'Monocular combination',pos=2,cex=1.5)
+# text(20,0.5,'Dichoptic combination',pos=2,cex=1.5)
+# 
+# dev.off()
+
+# 
+# 
+# allresps <- array(0, dim=c(length(d),4,2,9))
+# allspectra <- array(0, dim=c(length(d),4,6006))
+# allwaves <- array(0, dim=c(length(d), 4, 9009))
+# MEGtimecourse7Hz <- array(0, dim=c(length(d),4,8009))
+# MEGtimecourse5Hz <- array(0, dim=c(length(d),4,8009))
+# allRnos <- NULL
 # for (s in 1:length(d)){
-#   load(d[s])
-#   
-#   # remove any NaN values
-#   chanspec[which(is.na(chanspec))] <- 0
-#   allspec[which(is.na(allspec))] <- 0
-#   allsamples[which(is.na(allsamples))] <- 0
-#   
-#   ch <- match(targetelectrodes, electrodes) - 2
-#   
-#   meanchanspec <- (apply(chanspec,2:4,mean))
-#   spectoplot <- (apply(chanspec[,,ch,],c(2,4),mean))
-#   
-#   meanspec <- (apply(allspec,2:4,mean))
-#   for (f in 1:4){
+#   allRnos[s] <- substr(d2[s],1,5)
+#   data <- readMat(d[s])
+#   
 #   for (cond in 1:4){
-#       for (t in 1:10){
-#         temp <- allspec[,f,cond,t]
-#         tempxy <- data.frame(Re(temp),Im(temp))
+#       for (t in 1:9){
+#         all1F <- NULL
+#         all2F <- NULL
+#         for (rep in 1:data$trialcounter[1,cond]){
+#           trial <- data$alltrials[cond,rep,]
+# 
+#         sample <- trial[(1+((t-1)*1001)):(t*1001)]
+#         fftsample <- fft(sample)/length(sample)
+# 
+#         all1F[rep] <- fftsample[targetF + 1]
+#         all2F[rep] <- fftsample[maskF + 1]
+#       }
+# 
+#         tempxy <- data.frame(Re(all1F),Im(all1F))
 #         D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
 #         i <- which(D<3)
-#         meanspec[f,cond,t] <- (mean(temp[i]))
-#       }
-#     }
-#   }
-#   meanwaves <- apply(allsamples,2:3,mean)
-#   
-#   for (cond in 1:4){
+#         allresps[s,cond,1,t] <- mean(all1F[i])
+# 
+#         tempxy <- data.frame(Re(all2F),Im(all2F))
+#         D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+#         i <- which(D<3)
+#         allresps[s,cond,2,t] <- mean(all2F[i])
+#     }
+#     
+#     meanwave <- colMeans(data$alltrials[cond,1:data$trialcounter[1,cond],])
+#     
+#     sample <- meanwave[1001:7006]
+#     allspectra[s,cond,] <- fft(sample)/length(sample)  
+# 
+#     allwaves[s,cond,] <- meanwave
+#     
 # fspec1 <- NULL
 # fspec2 <- NULL
-# for (t in 1:(8000-binwidth)){
-#   spec <- fft(meanwaves[cond,t:(t+binwidth-1)])/binwidth
+# for (t in 1:(length(meanwave)-binwidth)){
+#   spec <- fft(meanwave[t:(t+binwidth-1)])/binwidth
 #   fspec1[t] <- spec[tindex]
@@
 # }
-#     EEGtimecourse5Hz[s,cond,] <- fspec1
-#     EEGtimecourse7Hz[s,cond,] <- fspec2 
-#   }
-#   
-#   meanwaves <- meanwaves - mean(meanwaves)
-#   meanwaves <- meanwaves / max(abs(meanwaves))
-#   groupmeans[s,,,] <- meanspec
-#   groupspec[s,,,] <- meanchanspec
-#   groupspecplot[s,,] <- spectoplot
-#   groupwaveforms[s,,] <- meanwaves
-#   
-# }
-# 
-# save(file='temp/EEGsummary.RData',list=c('groupmeans','groupspecplot','groupwaveforms','groupspec','EEGtimecourse5Hz','EEGtimecourse7Hz','electrodes'))
-# 
+#     MEGtimecourse5Hz[s,cond,] <- fspec1
+#     MEGtimecourse7Hz[s,cond,] <- fspec2
+#     
+#     
+#   }
+# }
+# 
+# save(file='temp/MEGsummary.RData',list=c('allspectra','allresps','allwaves','MEGtimecourse5Hz','MEGtimecourse7Hz','allRnos'))
 # }
@@
 # if (runcode==1){
-# load('temp/EEGsummary.RData')
-#     
-# meanspec <- abs(apply(groupmeans,c(2,3,4),mean))
-# spectoplot <- abs(apply(groupspecplot,c(2,3),mean))
-# meanwaves <- apply(groupwaveforms,c(2,3),mean)
-# meanchanspec <- abs(apply(groupspec,c(2,3,4),mean))
-# 
-# EEGmeantime5Hz <- matrix(0,nrow=4,ncol=7000) 
-# EEGmeantime7Hz <- matrix(0,nrow=4,ncol=7000) 
+#   
+#   load('temp/MEGsummary.RData')
+#   
+# allresps <- abs(allresps)
+# meanspec <- apply(allresps,2:4,mean)
+# 
+# MEGmeantime5Hz <- matrix(0,nrow=4,ncol=8009) 
+# MEGmeantime7Hz <- matrix(0,nrow=4,ncol=8009) 
 # for (cond in 1:4){
-# EEGmeantime7Hz[cond,] <- apply(abs(EEGtimecourse7Hz[,cond,]),2,mean)
-# EEGmeantime5Hz[cond,] <- apply(abs(EEGtimecourse5Hz[,cond,]),2,mean)
-# }
-# 
-# pdf("temp/figures/Fig3.pdf", bg="transparent", height = 10, width = 10)
+# MEGmeantime7Hz[cond,] <- apply(abs(MEGtimecourse7Hz[,cond,]),2,mean)
+# MEGmeantime5Hz[cond,] <- apply(abs(MEGtimecourse5Hz[,cond,]),2,mean)
+# }
+# 
+# 
+# qdata <- read.csv('~/Google Drive/Current work/Teaching/MSci project 2021/MSci project questionnaires 2021 (Responses) - Form Responses 1.csv')
+# qgroup <- as.factor(qdata[,5])
+# qRnos <- as.character(qdata[,2])
+# qAges <- qdata[,3]
+# qRnos[20] <- 'R5860'
+# qgroup[20] <- 'Yes'
+# qAges[20] <- 19
+# 
+#   
+# sortedgroups <- NULL
+# for (s in 1:length(allRnos)){sortedgroups[s] <- qgroup[which(qRnos==allRnos[s])]}
+# # sortedgroups now codes 1 = control, 2 = ASC in the order of the MEG data
+# 
+# lowAQ <- abs(apply(abs(allresps[which(sortedgroups==1),,,]),c(2,3,4),mean))
+# highAQ <- abs(apply(abs(allresps[which(sortedgroups==2),,,]),c(2,3,4),mean))
+# 
+# 
+# 
+# 
+# MEGmeantime5HzCON <- matrix(0,nrow=4,ncol=8009) 
+# MEGmeantime7HzCON <- matrix(0,nrow=4,ncol=8009) 
+# MEGmeantime5HzASD <- matrix(0,nrow=4,ncol=8009) 
+# MEGmeantime7HzASD <- matrix(0,nrow=4,ncol=8009) 
+# for (cond in 1:4){
+# MEGmeantime7HzCON[cond,] <- apply(abs(MEGtimecourse7Hz[which(sortedgroups==1),cond,]),2,mean)
+# MEGmeantime5HzCON[cond,] <- apply(abs(MEGtimecourse5Hz[which(sortedgroups==1),cond,]),2,mean)
+# MEGmeantime7HzASD[cond,] <- apply(abs(MEGtimecourse7Hz[which(sortedgroups==2),cond,]),2,mean)
+# MEGmeantime5HzASD[cond,] <- apply(abs(MEGtimecourse5Hz[which(sortedgroups==2),cond,]),2,mean)
+# }
+# 
+# pdf("temp/figures/Fig4.pdf", bg="transparent", height = 10, width = 10)
 # 
@@
 # 
-# times <- ((1:7000)-500)/1000
-# 
-# plotlims <- c(-1,8,0,1)
+# times <- ((1:8009)-500)/1000
+# 
+# plotlims <- c(-1,8,0,30)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
 # ticklocsx <- -1:8    # locations of tick marks on x axis
-# ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
+# ticklocsy <- seq(0,30,10)    # locations of tick marks on y axis
 # ticklabelsx <- -1:8        # set labels for x ticks
@@
 # 
-# lines(times,EEGmeantime5Hz[1,],lwd=2,col='red')
-# lines(times,EEGmeantime5Hz[2,],lwd=2,col='green')
-# lines(times,EEGmeantime5Hz[3,],lwd=2,col='blue')
-# lines(times,EEGmeantime5Hz[4,],lwd=2,col='orange')
-# 
-# 
-# spl5a <- smooth.spline(times,EEGmeantime5Hz[1,],df=20)
-# lines(spl5a$x,spl5a$y,col='red',lwd=2)
-# spl5b <- smooth.spline(times,EEGmeantime5Hz[2,],df=20)
+# # lines(times,1000*meanspec[1,1,],lwd=2,col=colpal[1])
+# # lines(times,1000*meanspec[2,1,],lwd=2,col='green')
+# # lines(times,1000*meanspec[3,1,],lwd=2,col=colpal[2])
+# # lines(times,1000*meanspec[4,1,],lwd=2,col=colpal[3])
+# 
+# 
+# # lines(times,1000*MEGmeantime5Hz[1,],lwd=2,col=colpal[1])
+# # lines(times,1000*MEGmeantime5Hz[2,],lwd=2,col='green')
+# # lines(times,1000*MEGmeantime5Hz[3,],lwd=2,col=colpal[2])
+# # lines(times,1000*MEGmeantime5Hz[4,],lwd=2,col=colpal[3])
+# spl5a <- smooth.spline(times,1000*MEGmeantime5Hz[1,],df=20)
+# lines(spl5a$x,spl5a$y,col=colpal[1],lwd=2)
+# spl5b <- smooth.spline(times,1000*MEGmeantime5Hz[2,],df=20)
 # lines(spl5b$x,spl5b$y,col='green',lwd=2)
-# spl5c <- smooth.spline(times,EEGmeantime5Hz[3,],df=20)
-# lines(spl5c$x,spl5c$y,col='blue',lwd=2)
-# spl5d <- smooth.spline(times,EEGmeantime5Hz[4,],df=20)
-# lines(spl5d$x,spl5d$y,col='orange',lwd=2)
-# 
-# 
-# plotlims <- c(-1,8,0,2) 
+# spl5c <- smooth.spline(times,1000*MEGmeantime5Hz[3,],df=20)
+# lines(spl5c$x,spl5c$y,col=colpal[2],lwd=2)
+# spl5d <- smooth.spline(times,1000*MEGmeantime5Hz[4,],df=20)
+# lines(spl5d$x,spl5d$y,col=colpal[3],lwd=2)
+# 
+# # lines(times,1000*MEGmeantime5HzASD[1,],lwd=2,col=colpal[1],lty=2)
+# # lines(times,1000*MEGmeantime5HzASD[2,],lwd=2,col='green',lty=2)
+# # lines(times,1000*MEGmeantime5HzASD[3,],lwd=2,col=colpal[2],lty=2)
+# # lines(times,1000*MEGmeantime5HzASD[4,],lwd=2,col=colpal[3],lty=2)
+# spl5aASD <- smooth.spline(times,1000*MEGmeantime5HzASD[1,],df=20)
+# lines(spl5aASD$x,spl5aASD$y,col=colpal[1],lwd=2,lty=2)
+# spl5bASD <- smooth.spline(times,1000*MEGmeantime5HzASD[2,],df=20)
+# lines(spl5bASD$x,spl5bASD$y,col='green',lwd=2,lty=2)
+# spl5cASD <- smooth.spline(times,1000*MEGmeantime5HzASD[3,],df=20)
+# lines(spl5cASD$x,spl5cASD$y,col=colpal[2],lwd=2,lty=2)
+# spl5dASD <- smooth.spline(times,1000*MEGmeantime5HzASD[4,],df=20)
+# lines(spl5dASD$x,spl5dASD$y,col=colpal[3],lwd=2,lty=2)
+# 
+# # lines(times,1000*MEGmeantime5HzCON[1,],lwd=2,col=colpal[1],lty=3)
+# # lines(times,1000*MEGmeantime5HzCON[2,],lwd=2,col='green',lty=3)
+# # lines(times,1000*MEGmeantime5HzCON[3,],lwd=2,col=colpal[2],lty=3)
+# # lines(times,1000*MEGmeantime5HzCON[4,],lwd=2,col=colpal[3],lty=3)
+# spl5aCON <- smooth.spline(times,1000*MEGmeantime5HzCON[1,],df=20)
+# lines(spl5aCON$x,spl5aCON$y,col=colpal[1],lwd=2,lty=3)
+# spl5bCON <- smooth.spline(times,1000*MEGmeantime5HzCON[2,],df=20)
+# lines(spl5bCON$x,spl5bCON$y,col='green',lwd=2,lty=3)
+# spl5cCON <- smooth.spline(times,1000*MEGmeantime5HzCON[3,],df=20)
+# lines(spl5cCON$x,spl5cCON$y,col=colpal[2],lwd=2,lty=3)
+# spl5dCON <- smooth.spline(times,1000*MEGmeantime5HzCON[4,],df=20)
+# lines(spl5dCON$x,spl5dCON$y,col=colpal[3],lwd=2,lty=3)
+# 
+# 
+# 
+# plotlims <- c(-1,8,0,2)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
 # ticklocsx <- -1:8    # locations of tick marks on x axis
@@
 # title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-# title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-# 
-# lines(times,EEGmeantime5Hz[1,]/EEGmeantime5Hz[3,],col='blue',lwd=2)
-# lines(times,EEGmeantime5Hz[1,]/EEGmeantime5Hz[4,],col='orange',lwd=2)
-# 
-# lines(spl5a$x,spl5a$y/spl5c$y,col='blue',lwd=2)
-# lines(spl5a$x,spl5a$y/spl5d$y,col='orange',lwd=2)
-# 
-# 
-# plotlims <- c(-1,8,0,1) 
+# title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+# 
+# lines(spl5b$x,spl5a$y/spl5c$y,col=colpal[2],lwd=2)
+# lines(spl5b$x,spl5a$y/spl5d$y,col=colpal[3],lwd=2)
+# 
+# lines(spl5bASD$x,spl5aASD$y/spl5cASD$y,col=colpal[2],lwd=2,lty=2)
+# lines(spl5bASD$x,spl5aASD$y/spl5dASD$y,col=colpal[3],lwd=2,lty=2)
+# 
+# lines(spl5bCON$x,spl5aCON$y/spl5cCON$y,col=colpal[2],lwd=2,lty=3)
+# lines(spl5bCON$x,spl5aCON$y/spl5dCON$y,col=colpal[3],lwd=2,lty=3)
+# 
+# 
+# plotlims <- c(-1,8,0,30)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
 # ticklocsx <- -1:8    # locations of tick marks on x axis
-# ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
+# ticklocsy <- seq(0,30,10)    # locations of tick marks on y axis
+# ticklabelsx <- -1:8        # set labels for x ticks
+# ticklabelsy <- ticklocsy    # set labels for y ticks
 # plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
@@
 # 
-# lines(times,EEGmeantime7Hz[1,],lwd=2,col='red')
-# lines(times,EEGmeantime7Hz[2,],lwd=2,col='green')
-# lines(times,EEGmeantime7Hz[3,],lwd=2,col='blue')
-# lines(times,EEGmeantime7Hz[4,],lwd=2,col='orange')
-# 
-# 
-# spl7a <- smooth.spline(times,EEGmeantime7Hz[1,],df=20)
-# lines(spl7a$x,spl7a$y,col='red',lwd=2)
-# spl7b <- smooth.spline(times,EEGmeantime7Hz[2,],df=20)
+# # lines(times,1000*MEGmeantime7Hz[1,],lwd=2,col=colpal[1])
+# # lines(times,1000*MEGmeantime7Hz[2,],lwd=2,col='green')
+# # lines(times,1000*MEGmeantime7Hz[3,],lwd=2,col=colpal[2])
+# # lines(times,1000*MEGmeantime7Hz[4,],lwd=2,col=colpal[3])
+# spl7a <- smooth.spline(times,1000*MEGmeantime7Hz[1,],df=20)
+# lines(spl7a$x,spl7a$y,col=colpal[1],lwd=2)
+# spl7b <- smooth.spline(times,1000*MEGmeantime7Hz[2,],df=20)
 # lines(spl7b$x,spl7b$y,col='green',lwd=2)
-# spl7c <- smooth.spline(times,EEGmeantime7Hz[3,],df=20)
-# lines(spl7c$x,spl7c$y,col='blue',lwd=2)
-# spl7d <- smooth.spline(times,EEGmeantime7Hz[4,],df=20)
-# lines(spl7d$x,spl7d$y,col='orange',lwd=2)
-# 
-# 
-# plotlims <- c(-1,8,0,2) 
+# spl7c <- smooth.spline(times,1000*MEGmeantime7Hz[3,],df=20)
+# lines(spl7c$x,spl7c$y,col=colpal[2],lwd=2)
+# spl7d <- smooth.spline(times,1000*MEGmeantime7Hz[4,],df=20)
+# lines(spl7d$x,spl7d$y,col=colpal[3],lwd=2)
+# 
+# # lines(times,1000*MEGmeantime7HzASD[1,],lwd=2,col=colpal[1],lty=2)
+# # lines(times,1000*MEGmeantime7HzASD[2,],lwd=2,col='green',lty=2)
+# # lines(times,1000*MEGmeantime7HzASD[3,],lwd=2,col=colpal[2],lty=2)
+# # lines(times,1000*MEGmeantime7HzASD[4,],lwd=2,col=colpal[3],lty=2)
+# spl7aASD <- smooth.spline(times,1000*MEGmeantime7HzASD[1,],df=20)
+# lines(spl7aASD$x,spl7aASD$y,col=colpal[1],lwd=2,lty=2)
+# spl7bASD <- smooth.spline(times,1000*MEGmeantime7HzASD[2,],df=20)
+# lines(spl7bASD$x,spl7bASD$y,col='green',lwd=2,lty=2)
+# spl7cASD <- smooth.spline(times,1000*MEGmeantime7HzASD[3,],df=20)
+# lines(spl7cASD$x,spl7cASD$y,col=colpal[2],lwd=2,lty=2)
+# spl7dASD <- smooth.spline(times,1000*MEGmeantime7HzASD[4,],df=20)
+# lines(spl7dASD$x,spl7dASD$y,col=colpal[3],lwd=2,lty=2)
+# 
+# # lines(times,1000*MEGmeantime7HzCON[1,],lwd=2,col=colpal[1],lty=3)
+# # lines(times,1000*MEGmeantime7HzCON[2,],lwd=2,col='green',lty=3)
+# # lines(times,1000*MEGmeantime7HzCON[3,],lwd=2,col=colpal[2],lty=3)
+# # lines(times,1000*MEGmeantime7HzCON[4,],lwd=2,col=colpal[3],lty=3)
+# spl7aCON <- smooth.spline(times,1000*MEGmeantime7HzCON[1,],df=20)
+# lines(spl7aCON$x,spl7aCON$y,col=colpal[1],lwd=2,lty=3)
+# spl7bCON <- smooth.spline(times,1000*MEGmeantime7HzCON[2,],df=20)
+# lines(spl7bCON$x,spl7bCON$y,col='green',lwd=2,lty=3)
+# spl7cCON <- smooth.spline(times,1000*MEGmeantime7HzCON[3,],df=20)
+# lines(spl7cCON$x,spl7cCON$y,col=colpal[2],lwd=2,lty=3)
+# spl7dCON <- smooth.spline(times,1000*MEGmeantime7HzCON[4,],df=20)
+# lines(spl7dCON$x,spl7dCON$y,col=colpal[3],lwd=2,lty=3)
+# 
+# 
+# plotlims <- c(-1,8,0,2)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
 # ticklocsx <- -1:8    # locations of tick marks on x axis
@@
 # title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-# title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-# 
-# lines(times,EEGmeantime7Hz[2,]/EEGmeantime7Hz[3,],col='blue',lwd=2)
-# lines(times,EEGmeantime7Hz[2,]/EEGmeantime7Hz[4,],col='orange',lwd=2)
-# 
-# lines(spl7b$x,spl7b$y/spl7c$y,col='blue',lwd=2)
-# lines(spl7b$x,spl7b$y/spl7d$y,col='orange',lwd=2)
+# title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+# 
+# lines(spl7b$x,spl7b$y/spl7c$y,col=colpal[2],lwd=2)
+# lines(spl7b$x,spl7b$y/spl7d$y,col=colpal[3],lwd=2)
+# 
+# lines(spl7bASD$x,spl7bASD$y/spl7cASD$y,col=colpal[2],lwd=2,lty=2)
+# lines(spl7bASD$x,spl7bASD$y/spl7dASD$y,col=colpal[3],lwd=2,lty=2)
+# 
+# lines(spl7bCON$x,spl7bCON$y/spl7cCON$y,col=colpal[2],lwd=2,lty=3)
+# lines(spl7bCON$x,spl7bCON$y/spl7dCON$y,col=colpal[3],lwd=2,lty=3)
+# 
+# 
+# # lines(times,1000*meanspec[1,2,],lwd=2,lty=2,col=colpal[1])
+# # lines(times,1000*meanspec[2,2,],lwd=2,lty=2,col='green')
+# # lines(times,1000*meanspec[3,2,],lwd=2,lty=2,col=colpal[2])
+# # lines(times,1000*meanspec[4,2,],lwd=2,lty=2,col=colpal[3])
+# 
+# # text(-0.5,3.8,paste0('N=',length(allRnos)),cex=2)
+# # condlist <- c('5Hz target only','5Hz mask only','5Hz mon','5Hz dich','7Hz target only','7Hz mask only','7Hz mon','7Hz dich')
+# # if (outputplot>0){legend(0,4,condlist,col=c(colpal[1],'green',colpal[2],colpal[3]),lty=c(1,1,1,1,2,2,2,2),lwd=2,box.lwd=2)}
 # 
 # dev.off()
-# 
-}
-
-```
-
-```{r EEGdata, fig.cap="E.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('temp/figures/Fig3.pdf')
-
-```
-
-Participants showed a wide range of scores on both the AQ and SPQ scales, which were negatively correlated (Fig 3a; R = , p < ).
-We again performed a median split by AQ on the EEG data, and calculated the timecourse of the EEG response and masking ratios for each group (Figure 3b,c).
-
-Next we repeated the experiment on 20 participants using a 248-channel whole-head cryogenic MEG system.
-Half of the participants had a diagnosis of autism, and the remainder were age and gender-matched controls.
-Source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm (reference) showed strong localisation of steady-state signals at the occipital pole (see Figure 4a,b).
-Responses across V1 showed a similar timecourse to those of the EEG experiment at both frequencies (Figure 4c,d), and showed increasing suppression during the first 4 seconds of stimulus presentation (Figure 4e,f).
-
-```{r include=FALSE, results='hide'}
-
-if (processraw==1){
-
-samplerate <- 1001
-targetF <- 5
-maskF <- 7
-    binwidth <- 1001
-    tindex <- 1 + targetF*(binwidth/samplerate)
-    mindex <- 1 + maskF*(binwidth/samplerate)
-
-# d <- dir(path = 'temp/V2/', pattern = '*alltrialsV2.mat', full.names=TRUE)
-# d2 <- dir(path = 'temp/V2/', pattern = '*alltrialsV2.mat', full.names=FALSE)
-d <- dir(path = 'temp/MEGdata/', pattern = '*alltrials.mat', full.names=TRUE)
-d2 <- dir(path = 'temp/MEGdata/', pattern = '*alltrials.mat', full.names=FALSE)
-
-allresps <- array(0, dim=c(length(d),4,2,9))
-allspectra <- array(0, dim=c(length(d),4,6006))
-allwaves <- array(0, dim=c(length(d), 4, 9010))
-MEGtimecourse7Hz <- array(0, dim=c(length(d),4,8009))
-MEGtimecourse5Hz <- array(0, dim=c(length(d),4,8009))
-allRnos <- NULL
-for (s in 1:length(d)){
-  allRnos[s] <- substr(d2[s],1,5)
-  data <- readMat(d[s])
-
-  for (cond in 1:4){
-      for (t in 1:9){
-        all1F <- NULL
-        all2F <- NULL
-        for (rep in 1:data$trialcounter[1,cond]){
-          trial <- data$alltrials[cond,rep,]
-
-        sample <- trial[(1+((t-1)*1001)):(t*1001)]
-        fftsample <- fft(sample)/length(sample)
-
-        all1F[rep] <- fftsample[targetF + 1]
-        all2F[rep] <- fftsample[maskF + 1]
-      }
-
-        tempxy <- data.frame(Re(all1F),Im(all1F))
-        D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
-        i <- which(D<3)
-        allresps[s,cond,1,t] <- mean(all1F[i])
-
-        tempxy <- data.frame(Re(all2F),Im(all2F))
-        D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
-        i <- which(D<3)
-        allresps[s,cond,2,t] <- mean(all2F[i])
-    }
-
-    meanwave <- colMeans(data$alltrials[cond,1:data$trialcounter[1,cond],])
-
-    sample <- meanwave[1001:7006]
-    allspectra[s,cond,] <- fft(sample)/length(sample)
-
-    allwaves[s,cond,] <- meanwave
-
-fspec1 <- NULL
-fspec2 <- NULL
-for (t in 1:(length(meanwave)-binwidth)){
-  spec <- fft(meanwave[t:(t+binwidth-1)])/binwidth
-  fspec1[t] <- spec[tindex]
-  fspec2[t] <- spec[mindex]
-}
-    MEGtimecourse5Hz[s,cond,] <- fspec1
-    MEGtimecourse7Hz[s,cond,] <- fspec2
-
-  }
-}
-
-save(file='temp/MEGsummary.RData',list=c('allspectra','allresps','allwaves','MEGtimecourse5Hz','MEGtimecourse7Hz','allRnos'))
-}
-
-if (runcode==1){
-
-  load('temp/MEGsummary.RData')
-
-allresps <- abs(allresps)
-meanspec <- apply(allresps,2:4,mean)
-
-MEGmeantime5Hz <- matrix(0,nrow=4,ncol=8009) 
-MEGmeantime7Hz <- matrix(0,nrow=4,ncol=8009) 
-for (cond in 1:4){
-MEGmeantime7Hz[cond,] <- apply(abs(MEGtimecourse7Hz[,cond,]),2,mean)
-MEGmeantime5Hz[cond,] <- apply(abs(MEGtimecourse5Hz[,cond,]),2,mean)
-}
-
-qdata <- read.csv('~/Google Drive/Current work/Teaching/MSci project 2021/MSci project questionnaires 2021 (Responses) - Form Responses 1.csv')
-qgroup <- as.factor(qdata[,5])
-qRnos <- as.character(qdata[,2])
-qAges <- qdata[,3]
-qRnos[20] <- 'R5860'
-qgroup[20] <- 'Yes'
-qAges[20] <- 19
-
-sortedgroups <- NULL
-for (s in 1:length(allRnos)){sortedgroups[s] <- qgroup[which(qRnos==allRnos[s])]}
-# sortedgroups now codes 1 = control, 2 = ASC in the order of the MEG data
-
-lowAQ <- abs(apply(abs(allresps[which(sortedgroups==1),,,]),c(2,3,4),mean))
-highAQ <- abs(apply(abs(allresps[which(sortedgroups==2),,,]),c(2,3,4),mean))
-
-MEGmeantime5HzCON <- matrix(0,nrow=4,ncol=8009) 
-MEGmeantime7HzCON <- matrix(0,nrow=4,ncol=8009) 
-MEGmeantime5HzASD <- matrix(0,nrow=4,ncol=8009) 
-MEGmeantime7HzASD <- matrix(0,nrow=4,ncol=8009) 
-for (cond in 1:4){
-MEGmeantime7HzCON[cond,] <- apply(abs(MEGtimecourse7Hz[which(sortedgroups==1),cond,]),2,mean)
-MEGmeantime5HzCON[cond,] <- apply(abs(MEGtimecourse5Hz[which(sortedgroups==1),cond,]),2,mean)
-MEGmeantime7HzASD[cond,] <- apply(abs(MEGtimecourse7Hz[which(sortedgroups==2),cond,]),2,mean)
-MEGmeantime5HzASD[cond,] <- apply(abs(MEGtimecourse5Hz[which(sortedgroups==2),cond,]),2,mean)
-}
-
-pdf("temp/figures/Fig4.pdf", bg="transparent", height = 10, width = 10)
-
-par(mfrow=c(2,2))
-
-times <- ((1:8009)-500)/1000
-
-plotlims <- c(-1,8,0,30)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
-ticklocsx <- -1:8    # locations of tick marks on x axis
-ticklocsy <- seq(0,30,10)    # locations of tick marks on y axis
-ticklabelsx <- -1:8        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-# lines(times,1000*meanspec[1,1,],lwd=2,col='red')
-# lines(times,1000*meanspec[2,1,],lwd=2,col='green')
-# lines(times,1000*meanspec[3,1,],lwd=2,col='blue')
-# lines(times,1000*meanspec[4,1,],lwd=2,col='orange')
-
-# lines(times,1000*MEGmeantime5Hz[1,],lwd=2,col='red')
-# lines(times,1000*MEGmeantime5Hz[2,],lwd=2,col='green')
-# lines(times,1000*MEGmeantime5Hz[3,],lwd=2,col='blue')
-# lines(times,1000*MEGmeantime5Hz[4,],lwd=2,col='orange')
-spl5a <- smooth.spline(times,1000*MEGmeantime5Hz[1,],df=20)
-lines(spl5a$x,spl5a$y,col='red',lwd=2)
-spl5b <- smooth.spline(times,1000*MEGmeantime5Hz[2,],df=20)
-lines(spl5b$x,spl5b$y,col='green',lwd=2)
-spl5c <- smooth.spline(times,1000*MEGmeantime5Hz[3,],df=20)
-lines(spl5c$x,spl5c$y,col='blue',lwd=2)
-spl5d <- smooth.spline(times,1000*MEGmeantime5Hz[4,],df=20)
-lines(spl5d$x,spl5d$y,col='orange',lwd=2)
-
-# lines(times,1000*MEGmeantime5HzASD[1,],lwd=2,col='red',lty=2)
-# lines(times,1000*MEGmeantime5HzASD[2,],lwd=2,col='green',lty=2)
-# lines(times,1000*MEGmeantime5HzASD[3,],lwd=2,col='blue',lty=2)
-# lines(times,1000*MEGmeantime5HzASD[4,],lwd=2,col='orange',lty=2)
-spl5aASD <- smooth.spline(times,1000*MEGmeantime5HzASD[1,],df=20)
-lines(spl5aASD$x,spl5aASD$y,col='red',lwd=2,lty=2)
-spl5bASD <- smooth.spline(times,1000*MEGmeantime5HzASD[2,],df=20)
-lines(spl5bASD$x,spl5bASD$y,col='green',lwd=2,lty=2)
-spl5cASD <- smooth.spline(times,1000*MEGmeantime5HzASD[3,],df=20)
-lines(spl5cASD$x,spl5cASD$y,col='blue',lwd=2,lty=2)
-spl5dASD <- smooth.spline(times,1000*MEGmeantime5HzASD[4,],df=20)
-lines(spl5dASD$x,spl5dASD$y,col='orange',lwd=2,lty=2)
-
-# lines(times,1000*MEGmeantime5HzCON[1,],lwd=2,col='red',lty=3)
-# lines(times,1000*MEGmeantime5HzCON[2,],lwd=2,col='green',lty=3)
-# lines(times,1000*MEGmeantime5HzCON[3,],lwd=2,col='blue',lty=3)
-# lines(times,1000*MEGmeantime5HzCON[4,],lwd=2,col='orange',lty=3)
-spl5aCON <- smooth.spline(times,1000*MEGmeantime5HzCON[1,],df=20)
-lines(spl5aCON$x,spl5aCON$y,col='red',lwd=2,lty=3)
-spl5bCON <- smooth.spline(times,1000*MEGmeantime5HzCON[2,],df=20)
-lines(spl5bCON$x,spl5bCON$y,col='green',lwd=2,lty=3)
-spl5cCON <- smooth.spline(times,1000*MEGmeantime5HzCON[3,],df=20)
-lines(spl5cCON$x,spl5cCON$y,col='blue',lwd=2,lty=3)
-spl5dCON <- smooth.spline(times,1000*MEGmeantime5HzCON[4,],df=20)
-lines(spl5dCON$x,spl5dCON$y,col='orange',lwd=2,lty=3)
-
-plotlims <- c(-1,8,0,2)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
-ticklocsx <- -1:8    # locations of tick marks on x axis
-ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
-ticklabelsx <- -1:8        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-lines(spl5b$x,spl5a$y/spl5c$y,col='blue',lwd=2)
-lines(spl5b$x,spl5a$y/spl5d$y,col='orange',lwd=2)
-
-lines(spl5bASD$x,spl5aASD$y/spl5cASD$y,col='blue',lwd=2,lty=2)
-lines(spl5bASD$x,spl5aASD$y/spl5dASD$y,col='orange',lwd=2,lty=2)
-
-lines(spl5bCON$x,spl5aCON$y/spl5cCON$y,col='blue',lwd=2,lty=3)
-lines(spl5bCON$x,spl5aCON$y/spl5dCON$y,col='orange',lwd=2,lty=3)
-
-plotlims <- c(-1,8,0,30)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
-ticklocsx <- -1:8    # locations of tick marks on x axis
-ticklocsy <- seq(0,30,10)    # locations of tick marks on y axis
-ticklabelsx <- -1:8        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-# lines(times,1000*MEGmeantime7Hz[1,],lwd=2,col='red')
-# lines(times,1000*MEGmeantime7Hz[2,],lwd=2,col='green')
-# lines(times,1000*MEGmeantime7Hz[3,],lwd=2,col='blue')
-# lines(times,1000*MEGmeantime7Hz[4,],lwd=2,col='orange')
-spl7a <- smooth.spline(times,1000*MEGmeantime7Hz[1,],df=20)
-lines(spl7a$x,spl7a$y,col='red',lwd=2)
-spl7b <- smooth.spline(times,1000*MEGmeantime7Hz[2,],df=20)
-lines(spl7b$x,spl7b$y,col='green',lwd=2)
-spl7c <- smooth.spline(times,1000*MEGmeantime7Hz[3,],df=20)
-lines(spl7c$x,spl7c$y,col='blue',lwd=2)
-spl7d <- smooth.spline(times,1000*MEGmeantime7Hz[4,],df=20)
-lines(spl7d$x,spl7d$y,col='orange',lwd=2)
-
-# lines(times,1000*MEGmeantime7HzASD[1,],lwd=2,col='red',lty=2)
-# lines(times,1000*MEGmeantime7HzASD[2,],lwd=2,col='green',lty=2)
-# lines(times,1000*MEGmeantime7HzASD[3,],lwd=2,col='blue',lty=2)
-# lines(times,1000*MEGmeantime7HzASD[4,],lwd=2,col='orange',lty=2)
-spl7aASD <- smooth.spline(times,1000*MEGmeantime7HzASD[1,],df=20)
-lines(spl7aASD$x,spl7aASD$y,col='red',lwd=2,lty=2)
-spl7bASD <- smooth.spline(times,1000*MEGmeantime7HzASD[2,],df=20)
-lines(spl7bASD$x,spl7bASD$y,col='green',lwd=2,lty=2)
-spl7cASD <- smooth.spline(times,1000*MEGmeantime7HzASD[3,],df=20)
-lines(spl7cASD$x,spl7cASD$y,col='blue',lwd=2,lty=2)
-spl7dASD <- smooth.spline(times,1000*MEGmeantime7HzASD[4,],df=20)
-lines(spl7dASD$x,spl7dASD$y,col='orange',lwd=2,lty=2)
-
-# lines(times,1000*MEGmeantime7HzCON[1,],lwd=2,col='red',lty=3)
-# lines(times,1000*MEGmeantime7HzCON[2,],lwd=2,col='green',lty=3)
-# lines(times,1000*MEGmeantime7HzCON[3,],lwd=2,col='blue',lty=3)
-# lines(times,1000*MEGmeantime7HzCON[4,],lwd=2,col='orange',lty=3)
-spl7aCON <- smooth.spline(times,1000*MEGmeantime7HzCON[1,],df=20)
-lines(spl7aCON$x,spl7aCON$y,col='red',lwd=2,lty=3)
-spl7bCON <- smooth.spline(times,1000*MEGmeantime7HzCON[2,],df=20)
-lines(spl7bCON$x,spl7bCON$y,col='green',lwd=2,lty=3)
-spl7cCON <- smooth.spline(times,1000*MEGmeantime7HzCON[3,],df=20)
-lines(spl7cCON$x,spl7cCON$y,col='blue',lwd=2,lty=3)
-spl7dCON <- smooth.spline(times,1000*MEGmeantime7HzCON[4,],df=20)
-lines(spl7dCON$x,spl7dCON$y,col='orange',lwd=2,lty=3)
-
-plotlims <- c(-1,8,0,2)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
-ticklocsx <- -1:8    # locations of tick marks on x axis
-ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
-ticklabelsx <- -1:8        # set labels for x ticks
-ticklabelsy <- ticklocsy    # set labels for y ticks
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
-mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-title(ylab="Masking ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-lines(spl7b$x,spl7b$y/spl7c$y,col='blue',lwd=2)
-lines(spl7b$x,spl7b$y/spl7d$y,col='orange',lwd=2)
-
-lines(spl7bASD$x,spl7bASD$y/spl7cASD$y,col='blue',lwd=2,lty=2)
-lines(spl7bASD$x,spl7bASD$y/spl7dASD$y,col='orange',lwd=2,lty=2)
-
-lines(spl7bCON$x,spl7bCON$y/spl7cCON$y,col='blue',lwd=2,lty=3)
-lines(spl7bCON$x,spl7bCON$y/spl7dCON$y,col='orange',lwd=2,lty=3)
-
-# lines(times,1000*meanspec[1,2,],lwd=2,lty=2,col='red')
-# lines(times,1000*meanspec[2,2,],lwd=2,lty=2,col='green')
-# lines(times,1000*meanspec[3,2,],lwd=2,lty=2,col='blue')
-# lines(times,1000*meanspec[4,2,],lwd=2,lty=2,col='orange')
-
-# text(-0.5,3.8,paste0('N=',length(allRnos)),cex=2)
-# condlist <- c('5Hz target only','5Hz mask only','5Hz mon','5Hz dich','7Hz target only','7Hz mask only','7Hz mon','7Hz dich')
-# if (outputplot>0){legend(0,4,condlist,col=c('red','green','blue','orange'),lty=c(1,1,1,1,2,2,2,2),lwd=2,box.lwd=2)}
+
+   PostScriptTrace(paste('timecourse1.ps',sep=''))
+  e6 <- readPicture('timecourse1.ps.xml')
+  for (n in 1:length(e6@paths)){
+    temp <- class(e6@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e6@paths[n]$path@rgb))<765){e6@paths[n]$path@rgb <- addalpha(e6@paths[n]$path@rgb,alpha=0.2)}}}
+
+   PostScriptTrace(paste('timecourse2.ps',sep=''))
+  e7 <- readPicture('timecourse2.ps.xml')
+  for (n in 1:length(e7@paths)){
+    temp <- class(e7@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e7@paths[n]$path@rgb))<765){e7@paths[n]$path@rgb <- addalpha(e7@paths[n]$path@rgb,alpha=0.2)}}}
+
+     PostScriptTrace(paste('timecourse3.ps',sep=''))
+  e8 <- readPicture('timecourse3.ps.xml')
+  for (n in 1:length(e8@paths)){
+    temp <- class(e8@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e8@paths[n]$path@rgb))<765){e8@paths[n]$path@rgb <- addalpha(e8@paths[n]$path@rgb,alpha=0.2)}}}
+
+     PostScriptTrace(paste('timecourse4.ps',sep=''))
+  e9 <- readPicture('timecourse4.ps.xml')
+  for (n in 1:length(e9@paths)){
+    temp <- class(e9@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e9@paths[n]$path@rgb))<765){e9@paths[n]$path@rgb <- addalpha(e9@paths[n]$path@rgb,alpha=0.2)}}}
+
+  pdf('temp/figures/Fig4.pdf', bg="transparent", height = 12, width = 12)
+  par(mar=c(0.1,0.1,0.1,0.1))
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
+
+  grid.picture(e6,x=0.25,y=0.75,width=0.5,height=1)
+  grid.picture(e7,x=0.75,y=0.75,width=0.5,height=1)
+  grid.picture(e8,x=0.25,y=0.25,width=0.5,height=1)
+  grid.picture(e9,x=0.75,y=0.25,width=0.5,height=1)
+
+  # text(-0.02,1,'(a)',pos=4,cex=2)
+  # text(-0.02,0.45,'(b)',pos=4,cex=2)
+  # text(0.515,1,'(c)',pos=4,cex=2)
+  # text(0.515,0.46,'(d)',pos=4,cex=2)
+  # text(0.785,1,'(e)',pos=4,cex=2)
+  # text(0.785,0.46,'(f)',pos=4,cex=2)
+  # 
+  # text(-0.02,0.61,'5Hz',pos=4,cex=2)
+  # text(-0.02,0.89,'7Hz',pos=4,cex=2)
 
   dev.off()
+
+  file.remove(c('timecourse1.ps','timecourse2.ps','timecourse3.ps','timecourse4.ps'))
+  file.remove(c('timecourse1.ps.xml','timecourse2.ps.xml','timecourse3.ps.xml','timecourse4.ps.xml'))
+
 }

### 2022-06-14 manuscript.Rmd
Analysis updates

@@
 author: Daniel H. Baker, Daniela Marinova, Richard Aveyard, Lydia Hargreaves, Alice
-  Renton, Ruby Castellani, Phoebe Hall, Miriam Harmens, Georgia Holroyd, Dorian Manning,
+  Renton, Ruby Castellani, Phoebe Hall, Miriam Harmens, Georgia Holroyd,
   Beth Nicholson, Emily Williams, Hannah M. Hobson & Alex R. Wade
@@
 
-runcode <- 1  # this flag chooses whether to run the underlying analysis code (1), or just load in the figures from the last time this was run (0)
-processraw <- 1  # this flag determines whether the raw data are downloaded from OSF and processed - this will require ~30GB of hard drive space and take several hours
-
-plotsmoothed <- 0 # either plot the raw data (0), or a smoothed spline (1)
+processdata <- 0  # this flag determines the amount of processing, with 4 levels:
+# 0 - do no processing, generate the pdf using existing versions of all scripts
+# 1 - generate figures using the processed group data (requires XGB of storage)
+# 2 - download processed individual data and analyse (requires XGB of storage)
+# 3 - download all raw data and analyse (requires XGB of storage)
+
+plotsmoothed <- 1 # either plot the raw data (0), or a smoothed spline (1)
 
@@
 
-if (processraw==1){
+    binwidth <- 1000
+    findex <- 1 + targetF*(binwidth/1000)
+    findex[2] <- 1 + maskF*(binwidth/1000)
+    findex[3] <- 1 + 2*targetF*(binwidth/1000)
+    findex[4] <- 1 + 2*maskF*(binwidth/1000)
+
+condlist <- c(6,8,13)
+
+if (processdata>2){
 
@@
     allsamples <- array(0, dim = c(10,20,64,duration*samplerate))
-    if (s < 10){untar(paste(datadir, 'S0', s, '.tar', sep = ''), exdir = tempdir)}
-    if (s > 9){untar(paste(datadir, 'S', s, '.tar', sep = ''), exdir = tempdir)}
+    if (s < 10){d <- dir(path = paste0(tempdir,'S0',s), pattern='*.csv.gz',full.names=TRUE)}
+    if (s > 9){d <- dir(path = paste0(tempdir,'S',s), pattern='*.csv.gz',full.names=TRUE)}
 
@@
     for (block in 1:length(d)) {
-      EEGdata <- read.csv(paste(tempdir, d[block], sep = ''), header = TRUE)
+      EEGdata <- read.csv(d[block], header = TRUE)
 
@@
       counter <- 0
-      for (n in 1000:nrow(EEGdata)) {    # ignore triggers starting in the first 1000ms that generate an error
-      for (n in 1:nrow(EEGdata)) {
+      for (n in 1500:nrow(EEGdata)) {    # ignore triggers starting in the first 1000ms that generate an error
         if (EEGdata$Trigger[n] %in% legaltriggers) {
@@
         temp <- as.matrix(EEGdata[(triggertimes[tr]:(triggertimes[tr] + samplerate * duration - 1))-1499, ch + 2])
-        temp <- temp - mean(temp[501:1500])   # baseline subtraction to remove DC component
+        temp <- temp - mean(temp[501:1500])
         allsamples[condcounter[cond],cond,ch,1:(1000*duration)] <- as.vector(rowMeans(temp))
@@
 meanwaveforms <- array(0,dim=c(14,64,14000))
+trialsincluded <- matrix(0,nrow=14,ncol=64)
     for (cond in 1:14){
@@
         meanwaveforms[cond,ch,] <- colMeans(temp[i,])
-      }
-      }
-    }
-
-     save(file = paste0('temp/VilidaiteProcessed/V',subjcounter,'processed.RData'), list = c('meanwaveforms','electrodes'))
-
-    for (block in 1:length(d)){file.remove(paste0(tempdir, d[block]))}
-
-  }
-}
-}
-}
-}
-
-if (runcode==1){
-#   d <- dir('temp/VilidaiteProcessed/')
-#   
-#   allwaves <- array(0,dim=c(length(d),14,64,14000))
-#   for (s in 1:length(d)){
-#     load(paste0('temp/VilidaiteProcessed/',d[s]))
-#     allwaves[s,,,] <- meanwaveforms
-#   }
-#   
-#   meanwaveforms <- array(0,dim=c(14,64,14000))
-#   alltarget <- matrix(0,nrow=14,ncol=64)
-#   allmask <- matrix(0,nrow=14,ncol=64)
-#     for (cond in 1:14){
-#       for (ch in 1:64){
-#         temp <- allwaves[,cond,ch,]
-#         allspec <- matrix(0,nrow=length(d),ncol=10000)
-#         for (subj in 1:length(d)){
-#           allspec[subj,] <- fft(temp[subj,2001:12000])/10000
-#         }
-#         targetresps <- allspec[,tindex]
-#         maskresps <- allspec[,mindex]
-#       if (sum(abs(targetresps))>0){  
-#       tempxy <- data.frame(Re(targetresps),Im(targetresps))
-#       D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
-#       i1 <- (D<3)
-#       tempxy <- data.frame(Re(maskresps),Im(maskresps))
-#       D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
-#       i2 <- (D<3)
-#       i <- which((i1*i2)>0)
-#         meanwaveforms[cond,ch,] <- colMeans(temp[i,])
-#       }
-#         spec <- fft(meanwaveforms[cond,ch,2001:12000])/10000
-#         alltarget[cond,ch] <- spec[tindex]
-#         allmask[cond,ch] <- spec[mindex]
-#       }
-#     }
-#   
-# }
-# 
-# targetchannels <- match(targetelectrodes, electrodes) - 2
-# 
-# elecave <- colMeans(meanwaveforms[6,targetchannels,])
-# binwidth <- 1000
-# f1 <- 7
-# tindex <- 1 + f1*(binwidth/1000)
-# fspec <- elecave*0
-# for (t in 1:(length(elecave)-binwidth)){
-#   temp <- elecave[t:(t+binwidth-1)]
-#   spec <- fft(temp)/binwidth
-#   fspec[t] <- abs(spec[tindex])
-# }
-# elecave <- colMeans(meanwaveforms[13,targetchannels,])
-# binwidth <- 1000
-# f1 <- 7
-# tindex <- 1 + f1*(binwidth/1000)
-# fspec2 <- elecave*0
-# for (t in 1:(length(elecave)-binwidth)){
-#   temp <- elecave[t:(t+binwidth-1)]
-#   spec <- fft(temp)/binwidth
-#   fspec2[t] <- abs(spec[tindex])
-# }
-# 
-# times <- -499:13500
-# plot(times,fspec,type='l',col=colpal[1])
-# lines(times,fspec2,col='green')
-#   d <- dir('temp/VilidaiteProcessed/')
-#   
-#   allwaves <- array(0,dim=c(length(d),14,64,14000))
-#   for (s in 1:length(d)){
-#     load(paste0('temp/VilidaiteProcessed/',d[s]))
-#     allwaves[s,,,] <- meanwaveforms
-#   }
-#   
-#   meanwaveforms <- array(0,dim=c(14,64,14000))
-#   alltarget <- matrix(0,nrow=14,ncol=64)
-#   allmask <- matrix(0,nrow=14,ncol=64)
-#     for (cond in 1:14){
-#       for (ch in 1:64){
-#         temp <- allwaves[,cond,ch,]
-#         allspec <- matrix(0,nrow=length(d),ncol=10000)
-#         for (subj in 1:length(d)){
-#           allspec[subj,] <- fft(temp[subj,2001:12000])/10000
-#         }
-#         targetresps <- allspec[,tindex]
-#         maskresps <- allspec[,mindex]
-#       if (sum(abs(targetresps))>0){  
-#       tempxy <- data.frame(Re(targetresps),Im(targetresps))
-#       D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
-#       i1 <- (D<3)
-#       tempxy <- data.frame(Re(maskresps),Im(maskresps))
-#       D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
-#       i2 <- (D<3)
-#       i <- which((i1*i2)>0)
-#         meanwaveforms[cond,ch,] <- colMeans(temp[i,])
-#       }
-#         spec <- fft(meanwaveforms[cond,ch,2001:12000])/10000
-#         alltarget[cond,ch] <- spec[tindex]
-#         allmask[cond,ch] <- spec[mindex]
-#       }
-#     }
-#   
-# }
-# 
-# targetchannels <- match(targetelectrodes, electrodes) - 2
-# 
-# elecave <- colMeans(meanwaveforms[6,targetchannels,])
-# binwidth <- 1000
-# f1 <- 7
-# tindex <- 1 + f1*(binwidth/1000)
-# fspec <- elecave*0
-# for (t in 1:(length(elecave)-binwidth)){
-#   temp <- elecave[t:(t+binwidth-1)]
-#   spec <- fft(temp)/binwidth
-#   fspec[t] <- abs(spec[tindex])
-# }
-# elecave <- colMeans(meanwaveforms[13,targetchannels,])
-# binwidth <- 1000
-# f1 <- 7
-# tindex <- 1 + f1*(binwidth/1000)
-# fspec2 <- elecave*0
-# for (t in 1:(length(elecave)-binwidth)){
-#   temp <- elecave[t:(t+binwidth-1)]
-#   spec <- fft(temp)/binwidth
-#   fspec2[t] <- abs(spec[tindex])
-# }
-# 
-# times <- -499:13500
-# plot(times,fspec,type='l',col=colpal[1])
-# lines(times,fspec2,col='green')
-
-# all electrodes, condition 6 @ 7Hz
-# all electrodes, condition 8 @ 5Hz
-# target electrodes, conditions 1-14 for CRF, 5&7Hz
-# target electrodes, full timecourse at 5 & 7Hz, conditions 6, 8, 13
-# allwaves dimensions: 67 x 14 x 64 x 14000
-
-# temp <- allwaves[,6,,2001:12000]
-# meantemp <- apply(allwaves,2:3,mean)
-
-# temp <- allwaves[,6,,2001:12000]
-# meantemp <- apply(allwaves,2:3,mean)
-
-f1 <- 7
-f2 <- 5
-    binwidth <- 1000
-    tindex <- 1 + f1*(binwidth/1000)
-    mindex <- 1 + f2*(binwidth/1000)
-    tindex2 <- 1 + 2*f1*(binwidth/1000)
-    mindex2 <- 1 + 2*f2*(binwidth/1000)
-
-condlist <- c(6,8,13)
+        trialsincluded[cond,ch] <- length(i)
+      }
+      }
+    }
+
+     save(file = paste0('temp/VilidaiteProcessed/V',subjcounter,'processed.RData'), list = c('meanwaveforms','electrodes','trialsincluded'))
+
+    for (block in 1:length(d)){file.remove(d[block])}
+
+  }
+}
+}
+}
+
+if (processdata>1){
 
 d <- dir(path = 'temp/VilidaiteProcessed', pattern = '*.RData', full.names=TRUE)
-EEGtimecourse5Hz <- array(0,dim=c(length(d),3,13000))
-EEGtimecourse7Hz <- array(0,dim=c(length(d),3,13000))
-EEGtimecourse10Hz <- array(0,dim=c(length(d),3,13000))
-EEGtimecourse14Hz <- array(0,dim=c(length(d),3,13000))
+EEGtimecourse <- array(0,dim=c(length(d),length(findex),3,13000))
+EEGspectra <- array(0,dim=c(length(d),3,20*10))
+EEGscalpresps <- array(0,dim=c(length(d),4,14,64))
+EEGallconds <- array(0,dim=c(length(d),4,14))
 
@@
   targetchannels <- match(targetelectrodes, electrodes) - 2
+
+  for (cond in 1:14){
+    temp <- colMeans(meanwaveforms[cond,targetchannels,],na.rm=TRUE)
+        nainds <- which(is.na(temp))   # find occasional NaN values in the waveform
+    temp[nainds] <- 0   # replace with zeros
+    spec <- fft(temp[2501:12500])/10000
+    EEGallconds[s,1,cond] <- spec[1+(10*targetF)]
+    EEGallconds[s,2,cond] <- spec[1+(10*maskF)]
+    EEGallconds[s,3,cond] <- spec[1+(2*10*targetF)]
+    EEGallconds[s,4,cond] <- spec[1+(2*10*maskF)]
+  }
   for (cond in 1:3){
@@
 
-fspec1 <- NULL
-fspec2 <- NULL
-fspec3 <- NULL
-fspec4 <- NULL
+    spec <- fft(temp[2501:12500])/10000
+    EEGspectra[s,cond,] <- spec[1:(20*10)]
+
 for (t in 1:(14000-binwidth)){
   spec <- fft(temp[t:(t+binwidth-1)])/binwidth
-  fspec1[t] <- spec[tindex]
-  fspec2[t] <- spec[mindex]
-  fspec3[t] <- spec[tindex2]
-  fspec4[t] <- spec[mindex2]
-
-}
-    EEGtimecourse5Hz[s,cond,] <- fspec1
-    EEGtimecourse7Hz[s,cond,] <- fspec2
-    EEGtimecourse10Hz[s,cond,] <- fspec3
-    EEGtimecourse14Hz[s,cond,] <- fspec4
-
-  }
-
-}
-
-save(file='temp/Pilotsummary.RData',list=c('EEGtimecourse5Hz','EEGtimecourse7Hz','EEGtimecourse10Hz','EEGtimecourse14Hz','electrodes'))
+  for (f in 1:length(findex)){
+  EEGtimecourse[s,f,cond,t] <- spec[findex[f]]
+  }
+}
+  }
+
+for (cond in 1:14){
+  for (ch in 1:64){
+     temp <- meanwaveforms[cond,ch,]
+    nainds <- which(is.na(temp))   # find occasional NaN values in the waveform
+    temp[nainds] <- 0   # replace with zeros
+   spec <- fft(temp[2501:12500])/10000
+   EEGscalpresps[s,1,cond,ch] <- spec[(targetF*10)+1]
+   EEGscalpresps[s,2,cond,ch] <- spec[(maskF*10)+1]
+   EEGscalpresps[s,3,cond,ch] <- spec[(2*targetF*10)+1]
+   EEGscalpresps[s,4,cond,ch] <- spec[(2*maskF*10)+1]
+  }
+}
+
+}
+
+save(file='temp/Pilotsummary.RData',list=c('EEGtimecourse','electrodes','EEGscalpresps','EEGspectra','EEGallconds'))
+}
+
+if (processdata>0){
 
 load('temp/Pilotsummary.RData')
-EEGmeantime5Hz <- matrix(0,nrow=3,ncol=13000)
-EEGmeantime7Hz <- matrix(0,nrow=3,ncol=13000)
-EEGmeantime10Hz <- matrix(0,nrow=3,ncol=13000)
-EEGmeantime14Hz <- matrix(0,nrow=3,ncol=13000)
-
+nsubjs <- dim(EEGtimecourse)[1]
+EEGmeantimes <- array(0,dim=c(length(findex),3,13000))
+EEGSEtimes <- array(0,dim=c(length(findex)+1,3,13000))
+EEGmaskindices <- array(0,dim=c(length(findex)+1,13000))
+EEGmaskSE <- array(0,dim=c(length(findex)+1,13000))
+EEGmeanscalp <- abs(apply(abs(EEGscalpresps),2:4,mean))
+EEGmeanspec <- abs(apply(abs(EEGspectra),2:3,mean))
+EEGmeanconds <- apply(abs(EEGallconds),2:3,mean)
+EEGcondsSE <- apply(abs(EEGallconds),2:3,sd)/sqrt(nsubjs)
+
+for (f in 1:length(findex)){
 for (cond in 1:3){
-EEGmeantime5Hz[cond,] <- apply(abs(EEGtimecourse5Hz[,cond,]),2,mean,na.rm=TRUE)
-EEGmeantime7Hz[cond,] <- apply(abs(EEGtimecourse7Hz[,cond,]),2,mean,na.rm=TRUE)
-EEGmeantime10Hz[cond,] <- apply(abs(EEGtimecourse10Hz[,cond,]),2,mean,na.rm=TRUE)
-EEGmeantime14Hz[cond,] <- apply(abs(EEGtimecourse14Hz[,cond,]),2,mean,na.rm=TRUE)
-}
-
-EEGmaskindex5 <- colMeans(20*log10(abs(EEGtimecourse5Hz[,1,])/abs(EEGtimecourse5Hz[,3,])))
-EEGmaskindex7 <- colMeans(20*log10(abs(EEGtimecourse7Hz[,2,])/abs(EEGtimecourse7Hz[,3,])))
-EEGmaskindex10 <- colMeans(20*log10(abs(EEGtimecourse10Hz[,1,])/abs(EEGtimecourse10Hz[,3,])))
-EEGmaskindex14 <- colMeans(20*log10(abs(EEGtimecourse14Hz[,2,])/abs(EEGtimecourse14Hz[,3,])))
-
-times <- -499:12500
-
-plot(times,EEGmeantime5Hz[1,],type='l',col=colpal[1],ylim=c(0,1))
-lines(times,EEGmeantime5Hz[2,],col='grey')
-lines(times,EEGmeantime5Hz[3,],col=colpal[2])
-spl5a <- smooth.spline(times,EEGmeantime5Hz[1,],df=20)
+EEGmeantimes[f,cond,] <- apply(abs(EEGtimecourse[,f,cond,]),2,mean,na.rm=TRUE)
+EEGSEtimes[f,cond,] <- apply(abs(EEGtimecourse[,f,cond,]),2,sd,na.rm=TRUE)/sqrt(nsubjs)
+}}
+
+EEGmaskindices[1,] <- colMeans(20*log10(abs(EEGtimecourse[,1,1,])/abs(EEGtimecourse[,1,3,])))
+EEGmaskindices[2,] <- colMeans(20*log10(abs(EEGtimecourse[,2,2,])/abs(EEGtimecourse[,2,3,])))
+EEGmaskindices[3,] <- colMeans(20*log10(abs(EEGtimecourse[,3,1,])/abs(EEGtimecourse[,3,3,])))
+EEGmaskindices[4,] <- colMeans(20*log10(abs(EEGtimecourse[,4,2,])/abs(EEGtimecourse[,4,3,])))
+
+meanindices <- (20*log10(abs(EEGtimecourse[,1,1,])/abs(EEGtimecourse[,1,3,])) + 20*log10(abs(EEGtimecourse[,2,2,])/abs(EEGtimecourse[,2,3,])) + 20*log10(abs(EEGtimecourse[,3,1,])/abs(EEGtimecourse[,3,3,])) + 20*log10(abs(EEGtimecourse[,4,2,])/abs(EEGtimecourse[,4,3,])))/4
+EEGmaskindices[5,] <- colMeans(meanindices)
+
+EEGmaskSE[1,] <- apply(20*log10(abs(EEGtimecourse[,1,1,])/abs(EEGtimecourse[,1,3,])),2,sd)/sqrt(nsubjs)
+EEGmaskSE[2,] <- apply(20*log10(abs(EEGtimecourse[,2,2,])/abs(EEGtimecourse[,2,3,])),2,sd)/sqrt(nsubjs)
+EEGmaskSE[3,] <- apply(20*log10(abs(EEGtimecourse[,3,1,])/abs(EEGtimecourse[,3,3,])),2,sd)/sqrt(nsubjs)
+EEGmaskSE[4,] <- apply(20*log10(abs(EEGtimecourse[,4,2,])/abs(EEGtimecourse[,4,3,])),2,sd)/sqrt(nsubjs)
+EEGmaskSE[5,] <- apply(meanindices,2,sd)/sqrt(nsubjs)
+
+times <- (-999:12000)/1000
+
+postscript("timecourse1.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,12,0,1)
+ticklocsx <- c(-1,seq(0,12,2))    # locations of tick marks on y axis
+ticklocsy <- seq(0,1,0.2)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = seq(0,12,2), side = 1, at=seq(0,12,2))
+mtext(text = ticklocsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,11,11,0),c(-0.035,-0.035,0.04,0.04),border=NA,col=rgb(0.5,0.5,0.5))
+
+if (plotsmoothed==0){
+polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[1,1,]+EEGSEtimes[1,1,],EEGmeantimes[1,1,13000:1]-EEGSEtimes[1,1,13000:1]),col=colpal[1],border=NA)
+polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[1,2,]+EEGSEtimes[1,2,],EEGmeantimes[1,2,13000:1]-EEGSEtimes[1,2,13000:1]),col='grey',border=NA)
+polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[1,3,]+EEGSEtimes[1,3,],EEGmeantimes[1,3,13000:1]-EEGSEtimes[1,3,13000:1]),col=colpal[2],border=NA)
+
+lines(times,EEGmeantimes[1,1,],col=colpal[1])
+lines(times,EEGmeantimes[1,2,],col='grey')
+lines(times,EEGmeantimes[1,3,],col=colpal[2])
+}
+if (plotsmoothed==1){
+
+spl5aU <- smooth.spline(times,EEGmeantimes[1,1,]+EEGSEtimes[1,1,],df=20)
+spl5aL <- smooth.spline(times,EEGmeantimes[1,1,]-EEGSEtimes[1,1,],df=20)
+polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[1],border=NA)
+
+spl5aU <- smooth.spline(times,EEGmeantimes[1,2,]+EEGSEtimes[1,2,],df=20)
+spl5aL <- smooth.spline(times,EEGmeantimes[1,2,]-EEGSEtimes[1,2,],df=20)
+polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col='grey',border=NA)
+
+spl5aU <- smooth.spline(times,EEGmeantimes[1,3,]+EEGSEtimes[1,3,],df=20)
+spl5aL <- smooth.spline(times,EEGmeantimes[1,3,]-EEGSEtimes[1,3,],df=20)
+polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[2],border=NA)
+
+spl5a <- smooth.spline(times,EEGmeantimes[1,1,],df=20)
 lines(spl5a$x,spl5a$y,col=colpal[1],lwd=2)
-spl5a <- smooth.spline(times,EEGmeantime5Hz[2,],df=20)
+spl5a <- smooth.spline(times,EEGmeantimes[1,2,],df=20)
 lines(spl5a$x,spl5a$y,col='grey',lwd=2)
-spl5a <- smooth.spline(times,EEGmeantime5Hz[3,],df=20)
+spl5a <- smooth.spline(times,EEGmeantimes[1,3,],df=20)
 lines(spl5a$x,spl5a$y,col=colpal[2],lwd=2)
-
-plot(times,EEGmeantime7Hz[2,],type='l',col=colpal[1],ylim=c(0,1))
-lines(times,EEGmeantime7Hz[1,],col='grey')
-lines(times,EEGmeantime7Hz[3,],col=colpal[2])
-spl5a <- smooth.spline(times,EEGmeantime7Hz[2,],df=20)
+}
+text(10,0.95,'7Hz',cex=2)
+
+dev.off()
+
+postscript("timecourse2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = seq(0,12,2), side = 1, at=seq(0,12,2))
+mtext(text = ticklocsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,11,11,0),c(-0.035,-0.035,0.04,0.04),border=NA,col=rgb(0.5,0.5,0.5))
+
+if (plotsmoothed==0){
+polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[2,2,]+EEGSEtimes[2,2,],EEGmeantimes[2,2,13000:1]-EEGSEtimes[2,2,13000:1]),col=colpal[1],border=NA)
+polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[2,1,]+EEGSEtimes[2,1,],EEGmeantimes[2,1,13000:1]-EEGSEtimes[2,1,13000:1]),col='grey',border=NA)
+polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[2,3,]+EEGSEtimes[2,3,],EEGmeantimes[2,3,13000:1]-EEGSEtimes[2,3,13000:1]),col=colpal[2],border=NA)
+
+lines(times,EEGmeantimes[2,2,],col=colpal[1])
+lines(times,EEGmeantimes[2,1,],col='grey')
+lines(times,EEGmeantimes[2,3,],col=colpal[2])
+}
+if (plotsmoothed==1){
+
+spl5aU <- smooth.spline(times,EEGmeantimes[2,2,]+EEGSEtimes[2,2,],df=20)
+spl5aL <- smooth.spline(times,EEGmeantimes[2,2,]-EEGSEtimes[2,2,],df=20)
+polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[1],border=NA)
+
+spl5aU <- smooth.spline(times,EEGmeantimes[2,1,]+EEGSEtimes[2,1,],df=20)
+spl5aL <- smooth.spline(times,EEGmeantimes[2,1,]-EEGSEtimes[2,1,],df=20)
+polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col='grey',border=NA)
+
+spl5aU <- smooth.spline(times,EEGmeantimes[2,3,]+EEGSEtimes[2,3,],df=20)
+spl5aL <- smooth.spline(times,EEGmeantimes[2,3,]-EEGSEtimes[2,3,],df=20)
+polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[2],border=NA)
+
+spl5a <- smooth.spline(times,EEGmeantimes[2,2,],df=20)
 lines(spl5a$x,spl5a$y,col=colpal[1],lwd=2)
-spl5a <- smooth.spline(times,EEGmeantime7Hz[1,],df=20)
+spl5a <- smooth.spline(times,EEGmeantimes[2,1,],df=20)
 lines(spl5a$x,spl5a$y,col='grey',lwd=2)
-spl5a <- smooth.spline(times,EEGmeantime7Hz[3,],df=20)
+spl5a <- smooth.spline(times,EEGmeantimes[2,3,],df=20)
 lines(spl5a$x,spl5a$y,col=colpal[2],lwd=2)
-
-plot(times,EEGmaskindex5,type='l',col=colpal[1],ylim=c(0,6))
-lines(times,EEGmaskindex7,col=colpal[2])
-lines(times,EEGmaskindex10,col=colpal[4])
-lines(times,EEGmaskindex14,col=colpal[5])
-lines(times,(EEGmaskindex5+EEGmaskindex7+EEGmaskindex10+EEGmaskindex14)/4,col=colpal[3])
-
-spl5a <- smooth.spline(times,EEGmaskindex5,df=20)
+}
+text(10,0.95,'5Hz',cex=2)
+
+dev.off()
+
+postscript("timecourse3.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = seq(0,12,2), side = 1, at=seq(0,12,2))
+mtext(text = ticklocsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,11,11,0),c(-0.035,-0.035,0.04,0.04),border=NA,col=rgb(0.5,0.5,0.5))
+
+if (plotsmoothed==0){
+polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[3,1,]+EEGSEtimes[3,1,],EEGmeantimes[3,1,13000:1]-EEGSEtimes[3,1,13000:1]),col=colpal[1],border=NA)
+polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[3,2,]+EEGSEtimes[3,2,],EEGmeantimes[3,2,13000:1]-EEGSEtimes[3,2,13000:1]),col='grey',border=NA)
+polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[3,3,]+EEGSEtimes[3,3,],EEGmeantimes[3,3,13000:1]-EEGSEtimes[3,3,13000:1]),col=colpal[2],border=NA)
+
+lines(times,EEGmeantimes[3,1,],col=colpal[1])
+lines(times,EEGmeantimes[3,2,],col='grey')
+lines(times,EEGmeantimes[3,3,],col=colpal[2])
+}
+if (plotsmoothed==1){
+
+spl5aU <- smooth.spline(times,EEGmeantimes[3,1,]+EEGSEtimes[3,1,],df=20)
+spl5aL <- smooth.spline(times,EEGmeantimes[3,1,]-EEGSEtimes[3,1,],df=20)
+polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[1],border=NA)
+
+spl5aU <- smooth.spline(times,EEGmeantimes[3,2,]+EEGSEtimes[3,2,],df=20)
+spl5aL <- smooth.spline(times,EEGmeantimes[3,2,]-EEGSEtimes[3,2,],df=20)
+polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col='grey',border=NA)
+
+spl5aU <- smooth.spline(times,EEGmeantimes[3,3,]+EEGSEtimes[3,3,],df=20)
+spl5aL <- smooth.spline(times,EEGmeantimes[3,3,]-EEGSEtimes[3,3,],df=20)
+polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[2],border=NA)
+
+spl5a <- smooth.spline(times,EEGmeantimes[3,1,],df=20)
 lines(spl5a$x,spl5a$y,col=colpal[1],lwd=2)
-spl5a <- smooth.spline(times,EEGmaskindex7,df=20)
+spl5a <- smooth.spline(times,EEGmeantimes[3,2,],df=20)
+lines(spl5a$x,spl5a$y,col='grey',lwd=2)
+spl5a <- smooth.spline(times,EEGmeantimes[3,3,],df=20)
 lines(spl5a$x,spl5a$y,col=colpal[2],lwd=2)
-spl5a <- smooth.spline(times,(EEGmaskindex5+EEGmaskindex7+EEGmaskindex10+EEGmaskindex14)/4,df=20)
-lines(spl5a$x,spl5a$y,col=colpal[3],lwd=4)
-
-# f1 <- 7
-# f2 <- 5
-#     binwidth <- 1000
-#     tindex <- 1 + f1*(binwidth/1000)
-#     mindex <- 1 + f2*(binwidth/1000)
-# condlist <- c(6,8,13)
-# 
-# d <- dir('temp/VilidaiteProcessed/')
-# all7Hz <- array(0,dim=c(length(d),14,64))
-# all5Hz <- array(0,dim=c(length(d),14,64))
-# timecourse7Hz <- array(0,dim=c(length(d),3,14000))
-# timecourse5Hz <- array(0,dim=c(length(d),3,14000))
-# 
-#   for (s in 1:length(d)){
-# 
-#     load(paste0('temp/VilidaiteProcessed/',d[s]))
-#     
-#     targetchannels <- match(targetelectrodes, electrodes) - 2
-# 
-#     for (cond in 1:14){
-#       for (ch in 1:64){
-#         temp <- meanwaveforms[cond,ch,2001:12000]
-#         spec <- fft(temp)/length(temp)
-#         all7Hz[s,cond,ch] <- spec[7*10+1]
-#         all5Hz[s,cond,ch] <- spec[5*10+1]
+}
+text(10,0.95,'14Hz',cex=2)
+
+dev.off()
+
+postscript("timecourse4.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = seq(0,12,2), side = 1, at=seq(0,12,2))
+mtext(text = ticklocsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,11,11,0),c(-0.035,-0.035,0.04,0.04),border=NA,col=rgb(0.5,0.5,0.5))
+
+if (plotsmoothed==0){
+polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[4,2,]+EEGSEtimes[4,2,],EEGmeantimes[4,2,13000:1]-EEGSEtimes[4,2,13000:1]),col=colpal[1],border=NA)
+polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[4,1,]+EEGSEtimes[4,1,],EEGmeantimes[4,1,13000:1]-EEGSEtimes[4,1,13000:1]),col='grey',border=NA)
+polygon(times[c(1:13000,13000:1)],c(EEGmeantimes[4,3,]+EEGSEtimes[4,3,],EEGmeantimes[4,3,13000:1]-EEGSEtimes[4,3,13000:1]),col=colpal[2],border=NA)
+
+lines(times,EEGmeantimes[4,2,],col=colpal[1])
+lines(times,EEGmeantimes[4,1,],col='grey')
+lines(times,EEGmeantimes[4,3,],col=colpal[2])
+}
+if (plotsmoothed==1){
+
+spl5aU <- smooth.spline(times,EEGmeantimes[4,2,]+EEGSEtimes[4,2,],df=20)
+spl5aL <- smooth.spline(times,EEGmeantimes[4,2,]-EEGSEtimes[4,2,],df=20)
+polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[1],border=NA)
+
+spl5aU <- smooth.spline(times,EEGmeantimes[4,1,]+EEGSEtimes[4,1,],df=20)
+spl5aL <- smooth.spline(times,EEGmeantimes[4,1,]-EEGSEtimes[4,1,],df=20)
+polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col='grey',border=NA)
+
+spl5aU <- smooth.spline(times,EEGmeantimes[4,3,]+EEGSEtimes[4,3,],df=20)
+spl5aL <- smooth.spline(times,EEGmeantimes[4,3,]-EEGSEtimes[4,3,],df=20)
+polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[2],border=NA)
+
+spl5a <- smooth.spline(times,EEGmeantimes[4,2,],df=20)
+lines(spl5a$x,spl5a$y,col=colpal[1],lwd=2)
+spl5a <- smooth.spline(times,EEGmeantimes[4,1,],df=20)
+lines(spl5a$x,spl5a$y,col='grey',lwd=2)
+spl5a <- smooth.spline(times,EEGmeantimes[4,3,],df=20)
+lines(spl5a$x,spl5a$y,col=colpal[2],lwd=2)
+}
+text(10,0.95,'10Hz',cex=2)
+
+dev.off()
+
+postscript("suppression.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,12,-3,6)
+ticklocsx <- c(-1,seq(0,12,2))    # locations of tick marks on y axis
+ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = seq(0,12,2), side = 1, at=seq(0,12,2))
+mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,11,11,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))
+
+lines(c(-1,12),c(0,0),lty=2)
+
+if (plotsmoothed==0){
+
+# for (f in 1:4){
+# polygon(times[c(1:13000,13000:1)],c(EEGmaskindices[f,]+EEGmaskSE[f,],EEGmaskindices[f,13000:1]-EEGmaskSE[f,13000:1]),col=colpal[f+1],border=NA)
 # }
+  polygon(times[c(1:13000,13000:1)],c(EEGmaskindices[5,]+EEGmaskSE[5,],EEGmaskindices[5,13000:1]-EEGmaskSE[5,13000:1]),col=colpal[1],border=NA)
+
+for (f in 1:4){lines(times,EEGmaskindices[f,],col=colpal[f+1])}
+lines(times,EEGmaskindices[5,],col=colpal[1],lwd=4)
+}
+
+if (plotsmoothed==1){
+# for (f in 1:4){  
+# spl5aU <- smooth.spline(times,EEGmaskindices[f,]+EEGmaskSE[f,],df=20)
+# spl5aL <- smooth.spline(times,EEGmaskindices[f,]-EEGmaskSE[f,],df=20)
+# polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[f+1],border=NA)
 # }
-#     for (cond in 1:3){
-#     temp <- colMeans(meanwaveforms[condlist[cond],targetchannels,])
-# 
-# fspec1 <- temp*0
-# fspec2 <- temp*0
-# for (t in 1:(length(temp)-binwidth)){
-#   spec <- fft(temp[t:(t+binwidth-1)])/binwidth
-#   fspec1[t] <- spec[tindex]
-#   fspec2[t] <- spec[mindex]
-# }
-#     timecourse7Hz[s,cond,] <- fspec1
-#     timecourse5Hz[s,cond,] <- fspec2
-#     
-#     }
-#     
-#   }
-# 
-# mean7 <- apply(all7Hz[,,targetchannels],1:2,mean)
-# mean5 <- apply(all5Hz[,,targetchannels],1:2,mean)
-# inclusionmatrix7 <- matrix(0,nrow=length(d),ncol=length(condlist))
-# inclusionmatrix5 <- matrix(0,nrow=length(d),ncol=length(condlist))
-# for (cond in 1:3){
-#   temp <- mean7[,condlist[cond]]
-#         tempxy <- data.frame(Re(temp),Im(temp))
-#       D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
-#       inclusionmatrix7[,cond] <- (D<3)
-#    temp <- mean5[,condlist[cond]]
-#         tempxy <- data.frame(Re(temp),Im(temp))
-#       D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
-#       inclusionmatrix5[,cond] <- (D<3)
-# }
-# 
-# meantime5Hz <- matrix(0,nrow=length(condlist),ncol=14000) 
-# meantime7Hz <- matrix(0,nrow=length(condlist),ncol=14000) 
-# for (cond in 1:3){
-# meantime7Hz[cond,] <- abs(apply(abs(timecourse7Hz[which(inclusionmatrix7[,cond]>0),cond,]),2,mean))
-# meantime5Hz[cond,] <- abs(apply(abs(timecourse5Hz[which(inclusionmatrix5[,cond]>0),cond,]),2,mean))
-# }
-# 
-# plot(-499:13500,meantime5Hz[2,],type='l',col=colpal[1])
-# lines(-499:13500,meantime5Hz[1,],col='grey')
-# lines(-499:13500,meantime5Hz[3,],col=colpal[2])
-# 
-# plot(-499:13500,meantime7Hz[1,],type='l',col=colpal[1])
-# lines(-499:13500,meantime7Hz[2,],col='grey')
-# lines(-499:13500,meantime7Hz[3,],col=colpal[2])
-# 
-# plot(-499:13500,meantime7Hz[1,]/meantime7Hz[3,],type='l',col=colpal[1])
-# lines(-499:13500,meantime5Hz[2,]/meantime5Hz[3,],col=colpal[2])
+  spl5aU <- smooth.spline(times,EEGmaskindices[5,]+EEGmaskSE[5,],df=20)
+spl5aL <- smooth.spline(times,EEGmaskindices[5,]-EEGmaskSE[5,],df=20)
+polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[1],border=NA)
+
+for (f in 1:4){
+spl5a <- smooth.spline(times,EEGmaskindices[f,],df=20)
+lines(spl5a$x,spl5a$y,col=colpal[f+1],lwd=2)
+}
+spl5a <- smooth.spline(times,EEGmaskindices[5,],df=20)
+lines(spl5a$x,spl5a$y,col=colpal[1],lwd=6)
+}
+legend(1,0,c('7Hz','5Hz'),lwd=4,col=colpal[c(2,3)],bty='n')
+legend(5,0,c('14Hz','10Hz'),lwd=4,col=colpal[c(4,5)],bty='n')
+legend(3,-1.4,c('Mean'),lwd=6,col=colpal[1],bty='n')
+
+dev.off()
+
+freqlist <- seq(0,19.9,1/10)
+
+postscript("spectrum.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 10)
+
+plotlims <- c(1,20,0,3)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+ticklocsx <- seq(2,20,2)    # locations of tick marks on x axis
+ticklocsy <- c(0,0.4,0.8,1,2,3)    # locations of tick marks on y axis
+ticklabelsx <- seq(2,20,2)        # set labels for x ticks
+ticklabelsy <- c(0,0.2,0.4,'','','')    # set labels for y ticks
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+lines(c(0,20),c(0,0),lty=3)
+lines(c(0,20),c(1,1),lty=3)
+lines(c(0,20),c(2,2),lty=3)
+
+polygon(c(freqlist[11],freqlist[11:200],19.9),c(0,2*EEGmeanspec[1,11:200],0)+2,border=NA,col=colpal[1])
+polygon(c(freqlist[11],freqlist[11:200],19.9),c(0,2*EEGmeanspec[2,11:200],0)+1,border=NA,col=colpal[2])
+polygon(c(freqlist[11],freqlist[11:200],19.9),c(0,2*EEGmeanspec[3,11:200],0),border=NA,col=colpal[3])
+
+lines(freqlist[11:200],2*EEGmeanspec[1,11:200]+2,lwd=2,col='black')
+lines(freqlist[11:200],2*EEGmeanspec[2,11:200]+1,lwd=2,col='black')
+lines(freqlist[11:200],2*EEGmeanspec[3,11:200],lwd=2,col='black')
+
+text(20,2.5,'7Hz target',pos=2,cex=1.5)
+text(20,1.5,'5Hz mask',pos=2,cex=1.5)
+text(20,0.5,'Plaid',pos=2,cex=1.5)
+
+dev.off()
+
+postscript("CRFs.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 9)
+
+contrastsdB <- seq(0,36,6)
+
+plotlims <- c(0,78,0,0.8)
+ticklocsx <- seq(0,36,6)    # locations of tick marks on y axis
+ticklocsy <- seq(0,0.8,0.2)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = c(0,2,4,8,16,32,64), side = 1, at=ticklocsx)
+mtext(text = ticklocsy, side = 2, at=ticklocsy, line=0.2, las=1)
+axis(1, at=ticklocsx+42, tck=0.01, lab=F, lwd=2)
+mtext(text = c(0,2,4,8,16,32,64), side = 1, at=ticklocsx+42)
+title(xlab="Target contrast (%)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+arrows(contrastsdB,EEGmeanconds[1,1:7],contrastsdB,EEGmeanconds[1,1:7]+EEGcondsSE[1,1:7],lwd=2,angle=90,length=0.015,col=colpal[1])
+arrows(contrastsdB,EEGmeanconds[1,1:7],contrastsdB,EEGmeanconds[1,1:7]-EEGcondsSE[1,1:7],lwd=2,angle=90,length=0.015,col=colpal[1])
+
+arrows(contrastsdB,EEGmeanconds[1,8:14],contrastsdB,EEGmeanconds[1,8:14]+EEGcondsSE[1,8:14],lwd=2,angle=90,length=0.015,col=colpal[2])
+arrows(contrastsdB,EEGmeanconds[1,8:14],contrastsdB,EEGmeanconds[1,8:14]-EEGcondsSE[1,8:14],lwd=2,angle=90,length=0.015,col=colpal[2])
+
+lines(contrastsdB,EEGmeanconds[1,1:7],lwd=2,col=colpal[1])
+lines(contrastsdB,EEGmeanconds[1,8:14],lwd=2,col=colpal[2])
+
+points(contrastsdB,EEGmeanconds[1,1:7],pch=16,cex=1.5,col=colpal[1])
+points(contrastsdB,EEGmeanconds[1,8:14],pch=15,cex=1.5,col=colpal[2])
+
+points(contrastsdB[6],EEGmeanconds[1,6],pch=16,cex=2.5,col=colpal[1])
+points(contrastsdB[6],EEGmeanconds[1,13],pch=15,cex=2.5,col=colpal[2])
+
+contrastsdB <- contrastsdB+42
+
+arrows(contrastsdB,EEGmeanconds[2,1:7],contrastsdB,EEGmeanconds[2,1:7]+EEGcondsSE[2,1:7],lwd=2,angle=90,length=0.015,col=colpal[1])
+arrows(contrastsdB,EEGmeanconds[2,1:7],contrastsdB,EEGmeanconds[2,1:7]-EEGcondsSE[2,1:7],lwd=2,angle=90,length=0.015,col=colpal[1])
+
+arrows(contrastsdB,EEGmeanconds[2,8:14],contrastsdB,EEGmeanconds[2,8:14]+EEGcondsSE[2,8:14],lwd=2,angle=90,length=0.015,col=colpal[2])
+arrows(contrastsdB,EEGmeanconds[2,8:14],contrastsdB,EEGmeanconds[2,8:14]-EEGcondsSE[2,8:14],lwd=2,angle=90,length=0.015,col=colpal[2])
+
+lines(contrastsdB,EEGmeanconds[2,1:7],lwd=2,col=colpal[1])
+lines(contrastsdB,EEGmeanconds[2,8:14],lwd=2,col=colpal[2])
+
+points(contrastsdB,EEGmeanconds[2,1:7],pch=16,cex=1.5,col=colpal[1])
+points(contrastsdB,EEGmeanconds[2,8:14],pch=15,cex=1.5,col=colpal[2])
+
+points(contrastsdB[1],EEGmeanconds[2,8],pch=15,cex=2.5,col=colpal[2])
+points(contrastsdB[6],EEGmeanconds[2,13],pch=15,cex=2.5,col=colpal[2])
+
+text(18,0.78,'7Hz response',cex=2,adj=0.5)
+text(42+18,0.78,'5Hz response',cex=2,adj=0.5)
+
+legend(65,0.7,c('Target','Target+mask'),pch=16:15,col=colpal[1:2],bty='n')
+
+dev.off()
+
+xpos <- 1:64
+ypos <- 1:64
+montageE <- toupper(as.character(hdata$Electrode))
+for (ch in 1:64){
+  i <- match(toupper(electrodes[ch+2]),montageE)
+  xpos[ch] <- hdata$X_position[i]
+  ypos[ch] <- hdata$Y_position[i]
+}
+
+for (f in 1:2){
+rmax <- 0.55   #specify a maximum boundary for the grid
+gridRes <- 100 #specify the interpolation grid resolution
+
+datatoplot <- abs(EEGmeanscalp[f,condlist[f],])
+datatoplot[which(is.na(datatoplot))] <- 0
+datatoplot[which(datatoplot<0)] <- 0
+datatoplot[which(datatoplot>30)] <- 0
+
+testDat<- data.frame(x = xpos,
+                     y = -ypos,
+                     z = datatoplot)
+
+#Create the interpolation grid
+xo <- seq(min(-rmax, testDat$x), max(rmax, testDat$x), length = gridRes)
+yo <- seq(max(rmax, testDat$y), min(-rmax, testDat$y), length = gridRes)
+
+interpV4 <- v4Interp(testDat, xo, yo, rmax, gridRes)
+
+zo2 <- as.matrix(interpV4[,2:ncol(interpV4)])
+
+xo2 <- matrix(rep(xo,length(yo)),nrow = length(xo),ncol = length(yo))
+yo2 <- t(matrix(rep(yo,length(xo)),nrow = length(yo),ncol = length(xo)))
+outsidecircle <- sqrt(xo2^2 + yo2^2) > 0.51
+zo2[outsidecircle] <- 0
+
+ramp2 <- colorRamp(c("white",colpal[2]))  
+colmatrix2 <- rgb(ramp2(seq(0, 1, length = 101)), max = 255)
+
+tiff(paste0('headplot',f,'.tif'), height = 600, width = 600, units="px", bg="white")
+
+plotlims <- c(-rmax,rmax,-rmax,rmax)  
+par(pty="s")  # make axis square
+plot(x=NULL,y=NULL,ann=FALSE, axes=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4]) 
+image(xo,xo,zo2,col=colmatrix2,zlim=c(0,0.7),add=TRUE,useRaster=FALSE)
+maskx <- c(hdata$OutlineX[1:51]*2.2,hdata$OutlineX[51:1])
+masky <- c(hdata$OutlineY[1:51]*2.2,hdata$OutlineY[51:1])
+polygon(maskx,masky,border=NA,col="white")
+maskx <- c(hdata$OutlineX[51:101]*2.2,hdata$OutlineX[101:51])
+masky <- c(hdata$OutlineY[51:101]*2.2,hdata$OutlineY[101:51])
+polygon(maskx,masky,border=NA,col="white")
+
+blackelectrodes <- match('OZ',toupper(as.character(electrodes[3:66])))
+points(xpos[blackelectrodes],ypos[blackelectrodes],pch=16,col="black",cex=1.6)
+blackelectrodes <- match('POZ',toupper(as.character(electrodes[3:66])))
+points(xpos[blackelectrodes],ypos[blackelectrodes],pch=16,col="black",cex=1.6)
+blackelectrodes <- match('O1',toupper(as.character(electrodes[3:66])))
+points(xpos[blackelectrodes],ypos[blackelectrodes],pch=16,col="black",cex=1.6)
+blackelectrodes <- match('O2',toupper(as.character(electrodes[3:66])))
+points(xpos[blackelectrodes],ypos[blackelectrodes],pch=16,col="black",cex=1.6)
+
+lines(hdata$OutlineX,hdata$OutlineY,col="black",lwd=2)
+lines(hdata$NoseX,hdata$NoseY,col="black",lwd=2)
+lines(hdata$LearX,hdata$LearY,col="black",lwd=2)
+lines(hdata$RearX,hdata$RearY,col="black",lwd=2)
+
+dev.off()
+}
+
+  e1 <- readTIFF('headplot1.tif')
+  e2 <- readTIFF('headplot2.tif')
+
+  PostScriptTrace(paste('CRFs.ps',sep=''))
+  e3 <- readPicture('CRFs.ps.xml')
+  PostScriptTrace(paste('suppression.ps',sep=''))
+  e4 <- readPicture('suppression.ps.xml')
+  for (n in 1:length(e4@paths)){
+    temp <- class(e4@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e4@paths[n]$path@rgb))<765){e4@paths[n]$path@rgb <- addalpha(e4@paths[n]$path@rgb,alpha=0.2)}}}
+
+  PostScriptTrace(paste('spectrum.ps',sep=''))
+  e5 <- readPicture('spectrum.ps.xml')
+  for (n in 1:length(e5@paths)){
+    temp <- class(e5@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e5@paths[n]$path@rgb))<765){e5@paths[n]$path@rgb <- addalpha(e5@paths[n]$path@rgb,alpha=0.2)}}}
+
+   PostScriptTrace(paste('timecourse1.ps',sep=''))
+  e6 <- readPicture('timecourse1.ps.xml')
+  for (n in 1:length(e6@paths)){
+    temp <- class(e6@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e6@paths[n]$path@rgb))<765){e6@paths[n]$path@rgb <- addalpha(e6@paths[n]$path@rgb,alpha=0.2)}}}
+
+   PostScriptTrace(paste('timecourse2.ps',sep=''))
+  e7 <- readPicture('timecourse2.ps.xml')
+  for (n in 1:length(e7@paths)){
+    temp <- class(e7@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e7@paths[n]$path@rgb))<765){e7@paths[n]$path@rgb <- addalpha(e7@paths[n]$path@rgb,alpha=0.2)}}}
+
+     PostScriptTrace(paste('timecourse3.ps',sep=''))
+  e8 <- readPicture('timecourse3.ps.xml')
+  for (n in 1:length(e8@paths)){
+    temp <- class(e8@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e8@paths[n]$path@rgb))<765){e8@paths[n]$path@rgb <- addalpha(e8@paths[n]$path@rgb,alpha=0.2)}}}
+
+     PostScriptTrace(paste('timecourse4.ps',sep=''))
+  e9 <- readPicture('timecourse4.ps.xml')
+  for (n in 1:length(e9@paths)){
+    temp <- class(e9@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e9@paths[n]$path@rgb))<765){e9@paths[n]$path@rgb <- addalpha(e9@paths[n]$path@rgb,alpha=0.2)}}}
+
+  pdf('temp/figures/Fig2.pdf', bg="transparent", height = 6, width = 16)
+  par(mar=c(0.1,0.1,0.1,0.1))
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
+
+  aspratio <- 6/16  # this is the aspect ratio of the output pdf
+  imwidth <- 0.25
+  xstart <- 0.02
+  ystart <- 0.58
+  rasterImage(e1,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth)
+  xstart <- 0.22
+  ystart <- 0.58
+  rasterImage(e2,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth)
+
+  grid.picture(e3,x=0.225,y=0.7,width=0.4,height=1)
+  grid.picture(e5,x=0.225,y=0.25,width=0.4,height=1)
+
+  grid.picture(e6,x=0.5,y=0.85,width=0.1,height=1)
+  grid.picture(e7,x=0.5,y=0.625,width=0.1,height=1)
+  grid.picture(e8,x=0.5,y=0.375,width=0.1,height=1)
+  grid.picture(e9,x=0.5,y=0.15,width=0.1,height=1)
+  grid.picture(e4,x=0.77,y=0.5,width=0.45,height=1)
+
+  text(-0.02,0.98,'(a)',pos=4,cex=2)
+  text(-0.02,0.45,'(b)',pos=4,cex=2)
+  text(0.41,0.98,'(c)',pos=4,cex=2)
+  text(0.57,0.98,'(d)',pos=4,cex=2)
+
+  dev.off()
+
+  file.remove(c('headplot1.tif','headplot2.tif','spectrum.ps','timecourse1.ps','timecourse2.ps','timecourse3.ps','timecourse4.ps','suppression.ps','CRFs.ps'))
+  file.remove(c('spectrum.ps.xml','timecourse1.ps.xml','timecourse2.ps.xml','timecourse3.ps.xml','timecourse4.ps.xml','suppression.ps.xml','CRFs.ps.xml'))
 
@@
 ```
+
+```{r Pilotdata, fig.cap="Summary of pilot analysis of data from Vilidiate et al.
+(2018).
+Panel (a) shows contrast response functions at the target frequency (7Hz, left) and the mask frequency (5Hz, right).
+Insets show the distribution of activity across the scalp, with points marking electrodes Oz, POz, O1 and O2.
+Panel (b) shows Fourier spectra for the single component stimuli and their combination (plaid).
+Note the strong second harmonic components at 14Hz and 10Hz.
+Panel (c) shows timecourses of responses to a single stimulus (black) and the plaid stimulus (blue), compared to baseline (grey).
+Panel (d) shows the timecourse of suppression at each frequency (7Hz, 5Hz, 14Hz, 10Hz) and their average (black curve).
+In panels (c,d), shaded regions indicate ±1SE, and grey rectangles indicate the timing of stimulus presentation.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('temp/figures/Fig2.pdf')
+
+```
+
 Our initial reanalysis was promising, however the data were noisy despite the large sample size, because each participant contributed only 8 trials to each condition.
@@
 
- if (processraw==1){
+ if (processdata>2){
 
@@
 
+ }
+if (processdata>1){    
 d <- dir(path = 'temp/EEGprocessed', pattern = '*.RData', full.names=TRUE)
@@
 
-if (runcode==1){
+if (processdata>0){
 load('temp/EEGsummary.RData')
@@
 
-if (processraw==1){
+if (processdata>1){
 
@@
 save(file='temp/MEGsummary.RData',list=c('allspec','MEGtimecourse5Hz','MEGtimecourse7Hz','allRnos'))
-
+}
+
+if (processdata>0){
 load('temp/MEGsummary.RData')

### 2022-06-14 manuscript.Rmd
Added AQ scoring

@@
 
-processdata <- 0  # this flag determines the amount of processing, with 4 levels:
+processdata <- 1  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all scripts
@@
 
+scoreAQ <- function(qdata){
+# score the AQ questionnaire
+# input is a row from a spreadsheet indicating responses to 50 questions
+AQanswers <- toupper(c('(1) Definitely agree','(2) Slightly agree', '(3) Slightly disagree', '(4) Definitely disagree'))
+reverseitems <- rep(0,50)
+ # reverse scored questionnaire items
+reverseitems[c(3,8,10,11,14,15,17,24,25,27,28,29,30,31,32,34,36,37,38,40,44,47,48,49,50)] <- 1
+
+  thisAQ <- 0
+  nansweredAQ <- 0
+  for (q in 1:50){
+    response <- which(AQanswers==toupper(as.character(qdata[1,q])))
+    if (length(response)>0){
+      nansweredAQ <- nansweredAQ + 1
+      if (reverseitems[q]==0){response <- 5 - response}
+      if (response>2){thisAQ <- thisAQ + 1}
+    }}
+thisAQ <- round(50*thisAQ/nansweredAQ)    
+return(thisAQ)}
+
 knitr::opts_chunk$set(echo = TRUE)
-colpal <- c('#000000','#8783CF','#FE5000','#004731','#603FB3')
+colpal <- c('#000000','#8783CF','#FE5000','#228B22','#8B8000')
 
@@
 
-plotlims <- c(1,20,0,3)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
-ticklocsx <- seq(2,20,2)    # locations of tick marks on x axis
+plotlims <- c(0,20,0,3)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+ticklocsx <- seq(0,20,5)    # locations of tick marks on x axis
 ticklocsy <- c(0,0.4,0.8,1,2,3)    # locations of tick marks on y axis
-ticklabelsx <- seq(2,20,2)        # set labels for x ticks
+ticklabelsx <- seq(0,20,5)        # set labels for x ticks
 ticklabelsy <- c(0,0.2,0.4,'','','')    # set labels for y ticks
@@
 allheads7 <- array(0,dim=c(length(d),4,64))
+allAQ <- NULL
 for (s in 1:length(d)){
@@
 
-}
-
-save(file='temp/EEGsummary.RData',list=c('allheads5','allheads7','allspec','allwaves','EEGtimecourse5Hz','EEGtimecourse7Hz','electrodes'))
+allAQ[s] <- scoreAQ(qdatasubj[1,5:54])
+
+}
+
+save(file='temp/EEGsummary.RData',list=c('allheads5','allheads7','allspec','allwaves','EEGtimecourse5Hz','EEGtimecourse7Hz','electrodes','allAQ'))
  }
@@
 
-meanspec[cond,] <- abs(colMeans(allspec[which(isincluded[cond,]==1),cond,],na.rm=TRUE))
+meanspec[cond,] <- colMeans(abs(allspec[which(isincluded[cond,]==1),cond,]),na.rm=TRUE)
 meanwave[cond,] <- colMeans(allwaves[which(isincluded[cond,]==1),cond,],na.rm=TRUE)
-meanhead5[cond,] <- abs(colMeans(allheads5[which(isincluded[cond,]==1),cond,],na.rm=TRUE))
-meanhead7[cond,] <- abs(colMeans(allheads7[which(isincluded[cond,]==1),cond,],na.rm=TRUE))
+meanhead5[cond,] <- abs(colMeans(abs(allheads5[which(isincluded[cond,]==1),cond,]),na.rm=TRUE))
+meanhead7[cond,] <- abs(colMeans(abs(allheads7[which(isincluded[cond,]==1),cond,]),na.rm=TRUE))
 }
@@
 
-polygon(c(1/6,freqlist,20),c(0,2*meanspec[1,],0)+3,border=NA,col=colpal[1])
-polygon(c(1/6,freqlist,20),c(0,2*meanspec[2,],0)+2,border=NA,col=colpal[1])
-polygon(c(1/6,freqlist,20),c(0,2*meanspec[3,],0)+1,border=NA,col=colpal[2])
-polygon(c(1/6,freqlist,20),c(0,2*meanspec[4,],0),border=NA,col=colpal[3])
-
-lines(freqlist,2*meanspec[1,]+3,lwd=2,col='black')
-lines(freqlist,2*meanspec[2,]+2,lwd=2,col='black')
-lines(freqlist,2*meanspec[3,]+1,lwd=2,col='black')
-lines(freqlist,2*meanspec[4,],lwd=2,col='black')
+polygon(c(1,freqlist[6:120],20),c(0,2*meanspec[1,6:120],0)+3,border=NA,col=colpal[1])
+polygon(c(1,freqlist[6:120],20),c(0,2*meanspec[2,6:120],0)+2,border=NA,col=colpal[1])
+polygon(c(1,freqlist[6:120],20),c(0,2*meanspec[3,6:120],0)+1,border=NA,col=colpal[2])
+polygon(c(1,freqlist[6:120],20),c(0,2*meanspec[4,6:120],0),border=NA,col=colpal[3])
+
+lines(freqlist[6:120],2*meanspec[1,6:120]+3,lwd=2,col='black')
+lines(freqlist[6:120],2*meanspec[2,6:120]+2,lwd=2,col='black')
+lines(freqlist[6:120],2*meanspec[3,6:120]+1,lwd=2,col='black')
+lines(freqlist[6:120],2*meanspec[4,6:120],lwd=2,col='black')
 
@@
 
-  text(-0.02,0.61,'5Hz',pos=4,cex=2)
-  text(-0.02,0.89,'7Hz',pos=4,cex=2)
+  text(-0.02,0.89,'5Hz',pos=4,cex=2)
+  text(-0.02,0.61,'7Hz',pos=4,cex=2)
 

### 2022-06-21 manuscript.Rmd
Doing analysis

@@
 ---
-title: 'The Dynamics of Normalization Reweighting (target journal: Neuron)'
+title: 'Temporal Dynamics of Normalization Reweighting (target journal: Neuron)'
 author: Daniel H. Baker, Daniela Marinova, Richard Aveyard, Lydia Hargreaves, Alice
-  Renton, Ruby Castellani, Phoebe Hall, Miriam Harmens, Georgia Holroyd,
-  Beth Nicholson, Emily Williams, Hannah M. Hobson & Alex R. Wade
+  Renton, Ruby Castellani, Phoebe Hall, Miriam Harmens, Georgia Holroyd, Beth Nicholson,
+  Emily Williams, Hannah M. Hobson & Alex R. Wade
 date: "`r Sys.Date()`"
@@
     fig_caption: yes
-    toc: false   
-    keep_tex: true
+    toc: no
+    keep_tex: yes
   word_document: default
+  pdf_document:
+    toc: no
   html_document: default
@@
 
-processdata <- 1  # this flag determines the amount of processing, with 4 levels:
+processdata <- 0  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all scripts
@@
 # reasonably compact code to check which packages are installed, install the missing ones, and activate all
-packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','tiff') # list of CRAN packages
+packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','tiff','pals') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
@@
 
+scoreAQshort <- function(qdata){
+# score the AQ questionnaire - short version
+# input is a row from a spreadsheet indicating responses to 28 questions
+AQanswers <- toupper(c('(1) Definitely agree','(2) Slightly agree', '(3) Slightly disagree', '(4) Definitely disagree'))
+reverseitems <- rep(0,28)
+ # reverse scored questionnaire items
+reverseitems[c(7, 50, 52, 54, 55, 58, 59, 62, 63, 64, 65, 66, 67, 69, 72)] <- 1
+
+  thisAQ <- 0
+  nansweredAQ <- 0
+  for (q in 1:28){
+    response <- which(AQanswers==toupper(as.character(qdata[1,q])))
+    if (length(response)>0){
+      nansweredAQ <- nansweredAQ + 1
+      if (reverseitems[q]==0){response <- 5 - response}
+      if (response>2){thisAQ <- thisAQ + 1}
+    }}
+thisAQ <- round(50*thisAQ/nansweredAQ)    
+return(thisAQ)}
+
 knitr::opts_chunk$set(echo = TRUE)
@@
 
-Our analysis of 220 human M/EEG datasets
+For decades, neural suppression in early visual cortex has been thought to be fixed.
+But recent work has challenged this assumption by showing that suppression can be \emph{reweighted} based on recent history; when pairs of stimuli are repeatedly presented together, suppression between them strengthens.
+Here we investigate the temporal dynamics of this process using a steady-state VEP paradigm that provides a time-resolved, direct index of suppression between pairs of stimuli flickering at different frequencies (5 and 7Hz).
+Our initial analysis of an existing EEG dataset (N=100) indicated that suppression increases substantially during the first 4 seconds of stimulus presentation.
+We then collected new EEG data (N=100) replicating this finding for both monocular and dichoptic mask arrangements in a preregistered study designed to measure reweighting.
+A third experiment (N=20) use source localized MEG, and found that suppression increases across the visual hierarchy, and that reweighting is more rapid in dorsal compared with ventral visual areas.
+Because long-standing theories propose inhibition/excitation differences in autism, we also compared reweighting between individuals with high vs low autistic traits, and with and without an autism diagnosis, across our 3 data sets (total N=220).
+We find .
+.
+.
 
@@
 
-Suppressive interactions between neurons are ubiquitous in the nervous system, and normalization (or gain control) processes have been proposed as a canonical neuronal computation (Carandini & Heeger).
+Suppressive interactions between neurons are ubiquitous in the nervous system, and normalization (or gain control) processes are considered a canonical neuronal computation (Carandini & Heeger).
 Yet the strength of suppression was for decades treated as fixed, largely due to the observation that adapting to one stimulus does not decrease its suppressive potency (refs).
@@
 This suggests that, far from being fixed, normalization is a dynamic process that is continuously updated by the sensory environment.
-Here, our objectives were to determine if the timecourse of these changes can be measured non-invasively from the human brain, assess if they occur across suppressive pathways, and determine whether they differ across the population as a function of self-reported sensory experience, and autistic traits.
-
-Atypical sensory experience is widely reported by individuals on the autism spectrum, yet the causal mechanisms remain unclear.
+Here, our objectives were to determine if the timecourse of these changes can be measured non-invasively from the human brain, assess if they occur across suppressive pathways, and determine whether they differ across the population as a function of autistic traits.
+
+Atypical sensory experience is widely reported by individuals on the autism spectrum, but the causal mechanisms remain unclear.
 Typical issues include hypersensitivity to intense stimuli such as loud sounds, bright lights and strong odours or flavours.
@@
 1999) are not consistently different from neurotypical controls.
-
-Simmons
-
-Dickinson 2014 oblique effect
-
-Vilidaite summary
-
 Theoretical accounts of sensory differences in autism have long proposed that the balance of inhibition and excitation may be disrupted, and there are isolated results that seem consistent with this.
-For example ...
+For example
 However many other studies have failed to find group differences using tasks that are at least superficially dependent on inhibition, such as...
 
-Priors
+A comprehensive review of the literature on vision in autism (Simmons et al., 2009)
+
+Our recent work has identified a potential autism-related difference in gain control using steady-state EEG methods.
+Vilidaite et al.
+(2018) measured contrast response functions for flickering stimuli in a large group of neurotypical adults, who were split by their autism quotient (AQ; Baron-Cohen et al., 2001) score.
+The responses were comparable between high and low AQ groups at the flicker frequency of the stimulus.
+However at the second harmonic frequency (twice the flicker frequency), the high AQ group showed weaker responses than the low AQ group.
+This effect was replicated in an independent sample of 12 adults with an autism diagnosis (compared with neurotypical controls).
+Because second harmonic responses are caused by nonlinear interactions in the visual system (they are absent in a linear system), this potentially implicates differences in divisive suppression in autism.
+Furthermore, there appears to be a developmental trajectory, as autistic children tested as part of the same study (Vilidaite et al., 2018) showed weaker responses at both the first and second harmonic frequencies.
 
@@
 This is possible, given that suppression within and between the eyes has different spatiotemporal tuning (Meese & Baker, 2009), and dichoptic masking can be reduced by adapting to the mask (Baker, 2007 and other studies), unlike within-eye masking.
-Dynamic fluctuations in interocular suppression are a feature of binocular rivalry (Wilson, 2003), for which differences in autism have also been reported (Robertson).
+Dynamic fluctuations in interocular suppression are a feature of binocular rivalry (Wilson, 2003; Alais et al., 2006), for which differences in autism have also been reported (Robertson).
 
@@
 In this paper we perform a time-course analysis of a previously published EEG data set, and report two novel pre-registered experiments using EEG and MEG.
-Our data show that suppression increases substantially during the first 4 seconds after stimulus onset, for both monocular and dichoptic masks, and as early as V1.
+Our data show that suppression increases substantially during the first 6 seconds after stimulus onset, for both monocular and dichoptic masks.
+The timecourse of reweighting is slower in ventral brain regions, and more rapid in dorsal parts of the visual pathway.
 Autism ...
@@
 In some conditions a single grating orientation was present flickering at 7Hz, whereas in other conditions a high contrast 'mask' was added at right angles to the target gratings, and flickering at 5Hz.
-Figure 1a shows contrast response functions with and without the mask - the presence of the mask reduces the 7Hz response to the target.
-Similarly, Figure 1b shows that the 5Hz response to the mask was itself suppressed by the presence of high contrast targets (note that the data from the mask conditions were not reported by Vilidaite et al.).
+The left panel of Figure \@ref(fig:Pilotdata)a shows contrast response functions with and without the mask - the presence of the mask reduces the 7Hz response to the target (blue squares are below the black circles).
+Similarly, the right panel of Figure \@ref(fig:Pilotdata)a shows that the 5Hz response to the mask was itself suppressed by the presence of high contrast targets (note that the data from the mask conditions were not reported by Vilidaite et al.).
 At both frequencies, responses were localised to the occipital pole (see insets).
 
-We then performed a novel timecourse analysis, in which we separated each 11-second trial into bins of 1 second duration.
-Figure 1c shows the response at the target frequency (7Hz) to a single stimulus of 32% contrast, and the response at 7Hz when the mask is added.
-For the target alone there is a gradual decline throughout the trial, consistent with traditional adaptation effects.
+We then performed a timecourse analysis, in which we analysed each 11-second trial using a sliding 1-second time window.
+Figure \@ref(fig:Pilotdata)c shows the response at the target frequency (7Hz) to a single stimulus of 32% contrast (black), and the response at 7Hz when the mask is added (blue).
+Analogous responses are shown at three other frequencies - the mask frequency (5Hz), and the second harmonics of both target and mask frequencies (14Hz, 10Hz), at which strong responses were also found (see spectra in Figure \@ref(fig:Pilotdata)b).
 The reduction in signal strength when the mask component is added illustrates the masking effect.
-Taking the ratio of the two timecourses reveals that masking increases steeply during the first 4 seconds of stimulus presentation, plateaus for several seconds, and then possibly declines.
-A similar pattern is observed at 5Hz (Figures 1e,f).
-Finally, we split the data set by median AQ score (see Figure 1g).
-Averaging across frequency, the low AQ group showed a strong increase over the first 4 seconds of the trial, whereas the high AQ group showed a much shallower change over the same time period (Figure 1h).
+Taking the ratio of the two timecourses to calculate a masking index reveals that masking increases steeply during the first two seconds of stimulus presentation, and then plateaus for several seconds (blue trace in Figure \@ref(fig:Pilotdata)d).
+A similar pattern is observed at 5Hz (red trace in Figure \@ref(fig:Pilotdata)d), with the increase continuing for around four seconds, as well as at the second harmonics.
+The black trace shows the average masking ratio across all four frequencies, which rises steeply for just over two seconds, mor gradually for a further two seconds, and then stays approximately constant.
 
@@
 Note the strong second harmonic components at 14Hz and 10Hz.
-Panel (c) shows timecourses of responses to a single stimulus (black) and the plaid stimulus (blue), compared to baseline (grey).
+Panel (c) shows timecourses of frequency-locked responses to a single stimulus (black) and the plaid stimulus (blue), compared to baseline (grey).
 Panel (d) shows the timecourse of suppression at each frequency (7Hz, 5Hz, 14Hz, 10Hz) and their average (black curve).
-In panels (c,d), shaded regions indicate ±1SE, and grey rectangles indicate the timing of stimulus presentation.", fig.align="center", echo=FALSE}
+Error bars in panel (a) and shaded regions in panels (c,d) indicate ±1SE, and grey rectangles indicate the timing of stimulus presentation.
+The larger symbols in panel (a) indicate conditions used for subsequent analyses.", fig.align="center", echo=FALSE}
 
@@
 
-Our initial reanalysis was promising, however the data were noisy despite the large sample size, because each participant contributed only 8 trials to each condition.
+Our initial reanalysis was promising, however the data were noisy despite the large sample size, because each participant contributed only 8 trials (88 seconds) to each condition.
 We therefore preregistered two new experiments (see https://osf.io/4qudc) to investigate these effects in greater detail.
 These had a similar overall design to the Vilidaite study, with some small changes intended to optimise the study (see Methods).
-The key differences were that we used shorter trials (because there were few changes in the latter part of the trials shown in Figure 1), and also focussed all trials into a smaller number of conditions, such that each participant contributed 48 repetitions to each of 4 conditions.
-The greater data fidelity afforded by this design allowed us to perform a sliding time window analysis of the results.
-
-Figure \@ref(fig:EEGdata) summarises the results of an EEG experiment testing 100 neurotypical participants.
+The key differences were that we used shorter trials (because there were few changes in the latter part of the trials shown in Figure \@ref(fig:Pilotdata)), and also focussed all trials into a smaller number of conditions, such that each participant contributed 48 repetitions (288 seconds of data) to each of 4 conditions.
+
+Figure \@ref(fig:EEGdata) summarises the results of our EEG experiment testing a further 100 neurotypical adults.
 Averaged EEG waveforms showed a strong oscillatory component at each of the two stimulus flicker frequencies (Figure \@ref(fig:EEGdata)a), which slightly lagged the driving signal.
-Signals were well-isolated in the Fourier domain, and localised to occipital electrodes (Figure \@ref(fig:EEGdata)b).
+Signals were well-isolated in the Fourier domain (Figure \@ref(fig:EEGdata)b), and localised to occipital electrodes.
 The timecourse at both frequencies showed an initial onset transient, and was then relatively stable for the 6 seconds of stimulus presentation (Figure \@ref(fig:EEGdata)c,d).
 Responses were weaker in the two masking conditions, and the ratio of target only to target + mask conditions increased over time (Figure \@ref(fig:EEGdata)e,f) for both mask types.
-At 5Hz the increase in masking continued over the first 5 seconds of stimulus presentation (Figure \@ref(fig:EEGdata)e), whereas at 7Hz the increase occurred mostly during the first second after onset (Figure \@ref(fig:EEGdata)f).
+At 5Hz the increase in masking continued over the first 5 seconds of stimulus presentation (Figure \@ref(fig:EEGdata)e), whereas at 7Hz the increase occurred mostly during the first second after onset (Figure \@ref(fig:EEGdata)f), consistent with the pilot data (see Figure \@ref(fig:Pilotdata)).
 
@@
 
-Participants showed a wide range of scores on both the AQ and SPQ scales, which were negatively correlated (Fig 3a; R = , p < ).
-We again performed a median split by AQ on the EEG data, and calculated the timecourse of the EEG response and suppression ratios for each group (Figure 3b,c).
-
 Next we repeated the experiment on 20 participants using a 248-channel whole-head cryogenic MEG system.
 Half of the participants had a diagnosis of autism, and the remainder were age and gender-matched controls.
-Source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm (reference) showed strong localisation of steady-state signals at the occipital pole (see Figure 4a,b).
+Source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm (reference) showed strong localisation of steady-state signals at the occipital pole (see Figure \@ref(fig:MEGdata)a,b).
+
 Responses across V1 showed a similar timecourse to those of the EEG experiment at both frequencies (Figure 4c,d), and showed increasing suppression during the first 4 seconds of stimulus presentation (Figure 4e,f).
@@
     mindex <- 1 + maskF*(binwidth/samplerate)
+MEGareacols <- cols25(8)[c(1:5,8,7)]
 
@@
   for (area in 1:nareas){
-spl5aU <- smooth.spline(times,MEGmeantime5Hz[1,]+MEGSEtime5Hz[1,],df=20)
-spl5aL <- smooth.spline(times,MEGmeantime5Hz[1,]-MEGSEtime5Hz[1,],df=20)
+spl5aU <- smooth.spline(times,MEGmeantime5Hz[area,1,]+MEGSEtime5Hz[area,1,],df=20)
+spl5aL <- smooth.spline(times,MEGmeantime5Hz[area,1,]-MEGSEtime5Hz[area,1,],df=20)
 polygon(times[c(1:8008,8008:1)],c(spl5aU$y,spl5aL$y[8008:1]),col=colpal[1],border=NA)
 
-spl5cU <- smooth.spline(times,MEGmeantime5Hz[3,]+MEGSEtime5Hz[3,],df=20)
-spl5cL <- smooth.spline(times,MEGmeantime5Hz[3,]-MEGSEtime5Hz[3,],df=20)
+spl5cU <- smooth.spline(times,MEGmeantime5Hz[area,3,]+MEGSEtime5Hz[area,3,],df=20)
+spl5cL <- smooth.spline(times,MEGmeantime5Hz[area,3,]-MEGSEtime5Hz[area,3,],df=20)
 polygon(times[c(1:8008,8008:1)],c(spl5cU$y,spl5cL$y[8008:1]),col=colpal[2],border=NA)
 
-spl5dU <- smooth.spline(times,MEGmeantime5Hz[4,]+MEGSEtime5Hz[4,],df=20)
-spl5dL <- smooth.spline(times,MEGmeantime5Hz[4,]-MEGSEtime5Hz[4,],df=20)
+spl5dU <- smooth.spline(times,MEGmeantime5Hz[area,4,]+MEGSEtime5Hz[area,4,],df=20)
+spl5dL <- smooth.spline(times,MEGmeantime5Hz[area,4,]-MEGSEtime5Hz[area,4,],df=20)
 polygon(times[c(1:8008,8008:1)],c(spl5dU$y,spl5dL$y[8008:1]),col=colpal[3],border=NA)
@@
 L <- smooth.spline(times,MEGmaskindex5[area,1,],df=20)
-lines(L$x,L$y,col=colpal[2],lwd=2)
+lines(L$x,L$y,col=MEGareacols[area],lwd=2)
+# L <- smooth.spline(times,MEGmaskindex5[area,2,],df=20)
+# lines(L$x,L$y,col=colpal[3],lwd=2)
+}
+legend(1,2,c('V1','V2','V3','hV4','TO','LO','VO'),col=MEGareacols,lwd=2)
+}
+
+dev.off()
+
+postscript("timecourse2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,7,-3,7)
+ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocsx, side = 1, at=ticklocsx)
+mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,6,6,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))
+
+lines(c(-1,7),c(0,0),lty=2)
+
+for (area in 1:nareas){ 
 L <- smooth.spline(times,MEGmaskindex5[area,2,],df=20)
-lines(L$x,L$y,col=colpal[3],lwd=2)
-}
-}
+lines(L$x,L$y,col=MEGareacols[area],lwd=2)
+# L <- smooth.spline(times,MEGmaskindex5[area,2,],df=20)
+# lines(L$x,L$y,col=colpal[3],lwd=2)
+}
+legend(1,2,c('V1','V2','V3','hV4','TO','LO','VO'),col=MEGareacols,lwd=2)
+
+dev.off()
+
+postscript("timecourse2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,7,-3,7)
+ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocsx, side = 1, at=ticklocsx)
+mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,6,6,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))
+
+lines(c(-1,7),c(0,0),lty=2)
+
+if (plotsmoothed==0){
+polygon(times[c(1:8008,8008:1)],c(MEGmaskindex5[1,]+MEGmaskindexSE5[1,],MEGmaskindex5[1,8008:1]-MEGmaskindexSE5[1,8008:1]),col=colpal[2],border=NA)
+polygon(times[c(1:8008,8008:1)],c(MEGmaskindex5[2,]+MEGmaskindexSE5[2,],MEGmaskindex5[2,8008:1]-MEGmaskindexSE5[2,8008:1]),col=colpal[3],border=NA)
+
+lines(times,MEGmaskindex5[1,],col=colpal[2],lwd=2)
+lines(times,MEGmaskindex5[2,],col=colpal[3],lwd=2)
+}
+if (plotsmoothed==1){
+U <- smooth.spline(times,MEGmaskindex5[1,]+MEGmaskindexSE5[1,],df=20)
+L <- smooth.spline(times,MEGmaskindex5[1,]-MEGmaskindexSE5[1,],df=20)
+polygon(times[c(1:8008,8008:1)],c(U$y,L$y[8008:1]),col=colpal[2],border=NA)
+
+U <- smooth.spline(times,MEGmaskindex5[2,]+MEGmaskindexSE5[2,],df=20)
+L <- smooth.spline(times,MEGmaskindex5[2,]-MEGmaskindexSE5[2,],df=20)
+polygon(times[c(1:8008,8008:1)],c(U$y,L$y[8008:1]),col=colpal[3],border=NA)
+
+for (area in 1:nareas){ 
+L <- smooth.spline(times,MEGmaskindex7[area,1,],df=20)
+lines(L$x,L$y,col=MEGareacols[area],lwd=2)
+# L <- smooth.spline(times,MEGmaskindex5[area,2,],df=20)
+# lines(L$x,L$y,col=colpal[3],lwd=2)
+}
+legend(1,2,c('V1','V2','V3','hV4','TO','LO','VO'),col=MEGareacols,lwd=2)
+}
+
+dev.off()
+
+postscript("timecourse2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,7,-3,7)
+ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocsx, side = 1, at=ticklocsx)
+mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,6,6,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))
+
+lines(c(-1,7),c(0,0),lty=2)
+
+for (area in 1:nareas){ 
+L <- smooth.spline(times,MEGmaskindex7[area,2,],df=20)
+lines(L$x,L$y,col=MEGareacols[area],lwd=2)
+# L <- smooth.spline(times,MEGmaskindex5[area,2,],df=20)
+# lines(L$x,L$y,col=colpal[3],lwd=2)
+}
+legend(1,2,c('V1','V2','V3','hV4','TO','LO','VO'),col=MEGareacols,lwd=2)
 
@@
 
+```{r include=FALSE, results='hide'}
+
+if (processdata>0){
+load('temp/EEGsummary.RData')
+
+isincluded <- matrix(rep(1,4*dim(allspec)[1]),nrow=4,ncol=dim(allspec)[1])
+for (cond in 1:4){
+  # note that in allspec the DC component has been removed
+  # so we don't need to add 1 to the index
+      tempxy <- data.frame(Re(allspec[,cond,duration*targetF]),Im(allspec[,cond,duration*targetF]))
+      D5 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+      tempxy <- data.frame(Re(allspec[,cond,duration*maskF]),Im(allspec[,cond,duration*maskF]))      
+      D7 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))      
+      isincluded[cond,which(D5>3)] <- 0
+      isincluded[cond,which(D7>3)] <- 0
+   for (s in 1:100){
+     if (max(abs(EEGtimecourse5Hz[s,cond,]))>5){isincluded[cond,s] <- 0}
+   }   
+}
+
+allwaves[which(allwaves<(-100))] <- 0
+allwaves[which(allwaves>100)] <- 0
+
+medAQ <- median(allAQ)
+islowAQ <- rep(0,100)
+ishighAQ <- rep(0,100)
+islowAQ[which(allAQ<medAQ)] <- 1
+ishighAQ[which(allAQ>medAQ)] <- 1
+
+EEGmeantime5HzL <- matrix(0,nrow=4,ncol=8000)
+EEGmeantime7HzL <- matrix(0,nrow=4,ncol=8000)
+EEGSEtime5HzL <- matrix(0,nrow=4,ncol=8000)
+EEGSEtime7HzL <- matrix(0,nrow=4,ncol=8000)
+EEGmeantime5HzH <- matrix(0,nrow=4,ncol=8000)
+EEGmeantime7HzH <- matrix(0,nrow=4,ncol=8000)
+EEGSEtime5HzH <- matrix(0,nrow=4,ncol=8000)
+EEGSEtime7HzH <- matrix(0,nrow=4,ncol=8000)
+
+for (cond in 1:4){
+lowAQincluded <- islowAQ * isincluded[cond,]
+highAQincluded <- ishighAQ * isincluded[cond,]
+
+EEGmeantime7HzL[cond,] <- apply(abs(EEGtimecourse7Hz[which(lowAQincluded==1),cond,]),2,mean,na.rm=TRUE)
+EEGmeantime5HzL[cond,] <- apply(abs(EEGtimecourse5Hz[which(lowAQincluded==1),cond,]),2,mean,na.rm=TRUE)
+
+EEGSEtime7HzL[cond,] <- apply(abs(EEGtimecourse7Hz[which(lowAQincluded==1),cond,]),2,sd,na.rm=TRUE)/sqrt(sum(lowAQincluded))
+EEGSEtime5HzL[cond,] <- apply(abs(EEGtimecourse5Hz[which(lowAQincluded==1),cond,]),2,sd,na.rm=TRUE)/sqrt(sum(lowAQincluded))
+
+EEGmeantime7HzH[cond,] <- apply(abs(EEGtimecourse7Hz[which(highAQincluded==1),cond,]),2,mean,na.rm=TRUE)
+EEGmeantime5HzH[cond,] <- apply(abs(EEGtimecourse5Hz[which(highAQincluded==1),cond,]),2,mean,na.rm=TRUE)
+
+EEGSEtime7HzH[cond,] <- apply(abs(EEGtimecourse7Hz[which(highAQincluded==1),cond,]),2,sd,na.rm=TRUE)/sqrt(sum(highAQincluded))
+EEGSEtime5HzH[cond,] <- apply(abs(EEGtimecourse5Hz[which(highAQincluded==1),cond,]),2,sd,na.rm=TRUE)/sqrt(sum(highAQincluded))
+}
+
+EEGmaskindex5L <- matrix(0,nrow=2,ncol=8000)
+EEGmaskindexSE5L <- matrix(0,nrow=2,ncol=8000)
+includedboth <- isincluded[1,]*isincluded[3,]*islowAQ
+monratios <- abs(EEGtimecourse5Hz[which(includedboth==1),1,])/abs(EEGtimecourse5Hz[which(includedboth==1),3,])
+EEGmaskindex5L[1,] <- colMeans(20*log10(monratios))
+EEGmaskindexSE5L[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+includedboth <- isincluded[1,]*isincluded[4,]*islowAQ
+dichratios <- abs(EEGtimecourse5Hz[which(includedboth==1),1,])/abs(EEGtimecourse5Hz[which(includedboth==1),4,])
+EEGmaskindex5L[2,] <- colMeans(20*log10(dichratios))
+EEGmaskindexSE5L[2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+
+EEGmaskindex5H <- matrix(0,nrow=2,ncol=8000)
+EEGmaskindexSE5H <- matrix(0,nrow=2,ncol=8000)
+includedboth <- isincluded[1,]*isincluded[3,]*ishighAQ
+monratios <- abs(EEGtimecourse5Hz[which(includedboth==1),1,])/abs(EEGtimecourse5Hz[which(includedboth==1),3,])
+EEGmaskindex5H[1,] <- colMeans(20*log10(monratios))
+EEGmaskindexSE5H[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+includedboth <- isincluded[1,]*isincluded[4,]*ishighAQ
+dichratios <- abs(EEGtimecourse5Hz[which(includedboth==1),1,])/abs(EEGtimecourse5Hz[which(includedboth==1),4,])
+EEGmaskindex5H[2,] <- colMeans(20*log10(dichratios))
+EEGmaskindexSE5H[2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+
+EEGmaskindex7L <- matrix(0,nrow=2,ncol=8000)
+EEGmaskindexSE7L <- matrix(0,nrow=2,ncol=8000)
+includedboth <- isincluded[2,]*isincluded[3,]*islowAQ
+monratios <- abs(EEGtimecourse7Hz[which(includedboth==1),2,])/abs(EEGtimecourse7Hz[which(includedboth==1),3,])
+EEGmaskindex7L[1,] <- colMeans(20*log10(monratios))
+EEGmaskindexSE7L[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+includedboth <- isincluded[2,]*isincluded[4,]*islowAQ
+dichratios <- abs(EEGtimecourse7Hz[which(includedboth==1),2,])/abs(EEGtimecourse7Hz[which(includedboth==1),4,])
+EEGmaskindex7L[2,] <- colMeans(20*log10(dichratios))
+EEGmaskindexSE7L[2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+
+EEGmaskindex7H <- matrix(0,nrow=2,ncol=8000)
+EEGmaskindexSE7H <- matrix(0,nrow=2,ncol=8000)
+includedboth <- isincluded[2,]*isincluded[3,]*ishighAQ
+monratios <- abs(EEGtimecourse7Hz[which(includedboth==1),2,])/abs(EEGtimecourse7Hz[which(includedboth==1),3,])
+EEGmaskindex7H[1,] <- colMeans(20*log10(monratios))
+EEGmaskindexSE7H[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+includedboth <- isincluded[2,]*isincluded[4,]*ishighAQ
+dichratios <- abs(EEGtimecourse7Hz[which(includedboth==1),2,])/abs(EEGtimecourse7Hz[which(includedboth==1),4,])
+EEGmaskindex7H[2,] <- colMeans(20*log10(dichratios))
+EEGmaskindexSE7H[2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+
+times <- ((1:8000)-1000)/1000
+
+for (masktype in 1:2){
+postscript(paste0("timecourse",masktype,".ps"), horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,7,-3,6)
+ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocsx, side = 1, at=ticklocsx)
+mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,6,6,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))
+
+lines(c(-1,7),c(0,0),lty=2)
+
+if (plotsmoothed==0){
+polygon(times[c(1:8000,8000:1)],c(EEGmaskindex5L[masktype,]+EEGmaskindexSE5L[masktype,],EEGmaskindex5L[masktype,8000:1]-EEGmaskindexSE5L[masktype,8000:1]),col=colpal[2],border=NA)
+polygon(times[c(1:8000,8000:1)],c(EEGmaskindex5H[masktype,]+EEGmaskindexSE5H[masktype,],EEGmaskindex5H[masktype,8000:1]-EEGmaskindexSE5H[masktype,8000:1]),col=colpal[3],border=NA)
+
+lines(times,EEGmaskindex5L[masktype,],col=colpal[2],lwd=2)
+lines(times,EEGmaskindex5H[masktype,],col=colpal[3],lwd=2)
+}
+
+if (plotsmoothed==1){
+U <- smooth.spline(times,EEGmaskindex5L[masktype,]+EEGmaskindexSE5L[masktype,],df=20)
+L <- smooth.spline(times,EEGmaskindex5L[masktype,]-EEGmaskindexSE5L[masktype,],df=20)
+polygon(times[c(1:8000,8000:1)],c(U$y,L$y[8000:1]),col=colpal[2],border=NA)
+
+U <- smooth.spline(times,EEGmaskindex5H[masktype,]+EEGmaskindexSE5H[masktype,],df=20)
+L <- smooth.spline(times,EEGmaskindex5H[masktype,]-EEGmaskindexSE5H[masktype,],df=20)
+polygon(times[c(1:8000,8000:1)],c(U$y,L$y[8000:1]),col=colpal[3],border=NA)
+
+L <- smooth.spline(times,EEGmaskindex5L[masktype,],df=20)
+lines(L$x,L$y,col=colpal[2],lwd=2)
+L <- smooth.spline(times,EEGmaskindex5H[masktype,],df=20)
+lines(L$x,L$y,col=colpal[3],lwd=2)
+}
+
+dev.off()
+
+postscript(paste0("timecourse",masktype+2,".ps"), horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,7,-3,6)
+ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocsx, side = 1, at=ticklocsx)
+mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,6,6,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))
+
+lines(c(-1,7),c(0,0),lty=2)
+
+if (plotsmoothed==0){
+polygon(times[c(1:8000,8000:1)],c(EEGmaskindex7L[masktype,]+EEGmaskindexSE7L[masktype,],EEGmaskindex7L[masktype,8000:1]-EEGmaskindexSE7L[masktype,8000:1]),col=colpal[2],border=NA)
+polygon(times[c(1:8000,8000:1)],c(EEGmaskindex7H[masktype,]+EEGmaskindexSE7H[masktype,],EEGmaskindex7H[masktype,8000:1]-EEGmaskindexSE7H[masktype,8000:1]),col=colpal[3],border=NA)
+
+lines(times,EEGmaskindex7L[masktype,],col=colpal[2],lwd=2)
+lines(times,EEGmaskindex7H[masktype,],col=colpal[3],lwd=2)
+}
+
+if (plotsmoothed==1){
+U <- smooth.spline(times,EEGmaskindex7L[masktype,]+EEGmaskindexSE7L[masktype,],df=20)
+L <- smooth.spline(times,EEGmaskindex7L[masktype,]-EEGmaskindexSE7L[masktype,],df=20)
+polygon(times[c(1:8000,8000:1)],c(U$y,L$y[8000:1]),col=colpal[2],border=NA)
+
+U <- smooth.spline(times,EEGmaskindex7H[masktype,]+EEGmaskindexSE7H[masktype,],df=20)
+L <- smooth.spline(times,EEGmaskindex7H[masktype,]-EEGmaskindexSE7H[masktype,],df=20)
+polygon(times[c(1:8000,8000:1)],c(U$y,L$y[8000:1]),col=colpal[3],border=NA)
+
+L <- smooth.spline(times,EEGmaskindex7L[masktype,],df=20)
+lines(L$x,L$y,col=colpal[2],lwd=2)
+L <- smooth.spline(times,EEGmaskindex7H[masktype,],df=20)
+lines(L$x,L$y,col=colpal[3],lwd=2)
+}
+
+dev.off()
+
+}
+}
+
+```
+
+Participants showed a wide range of scores on both the AQ and SPQ scales, which were negatively correlated (Fig 3a; R = , p < ).
+We again performed a median split by AQ on the EEG data, and calculated the timecourse of the EEG response and suppression ratios for each group (Figure 3b,c).
+
+Finally, we split the data set by median AQ score (see Figure 1g).
+Averaging across frequency, the low AQ group showed a strong increase over the first 4 seconds of the trial, whereas the high AQ group showed a much shallower change over the same time period (Figure 1h).
+
 ## Discussion
 
+Priors, Dickinson 2014 oblique effect
+
 ## Methods

### 2022-09-30 manuscript.Rmd
Update of manuscript

@@
 ---
-title: 'Temporal Dynamics of Normalization Reweighting (target journal: Neuron)'
-author: Daniel H. Baker, Daniela Marinova, Richard Aveyard, Lydia Hargreaves, Alice
-  Renton, Ruby Castellani, Phoebe Hall, Miriam Harmens, Georgia Holroyd, Beth Nicholson,
-  Emily Williams, Hannah M. Hobson & Alex R. Wade
+title: 'Temporal Dynamics of Normalization Reweighting'
+author: | 
+  | Daniel H. Baker, Daniela Marinova, Richard Aveyard, Lydia J. Hargreaves, Alice Renton,  
+  | Ruby Castellani, Phoebe Hall, Miriam Harmens, Georgia Holroyd, Beth Nicholson, 
+  | Emily L. Williams, Hannah M. Hobson & Alex R. Wade
 date: "`r Sys.Date()`"
@@
   html_document: default
+bibliography: references.bib
+csl: elife.csl
 ---
@@
 processdata <- 0  # this flag determines the amount of processing, with 4 levels:
-# 0 - do no processing, generate the pdf using existing versions of all scripts
+# 0 - do no processing, generate the pdf using existing versions of all figures
 # 1 - generate figures using the processed group data (requires XGB of storage)
@@
 plotsmoothed <- 1 # either plot the raw data (0), or a smoothed spline (1)
+useSPQ <- 0  # optionally do the median split by SPQ for the main EEG experiment
 
 # reasonably compact code to check which packages are installed, install the missing ones, and activate all
-packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','tiff','pals') # list of CRAN packages
+packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','tiff','pals','ez','gtools') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
@@
 
+scoreSPQ <- function(qdata){
+# score the SPQ questionnaire
+# input is a row from a spreadsheet indicating responses to 92 questions
+SPQanswers <- toupper(c('Strongly agree','Agree','Disagree','Strongly Disagree'))
+# SPQorder <- c(4,2,1,3)
+reverseitemsSPQ <- (1:ncol(qdata))*0
+reverseitemsSPQ[c(3,4,5,10,13,15:18,20,22,25:29,31,34,39,40,42:44,46:48,51,54,56,57,63,66,67,72,75,77:80,86,89,92)] <- 1  # reverse scored questionnaire items
+
+  thisSPQ <- 0
+  nansweredSPQ <- 0
+  for (q in 1:92){
+    response <- which(SPQanswers==toupper(as.character(qdata[1,q]))) - 1
+    if (length(response)>0){
+      nansweredSPQ <- nansweredSPQ + 1
+      if (reverseitemsSPQ[q]==1){response <- 3 - response}
+      thisSPQ <- thisSPQ + response
+    }
+  }
+
+return(thisSPQ)}
+
+clustercorrect <- function(datax,datay=NULL,adjacencymatrix=NULL,testtype=1,paired=TRUE,clustformthresh=0.05,clustthresh=0.05,nresamples=10000) {
+  clustout <- NULL
+  sigclustercount <- 0
+  clusterpout <- NULL
+  clusterpoints <- list()
+  nulldist <- NULL
+  N <- nrow(datax)  # number of observations (e.g. participants)
+  m <- ncol(datax)  # number of measurements (e.g. sensors, voxels, timepoints)
+
+  # if complex data have been passed in and t-test selected, convert to amplitudes
+  if (is.complex(datax) && testtype==1){datax <- abs(datax)}
+  if (is.complex(datay) && testtype==1){datay <- abs(datay)}
+
+  # if two data sets have been passed in, note the size of the second matrix
+  if (!pracma::isempty(datay)){N2 <- nrow(datay)}
+
+  # if it's a paired design, subtract the two data sets and delete the second one
+  if (paired==TRUE && !pracma::isempty(datay)){
+    datax <- datax - datay
+    datay <- NULL}
+
+  if (length(adjacencymatrix)==0){
+    # if no adjacency matrix has been passed in, we assume that subsequent observations are adjacent
+    adjacencymatrix <- matrix(0,nrow=m,ncol=m)
+    for (n in 1:(m-1)){adjacencymatrix[n,n+1] <- 1}
+    for (n in 2:m){adjacencymatrix[n,n-1] <- 1}
+  }
+
+  allp <- NULL
+  allt <- NULL
+  # loop through all elements (sensors/time points) and calculate the test statistic and p-value
+  for (n in 1:m){
+
+    if (pracma::isempty(datay)){
+      # one-sample or paired test
+      if (testtype==1){
+        output <- t.test(datax[,n])  # univariate t-test
+        allp[n] <- output$p.value
+        allt[n] <- output$statistic}
+      if (testtype==2){
+        output <- tsqh.test(datax[,n])  # one-sample Hotelling's t-squared
+        allp[n] <- output$pval
+        allt[n] <- output$tsq}
+      if (testtype==3){
+        output <- tsqc.test(datax[,n])  # T-squared-circ
+        allp[n] <- output$pval
+        allt[n] <- output$tsqc}
+      if (testtype==4){
+        output <- t.test(datax[,n],alternative='greater')  # univariate t-test
+        allp[n] <- output$p.value
+        allt[n] <- output$statistic}
+    }
+
+    # independent samples test
+    if (!pracma::isempty(datay) && is.matrix(datay)){
+      if (testtype==1){
+        output <- t.test(datax[,n],datay[,n]) # independent t-test
+        allp[n] <- output$p.value
+        allt[n] <- output$statistic}
+      if (testtype==2){
+        output <- tsqh.test(datax[,n],datay[,n],paired=FALSE)  # independent T-squared
+        allp[n] <- output$pval
+        allt[n] <- output$tsq}
+      if (testtype==3){
+        output <- tsqc.test(datax[,n],datay[,n],paired=FALSE)  # independent T-squared-circ
+        allp[n] <- output$pval
+        allt[n] <- output$tsqc}
+            if (testtype==4){
+        output <- t.test(datax[,n],datay[,n],alternative='greater') 
+        allp[n] <- output$p.value
+        allt[n] <- output$statistic}
+    }
+  }
+
+  allp[which(is.na(allp))] <- 1
+
+  # now generate a list of clusters of adjacent significant elements
+  hvect <- rep(0,m)
+  hvect[which(allp<clustformthresh)] <- 1
+  hmat <- matrix(hvect,nrow=m,ncol=m)
+  hmat2 <- hmat * t(hmat)
+  clustprod <- hmat2 * adjacencymatrix
+
+  clusterlist <- list()
+  nclusts <- 0
+  for (n in 1:m){
+    temp = sum(clustprod[n,])
+    if (temp>0){
+      i <- which(clustprod[n,]>0)
+      tempclust <- c(n, i)
+      clustprod[n,] <- 0
+      clustprod[,n] <- 0
+      cnt <- 0
+      while (cnt<length(tempclust)){
+        cnt <- cnt + 1
+        temp = sum(clustprod[tempclust[cnt],])
+        if (temp>0){
+          i <- which(clustprod[tempclust[cnt],]>0)
+          tempclust <- c(tempclust, i)
+          clustprod[tempclust[cnt],] <- 0
+          clustprod[,tempclust[cnt]] <- 0
+        }
+      }
+      nclusts <- nclusts + 1
+      clusterlist[[nclusts]] <- sort(unique(tempclust))
+    }
+  }
+
+  if (nclusts>0){
+    sumtvals <- NULL
+    for (cc in 1:nclusts){
+      Cindices <- as.numeric(clusterlist[[cc]])
+      sumtvals[cc] <- sum(allt[Cindices])}
+
+    i <- which(sumtvals==max(sumtvals))  # find the largest cluster
+    maxcluster <- clusterlist[[i]]  # store the largest cluster
+
+    if (length(maxcluster)>1){
+    # build a null distribution by permuting signs/group labels
+    for (n in 1:nresamples){
+      tsum <- 0
+      if (pracma::isempty(datay)){randsigns <- (round(runif(N))*2)-1}
+      if (!pracma::isempty(datay) && is.matrix(datay)){randgroups <- permute(c(1:N,(N+1):(N+N2)))}
+      for (elcounter in 1:length(maxcluster)){
+
+        if (pracma::isempty(datay)){  # one-sample or paired test
+          tempdataA <- datax[,maxcluster[elcounter]]*randsigns
+          if (testtype==1){
+            output <- t.test(tempdataA)
+            tsum <- tsum + output$statistic}
+          if (testtype==2){
+            output <- tsqh.test(tempdataA)
+            tsum <- tsum + output$tsq}
+          if (testtype==3){
+            output <- tsqc.test(tempdataA)
+            tsum <- tsum + output$tsqc}
+        }
+
+        if (!pracma::isempty(datay) && is.matrix(datay)){  # independent samples test
+          tempdata <- c(datax[,maxcluster[elcounter]],datay[,maxcluster[elcounter]])
+          tempdataA <- tempdata[randgroups[1:N]]
+          tempdataB <- tempdata[randgroups[(N+1):(N+N2)]]
+          if (testtype==1){
+            output <- t.test(tempdataA,tempdataB)
+            tsum <- tsum + output$statistic}
+          if (testtype==2){
+            output <- tsqh.test(tempdataA,tempdataB,paired=FALSE)
+            tsum <- tsum + output$tsq}
+          if (testtype==3){
+            output <- tsqc.test(tempdataA,tempdataB,paired=FALSE)
+            tsum <- tsum + output$tsqc}
+        }
+      }
+      nulldist[n] <- tsum
+    }
+    }
+
+    # compare each cluster to the null distribution, retain the significant ones
+    clusterps <- 0*(1:nclusts)
+    if (length(nulldist)==nresamples){
+    for (cc in 1:nclusts){
+      i <- which(abs(nulldist)>abs(sumtvals[cc]))
+      if (!isempty(i)){clusterps[cc] <- length(i)/nresamples}
+      if (clusterps[cc]<clustthresh){
+        sigclustercount <- sigclustercount + 1
+        clusterpoints[[sigclustercount]] <- clusterlist[[cc]]
+        clusterpout[sigclustercount] <- clusterps[cc]
+        }
+    }}
+  }
+clustout <- NULL
+clustout$clusterpoints <- clusterpoints
+clustout$nclusters <- sigclustercount
+clustout$pvals <- clusterpout
+
+return(clustout)
+}
+
 knitr::opts_chunk$set(echo = TRUE)
-colpal <- c('#000000','#8783CF','#FE5000','#228B22','#8B8000')
+colpal <- c('#000000','#8783CF','#FE5000','#228B22','#6d008b','#8B8000')
 
@@
 
+nbootstraps <- 1000    # number of bootstrap resamples for cluster correction
+timeoffset <- 1000  # time offset for determining if suppression is increasing
+
 ```
 
-## Abstract
+# Abstract
 
@@
 Here we investigate the temporal dynamics of this process using a steady-state VEP paradigm that provides a time-resolved, direct index of suppression between pairs of stimuli flickering at different frequencies (5 and 7Hz).
-Our initial analysis of an existing EEG dataset (N=100) indicated that suppression increases substantially during the first 4 seconds of stimulus presentation.
+Our initial analysis of an existing EEG dataset (N=100) indicated that suppression increases substantially during the first 2-5 seconds of stimulus presentation (with some variation across stimulation frequency).
 We then collected new EEG data (N=100) replicating this finding for both monocular and dichoptic mask arrangements in a preregistered study designed to measure reweighting.
-A third experiment (N=20) use source localized MEG, and found that suppression increases across the visual hierarchy, and that reweighting is more rapid in dorsal compared with ventral visual areas.
+A third experiment (N=20) used source localized MEG, and found that these effects are apparent in primary visual cortex (V1), consistent with results from neurophysiological work.
 Because long-standing theories propose inhibition/excitation differences in autism, we also compared reweighting between individuals with high vs low autistic traits, and with and without an autism diagnosis, across our 3 data sets (total N=220).
-We find .
-.
-.
-
-## Introduction
-
-Suppressive interactions between neurons are ubiquitous in the nervous system, and normalization (or gain control) processes are considered a canonical neuronal computation (Carandini & Heeger).
-Yet the strength of suppression was for decades treated as fixed, largely due to the observation that adapting to one stimulus does not decrease its suppressive potency (refs).
-This orthodoxy was recently challenged by a series of innovative studies showing that normalization can be 'reweighted' by recent history (Westrick, Aschner, Yiltiz).
-Specifically, when pairs of stimuli are repeatedly presented together, they come to suppress each other more strongly.
+We find no compelling differences in reweighting that are associated with autism.
+Our results support the normalization reweighting model, and indicate that for prolonged stimulation, increases in suppression occur on the order of 2-5 seconds after stimulus onset.
+
+# Introduction
+
+Suppressive interactions between neurons are ubiquitous in the nervous system, and normalization (or gain control) processes are considered a canonical neuronal computation [@Carandini2011].
+Yet for decades the strength of suppression was treated as fixed, largely due to the observation that adapting to one stimulus does not decrease its suppressive potency [@Foley1997; @Freeman2002].
+This orthodoxy was recently challenged by a series of innovative studies showing that normalization can be 'reweighted' by recent history [@Westrick2016; @Aschner2018; @Yiltiz2020].
+Specifically, when pairs of stimuli are repeatedly presented together, their neural representations come to suppress each other more strongly.
 This suggests that, far from being fixed, normalization is a dynamic process that is continuously updated by the sensory environment.
-Here, our objectives were to determine if the timecourse of these changes can be measured non-invasively from the human brain, assess if they occur across suppressive pathways, and determine whether they differ across the population as a function of autistic traits.
-
-Atypical sensory experience is widely reported by individuals on the autism spectrum, but the causal mechanisms remain unclear.
+Here, our objectives were to determine if the timecourse of these changes can be measured non-invasively from the human brain, assess if they occur similarly in distinct suppressive pathways, and determine whether they differ across the population as a function of autistic traits.
+
+Plastic changes within the visual system occur over multiple timescales [see @Webster2015 for a recent review].
+In the retina, adaptation to complete darkness takes around 30 minutes [@Lamb2006], and has established physiological substrates (i.e.
+the regeneration rate of chemicals in different photoreceptor classes).
+Cortical forms of adaptation to cues such as stimulus contrast [@Blakemore1969], orientation [@Gibson1937] and motion [@Mather2008] can be observed within a few seconds, but also build up over durations on the order of several minutes [@Greenlee1991].
+A recent form of binocular plasticity [@Lunghi2011], in which one eye is patched and subsequently contributes more to binocular vision, requires more than an hour.
+Other types of adaptation have been identified with changes occurring over longer time periods, such as over several hours [@Kwon2009] or days [@Haak2014].
+Finally adaptation to specific combinations of orientation and colour [the @McCollough1965 effect] can persist for several weeks [@Jones1975], even with a brief induction period.
+Previous work on normalization reweighting has involved adapting sequences of around 40 -- 60s [@Aschner2018; @Yiltiz2020], though it is possible that reweighting might occur faster than this, consistent with other types of contrast adaptation.
+
+Normalization itself is not a single process.
+Multiple suppressive pathways have been identified in the visual system, including between stimuli differing in orientation [@Heeger1992; @Foley1994], eye-of-origin [@Legge1979; @Sengpiel1994] and spatial position [@Petrov2005; @Cannon1991].
+At present there is evidence of normalization reweighting between stimuli with orthogonal orientations [@Aschner2018], and adjacent spatial positions [@Yiltiz2020].
+We anticipated that interocular suppression should also be subject to reweighting, but that there might be differences in the dynamics across suppressive pathways.
+This is plausible, given that suppression within and between the eyes has different spatiotemporal tuning [@Meese2009], and dichoptic masking can be reduced by adapting to the mask [@Sengpiel2005; @Li2005; @Baker2007], unlike within-eye masking.
+Dynamic fluctuations in interocular suppression are a key feature of binocular rivalry [@Wilson2003; @Alais2010], for which autism-related differences have also been reported [@Robertson2013].
+
+Atypical sensory experience is widely reported by individuals on the autism spectrum [@MacLennan2022; @Simmons2009], but the causal mechanisms remain unclear.
 Typical issues include hypersensitivity to intense stimuli such as loud sounds, bright lights and strong odours or flavours.
-Yet fundamental measures of sensitivity such as visual acuity, contrast sensitivity, and audiometric performance (Rosenhall et al.
-1999) are not consistently different from neurotypical controls.
-Theoretical accounts of sensory differences in autism have long proposed that the balance of inhibition and excitation may be disrupted, and there are isolated results that seem consistent with this.
-For example
-However many other studies have failed to find group differences using tasks that are at least superficially dependent on inhibition, such as...
-
-A comprehensive review of the literature on vision in autism (Simmons et al., 2009)
+Yet fundamental measures of sensitivity such as visual acuity [@Tavassoli2011], contrast sensitivity [@Koh2010], and audiometric performance [@Rosenhall1999] are not consistently different from neurotypical controls.
+Theoretical accounts of sensory differences in autism have long proposed that the balance of inhibition and excitation may be disrupted [@Rubenstein2003; @Rosenberg2015], and there are isolated results that appear consistent with this.
+For example neural measures of surround suppression are weaker in autism [@Schallmo2020], binocular rivalry is slower [@Robertson2013] and orientation discrimination performance is better [@Dickinson2014].
+Conversely, other studies have failed to find group differences using paradigms that should be equally dependent on inhibition, such as orientation repulsion [@VandeCruys2018], repetition suppression [@Utzerath2018] and psychophysical measures of surround suppression [@Sandhu2020].
+The evidence for atypical inhibition in autism is therefore currently inconclusive.
 
 Our recent work has identified a potential autism-related difference in gain control using steady-state EEG methods.
-Vilidaite et al.
-(2018) measured contrast response functions for flickering stimuli in a large group of neurotypical adults, who were split by their autism quotient (AQ; Baron-Cohen et al., 2001) score.
+@Vilidaite2018 measured contrast response functions for flickering stimuli in a large group of neurotypical adults, who were split by their autism quotient [AQ, see @Baron-Cohen2001] score.
 The responses were comparable between high and low AQ groups at the flicker frequency of the stimulus.
@@
 This effect was replicated in an independent sample of 12 adults with an autism diagnosis (compared with neurotypical controls).
-Because second harmonic responses are caused by nonlinear interactions in the visual system (they are absent in a linear system), this potentially implicates differences in divisive suppression in autism.
-Furthermore, there appears to be a developmental trajectory, as autistic children tested as part of the same study (Vilidaite et al., 2018) showed weaker responses at both the first and second harmonic frequencies.
-
-Suppression itself is not a single process.
-Multiple suppressive pathways have been identified in the visual system, including between stimuli differing in orientation, eye-of-origin and spatial position.
-At present there is evidence of normalization reweighting between stimuli of orthogonal orientations (Aschner, 2018), and adjacent spatial positions (Yiltiz, 2020).
-We also wondered if interocular suppression might be subject to reweighting, and if there are differences in the dynamics across pathways.
-This is possible, given that suppression within and between the eyes has different spatiotemporal tuning (Meese & Baker, 2009), and dichoptic masking can be reduced by adapting to the mask (Baker, 2007 and other studies), unlike within-eye masking.
-Dynamic fluctuations in interocular suppression are a feature of binocular rivalry (Wilson, 2003; Alais et al., 2006), for which differences in autism have also been reported (Robertson).
-
-We hypothesised that normalization reweighting might differ as a function of autistic traits.
+Because second harmonic responses are caused by nonlinear interactions in the visual system (they are absent in a linear system), and divisive suppression is a nonlinearity, this potentially implicates differences in suppression in autism.
+Furthermore, there appears to be a developmental trajectory, as autistic children tested as part of the same study [@Vilidaite2018] showed weaker responses at both the first and second harmonic frequencies.
+
+In this paper we perform a time-course analysis of a previously published EEG data set, and report two novel pre-registered experiments using EEG and MEG.
+Our data show that suppression increases substantially during the first 2-5 seconds following stimulus onset, for both monocular and dichoptic masks.
+Source localisation of MEG data indicate that the reweighting is present as early as primary visual cortex (V1).
+We also hypothesised that normalization reweighting might differ as a function of autistic traits.
 The relative novelty of the reweighting framework could explain why any differences have not previously been detected, and why the literature on inhibition in autism is relatively inconclusive.
-In this paper we perform a time-course analysis of a previously published EEG data set, and report two novel pre-registered experiments using EEG and MEG.
-Our data show that suppression increases substantially during the first 6 seconds after stimulus onset, for both monocular and dichoptic masks.
-The timecourse of reweighting is slower in ventral brain regions, and more rapid in dorsal parts of the visual pathway.
-Autism ...
-
-## Results
-
-We began by reanalysing data from a steady-state visually evoked potential (SSVEP) experiment reported by Vilidaite et al (2018).
-Participants viewed arrays of flickering gratings of varying contrasts.
-In some conditions a single grating orientation was present flickering at 7Hz, whereas in other conditions a high contrast 'mask' was added at right angles to the target gratings, and flickering at 5Hz.
-The left panel of Figure \@ref(fig:Pilotdata)a shows contrast response functions with and without the mask - the presence of the mask reduces the 7Hz response to the target (blue squares are below the black circles).
-Similarly, the right panel of Figure \@ref(fig:Pilotdata)a shows that the 5Hz response to the mask was itself suppressed by the presence of high contrast targets (note that the data from the mask conditions were not reported by Vilidaite et al.).
-At both frequencies, responses were localised to the occipital pole (see insets).
-
-We then performed a timecourse analysis, in which we analysed each 11-second trial using a sliding 1-second time window.
-Figure \@ref(fig:Pilotdata)c shows the response at the target frequency (7Hz) to a single stimulus of 32% contrast (black), and the response at 7Hz when the mask is added (blue).
-Analogous responses are shown at three other frequencies - the mask frequency (5Hz), and the second harmonics of both target and mask frequencies (14Hz, 10Hz), at which strong responses were also found (see spectra in Figure \@ref(fig:Pilotdata)b).
-The reduction in signal strength when the mask component is added illustrates the masking effect.
-Taking the ratio of the two timecourses to calculate a masking index reveals that masking increases steeply during the first two seconds of stimulus presentation, and then plateaus for several seconds (blue trace in Figure \@ref(fig:Pilotdata)d).
-A similar pattern is observed at 5Hz (red trace in Figure \@ref(fig:Pilotdata)d), with the increase continuing for around four seconds, as well as at the second harmonics.
-The black trace shows the average masking ratio across all four frequencies, which rises steeply for just over two seconds, mor gradually for a further two seconds, and then stays approximately constant.
+However we did not find convincing support for this hypothesis.
+
+# Results
 
@@
 
+earlydata <- meanindices*0
+latedata <- meanindices*0
+earlydata[,1:(dim(meanindices)[2]-(timeoffset/2))] <- meanindices[,1:(dim(meanindices)[2]-(timeoffset/2))]
+earlydata[,1:(timeoffset/2)] <- 0
+latedata[,(1+(timeoffset/2)):(dim(meanindices)[2])] <- meanindices[,1:(dim(meanindices)[2]-(timeoffset/2))]
+latedata[1:dim(meanindices)[1],(dim(meanindices)[2])+(1-(timeoffset/2)):0] <- 0
+
+if (nbootstraps>0){clustout <- clustercorrect(earlydata,latedata,testtype=4,paired=TRUE)}
+
 EEGmaskSE[1,] <- apply(20*log10(abs(EEGtimecourse[,1,1,])/abs(EEGtimecourse[,1,3,])),2,sd)/sqrt(nsubjs)
@@
 legend(3,-1.4,c('Mean'),lwd=6,col=colpal[1],bty='n')
+
+  if (nbootstraps>0){
+    for (n in 1:clustout$nclusters){
+      temp <- unlist(clustout$clusterpoints[n])
+      lines(times[temp[c(1,length(temp))]]-((timeoffset/2)/1000),c(5.5, 5.5),lwd=3)
+    }
+  }
 
@@
 
-  pdf('temp/figures/Fig2.pdf', bg="transparent", height = 6, width = 16)
+  pdf('temp/figures/Fig1.pdf', bg="transparent", height = 6, width = 16)
   par(mar=c(0.1,0.1,0.1,0.1))
@@
 
+load('temp/Pilotsummary.RData')
+
+targetcond <- NULL
+maskcond <- NULL
+subj <- NULL
+targetamp <- NULL
+maskamp <- NULL
+i <- 0
+for (s in 1:100){
+  for (cond in 1:14){
+    i <- i + 1
+    subj[i] <- s
+    targetcond[i] <- ((cond-1) %% 7) + 1
+    maskcond[i] <- ceiling(cond/7)
+    targetamp[i] <- abs(EEGallconds[s,1,cond])
+    maskamp[i] <- abs(EEGallconds[s,2,cond])
+  }
+}
+anovadata <- data.frame(subj,targetcond,maskcond,targetamp,maskamp)
+anovadata$subj <- as.factor(anovadata$subj)
+anovadata$targetcond <- as.factor(anovadata$targetcond)
+anovadata$maskcond <- as.factor(anovadata$maskcond)
+
+maskinganova1 <- ezANOVA(anovadata, dv=targetamp, wid=subj, within=c(targetcond,maskcond))
+
+anovadataM <- subset(anovadata,maskcond==2)
+maskinganova2 <- ezANOVA(anovadataM, dv=maskamp, wid=subj, within=targetcond)
+gg <- maskinganova2$`Sphericity Corrections`$GGe
+
 ```
+
+We began by reanalysing data from a steady-state visually evoked potential (SSVEP) experiment reported by @Vilidaite2018.
+Participants viewed arrays of flickering gratings of varying contrasts.
+In some conditions a single grating orientation was present flickering at 7Hz, whereas in other conditions a high contrast 'mask' was added at right angles to the target gratings, and flickering at 5Hz.
+The left panel of Figure \@ref(fig:Pilotdata)a shows contrast response functions with and without the mask - the presence of the mask reduces the 7Hz response to the target (blue squares are below the black circles; significant main effect of mask contrast, F(1,99) = `r round(maskinganova1$ANOVA$F[2],digits=2)`, \emph{p} < 0.001).
+Similarly, the right panel of Figure \@ref(fig:Pilotdata)a shows that the 5Hz response to the mask was itself suppressed by the presence of high contrast targets (main effect of target contrast on the mask response, F(`r round(maskinganova2$ANOVA$DFn*gg,digits=2)`,`r round(maskinganova2$ANOVA$DFd*gg,digits=2)`) = `r round(maskinganova2$ANOVA$F,digits=2)`, \emph{p} < 0.001; note that the data from the masking conditions were not reported by @Vilidaite2018).
+At both frequencies, responses were localised to the occipital pole (see insets).
 
@@
 Panel (a) shows contrast response functions at the target frequency (7Hz, left) and the mask frequency (5Hz, right).
-Insets show the distribution of activity across the scalp, with points marking electrodes Oz, POz, O1 and O2.
+Insets show the distribution of activity across the scalp, with points marking the electrodes over which signals were averaged (Oz, POz, O1 and O2).
 Panel (b) shows Fourier spectra for the single component stimuli and their combination (plaid).
@@
 Panel (d) shows the timecourse of suppression at each frequency (7Hz, 5Hz, 14Hz, 10Hz) and their average (black curve).
+Points around y = 1.8 indicate a significantly increasing ratio.
 Error bars in panel (a) and shaded regions in panels (c,d) indicate ±1SE, and grey rectangles indicate the timing of stimulus presentation.
-The larger symbols in panel (a) indicate conditions used for subsequent analyses.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('temp/figures/Fig2.pdf')
+The larger symbols in panel (a) indicate the conditions used for subsequent analyses.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('temp/figures/Fig1.pdf')
 
 ```
+
+We then performed a timecourse analysis, in which we analysed each 11-second trial using a sliding 1-second time window.
+The top panel of Figure \@ref(fig:Pilotdata)c shows the response at the target frequency (7Hz) to a single stimulus of 32% contrast (black), and the response at 7Hz when the 32% contrast mask is added (blue).
+Analogous responses are shown at three other frequencies - the mask frequency (5Hz), and the second harmonics of both target and mask frequencies (14Hz, 10Hz), at which strong responses were also found (see spectra in Figure \@ref(fig:Pilotdata)b).
+The reduction in signal strength when the mask component is added illustrates the masking effect.
+
+Taking the ratio of the two timecourses to calculate a masking index reveals that at 7Hz masking increases steeply during the first two seconds of stimulus presentation, and then plateaus for several seconds (blue trace in Figure \@ref(fig:Pilotdata)d).
+A similar pattern is observed at 5Hz (red trace in Figure \@ref(fig:Pilotdata)d), as well as at the second harmonics, with some variability in the timecourse across frequencies; for example at 5Hz suppression peaks at around 4 seconds.
+The black trace shows the average masking ratio across all four frequencies, which rises steeply for just over two seconds and then stays approximately constant until stimulus offset.
+We conducted cluster-corrected t-tests between ratios separated by `r timeoffset`ms, testing for an increase in suppression ratio across time (i.e.
+a one-sided test).
+Points at y = 1.8 in Figure \@ref(fig:Pilotdata)d indicate time points where the ratio is significantly increasing, and occur mostly during the first 2 seconds of stimulus presentation.
 
@@
 We therefore preregistered two new experiments (see https://osf.io/4qudc) to investigate these effects in greater detail.
-These had a similar overall design to the Vilidaite study, with some small changes intended to optimise the study (see Methods).
-The key differences were that we used shorter trials (because there were few changes in the latter part of the trials shown in Figure \@ref(fig:Pilotdata)), and also focussed all trials into a smaller number of conditions, such that each participant contributed 48 repetitions (288 seconds of data) to each of 4 conditions.
-
-Figure \@ref(fig:EEGdata) summarises the results of our EEG experiment testing a further 100 neurotypical adults.
-Averaged EEG waveforms showed a strong oscillatory component at each of the two stimulus flicker frequencies (Figure \@ref(fig:EEGdata)a), which slightly lagged the driving signal.
-Signals were well-isolated in the Fourier domain (Figure \@ref(fig:EEGdata)b), and localised to occipital electrodes.
-The timecourse at both frequencies showed an initial onset transient, and was then relatively stable for the 6 seconds of stimulus presentation (Figure \@ref(fig:EEGdata)c,d).
-Responses were weaker in the two masking conditions, and the ratio of target only to target + mask conditions increased over time (Figure \@ref(fig:EEGdata)e,f) for both mask types.
-At 5Hz the increase in masking continued over the first 5 seconds of stimulus presentation (Figure \@ref(fig:EEGdata)e), whereas at 7Hz the increase occurred mostly during the first second after onset (Figure \@ref(fig:EEGdata)f), consistent with the pilot data (see Figure \@ref(fig:Pilotdata)).
+These had a similar overall design to the @Vilidaite2018 study, with some small changes intended to optimise the study (see Methods).
+The key differences were that we used shorter trials (because there were few changes in the latter part of the trials shown in Figure \@ref(fig:Pilotdata)d), and also focussed all trials into a smaller number of conditions, such that each participant contributed 48 repetitions (288 seconds of data) to each of 4 conditions.
 
@@
  }
+
 if (processdata>1){    
@@
 allAQ <- NULL
+allSPQ <- NULL
 for (s in 1:length(d)){
@@
 allAQ[s] <- scoreAQ(qdatasubj[1,5:54]) 
-
-}
-
-save(file='temp/EEGsummary.RData',list=c('allheads5','allheads7','allspec','allwaves','EEGtimecourse5Hz','EEGtimecourse7Hz','electrodes','allAQ'))
- }
-
-if (processdata>0){
+allSPQ[s] <- scoreSPQ(qdatasubj[1,55:146])
+}
+
+save(file='temp/EEGsummary.RData',list=c('allheads5','allheads7','allspec','allwaves','EEGtimecourse5Hz','EEGtimecourse7Hz','electrodes','allAQ','allSPQ'))
+ }
+
 load('temp/EEGsummary.RData')
@@
 
+if (processdata>0){
+
 allwaves[which(allwaves<(-100))] <- 0
@@
 
+earlydataM <- monratios*0
+latedataM <- monratios*0
+earlydataM[,1:(dim(monratios)[2]-(timeoffset/2))] <- monratios[,1:(dim(monratios)[2]-(timeoffset/2))]
+earlydataM[,1:(timeoffset/2)] <- 0
+latedataM[,(1+(timeoffset/2)):(dim(monratios)[2])] <- monratios[,1:(dim(monratios)[2]-(timeoffset/2))]
+latedataM[1:dim(monratios)[1],(dim(monratios)[2])+(1-(timeoffset/2)):0] <- 0
+
+if (nbootstraps>0){clustoutM5 <- clustercorrect(earlydataM,latedataM,testtype=4,paired=TRUE)}
+
+earlydataD <- dichratios*0
+latedataD <- dichratios*0
+earlydataD[,1:(dim(dichratios)[2]-(timeoffset/2))] <- dichratios[,1:(dim(dichratios)[2]-(timeoffset/2))]
+earlydataD[,1:(timeoffset/2)] <- 0
+latedataD[,(1+(timeoffset/2)):(dim(dichratios)[2])] <- dichratios[,1:(dim(dichratios)[2]-(timeoffset/2))]
+latedataD[1:dim(dichratios)[1],(dim(dichratios)[2])+(1-(timeoffset/2)):0] <- 0
+
+if (nbootstraps>0){clustoutD5 <- clustercorrect(earlydataD,latedataD,testtype=4,paired=TRUE)}
+
 EEGmaskindex7 <- matrix(0,nrow=2,ncol=8000)
@@
 
-# pdf("temp/figures/Fig3.pdf", bg="transparent", height = 10, width = 12)
+earlydataM <- monratios*0
+latedataM <- monratios*0
+earlydataM[,1:(dim(monratios)[2]-(timeoffset/2))] <- monratios[,1:(dim(monratios)[2]-(timeoffset/2))]
+earlydataM[,1:(timeoffset/2)] <- 0
+latedataM[,(1+(timeoffset/2)):(dim(monratios)[2])] <- monratios[,1:(dim(monratios)[2]-(timeoffset/2))]
+latedataM[1:dim(monratios)[1],(dim(monratios)[2])+(1-(timeoffset/2)):0] <- 0
+
+if (nbootstraps>0){clustoutM7 <- clustercorrect(earlydataM,latedataM,testtype=4,paired=TRUE)}
+
+earlydataD <- dichratios*0
+latedataD <- dichratios*0
+earlydataD[,1:(dim(dichratios)[2]-(timeoffset/2))] <- dichratios[,1:(dim(dichratios)[2]-(timeoffset/2))]
+earlydataD[,1:(timeoffset/2)] <- 0
+latedataD[,(1+(timeoffset/2)):(dim(dichratios)[2])] <- dichratios[,1:(dim(dichratios)[2]-(timeoffset/2))]
+latedataD[1:dim(dichratios)[1],(dim(dichratios)[2])+(1-(timeoffset/2)):0] <- 0
+
+if (nbootstraps>0){clustoutD7 <- clustercorrect(earlydataD,latedataD,testtype=4,paired=TRUE)}
+
+# pdf("temp/figures/Fig2.pdf", bg="transparent", height = 10, width = 12)
 # 
@@
 }
+text(6,0.55,'5Hz',cex=2)
+  legend(1.25,0.2,c('Baseline','Monocular','Dichoptic'),lty=1,lwd=2,col=colpal[1:3],box.lwd=2)
+dev.off()
+
+postscript("timecourse3.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,7,0,0.6)
+ticklocsy <- seq(0,0.6,0.1)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = ticklocsx, side = 1, at=ticklocsx)
+mtext(text = ticklocsy, side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,6,6,0),c(-0.022,-0.022,0.02,0.02),border=NA,col=rgb(0.5,0.5,0.5))
+
+if (plotsmoothed==0){
+polygon(times[c(1:8000,8000:1)],c(EEGmeantime7Hz[2,]+EEGSEtime7Hz[2,],EEGmeantime7Hz[2,8000:1]-EEGSEtime7Hz[2,8000:1]),col=colpal[1],border=NA)
+polygon(times[c(1:8000,8000:1)],c(EEGmeantime7Hz[3,]+EEGSEtime7Hz[3,],EEGmeantime7Hz[3,8000:1]-EEGSEtime7Hz[3,8000:1]),col=colpal[2],border=NA)
+polygon(times[c(1:8000,8000:1)],c(EEGmeantime7Hz[4,]+EEGSEtime7Hz[4,],EEGmeantime7Hz[4,8000:1]-EEGSEtime7Hz[4,8000:1]),col=colpal[3],border=NA)
+
+# lines(times,EEGmeantime7Hz[1,],lwd=2,col=colpal[1])
+lines(times,EEGmeantime7Hz[2,],lwd=2,col=colpal[1])
+lines(times,EEGmeantime7Hz[3,],lwd=2,col=colpal[2])
+lines(times,EEGmeantime7Hz[4,],lwd=2,col=colpal[3])
+}
+if (plotsmoothed==1){
+
+spl7bU <- smooth.spline(times,EEGmeantime7Hz[2,]+EEGSEtime7Hz[2,],df=20)
+spl7bL <- smooth.spline(times,EEGmeantime7Hz[2,]-EEGSEtime7Hz[2,],df=20)
+polygon(times[c(1:8000,8000:1)],c(spl7bU$y,spl7bL$y[8000:1]),col=colpal[1],border=NA)
+
+spl7cU <- smooth.spline(times,EEGmeantime7Hz[3,]+EEGSEtime7Hz[3,],df=20)
+spl7cL <- smooth.spline(times,EEGmeantime7Hz[3,]-EEGSEtime7Hz[3,],df=20)
+polygon(times[c(1:8000,8000:1)],c(spl7cU$y,spl7cL$y[8000:1]),col=colpal[2],border=NA)
+
+spl7dU <- smooth.spline(times,EEGmeantime7Hz[4,]+EEGSEtime7Hz[4,],df=20)
+spl7dL <- smooth.spline(times,EEGmeantime7Hz[4,]-EEGSEtime7Hz[4,],df=20)
+polygon(times[c(1:8000,8000:1)],c(spl7dU$y,spl7dL$y[8000:1]),col=colpal[3],border=NA)
+
+# spl7a <- smooth.spline(times,EEGmeantime7Hz[1,],df=20)
+# lines(spl7a$x,spl7a$y,col=colpal[1],lwd=2)
+spl7b <- smooth.spline(times,EEGmeantime7Hz[2,],df=20)
+lines(spl7b$x,spl7b$y,col=colpal[1],lwd=2)
+spl7c <- smooth.spline(times,EEGmeantime7Hz[3,],df=20)
+lines(spl7c$x,spl7c$y,col=colpal[2],lwd=2)
+spl7d <- smooth.spline(times,EEGmeantime7Hz[4,],df=20)
+lines(spl7d$x,spl7d$y,col=colpal[3],lwd=2)
+}
+text(6,0.55,'7Hz',cex=2)
 
@@
 polygon(times[c(1:8000,8000:1)],c(EEGmaskindex5[1,]+EEGmaskindexSE5[1,],EEGmaskindex5[1,8000:1]-EEGmaskindexSE5[1,8000:1]),col=colpal[2],border=NA)
-polygon(times[c(1:8000,8000:1)],c(EEGmaskindex5[2,]+EEGmaskindexSE5[2,],EEGmaskindex5[2,8000:1]-EEGmaskindexSE5[2,8000:1]),col=colpal[3],border=NA)
+polygon(times[c(1:8000,8000:1)],c(EEGmaskindex5[2,]+EEGmaskindexSE5[2,],EEGmaskindex5[1,8000:1]-EEGmaskindexSE5[2,8000:1]),col=colpal[3],border=NA)
 
@@
 
-dev.off()
-
-postscript("timecourse3.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
-
-plotlims <- c(-1,7,0,0.6)
-ticklocsy <- seq(0,0.6,0.1)    # locations of tick marks on y axis
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklocsx, side = 1, at=ticklocsx)
-mtext(text = ticklocsy, side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
-title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-polygon(c(0,6,6,0),c(-0.022,-0.022,0.02,0.02),border=NA,col=rgb(0.5,0.5,0.5))
-
-if (plotsmoothed==0){
-polygon(times[c(1:8000,8000:1)],c(EEGmeantime7Hz[2,]+EEGSEtime7Hz[2,],EEGmeantime7Hz[2,8000:1]-EEGSEtime7Hz[2,8000:1]),col=colpal[1],border=NA)
-polygon(times[c(1:8000,8000:1)],c(EEGmeantime7Hz[3,]+EEGSEtime7Hz[3,],EEGmeantime7Hz[3,8000:1]-EEGSEtime7Hz[3,8000:1]),col=colpal[2],border=NA)
-polygon(times[c(1:8000,8000:1)],c(EEGmeantime7Hz[4,]+EEGSEtime7Hz[4,],EEGmeantime7Hz[4,8000:1]-EEGSEtime7Hz[4,8000:1]),col=colpal[3],border=NA)
-
-# lines(times,EEGmeantime7Hz[1,],lwd=2,col=colpal[1])
-lines(times,EEGmeantime7Hz[2,],lwd=2,col=colpal[1])
-lines(times,EEGmeantime7Hz[3,],lwd=2,col=colpal[2])
-lines(times,EEGmeantime7Hz[4,],lwd=2,col=colpal[3])
-}
-if (plotsmoothed==1){
-
-spl7bU <- smooth.spline(times,EEGmeantime7Hz[2,]+EEGSEtime7Hz[2,],df=20)
-spl7bL <- smooth.spline(times,EEGmeantime7Hz[2,]-EEGSEtime7Hz[2,],df=20)
-polygon(times[c(1:8000,8000:1)],c(spl7bU$y,spl7bL$y[8000:1]),col=colpal[1],border=NA)
-
-spl7cU <- smooth.spline(times,EEGmeantime7Hz[3,]+EEGSEtime7Hz[3,],df=20)
-spl7cL <- smooth.spline(times,EEGmeantime7Hz[3,]-EEGSEtime7Hz[3,],df=20)
-polygon(times[c(1:8000,8000:1)],c(spl7cU$y,spl7cL$y[8000:1]),col=colpal[2],border=NA)
-
-spl7dU <- smooth.spline(times,EEGmeantime7Hz[4,]+EEGSEtime7Hz[4,],df=20)
-spl7dL <- smooth.spline(times,EEGmeantime7Hz[4,]-EEGSEtime7Hz[4,],df=20)
-polygon(times[c(1:8000,8000:1)],c(spl7dU$y,spl7dL$y[8000:1]),col=colpal[3],border=NA)
-
-# spl7a <- smooth.spline(times,EEGmeantime7Hz[1,],df=20)
-# lines(spl7a$x,spl7a$y,col=colpal[1],lwd=2)
-spl7b <- smooth.spline(times,EEGmeantime7Hz[2,],df=20)
-lines(spl7b$x,spl7b$y,col=colpal[1],lwd=2)
-spl7c <- smooth.spline(times,EEGmeantime7Hz[3,],df=20)
-lines(spl7c$x,spl7c$y,col=colpal[2],lwd=2)
-spl7d <- smooth.spline(times,EEGmeantime7Hz[4,],df=20)
-lines(spl7d$x,spl7d$y,col=colpal[3],lwd=2)
+  if (nbootstraps>0){
+    for (n in 1:clustoutM5$nclusters){
+      temp <- unlist(clustoutM5$clusterpoints[n])
+      lines(times[temp[c(1,length(temp))]],c(-2, -2),lwd=3,col=colpal[2])
+    }
+        for (n in 1:clustoutD5$nclusters){
+      temp <- unlist(clustoutD5$clusterpoints[n])
+      lines(times[temp[c(1,length(temp))]],c(-1.5, -1.5),lwd=3,col=colpal[3])
+    }
   }
@@
 lines(L$x,L$y,col=colpal[3],lwd=2)
+}
+
+  if (nbootstraps>0){
+    for (n in 1:clustoutM7$nclusters){
+      temp <- unlist(clustoutM7$clusterpoints[n])
+      lines(times[temp[c(1,length(temp))]],c(-2, -2),lwd=3,col=colpal[2])
+    }
+        for (n in 1:clustoutD7$nclusters){
+      temp <- unlist(clustoutD7$clusterpoints[n])
+      lines(times[temp[c(1,length(temp))]],c(-1.5, -1.5),lwd=3,col=colpal[3])
+    }
   }
@@
 
-  pdf('temp/figures/Fig3.pdf', bg="transparent", height = 6, width = 15)
+  pdf('temp/figures/Fig2.pdf', bg="transparent", height = 6, width = 15)
   par(mar=c(0.1,0.1,0.1,0.1))
@@
 
+targetcond <- NULL
+maskcond <- NULL
+subj <- NULL
+targetamp <- NULL
+maskamp <- NULL
+i <- 0
+for (s in 1:100){
+
+  if ((isincluded[1,s]*isincluded[3,s]*isincluded[4,s])==1){
+    i <- i + 1
+    subj[i] <- s
+    targetcond[i] <- 5
+    maskcond[i] <- 1
+    targetamp[i] <- (allspec[s,1,duration*targetF])
+
+    i <- i + 1
+    subj[i] <- s
+        targetcond[i] <- 5
+    maskcond[i] <- 2
+    targetamp[i] <- (allspec[s,3,duration*targetF])
+
+    i <- i + 1
+    subj[i] <- s
+        targetcond[i] <- 5
+    maskcond[i] <- 3
+    targetamp[i] <- (allspec[s,4,duration*targetF])
+  }
+  if ((isincluded[2,s]*isincluded[3,s]*isincluded[4,s])==1){  
+    i <- i + 1
+    subj[i] <- s
+    targetcond[i] <- 7
+    maskcond[i] <- 1
+    targetamp[i] <- (allspec[s,2,duration*maskF])
+
+    i <- i + 1
+    subj[i] <- s
+        targetcond[i] <- 7
+    maskcond[i] <- 2
+    targetamp[i] <- (allspec[s,3,duration*maskF])
+
+    i <- i + 1
+    subj[i] <- s
+        targetcond[i] <- 7
+    maskcond[i] <- 3
+    targetamp[i] <- (allspec[s,4,duration*maskF])
+  }
+}
+alldata <- data.frame(subj,targetcond,maskcond,targetamp)
+alldata$subj <- as.factor(alldata$subj)
+alldata$targetcond <- as.factor(alldata$targetcond)
+alldata$maskcond <- as.factor(alldata$maskcond)
+
+all5 <- subset(alldata,targetcond==5)
+all7 <- subset(alldata,targetcond==7)
+
+baseline5 <- subset(all5,maskcond==1)
+baseline7 <- subset(all7,maskcond==1)
+mon5 <- subset(all5,maskcond==2)
+mon7 <- subset(all7,maskcond==2)
+dich5 <- subset(all5,maskcond==3)
+dich7 <- subset(all7,maskcond==3)
+
+# tsqc.test(baseline7$targetamp,mon7$targetamp,paired=TRUE)
+# tsqc.test(baseline7$targetamp,dich7$targetamp,paired=TRUE)
+# tsqc.test(mon7$targetamp,dich7$targetamp,paired=TRUE)
+# 
+# tsqc.test(baseline5$targetamp,mon5$targetamp,paired=TRUE)
+# tsqc.test(baseline5$targetamp,dich5$targetamp,paired=TRUE)
+# tsqc.test(mon5$targetamp,dich5$targetamp,paired=TRUE)
+
+t7a <- t.test(abs(baseline7$targetamp),abs(mon7$targetamp),paired=TRUE)
+t7b <- t.test(abs(baseline7$targetamp),abs(dich7$targetamp),paired=TRUE)
+t7c <- t.test(abs(mon7$targetamp),abs(dich7$targetamp),paired=TRUE)
+
+t5a <- t.test(abs(baseline5$targetamp),abs(mon5$targetamp),paired=TRUE)
+t5b <- t.test(abs(baseline5$targetamp),abs(dich5$targetamp),paired=TRUE)
+t5c <- t.test(abs(mon5$targetamp),abs(dich5$targetamp),paired=TRUE)
+
 ```
 
-```{r EEGdata, fig.cap="Summary of EEG results for N=100 neurotypical participants.
+Figure \@ref(fig:EEGdata) summarises the results of our EEG experiment testing a further 100 adult participants.
+Averaged EEG waveforms showed a strong oscillatory component at each of the two stimulus flicker frequencies (Figure \@ref(fig:EEGdata)a), which slightly lagged the driving signal.
+Signals were well-isolated in the Fourier domain (Figure \@ref(fig:EEGdata)b), and localised to occipital electrodes.
+Responses at 7Hz were weaker in the two masking conditions, showing significant changes in response amplitude for both the monocular (\emph{t} = `r round(t7a$statistic,digits=2)`, \emph{df} = `r t7a$parameter`, \emph{p} < 0.001) and dichoptic (\emph{t} = `r round(t7b$statistic,digits=2)`, \emph{df} = `r t7b$parameter`, \emph{p} < 0.001) masks.
+Dichoptic masking was significantly stronger than monocular masking (\emph{t} = `r round(t7c$statistic,digits=2)`, \emph{df} = `r t7c$parameter`, \emph{p} < 0.001), and a similar pattern was evident at 5Hz.
+
+```{r EEGdata, fig.cap="Summary of EEG results for N=100 adult participants.
 Panel (a) shows scalp topographies and averaged waveforms for 5Hz (top) and 7Hz (bottom) stimuli.
@@
 Panels (c,d) show timecourses at each frequency for the baseline condition (black), and the monocular (blue) and dichoptic (red) masking conditions.
-Panels (e,f) show suppression ratios as a function of time for each mask type.
-Light grey rectangles indicate the period of stimulus presentation.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('temp/figures/Fig3.pdf')
+Panels (e,f) show suppression ratios as a function of time for each mask type, with points around y = 0.8 indicating a significantly increasing ratio.
+Shaded regions in panels (c-f) span ±1SE across participants, and light grey rectangles indicate the period of stimulus presentation.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('temp/figures/Fig2.pdf')
 
@@
 
-Next we repeated the experiment on 20 participants using a 248-channel whole-head cryogenic MEG system.
-Half of the participants had a diagnosis of autism, and the remainder were age and gender-matched controls.
-Source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm (reference) showed strong localisation of steady-state signals at the occipital pole (see Figure \@ref(fig:MEGdata)a,b).
-
-Responses across V1 showed a similar timecourse to those of the EEG experiment at both frequencies (Figure 4c,d), and showed increasing suppression during the first 4 seconds of stimulus presentation (Figure 4e,f).
+The timecourse at both flicker frequencies showed an initial onset transient, and was then relatively stable for the 6 seconds of stimulus presentation (Figure \@ref(fig:EEGdata)c,d).
+The ratio of target only to target + mask conditions increased over time (Figure \@ref(fig:EEGdata)e,f) for both mask types.
+At 5Hz the increase in masking continued over the first 5 seconds of stimulus presentation (Figure \@ref(fig:EEGdata)e; points at y = 0.8 indicate significantly increasing suppression), whereas at 7Hz the increase occurred primarily during the first second after onset (Figure \@ref(fig:EEGdata)f).
+These differences across frequency are consistent with the pilot data (see Figure \@ref(fig:Pilotdata)d).
+Both monocular and dichoptic masks produced similar timecourses of suppression.
+Overall, this second study confirmed that normalization increases during the first few seconds of a steady-state trial, and extends this finding to dichoptic mask arrangements.
 
@@
 
-nareas <- 7
 samplerate <- 1001
@@
     mindex <- 1 + maskF*(binwidth/samplerate)
-MEGareacols <- cols25(8)[c(1:5,8,7)]
 
@@
 
-d <- dir(path = 'temp/MEGtrialsWang/', pattern = '*alltrials.mat', full.names=TRUE)
-d2 <- dir(path = 'temp/MEGtrialsWang/', pattern = '*alltrials.mat', full.names=FALSE)
-
-MEGtimecourse5Hz <- array(0,dim=c(length(d),nareas,4,8008))
-MEGtimecourse7Hz <- array(0,dim=c(length(d),nareas,4,8008))
+  d <- dir(path = 'temp/wang/', pattern = '*alltrialsFullV1.mat', full.names=TRUE)
+  d2 <- dir(path = 'temp/wang/', pattern = '*alltrialsFullV1.mat', full.names=FALSE)
+
+  MEGtimecourse5Hz <- array(0,dim=c(length(d),4,8008))
+  MEGtimecourse7Hz <- array(0,dim=c(length(d),4,8008))
   # allwaves <- array(0,dim=c(length(d),4,9009))
-allspec <- array(0,dim=c(length(d),nareas,4,duration*20))
+  allspec <- array(0,dim=c(length(d),4,duration*20))
   allRnos <- NULL
@@
     data <- readMat(d[s])
-  for (area in 1:nareas){
+
       for (cond in 1:4){
-    temp <- colMeans(data$alltrials[area,cond,1:data$trialcounter[1,cond],],na.rm=TRUE)
+        temp <- colMeans(data$alltrials[cond,1:data$trialcounter[1,cond],],na.rm=TRUE)
         nainds <- which(is.na(temp))   # find occasional NaN values in the waveform
@@
         spec <- fft(temp[1501:7500])/6000
-    allspec[s,area,cond,] <- spec[1+(1:(duration*20))]
+        allspec[s,cond,] <- spec[1+(1:(duration*20))]
 
@@
         }
-    MEGtimecourse5Hz[s,area,cond,] <- fspec1
-    MEGtimecourse7Hz[s,area,cond,] <- fspec2
-
-  }
-
-}
-}
-
-save(file='temp/MEGsummary.RData',list=c('allspec','MEGtimecourse5Hz','MEGtimecourse7Hz','allRnos'))
+        MEGtimecourse5Hz[s,cond,] <- fspec1
+        MEGtimecourse7Hz[s,cond,] <- fspec2
+
+    }
+  }
+
+  save(file='temp/MEGsummaryV1.RData',list=c('allspec','MEGtimecourse5Hz','MEGtimecourse7Hz','allRnos'))
+
 }
@@
 if (processdata>0){
-load('temp/MEGsummary.RData')
-
-isincluded <- array(1, dim=c(nareas,4,dim(allspec)[1]))
-for (area in 1:nareas){
+  load('temp/MEGsummaryV1.RData')
+
+  isincluded <- array(1, dim=c(4,dim(allspec)[1]))
     for (cond in 1:4){
@@
       # so we don't need to add 1 to the index
-      tempxy <- data.frame(Re(allspec[,area,cond,duration*targetF]),Im(allspec[,area,cond,duration*targetF]))
+      tempxy <- data.frame(Re(allspec[,cond,duration*targetF]),Im(allspec[,cond,duration*targetF]))
       D5 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
-      tempxy <- data.frame(Re(allspec[,area,cond,duration*maskF]),Im(allspec[,area,cond,duration*maskF]))      
+      tempxy <- data.frame(Re(allspec[,cond,duration*maskF]),Im(allspec[,cond,duration*maskF]))      
       D7 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))      
-      isincluded[area,cond,which(D5>3)] <- 0
-      isincluded[area,cond,which(D7>3)] <- 0
+      isincluded[cond,which(D5>3)] <- 0
+      isincluded[cond,which(D7>3)] <- 0
       for (s in 1:20){
-     if (max(abs(MEGtimecourse5Hz[s,area,cond,]))>5){isincluded[area,cond,s] <- 0}
-   }   
-}
-}
-
-MEGmeantime5Hz <- array(0,dim=c(nareas,4,8008))
-MEGmeantime7Hz <- array(0,dim=c(nareas,4,8008))
-MEGSEtime5Hz <- array(0,dim=c(nareas,4,8008))
-MEGSEtime7Hz <- array(0,dim=c(nareas,4,8008))
-meanspec <- array(0,dim=c(nareas,4,120))
-for (area in 1:nareas){
+        if (max(abs(MEGtimecourse5Hz[s,cond,]))>5){isincluded[cond,s] <- 0}
+      }   
+    }
+
+  MEGmeantime5Hz <- array(0,dim=c(4,8008))
+  MEGmeantime7Hz <- array(0,dim=c(4,8008))
+  MEGSEtime5Hz <- array(0,dim=c(4,8008))
+  MEGSEtime7Hz <- array(0,dim=c(4,8008))
+  meanspec <- array(0,dim=c(4,120))
+
     for (cond in 1:4){
-MEGmeantime7Hz[area,cond,] <- apply(abs(MEGtimecourse7Hz[which(isincluded[area,cond,]==1),area,cond,]),2,mean,na.rm=TRUE)
-MEGmeantime5Hz[area,cond,] <- apply(abs(MEGtimecourse5Hz[which(isincluded[area,cond,]==1),area,cond,]),2,mean,na.rm=TRUE)
-
-MEGSEtime7Hz[area,cond,] <- apply(abs(MEGtimecourse7Hz[which(isincluded[area,cond,]==1),area,cond,]),2,sd,na.rm=TRUE)/sqrt(sum(isincluded[area,cond,]))
-MEGSEtime5Hz[area,cond,] <- apply(abs(MEGtimecourse5Hz[which(isincluded[area,cond,]==1),area,cond,]),2,sd,na.rm=TRUE)/sqrt(sum(isincluded[area,cond,]))
-
-meanspec[area,cond,] <- abs(colMeans(allspec[which(isincluded[area,cond,]==1),area,cond,],na.rm=TRUE))
+      MEGmeantime7Hz[cond,] <- apply(abs(MEGtimecourse7Hz[which(isincluded[cond,]==1),cond,]),2,mean,na.rm=TRUE)
+      MEGmeantime5Hz[cond,] <- apply(abs(MEGtimecourse5Hz[which(isincluded[cond,]==1),cond,]),2,mean,na.rm=TRUE)
+
+      MEGSEtime7Hz[cond,] <- apply(abs(MEGtimecourse7Hz[which(isincluded[cond,]==1),cond,]),2,sd,na.rm=TRUE)/sqrt(sum(isincluded[cond,]))
+      MEGSEtime5Hz[cond,] <- apply(abs(MEGtimecourse5Hz[which(isincluded[cond,]==1),cond,]),2,sd,na.rm=TRUE)/sqrt(sum(isincluded[cond,]))
+
+      meanspec[cond,] <- colMeans(abs(allspec[which(isincluded[cond,]==1),cond,]),na.rm=TRUE)
       # meanwave[area,cond,] <- colMeans(allwaves[which(isincluded[area,cond,]==1),area,cond,],na.rm=TRUE)
     }
-}
-
-MEGmaskindex5 <- array(0, dim=c(nareas,2,8008))
-MEGmaskindexSE5 <- array(0, dim=c(nareas,2,8008))
-MEGmaskindex7 <- array(0, dim=c(nareas,2,8008))
-MEGmaskindexSE7 <- array(0, dim=c(nareas,2,8008))
-for (area in 1:nareas){
-includedboth <- isincluded[area,1,]*isincluded[area,3,]
-monratios <- abs(MEGtimecourse5Hz[which(includedboth==1),area,1,])/abs(MEGtimecourse5Hz[which(includedboth==1),area,3,])
-MEGmaskindex5[area,1,] <- colMeans(20*log10(monratios))
-MEGmaskindexSE5[area,1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
-includedboth <- isincluded[area,1,]*isincluded[area,4,]
-dichratios <- abs(MEGtimecourse5Hz[which(includedboth==1),area,1,])/abs(MEGtimecourse5Hz[which(includedboth==1),area,4,])
-MEGmaskindex5[area,2,] <- colMeans(20*log10(dichratios))
-MEGmaskindexSE5[area,2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
-
-includedboth <- isincluded[area,2,]*isincluded[area,3,]
-monratios <- abs(MEGtimecourse7Hz[which(includedboth==1),area,2,])/abs(MEGtimecourse7Hz[which(includedboth==1),area,3,])
-MEGmaskindex7[area,1,] <- colMeans(20*log10(monratios))
-MEGmaskindexSE7[area,1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
-includedboth <- isincluded[area,2,]*isincluded[area,4,]
-dichratios <- abs(MEGtimecourse7Hz[which(includedboth==1),area,2,])/abs(MEGtimecourse7Hz[which(includedboth==1),area,4,])
-MEGmaskindex7[area,2,] <- colMeans(20*log10(dichratios))
-MEGmaskindexSE7[area,2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
-}
+
+  MEGmaskindex5 <- array(0, dim=c(2,8008))
+  MEGmaskindexSE5 <- array(0, dim=c(2,8008))
+  MEGmaskindex7 <- array(0, dim=c(2,8008))
+  MEGmaskindexSE7 <- array(0, dim=c(2,8008))
+
+    includedboth <- isincluded[1,]*isincluded[3,]
+    monratios <- abs(MEGtimecourse5Hz[which(includedboth==1),1,])/abs(MEGtimecourse5Hz[which(includedboth==1),3,])
+    MEGmaskindex5[1,] <- colMeans(20*log10(monratios))
+    MEGmaskindexSE5[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+    includedboth <- isincluded[1,]*isincluded[4,]
+    dichratios <- abs(MEGtimecourse5Hz[which(includedboth==1),1,])/abs(MEGtimecourse5Hz[which(includedboth==1),4,])
+    MEGmaskindex5[2,] <- colMeans(20*log10(dichratios))
+    MEGmaskindexSE5[2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+
+    earlydataM <- monratios*0
+latedataM <- monratios*0
+earlydataM[,1:(dim(monratios)[2]-(timeoffset/2))] <- monratios[,1:(dim(monratios)[2]-(timeoffset/2))]
+earlydataM[,1:(timeoffset/2)] <- 0
+latedataM[,(1+(timeoffset/2)):(dim(monratios)[2])] <- monratios[,1:(dim(monratios)[2]-(timeoffset/2))]
+latedataM[1:dim(monratios)[1],(dim(monratios)[2])+(1-(timeoffset/2)):0] <- 0
+
+if (nbootstraps>0){clustoutM5 <- clustercorrect(earlydataM,latedataM,testtype=4,paired=TRUE)}
+
+earlydataD <- dichratios*0
+latedataD <- dichratios*0
+earlydataD[,1:(dim(dichratios)[2]-(timeoffset/2))] <- dichratios[,1:(dim(dichratios)[2]-(timeoffset/2))]
+earlydataD[,1:(timeoffset/2)] <- 0
+latedataD[,(1+(timeoffset/2)):(dim(dichratios)[2])] <- dichratios[,1:(dim(dichratios)[2]-(timeoffset/2))]
+latedataD[1:dim(dichratios)[1],(dim(dichratios)[2])+(1-(timeoffset/2)):0] <- 0
+
+if (nbootstraps>0){clustoutD5 <- clustercorrect(earlydataD,latedataD,testtype=4,paired=TRUE)}
+
+    includedboth <- isincluded[2,]*isincluded[3,]
+    monratios <- abs(MEGtimecourse7Hz[which(includedboth==1),2,])/abs(MEGtimecourse7Hz[which(includedboth==1),3,])
+    MEGmaskindex7[1,] <- colMeans(20*log10(monratios))
+    MEGmaskindexSE7[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+    includedboth <- isincluded[2,]*isincluded[4,]
+    dichratios <- abs(MEGtimecourse7Hz[which(includedboth==1),2,])/abs(MEGtimecourse7Hz[which(includedboth==1),4,])
+    MEGmaskindex7[2,] <- colMeans(20*log10(dichratios))
+    MEGmaskindexSE7[2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+
+  earlydataM <- monratios*0
+latedataM <- monratios*0
+earlydataM[,1:(dim(monratios)[2]-(timeoffset/2))] <- monratios[,1:(dim(monratios)[2]-(timeoffset/2))]
+earlydataM[,1:(timeoffset/2)] <- 0
+latedataM[,(1+(timeoffset/2)):(dim(monratios)[2])] <- monratios[,1:(dim(monratios)[2]-(timeoffset/2))]
+latedataM[1:dim(monratios)[1],(dim(monratios)[2])+(1-(timeoffset/2)):0] <- 0
+
+if (nbootstraps>0){clustoutM7 <- clustercorrect(earlydataM,latedataM,testtype=4,paired=TRUE)}
+
+earlydataD <- dichratios*0
+latedataD <- dichratios*0
+earlydataD[,1:(dim(dichratios)[2]-(timeoffset/2))] <- dichratios[,1:(dim(dichratios)[2]-(timeoffset/2))]
+earlydataD[,1:(timeoffset/2)] <- 0
+latedataD[,(1+(timeoffset/2)):(dim(dichratios)[2])] <- dichratios[,1:(dim(dichratios)[2]-(timeoffset/2))]
+latedataD[1:dim(dichratios)[1],(dim(dichratios)[2])+(1-(timeoffset/2)):0] <- 0
+
+if (nbootstraps>0){clustoutD7 <- clustercorrect(earlydataD,latedataD,testtype=4,paired=TRUE)}
 
@@
 
-plotlims <- c(-1,7,0,0.6)
+  plotlims <- c(-1,7,0,3)
   ticklocsx <- -1:7    # locations of tick marks on x axis
-ticklocsy <- seq(0,0.6,0.1)    # locations of tick marks on y axis
+  ticklocsy <- seq(0,3,1)    # locations of tick marks on y axis
   plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
@@
 
-polygon(c(0,6,6,0),c(-0.022,-0.022,0.02,0.02),border=NA,col=rgb(0.5,0.5,0.5))
+  polygon(c(0,6,6,0),c(-0.08,-0.08,0.1,0.1),border=NA,col=rgb(0.5,0.5,0.5))
 
   if (plotsmoothed==0){
-polygon(times[c(1:8008,8008:1)],10*c(MEGmeantime5Hz[1,]+MEGSEtime5Hz[1,],MEGmeantime5Hz[1,8008:1]-MEGSEtime5Hz[1,8008:1]),col=colpal[1],border=NA)
-polygon(times[c(1:8008,8008:1)],10*c(MEGmeantime5Hz[3,]+MEGSEtime5Hz[3,],MEGmeantime5Hz[3,8008:1]-MEGSEtime5Hz[3,8008:1]),col=colpal[2],border=NA)
-polygon(times[c(1:8008,8008:1)],10*c(MEGmeantime5Hz[4,]+MEGSEtime5Hz[4,],MEGmeantime5Hz[4,8008:1]-MEGSEtime5Hz[4,8008:1]),col=colpal[3],border=NA)
-
-lines(times,10*MEGmeantime5Hz[1,],lwd=2,col=colpal[1])
+    polygon(times[c(1:8008,8008:1)],100*c(MEGmeantime5Hz[1,]+MEGSEtime5Hz[1,],MEGmeantime5Hz[1,8008:1]-MEGSEtime5Hz[1,8008:1]),col=colpal[1],border=NA)
+    polygon(times[c(1:8008,8008:1)],100*c(MEGmeantime5Hz[3,]+MEGSEtime5Hz[3,],MEGmeantime5Hz[3,8008:1]-MEGSEtime5Hz[3,8008:1]),col=colpal[2],border=NA)
+    polygon(times[c(1:8008,8008:1)],100*c(MEGmeantime5Hz[4,]+MEGSEtime5Hz[4,],MEGmeantime5Hz[4,8008:1]-MEGSEtime5Hz[4,8008:1]),col=colpal[3],border=NA)
+
+    lines(times,100*MEGmeantime5Hz[1,],lwd=2,col=colpal[1])
     # lines(times,MEGmeantime5Hz[2,],lwd=2,col='green')
-lines(times,10*MEGmeantime5Hz[3,],lwd=2,col=colpal[2])
-lines(times,10*MEGmeantime5Hz[4,],lwd=2,col=colpal[3])
+    lines(times,100*MEGmeantime5Hz[3,],lwd=2,col=colpal[2])
+    lines(times,100*MEGmeantime5Hz[4,],lwd=2,col=colpal[3])
   }
@@
   if (plotsmoothed==1){
-  for (area in 1:nareas){
-spl5aU <- smooth.spline(times,MEGmeantime5Hz[area,1,]+MEGSEtime5Hz[area,1,],df=20)
-spl5aL <- smooth.spline(times,MEGmeantime5Hz[area,1,]-MEGSEtime5Hz[area,1,],df=20)
+
+      spl5aU <- smooth.spline(times,100*(MEGmeantime5Hz[1,]+MEGSEtime5Hz[1,]),df=20)
+      spl5aL <- smooth.spline(times,100*(MEGmeantime5Hz[1,]-MEGSEtime5Hz[1,]),df=20)
       polygon(times[c(1:8008,8008:1)],c(spl5aU$y,spl5aL$y[8008:1]),col=colpal[1],border=NA)
 
-spl5cU <- smooth.spline(times,MEGmeantime5Hz[area,3,]+MEGSEtime5Hz[area,3,],df=20)
-spl5cL <- smooth.spline(times,MEGmeantime5Hz[area,3,]-MEGSEtime5Hz[area,3,],df=20)
+      spl5cU <- smooth.spline(times,100*(MEGmeantime5Hz[3,]+MEGSEtime5Hz[3,]),df=20)
+      spl5cL <- smooth.spline(times,100*(MEGmeantime5Hz[3,]-MEGSEtime5Hz[3,]),df=20)
       polygon(times[c(1:8008,8008:1)],c(spl5cU$y,spl5cL$y[8008:1]),col=colpal[2],border=NA)
 
-spl5dU <- smooth.spline(times,MEGmeantime5Hz[area,4,]+MEGSEtime5Hz[area,4,],df=20)
-spl5dL <- smooth.spline(times,MEGmeantime5Hz[area,4,]-MEGSEtime5Hz[area,4,],df=20)
+      spl5dU <- smooth.spline(times,100*(MEGmeantime5Hz[4,]+MEGSEtime5Hz[4,]),df=20)
+      spl5dL <- smooth.spline(times,100*(MEGmeantime5Hz[4,]-MEGSEtime5Hz[4,]),df=20)
       polygon(times[c(1:8008,8008:1)],c(spl5dU$y,spl5dL$y[8008:1]),col=colpal[3],border=NA)
-  }
-  for (area in 1:nareas){  
-spl5a <- smooth.spline(times,10*MEGmeantime5Hz[area,1,],df=20)
+
+      spl5a <- smooth.spline(times,100*MEGmeantime5Hz[1,],df=20)
       lines(spl5a$x,spl5a$y,col=colpal[1],lwd=2)
@@
       # lines(spl5b$x,spl5b$y,col='green',lwd=2)
-spl5c <- smooth.spline(times,10*MEGmeantime5Hz[area,3,],df=20)
+      spl5c <- smooth.spline(times,100*MEGmeantime5Hz[3,],df=20)
       lines(spl5c$x,spl5c$y,col=colpal[2],lwd=2)
-spl5d <- smooth.spline(times,10*MEGmeantime5Hz[area,4,],df=20)
+      spl5d <- smooth.spline(times,100*MEGmeantime5Hz[4,],df=20)
       lines(spl5d$x,spl5d$y,col=colpal[3],lwd=2)
-}
-}
-
+
+  }
+  text(6,2.8,'5Hz',cex=2)
+  legend(1.25,1,c('Baseline','Monocular','Dichoptic'),lty=1,lwd=2,col=colpal[1:3],box.lwd=2)
   dev.off()
@@
     L <- smooth.spline(times,MEGmaskindex5[1,]-MEGmaskindexSE5[1,],df=20)
+    U$y[which(U$y<(-3))] <- -3
+    L$y[which(L$y<(-3))] <- -3
     polygon(times[c(1:8008,8008:1)],c(U$y,L$y[8008:1]),col=colpal[2],border=NA)
@@
     L <- smooth.spline(times,MEGmaskindex5[2,]-MEGmaskindexSE5[2,],df=20)
+    U$y[which(U$y<(-3))] <- -3
+    L$y[which(L$y<(-3))] <- -3
     polygon(times[c(1:8008,8008:1)],c(U$y,L$y[8008:1]),col=colpal[3],border=NA)
 
-for (area in 1:nareas){ 
-L <- smooth.spline(times,MEGmaskindex5[area,1,],df=20)
-lines(L$x,L$y,col=MEGareacols[area],lwd=2)
-# L <- smooth.spline(times,MEGmaskindex5[area,2,],df=20)
-# lines(L$x,L$y,col=colpal[3],lwd=2)
-}
-legend(1,2,c('V1','V2','V3','hV4','TO','LO','VO'),col=MEGareacols,lwd=2)
+      L <- smooth.spline(times,MEGmaskindex5[1,],df=20)
+      L$y[which(L$y<(-3))] <- -3
+      lines(L$x,L$y,col=colpal[2],lwd=2)
+      L <- smooth.spline(times,MEGmaskindex5[2,],df=20)
+      L$y[which(L$y<(-3))] <- -3
+      lines(L$x,L$y,col=colpal[3],lwd=2)
+
+  }
+
+  if (nbootstraps>0){
+    for (n in 1:clustoutM5$nclusters){
+      temp <- unlist(clustoutM5$clusterpoints[n])
+      lines(times[temp[c(1,length(temp))]],c(-2, -2),lwd=3,col=colpal[2])
+    }
+        for (n in 1:clustoutD5$nclusters){
+      temp <- unlist(clustoutD5$clusterpoints[n])
+      lines(times[temp[c(1,length(temp))]],c(-1.5, -1.5),lwd=3,col=colpal[3])
+    }
   }
@@
 
-postscript("timecourse2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
-
-plotlims <- c(-1,7,-3,7)
-ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklocsx, side = 1, at=ticklocsx)
-mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
-title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-polygon(c(0,6,6,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))
-
-lines(c(-1,7),c(0,0),lty=2)
-
-for (area in 1:nareas){ 
-L <- smooth.spline(times,MEGmaskindex5[area,2,],df=20)
-lines(L$x,L$y,col=MEGareacols[area],lwd=2)
-# L <- smooth.spline(times,MEGmaskindex5[area,2,],df=20)
-# lines(L$x,L$y,col=colpal[3],lwd=2)
-}
-legend(1,2,c('V1','V2','V3','hV4','TO','LO','VO'),col=MEGareacols,lwd=2)
-
-dev.off()
-
-postscript("timecourse2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
-
-plotlims <- c(-1,7,-3,7)
-ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklocsx, side = 1, at=ticklocsx)
-mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
-title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-polygon(c(0,6,6,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))
-
-lines(c(-1,7),c(0,0),lty=2)
-
-if (plotsmoothed==0){
-polygon(times[c(1:8008,8008:1)],c(MEGmaskindex5[1,]+MEGmaskindexSE5[1,],MEGmaskindex5[1,8008:1]-MEGmaskindexSE5[1,8008:1]),col=colpal[2],border=NA)
-polygon(times[c(1:8008,8008:1)],c(MEGmaskindex5[2,]+MEGmaskindexSE5[2,],MEGmaskindex5[2,8008:1]-MEGmaskindexSE5[2,8008:1]),col=colpal[3],border=NA)
-
-lines(times,MEGmaskindex5[1,],col=colpal[2],lwd=2)
-lines(times,MEGmaskindex5[2,],col=colpal[3],lwd=2)
-}
-if (plotsmoothed==1){
-U <- smooth.spline(times,MEGmaskindex5[1,]+MEGmaskindexSE5[1,],df=20)
-L <- smooth.spline(times,MEGmaskindex5[1,]-MEGmaskindexSE5[1,],df=20)
-polygon(times[c(1:8008,8008:1)],c(U$y,L$y[8008:1]),col=colpal[2],border=NA)
-
-U <- smooth.spline(times,MEGmaskindex5[2,]+MEGmaskindexSE5[2,],df=20)
-L <- smooth.spline(times,MEGmaskindex5[2,]-MEGmaskindexSE5[2,],df=20)
-polygon(times[c(1:8008,8008:1)],c(U$y,L$y[8008:1]),col=colpal[3],border=NA)
-
-for (area in 1:nareas){ 
-L <- smooth.spline(times,MEGmaskindex7[area,1,],df=20)
-lines(L$x,L$y,col=MEGareacols[area],lwd=2)
-# L <- smooth.spline(times,MEGmaskindex5[area,2,],df=20)
-# lines(L$x,L$y,col=colpal[3],lwd=2)
-}
-legend(1,2,c('V1','V2','V3','hV4','TO','LO','VO'),col=MEGareacols,lwd=2)
-}
-
-dev.off()
-
-postscript("timecourse2.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
-
-plotlims <- c(-1,7,-3,7)
-ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
-plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
-axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
-axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-mtext(text = ticklocsx, side = 1, at=ticklocsx)
-mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
-title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
-title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-polygon(c(0,6,6,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))
-
-lines(c(-1,7),c(0,0),lty=2)
-
-for (area in 1:nareas){ 
-L <- smooth.spline(times,MEGmaskindex7[area,2,],df=20)
-lines(L$x,L$y,col=MEGareacols[area],lwd=2)
-# L <- smooth.spline(times,MEGmaskindex5[area,2,],df=20)
-# lines(L$x,L$y,col=colpal[3],lwd=2)
-}
-legend(1,2,c('V1','V2','V3','hV4','TO','LO','VO'),col=MEGareacols,lwd=2)
-
-dev.off()
-
   postscript("timecourse3.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
 
-plotlims <- c(-1,7,0,0.6)
-ticklocsy <- seq(0,0.6,0.1)    # locations of tick marks on y axis
+  plotlims <- c(-1,7,0,3)
+  ticklocsy <- seq(0,3,1)    # locations of tick marks on y axis
   plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
@@
   title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
-title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-
-polygon(c(0,6,6,0),c(-0.022,-0.022,0.02,0.02),border=NA,col=rgb(0.5,0.5,0.5))
+  title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+  polygon(c(0,6,6,0),c(-0.11,-0.11,0.15,0.15),border=NA,col=rgb(0.5,0.5,0.5))
 
   if (plotsmoothed==0){
-polygon(times[c(1:8008,8008:1)],10*c(MEGmeantime7Hz[2,]+MEGSEtime7Hz[2,],MEGmeantime7Hz[2,8008:1]-MEGSEtime7Hz[2,8008:1]),col=colpal[1],border=NA)
-polygon(times[c(1:8008,8008:1)],10*c(MEGmeantime7Hz[3,]+MEGSEtime7Hz[3,],MEGmeantime7Hz[3,8008:1]-MEGSEtime7Hz[3,8008:1]),col=colpal[2],border=NA)
-polygon(times[c(1:8008,8008:1)],10*c(MEGmeantime7Hz[4,]+MEGSEtime7Hz[4,],MEGmeantime7Hz[4,8008:1]-MEGSEtime7Hz[4,8008:1]),col=colpal[3],border=NA)
+    polygon(times[c(1:8008,8008:1)],100*c(MEGmeantime7Hz[2,]+MEGSEtime7Hz[2,],MEGmeantime7Hz[2,8008:1]-MEGSEtime7Hz[2,8008:1]),col=colpal[1],border=NA)
+    polygon(times[c(1:8008,8008:1)],100*c(MEGmeantime7Hz[3,]+MEGSEtime7Hz[3,],MEGmeantime7Hz[3,8008:1]-MEGSEtime7Hz[3,8008:1]),col=colpal[2],border=NA)
+    polygon(times[c(1:8008,8008:1)],100*c(MEGmeantime7Hz[4,]+MEGSEtime7Hz[4,],MEGmeantime7Hz[4,8008:1]-MEGSEtime7Hz[4,8008:1]),col=colpal[3],border=NA)
 
     # lines(times,MEGmeantime7Hz[1,],lwd=2,col=colpal[1])
-lines(times,10*MEGmeantime7Hz[2,],lwd=2,col=colpal[1])
-lines(times,10*MEGmeantime7Hz[3,],lwd=2,col=colpal[2])
-lines(times,10*MEGmeantime7Hz[4,],lwd=2,col=colpal[3])
+    lines(times,100*MEGmeantime7Hz[2,],lwd=2,col=colpal[1])
+    lines(times,100*MEGmeantime7Hz[3,],lwd=2,col=colpal[2])
+    lines(times,100*MEGmeantime7Hz[4,],lwd=2,col=colpal[3])
   }
@@
 
-spl7bU <- smooth.spline(times,MEGmeantime7Hz[2,]+MEGSEtime7Hz[2,],df=20)
-spl7bL <- smooth.spline(times,MEGmeantime7Hz[2,]-MEGSEtime7Hz[2,],df=20)
+    spl7bU <- smooth.spline(times,100*(MEGmeantime7Hz[2,]+MEGSEtime7Hz[2,]),df=20)
+    spl7bL <- smooth.spline(times,100*(MEGmeantime7Hz[2,]-MEGSEtime7Hz[2,]),df=20)
     polygon(times[c(1:8008,8008:1)],c(spl7bU$y,spl7bL$y[8008:1]),col=colpal[1],border=NA)
 
-spl7cU <- smooth.spline(times,MEGmeantime7Hz[3,]+MEGSEtime7Hz[3,],df=20)
-spl7cL <- smooth.spline(times,MEGmeantime7Hz[3,]-MEGSEtime7Hz[3,],df=20)
+    spl7cU <- smooth.spline(times,100*(MEGmeantime7Hz[3,]+MEGSEtime7Hz[3,]),df=20)
+    spl7cL <- smooth.spline(times,100*(MEGmeantime7Hz[3,]-MEGSEtime7Hz[3,]),df=20)
     polygon(times[c(1:8008,8008:1)],c(spl7cU$y,spl7cL$y[8008:1]),col=colpal[2],border=NA)
 
-spl7dU <- smooth.spline(times,MEGmeantime7Hz[4,]+MEGSEtime7Hz[4,],df=20)
-spl7dL <- smooth.spline(times,MEGmeantime7Hz[4,]-MEGSEtime7Hz[4,],df=20)
+    spl7dU <- smooth.spline(times,100*(MEGmeantime7Hz[4,]+MEGSEtime7Hz[4,]),df=20)
+    spl7dL <- smooth.spline(times,100*(MEGmeantime7Hz[4,]-MEGSEtime7Hz[4,]),df=20)
     polygon(times[c(1:8008,8008:1)],c(spl7dU$y,spl7dL$y[8008:1]),col=colpal[3],border=NA)
@@
     # lines(spl7a$x,spl7a$y,col=colpal[1],lwd=2)
-  for (area in 1:nareas){ 
-spl7b <- smooth.spline(times,10*MEGmeantime7Hz[area,2,],df=20)
+
+      spl7b <- smooth.spline(times,100*MEGmeantime7Hz[2,],df=20)
       lines(spl7b$x,spl7b$y,col=colpal[1],lwd=2)
-spl7c <- smooth.spline(times,10*MEGmeantime7Hz[area,3,],df=20)
+      spl7c <- smooth.spline(times,100*MEGmeantime7Hz[3,],df=20)
       lines(spl7c$x,spl7c$y,col=colpal[2],lwd=2)
-spl7d <- smooth.spline(times,10*MEGmeantime7Hz[area,4,],df=20)
+      spl7d <- smooth.spline(times,100*MEGmeantime7Hz[4,],df=20)
       lines(spl7d$x,spl7d$y,col=colpal[3],lwd=2)
-}
-}
+
+  }
+    text(6,2.8,'7Hz',cex=2)
 
@@
 
-for (area in 1:nareas){
-L <- smooth.spline(times,MEGmaskindex7[area,1,],df=20)
+      L <- smooth.spline(times,MEGmaskindex7[1,],df=20)
       lines(L$x,L$y,col=colpal[2],lwd=2)
-L <- smooth.spline(times,MEGmaskindex7[area,2,],df=20)
+      L <- smooth.spline(times,MEGmaskindex7[2,],df=20)
       lines(L$x,L$y,col=colpal[3],lwd=2)
+
+  }
+
+    if (nbootstraps>0){
+    for (n in 1:clustoutM7$nclusters){
+      temp <- unlist(clustoutM7$clusterpoints[n])
+      lines(times[temp[c(1,length(temp))]],c(-2, -2),lwd=3,col=colpal[2])
+    }
+        for (n in 1:clustoutD7$nclusters){
+      temp <- unlist(clustoutD7$clusterpoints[n])
+      lines(times[temp[c(1,length(temp))]],c(-1.5, -1.5),lwd=3,col=colpal[3])
     }
@@
 
-# freqlist <- seq(1/6,20,length=ncol(meanspec))
-# 
-# postscript("spectrum.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 10)
-# 
-# plotlims <- c(0,20,0,4)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
-# ticklocsx <- seq(0,20,5)    # locations of tick marks on x axis
-# ticklocsy <- c(0,0.4,0.8,1,2,3,4)    # locations of tick marks on y axis
-# ticklabelsx <- seq(0,20,5)        # set labels for x ticks
-# ticklabelsy <- c(0,0.2,0.4,'','','','')    # set labels for y ticks
-# plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-# axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
-# axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-# mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
-# mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
-# title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-# title(ylab="Amplitude (µV)", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-# 
-# lines(c(0,20),c(0,0),lty=3)
-# lines(c(0,20),c(1,1),lty=3)
-# lines(c(0,20),c(2,2),lty=3)
-# lines(c(0,20),c(3,3),lty=3)
-# 
-# # lines(c(5,5),c(0,4),col='grey',lwd=2)
-# # lines(c(7,7),c(0,4),col='grey',lwd=2)
-# 
-# polygon(c(1/6,freqlist,20),c(0,100*meanspec[1,],0)+3,border=NA,col=colpal[1])
-# polygon(c(1/6,freqlist,20),c(0,100*meanspec[2,],0)+2,border=NA,col=colpal[1])
-# polygon(c(1/6,freqlist,20),c(0,100*meanspec[3,],0)+1,border=NA,col=colpal[2])
-# polygon(c(1/6,freqlist,20),c(0,100*meanspec[4,],0),border=NA,col=colpal[3])
-# 
-# lines(freqlist,100*meanspec[1,]+3,lwd=2,col='black')
-# lines(freqlist,100*meanspec[2,]+2,lwd=2,col='black')
-# lines(freqlist,100*meanspec[3,]+1,lwd=2,col='black')
-# lines(freqlist,100*meanspec[4,],lwd=2,col='black')
-# 
-# text(20,3.5,'5Hz monocular target',pos=2,cex=1.5)
-# text(20,2.5,'7Hz monocular target',pos=2,cex=1.5)
-# text(20,1.5,'Monocular combination',pos=2,cex=1.5)
-# text(20,0.5,'Dichoptic combination',pos=2,cex=1.5)
-# 
-# dev.off()
-
-# 
-# 
-# allresps <- array(0, dim=c(length(d),4,2,9))
-# allspectra <- array(0, dim=c(length(d),4,6006))
-# allwaves <- array(0, dim=c(length(d), 4, 9009))
-# MEGtimecourse7Hz <- array(0, dim=c(length(d),4,8009))
-# MEGtimecourse5Hz <- array(0, dim=c(length(d),4,8009))
-# allRnos <- NULL
-# for (s in 1:length(d)){
-#   allRnos[s] <- substr(d2[s],1,5)
-#   data <- readMat(d[s])
-#   
-#   for (cond in 1:4){
-#       for (t in 1:9){
-#         all1F <- NULL
-#         all2F <- NULL
-#         for (rep in 1:data$trialcounter[1,cond]){
-#           trial <- data$alltrials[cond,rep,]
-# 
-#         sample <- trial[(1+((t-1)*1001)):(t*1001)]
-#         fftsample <- fft(sample)/length(sample)
-# 
-#         all1F[rep] <- fftsample[targetF + 1]
-#         all2F[rep] <- fftsample[maskF + 1]
-#       }
-# 
-#         tempxy <- data.frame(Re(all1F),Im(all1F))
-#         D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
-#         i <- which(D<3)
-#         allresps[s,cond,1,t] <- mean(all1F[i])
-# 
-#         tempxy <- data.frame(Re(all2F),Im(all2F))
-#         D <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
-#         i <- which(D<3)
-#         allresps[s,cond,2,t] <- mean(all2F[i])
-#     }
-#     
-#     meanwave <- colMeans(data$alltrials[cond,1:data$trialcounter[1,cond],])
-#     
-#     sample <- meanwave[1001:7006]
-#     allspectra[s,cond,] <- fft(sample)/length(sample)  
-# 
-#     allwaves[s,cond,] <- meanwave
-#     
-# fspec1 <- NULL
-# fspec2 <- NULL
-# for (t in 1:(length(meanwave)-binwidth)){
-#   spec <- fft(meanwave[t:(t+binwidth-1)])/binwidth
-#   fspec1[t] <- spec[tindex]
-#   fspec2[t] <- spec[mindex]
-# }
-#     MEGtimecourse5Hz[s,cond,] <- fspec1
-#     MEGtimecourse7Hz[s,cond,] <- fspec2
-#     
-#     
-#   }
-# }
-# 
-# save(file='temp/MEGsummary.RData',list=c('allspectra','allresps','allwaves','MEGtimecourse5Hz','MEGtimecourse7Hz','allRnos'))
-# }
-#     
-# if (runcode==1){
-#   
-#   load('temp/MEGsummary.RData')
-#   
-# allresps <- abs(allresps)
-# meanspec <- apply(allresps,2:4,mean)
-# 
-# MEGmeantime5Hz <- matrix(0,nrow=4,ncol=8009) 
-# MEGmeantime7Hz <- matrix(0,nrow=4,ncol=8009) 
-# for (cond in 1:4){
-# MEGmeantime7Hz[cond,] <- apply(abs(MEGtimecourse7Hz[,cond,]),2,mean)
-# MEGmeantime5Hz[cond,] <- apply(abs(MEGtimecourse5Hz[,cond,]),2,mean)
-# }
-# 
-# 
-# qdata <- read.csv('~/Google Drive/Current work/Teaching/MSci project 2021/MSci project questionnaires 2021 (Responses) - Form Responses 1.csv')
-# qgroup <- as.factor(qdata[,5])
-# qRnos <- as.character(qdata[,2])
-# qAges <- qdata[,3]
-# qRnos[20] <- 'R5860'
-# qgroup[20] <- 'Yes'
-# qAges[20] <- 19
-# 
-#   
-# sortedgroups <- NULL
-# for (s in 1:length(allRnos)){sortedgroups[s] <- qgroup[which(qRnos==allRnos[s])]}
-# # sortedgroups now codes 1 = control, 2 = ASC in the order of the MEG data
-# 
-# lowAQ <- abs(apply(abs(allresps[which(sortedgroups==1),,,]),c(2,3,4),mean))
-# highAQ <- abs(apply(abs(allresps[which(sortedgroups==2),,,]),c(2,3,4),mean))
-# 
-# 
-# 
-# 
-# MEGmeantime5HzCON <- matrix(0,nrow=4,ncol=8009) 
-# MEGmeantime7HzCON <- matrix(0,nrow=4,ncol=8009) 
-# MEGmeantime5HzASD <- matrix(0,nrow=4,ncol=8009) 
-# MEGmeantime7HzASD <- matrix(0,nrow=4,ncol=8009) 
-# for (cond in 1:4){
-# MEGmeantime7HzCON[cond,] <- apply(abs(MEGtimecourse7Hz[which(sortedgroups==1),cond,]),2,mean)
-# MEGmeantime5HzCON[cond,] <- apply(abs(MEGtimecourse5Hz[which(sortedgroups==1),cond,]),2,mean)
-# MEGmeantime7HzASD[cond,] <- apply(abs(MEGtimecourse7Hz[which(sortedgroups==2),cond,]),2,mean)
-# MEGmeantime5HzASD[cond,] <- apply(abs(MEGtimecourse5Hz[which(sortedgroups==2),cond,]),2,mean)
-# }
-# 
-# pdf("temp/figures/Fig4.pdf", bg="transparent", height = 10, width = 10)
-# 
-# par(mfrow=c(2,2))
-# 
-# times <- ((1:8009)-500)/1000
-# 
-# plotlims <- c(-1,8,0,30)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
-# ticklocsx <- -1:8    # locations of tick marks on x axis
-# ticklocsy <- seq(0,30,10)    # locations of tick marks on y axis
-# ticklabelsx <- -1:8        # set labels for x ticks
-# ticklabelsy <- ticklocsy    # set labels for y ticks
-# plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-# axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
-# axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-# mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
-# mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-# title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-# title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-# 
-# # lines(times,1000*meanspec[1,1,],lwd=2,col=colpal[1])
-# # lines(times,1000*meanspec[2,1,],lwd=2,col='green')
-# # lines(times,1000*meanspec[3,1,],lwd=2,col=colpal[2])
-# # lines(times,1000*meanspec[4,1,],lwd=2,col=colpal[3])
-# 
-# 
-# # lines(times,1000*MEGmeantime5Hz[1,],lwd=2,col=colpal[1])
-# # lines(times,1000*MEGmeantime5Hz[2,],lwd=2,col='green')
-# # lines(times,1000*MEGmeantime5Hz[3,],lwd=2,col=colpal[2])
-# # lines(times,1000*MEGmeantime5Hz[4,],lwd=2,col=colpal[3])
-# spl5a <- smooth.spline(times,1000*MEGmeantime5Hz[1,],df=20)
-# lines(spl5a$x,spl5a$y,col=colpal[1],lwd=2)
-# spl5b <- smooth.spline(times,1000*MEGmeantime5Hz[2,],df=20)
-# lines(spl5b$x,spl5b$y,col='green',lwd=2)
-# spl5c <- smooth.spline(times,1000*MEGmeantime5Hz[3,],df=20)
-# lines(spl5c$x,spl5c$y,col=colpal[2],lwd=2)
-# spl5d <- smooth.spline(times,1000*MEGmeantime5Hz[4,],df=20)
-# lines(spl5d$x,spl5d$y,col=colpal[3],lwd=2)
-# 
-# # lines(times,1000*MEGmeantime5HzASD[1,],lwd=2,col=colpal[1],lty=2)
-# # lines(times,1000*MEGmeantime5HzASD[2,],lwd=2,col='green',lty=2)
-# # lines(times,1000*MEGmeantime5HzASD[3,],lwd=2,col=colpal[2],lty=2)
-# # lines(times,1000*MEGmeantime5HzASD[4,],lwd=2,col=colpal[3],lty=2)
-# spl5aASD <- smooth.spline(times,1000*MEGmeantime5HzASD[1,],df=20)
-# lines(spl5aASD$x,spl5aASD$y,col=colpal[1],lwd=2,lty=2)
-# spl5bASD <- smooth.spline(times,1000*MEGmeantime5HzASD[2,],df=20)
-# lines(spl5bASD$x,spl5bASD$y,col='green',lwd=2,lty=2)
-# spl5cASD <- smooth.spline(times,1000*MEGmeantime5HzASD[3,],df=20)
-# lines(spl5cASD$x,spl5cASD$y,col=colpal[2],lwd=2,lty=2)
-# spl5dASD <- smooth.spline(times,1000*MEGmeantime5HzASD[4,],df=20)
-# lines(spl5dASD$x,spl5dASD$y,col=colpal[3],lwd=2,lty=2)
-# 
-# # lines(times,1000*MEGmeantime5HzCON[1,],lwd=2,col=colpal[1],lty=3)
-# # lines(times,1000*MEGmeantime5HzCON[2,],lwd=2,col='green',lty=3)
-# # lines(times,1000*MEGmeantime5HzCON[3,],lwd=2,col=colpal[2],lty=3)
-# # lines(times,1000*MEGmeantime5HzCON[4,],lwd=2,col=colpal[3],lty=3)
-# spl5aCON <- smooth.spline(times,1000*MEGmeantime5HzCON[1,],df=20)
-# lines(spl5aCON$x,spl5aCON$y,col=colpal[1],lwd=2,lty=3)
-# spl5bCON <- smooth.spline(times,1000*MEGmeantime5HzCON[2,],df=20)
-# lines(spl5bCON$x,spl5bCON$y,col='green',lwd=2,lty=3)
-# spl5cCON <- smooth.spline(times,1000*MEGmeantime5HzCON[3,],df=20)
-# lines(spl5cCON$x,spl5cCON$y,col=colpal[2],lwd=2,lty=3)
-# spl5dCON <- smooth.spline(times,1000*MEGmeantime5HzCON[4,],df=20)
-# lines(spl5dCON$x,spl5dCON$y,col=colpal[3],lwd=2,lty=3)
-# 
-# 
-# 
-# plotlims <- c(-1,8,0,2)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
-# ticklocsx <- -1:8    # locations of tick marks on x axis
-# ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
-# ticklabelsx <- -1:8        # set labels for x ticks
-# ticklabelsy <- ticklocsy    # set labels for y ticks
-# plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-# axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
-# axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-# mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
-# mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-# title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-# title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-# 
-# lines(spl5b$x,spl5a$y/spl5c$y,col=colpal[2],lwd=2)
-# lines(spl5b$x,spl5a$y/spl5d$y,col=colpal[3],lwd=2)
-# 
-# lines(spl5bASD$x,spl5aASD$y/spl5cASD$y,col=colpal[2],lwd=2,lty=2)
-# lines(spl5bASD$x,spl5aASD$y/spl5dASD$y,col=colpal[3],lwd=2,lty=2)
-# 
-# lines(spl5bCON$x,spl5aCON$y/spl5cCON$y,col=colpal[2],lwd=2,lty=3)
-# lines(spl5bCON$x,spl5aCON$y/spl5dCON$y,col=colpal[3],lwd=2,lty=3)
-# 
-# 
-# plotlims <- c(-1,8,0,30)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
-# ticklocsx <- -1:8    # locations of tick marks on x axis
-# ticklocsy <- seq(0,30,10)    # locations of tick marks on y axis
-# ticklabelsx <- -1:8        # set labels for x ticks
-# ticklabelsy <- ticklocsy    # set labels for y ticks
-# plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-# axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
-# axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-# mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
-# mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-# title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-# title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-# 
-# 
-# # lines(times,1000*MEGmeantime7Hz[1,],lwd=2,col=colpal[1])
-# # lines(times,1000*MEGmeantime7Hz[2,],lwd=2,col='green')
-# # lines(times,1000*MEGmeantime7Hz[3,],lwd=2,col=colpal[2])
-# # lines(times,1000*MEGmeantime7Hz[4,],lwd=2,col=colpal[3])
-# spl7a <- smooth.spline(times,1000*MEGmeantime7Hz[1,],df=20)
-# lines(spl7a$x,spl7a$y,col=colpal[1],lwd=2)
-# spl7b <- smooth.spline(times,1000*MEGmeantime7Hz[2,],df=20)
-# lines(spl7b$x,spl7b$y,col='green',lwd=2)
-# spl7c <- smooth.spline(times,1000*MEGmeantime7Hz[3,],df=20)
-# lines(spl7c$x,spl7c$y,col=colpal[2],lwd=2)
-# spl7d <- smooth.spline(times,1000*MEGmeantime7Hz[4,],df=20)
-# lines(spl7d$x,spl7d$y,col=colpal[3],lwd=2)
-# 
-# # lines(times,1000*MEGmeantime7HzASD[1,],lwd=2,col=colpal[1],lty=2)
-# # lines(times,1000*MEGmeantime7HzASD[2,],lwd=2,col='green',lty=2)
-# # lines(times,1000*MEGmeantime7HzASD[3,],lwd=2,col=colpal[2],lty=2)
-# # lines(times,1000*MEGmeantime7HzASD[4,],lwd=2,col=colpal[3],lty=2)
-# spl7aASD <- smooth.spline(times,1000*MEGmeantime7HzASD[1,],df=20)
-# lines(spl7aASD$x,spl7aASD$y,col=colpal[1],lwd=2,lty=2)
-# spl7bASD <- smooth.spline(times,1000*MEGmeantime7HzASD[2,],df=20)
-# lines(spl7bASD$x,spl7bASD$y,col='green',lwd=2,lty=2)
-# spl7cASD <- smooth.spline(times,1000*MEGmeantime7HzASD[3,],df=20)
-# lines(spl7cASD$x,spl7cASD$y,col=colpal[2],lwd=2,lty=2)
-# spl7dASD <- smooth.spline(times,1000*MEGmeantime7HzASD[4,],df=20)
-# lines(spl7dASD$x,spl7dASD$y,col=colpal[3],lwd=2,lty=2)
-# 
-# # lines(times,1000*MEGmeantime7HzCON[1,],lwd=2,col=colpal[1],lty=3)
-# # lines(times,1000*MEGmeantime7HzCON[2,],lwd=2,col='green',lty=3)
-# # lines(times,1000*MEGmeantime7HzCON[3,],lwd=2,col=colpal[2],lty=3)
-# # lines(times,1000*MEGmeantime7HzCON[4,],lwd=2,col=colpal[3],lty=3)
-# spl7aCON <- smooth.spline(times,1000*MEGmeantime7HzCON[1,],df=20)
-# lines(spl7aCON$x,spl7aCON$y,col=colpal[1],lwd=2,lty=3)
-# spl7bCON <- smooth.spline(times,1000*MEGmeantime7HzCON[2,],df=20)
-# lines(spl7bCON$x,spl7bCON$y,col='green',lwd=2,lty=3)
-# spl7cCON <- smooth.spline(times,1000*MEGmeantime7HzCON[3,],df=20)
-# lines(spl7cCON$x,spl7cCON$y,col=colpal[2],lwd=2,lty=3)
-# spl7dCON <- smooth.spline(times,1000*MEGmeantime7HzCON[4,],df=20)
-# lines(spl7dCON$x,spl7dCON$y,col=colpal[3],lwd=2,lty=3)
-# 
-# 
-# plotlims <- c(-1,8,0,2)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
-# ticklocsx <- -1:8    # locations of tick marks on x axis
-# ticklocsy <- seq(0,2,1)    # locations of tick marks on y axis
-# ticklabelsx <- -1:8        # set labels for x ticks
-# ticklabelsy <- ticklocsy    # set labels for y ticks
-# plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
-# axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2) 
-# axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
-# mtext(text = ticklabelsx, side = 1, at=ticklocsx) 
-# mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1)  
-# title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
-# title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
-# 
-# lines(spl7b$x,spl7b$y/spl7c$y,col=colpal[2],lwd=2)
-# lines(spl7b$x,spl7b$y/spl7d$y,col=colpal[3],lwd=2)
-# 
-# lines(spl7bASD$x,spl7bASD$y/spl7cASD$y,col=colpal[2],lwd=2,lty=2)
-# lines(spl7bASD$x,spl7bASD$y/spl7dASD$y,col=colpal[3],lwd=2,lty=2)
-# 
-# lines(spl7bCON$x,spl7bCON$y/spl7cCON$y,col=colpal[2],lwd=2,lty=3)
-# lines(spl7bCON$x,spl7bCON$y/spl7dCON$y,col=colpal[3],lwd=2,lty=3)
-# 
-# 
-# # lines(times,1000*meanspec[1,2,],lwd=2,lty=2,col=colpal[1])
-# # lines(times,1000*meanspec[2,2,],lwd=2,lty=2,col='green')
-# # lines(times,1000*meanspec[3,2,],lwd=2,lty=2,col=colpal[2])
-# # lines(times,1000*meanspec[4,2,],lwd=2,lty=2,col=colpal[3])
-# 
-# # text(-0.5,3.8,paste0('N=',length(allRnos)),cex=2)
-# # condlist <- c('5Hz target only','5Hz mask only','5Hz mon','5Hz dich','7Hz target only','7Hz mask only','7Hz mon','7Hz dich')
-# # if (outputplot>0){legend(0,4,condlist,col=c(colpal[1],'green',colpal[2],colpal[3]),lty=c(1,1,1,1,2,2,2,2),lwd=2,box.lwd=2)}
-# 
-# dev.off()
+  freqlist <- seq(1/6,20,length=ncol(meanspec))
+
+  postscript("spectrum.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 10)
+
+  plotlims <- c(0,20,0,4)  # define the x and y limits of the plot (minx,maxx,miny,maxy)
+  ticklocsx <- seq(0,20,5)    # locations of tick marks on x axis
+  ticklocsy <- c(0,0.4,0.8,1,2,3,4)    # locations of tick marks on y axis
+  ticklabelsx <- seq(0,20,5)        # set labels for x ticks
+  ticklabelsy <- c(0,0.2,0.4,'','','','')    # set labels for y ticks
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])   
+  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)     # plot tick marks (no labels)
+  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+  mtext(text = ticklabelsx, side = 1, at=ticklocsx)     # add the tick labels
+  mtext(text = ticklabelsy, side = 2, at=ticklocsy, line=0.2, las=1) 
+  title(xlab="Frequency (Hz)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    # titles for axes
+  title(ylab="Amplitude", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+  lines(c(0,20),c(0,0),lty=3)
+  lines(c(0,20),c(1,1),lty=3)
+  lines(c(0,20),c(2,2),lty=3)
+  lines(c(0,20),c(3,3),lty=3)
+
+  # lines(c(5,5),c(0,4),col='grey',lwd=2)
+  # lines(c(7,7),c(0,4),col='grey',lwd=2)
+
+  polygon(c(1,freqlist[6:120],20),c(0,40*meanspec[1,6:120],0)+3,border=NA,col=colpal[1])
+  polygon(c(1,freqlist[6:120],20),c(0,40*meanspec[2,6:120],0)+2,border=NA,col=colpal[1])
+  polygon(c(1,freqlist[6:120],20),c(0,40*meanspec[3,6:120],0)+1,border=NA,col=colpal[2])
+  polygon(c(1,freqlist[6:120],20),c(0,40*meanspec[4,6:120],0),border=NA,col=colpal[3])
+
+  lines(freqlist[6:120],40*meanspec[1,6:120]+3,lwd=2,col='black')
+  lines(freqlist[6:120],40*meanspec[2,6:120]+2,lwd=2,col='black')
+  lines(freqlist[6:120],40*meanspec[3,6:120]+1,lwd=2,col='black')
+  lines(freqlist[6:120],40*meanspec[4,6:120],lwd=2,col='black')
+
+  text(20,3.5,'5Hz monocular target',pos=2,cex=1.5)
+  text(20,2.5,'7Hz monocular target',pos=2,cex=1.5)
+  text(20,1.5,'Monocular combination',pos=2,cex=1.5)
+  text(20,0.5,'Dichoptic combination',pos=2,cex=1.5)
+
+  dev.off()
 
@@
 
-  pdf('temp/figures/Fig4.pdf', bg="transparent", height = 12, width = 12)
+  PostScriptTrace(paste('spectrum.ps',sep=''))
+  e10 <- readPicture('spectrum.ps.xml')
+  for (n in 1:length(e10@paths)){
+    temp <- class(e10@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e10@paths[n]$path@rgb))<765){e10@paths[n]$path@rgb <- addalpha(e10@paths[n]$path@rgb,alpha=0.2)}}}
+
+  e1 <- readTIFF('temp/figures/groupbrainbothSNR.tif')
+  e2 <- readTIFF('temp/figures/LH.tif')
+  e3 <- readTIFF('temp/figures/RH.tif')
+
+  pdf('temp/figures/Fig3.pdf', bg="transparent", height = 6, width = 15)
   par(mar=c(0.1,0.1,0.1,0.1))
@@
 
-  grid.picture(e6,x=0.25,y=0.75,width=0.5,height=1)
-  grid.picture(e7,x=0.75,y=0.75,width=0.5,height=1)
-  grid.picture(e8,x=0.25,y=0.25,width=0.5,height=1)
-  grid.picture(e9,x=0.75,y=0.25,width=0.5,height=1)
-
-  # text(-0.02,1,'(a)',pos=4,cex=2)
-  # text(-0.02,0.45,'(b)',pos=4,cex=2)
-  # text(0.515,1,'(c)',pos=4,cex=2)
-  # text(0.515,0.46,'(d)',pos=4,cex=2)
-  # text(0.785,1,'(e)',pos=4,cex=2)
-  # text(0.785,0.46,'(f)',pos=4,cex=2)
-  # 
-  # text(-0.02,0.61,'5Hz',pos=4,cex=2)
-  # text(-0.02,0.89,'7Hz',pos=4,cex=2)
+  aspratio <- (2500/1600)*(6/15)  # this is the aspect ratio of the output pdf
+  imwidth <- 0.5
+  xstart <- 0
+  ystart <- 0.5
+  rasterImage(e1,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth)
+
+  aspratio <- (1024/682)*(6/15)  # this is the aspect ratio of the output pdf
+  imwidth <- 0.25
+  xstart <- 0.3
+  ystart <- 0.76
+  rasterImage(e2,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth)
+  ystart <- 0.52
+  rasterImage(e3,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth)
+
+  grid.picture(e10,x=0.25,y=0.25,width=0.45,height=1)
+
+  grid.picture(e6,x=0.6,y=0.75,width=0.25,height=1)
+  grid.picture(e7,x=0.85,y=0.75,width=0.25,height=1)
+  grid.picture(e8,x=0.6,y=0.25,width=0.25,height=1)
+  grid.picture(e9,x=0.85,y=0.25,width=0.25,height=1)
+
+  text(-0.02,1,'(a)',pos=4,cex=2)
+  text(-0.02,0.45,'(b)',pos=4,cex=2)
+  text(0.515,1,'(c)',pos=4,cex=2)
+  text(0.515,0.46,'(d)',pos=4,cex=2)
+  text(0.785,1,'(e)',pos=4,cex=2)
+  text(0.785,0.46,'(f)',pos=4,cex=2)
+
+  # text(-0.02,0.89,'5Hz',pos=4,cex=2)
+  # text(-0.02,0.61,'7Hz',pos=4,cex=2)
 
@@
 
-  file.remove(c('timecourse1.ps','timecourse2.ps','timecourse3.ps','timecourse4.ps'))
-  file.remove(c('timecourse1.ps.xml','timecourse2.ps.xml','timecourse3.ps.xml','timecourse4.ps.xml'))
+  file.remove(c('timecourse1.ps','timecourse2.ps','timecourse3.ps','timecourse4.ps','spectrum.ps'))
+  file.remove(c('timecourse1.ps.xml','timecourse2.ps.xml','timecourse3.ps.xml','timecourse4.ps.xml','spectrum.ps.xml'))
 
@@
 
-```{r MEGdata, fig.cap="E.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('temp/figures/Fig4.pdf')
+```{r MEGdata, fig.cap="Summary of MEG results for N=20 adults.
+Panel (a) shows average SSVEP response in source space, thresholded at SNR=2 (blue, left), and locations of the V1 ROI on the medial surface of both hemispheres (right, red).
+Panel (b) shows the Fourier spectra for the four experimental conditions, from the most responsive vertex in V1.
+Panels (c,d) show timecourses at 5Hz and 7Hz, and panels (e,f) show suppression ratios for the monocular and dichoptic conditions at each frequency, with points around y = 0.8 indicating a significantly increasing ratio.
+Shaded regions in panels (c-f) indicate ±1SE across participants, and light grey rectangles indicate the period of stimulus presentation.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('temp/figures/Fig3.pdf')
 
@@
 
-Figure summarising the MEG experiment
-Brains showing location of activity and V1 ROI
-Spectra, timecourses
-NR for each frequency, mon & dich, split by group
+Next we repeated the experiment on 20 participants using a 248-channel whole-head cryogenic MEG system.
+Half of the participants had a diagnosis of autism, and the remainder were age- and gender-matched controls.
+Source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm [@VanVeen1997] showed strong localisation of steady-state signals at the occipital pole (see Figure \@ref(fig:MEGdata)a), and in the Fourier domain (Figure \@ref(fig:MEGdata)b).
+Responses from the most responsive V1 vertex showed a similar timecourse to those of the EEG experiments at both frequencies (Figure \@ref(fig:MEGdata)c,d), and showed increasing suppression during the first few seconds of stimulus presentation (Figure \@ref(fig:MEGdata)e,f).
+The normalization reweighting effect was again clearest at 5Hz, especially for the dichoptic condition (red curve in Figure \@ref(fig:MEGdata)e).
+This confirms that the reweighting effects can occur as early as primary visual cortex, consistent with findings from neurophysiology [@Aschner2018].
+However the data are more variable than for our EEG experiments, and had fewer significant clusters, owing to the smaller sample size for this dataset.
 
@@
 
+load('temp/EEGsummary.RData')
+
+pilotAQ <- read.csv('temp/AQscores.csv',header=FALSE)
+pilotAQ <- pilotAQ[-75,2]
+
+load("temp/questionnairedataMSci.RData")
+MEGAQ <- qdata$AQ[1:19]
+MEGgroup <- qdata$Diagnosis[1:19]
+
+MEG_A <- MEGAQ[which(MEGgroup=="Yes")]
+MEG_C <- MEGAQ[which(MEGgroup=="No")]
+t <- t.test(MEG_A,MEG_C,paired=FALSE)
+
+t_age <- t.test(qdata$Age[which(qdata$Diagnosis=='Yes')],qdata$Age[which(qdata$Diagnosis=='No')],paired=FALSE,var.equal=TRUE)
+
+corMEG <- cor.test(qdata$AQ[1:19],qdata$SPQ[1:19])
+corEEG <- cor.test(allAQ,allSPQ)
+
 if (processdata>0){
+
+  postscript('AQplot1.ps', horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+  plotlims <- c(0,50,0,2)
+  ticklocsx <- seq(0,50,10)    # locations of tick marks on y axis
+  ticklocsy <- c(0, 2)
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+  mtext(text = ticklocsx, side = 1, at=ticklocsx)
+
+  title(xlab="AQ score", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+  title(ylab="Pilot experiment", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
+
+  a <- density(pilotAQ,from=0,to=50)
+  a$y <- a$y/max(a$y)
+
+  i <- which(a$x<median(pilotAQ))
+  polygon(c(0,a$x[c(i,i[length(i)])]),c(0,a$y[i],0),border=NA,col=colpal[4])
+
+  i <- which(a$x>median(pilotAQ))
+  polygon(a$x[c(i[1],i)],c(0,a$y[i]),border=NA,col=colpal[5])
+
+  lines(c(0,a$x),c(0,a$y),lwd=3)
+
+  lines(c(median(pilotAQ),median(pilotAQ)),c(0,1.1),lwd=5,col='grey')
+
+  temp <- pilotAQ[which(pilotAQ<median(pilotAQ))]
+  points(temp,0.5*runif(length(temp))+1.25,col=colpal[4],pch=16)
+
+  temp <- pilotAQ[which(pilotAQ>median(pilotAQ))]
+  points(temp,0.5*runif(length(temp))+1.25,col=colpal[5],pch=16)
+
+  temp <- pilotAQ[which(pilotAQ==median(pilotAQ))]
+  points(temp,0.5*runif(length(temp))+1.25,col='grey',pch=16)
+
+  dev.off()
+
+    postscript('AQplot2.ps', horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+  plotlims <- c(0,50,0,2)
+  ticklocsx <- seq(0,50,10)    # locations of tick marks on y axis
+  ticklocsy <- c(0, 2)
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+  mtext(text = ticklocsx, side = 1, at=ticklocsx)
+
+  title(xlab="AQ score", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+  title(ylab="EEG experiment", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
+
+  a <- density(allAQ,from=0,to=50)
+  a$y <- a$y/max(a$y)
+
+  i <- which(a$x<median(allAQ))
+  polygon(c(0,a$x[c(i,i[length(i)])]),c(0,a$y[i],0),border=NA,col=colpal[4])
+
+  i <- which(a$x>median(allAQ))
+  polygon(a$x[c(i[1],i)],c(0,a$y[i]),border=NA,col=colpal[5])
+
+  lines(c(0,a$x),c(0,a$y),lwd=3)
+
+  lines(c(median(allAQ),median(allAQ)),c(0,1.1),lwd=5,col='grey')
+
+  temp <- allAQ[which(allAQ<median(allAQ))]
+  points(temp,0.5*runif(length(temp))+1.25,col=colpal[4],pch=16)
+
+  temp <- allAQ[which(allAQ>median(allAQ))]
+  points(temp,0.5*runif(length(temp))+1.25,col=colpal[5],pch=16)
+
+  temp <- allAQ[which(allAQ==median(allAQ))]
+  points(temp,0.5*runif(length(temp))+1.25,col='grey',pch=16)
+
+  dev.off()
+
+    postscript('AQplot3.ps', horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+  plotlims <- c(0,50,0,2)
+  ticklocsx <- seq(0,50,10)    # locations of tick marks on y axis
+  ticklocsy <- c(0, 2)
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+  mtext(text = ticklocsx, side = 1, at=ticklocsx)
+
+  title(xlab="AQ score", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+  title(ylab="MEG experiment", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)
+
+  temp <- MEGAQ[which(MEGgroup=='No')]
+  points(temp,0.5*runif(length(temp))+1.25,col=colpal[4],pch=16)
+  a <- density(temp,from=0,to=50)
+  a$y <- a$y/max(a$y)
+  polygon(a$x,a$y,border=NA,col=colpal[4])
+  lines(a$x,a$y,lwd=3)
+
+  temp <- MEGAQ[which(MEGgroup=='Yes')]
+  points(temp,0.5*runif(length(temp))+1.25,col=colpal[5],pch=16)
+  a <- density(temp,from=0,to=50)
+  a$y <- a$y/max(a$y)
+  polygon(c(a$x,50),c(a$y,0),border=NA,col=colpal[5])
+  lines(c(a$x,50),c(a$y,0),lwd=3)
+
+  dev.off()
+
+  load('temp/Pilotsummary.RData')
+
+  duration <- 10
+  targetF <- 7
+  maskF <- 5
+  isincluded <- matrix(rep(1,3*dim(EEGspectra)[1]),nrow=3,ncol=dim(EEGspectra)[1])
+  for (cond in 1:3){
+    # note that in allspec the DC component has been removed
+    # so we don't need to add 1 to the index
+    tempxy <- data.frame(Re(EEGspectra[,cond,duration*targetF]),Im(EEGspectra[,cond,duration*targetF]))
+    D5 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+    tempxy <- data.frame(Re(EEGspectra[,cond,duration*maskF]),Im(EEGspectra[,cond,duration*maskF]))      
+    D7 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))      
+    isincluded[cond,which(D5>3)] <- 0
+    isincluded[cond,which(D7>3)] <- 0
+  }
+
+  medAQp <- median(pilotAQ)
+  islowAQp <- rep(0,100)
+  ishighAQp <- rep(0,100)
+  islowAQp[which(pilotAQ<medAQp)] <- 1
+  ishighAQp[which(pilotAQ>medAQp)] <- 1
+
+  Pilotmeantime5HzL <- matrix(0,nrow=3,ncol=13000)
+  Pilotmeantime7HzL <- matrix(0,nrow=3,ncol=13000)
+  Pilotmeantime5HzH <- matrix(0,nrow=3,ncol=13000)
+  Pilotmeantime7HzH <- matrix(0,nrow=3,ncol=13000)
+  Pilotmeantime10HzL <- matrix(0,nrow=3,ncol=13000)
+  Pilotmeantime14HzL <- matrix(0,nrow=3,ncol=13000)
+  Pilotmeantime10HzH <- matrix(0,nrow=3,ncol=13000)
+  Pilotmeantime14HzH <- matrix(0,nrow=3,ncol=13000)
+
+  for (cond in 1:3){
+    lowAQincluded <- islowAQp * isincluded[cond,]
+    highAQincluded <- ishighAQp * isincluded[cond,]
+
+    Pilotmeantime7HzL[cond,] <- apply(abs(EEGtimecourse[which(lowAQincluded==1),1,cond,]),2,mean,na.rm=TRUE)
+    Pilotmeantime5HzL[cond,] <- apply(abs(EEGtimecourse[which(lowAQincluded==1),2,cond,]),2,mean,na.rm=TRUE)
+
+    Pilotmeantime7HzH[cond,] <- apply(abs(EEGtimecourse[which(highAQincluded==1),1,cond,]),2,mean,na.rm=TRUE)
+    Pilotmeantime5HzH[cond,] <- apply(abs(EEGtimecourse[which(highAQincluded==1),2,cond,]),2,mean,na.rm=TRUE)
+
+    Pilotmeantime14HzL[cond,] <- apply(abs(EEGtimecourse[which(lowAQincluded==1),3,cond,]),2,mean,na.rm=TRUE)
+    Pilotmeantime10HzL[cond,] <- apply(abs(EEGtimecourse[which(lowAQincluded==1),4,cond,]),2,mean,na.rm=TRUE)
+
+    Pilotmeantime14HzH[cond,] <- apply(abs(EEGtimecourse[which(highAQincluded==1),3,cond,]),2,mean,na.rm=TRUE)
+    Pilotmeantime10HzH[cond,] <- apply(abs(EEGtimecourse[which(highAQincluded==1),4,cond,]),2,mean,na.rm=TRUE)
+
+  }
+
+  includedboth <- isincluded[2,]*isincluded[3,]*islowAQp
+  monratios1 <- abs(EEGtimecourse[which(includedboth==1),2,2,])/abs(EEGtimecourse[which(includedboth==1),2,3,])
+  monratios2 <- abs(EEGtimecourse[which(includedboth==1),1,1,])/abs(EEGtimecourse[which(includedboth==1),1,3,])
+  monratios3 <- abs(EEGtimecourse[which(includedboth==1),4,2,])/abs(EEGtimecourse[which(includedboth==1),4,3,])
+  monratios4 <- abs(EEGtimecourse[which(includedboth==1),3,1,])/abs(EEGtimecourse[which(includedboth==1),3,3,])
+  monratios <- (20*log10(monratios1) + 20*log10(monratios2) + 20*log10(monratios3) + 20*log10(monratios4))/4
+  PilotmaskindexL <- colMeans(monratios)
+  PilotmaskindexSEL <- apply(monratios,2,sd)/sqrt(sum(includedboth))
+
+  lowgroup <- monratios
+
+  includedboth <- isincluded[2,]*isincluded[3,]*ishighAQp
+  monratios1 <- abs(EEGtimecourse[which(includedboth==1),2,2,])/abs(EEGtimecourse[which(includedboth==1),2,3,])
+  monratios2 <- abs(EEGtimecourse[which(includedboth==1),1,1,])/abs(EEGtimecourse[which(includedboth==1),1,3,])
+  monratios3 <- abs(EEGtimecourse[which(includedboth==1),4,2,])/abs(EEGtimecourse[which(includedboth==1),4,3,])
+  monratios4 <- abs(EEGtimecourse[which(includedboth==1),3,1,])/abs(EEGtimecourse[which(includedboth==1),3,3,])
+  monratios <- (20*log10(monratios1) + 20*log10(monratios2) + 20*log10(monratios3) + 20*log10(monratios4))/4
+  PilotmaskindexH <- colMeans(monratios)
+  PilotmaskindexSEH <- apply(monratios,2,sd)/sqrt(sum(includedboth))
+
+  highgroup <- monratios
+
+  Pilotmaskindex5L <- matrix(0,nrow=2,ncol=13000)
+  PilotmaskindexSE5L <- matrix(0,nrow=2,ncol=13000)
+  includedboth <- isincluded[2,]*isincluded[3,]*islowAQp
+  monratios <- abs(EEGtimecourse[which(includedboth==1),2,2,])/abs(EEGtimecourse[which(includedboth==1),2,3,])
+  Pilotmaskindex5L[1,] <- colMeans(20*log10(monratios))
+  PilotmaskindexSE5L[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+
+  Pilotmaskindex5H <- matrix(0,nrow=2,ncol=13000)
+  PilotmaskindexSE5H <- matrix(0,nrow=2,ncol=13000)
+  includedboth <- isincluded[2,]*isincluded[3,]*ishighAQp
+  monratios <- abs(EEGtimecourse[which(includedboth==1),2,2,])/abs(EEGtimecourse[which(includedboth==1),2,3,])
+  Pilotmaskindex5H[1,] <- colMeans(20*log10(monratios))
+  PilotmaskindexSE5H[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+
+  Pilotmaskindex7L <- matrix(0,nrow=2,ncol=13000)
+  PilotmaskindexSE7L <- matrix(0,nrow=2,ncol=13000)
+  includedboth <- isincluded[1,]*isincluded[3,]*islowAQp
+  monratios <- abs(EEGtimecourse[which(includedboth==1),1,1,])/abs(EEGtimecourse[which(includedboth==1),1,3,])
+  Pilotmaskindex7L[1,] <- colMeans(20*log10(monratios))
+  PilotmaskindexSE7L[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+
+  Pilotmaskindex7H <- matrix(0,nrow=2,ncol=13000)
+  PilotmaskindexSE7H <- matrix(0,nrow=2,ncol=13000)
+  includedboth <- isincluded[1,]*isincluded[3,]*ishighAQp
+  monratios <- abs(EEGtimecourse[which(includedboth==1),1,1,])/abs(EEGtimecourse[which(includedboth==1),1,3,])
+  Pilotmaskindex7H[1,] <- colMeans(20*log10(monratios))
+  PilotmaskindexSE7H[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+
+  if (nbootstraps>0){clustout <- clustercorrect(lowgroup,highgroup,paired=FALSE,nresamples=nbootstraps)}
+
+  times <- ((1:13000)-1000)/1000
+
+  postscript("Ptimecourse.ps", horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+  plotlims <- c(-1,12,-3,6)
+  ticklocsx <- -1:12
+  ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+  axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+  axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+  mtext(text = ticklocsx, side = 1, at=ticklocsx)
+  mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
+  title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+  title(ylab="Suppression ratio", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+  polygon(c(0,11,11,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))
+
+  lines(c(-1,12),c(0,0),lty=2)
+
+  if (plotsmoothed==0){
+    polygon(times[c(1:13000,13000:1)],c(PilotmaskindexL+PilotmaskindexSEL,PilotmaskindexL[13000:1]-PilotmaskindexSEL[13000:1]),col=colpal[4],border=NA)
+    polygon(times[c(1:13000,13000:1)],c(PilotmaskindexH+PilotmaskindexSEH,PilotmaskindexH[13000:1]-PilotmaskindexSEH[13000:1]),col=colpal[5],border=NA)
+
+    lines(times,PilotmaskindexL,col=colpal[4],lwd=2)
+    lines(times,PilotmaskindexH,col=colpal[5],lwd=2)
+  }
+
+  if (plotsmoothed==1){
+    U <- smooth.spline(times,PilotmaskindexL+PilotmaskindexSEL,df=20)
+    L <- smooth.spline(times,PilotmaskindexL-PilotmaskindexSEL,df=20)
+    polygon(times[c(1:13000,13000:1)],c(U$y,L$y[13000:1]),col=colpal[4],border=NA)
+
+    U <- smooth.spline(times,PilotmaskindexH+PilotmaskindexSEH,df=20)
+    L <- smooth.spline(times,PilotmaskindexH-PilotmaskindexSEH,df=20)
+    polygon(times[c(1:13000,13000:1)],c(U$y,L$y[13000:1]),col=colpal[5],border=NA)
+
+    L <- smooth.spline(times,PilotmaskindexL,df=20)
+    lines(L$x,L$y,col=colpal[4],lwd=2)
+    L <- smooth.spline(times,PilotmaskindexH,df=20)
+    lines(L$x,L$y,col=colpal[5],lwd=2)
+  }
+
+  if (nbootstraps>0){
+    for (n in 1:clustout$nclusters){
+      temp <- unlist(clustout$clusterpoints[n])
+      lines(times[temp[c(1,length(temp))]],c(-1.5, -1.5),lwd=3)
+    }
+    }
+
+  dev.off()
+
   load('temp/EEGsummary.RData')
 
+  duration <- 6
+  targetF <- 5
+  maskF <- 7
   isincluded <- matrix(rep(1,4*dim(allspec)[1]),nrow=4,ncol=dim(allspec)[1])
@@
 
-allwaves[which(allwaves<(-100))] <- 0
-allwaves[which(allwaves>100)] <- 0
-
+    if (useSPQ==1){
+    # if this flag is set, we do the median split by SPQ instead of AQ
+  medAQ <- median(allSPQ)
+  islowAQ <- rep(0,100)
+  ishighAQ <- rep(0,100)
+  islowAQ[which(allSPQ<medAQ)] <- 1
+  ishighAQ[which(allSPQ>medAQ)] <- 1
+    }
+  if (useSPQ==0){
   medAQ <- median(allAQ)
@@
   ishighAQ[which(allAQ>medAQ)] <- 1
+  }
 
@@
   }
+
+  EEGmaskindexL <- matrix(0,nrow=2,ncol=8000)
+  EEGmaskindexSEL <- matrix(0,nrow=2,ncol=8000)
+  includedboth <- isincluded[1,]*isincluded[3,]*islowAQ
+  monratios1 <- abs(EEGtimecourse5Hz[which(includedboth==1),1,])/abs(EEGtimecourse5Hz[which(includedboth==1),3,])
+  monratios2 <- abs(EEGtimecourse7Hz[which(includedboth==1),2,])/abs(EEGtimecourse7Hz[which(includedboth==1),3,])
+  monratios <- (20*log10(monratios1) + 20*log10(monratios2))/2
+  EEGmaskindexL[1,] <- colMeans(monratios)
+  EEGmaskindexSEL[1,] <- apply(monratios,2,sd)/sqrt(sum(includedboth))
+  includedboth <- isincluded[1,]*isincluded[4,]*islowAQ
+  dichratios1 <- abs(EEGtimecourse5Hz[which(includedboth==1),1,])/abs(EEGtimecourse5Hz[which(includedboth==1),4,])
+  dichratios2 <- abs(EEGtimecourse7Hz[which(includedboth==1),2,])/abs(EEGtimecourse7Hz[which(includedboth==1),4,])
+  dichratios <- (20*log10(dichratios1) + 20*log10(dichratios2))/2
+  EEGmaskindexL[2,] <- colMeans(dichratios)
+  EEGmaskindexSEL[2,] <- apply(dichratios,2,sd)/sqrt(sum(includedboth))
+
+  lowgroupM <- monratios
+  lowgroupD <- dichratios
+
+  EEGmaskindexH <- matrix(0,nrow=2,ncol=8000)
+  EEGmaskindexSEH <- matrix(0,nrow=2,ncol=8000)
+  includedboth <- isincluded[1,]*isincluded[3,]*ishighAQ
+  monratios1 <- abs(EEGtimecourse5Hz[which(includedboth==1),1,])/abs(EEGtimecourse5Hz[which(includedboth==1),3,])
+  monratios2 <- abs(EEGtimecourse7Hz[which(includedboth==1),2,])/abs(EEGtimecourse7Hz[which(includedboth==1),3,])
+  monratios <- (20*log10(monratios1) + 20*log10(monratios2))/2
+  EEGmaskindexH[1,] <- colMeans(monratios)
+  EEGmaskindexSEH[1,] <- apply(monratios,2,sd)/sqrt(sum(includedboth))
+  includedboth <- isincluded[1,]*isincluded[4,]*ishighAQ
+  dichratios1 <- abs(EEGtimecourse5Hz[which(includedboth==1),1,])/abs(EEGtimecourse5Hz[which(includedboth==1),4,])
+  dichratios2 <- abs(EEGtimecourse7Hz[which(includedboth==1),2,])/abs(EEGtimecourse7Hz[which(includedboth==1),4,])
+  dichratios <- (20*log10(dichratios1) + 20*log10(dichratios2))/2
+  EEGmaskindexH[2,] <- colMeans(dichratios)
+  EEGmaskindexSEH[2,] <- apply(dichratios,2,sd)/sqrt(sum(includedboth))
+
+  highgroupM <- monratios
+  highgroupD <- dichratios
 
@@
 
+    if (nbootstraps>0){
+      clustoutM <- clustercorrect(lowgroupM,highgroupM,paired=FALSE,nresamples=nbootstraps)
+      clustoutD <- clustercorrect(lowgroupD,highgroupD,paired=FALSE,nresamples=nbootstraps)    
+    }
+
   times <- ((1:8000)-1000)/1000
@@
   for (masktype in 1:2){
-postscript(paste0("timecourse",masktype,".ps"), horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+    postscript(paste0("timecourse",masktype,"all.ps"), horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
 
     plotlims <- c(-1,7,-3,6)
+    ticklocsx <- -1:7
     ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
@@
     if (plotsmoothed==0){
-polygon(times[c(1:8000,8000:1)],c(EEGmaskindex5L[masktype,]+EEGmaskindexSE5L[masktype,],EEGmaskindex5L[masktype,8000:1]-EEGmaskindexSE5L[masktype,8000:1]),col=colpal[2],border=NA)
-polygon(times[c(1:8000,8000:1)],c(EEGmaskindex5H[masktype,]+EEGmaskindexSE5H[masktype,],EEGmaskindex5H[masktype,8000:1]-EEGmaskindexSE5H[masktype,8000:1]),col=colpal[3],border=NA)
-
-lines(times,EEGmaskindex5L[masktype,],col=colpal[2],lwd=2)
-lines(times,EEGmaskindex5H[masktype,],col=colpal[3],lwd=2)
+      polygon(times[c(1:8000,8000:1)],c(EEGmaskindexL[masktype,]+EEGmaskindexSEL[masktype,],EEGmaskindexL[masktype,8000:1]-EEGmaskindexSEL[masktype,8000:1]),col=colpal[4],border=NA)
+      polygon(times[c(1:8000,8000:1)],c(EEGmaskindexH[masktype,]+EEGmaskindexSEH[masktype,],EEGmaskindexH[masktype,8000:1]-EEGmaskindexSEH[masktype,8000:1]),col=colpal[5],border=NA)
+
+      lines(times,EEGmaskindexL[masktype,],col=colpal[4],lwd=2)
+      lines(times,EEGmaskindexH[masktype,],col=colpal[5],lwd=2)
     }
@@
     if (plotsmoothed==1){
-U <- smooth.spline(times,EEGmaskindex5L[masktype,]+EEGmaskindexSE5L[masktype,],df=20)
-L <- smooth.spline(times,EEGmaskindex5L[masktype,]-EEGmaskindexSE5L[masktype,],df=20)
-polygon(times[c(1:8000,8000:1)],c(U$y,L$y[8000:1]),col=colpal[2],border=NA)
-
-U <- smooth.spline(times,EEGmaskindex5H[masktype,]+EEGmaskindexSE5H[masktype,],df=20)
-L <- smooth.spline(times,EEGmaskindex5H[masktype,]-EEGmaskindexSE5H[masktype,],df=20)
-polygon(times[c(1:8000,8000:1)],c(U$y,L$y[8000:1]),col=colpal[3],border=NA)
-
-L <- smooth.spline(times,EEGmaskindex5L[masktype,],df=20)
-lines(L$x,L$y,col=colpal[2],lwd=2)
-L <- smooth.spline(times,EEGmaskindex5H[masktype,],df=20)
-lines(L$x,L$y,col=colpal[3],lwd=2)
+      U <- smooth.spline(times,EEGmaskindexL[masktype,]+EEGmaskindexSEL[masktype,],df=20)
+      L <- smooth.spline(times,EEGmaskindexL[masktype,]-EEGmaskindexSEL[masktype,],df=20)
+      polygon(times[c(1:8000,8000:1)],c(U$y,L$y[8000:1]),col=colpal[4],border=NA)
+
+      U <- smooth.spline(times,EEGmaskindexH[masktype,]+EEGmaskindexSEH[masktype,],df=20)
+      L <- smooth.spline(times,EEGmaskindexH[masktype,]-EEGmaskindexSEH[masktype,],df=20)
+      polygon(times[c(1:8000,8000:1)],c(U$y,L$y[8000:1]),col=colpal[5],border=NA)
+
+      L <- smooth.spline(times,EEGmaskindexL[masktype,],df=20)
+      lines(L$x,L$y,col=colpal[4],lwd=2)
+      L <- smooth.spline(times,EEGmaskindexH[masktype,],df=20)
+      lines(L$x,L$y,col=colpal[5],lwd=2)
+    }
+
+          if (nbootstraps>0){
+        if (masktype==1){
+    for (n in 1:clustoutM$nclusters){
+      temp <- unlist(clustoutM$clusterpoints[n])
+      lines(times[temp[c(1,length(temp))]],c(-1.5, -1.5),lwd=2)
+    }}
+        if (masktype==2){
+    for (n in 1:clustoutD$nclusters){
+      temp <- unlist(clustoutD$clusterpoints[n])
+      lines(times[temp[c(1,length(temp))]],c(-1.5, -1.5),lwd=2)
+    }}   
           }
@@
 
-postscript(paste0("timecourse",masktype+2,".ps"), horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+  }
+
+  load('temp/MEGsummaryV1.RData')
+  MEGgroup <- qdata$Diagnosis
+  MEGID <- qdata$ID
+  dataorder <- match(MEGID,allRnos)
+  # dataorder tells us the indices into the MEG data for each AQ score
+
+  MEGmeantime5HzC <- matrix(0,nrow=4,ncol=8008)
+  MEGmeantime7HzC <- matrix(0,nrow=4,ncol=8008)
+  MEGSEtime5HzC <- matrix(0,nrow=4,ncol=8008)
+  MEGSEtime7HzC <- matrix(0,nrow=4,ncol=8008)
+  MEGmeantime5HzA <- matrix(0,nrow=4,ncol=8008)
+  MEGmeantime7HzA <- matrix(0,nrow=4,ncol=8008)
+  MEGSEtime5HzA <- matrix(0,nrow=4,ncol=8008)
+  MEGSEtime7HzA <- matrix(0,nrow=4,ncol=8008)
+
+  CONindices <- dataorder[which(MEGgroup=='No')]
+  ASCindices <- dataorder[which(MEGgroup=='Yes')]
+  isCON <- (1:20)*0
+  isASC <- (1:20)*0
+  isCON[CONindices] <- 1
+  isASC[ASCindices] <- 1
+
+  duration <- 6
+  targetF <- 5
+  maskF <- 7
+  isincluded <- matrix(rep(1,4*dim(allspec)[1]),nrow=4,ncol=dim(allspec)[1])
+  for (cond in 1:4){
+    # note that in allspec the DC component has been removed
+    # so we don't need to add 1 to the index
+    tempxy <- data.frame(Re(allspec[,cond,duration*targetF]),Im(allspec[,cond,duration*targetF]))
+    D5 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+    tempxy <- data.frame(Re(allspec[,cond,duration*maskF]),Im(allspec[,cond,duration*maskF]))      
+    D7 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))      
+    isincluded[cond,which(D5>3)] <- 0
+    isincluded[cond,which(D7>3)] <- 0
+  }
+
+  for (cond in 1:4){
+    CONincluded <- isCON * isincluded[cond,]
+    ASCincluded <- isASC * isincluded[cond,]
+
+    MEGmeantime7HzC[cond,] <- apply(abs(MEGtimecourse7Hz[which(CONincluded==1),cond,]),2,mean,na.rm=TRUE)
+    MEGmeantime5HzC[cond,] <- apply(abs(MEGtimecourse5Hz[which(CONincluded==1),cond,]),2,mean,na.rm=TRUE)
+
+    MEGSEtime7HzC[cond,] <- apply(abs(MEGtimecourse7Hz[which(CONincluded==1),cond,]),2,sd,na.rm=TRUE)/sqrt(sum(CONincluded))
+    MEGSEtime5HzC[cond,] <- apply(abs(MEGtimecourse5Hz[which(CONincluded==1),cond,]),2,sd,na.rm=TRUE)/sqrt(sum(CONincluded))
+
+    MEGmeantime7HzA[cond,] <- apply(abs(MEGtimecourse7Hz[which(ASCincluded==1),cond,]),2,mean,na.rm=TRUE)
+    MEGmeantime5HzA[cond,] <- apply(abs(MEGtimecourse5Hz[which(ASCincluded==1),cond,]),2,mean,na.rm=TRUE)
+
+    MEGSEtime7HzA[cond,] <- apply(abs(MEGtimecourse7Hz[which(ASCincluded==1),cond,]),2,sd,na.rm=TRUE)/sqrt(sum(ASCincluded))
+    MEGSEtime5HzA[cond,] <- apply(abs(MEGtimecourse5Hz[which(ASCincluded==1),cond,]),2,sd,na.rm=TRUE)/sqrt(sum(ASCincluded))
+  }
+
+  MEGmaskindexC <- matrix(0,nrow=2,ncol=8008)
+  MEGmaskindexSEC <- matrix(0,nrow=2,ncol=8008)
+  includedboth <- isincluded[1,]*isincluded[3,]*isCON
+  monratios1 <- abs(MEGtimecourse5Hz[which(includedboth==1),1,])/abs(MEGtimecourse5Hz[which(includedboth==1),3,])
+  monratios2 <- abs(MEGtimecourse7Hz[which(includedboth==1),2,])/abs(MEGtimecourse7Hz[which(includedboth==1),3,])
+  monratios <- (20*log10(monratios1) + 20*log10(monratios2))/2
+  MEGmaskindexC[1,] <- colMeans(monratios)
+  MEGmaskindexSEC[1,] <- apply(monratios,2,sd)/sqrt(sum(includedboth))
+  includedboth <- isincluded[1,]*isincluded[4,]*isCON
+  dichratios1 <- abs(MEGtimecourse5Hz[which(includedboth==1),1,])/abs(MEGtimecourse5Hz[which(includedboth==1),4,])
+  dichratios2 <- abs(MEGtimecourse7Hz[which(includedboth==1),2,])/abs(MEGtimecourse7Hz[which(includedboth==1),4,])
+  dichratios <- (20*log10(dichratios1) + 20*log10(dichratios2))/2
+  MEGmaskindexC[2,] <- colMeans(dichratios)
+  MEGmaskindexSEC[2,] <- apply(dichratios,2,sd)/sqrt(sum(includedboth))
+
+  CgroupM <- monratios
+  CgroupD <- dichratios
+
+  MEGmaskindexA <- matrix(0,nrow=2,ncol=8008)
+  MEGmaskindexSEA <- matrix(0,nrow=2,ncol=8008)
+  includedboth <- isincluded[1,]*isincluded[3,]*isASC
+  monratios1 <- abs(MEGtimecourse5Hz[which(includedboth==1),1,])/abs(MEGtimecourse5Hz[which(includedboth==1),3,])
+  monratios2 <- abs(MEGtimecourse7Hz[which(includedboth==1),2,])/abs(MEGtimecourse7Hz[which(includedboth==1),3,])
+  monratios <- (20*log10(monratios1) + 20*log10(monratios2))/2
+  MEGmaskindexA[1,] <- colMeans(monratios)
+  MEGmaskindexSEA[1,] <- apply(monratios,2,sd)/sqrt(sum(includedboth))
+  includedboth <- isincluded[1,]*isincluded[4,]*isASC
+  dichratios1 <- abs(MEGtimecourse5Hz[which(includedboth==1),1,])/abs(MEGtimecourse5Hz[which(includedboth==1),4,])
+  dichratios2 <- abs(MEGtimecourse7Hz[which(includedboth==1),2,])/abs(MEGtimecourse7Hz[which(includedboth==1),4,])
+  dichratios <- (20*log10(dichratios1) + 20*log10(dichratios2))/2
+  MEGmaskindexA[2,] <- colMeans(dichratios)
+  MEGmaskindexSEA[2,] <- apply(dichratios,2,sd)/sqrt(sum(includedboth))
+
+  MEGmaskindexA <- matrix(0,nrow=2,ncol=8008)
+  MEGmaskindexSEA <- matrix(0,nrow=2,ncol=8008)
+  includedboth <- isincluded[1,]*isincluded[3,]*isASC
+  monratios <- abs(MEGtimecourse5Hz[which(includedboth==1),1,])/abs(MEGtimecourse5Hz[which(includedboth==1),3,])
+  MEGmaskindexA[1,] <- colMeans(20*log10(monratios))
+  MEGmaskindexSEA[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+  includedboth <- isincluded[1,]*isincluded[4,]*isASC
+  dichratios <- abs(MEGtimecourse5Hz[which(includedboth==1),1,])/abs(MEGtimecourse5Hz[which(includedboth==1),4,])
+  MEGmaskindexA[2,] <- colMeans(20*log10(dichratios))
+  MEGmaskindexSEA[2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+
+  AgroupM <- monratios
+  AgroupD <- dichratios
+
+  MEGmaskindex5C <- matrix(0,nrow=2,ncol=8008)
+  MEGmaskindexSE5C <- matrix(0,nrow=2,ncol=8008)
+  includedboth <- isincluded[1,]*isincluded[3,]*isCON
+  monratios <- abs(MEGtimecourse5Hz[which(includedboth==1),1,])/abs(MEGtimecourse5Hz[which(includedboth==1),3,])
+  MEGmaskindex5C[1,] <- colMeans(20*log10(monratios))
+  MEGmaskindexSE5C[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+  includedboth <- isincluded[1,]*isincluded[4,]*isCON
+  dichratios <- abs(MEGtimecourse5Hz[which(includedboth==1),1,])/abs(MEGtimecourse5Hz[which(includedboth==1),4,])
+  MEGmaskindex5C[2,] <- colMeans(20*log10(dichratios))
+  MEGmaskindexSE5C[2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+
+  MEGmaskindex5A <- matrix(0,nrow=2,ncol=8008)
+  MEGmaskindexSE5A <- matrix(0,nrow=2,ncol=8008)
+  includedboth <- isincluded[1,]*isincluded[3,]*isASC
+  monratios <- abs(MEGtimecourse5Hz[which(includedboth==1),1,])/abs(MEGtimecourse5Hz[which(includedboth==1),3,])
+  MEGmaskindex5A[1,] <- colMeans(20*log10(monratios))
+  MEGmaskindexSE5A[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+  includedboth <- isincluded[1,]*isincluded[4,]*isASC
+  dichratios <- abs(MEGtimecourse5Hz[which(includedboth==1),1,])/abs(MEGtimecourse5Hz[which(includedboth==1),4,])
+  MEGmaskindex5A[2,] <- colMeans(20*log10(dichratios))
+  MEGmaskindexSE5A[2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+
+  MEGmaskindex7C <- matrix(0,nrow=2,ncol=8008)
+  MEGmaskindexSE7C <- matrix(0,nrow=2,ncol=8008)
+  includedboth <- isincluded[2,]*isincluded[3,]*isCON
+  monratios <- abs(MEGtimecourse7Hz[which(includedboth==1),2,])/abs(MEGtimecourse7Hz[which(includedboth==1),3,])
+  MEGmaskindex7C[1,] <- colMeans(20*log10(monratios))
+  MEGmaskindexSE7C[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+  includedboth <- isincluded[2,]*isincluded[4,]*isCON
+  dichratios <- abs(MEGtimecourse7Hz[which(includedboth==1),2,])/abs(MEGtimecourse7Hz[which(includedboth==1),4,])
+  MEGmaskindex7C[2,] <- colMeans(20*log10(dichratios))
+  MEGmaskindexSE7C[2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+
+  MEGmaskindex7A <- matrix(0,nrow=2,ncol=8008)
+  MEGmaskindexSE7A <- matrix(0,nrow=2,ncol=8008)
+  includedboth <- isincluded[2,]*isincluded[3,]*isASC
+  monratios <- abs(MEGtimecourse7Hz[which(includedboth==1),2,])/abs(MEGtimecourse7Hz[which(includedboth==1),3,])
+  MEGmaskindex7A[1,] <- colMeans(20*log10(monratios))
+  MEGmaskindexSE7A[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+  includedboth <- isincluded[2,]*isincluded[4,]*isASC
+  dichratios <- abs(MEGtimecourse7Hz[which(includedboth==1),2,])/abs(MEGtimecourse7Hz[which(includedboth==1),4,])
+  MEGmaskindex7A[2,] <- colMeans(20*log10(dichratios))
+  MEGmaskindexSE7A[2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+
+      if (nbootstraps>0){
+      clustoutM <- clustercorrect(CgroupM,AgroupM,paired=FALSE,nresamples=nbootstraps)
+      clustoutD <- clustercorrect(CgroupD,AgroupD,paired=FALSE,nresamples=nbootstraps)    
+    }
+
+  times <- ((1:8008)-1001)/1001
+
+  for (masktype in 1:2){
+
+    postscript(paste0("MEGtimecourse",masktype,"a.ps"), horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
 
     plotlims <- c(-1,7,-3,6)
+    ticklocsx <- -1:7
     ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
@@
     if (plotsmoothed==0){
-polygon(times[c(1:8000,8000:1)],c(EEGmaskindex7L[masktype,]+EEGmaskindexSE7L[masktype,],EEGmaskindex7L[masktype,8000:1]-EEGmaskindexSE7L[masktype,8000:1]),col=colpal[2],border=NA)
-polygon(times[c(1:8000,8000:1)],c(EEGmaskindex7H[masktype,]+EEGmaskindexSE7H[masktype,],EEGmaskindex7H[masktype,8000:1]-EEGmaskindexSE7H[masktype,8000:1]),col=colpal[3],border=NA)
-
-lines(times,EEGmaskindex7L[masktype,],col=colpal[2],lwd=2)
-lines(times,EEGmaskindex7H[masktype,],col=colpal[3],lwd=2)
+      polygon(times[c(1:8008,8008:1)],c(MEGmaskindexC[masktype,]+MEGmaskindexSEC[masktype,],MEGmaskindexC[masktype,8008:1]-MEGmaskindexSEC[masktype,8008:1]),col=colpal[4],border=NA)
+      polygon(times[c(1:8008,8008:1)],c(MEGmaskindexA[masktype,]+MEGmaskindexSEA[masktype,],MEGmaskindexA[masktype,8008:1]-MEGmaskindexSEA[masktype,8008:1]),col=colpal[5],border=NA)
+
+      lines(times,MEGmaskindexC[masktype,],col=colpal[4],lwd=2)
+      lines(times,MEGmaskindexA[masktype,],col=colpal[5],lwd=2)
     }
@@
     if (plotsmoothed==1){
-U <- smooth.spline(times,EEGmaskindex7L[masktype,]+EEGmaskindexSE7L[masktype,],df=20)
-L <- smooth.spline(times,EEGmaskindex7L[masktype,]-EEGmaskindexSE7L[masktype,],df=20)
-polygon(times[c(1:8000,8000:1)],c(U$y,L$y[8000:1]),col=colpal[2],border=NA)
-
-U <- smooth.spline(times,EEGmaskindex7H[masktype,]+EEGmaskindexSE7H[masktype,],df=20)
-L <- smooth.spline(times,EEGmaskindex7H[masktype,]-EEGmaskindexSE7H[masktype,],df=20)
-polygon(times[c(1:8000,8000:1)],c(U$y,L$y[8000:1]),col=colpal[3],border=NA)
-
-L <- smooth.spline(times,EEGmaskindex7L[masktype,],df=20)
-lines(L$x,L$y,col=colpal[2],lwd=2)
-L <- smooth.spline(times,EEGmaskindex7H[masktype,],df=20)
-lines(L$x,L$y,col=colpal[3],lwd=2)
+      U <- smooth.spline(times,MEGmaskindexC[masktype,]+MEGmaskindexSEC[masktype,],df=20)
+      L <- smooth.spline(times,MEGmaskindexC[masktype,]-MEGmaskindexSEC[masktype,],df=20)
+      U$y[which(U$y<(-3))] <- -3
+      L$y[which(L$y<(-3))] <- -3
+      U$y[which(U$y>6)] <- 6
+      L$y[which(L$y>6)] <- 6
+      polygon(times[c(1:8008,8008:1)],c(U$y,L$y[8008:1]),col=colpal[4],border=NA)
+
+      U <- smooth.spline(times,MEGmaskindexA[masktype,]+MEGmaskindexSEA[masktype,],df=20)
+      L <- smooth.spline(times,MEGmaskindexA[masktype,]-MEGmaskindexSEA[masktype,],df=20)
+      U$y[which(U$y<(-3))] <- -3
+      L$y[which(L$y<(-3))] <- -3
+      U$y[which(U$y>6)] <- 6
+      L$y[which(L$y>6)] <- 6
+      polygon(times[c(1:8008,8008:1)],c(U$y,L$y[8008:1]),col=colpal[5],border=NA)
+
+      L <- smooth.spline(times,MEGmaskindexC[masktype,],df=20)
+      L$y[which(L$y<(-3))] <- -3
+      L$y[which(L$y>6)] <- 6
+      lines(L$x,L$y,col=colpal[4],lwd=2)
+      L <- smooth.spline(times,MEGmaskindexA[masktype,],df=20)
+      L$y[which(L$y<(-3))] <- -3
+      L$y[which(L$y>6)] <- 6
+      lines(L$x,L$y,col=colpal[5],lwd=2)
+    }
+
+      if (nbootstraps>0){
+        if (masktype==1){
+    for (n in 1:clustoutM$nclusters){
+      temp <- unlist(clustoutM$clusterpoints[n])
+      lines(times[temp[c(1,length(temp))]],c(-1.5, -1.5),lwd=2)
+    }}
+        if (masktype==2){
+    for (n in 1:clustoutD$nclusters){
+      temp <- unlist(clustoutD$clusterpoints[n])
+      lines(times[temp[c(1,length(temp))]],c(-1.5, -1.5),lwd=2)
+    }}   
       }
@@
   }
+
+  PostScriptTrace(paste('AQplot1.ps',sep=''))
+  e1a <- readPicture('AQplot1.ps.xml')
+  for (n in 1:length(e1a@paths)){
+    temp <- class(e1a@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e1a@paths[n]$path@rgb))<765){e1a@paths[n]$path@rgb <- addalpha(e1a@paths[n]$path@rgb,alpha=0.2)}}}
+
+    PostScriptTrace(paste('AQplot2.ps',sep=''))
+  e1b <- readPicture('AQplot2.ps.xml')
+  for (n in 1:length(e1b@paths)){
+    temp <- class(e1b@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e1b@paths[n]$path@rgb))<765){e1b@paths[n]$path@rgb <- addalpha(e1b@paths[n]$path@rgb,alpha=0.2)}}}
+
+    PostScriptTrace(paste('AQplot3.ps',sep=''))
+  e1c <- readPicture('AQplot3.ps.xml')
+  for (n in 1:length(e1c@paths)){
+    temp <- class(e1c@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e1c@paths[n]$path@rgb))<765){e1c@paths[n]$path@rgb <- addalpha(e1c@paths[n]$path@rgb,alpha=0.2)}}}
+
+  PostScriptTrace(paste('Ptimecourse.ps',sep=''))
+  e2a <- readPicture('Ptimecourse.ps.xml')
+  for (n in 1:length(e2a@paths)){
+    temp <- class(e2a@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e2a@paths[n]$path@rgb))<765){e2a@paths[n]$path@rgb <- addalpha(e2a@paths[n]$path@rgb,alpha=0.2)}}}
+
+  PostScriptTrace(paste('timecourse1all.ps',sep=''))
+  e4 <- readPicture('timecourse1all.ps.xml')
+  for (n in 1:length(e4@paths)){
+    temp <- class(e4@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e4@paths[n]$path@rgb))<765){e4@paths[n]$path@rgb <- addalpha(e4@paths[n]$path@rgb,alpha=0.2)}}}
+
+  PostScriptTrace(paste('timecourse2all.ps',sep=''))
+  e5 <- readPicture('timecourse2all.ps.xml')
+  for (n in 1:length(e5@paths)){
+    temp <- class(e5@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e5@paths[n]$path@rgb))<765){e5@paths[n]$path@rgb <- addalpha(e5@paths[n]$path@rgb,alpha=0.2)}}}
+
+  PostScriptTrace(paste('MEGtimecourse1a.ps',sep=''))
+  e8 <- readPicture('MEGtimecourse1a.ps.xml')
+  for (n in 1:length(e8@paths)){
+    temp <- class(e8@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e8@paths[n]$path@rgb))<765){e8@paths[n]$path@rgb <- addalpha(e8@paths[n]$path@rgb,alpha=0.2)}}}
+
+  PostScriptTrace(paste('MEGtimecourse2a.ps',sep=''))
+  e9 <- readPicture('MEGtimecourse2a.ps.xml')
+  for (n in 1:length(e9@paths)){
+    temp <- class(e9@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e9@paths[n]$path@rgb))<765){e9@paths[n]$path@rgb <- addalpha(e9@paths[n]$path@rgb,alpha=0.2)}}}
+
+  pdf('temp/figures/Fig4.pdf', bg="transparent", height = 10, width = 12)
+  par(mar=c(0.1,0.1,0.1,0.1))
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
+
+  grid.picture(e1a,x=1/6,y=5/6,width=0.33,height=1)
+  grid.picture(e1b,x=1/6,y=3/6,width=0.33,height=1)
+  grid.picture(e1c,x=1/6,y=1/6,width=0.33,height=1)
+
+  grid.picture(e2a,x=3/6,y=5/6,width=0.33,height=1)
+  grid.picture(e4,x=3/6,y=3/6,width=0.33,height=1)
+  grid.picture(e5,x=5/6,y=3/6,width=0.33,height=1)
+  grid.picture(e8,x=3/6,y=1/6,width=0.33,height=1)
+  grid.picture(e9,x=5/6,y=1/6,width=0.33,height=1)
+
+  text(0.01,1,'(a)',pos=4,cex=2)
+  text(0.01,0.64,'(b)',pos=4,cex=2)
+  text(0.01,0.28,'(c)',pos=4,cex=2)
+  text(0.375,1,'(d)',pos=4,cex=2)
+  text(0.375,0.64,'(e)',pos=4,cex=2)
+  text(0.735,0.64,'(f)',pos=4,cex=2)
+  text(0.375,0.28,'(g)',pos=4,cex=2)
+  text(0.735,0.28,'(h)',pos=4,cex=2)
+
+  text(0.47,1,'Binocular',pos=4,cex=1.5)
+  text(0.47,0.64,'Monocular',pos=4,cex=1.5)
+  text(0.83,0.64,'Dichoptic',pos=4,cex=1.5)
+  text(0.47,0.28,'Monocular',pos=4,cex=1.5)
+  text(0.83,0.28,'Dichoptic',pos=4,cex=1.5)
+
+  legend(0.78,0.9,c('Low AQ/control','High AQ/autism'), lwd=4,col=colpal[4:5],bty='n')
+
+  dev.off()
+
+  file.remove(c('AQplot1.ps','AQplot2.ps','AQplot3.ps'))
+  file.remove(c('AQplot1.ps.xml','AQplot2.ps.xml','AQplot3.ps.xml'))
+  file.remove(c('Ptimecourse.ps','Ptimecourse.ps.xml'))
+  file.remove(c('timecourse1all.ps','timecourse1all.ps.xml'))
+  file.remove(c('timecourse2all.ps','timecourse2all.ps.xml'))
+  file.remove(c('MEGtimecourse1a.ps','MEGtimecourse1a.ps.xml'))
+  file.remove(c('MEGtimecourse2a.ps','MEGtimecourse2a.ps.xml'))
+
 }
@@
 
-Participants showed a wide range of scores on both the AQ and SPQ scales, which were negatively correlated (Fig 3a; R = , p < ).
-We again performed a median split by AQ on the EEG data, and calculated the timecourse of the EEG response and suppression ratios for each group (Figure 3b,c).
-
-Finally, we split the data set by median AQ score (see Figure 1g).
-Averaging across frequency, the low AQ group showed a strong increase over the first 4 seconds of the trial, whereas the high AQ group showed a much shallower change over the same time period (Figure 1h).
-
-## Discussion
-
-Priors, Dickinson 2014 oblique effect
-
-## Methods
+```{r AQanalysis, fig.cap="Analysis of the effect of autistic traits on normalization reweighting.
+Panels (a-c) show distributions of AQ scores across the three data sets.
+Panels (d-h) show timecourses of suppression averaged across stimulation frequency, and split by AQ score (d-f) or autism status (g, h).
+Panels (d,e,g) are for binocular or monocular presentation, and panels (f,h) are for dichoptic presentation.
+Shaded regions in panels (d-h) indicate ±1SE across participants, and black points at y = 0.8 indicate significant differences between groups.", fig.align="center", fig.width=0.5, echo=FALSE}
+
+knitr::include_graphics('temp/figures/Fig4.pdf')
+
+```
+
+To investigate whether normalization reweighting effects differ with respect to autistic traits, we then split each dataset (averaged across temporal frequency) using median AQ score (for the EEG experiments) or according to diagnostic group (autism vs controls) for the MEG data.
+Figure \@ref(fig:AQanalysis)a-c shows distributions of AQ scores for each experiment, and indicates for the pilot and EEG data which participants were in the high (purple) and low (green) AQ groups.
+The median AQ scores were `r round(median(pilotAQ),digits=0)` for the pilot data, and `r median(allAQ)` for the EEG data, consistent with previous results for the general population [@Baron-Cohen2001].
+In the MEG experiment, AQ scores for the autism group (mean `r round(mean(MEG_A),digits=1)`) and the control group (mean `r round(mean(MEG_C),digits=1)`) were significantly different (*t* = `r format(round(t$statistic,digits=2),nsmall=2)`, *df* = `r round(t$parameter,digits=1)`, *p* < 0.001), with minimal overlap (one participant with an autism diagnosis had an AQ score marginally lower than the highest AQ scores from the control group).
+
+We compared the timecourse of suppression between groups using a nonparametric cluster correction approach [@Maris2007] to control the type I error rate.
+Significant clusters are indicated at y = 0.8 in panels d-h of Figure \@ref(fig:AQanalysis).
+Despite some occasionally significant clusters, there is no clear or consistent difference between groups across our three data sets.
+In particular, none of the significant clusters occur during the first few seconds of stimulus onset, when reweighting takes place.
+We also compared suppression ratios calculated on Fourier components for the full trial, and found no significant effects of autism on suppression strength.
+We therefore conclude that autism/AQ score is not associated with normalization reweighting, or the strength of suppression more generally.
+
+# Discussion
+
+We found evidence of dynamic normalization reweighting across three separate datasets.
+Suppression increased significantly during the first 2-5 seconds of stimulus presentation, though with some variation across temporal frequency.
+Reweighting had a similar timecourse for monocular and dichoptic stimulus presentation, and was apparent as early as V1.
+We did not find compelling differences associated with autism, or high vs low autistic traits.
+In the remainder of this section we will discuss possible explanations for temporal frequency differences, evidence for inhibitory differences in autism, and more general implications of dynamic normalization reweighting.
+
+One important question is whether the dynamic increase in suppression can be explained by the stimulus onset transient.
+This is a possibility that cannot be ruled out for some of our data.
+For example, the steep increase in suppression in Figure \@ref(fig:EEGdata)f has a similar timecourse to the onset transient in Figure \@ref(fig:EEGdata)d.
+However, there are also counterexamples where suppression continues to increase well beyond the first 1 second of stimulus presentation (e.g.
+Figure \@ref(fig:EEGdata)e).
+It is currently unclear why there appear to be such substantial differences between temporal frequency conditions, especially with such similar frequencies (5 and 7Hz).
+However the differences are relatively consistent across experiments.
+For example, 5Hz flicker produces a more gradual increase in suppression across all three data sets, compared with 7Hz flicker.
+These differences may be a consequence of visual channels with different temporal tuning interacting with the stimulation frequency, as well as any nonlinearities that govern suppression.
+Or there could be an asymmetry, whereby the relative temporal frequency between the two stimulus components affects the character of suppression [@Liza2022].
+We hope that in future dynamic models of early vision [e.g.
+@Zhou2019] will be able to explain these differences.
+
+The relationship between normalization reweighting and other forms of visual plasticity is currently unclear.
+One phenomenon that might be closely related to our dichoptic effect is the change in interocular suppression that occurs when one eye is patched for a period of time [@Lunghi2011].
+In the patching paradigm, the inputs to the two eyes are uncorrelated while one eye is patched, which the normalization reweighting model predicts should reduce suppression between the eyes.
+Most studies using patching have focussed on the resulting imbalance between the patched and non-patched eye, in which the patched eye contributes more to binocular single vision than the non-patched eye.
+In principle this could be due to increased suppression of the non-patched eye (inconsistent with normalization reweighting), or reduced suppression of the patched eye (consistent with normalization reweighting).
+It is difficult to distinguish these possibilities using paradigms that assess the balance between the two eyes, such as the binocular rivalry paradigm from the original @Lunghi2011 study.
+However subsequent work has shown that patching increases the patched eye's response [@Zhou2015], and reduces both dichoptic masking [@Baldwin2018] and levels of the inhibitory neurotransmitter GABA [@Lunghi2015].
+All of these findings are consistent with a reweighting account.
+
+Participants in Experiments 2 & 3 also completed the sensory perception quotient (SPQ) scale.
+SPQ scores showed significant negative correlation with AQ for both data sets (EEG data, *r* = `r round(corEEG$estimate,digits=2)`, *p* < `r ceiling(1000*corEEG$p.value)/1000`; MEG data, *r* = `r round(corMEG$estimate,digits=2)`, *p* = `r round(corMEG$p.value,digits=3)`) with effect sizes comparable to those reported previously [@Tavassoli2014].
+We also conducted an exploratory analysis of the EEG data from Experiment 2, splitting participants by SPQ instead of AQ.
+However this analysis did not reveal any convincing differences in normalization reweighting either.
+Our preregistration also proposed to replicate our earlier finding of a reduced second harmonic response in participants with autism/high AQ scores.
+However the changes to the experimental design greatly reduced the second harmonic response in both experiments, such that it could not be observed reliably (see Figures \@ref(fig:EEGdata)b and \@ref(fig:MEGdata)b).
+We were therefore not confident in conducting this analysis.
+We suspect that the increase in spatial frequency from 0.5 c/deg in the @Vilidaite2018 study to 2 c/deg here is most likely responsible for the dramatically reduced second harmonic response.
+
+The idea that the dynamic balance of inhibition and excitation might be different in autism [@Rubenstein2003; @Rosenberg2015] has compelling face validity.
+For example individuals with autism often report difficulties with changes in their sensory environment, which might be due to gain control processes failing to adapt appropriately.
+Indeed, there is experimental evidence of reduced adaptation across various domains [@Pellicano2007; @Turi2015], which is predicted by some autism models [@Pellicano2012].
+However this appears not to extend to changes in normalization reweighting, despite the link between reweighting and adaptation [@Westrick2016].
+
+## Conclusions
+
+We investigated the timecourse of normalization reweighting across three datasets, with a total of 220 participants.
+We found clear evidence that suppression increases during the first 2-5 seconds of stimulus presentation, though there were differences across frequency that are currently unexplained.
+We did not find evidence of autism-related differences in either the magnitude or timecourse of suppression.
+Our results support an emerging theory that suppression is a dynamic process that allows sensory systems to recalibrate according to their recent history.
+
+# Methods
+
+## Participants
+
+Experiment 1 was completed by 100 adult participants (32 male, 68 female; mean age 21.9) in early 2015, and first reported by @Vilidaite2018.
+Here we reanalysed the dataset, and report the results of masking conditions not previously published.
+Experiment 2 was completed by 100 adult participants (23 male, 74 female, 3 other/not stated; mean age 22.1) in early 2022.
+Experiment 3 was completed by 10 adults (2 male, 8 female) with a clinical diagnosis of autism, and 10 control participants who were closely matched for age (means of `r t_age$estimate[1]` and `r t_age$estimate[2]`, *t* = `r format(round(abs(t_age$statistic),digits=2))`, *df* = `r t_age$parameter`, *p* = `r format(round(abs(t_age$p.value),digits=2))`) and exactly matched for gender.
+Procedures in Experiments 1 and 2 were approved by the ethics committee of the Department of Psychology at the University of York.
+Procedures for Experiment 3 were approved by the ethics committee of the York Neuroimaging Centre.
+All participants provided written informed consent.
+
+## Apparatus and stimuli
+
+In Experiments 1 and 2, stimuli were presented using a ViewPixx LCD display device (VPixx Technologies, Canada) with a resolution of 1920 $\times$ 1080 pixels and a refresh rate of 120Hz.
+The display was gamma corrected using a Minolta LS110 photometer.
+In Experiment 2, participants wore active stereo shutter glasses (NVidia 3D Vision 2) that were synchronised with the display using an infra-red signal.
+EEG data were collected using a 64-channel Waveguard cap, and were amplified and digitised at 1000Hz using an ANT Neuroscan system.
+Electrode impedance was maintained below 5k$\Omega$, and referenced to a whole-head average.
+
+In Experiment 3, stimuli were presented using a ProPixx DLP projector (VPixx Technologies) running at 120Hz.
+Stereo presentation was enabled using a circular polariser that was synchronised with the projector refresh, and participants wore passive polarised glasses during the experiment.
+DLP projectors are perfectly linear, so gamma correction was not required.
+Data were acquired using a refurbished 248-channel 4D Neuroimaging Magnes 3600 MEG scanner, recording at 1001Hz.
+Participant head shape was digitised using a Polhemus Fastrak device, and head position was recorded at the start and end of each block by passing current through 5 position coils placed at fiducial points on the head.
+We also obtained structural MRI scans using a 3 Tesla Siemens Magnetom Prisma scanner to aid in source localisation.
+Two participants were not available for MRI scans, so we used the MNI ICBM152 template brain [@Fonov2011] for these individuals.
+
+Stimuli were patches of sine wave grating with a diameter of 2 degrees, flickering sinusoidally (on/off flicker) at either 5Hz or 7Hz.
+In Experiment 1 the gratings had a spatial frequency of 0.5c/deg, and in Experiments 2 & 3 this was increased to 2c/deg.
+A symmetrical array of 36 individual patches tiled the display.
+In Experiment 1 the patch orientation was randomly selected on each trial, and all patches had the same orientation.
+In Experiments 2 & 3 each patch had a random orientation, which was intended to prevent any sequential effects between trials with similar orientations.
+The central patch was omitted and replaced by a fixation marker constructed from randomly overlaid squares.
+During each experiment, the fixation marker could be resampled on each trial with a probability of 0.5.
+Participants were instructed to monitor the fixation marker and count the number of times it changed throughout the experiment.
+This was intended to maintain attention towards the display and keep participants occupied.
+
+Participants also completed either the short AQ [@Hoekstra2011] in Experiment 1, or the full AQ [@Baron-Cohen2001] in Experiments 2 and 3.
+For comparison across experiments, we rescaled the short AQ to the same range as the full AQ (0-50).
+In Experiments 2 and 3, the sensory perception quotient (SPQ) questionnaire [@Tavassoli2014] was also completed.
+
+## Procedures
+
+In Experiment 1, target stimuli flickering at 7Hz were presented at a range of contrasts (1 - 64%).
+In half of the conditions a superimposed orthogonal mask of 32% contrast was presented simultaneously, flickering at 5Hz.
+Stimuli were displayed for trials of 11 seconds, with a 3 second inter-trial interval.
+The experiment consisted of 4 blocks of trials, each lasting around 10 minutes, and resulting in 8 repetitions of each condition.
+Participants viewed the display from 57cm, were comfortably seated in an upright position, and were able to rest between blocks.
+Low latency 8-bit digital triggers transmitted the trial onset and condition information directly to the EEG amplifier.
+
+The procedure for Experiment 2 was very similar, except that participants also wore stereo shutter glasses during the experiment.
+There were four conditions: (i) monocular presentation of a 5Hz stimulus of 48% contrast, (ii) monocular presentation of a 7Hz stimulus of 48% contrast, (iii) monocular presentation of both stimuli superimposed at right angles, and (iv) dichoptic presentation of both stimuli at right angles (i.e.
+one stimulus to the left eye, one to the right eye).
+Eye of presentation was pseudo-randomised to ensure equal numbers of left-eye and right-eye presentations.
+The trial duration was 6 seconds, with a 3 second inter-trial interval.
+Participants completed 3 blocks, each lasting around 10 minutes, resulting in a total of 48 repetitions of each condition.
+Experiment 3 was identical, except that the projector screen was viewed from a distance of 85cm.
+
+## Data analysis
+
+EEG data from Experiments 1 and 2 were first imported into Matlab using components of the EEGlab toolbox [@Delorme2004], and converted into a compressed ASCII format.
+Primary data analysis was then conducted using a bespoke _R_ script.
+In brief, we epoched each trial and extracted the average timecourse across four occipital electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}), and then calculated the Fourier transform of this average waveform.
+We excluded trials for which the Mahalanobis distance of the complex Fourier components exceeded 3 [for details see @Baker2021].
+This resulted in % of trials being excluded for Experiment 1, % of trials for Experiment 2, and % of trials for Experiment 3.
+Next we averaged the waveforms across all remaining trials, and calculated the Fourier transform in a 1-second sliding window to generate timecourses for each participant.
+We divided the timecourse for the target-only condition by the timecourse for the target + mask condition to produce a suppression ratio.
+These were then converted to logarithmic (dB) units for averaging, calculation of standard errors, and statistical comparisons.
+For display purposes we smoothed the timecourses using a cubic spline function, however all statistical comparisons used the unsmoothed data.
+
+For Experiment 3, we performed source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm, implemented in Brainstorm [@Tadel2011].
+Structural MRI scans were processed using Freesurfer [@Dale1999] to generate a 3D mesh of the head and brain, and we calculated source weights for each block with reference to a 5-minute empty room recording, usually recorded on the day of the experiment.
+The matrix of source weights for each block was used in a custom Matlab script to extract signals from V1, identified using the probabilistic maps of @Wang2015.
+These signals were then imported into R for the main analysis, which was consistent with the EEG analysis described above.
+
+To make comparisons between groups of participants across time, we used a non-parametric cluster correction technique [@Maris2007] based on t-tests.
+Clusters were identified as temporally adjacent observations that were all statistically significant, and a summed t-value was calculated for each cluster.
+A null distribution was then generated by randomising group membership and recalculating the summed t-value for the largest cluster, and repeating this procedure `r nbootstraps` times.
+Clusters were considered significant if they fell outside of the 95% confidence limits of the null distribution.
+We adapted this approach to test for significantly increasing suppression by conducting one-way t-tests between time points separated by `r timeoffset`ms, and repeating the cluster correction procedure as described above.
+
+## Preregistration, data and code availability
+
+Following a preliminary analysis of the data from Experiment 1, we preregistered our hypotheses and analysis plan for Experiments 2 and 3 on the Open Science Framework website.
+The preregistration document, along with raw and processed data, and analysis scripts, are publicly available at the project repository: https://osf.io/ab3yv/
+
+# Acknowledgements
+
+Supported by BBSRC grant BB/V007580/1 awarded to DHB and ARW. We are grateful to all of the participants who took part in the experiments reported here.
+
+# References

### 2022-09-30 manuscript.tex
Update of manuscript

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Temporal Dynamics of Normalization Reweighting},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Temporal Dynamics of Normalization Reweighting}
\author{Daniel H. Baker, Daniela Marinova, Richard Aveyard, Lydia Hargreaves, Alice Renton,\\
Ruby Castellani, Phoebe Hall, Miriam Harmens, Georgia Holroyd, Beth Nicholson,\\
Emily Williams, Hannah M. Hobson \& Alex R. Wade}
\date{2022-09-11}

\begin{document}
\maketitle

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

For decades, neural suppression in early visual cortex has been thought to be fixed. But recent work has challenged this assumption by showing that suppression can be \emph{reweighted} based on recent history; when pairs of stimuli are repeatedly presented together, suppression between them strengthens. Here we investigate the temporal dynamics of this process using a steady-state VEP paradigm that provides a time-resolved, direct index of suppression between pairs of stimuli flickering at different frequencies (5 and 7Hz). Our initial analysis of an existing EEG dataset (N=100) indicated that suppression increases substantially during the first 2-5 seconds of stimulus presentation (with some variation across stimulation frequency). We then collected new EEG data (N=100) replicating this finding for both monocular and dichoptic mask arrangements in a preregistered study designed to measure reweighting. A third experiment (N=20) used source localized MEG, and found that these effects are apparent in primary visual cortex (V1), consistent with results from neurophysiological work. Because long-standing theories propose inhibition/excitation differences in autism, we also compared reweighting between individuals with high vs low autistic traits, and with and without an autism diagnosis, across our 3 data sets (total N=220). We find no compelling differences in reweighting that are associated with autism. Our results support the normalization reweighting model, and indicate that for prolonged stimulation, increases in suppression occur on the order of 2-5 seconds after stimulus onset.

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Suppressive interactions between neurons are ubiquitous in the nervous system, and normalization (or gain control) processes are considered a canonical neuronal computation (Carandini and Heeger, 2011). Yet for decades the strength of suppression was treated as fixed, largely due to the observation that adapting to one stimulus does not decrease its suppressive potency (Foley and Chen, 1997; Freeman et al., 2002). This orthodoxy was recently challenged by a series of innovative studies showing that normalization can be `reweighted' by recent history (Aschner et al., 2018; Westrick et al., 2016; Yiltiz et al., 2020). Specifically, when pairs of stimuli are repeatedly presented together, their neural representations come to suppress each other more strongly. This suggests that, far from being fixed, normalization is a dynamic process that is continuously updated by the sensory environment. Here, our objectives were to determine if the timecourse of these changes can be measured non-invasively from the human brain, assess if they occur similarly in distinct suppressive pathways, and determine whether they differ across the population as a function of autistic traits.

Plastic changes within the visual system occur over multiple timescales (see Webster, 2015 for a recent review). In the retina, adaptation to complete darkness takes around 30 minutes (Lamb and Pugh, 2006), and has established physiological substrates (i.e.~the regeneration rate of chemicals in different photoreceptor classes). Cortical forms of adaptation to cues such as stimulus contrast (Blakemore and Campbell, 1969), orientation (Gibson and Radner, 1937) and motion (Mather et al., 2008) can be observed within a few seconds, but also build up over durations on the order of several minutes (Greenlee et al., 1991). A recent form of binocular plasticity (Lunghi et al., 2011), in which one eye is patched and subsequently contributes more to binocular vision, requires more than an hour. Other types of adaptation have been identified with changes occurring over longer time periods, such as over several hours (Kwon et al., 2009) or days (Haak et al., 2014). Finally adaptation to specific combinations of orientation and colour (the McCollough, 1965 effect) can persist for several weeks (Jones and Holding, 1975), even with a brief induction period. Previous work on normalization reweighting has involved adapting sequences of around 40 -- 60s (Aschner et al., 2018; Yiltiz et al., 2020), though it is possible that reweighting might occur faster than this, consistent with other types of contrast adaptation.

Normalization itself is not a single process. Multiple suppressive pathways have been identified in the visual system, including between stimuli differing in orientation (Foley, 1994; Heeger, 1992), eye-of-origin (Legge, 1979; Sengpiel and Blakemore, 1994) and spatial position (Cannon and Fullenkamp, 1991; Petrov, 2005). At present there is evidence of normalization reweighting between stimuli with orthogonal orientations (Aschner et al., 2018), and adjacent spatial positions (Yiltiz et al., 2020). We anticipated that interocular suppression should also be subject to reweighting, but that there might be differences in the dynamics across suppressive pathways. This is plausible, given that suppression within and between the eyes has different spatiotemporal tuning (Meese and Baker, 2009), and dichoptic masking can be reduced by adapting to the mask (Baker et al., 2007; Li et al., 2005; Sengpiel and Vorobyov, 2005), unlike within-eye masking. Dynamic fluctuations in interocular suppression are a key feature of binocular rivalry (Alais et al., 2010; Wilson, 2003), for which autism-related differences have also been reported (Robertson et al., 2013).

Atypical sensory experience is widely reported by individuals on the autism spectrum (MacLennan et al., 2022; Simmons et al., 2009), but the causal mechanisms remain unclear. Typical issues include hypersensitivity to intense stimuli such as loud sounds, bright lights and strong odours or flavours. Yet fundamental measures of sensitivity such as visual acuity (Tavassoli et al., 2011), contrast sensitivity (Koh et al., 2010), and audiometric performance (Rosenhall et al., 1999) are not consistently different from neurotypical controls. Theoretical accounts of sensory differences in autism have long proposed that the balance of inhibition and excitation may be disrupted (Rosenberg et al., 2015; Rubenstein and Merzenich, 2003), and there are isolated results that appear consistent with this. For example neural measures of surround suppression are weaker in autism (Schallmo et al., 2020), binocular rivalry is slower (Robertson et al., 2013) and orientation discrimination performance is better (Dickinson et al., 2014). Conversely, other studies have failed to find group differences using paradigms that should be equally dependent on inhibition, such as orientation repulsion (Van de Cruys et al., 2018), repetition suppression (Utzerath et al., 2018) and psychophysical measures of surround suppression (Sandhu et al., 2020). The evidence for atypical inhibition in autism is therefore currently inconclusive.

Our recent work has identified a potential autism-related difference in gain control using steady-state EEG methods. Vilidaite et al. (2018) measured contrast response functions for flickering stimuli in a large group of neurotypical adults, who were split by their autism quotient (AQ, see Baron-Cohen et al., 2001) score. The responses were comparable between high and low AQ groups at the flicker frequency of the stimulus. However at the second harmonic frequency (twice the flicker frequency), the high AQ group showed weaker responses than the low AQ group. This effect was replicated in an independent sample of 12 adults with an autism diagnosis (compared with neurotypical controls). Because second harmonic responses are caused by nonlinear interactions in the visual system (they are absent in a linear system), and divisive suppression is a nonlinearity, this potentially implicates differences in suppression in autism. Furthermore, there appears to be a developmental trajectory, as autistic children tested as part of the same study (Vilidaite et al., 2018) showed weaker responses at both the first and second harmonic frequencies.

In this paper we perform a time-course analysis of a previously published EEG data set, and report two novel pre-registered experiments using EEG and MEG. Our data show that suppression increases substantially during the first 2-5 seconds following stimulus onset, for both monocular and dichoptic masks. Source localisation of MEG data indicate that the reweighting is present as early as primary visual cortex (V1). We also hypothesised that normalization reweighting might differ as a function of autistic traits. The relative novelty of the reweighting framework could explain why any differences have not previously been detected, and why the literature on inhibition in autism is relatively inconclusive. However we did not find convincing support for this hypothesis.

\hypertarget{results}{%
\section{Results}\label{results}}

We began by reanalysing data from a steady-state visually evoked potential (SSVEP) experiment reported by Vilidaite et al. (2018). Participants viewed arrays of flickering gratings of varying contrasts. In some conditions a single grating orientation was present flickering at 7Hz, whereas in other conditions a high contrast `mask' was added at right angles to the target gratings, and flickering at 5Hz. The left panel of Figure \ref{fig:Pilotdata}a shows contrast response functions with and without the mask - the presence of the mask reduces the 7Hz response to the target (blue squares are below the black circles; significant main effect of mask contrast, F(1,99) = 26.52, \emph{p} \textless{} 0.001). Similarly, the right panel of Figure \ref{fig:Pilotdata}a shows that the 5Hz response to the mask was itself suppressed by the presence of high contrast targets (main effect of target contrast on the mask response, F(2.92,288.63) = 46.77, \emph{p} \textless{} 0.001; note that the data from the masking conditions were not reported by Vilidaite et al. (2018)). At both frequencies, responses were localised to the occipital pole (see insets).

\begin{figure}

{\centering \includegraphics{temp/figures/Fig1}

}

\caption{Summary of pilot analysis of data from Vilidiate et al. (2018). Panel (a) shows contrast response functions at the target frequency (7Hz, left) and the mask frequency (5Hz, right). Insets show the distribution of activity across the scalp, with points marking the electrodes over which signals were averaged (Oz, POz, O1 and O2). Panel (b) shows Fourier spectra for the single component stimuli and their combination (plaid). Note the strong second harmonic components at 14Hz and 10Hz. Panel (c) shows timecourses of frequency-locked responses to a single stimulus (black) and the plaid stimulus (blue), compared to baseline (grey). Panel (d) shows the timecourse of suppression at each frequency (7Hz, 5Hz, 14Hz, 10Hz) and their average (black curve). Points around y = 1.8 indicate a significantly increasing ratio. Error bars in panel (a) and shaded regions in panels (c,d) indicate ±1SE, and grey rectangles indicate the timing of stimulus presentation. The larger symbols in panel (a) indicate the conditions used for subsequent analyses.}\label{fig:Pilotdata}
\end{figure}

We then performed a timecourse analysis, in which we analysed each 11-second trial using a sliding 1-second time window. The top panel of Figure \ref{fig:Pilotdata}c shows the response at the target frequency (7Hz) to a single stimulus of 32\% contrast (black), and the response at 7Hz when the 32\% contrast mask is added (blue). Analogous responses are shown at three other frequencies - the mask frequency (5Hz), and the second harmonics of both target and mask frequencies (14Hz, 10Hz), at which strong responses were also found (see spectra in Figure \ref{fig:Pilotdata}b). The reduction in signal strength when the mask component is added illustrates the masking effect.

Taking the ratio of the two timecourses to calculate a masking index reveals that at 7Hz masking increases steeply during the first two seconds of stimulus presentation, and then plateaus for several seconds (blue trace in Figure \ref{fig:Pilotdata}d). A similar pattern is observed at 5Hz (red trace in Figure \ref{fig:Pilotdata}d), as well as at the second harmonics, with some variability in the timecourse across frequencies; for example at 5Hz suppression peaks at around 4 seconds. The black trace shows the average masking ratio across all four frequencies, which rises steeply for just over two seconds and then stays approximately constant until stimulus offset. We conducted cluster-corrected t-tests between ratios separated by 1000ms, testing for an increase in suppression ratio across time (i.e.~a one-sided test). Points at y = 1.8 in Figure \ref{fig:Pilotdata}d indicate time points where the ratio is significantly increasing, and occur mostly during the first 2 seconds of stimulus presentation.

Our initial reanalysis was promising, however the data were noisy despite the large sample size, because each participant contributed only 8 trials (88 seconds) to each condition. We therefore preregistered two new experiments (see \url{https://osf.io/4qudc}) to investigate these effects in greater detail. These had a similar overall design to the Vilidaite et al. (2018) study, with some small changes intended to optimise the study (see Methods). The key differences were that we used shorter trials (because there were few changes in the latter part of the trials shown in Figure \ref{fig:Pilotdata}d), and also focussed all trials into a smaller number of conditions, such that each participant contributed 48 repetitions (288 seconds of data) to each of 4 conditions.

Figure \ref{fig:EEGdata} summarises the results of our EEG experiment testing a further 100 adult participants. Averaged EEG waveforms showed a strong oscillatory component at each of the two stimulus flicker frequencies (Figure \ref{fig:EEGdata}a), which slightly lagged the driving signal. Signals were well-isolated in the Fourier domain (Figure \ref{fig:EEGdata}b), and localised to occipital electrodes. Responses at 7Hz were weaker in the two masking conditions, showing significant changes in response amplitude for both the monocular (\emph{t} = 7.56, \emph{df} = 87, \emph{p} \textless{} 0.001) and dichoptic (\emph{t} = 11.35, \emph{df} = 87, \emph{p} \textless{} 0.001) masks. Dichoptic masking was significantly stronger than monocular masking (\emph{t} = 7.96, \emph{df} = 87, \emph{p} \textless{} 0.001), and a similar pattern was evident at 5Hz.

\begin{figure}

{\centering \includegraphics{temp/figures/Fig2}

}

\caption{Summary of EEG results for N=100 adult participants. Panel (a) shows scalp topographies and averaged waveforms for 5Hz (top) and 7Hz (bottom) stimuli. The black sine wave trace in each panel illustrates the driving contrast modulation, and black points on the scalp topographies indicate electrodes Oz, O1, O2 and POz. Panel (b) shows the Fourier amplitude spectrum for each condition, with clear peaks at 5Hz and 7Hz. Panels (c,d) show timecourses at each frequency for the baseline condition (black), and the monocular (blue) and dichoptic (red) masking conditions. Panels (e,f) show suppression ratios as a function of time for each mask type, with points around y = 0.8 indicating a significantly increasing ratio. Shaded regions in panels (c-f) span ±1SE across participants, and light grey rectangles indicate the period of stimulus presentation.}\label{fig:EEGdata}
\end{figure}

The timecourse at both flicker frequencies showed an initial onset transient, and was then relatively stable for the 6 seconds of stimulus presentation (Figure \ref{fig:EEGdata}c,d). The ratio of target only to target + mask conditions increased over time (Figure \ref{fig:EEGdata}e,f) for both mask types. At 5Hz the increase in masking continued over the first 5 seconds of stimulus presentation (Figure \ref{fig:EEGdata}e; points at y = 0.8 indicate significantly increasing suppression), whereas at 7Hz the increase occurred primarily during the first second after onset (Figure \ref{fig:EEGdata}f). These differences across frequency are consistent with the pilot data (see Figure \ref{fig:Pilotdata}d). Both monocular and dichoptic masks produced similar timecourses of suppression. Overall, this second study confirmed that normalization increases during the first few seconds of a steady-state trial, and extends this finding to dichoptic mask arrangements.

\begin{figure}

{\centering \includegraphics{temp/figures/Fig3}

}

\caption{Summary of MEG results for N=20 adults. Panel (a) shows average SSVEP response in source space, thresholded at SNR=2 (blue, left), and locations of the V1 ROI on the medial surface of both hemispheres (right, red). Panel (b) shows the Fourier spectra for the four experimental conditions, from the most responsive vertex in V1. Panels (c,d) show timecourses at 5Hz and 7Hz, and panels (e,f) show suppression ratios for the monocular and dichoptic conditions at each frequency, with points around y = 0.8 indicating a significantly increasing ratio. Shaded regions in panels (c-f) indicate ±1SE across participants, and light grey rectangles indicate the period of stimulus presentation.}\label{fig:MEGdata}
\end{figure}

Next we repeated the experiment on 20 participants using a 248-channel whole-head cryogenic MEG system. Half of the participants had a diagnosis of autism, and the remainder were age- and gender-matched controls. Source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm (Van Veen et al., 1997) showed strong localisation of steady-state signals at the occipital pole (see Figure \ref{fig:MEGdata}a), and in the Fourier domain (Figure \ref{fig:MEGdata}b). Responses from the most responsive V1 vertex showed a similar timecourse to those of the EEG experiments at both frequencies (Figure \ref{fig:MEGdata}c,d), and showed increasing suppression during the first few seconds of stimulus presentation (Figure \ref{fig:MEGdata}e,f). The normalization reweighting effect was again clearest at 5Hz, especially for the dichoptic condition (red curve in Figure \ref{fig:MEGdata}e). This confirms that the reweighting effects can occur as early as primary visual cortex, consistent with findings from neurophysiology (Aschner et al., 2018). However the data are more variable than for our EEG experiments, and had fewer significant clusters, owing to the smaller sample size for this dataset.

\begin{figure}

{\centering \includegraphics{temp/figures/Fig4}

}

\caption{Analysis of the effect of autistic traits on normalization reweighting. Panels (a-c) show distributions of AQ scores across the three data sets. Panels (d-h) show timecourses of suppression averaged across stimulation frequency, and split by AQ score (d-f) or autism status (g, h). Panels (d,e,g) are for binocular or monocular presentation, and panels (f,h) are for dichoptic presentation. Shaded regions in panels (d-h) indicate ±1SE across participants, and black points at y = 0.8 indicate significant differences between groups.}\label{fig:AQanalysis}
\end{figure}

To investigate whether normalization reweighting effects differ with respect to autistic traits, we then split each dataset (averaged across temporal frequency) using median AQ score (for the EEG experiments) or according to diagnostic group (autism vs controls) for the MEG data. Figure \ref{fig:AQanalysis}a-c shows distributions of AQ scores for each experiment, and indicates for the pilot and EEG data which participants were in the high (purple) and low (green) AQ groups. The median AQ scores were 14 for the pilot data, and 18 for the EEG data, consistent with previous results for the general population (Baron-Cohen et al., 2001). In the MEG experiment, AQ scores for the autism group (mean 36.1) and the control group (mean 16.7) were significantly different (\emph{t} = 6.00, \emph{df} = 14.2, \emph{p} \textless{} 0.001), with minimal overlap (one participant with an autism diagnosis had an AQ score marginally lower than the highest AQ scores from the control group).

We compared the timecourse of suppression between groups using a nonparametric cluster correction approach (Maris and Oostenveld, 2007) to control the type I error rate. Significant clusters are indicated at y = 0.8 in panels d-h of Figure \ref{fig:AQanalysis}. Despite some occasionally significant clusters, there is no clear or consistent difference between groups across our three data sets. In particular, none of the significant clusters occur during the first few seconds of stimulus onset, when reweighting takes place. We also compared suppression ratios calculated on Fourier components for the full trial, and found no significant effects of autism on suppression strength. We therefore conclude that autism/AQ score is not associated with normalization reweighting, or the strength of suppression more generally.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

We found evidence of dynamic normalization reweighting across three separate datasets. Suppression increased significantly during the first 2-5 seconds of stimulus presentation, though with some variation across temporal frequency. Reweighting had a similar timecourse for monocular and dichoptic stimulus presentation, and was apparent as early as V1. We did not find compelling differences associated with autism, or high vs low autistic traits. In the remainder of this section we will discuss possible explanations for temporal frequency differences, evidence for inhibitory differences in autism, and more general implications of dynamic normalization reweighting.

One important question is whether the dynamic increase in suppression can be explained by the stimulus onset transient. This is a possibility that cannot be ruled out for some of our data. For example, the steep increase in suppression in Figure \ref{fig:EEGdata}f has a similar timecourse to the onset transient in Figure \ref{fig:EEGdata}d.~However, there are also counterexamples where suppression continues to increase well beyond the first 1 second of stimulus presentation (e.g.~Figure \ref{fig:EEGdata}e). It is currently unclear why there appear to be such substantial differences between temporal frequency conditions, especially with such similar frequencies (5 and 7Hz). However the differences are relatively consistent across experiments. For example, 5Hz flicker produces a more gradual increase in suppression across all three data sets, compared with 7Hz flicker. These differences may be a consequence of visual channels with different temporal tuning interacting with the stimulation frequency, as well as any nonlinearities that govern suppression. Or there could be an asymmetry, whereby the relative temporal frequency between the two stimulus components affects the character of suppression (Liza and Ray, 2022). We hope that in future dynamic models of early vision (e.g. Groen et al., 2022) will be able to explain these differences.

The relationship between normalization reweighting and other forms of visual plasticity is currently unclear. One phenomenon that might be closely related to our dichoptic effect is the change in interocular suppression that occurs when one eye is patched for a period of time (Lunghi et al., 2011). In the patching paradigm, the inputs to the two eyes are uncorrelated while one eye is patched, which the normalization reweighting model predicts should reduce suppression between the eyes. Most studies using patching have focussed on the resulting imbalance between the patched and non-patched eye, in which the patched eye contributes more to binocular single vision than the non-patched eye. In principle this could be due to increased suppression of the non-patched eye (inconsistent with normalization reweighting), or reduced suppression of the patched eye (consistent with normalization reweighting). It is difficult to distinguish these possibilities using paradigms that assess the balance between the two eyes, such as the binocular rivalry paradigm from the original Lunghi et al. (2011) study. However subsequent work has shown that patching increases the patched eye's response (Zhou et al., 2015), and reduces both dichoptic masking (Baldwin and Hess, 2018) and levels of the inhibitory neurotransmitter GABA (Lunghi et al., 2015). All of these findings are consistent with a reweighting account.

Participants in Experiments 2 \& 3 also completed the sensory perception quotient (SPQ) scale. SPQ scores showed significant negative correlation with AQ for both data sets (EEG data, \emph{r} = -0.35, \emph{p} \textless{} 0.001; MEG data, \emph{r} = -0.57, \emph{p} = 0.011) with effect sizes comparable to those reported previously (Tavassoli et al., 2014). We also conducted an exploratory analysis of the EEG data from Experiment 2, splitting participants by SPQ instead of AQ. However this analysis did not reveal any convincing differences in normalization reweighting either. Our preregistration also proposed to replicate our earlier finding of a reduced second harmonic response in participants with autism/high AQ scores. However the changes to the experimental design greatly reduced the second harmonic response in both experiments, such that it could not be observed reliably (see Figures \ref{fig:EEGdata}b and \ref{fig:MEGdata}b). We were therefore not confident in conducting this analysis. We suspect that the increase in spatial frequency from 0.5 c/deg in the Vilidaite et al. (2018) study to 2 c/deg here is most likely responsible for the dramatically reduced second harmonic response.

The idea that the dynamic balance of inhibition and excitation might be different in autism (Rosenberg et al., 2015; Rubenstein and Merzenich, 2003) has compelling face validity. For example individuals with autism often report difficulties with changes in their sensory environment, which might be due to gain control processes failing to adapt appropriately. Indeed, there is experimental evidence of reduced adaptation across various domains (Pellicano et al., 2007; Turi et al., 2015), which is predicted by some autism models (Pellicano and Burr, 2012). However this appears not to extend to changes in normalization reweighting, despite the link between reweighting and adaptation (Westrick et al., 2016).

\hypertarget{conclusions}{%
\subsection{Conclusions}\label{conclusions}}

We investigated the timecourse of normalization reweighting across three datasets, with a total of 220 participants. We found clear evidence that suppression increases during the first 2-5 seconds of stimulus presentation, though there were differences across frequency that are currently unexplained. We did not find evidence of autism-related differences in either the magnitude or timecourse of suppression. Our results support an emerging theory that suppression is a dynamic process that allows sensory systems to recalibrate according to their recent history.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

Experiment 1 was completed by 100 adult participants (32 male, 68 female; mean age 21.9) in early 2015, and first reported by Vilidaite et al. (2018). Here we reanalysed the dataset, and report the results of masking conditions not previously published. Experiment 2 was completed by 100 adult participants (23 male, 74 female, 3 other/not stated; mean age 22.1) in early 2022. Experiment 3 was completed by 10 adults (2 male, 8 female) with a clinical diagnosis of autism, and 10 control participants who were closely matched for age (means of 21.8 and 22, \emph{t} = 0.18, \emph{df} = 18, \emph{p} = 0.86) and exactly matched for gender. Procedures in Experiments 1 and 2 were approved by the ethics committee of the Department of Psychology at the University of York. Procedures for Experiment 3 were approved by the ethics committee of the York Neuroimaging Centre. All participants provided written informed consent.

\hypertarget{apparatus-and-stimuli}{%
\subsection{Apparatus and stimuli}\label{apparatus-and-stimuli}}

In Experiments 1 and 2, stimuli were presented using a ViewPixx LCD display device (VPixx Technologies, Canada) with a resolution of 1920 \(\times\) 1080 pixels and a refresh rate of 120Hz. The display was gamma corrected using a Minolta LS110 photometer. In Experiment 2, participants wore active stereo shutter glasses (NVidia 3D Vision 2) that were synchronised with the display using an infra-red signal. EEG data were collected using a 64-channel Waveguard cap, and were amplified and digitised at 1000Hz using an ANT Neuroscan system. Electrode impedance was maintained below 5k\(\Omega\), and referenced to a whole-head average.

In Experiment 3, stimuli were presented using a ProPixx DLP projector (VPixx Technologies) running at 120Hz. Stereo presentation was enabled using a circular polariser that was synchronised with the projector refresh, and participants wore passive polarised glasses during the experiment. DLP projectors are perfectly linear, so gamma correction was not required. Data were acquired using a refurbished 248-channel 4D Neuroimaging Magnes 3600 MEG scanner, recording at 1001Hz. Participant head shape was digitised using a Polhemus Fastrak device, and head position was recorded at the start and end of each block by passing current through 5 position coils placed at fiducial points on the head. We also obtained structural MRI scans using a 3 Tesla Siemens Magnetom Prisma scanner to aid in source localisation. Two participants were not available for MRI scans, so we used the MNI ICBM152 template brain (Fonov et al., 2011) for these individuals.

Stimuli were patches of sine wave grating with a diameter of 2 degrees, flickering sinusoidally (on/off flicker) at either 5Hz or 7Hz. In Experiment 1 the gratings had a spatial frequency of 0.5c/deg, and in Experiments 2 \& 3 this was increased to 2c/deg. A symmetrical array of 36 individual patches tiled the display. In Experiment 1 the patch orientation was randomly selected on each trial, and all patches had the same orientation. In Experiments 2 \& 3 each patch had a random orientation, which was intended to prevent any sequential effects between trials with similar orientations. The central patch was omitted and replaced by a fixation marker constructed from randomly overlaid squares. During each experiment, the fixation marker could be resampled on each trial with a probability of 0.5. Participants were instructed to monitor the fixation marker and count the number of times it changed throughout the experiment. This was intended to maintain attention towards the display and keep participants occupied.

Participants also completed either the short AQ (Hoekstra et al., 2011) in Experiment 1, or the full AQ (Baron-Cohen et al., 2001) in Experiments 2 and 3. For comparison across experiments, we rescaled the short AQ to the same range as the full AQ (0-50). In Experiments 2 and 3, the sensory perception quotient (SPQ) questionnaire (Tavassoli et al., 2014) was also completed.

\hypertarget{procedures}{%
\subsection{Procedures}\label{procedures}}

In Experiment 1, target stimuli flickering at 7Hz were presented at a range of contrasts (1 - 64\%). In half of the conditions a superimposed orthogonal mask of 32\% contrast was presented simultaneously, flickering at 5Hz. Stimuli were displayed for trials of 11 seconds, with a 3 second inter-trial interval. The experiment consisted of 4 blocks of trials, each lasting around 10 minutes, and resulting in 8 repetitions of each condition. Participants viewed the display from 57cm, were comfortably seated in an upright position, and were able to rest between blocks. Low latency 8-bit digital triggers transmitted the trial onset and condition information directly to the EEG amplifier.

The procedure for Experiment 2 was very similar, except that participants also wore stereo shutter glasses during the experiment. There were four conditions: (i) monocular presentation of a 5Hz stimulus of 48\% contrast, (ii) monocular presentation of a 7Hz stimulus of 48\% contrast, (iii) monocular presentation of both stimuli superimposed at right angles, and (iv) dichoptic presentation of both stimuli at right angles (i.e.~one stimulus to the left eye, one to the right eye). Eye of presentation was pseudo-randomised to ensure equal numbers of left-eye and right-eye presentations. The trial duration was 6 seconds, with a 3 second inter-trial interval. Participants completed 3 blocks, each lasting around 10 minutes, resulting in a total of 48 repetitions of each condition. Experiment 3 was identical, except that the projector screen was viewed from a distance of 85cm.

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

EEG data from Experiments 1 and 2 were first imported into Matlab using components of the EEGlab toolbox (Delorme and Makeig, 2004), and converted into a compressed ASCII format. Primary data analysis was then conducted using a bespoke \emph{R} script. In brief, we epoched each trial and extracted the average timecourse across four occipital electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}), and then calculated the Fourier transform of this average waveform. We excluded trials for which the Mahalanobis distance of the complex Fourier components exceeded 3 (for details see Baker, 2021). This resulted in \% of trials being excluded for Experiment 1, \% of trials for Experiment 2, and \% of trials for Experiment 3. Next we averaged the waveforms across all remaining trials, and calculated the Fourier transform in a 1-second sliding window to generate timecourses for each participant. We divided the timecourse for the target-only condition by the timecourse for the target + mask condition to produce a suppression ratio. These were then converted to logarithmic (dB) units for averaging, calculation of standard errors, and statistical comparisons. For display purposes we smoothed the timecourses using a cubic spline function, however all statistical comparisons used the unsmoothed data.

For Experiment 3, we performed source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm, implemented in Brainstorm (Tadel et al., 2011). Structural MRI scans were processed using Freesurfer (Dale et al., 1999) to generate a 3D mesh of the head and brain, and we calculated source weights for each block with reference to a 5-minute empty room recording, usually recorded on the day of the experiment. The matrix of source weights for each block was used in a custom Matlab script to extract signals from V1, identified using the probabilistic maps of Wang et al. (2015). These signals were then imported into R for the main analysis, which was consistent with the EEG analysis described above.

To make comparisons between groups of participants across time, we used a non-parametric cluster correction technique (Maris and Oostenveld, 2007) based on t-tests. Clusters were identified as temporally adjacent observations that were all statistically significant, and a summed t-value was calculated for each cluster. A null distribution was then generated by randomising group membership and recalculating the summed t-value for the largest cluster, and repeating this procedure 1000 times. Clusters were considered significant if they fell outside of the 95\% confidence limits of the null distribution. We adapted this approach to test for significantly increasing suppression by conducting one-way t-tests between time points separated by 1000ms, and repeating the cluster correction procedure as described above.

\hypertarget{preregistration-data-and-code-availability}{%
\subsection{Preregistration, data and code availability}\label{preregistration-data-and-code-availability}}

Following a preliminary analysis of the data from Experiment 1, we preregistered our hypotheses and analysis plan for Experiments 2 and 3 on the Open Science Framework website. The preregistration document, along with raw and processed data, and analysis scripts, are publicly available at the project repository: \url{https://osf.io/ab3yv/}

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

Supported by BBSRC grant BB/V007580/1 awarded to DHB and ARW. We are grateful to all of the participants who took part in the experiments reported here.

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-Alais2010}{}}%
Alais D, Cass J, OShea RP, Blake R. 2010. Visual sensitivity underlying changes in visual consciousness. \emph{Current Biology} \textbf{20}:1362--1367. doi:\href{https://doi.org/10.1016/j.cub.2010.06.015}{10.1016/j.cub.2010.06.015}

\leavevmode\vadjust pre{\hypertarget{ref-Aschner2018}{}}%
Aschner A, Solomon SG, Landy MS, Heeger DJ, Kohn A. 2018. Temporal contingencies determine whether adaptation strengthens or weakens normalization. \emph{J Neurosci} \textbf{38}:10129--10142. doi:\href{https://doi.org/10.1523/JNEUROSCI.1131-18.2018}{10.1523/JNEUROSCI.1131-18.2018}

\leavevmode\vadjust pre{\hypertarget{ref-Baker2021}{}}%
Baker DH. 2021. Statistical analysis of periodic data in neuroscience. \emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5}. doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}

\leavevmode\vadjust pre{\hypertarget{ref-Baker2007}{}}%
Baker DH, Meese TS, Summers RJ. 2007. Psychophysical evidence for two routes to suppression before binocular summation of signals in human vision. \emph{Neuroscience} \textbf{146}:435--448. doi:\href{https://doi.org/10.1016/j.neuroscience.2007.01.030}{10.1016/j.neuroscience.2007.01.030}

\leavevmode\vadjust pre{\hypertarget{ref-Baldwin2018}{}}%
Baldwin AS, Hess RF. 2018. The mechanism of short-term monocular deprivation is not simple: Separate effects on parallel and cross-oriented dichoptic masking. \emph{Sci Rep} \textbf{8}:6191. doi:\href{https://doi.org/10.1038/s41598-018-24584-9}{10.1038/s41598-018-24584-9}

\leavevmode\vadjust pre{\hypertarget{ref-Baron-Cohen2001}{}}%
Baron-Cohen S, Wheelwright S, Skinner R, Martin J, Clubley E. 2001. The autism-spectrum quotient (AQ): Evidence from asperger syndrome/high-functioning autism, males and females, scientists and mathematicians. \emph{J Autism Dev Disord} \textbf{31}:5--17. doi:\href{https://doi.org/10.1023/a:1005653411471}{10.1023/a:1005653411471}

\leavevmode\vadjust pre{\hypertarget{ref-Blakemore1969}{}}%
Blakemore C, Campbell FW. 1969. On the existence of neurones in the human visual system selectively sensitive to the orientation and size of retinal images. \emph{J Physiol} \textbf{203}:237--60. doi:\href{https://doi.org/10.1113/jphysiol.1969.sp008862}{10.1113/jphysiol.1969.sp008862}

\leavevmode\vadjust pre{\hypertarget{ref-Cannon1991}{}}%
Cannon MW, Fullenkamp SC. 1991. Spatial interactions in apparent contrast: Inhibitory effects among grating patterns of different spatial frequencies, spatial positions and orientations. \emph{Vision Res} \textbf{31}:1985--98. doi:\href{https://doi.org/10.1016/0042-6989(91)90193-9}{10.1016/0042-6989(91)90193-9}

\leavevmode\vadjust pre{\hypertarget{ref-Carandini2011}{}}%
Carandini M, Heeger DJ. 2011. Normalization as a canonical neural computation. \emph{Nature Reviews Neuroscience} \textbf{13}:51--62. doi:\href{https://doi.org/10.1038/nrn3136}{10.1038/nrn3136}

\leavevmode\vadjust pre{\hypertarget{ref-Dale1999}{}}%
Dale AM, Fischl B, Sereno MI. 1999. Cortical surface-based analysis. I. Segmentation and surface reconstruction. \emph{Neuroimage} \textbf{9}:179--94. doi:\href{https://doi.org/10.1006/nimg.1998.0395}{10.1006/nimg.1998.0395}

\leavevmode\vadjust pre{\hypertarget{ref-Delorme2004}{}}%
Delorme A, Makeig S. 2004. EEGLAB: An open source toolbox for analysis of single-trial EEG dynamics including independent component analysis. \emph{J Neurosci Methods} \textbf{134}:9--21. doi:\href{https://doi.org/10.1016/j.jneumeth.2003.10.009}{10.1016/j.jneumeth.2003.10.009}

\leavevmode\vadjust pre{\hypertarget{ref-Dickinson2014}{}}%
Dickinson A, Jones M, Milne E. 2014. Oblique orientation discrimination thresholds are superior in those with a high level of autistic traits. \emph{Journal of Autism and Developmental Disorders} \textbf{44}:2844--2850. doi:\href{https://doi.org/10.1007/s10803-014-2147-1}{10.1007/s10803-014-2147-1}

\leavevmode\vadjust pre{\hypertarget{ref-Foley1994}{}}%
Foley JM. 1994. Human luminance pattern-vision mechanisms: Masking experiments require a new model. \emph{J Opt Soc Am A Opt Image Sci Vis} \textbf{11}:1710--9. doi:\href{https://doi.org/10.1364/josaa.11.001710}{10.1364/josaa.11.001710}

\leavevmode\vadjust pre{\hypertarget{ref-Foley1997}{}}%
Foley JM, Chen CC. 1997. Analysis of the effect of pattern adaptation on pattern pedestal effects: A two-process model. \emph{Vision Res} \textbf{37}:2779--88. doi:\href{https://doi.org/10.1016/s0042-6989(97)00081-3}{10.1016/s0042-6989(97)00081-3}

\leavevmode\vadjust pre{\hypertarget{ref-Fonov2011}{}}%
Fonov V, Evans AC, Botteron K, Almli CR, McKinstry RC, Collins DL, Brain Development Cooperative Group. 2011. Unbiased average age-appropriate atlases for pediatric studies. \emph{Neuroimage} \textbf{54}:313--27. doi:\href{https://doi.org/10.1016/j.neuroimage.2010.07.033}{10.1016/j.neuroimage.2010.07.033}

\leavevmode\vadjust pre{\hypertarget{ref-Freeman2002}{}}%
Freeman TCB, Durand S, Kiper DC, Carandini M. 2002. Suppression without inhibition in visual cortex. \emph{Neuron} \textbf{35}:759--71. doi:\href{https://doi.org/10.1016/s0896-6273(02)00819-x}{10.1016/s0896-6273(02)00819-x}

\leavevmode\vadjust pre{\hypertarget{ref-Gibson1937}{}}%
Gibson JJ, Radner M. 1937. Adaptation, after-effect and contrast in the perception of tilted lines. {I}. {Quantitative} studies. \emph{Journal of Experimental Psychology} \textbf{20}:453--467. doi:\href{https://doi.org/10.1037/h0059826}{10.1037/h0059826}

\leavevmode\vadjust pre{\hypertarget{ref-Greenlee1991}{}}%
Greenlee MW, Georgeson MA, Magnussen S, Harris JP. 1991. The time course of adaptation to spatial contrast. \emph{Vision Res} \textbf{31}:223--36. doi:\href{https://doi.org/10.1016/0042-6989(91)90113-j}{10.1016/0042-6989(91)90113-j}

\leavevmode\vadjust pre{\hypertarget{ref-Groen2022}{}}%
Groen IIA, Piantoni G, Montenegro S, Flinker A, Devore S, Devinsky O, Doyle W, Dugan P, Friedman D, Ramsey N, Petridou N, Winawer J. 2022. Temporal dynamics of neural responses in human visual cortex. \emph{J Neurosci}. doi:\href{https://doi.org/10.1523/JNEUROSCI.1812-21.2022}{10.1523/JNEUROSCI.1812-21.2022}

\leavevmode\vadjust pre{\hypertarget{ref-Haak2014}{}}%
Haak KV, Fast E, Bao M, Lee M, Engel SA. 2014. Four days of visual contrast deprivation reveals limits of neuronal adaptation. \emph{Curr Biol} \textbf{24}:2575--9. doi:\href{https://doi.org/10.1016/j.cub.2014.09.027}{10.1016/j.cub.2014.09.027}

\leavevmode\vadjust pre{\hypertarget{ref-Heeger1992}{}}%
Heeger DJ. 1992. Normalization of cell responses in cat striate cortex. \emph{Vis Neurosci} \textbf{9}:181--97. doi:\href{https://doi.org/10.1017/s0952523800009640}{10.1017/s0952523800009640}

\leavevmode\vadjust pre{\hypertarget{ref-Hoekstra2011}{}}%
Hoekstra RA, Vinkhuyzen AAE, Wheelwright S, Bartels M, Boomsma DI, Baron-Cohen S, Posthuma D, Sluis S van der. 2011. The construction and validation of an abridged version of the autism-spectrum quotient (AQ-short). \emph{J Autism Dev Disord} \textbf{41}:589--96. doi:\href{https://doi.org/10.1007/s10803-010-1073-0}{10.1007/s10803-010-1073-0}

\leavevmode\vadjust pre{\hypertarget{ref-Jones1975}{}}%
Jones PD, Holding DH. 1975. Extremely long-term persistence of the McCollough effect. \emph{J Exp Psychol Hum Percept Perform} \textbf{1}:323--7. doi:\href{https://doi.org/10.1037//0096-1523.1.4.323}{10.1037//0096-1523.1.4.323}

\leavevmode\vadjust pre{\hypertarget{ref-Koh2010}{}}%
Koh HC, Milne E, Dobkins K. 2010. Spatial contrast sensitivity in adolescents with autism spectrum disorders. \emph{J Autism Dev Disord} \textbf{40}:978--87. doi:\href{https://doi.org/10.1007/s10803-010-0953-7}{10.1007/s10803-010-0953-7}

\leavevmode\vadjust pre{\hypertarget{ref-Kwon2009}{}}%
Kwon M, Legge GE, Fang F, Cheong AMY, He S. 2009. Adaptive changes in visual cortex following prolonged contrast reduction. \emph{J Vis} \textbf{9}:20.1--16. doi:\href{https://doi.org/10.1167/9.2.20}{10.1167/9.2.20}

\leavevmode\vadjust pre{\hypertarget{ref-Lamb2006}{}}%
Lamb TD, Pugh EN Jr. 2006. Phototransduction, dark adaptation, and rhodopsin regeneration the proctor lecture. \emph{Invest Ophthalmol Vis Sci} \textbf{47}:5137--52. doi:\href{https://doi.org/10.1167/iovs.06-0849}{10.1167/iovs.06-0849}

\leavevmode\vadjust pre{\hypertarget{ref-Legge1979}{}}%
Legge GE. 1979. Spatial frequency masking in human vision: Binocular interactions. \emph{J Opt Soc Am} \textbf{69}:838--47. doi:\href{https://doi.org/10.1364/josa.69.000838}{10.1364/josa.69.000838}

\leavevmode\vadjust pre{\hypertarget{ref-Li2005}{}}%
Li B, Peterson MR, Thompson JK, Duong T, Freeman RD. 2005. Cross-orientation suppression: Monoptic and dichoptic mechanisms are different. \emph{J Neurophysiol} \textbf{94}:1645--50. doi:\href{https://doi.org/10.1152/jn.00203.2005}{10.1152/jn.00203.2005}

\leavevmode\vadjust pre{\hypertarget{ref-Liza2022}{}}%
Liza K, Ray S. 2022. Local interactions between steady-state visually evoked potentials at nearby flickering frequencies. \emph{J Neurosci} \textbf{42}:3965--3974. doi:\href{https://doi.org/10.1523/JNEUROSCI.0180-22.2022}{10.1523/JNEUROSCI.0180-22.2022}

\leavevmode\vadjust pre{\hypertarget{ref-Lunghi2011}{}}%
Lunghi C, Burr DC, Morrone C. 2011. Brief periods of monocular deprivation disrupt ocular balance in human adult visual cortex. \emph{Curr Biol} \textbf{21}:R538--9. doi:\href{https://doi.org/10.1016/j.cub.2011.06.004}{10.1016/j.cub.2011.06.004}

\leavevmode\vadjust pre{\hypertarget{ref-Lunghi2015}{}}%
Lunghi C, Emir UE, Morrone MC, Bridge H. 2015. Short-term monocular deprivation alters GABA in the adult human visual cortex. \emph{Curr Biol} \textbf{25}:1496--501. doi:\href{https://doi.org/10.1016/j.cub.2015.04.021}{10.1016/j.cub.2015.04.021}

\leavevmode\vadjust pre{\hypertarget{ref-MacLennan2022}{}}%
MacLennan K, O'Brien S, Tavassoli T. 2022. In our own words: The complex sensory experiences of autistic adults. \emph{J Autism Dev Disord} \textbf{52}:3061--3075. doi:\href{https://doi.org/10.1007/s10803-021-05186-3}{10.1007/s10803-021-05186-3}

\leavevmode\vadjust pre{\hypertarget{ref-Maris2007}{}}%
Maris E, Oostenveld R. 2007. Nonparametric statistical testing of EEG- and MEG-data. \emph{J Neurosci Methods} \textbf{164}:177--90. doi:\href{https://doi.org/10.1016/j.jneumeth.2007.03.024}{10.1016/j.jneumeth.2007.03.024}

\leavevmode\vadjust pre{\hypertarget{ref-Mather2008}{}}%
Mather G, Pavan A, Campana G, Casco C. 2008. The motion aftereffect reloaded. \emph{Trends Cogn Sci} \textbf{12}:481--7. doi:\href{https://doi.org/10.1016/j.tics.2008.09.002}{10.1016/j.tics.2008.09.002}

\leavevmode\vadjust pre{\hypertarget{ref-McCollough1965}{}}%
McCollough C. 1965. Color adaptation of edge-detectors in the human visual system. \emph{Science} \textbf{149}:1115--6. doi:\href{https://doi.org/10.1126/science.149.3688.1115}{10.1126/science.149.3688.1115}

\leavevmode\vadjust pre{\hypertarget{ref-Meese2009}{}}%
Meese TS, Baker DH. 2009. Cross-orientation masking is speed invariant between ocular pathways but speed dependent within them. \emph{Journal of Vision} \textbf{9}:2. doi:\href{https://doi.org/10.1167/9.5.2}{10.1167/9.5.2}

\leavevmode\vadjust pre{\hypertarget{ref-Pellicano2012}{}}%
Pellicano E, Burr D. 2012. When the world becomes 'too real': A bayesian explanation of autistic perception. \emph{Trends Cogn Sci} \textbf{16}:504--10. doi:\href{https://doi.org/10.1016/j.tics.2012.08.009}{10.1016/j.tics.2012.08.009}

\leavevmode\vadjust pre{\hypertarget{ref-Pellicano2007}{}}%
Pellicano E, Jeffery L, Burr D, Rhodes G. 2007. Abnormal adaptive face-coding mechanisms in children with autism spectrum disorder. \emph{Curr Biol} \textbf{17}:1508--12. doi:\href{https://doi.org/10.1016/j.cub.2007.07.065}{10.1016/j.cub.2007.07.065}

\leavevmode\vadjust pre{\hypertarget{ref-Petrov2005}{}}%
Petrov Y. 2005. Two distinct mechanisms of suppression in human vision. \emph{Journal of Neuroscience} \textbf{25}:8704--8707. doi:\href{https://doi.org/10.1523/jneurosci.2871-05.2005}{10.1523/jneurosci.2871-05.2005}

\leavevmode\vadjust pre{\hypertarget{ref-Robertson2013}{}}%
Robertson CE, Kravitz DJ, Freyberg J, Baron-Cohen S, Baker CI. 2013. Slower rate of binocular rivalry in autism. \emph{The Journal of Neuroscience} \textbf{33}:16983--16991. doi:\href{https://doi.org/10.1523/jneurosci.0448-13.2013}{10.1523/jneurosci.0448-13.2013}

\leavevmode\vadjust pre{\hypertarget{ref-Rosenberg2015}{}}%
Rosenberg A, Patterson JS, Angelaki DE. 2015. A computational perspective on autism. \emph{Proc Natl Acad Sci U S A} \textbf{112}:9158--65. doi:\href{https://doi.org/10.1073/pnas.1510583112}{10.1073/pnas.1510583112}

\leavevmode\vadjust pre{\hypertarget{ref-Rosenhall1999}{}}%
Rosenhall U, Nordin V, Sandström M, Ahlsén G, Gillberg C. 1999. Autism and hearing loss. \emph{J Autism Dev Disord} \textbf{29}:349--57. doi:\href{https://doi.org/10.1023/a:1023022709710}{10.1023/a:1023022709710}

\leavevmode\vadjust pre{\hypertarget{ref-Rubenstein2003}{}}%
Rubenstein JLR, Merzenich MM. 2003. Model of autism: Increased ratio of excitation/inhibition in key neural systems. \emph{Genes Brain Behav} \textbf{2}:255--67. doi:\href{https://doi.org/10.1034/j.1601-183x.2003.00037.x}{10.1034/j.1601-183x.2003.00037.x}

\leavevmode\vadjust pre{\hypertarget{ref-Sandhu2020}{}}%
Sandhu TR, Reese G, Lawson RP. 2020. Preserved low-level visual gain control in autistic adults. \emph{Wellcome Open Research} \textbf{4}. doi:\href{https://doi.org/10.12688/wellcomeopenres.15615.1}{10.12688/wellcomeopenres.15615.1}

\leavevmode\vadjust pre{\hypertarget{ref-Schallmo2020}{}}%
Schallmo M-P, Kolodny T, Kale AM, Millin R, Flevaris AV, Edden RAE, Gerdts J, Bernier RA, Murray SO. 2020. Weaker neural suppression in autism. \emph{Nat Commun} \textbf{11}:2675. doi:\href{https://doi.org/10.1038/s41467-020-16495-z}{10.1038/s41467-020-16495-z}

\leavevmode\vadjust pre{\hypertarget{ref-Sengpiel1994}{}}%
Sengpiel F, Blakemore C. 1994. Interocular control of neuronal responsiveness in cat visual cortex. \emph{Nature} \textbf{368}:847--50. doi:\href{https://doi.org/10.1038/368847a0}{10.1038/368847a0}

\leavevmode\vadjust pre{\hypertarget{ref-Sengpiel2005}{}}%
Sengpiel F, Vorobyov V. 2005. Intracortical origins of interocular suppression in the visual cortex. \emph{J Neurosci} \textbf{25}:6394--400. doi:\href{https://doi.org/10.1523/JNEUROSCI.0862-05.2005}{10.1523/JNEUROSCI.0862-05.2005}

\leavevmode\vadjust pre{\hypertarget{ref-Simmons2009}{}}%
Simmons DR, Robertson AE, McKay LS, Toal E, McAleer P, Pollick FE. 2009. Vision in autism spectrum disorders. \emph{Vision Research} \textbf{49}:2705--2739. doi:\href{https://doi.org/10.1016/j.visres.2009.08.005}{10.1016/j.visres.2009.08.005}

\leavevmode\vadjust pre{\hypertarget{ref-Tadel2011}{}}%
Tadel F, Baillet S, Mosher JC, Pantazis D, Leahy RM. 2011. Brainstorm: A user-friendly application for MEG/EEG analysis. \emph{Comput Intell Neurosci} \textbf{2011}:879716. doi:\href{https://doi.org/10.1155/2011/879716}{10.1155/2011/879716}

\leavevmode\vadjust pre{\hypertarget{ref-Tavassoli2014}{}}%
Tavassoli T, Hoekstra RA, Baron-Cohen S. 2014. The sensory perception quotient (SPQ): Development and validation of a new sensory questionnaire for adults with and without autism. \emph{Mol Autism} \textbf{5}:29. doi:\href{https://doi.org/10.1186/2040-2392-5-29}{10.1186/2040-2392-5-29}

\leavevmode\vadjust pre{\hypertarget{ref-Tavassoli2011}{}}%
Tavassoli T, Latham K, Bach M, Dakin SC, Baron-Cohen S. 2011. Psychophysical measures of visual acuity in autism spectrum conditions. \emph{Vision Research} \textbf{51}:1778--1780. doi:\href{https://doi.org/10.1016/j.visres.2011.06.004}{10.1016/j.visres.2011.06.004}

\leavevmode\vadjust pre{\hypertarget{ref-Turi2015}{}}%
Turi M, Burr DC, Igliozzi R, Aagten-Murphy D, Muratori F, Pellicano E. 2015. Children with autism spectrum disorder show reduced adaptation to number. \emph{Proc Natl Acad Sci U S A} \textbf{112}:7868--72. doi:\href{https://doi.org/10.1073/pnas.1504099112}{10.1073/pnas.1504099112}

\leavevmode\vadjust pre{\hypertarget{ref-Utzerath2018}{}}%
Utzerath C, Schmits IC, Buitelaar J, Lange FP de. 2018. Adolescents with autism show typical fMRI repetition suppression, but atypical surprise response. \emph{Cortex} \textbf{109}:25--34. doi:\href{https://doi.org/10.1016/j.cortex.2018.08.019}{10.1016/j.cortex.2018.08.019}

\leavevmode\vadjust pre{\hypertarget{ref-VandeCruys2018}{}}%
Van de Cruys S, Vanmarcke S, Steyaert J, Wagemans J. 2018. Intact perceptual bias in autism contradicts the decreased normalization model. \emph{Scientific Reports} \textbf{8}. doi:\href{https://doi.org/10.1038/s41598-018-31042-z}{10.1038/s41598-018-31042-z}

\leavevmode\vadjust pre{\hypertarget{ref-VanVeen1997}{}}%
Van Veen BD, Drongelen W van, Yuchtman M, Suzuki A. 1997. Localization of brain electrical activity via linearly constrained minimum variance spatial filtering. \emph{IEEE Trans Biomed Eng} \textbf{44}:867--80. doi:\href{https://doi.org/10.1109/10.623056}{10.1109/10.623056}

\leavevmode\vadjust pre{\hypertarget{ref-Vilidaite2018}{}}%
Vilidaite G, Norcia AM, West RJH, Elliott CJH, Pei F, Wade AR, Baker DH. 2018. Autism sensory dysfunction in an evolutionarily conserved system. \emph{Proc Biol Sci} \textbf{285}:20182255. doi:\href{https://doi.org/10.1098/rspb.2018.2255}{10.1098/rspb.2018.2255}

\leavevmode\vadjust pre{\hypertarget{ref-Wang2015}{}}%
Wang L, Mruczek REB, Arcaro MJ, Kastner S. 2015. Probabilistic maps of visual topography in human cortex. \emph{Cereb Cortex} \textbf{25}:3911--31. doi:\href{https://doi.org/10.1093/cercor/bhu277}{10.1093/cercor/bhu277}

\leavevmode\vadjust pre{\hypertarget{ref-Webster2015}{}}%
Webster MA. 2015. Visual adaptation. \emph{Annu Rev Vis Sci} \textbf{1}:547--567. doi:\href{https://doi.org/10.1146/annurev-vision-082114-035509}{10.1146/annurev-vision-082114-035509}

\leavevmode\vadjust pre{\hypertarget{ref-Westrick2016}{}}%
Westrick ZM, Heeger DJ, Landy MS. 2016. Pattern adaptation and normalization reweighting. \emph{Journal of Neuroscience} \textbf{36}:9805--9816. doi:\href{https://doi.org/10.1523/jneurosci.1067-16.2016}{10.1523/jneurosci.1067-16.2016}

\leavevmode\vadjust pre{\hypertarget{ref-Wilson2003}{}}%
Wilson HR. 2003. Computational evidence for a rivalry hierarchy in vision. \emph{Proc Natl Acad Sci U S A} \textbf{100}:14499--503. doi:\href{https://doi.org/10.1073/pnas.2333622100}{10.1073/pnas.2333622100}

\leavevmode\vadjust pre{\hypertarget{ref-Yiltiz2020}{}}%
Yiltiz H, Heeger DJ, Landy MS. 2020. Contingent adaptation in masking and surround suppression. \emph{Vision Res} \textbf{166}:72--80. doi:\href{https://doi.org/10.1016/j.visres.2019.11.004}{10.1016/j.visres.2019.11.004}

\leavevmode\vadjust pre{\hypertarget{ref-Zhou2015}{}}%
Zhou J, Baker DH, Simard M, Saint-Amour D, Hess RF. 2015. Short-term monocular patching boosts the patched eye's response in visual cortex. \emph{Restor Neurol Neurosci} \textbf{33}:381--7. doi:\href{https://doi.org/10.3233/RNN-140472}{10.3233/RNN-140472}

\end{CSLReferences}

\end{document}

### 2022-09-30 renameandupload.R

@@ -1,108 +1,0 @@
-# script to rename raw EEG files to preserve participant anonymity
-# also re-orders by AQ score, and uploads data to OSF
-# DHB 23/5/22
-
-packagelist <- c('remotes','tictoc','utils','R.matlab')
-missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
-if (length(missingpackages)>0){install.packages(missingpackages)}
-if (packagelist[!'osfr' %in% installed.packages()[,1]]){remotes::install_github("centerforopenscience/osfr")}
-packagelist <- c(packagelist,'osfr')
-toinstall <- packagelist[which(!packagelist %in% (.packages()))]
-invisible(lapply(toinstall,library,character.only=TRUE))
-
-my_wd <- getwd()
-
-osf_auth(token = '')
-osfproject <- osf_retrieve_node("ab3yv")
-componentlist <- osf_ls_nodes(osfproject)
-EEGID <- pmatch('Raw EEG data 1',as.character(unlist(componentlist[,1])))
-EEGtokenLow <- componentlist[EEGID,2]
-EEGfilesLow <- osf_ls_files(EEGtokenLow,n_max=300)
-EEGID <- pmatch('Raw EEG data 2',as.character(unlist(componentlist[,1])))
-EEGtokenHi <- componentlist[EEGID,2]
-EEGfilesHi <- osf_ls_files(EEGtokenHi,n_max=300)
-
-rawdatadir <- '~/Desktop/UG2021/'
-
-rawdata <- read.csv('~/Google Drive/Current work/Teaching/BSc projects 2021/ASD/BSc project questionnaires 2021 (Responses) - Form Responses 1.csv')
-
-IDnos <- readMat('~/Google Drive/Current work/Research/normalization/IDnos.mat')
-uniqueID <- unlist(IDnos$allU)
-load('~/Google Drive/Current work/Research/normalization/questionnairedata.RData')
-QIDs <- as.character(qdata$ID)
-
-# fix duplicate ID numbers
-uniqueID[12] <- '2001b'
-QIDs[12] <- '2001b'
-uniqueID[46] <- '2001c'
-QIDs[46] <- '2001c'
-uniqueID[56] <- '1357b'
-QIDs[55] <- '1357b'
-uniqueID[70] <- '1234b'
-QIDs[68] <- '1234b'
-uniqueID[77] <- '1234c'
-QIDs[75] <- '1234c'
[…]

### 2022-09-30 manuscript.Rmd
Minor changes to keep track of rejected trials.

@@
 # reasonably compact code to check which packages are installed, install the missing ones, and activate all
-packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','grImport','tiff','pals','ez','gtools') # list of CRAN packages
+packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','rmarkdown','grImport','tiff','pals','ez','gtools','pracma') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
@@
 invisible(lapply(toinstall,library,character.only=TRUE))
-
-osf_auth(token = '3dEYuhZNmwWbG3xuhRIiVRo0T2oniOkEP3Ip8i1LPG4PNjeTRln54eGNAG7oyTT9xozWwJ')
 
@@
       i <- which(abs(nulldist)>abs(sumtvals[cc]))
-      if (!isempty(i)){clusterps[cc] <- length(i)/nresamples}
+      if (!pracma::isempty(i)){clusterps[cc] <- length(i)/nresamples}
       if (clusterps[cc]<clustthresh){
@@
 if (!dir.exists('temp/')){dir.create('temp/')}
-if (!dir.exists('temp/figures/')){dir.create('temp/figures/')}
 if (!dir.exists('temp/VilidaiteProcessed/')){dir.create('temp/VilidaiteProcessed/')}
@@
 Dynamic fluctuations in interocular suppression are a key feature of binocular rivalry [@Wilson2003; @Alais2010], for which autism-related differences have also been reported [@Robertson2013].
+By comparing monocular and dichoptic suppression, we are also able to isolate any contribution of early pre-cortical factors.
+This is because interocular suppression impacts in primary visual cortex, and therefore bypasses earlier retinal and subcortical stages of processing that may contribute to monocular suppression [@Li2005].
 
@@
 Our recent work has identified a potential autism-related difference in gain control using steady-state EEG methods.
-@Vilidaite2018 measured contrast response functions for flickering stimuli in a large group of neurotypical adults, who were split by their autism quotient [AQ, see @Baron-Cohen2001] score.
+@Vilidaite2018 measured contrast response functions for flickering stimuli in a large group of neurotypical adults, who were grouped according to their autism quotient [AQ, see @Baron-Cohen2001] score.
 The responses were comparable between high and low AQ groups at the flicker frequency of the stimulus.
@@
 
+# single participant analysis of data from Vilidaite et al. (2018)
+
 samplerate <- 1000
@@
 
-# datadir <- '/Volumes/Seagate/EEG data/UG2014/tar/'
-# tempdir <- '/Volumes/Seagate/EEG data/UG2014/tar/temp/'
 datadir <- 'temp/raw/'
@@
         temp <- as.matrix(EEGdata[(triggertimes[tr]:(triggertimes[tr] + samplerate * duration - 1))-1499, ch + 2])
-        temp <- temp - mean(temp[501:1500])
+        temp <- temp - mean(temp[501:1500])  # subtract mean of 1 second pre-trial baseline average
         allsamples[condcounter[cond],cond,ch,1:(1000*duration)] <- as.vector(rowMeans(temp))
@@
 
+```
+
+```{r include=FALSE, results='hide'}
+
+# group level analysis of data from Vilidaite et al. (2018)
+
 if (processdata>1){
@@
 EEGallconds <- array(0,dim=c(length(d),4,14))
+alltrialcounts <- array(0,dim=c(length(d),14,64))
 
@@
   targetchannels <- match(targetelectrodes, electrodes) - 2
+  alltrialcounts[s,,] <- trialsincluded
 
@@
 
-save(file='temp/Pilotsummary.RData',list=c('EEGtimecourse','electrodes','EEGscalpresps','EEGspectra','EEGallconds'))
-}
+save(file='temp/Pilotsummary.RData',list=c('EEGtimecourse','electrodes','EEGscalpresps','EEGspectra','EEGallconds','alltrialcounts'))
+}
+
+```
+
+```{r include=FALSE, results='hide'}
+
+# plot data from Vilidaite et al. (2018)
 
@@
 load('temp/Pilotsummary.RData')
+
 nsubjs <- dim(EEGtimecourse)[1]
@@
 
-  pdf('temp/figures/Fig1.pdf', bg="transparent", height = 6, width = 16)
+  pdf('Figures/VilidaiteData.pdf', bg="transparent", height = 6, width = 16)
   par(mar=c(0.1,0.1,0.1,0.1))
@@
 
+```
+
+```{r include=FALSE, results='hide'}
+
+# do statistics for Vilidiate et al. data
+
 load('temp/Pilotsummary.RData')
 
+Pilotpercentexcluded <- 100 - (100*mean(alltrialcounts[,condlist,28:31])/8)
 targetcond <- NULL
@@
 Points around y = 1.8 indicate a significantly increasing ratio.
-Error bars in panel (a) and shaded regions in panels (c,d) indicate ±1SE, and grey rectangles indicate the timing of stimulus presentation.
+Error bars in panel (a) and shaded regions in panels (c,d) indicate ±1SE across N=100 participants, and grey rectangles indicate the timing of stimulus presentation.
 The larger symbols in panel (a) indicate the conditions used for subsequent analyses.", fig.align="center", echo=FALSE}
 
-knitr::include_graphics('temp/figures/Fig1.pdf')
+knitr::include_graphics('Figures/VilidaiteData.pdf')
 
@@
 
-Our initial reanalysis was promising, however the data were noisy despite the large sample size, because each participant contributed only 8 trials (88 seconds) to each condition.
+Our initial reanalysis was promising, however the data were noisy despite the large sample size (of N=100), because each participant contributed only 8 trials (88 seconds) to each condition.
 We therefore preregistered two new experiments (see https://osf.io/4qudc) to investigate these effects in greater detail.
@@
 ```{r include=FALSE, results='hide'}
+
+# analyse raw data from EEG study
 
@@
 
+```
+
+```{r include=FALSE, results='hide'}
+
+# average EEG data across participants
+
 if (processdata>1){
+
 d <- dir(path = 'temp/EEGprocessed', pattern = '*.RData', full.names=TRUE)
@@
 allheads7 <- array(0,dim=c(length(d),4,64))
+EEGtrialsincluded <- array(0,dim=c(length(d),4,64))
 allAQ <- NULL
@@
   targetchannels <- match(targetelectrodes, electrodes) - 2
+  EEGtrialsincluded[s,,] <- trialsincluded
   for (cond in 1:4){
@@
 
-save(file='temp/EEGsummary.RData',list=c('allheads5','allheads7','allspec','allwaves','EEGtimecourse5Hz','EEGtimecourse7Hz','electrodes','allAQ','allSPQ'))
- }
+save(file='temp/EEGsummary.RData',list=c('allheads5','allheads7','allspec','allwaves','EEGtimecourse5Hz','EEGtimecourse7Hz','electrodes','allAQ','allSPQ','EEGtrialsincluded'))
+ }
+
+```
+
+```{r include=FALSE, results='hide'}
+
+# bootstrapping and figure plotting for EEG data
 
 load('temp/EEGsummary.RData')
+
+EEGpercentexcluded <- 100 - mean(100*EEGtrialsincluded[,,28:31]/48)
 
@@
 if (nbootstraps>0){clustoutD7 <- clustercorrect(earlydataD,latedataD,testtype=4,paired=TRUE)}
-
-# pdf("temp/figures/Fig2.pdf", bg="transparent", height = 10, width = 12)
-# 
-# par(mfrow=c(3,4))
 
@@
 
-  pdf('temp/figures/Fig2.pdf', bg="transparent", height = 6, width = 15)
+  pdf('Figures/EEGdata.pdf', bg="transparent", height = 6, width = 15)
   par(mar=c(0.1,0.1,0.1,0.1))
@@
 
+```
+
+```{r include=FALSE, results='hide'}
+
+# statistical testing
+
 targetcond <- NULL
@@
 
-knitr::include_graphics('temp/figures/Fig2.pdf')
+knitr::include_graphics('Figures/EEGdata.pdf')
 
@@
 ```{r include=FALSE, results='hide'}
+
+# combine MEG data across participants
 
@@
 }
+
+```
+
+```{r include=FALSE, results='hide'}
+
+# plot MEG figure
 
@@
 
-  e1 <- readTIFF('temp/figures/groupbrainbothSNR.tif')
-  e2 <- readTIFF('temp/figures/LH.tif')
-  e3 <- readTIFF('temp/figures/RH.tif')
-
-  pdf('temp/figures/Fig3.pdf', bg="transparent", height = 6, width = 15)
+  e1 <- readTIFF('temp/groupbrainbothSNR.tif')
+  e2 <- readTIFF('temp/LH.tif')
+  e3 <- readTIFF('temp/RH.tif')
+
+  pdf('Figures/MEGdata.pdf', bg="transparent", height = 6, width = 15)
   par(mar=c(0.1,0.1,0.1,0.1))
@@
 
-knitr::include_graphics('temp/figures/Fig3.pdf')
+knitr::include_graphics('Figures/MEGdata.pdf')
 
@@
 
-  pdf('temp/figures/Fig4.pdf', bg="transparent", height = 10, width = 12)
+  pdf('Figures/AQfigure.pdf', bg="transparent", height = 10, width = 12)
   par(mar=c(0.1,0.1,0.1,0.1))
@@
 
-knitr::include_graphics('temp/figures/Fig4.pdf')
+knitr::include_graphics('Figures/AQfigure.pdf')
 
@@
 Or there could be an asymmetry, whereby the relative temporal frequency between the two stimulus components affects the character of suppression [@Liza2022].
-We hope that in future dynamic models of early vision [e.g.
-@Zhou2019] will be able to explain these differences.
+We hope to be able to model these effects in the future, for example by using dynamic models of early vision that incorporate time-lagged gain control [e.g.
+@Zhou2019].
+
+We did not observe clear differences in the timecourse between monocular and dichoptic suppression.
+This is important, because the dichoptic arrangement bypasses early stages of processing before the cortex (e.g.
+the retina and lateral geniculate nucleus).
+It suggests that the dynamic increases in suppression occur in the cortex, consistent with our MEG data that find evidence of reweighting in V1 (see Fig \@ref(fig:MEGdata)), and with previous neurophysiological work [@Aschner2018].
+It is currently unclear whether these effects originate in V1, or might involve feedback from higher areas.
+The similarity between monocular and dichoptic effects also differs from work on adaptation to individual mask components.
+In both physiological [@Li2005; @Sengpiel2005] and psychophysical [@Baker2007] paradigms, adapting to a dichoptic mask reduces its potency, whereas adapting to a monocular mask has little or no effect.
+Normalization reweighting offers an explanation for why monocular masks presented in isolation do not adapt: if suppressive weights are determined by co-occurrence of stimuli, presentation of an isolated mask will have little effect.
+However this cannot explain the dichoptic adaptation effects without invoking additional binocular processes, such as competition between summing and differencing channels [e.g.
+@May2012].
 
@@
 
-In Experiments 1 and 2, stimuli were presented using a ViewPixx LCD display device (VPixx Technologies, Canada) with a resolution of 1920 $\times$ 1080 pixels and a refresh rate of 120Hz.
+In Experiments 1 and 2, stimuli were presented using a ViewPixx 3D LCD display device (VPixx Technologies, Canada) with a resolution of 1920 $\times$ 1080 pixels and a refresh rate of 120Hz.
 The display was gamma corrected using a Minolta LS110 photometer.
@@
 We excluded trials for which the Mahalanobis distance of the complex Fourier components exceeded 3 [for details see @Baker2021].
-This resulted in % of trials being excluded for Experiment 1, % of trials for Experiment 2, and % of trials for Experiment 3.
+This resulted in `r round(Pilotpercentexcluded,digits=2)`% of trials being excluded for Experiment 1, `r round(EEGpercentexcluded,digits=2)`% of trials for Experiment 2, and `r round(EEGpercentexcluded,digits=2)`% of trials for Experiment 3.
 Next we averaged the waveforms across all remaining trials, and calculated the Fourier transform in a 1-second sliding window to generate timecourses for each participant.

### 2022-09-30 manuscript.tex
Minor changes to keep track of rejected trials.

@@
 \title{Temporal Dynamics of Normalization Reweighting}
-\author{Daniel H. Baker, Daniela Marinova, Richard Aveyard, Lydia Hargreaves, Alice Renton,\\
+\author{Daniel H. Baker, Daniela Marinova, Richard Aveyard, Lydia J. Hargreaves, Alice Renton,\\
 Ruby Castellani, Phoebe Hall, Miriam Harmens, Georgia Holroyd, Beth Nicholson,\\
-Emily Williams, Hannah M. Hobson \& Alex R. Wade}
-\date{2022-09-11}
+Emily L. Williams, Hannah M. Hobson \& Alex R. Wade}
+\date{2022-09-30}
 
@@
 Dynamic fluctuations in interocular suppression are a key feature of binocular rivalry (Alais et al., 2010; Wilson, 2003), for which autism-related differences have also been reported (Robertson et al., 2013).
+By comparing monocular and dichoptic suppression, we are also able to isolate any contribution of early pre-cortical factors.
+This is because interocular suppression impacts in primary visual cortex, and therefore bypasses earlier retinal and subcortical stages of processing that may contribute to monocular suppression (Li et al., 2005).
 
@@
 Vilidaite et al.
-(2018) measured contrast response functions for flickering stimuli in a large group of neurotypical adults, who were split by their autism quotient (AQ, see Baron-Cohen et al., 2001) score.
+(2018) measured contrast response functions for flickering stimuli in a large group of neurotypical adults, who were grouped according to their autism quotient (AQ, see Baron-Cohen et al., 2001) score.
 The responses were comparable between high and low AQ groups at the flicker frequency of the stimulus.
@@
 
-{\centering \includegraphics{temp/figures/Fig1}
+{\centering \includegraphics{Figures/VilidaiteData}
 
@@
 Points around y = 1.8 indicate a significantly increasing ratio.
-Error bars in panel (a) and shaded regions in panels (c,d) indicate ±1SE, and grey rectangles indicate the timing of stimulus presentation.
+Error bars in panel (a) and shaded regions in panels (c,d) indicate ±1SE across N=100 participants, and grey rectangles indicate the timing of stimulus presentation.
 The larger symbols in panel (a) indicate the conditions used for subsequent analyses.}\label{fig:Pilotdata}
@@
 
-Our initial reanalysis was promising, however the data were noisy despite the large sample size, because each participant contributed only 8 trials (88 seconds) to each condition.
+Our initial reanalysis was promising, however the data were noisy despite the large sample size (of N=100), because each participant contributed only 8 trials (88 seconds) to each condition.
 We therefore preregistered two new experiments (see \url{https://osf.io/4qudc}) to investigate these effects in greater detail.
@@
 Or there could be an asymmetry, whereby the relative temporal frequency between the two stimulus components affects the character of suppression (Liza and Ray, 2022).
-We hope that in future dynamic models of early vision (e.g.
-Groen et al., 2022) will be able to explain these differences.
+We hope to be able to model these effects in the future, for example by using dynamic models of early vision that incorporate time-lagged gain control (e.g.
+Zhou et al., 2019).
+
+We did not observe clear differences in the timecourse between monocular and dichoptic suppression.
+This is important, because the dichoptic arrangement bypasses early stages of processing before the cortex (e.g.~the retina and lateral geniculate nucleus).
+It suggests that the dynamic increases in suppression occur in the cortex, consistent with our MEG data that find evidence of reweighting in V1 (see Fig \ref{fig:MEGdata}), and with previous neurophysiological work (Aschner et al., 2018).
+It is currently unclear whether these effects originate in V1, or might involve feedback from higher areas.
+The similarity between monocular and dichoptic effects also differs from work on adaptation to individual mask components.
+In both physiological (Li et al., 2005; \textbf{Sengpiel2006?}) and psychophysical (Baker et al., 2007) paradigms, adapting to a dichoptic mask reduces its potency, whereas adapting to a monocular mask has little or no effect.
+Normalization reweighting offers an explanation for why monocular masks presented in isolation do not adapt: if suppressive weights are determined by co-occurrence of stimuli, presentation of an isolated mask will have little effect.
+However this cannot explain the dichoptic adaptation effects without invoking additional binocular processes, such as competition between summing and differencing channels (e.g.
+May et al., 2012).
 
@@
 
-In Experiments 1 and 2, stimuli were presented using a ViewPixx LCD display device (VPixx Technologies, Canada) with a resolution of 1920 \(\times\) 1080 pixels and a refresh rate of 120Hz.
+In Experiments 1 and 2, stimuli were presented using a ViewPixx 3D LCD display device (VPixx Technologies, Canada) with a resolution of 1920 \(\times\) 1080 pixels and a refresh rate of 120Hz.
 The display was gamma corrected using a Minolta LS110 photometer.
@@
 We excluded trials for which the Mahalanobis distance of the complex Fourier components exceeded 3 (for details see Baker, 2021).
-This resulted in \% of trials being excluded for Experiment 1, \% of trials for Experiment 2, and \% of trials for Experiment 3.
+This resulted in 0.25\% of trials being excluded for Experiment 1, 4.51\% of trials for Experiment 2, and 4.51\% of trials for Experiment 3.
 Next we averaged the waveforms across all remaining trials, and calculated the Fourier transform in a 1-second sliding window to generate timecourses for each participant.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Groen2022}{}}%
-Groen IIA, Piantoni G, Montenegro S, Flinker A, Devore S, Devinsky O, Doyle W, Dugan P, Friedman D, Ramsey N, Petridou N, Winawer J.
-2022.
-Temporal dynamics of neural responses in human visual cortex.
-\emph{J Neurosci}.
-doi:\href{https://doi.org/10.1523/JNEUROSCI.1812-21.2022}{10.1523/JNEUROSCI.1812-21.2022}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Haak2014}{}}%
@@
 doi:\href{https://doi.org/10.1016/j.tics.2008.09.002}{10.1016/j.tics.2008.09.002}
+
+\leavevmode\vadjust pre{\hypertarget{ref-May2012}{}}%
+May KA, Zhaoping L, Hibbard PB.
+2012.
+Perceived direction of motion determined by adaptation to static binocular images.
+\emph{Curr Biol} \textbf{22}:28--32.
+doi:\href{https://doi.org/10.1016/j.cub.2011.11.025}{10.1016/j.cub.2011.11.025}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Zhou2019}{}}%
+Zhou J, Benson NC, Kay K, Winawer J.
+2019.
+Predicting neuronal dynamics with a delayed gain control model.
+\emph{PLoS Comput Biol} \textbf{15}:e1007484.
+doi:\href{https://doi.org/10.1371/journal.pcbi.1007484}{10.1371/journal.pcbi.1007484}
+
 \end{CSLReferences}

### 2022-10-01 manuscript.Rmd
Added code for automatically downloading data from OSF

@@
 # 2 - download processed individual data and analyse (requires XGB of storage)
-# 3 - download all raw data and analyse (requires XGB of storage)
+# 3 - download all raw data and analyse (requires 78+GB of storage)
 
@@
 # input is a row from a spreadsheet indicating responses to 28 questions
-AQanswers <- toupper(c('(1) Definitely agree','(2) Slightly agree', '(3) Slightly disagree', '(4) Definitely disagree'))
-reverseitems <- rep(0,28)
+AQanswers <- toupper(c('(4) Definitely agree','(3) Slightly agree', '(2) Slightly disagree', '(1) Definitely disagree'))
+reverseitems <- rep(1,28)
  # reverse scored questionnaire items
-reverseitems[c(7, 50, 52, 54, 55, 58, 59, 62, 63, 64, 65, 66, 67, 69, 72)] <- 1
+reverseitems[c(3,5,8,11,12,19,21,22,24,25,26,27,28)] <- 0
 
@@
 if (!dir.exists('temp/EEGprocessed/')){dir.create('temp/EEGprocessed/')}
+if (!dir.exists('temp/pilotraw/')){dir.create('temp/pilotraw/')}
+if (!dir.exists('temp/pilotraw/temp/')){dir.create('temp/pilotraw/temp/')}
 
@@
 
-hdata <- read.csv('~/Google Drive/Current work/R scripts/EEG analysis/headerfile.csv', header = TRUE)
+osfproject <- osf_retrieve_node("ab3yv")
+componentlist <- osf_ls_nodes(osfproject)
+osffiles <- osf_ls_files(osfproject,n_max=300)
+
+pilotproject <- osf_retrieve_node("y4n5k")
+pilotfiles <- osf_ls_files(pilotproject,n_max=300)
+if (!file.exists('temp/headerfile.csv')){
+  hid <- pmatch('headerfile.csv',as.character(unlist(pilotfiles[,1])))
+  osf_download(pilotfiles[hid,], path='temp/')
+}
+hdata <- read.csv('temp/headerfile.csv')
 
@@
 
-osfnode <- 'y4n5k'    # this is where the pilot data are stored
-osfproject <- osf_retrieve_node(osfnode)
-EEGfiles <- osf_ls_files(osfproject,n_max=300)
-
-datadir <- 'temp/raw/'
-tempdir <- 'temp/raw/temp/'
-
-hdata <- read.csv('~/Google Drive/Current work/R scripts/EEG analysis/headerfile.csv', header = TRUE)
+datadir <- 'temp/pilotraw/'
+
 legaltriggers <- hdata$Trigger[!is.na(hdata$Trigger)]
@@
 
-    if (s < 10){tarname <- paste0('S0', s, '.tar')}
-    if (s > 9){tarname <- paste0('S', s, '.tar')}
+    if (s < 10){subname <- paste0('S0', s)}
+    if (s > 9){subname <- paste0('S', s)}
+
+    tarname <- paste0(subname,'.tar')
 
     if (!file.exists(paste0(datadir,tarname))){
-      fid <- which(EEGfiles$name==tarname)
-      osf_download(EEGfiles[fid,],datadir,progress=TRUE)
-    }
+      fid <- which(pilotfiles$name==tarname)
+      osf_download(pilotfiles[fid,],datadir,progress=TRUE)
+    }
+    untar(paste0(datadir,tarname),exdir=paste0(datadir,subname))
+    file.remove(paste0(datadir,tarname))  # delete after unpacking
 
@@
     allsamples <- array(0, dim = c(10,20,64,duration*samplerate))
-
-    untar(paste0(datadir,tarname),exdir=tempdir)
-
-    condcounter <- (1:20) * 0
-    allsamples <- array(0, dim = c(10,20,64,duration*samplerate))
-    if (s < 10){d <- dir(path = paste0(tempdir,'S0',s), pattern='*.csv.gz',full.names=TRUE)}
-    if (s > 9){d <- dir(path = paste0(tempdir,'S',s), pattern='*.csv.gz',full.names=TRUE)}
-
-    d <- dir(path = tempdir, pattern = '*.csv.gz')
+    d <- dir(path = paste0(datadir,subname), pattern='*.csv.gz',full.names=TRUE)
 
@@
       counter <- 0
-      for (n in 1500:nrow(EEGdata)) {    # ignore triggers starting in the first 1000ms that generate an error
+       # ignore triggers starting in the first 1000ms that generate an error
+      for (n in 1500:nrow(EEGdata)) {   
         if (EEGdata$Trigger[n] %in% legaltriggers) {
@@
 
-    for (block in 1:length(d)){file.remove(d[block])}
+     # optionally delete the files after use
+    # for (block in 1:length(d)){file.remove(d[block])}
 
@@
 d <- dir(path = 'temp/VilidaiteProcessed', pattern = '*.RData', full.names=TRUE)
+
+# download any missing data files from osf
+if (length(d)<100){
+  pilotrepo <- pmatch('Processed pilot data',as.character(unlist(componentlist[,1])))
+  pilotfiles <- osf_ls_files(componentlist[pilotrepo,2],n_max=300)
+  for (s in 1:length(pilotfiles)){
+    if (!file.exists(paste0('temp/VilidaiteProcessed/',pilotfiles[s,1]))){
+      osf_download(pilotfiles[s,],'temp/VilidaiteProcessed/',progress=TRUE)
+    }
+  }
+}
+
+d <- dir(path = 'temp/VilidaiteProcessed', pattern = '*.RData', full.names=TRUE)
+
 EEGtimecourse <- array(0,dim=c(length(d),length(findex),3,13000))
@@
 
+      if (!file.exists('temp/Pilotsummary.RData')){
+      hid <- pmatch('Pilotsummary.RData',as.character(unlist(osffiles[,1])))
+      osf_download(osffiles[hid,],'temp/',progress=TRUE)
+      }  
 load('temp/Pilotsummary.RData')
@@
 
+ if (!file.exists('temp/Pilotsummary.RData')){
+      hid <- pmatch('Pilotsummary.RData',as.character(unlist(osffiles[,1])))
+      osf_download(osffiles[hid,],'temp/',progress=TRUE)
+}
 load('temp/Pilotsummary.RData')
@@
 The top panel of Figure \@ref(fig:Pilotdata)c shows the response at the target frequency (7Hz) to a single stimulus of 32% contrast (black), and the response at 7Hz when the 32% contrast mask is added (blue).
+For comparison, a baseline timecourse is also shown (grey), which was the response at 7Hz when a 5Hz stimulus was shown (therefore controlling for attention, blinking etc.).
 Analogous responses are shown at three other frequencies - the mask frequency (5Hz), and the second harmonics of both target and mask frequencies (14Hz, 10Hz), at which strong responses were also found (see spectra in Figure \@ref(fig:Pilotdata)b).
@@
     }
-
  }
@@
 d <- dir(path = 'temp/EEGprocessed', pattern = '*.RData', full.names=TRUE)
+
+# download any missing data files from osf
+if (length(d)<100){
+  EEGrepo <- pmatch('Processed EEG data',as.character(unlist(componentlist[,1])))
+  EEGfiles <- osf_ls_files(componentlist[EEGrepo,2],n_max=300)
+  for (s in 1:length(EEGfiles)){
+    if (!file.exists(paste0('temp/EEGProcessed/',EEGfiles[s,1]))){
+      osf_download(EEGfiles[s,],'temp/EEGProcessed/',progress=TRUE)
+    }
+  }
+}
+
+d <- dir(path = 'temp/EEGprocessed', pattern = '*.RData', full.names=TRUE)
+
 EEGtimecourse5Hz <- array(0,dim=c(length(d),4,8000))
@@
 # bootstrapping and figure plotting for EEG data
+
+ if (!file.exists('temp/EEGsummary.RData')){
+      hid <- pmatch('EEGsummary.RData',as.character(unlist(osffiles[,1])))
+      osf_download(osffiles[hid,],'temp/',progress=TRUE)
+ }
 
@@
 
-  d <- dir(path = 'temp/wang/', pattern = '*alltrialsFullV1.mat', full.names=TRUE)
-  d2 <- dir(path = 'temp/wang/', pattern = '*alltrialsFullV1.mat', full.names=FALSE)
+  d <- dir(path = 'temp/MEGdata/', pattern = '*data.RData', full.names=TRUE)
+
+  # download any missing data files from osf
+if (length(d)<20){
+  MEGrepo <- pmatch('Processed MEG data',as.character(unlist(componentlist[,1])))
+  MEGfiles <- osf_ls_files(componentlist[MEGrepo,2],n_max=300)
+  for (s in 1:length(MEGfiles)){
+    if (!file.exists(paste0('temp/MEGdata/',MEGfiles[s,1]))){
+      osf_download(MEGfiles[s,],'temp/MEGdata/',progress=TRUE)
+    }
+  }
+}
+
+   d <- dir(path = 'temp/MEGdata/', pattern = '*data.RData', full.names=TRUE)
 
@@
   MEGtimecourse7Hz <- array(0,dim=c(length(d),4,8008))
-  # allwaves <- array(0,dim=c(length(d),4,9009))
+  MEGtrialsincluded <- matrix(0,nrow=20,ncol=4)
+  MEGsubjwaves <- array(0,dim=c(length(d),4,9009))
   allspec <- array(0,dim=c(length(d),4,duration*20))
-  allRnos <- NULL
+  MEGallAQ <- NULL
+  MEGallSPQ <- NULL
+  MEGallAge <- NULL
+  MEGallGender <- NULL
+  MEGallDiagnosis <- NULL
   for (s in 1:length(d)){
-    allRnos[s] <- substr(d2[s],1,5)
-    data <- readMat(d[s])
+
+    load(d[s])
+
+    MEGallAge[s] <- qdatasubj[1,1]
+    MEGallGender[s] <- qdatasubj[1,2]
+    MEGallDiagnosis[s] <- qdatasubj[1,3]
+    if (qdatasubj[1,5]!=0){
+    MEGallAQ[s] <- scoreAQ(qdatasubj[1,5:54])
+    MEGallSPQ[s] <- scoreSPQ(qdatasubj[1,55:146])
+    }
+    if (qdatasubj[1,5]==0){MEGallAQ[s] <- 999
+    MEGallSPQ[s] <- 999}
 
       for (cond in 1:4){
-        temp <- colMeans(data$alltrials[cond,1:data$trialcounter[1,cond],],na.rm=TRUE)
-        nainds <- which(is.na(temp))   # find occasional NaN values in the waveform
-        temp[nainds] <- 0   # replace with zeros
-        # allwaves[s,cond,] <- temp - mean(temp)
-        spec <- fft(temp[1501:7500])/6000
+
+          temp <- alltrials[cond,1:trialcounter[1,cond],]
+          spec5 <- NULL
+          spec7 <- NULL
+          for (t in 1:trialcounter[1,cond]){
+            spec <- fft(temp[t,1501:7506])/6006
+            spec5[t] <- spec[targetF*duration+1]
+            spec7[t] <- spec[maskF*duration+1]
+          }
+        spec5[which(is.na(spec5))] <- 0
+        spec7[which(is.na(spec7))] <- 0
+      if (length(which(abs(spec5)>0))>2){  
+      tempxy <- data.frame(Re(spec5),Im(spec5))
+      D5 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+      tempxy <- data.frame(Re(spec7),Im(spec7))
+      D7 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))      
+      i <- which(D5<3 & D7<3)
+      MEGtrialsincluded[s,cond] <- length(i)
+      temp <- colMeans(temp[i,])
+      MEGsubjwaves[s,cond,] <- temp
+      spec <- fft(temp[1501:7506])/6006
       allspec[s,cond,] <- spec[1+(1:(duration*20))]
@@
         }
+
         MEGtimecourse5Hz[s,cond,] <- fspec1
@@
 
-  save(file='temp/MEGsummaryV1.RData',list=c('allspec','MEGtimecourse5Hz','MEGtimecourse7Hz','allRnos'))
+  }
+
+  save(file='temp/MEGsummary.RData',list=c('allspec','MEGtimecourse5Hz','MEGtimecourse7Hz','MEGtrialsincluded','MEGallAge','MEGallGender','MEGallDiagnosis','MEGallAQ','MEGallSPQ'))
 
@@
 
+ if (!file.exists('temp/MEGsummary.RData')){
+      hid <- pmatch('MEGsummary.RData',as.character(unlist(osffiles[,1])))
+      osf_download(osffiles[hid,],'temp/',progress=TRUE)
+ }
+
+load('temp/MEGsummary.RData')
+MEGpercentexcluded <- 100 - (100*mean(MEGtrialsincluded)/48)
+
 if (processdata>0){
-  load('temp/MEGsummaryV1.RData')
 
@@
       meanspec[cond,] <- colMeans(abs(allspec[which(isincluded[cond,]==1),cond,]),na.rm=TRUE)
-      # meanwave[area,cond,] <- colMeans(allwaves[which(isincluded[area,cond,]==1),area,cond,],na.rm=TRUE)
     }
@@
     polygon(times[c(1:8008,8008:1)],c(spl7dU$y,spl7dL$y[8008:1]),col=colpal[3],border=NA)
-
-    # spl7a <- smooth.spline(times,MEGmeantime7Hz[1,],df=20)
-    # lines(spl7a$x,spl7a$y,col=colpal[1],lwd=2)
 
@@
 
-  # lines(c(5,5),c(0,4),col='grey',lwd=2)
-  # lines(c(7,7),c(0,4),col='grey',lwd=2)
-
   polygon(c(1,freqlist[6:120],20),c(0,40*meanspec[1,6:120],0)+3,border=NA,col=colpal[1])
@@
 
+   if (!file.exists('temp/groupbrainbothSNR.tif')){
+      hid <- pmatch('groupbrainbothSNR.tif',as.character(unlist(osffiles[,1])))
+      osf_download(osffiles[hid,],'temp/',progress=TRUE)
+   }
+   if (!file.exists('temp/LH.tif')){
+      hid <- pmatch('LH.tif',as.character(unlist(osffiles[,1])))
+      osf_download(osffiles[hid,],'temp/',progress=TRUE)
+   }
+  if (!file.exists('temp/RH.tif')){
+      hid <- pmatch('RH.tif',as.character(unlist(osffiles[,1])))
+      osf_download(osffiles[hid,],'temp/',progress=TRUE)
+   }
   e1 <- readTIFF('temp/groupbrainbothSNR.tif')
@@
 
-  # text(-0.02,0.89,'5Hz',pos=4,cex=2)
-  # text(-0.02,0.61,'7Hz',pos=4,cex=2)
-
   dev.off()
@@
 
+ if (!file.exists('temp/EEGsummary.RData')){
+      hid <- pmatch('EEGsummary.RData',as.character(unlist(osffiles[,1])))
+      osf_download(osffiles[hid,],'temp/',progress=TRUE)
+ }
 load('temp/EEGsummary.RData')
 
-pilotAQ <- read.csv('temp/AQscores.csv',header=FALSE)
-pilotAQ <- pilotAQ[-75,2]
-
-load("temp/questionnairedataMSci.RData")
-MEGAQ <- qdata$AQ[1:19]
-MEGgroup <- qdata$Diagnosis[1:19]
+ if (!file.exists('temp/pilotquestionnaire.csv')){
+      hid <- pmatch('pilotquestionnaire.csv',as.character(unlist(osffiles[,1])))
+      osf_download(osffiles[hid,],'temp/',progress=TRUE)
+ }
+pilotqdata <- read.csv('temp/pilotquestionnaire.csv')
+pilotAQ <- NULL
+for (n in 1:101){
+  pilotAQ[n] <- scoreAQshort(pilotqdata[n,3:30])
+}
+pilotAQ <- pilotAQ[-75]
+
+ if (!file.exists('temp/MEGsummary.RData')){
+      hid <- pmatch('MEGsummary.RData',as.character(unlist(osffiles[,1])))
+      osf_download(osffiles[hid,],'temp/',progress=TRUE)
+ }
+load("temp/MEGsummary.RData")
+MEGAQ <- MEGallAQ[2:20]
+MEGgroup <- MEGallDiagnosis[2:20]
 
@@
 
-t_age <- t.test(qdata$Age[which(qdata$Diagnosis=='Yes')],qdata$Age[which(qdata$Diagnosis=='No')],paired=FALSE,var.equal=TRUE)
-
-corMEG <- cor.test(qdata$AQ[1:19],qdata$SPQ[1:19])
+t_age <- t.test(MEGallAge[which(MEGallDiagnosis=='Yes')],MEGallAge[which(MEGallDiagnosis=='No')],paired=FALSE,var.equal=TRUE)
+
+corMEG <- cor.test(MEGallAQ[2:20],MEGallSPQ[2:20])
 corEEG <- cor.test(allAQ,allSPQ)
@@
 
+   if (!file.exists('temp/Pilotsummary.RData')){
+      hid <- pmatch('Pilotsummary.RData',as.character(unlist(osffiles[,1])))
+      osf_download(osffiles[hid,],'temp/',progress=TRUE)
+ }
   load('temp/Pilotsummary.RData')
@@
 
-  load('temp/MEGsummaryV1.RData')
-  MEGgroup <- qdata$Diagnosis
-  MEGID <- qdata$ID
-  dataorder <- match(MEGID,allRnos)
-  # dataorder tells us the indices into the MEG data for each AQ score
+  load('temp/MEGsummary.RData')
+  MEGgroup <- MEGallDiagnosis
 
@@
 
-  CONindices <- dataorder[which(MEGgroup=='No')]
-  ASCindices <- dataorder[which(MEGgroup=='Yes')]
+  CONindices <- which(MEGgroup=='No')
+  ASCindices <- which(MEGgroup=='Yes')
   isCON <- (1:20)*0
@@
 Figure \@ref(fig:AQanalysis)a-c shows distributions of AQ scores for each experiment, and indicates for the pilot and EEG data which participants were in the high (purple) and low (green) AQ groups.
-The median AQ scores were `r round(median(pilotAQ),digits=0)` for the pilot data, and `r median(allAQ)` for the EEG data, consistent with previous results for the general population [@Baron-Cohen2001].
+The median AQ scores were `r round(median(pilotAQ),digits=0)` for the pilot data, and `r median(allAQ)` for the EEG data.
 In the MEG experiment, AQ scores for the autism group (mean `r round(mean(MEG_A),digits=1)`) and the control group (mean `r round(mean(MEG_C),digits=1)`) were significantly different (*t* = `r format(round(t$statistic,digits=2),nsmall=2)`, *df* = `r round(t$parameter,digits=1)`, *p* < 0.001), with minimal overlap (one participant with an autism diagnosis had an AQ score marginally lower than the highest AQ scores from the control group).
+These distributions are consistent with previous results for AQ [@Baron-Cohen2001].
 
@@
 We excluded trials for which the Mahalanobis distance of the complex Fourier components exceeded 3 [for details see @Baker2021].
-This resulted in `r round(Pilotpercentexcluded,digits=2)`% of trials being excluded for Experiment 1, `r round(EEGpercentexcluded,digits=2)`% of trials for Experiment 2, and `r round(EEGpercentexcluded,digits=2)`% of trials for Experiment 3.
+This resulted in `r round(Pilotpercentexcluded,digits=2)`% of trials being excluded for Experiment 1, and `r round(EEGpercentexcluded,digits=2)`% of trials for Experiment 2.
 Next we averaged the waveforms across all remaining trials, and calculated the Fourier transform in a 1-second sliding window to generate timecourses for each participant.
@@
 These signals were then imported into R for the main analysis, which was consistent with the EEG analysis described above.
+The outlier rejection procedure excluded `r round(MEGpercentexcluded,digits=2)`% of trials for Experiment 3.
 

### 2022-10-01 manuscript.tex
Added code for automatically downloading data from OSF

@@
 The top panel of Figure \ref{fig:Pilotdata}c shows the response at the target frequency (7Hz) to a single stimulus of 32\% contrast (black), and the response at 7Hz when the 32\% contrast mask is added (blue).
+For comparison, a baseline timecourse is also shown (grey), which was the response at 7Hz when a 5Hz stimulus was shown (therefore controlling for attention, blinking etc.).
 Analogous responses are shown at three other frequencies - the mask frequency (5Hz), and the second harmonics of both target and mask frequencies (14Hz, 10Hz), at which strong responses were also found (see spectra in Figure \ref{fig:Pilotdata}b).
@@
 
-{\centering \includegraphics{temp/figures/Fig2}
+{\centering \includegraphics{Figures/EEGdata}
 
@@
 
-{\centering \includegraphics{temp/figures/Fig3}
+{\centering \includegraphics{Figures/MEGdata}
 
@@
 
-{\centering \includegraphics{temp/figures/Fig4}
+{\centering \includegraphics{Figures/AQfigure}
 
@@
 Figure \ref{fig:AQanalysis}a-c shows distributions of AQ scores for each experiment, and indicates for the pilot and EEG data which participants were in the high (purple) and low (green) AQ groups.
-The median AQ scores were 14 for the pilot data, and 18 for the EEG data, consistent with previous results for the general population (Baron-Cohen et al., 2001).
+The median AQ scores were 14 for the pilot data, and 18 for the EEG data.
 In the MEG experiment, AQ scores for the autism group (mean 36.1) and the control group (mean 16.7) were significantly different (\emph{t} = 6.00, \emph{df} = 14.2, \emph{p} \textless{} 0.001), with minimal overlap (one participant with an autism diagnosis had an AQ score marginally lower than the highest AQ scores from the control group).
+These distributions are consistent with previous results for AQ (Baron-Cohen et al., 2001).
 
@@
 The similarity between monocular and dichoptic effects also differs from work on adaptation to individual mask components.
-In both physiological (Li et al., 2005; \textbf{Sengpiel2006?}) and psychophysical (Baker et al., 2007) paradigms, adapting to a dichoptic mask reduces its potency, whereas adapting to a monocular mask has little or no effect.
+In both physiological (Li et al., 2005; Sengpiel and Vorobyov, 2005) and psychophysical (Baker et al., 2007) paradigms, adapting to a dichoptic mask reduces its potency, whereas adapting to a monocular mask has little or no effect.
 Normalization reweighting offers an explanation for why monocular masks presented in isolation do not adapt: if suppressive weights are determined by co-occurrence of stimuli, presentation of an isolated mask will have little effect.
@@
 We excluded trials for which the Mahalanobis distance of the complex Fourier components exceeded 3 (for details see Baker, 2021).
-This resulted in 0.25\% of trials being excluded for Experiment 1, 4.51\% of trials for Experiment 2, and 4.51\% of trials for Experiment 3.
+This resulted in 0.25\% of trials being excluded for Experiment 1, and 4.51\% of trials for Experiment 2.
 Next we averaged the waveforms across all remaining trials, and calculated the Fourier transform in a 1-second sliding window to generate timecourses for each participant.
@@
 These signals were then imported into R for the main analysis, which was consistent with the EEG analysis described above.
+The outlier rejection procedure excluded 2.47\% of trials for Experiment 3.
 

### 2022-10-02 manuscript.Rmd
Bug fixes

@@
 # 0 - do no processing, generate the pdf using existing versions of all figures
-# 1 - generate figures using the processed group data (requires XGB of storage)
-# 2 - download processed individual data and analyse (requires XGB of storage)
-# 3 - download all raw data and analyse (requires 78+GB of storage)
+# 1 - generate figures using the processed group data (requires 0.4GB of storage)
+# 2 - download processed individual data and analyse (requires 11.5GB of storage)
+# 3 - download all raw data and analyse (requires 143GB of storage)
 
@@
 if (!dir.exists('temp/pilotraw/')){dir.create('temp/pilotraw/')}
-if (!dir.exists('temp/pilotraw/temp/')){dir.create('temp/pilotraw/temp/')}
 
@@
 osffiles <- osf_ls_files(osfproject,n_max=300)
-
 pilotproject <- osf_retrieve_node("y4n5k")
 pilotfiles <- osf_ls_files(pilotproject,n_max=300)
+
 if (!file.exists('temp/headerfile.csv')){
@@
       fid <- which(pilotfiles$name==tarname)
-      osf_download(pilotfiles[fid,],datadir,progress=TRUE)
-    }
+      if (!pracma::isempty(fid)){
+      osf_download(pilotfiles[fid,],datadir,progress=TRUE)}
+    }
+    if (file.exists(paste0(datadir,tarname))){
     untar(paste0(datadir,tarname),exdir=paste0(datadir,subname))
     file.remove(paste0(datadir,tarname))  # delete after unpacking
-
+    }
     condcounter <- (1:20) * 0
@@
 
+    if (!pracma::isempty(d)){
     for (block in 1:length(d)) {
@@
     # for (block in 1:length(d)){file.remove(d[block])}
-
+}
   }
@@
   pilotfiles <- osf_ls_files(componentlist[pilotrepo,2],n_max=300)
-  for (s in 1:length(pilotfiles)){
+  for (s in 1:nrow(pilotfiles)){
     if (!file.exists(paste0('temp/VilidaiteProcessed/',pilotfiles[s,1]))){
@@
 i <- 0
-for (s in 1:100){
+for (s in 1:dim(EEGallconds)[1]){
   for (cond in 1:14){
@@
     subjcounter <- subjcounter + 1
-    print(subjcounter)
+    subID <- unlist(strsplit(EEGfiles$name[f],'.zip'))
+    print(subID)
     # first check if we have this participant's data
-    if (!file.exists(paste0('temp/EEGprocessed/S',subjcounter,'data.RData'))){
+    if (!file.exists(paste0('temp/EEGprocessed/',subID,'data.RData'))){
       # if we haven't processed the data, check if we need to download the raw data
-      if (!dir.exists(paste0('temp/raw/S',subjcounter))){
-        if (!file.exists(paste0('temp/raw/S',subjcounter,'.zip'))){
+      if (!dir.exists(paste0('temp/raw/',subID))){
+        if (!file.exists(paste0('temp/raw/',EEGfiles$name[f]))){
           osf_download(EEGfiles[f,], path='temp/raw/',progress=TRUE)
         }
-          unzip(paste0('temp/raw/S',subjcounter,'.zip'),exdir='temp/raw/')
-          file.remove(paste0('temp/raw/S',subjcounter,'.zip'))
+          unzip(paste0('temp/raw/',EEGfiles$name[f]),exdir='temp/raw/')
+          file.remove(paste0('temp/raw/',EEGfiles$name[f]))
       }
@@
 
-      d <- dir(paste0('temp/raw/S',subjcounter), pattern='*.csv.gz',full.names=TRUE)
+      d <- dir(paste0('temp/raw/',subID), pattern='*.csv.gz',full.names=TRUE)
       condcounter <- (1:4) * 0
@@
 
-      qdatasubj <- read.csv(paste0('temp/raw/S',subjcounter,'/questionnairedata.csv'))
-      save(file=paste0('temp/EEGprocessed/S',subjcounter,'data.RData'),list=c('qdatasubj','condcounter','trialsincluded','subjwaves','electrodes'))
+      qdatasubj <- read.csv(paste0('temp/raw/',subID,'/questionnairedata.csv'))
+      save(file=paste0('temp/EEGprocessed/',subID,'data.RData'),list=c('qdatasubj','condcounter','trialsincluded','subjwaves','electrodes'))
     }
@@
   EEGfiles <- osf_ls_files(componentlist[EEGrepo,2],n_max=300)
-  for (s in 1:length(EEGfiles)){
-    if (!file.exists(paste0('temp/EEGProcessed/',EEGfiles[s,1]))){
-      osf_download(EEGfiles[s,],'temp/EEGProcessed/',progress=TRUE)
+  for (s in 1:nrow(EEGfiles)){
+    if (!file.exists(paste0('temp/EEGprocessed/',EEGfiles[s,1]))){
+      osf_download(EEGfiles[s,],'temp/EEGprocessed/',progress=TRUE)
     }
@@
   MEGfiles <- osf_ls_files(componentlist[MEGrepo,2],n_max=300)
-  for (s in 1:length(MEGfiles)){
+  for (s in 1:nrow(MEGfiles)){
     if (!file.exists(paste0('temp/MEGdata/',MEGfiles[s,1]))){

### 2023-02-10 manuscript.Rmd
Reformatted for journal submmission

@@
   | Emily L. Williams, Hannah M. Hobson & Alex R. Wade
-date: "`r Sys.Date()`"
+date: "Department of Psychology, University of York, UK"
 output:
@@
 # reasonably compact code to check which packages are installed, install the missing ones, and activate all
-packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','rmarkdown','grImport','tiff','pals','ez','gtools','pracma') # list of CRAN packages
+packagelist <- c('knitr','remotes','tictoc','R.matlab','bookdown','rmarkdown','grImport','tiff','pals','ez','gtools','pracma','osfr') # list of CRAN packages
 missingpackages <- packagelist[!packagelist %in% installed.packages()[,1]]
 if (length(missingpackages)>0){install.packages(missingpackages)}
-if (!'osfr' %in% installed.packages()[,1]){remotes::install_github("centerforopenscience/osfr")}
 if (!'FourierStats' %in% installed.packages()[,1]){remotes::install_github("bakerdh/FourierStats")}
-packagelist <- c(packagelist,'osfr','FourierStats')
+packagelist <- c(packagelist,'FourierStats')
 toinstall <- packagelist[which(!packagelist %in% (.packages()))]
@@
 
-# Abstract
-
-For decades, neural suppression in early visual cortex has been thought to be fixed.
-But recent work has challenged this assumption by showing that suppression can be \emph{reweighted} based on recent history; when pairs of stimuli are repeatedly presented together, suppression between them strengthens.
-Here we investigate the temporal dynamics of this process using a steady-state VEP paradigm that provides a time-resolved, direct index of suppression between pairs of stimuli flickering at different frequencies (5 and 7Hz).
-Our initial analysis of an existing EEG dataset (N=100) indicated that suppression increases substantially during the first 2-5 seconds of stimulus presentation (with some variation across stimulation frequency).
-We then collected new EEG data (N=100) replicating this finding for both monocular and dichoptic mask arrangements in a preregistered study designed to measure reweighting.
-A third experiment (N=20) used source localized MEG, and found that these effects are apparent in primary visual cortex (V1), consistent with results from neurophysiological work.
-Because long-standing theories propose inhibition/excitation differences in autism, we also compared reweighting between individuals with high vs low autistic traits, and with and without an autism diagnosis, across our 3 data sets (total N=220).
-We find no compelling differences in reweighting that are associated with autism.
-Our results support the normalization reweighting model, and indicate that for prolonged stimulation, increases in suppression occur on the order of 2-5 seconds after stimulus onset.
-
-# Introduction
-
-Suppressive interactions between neurons are ubiquitous in the nervous system, and normalization (or gain control) processes are considered a canonical neuronal computation [@Carandini2011].
-Yet for decades the strength of suppression was treated as fixed, largely due to the observation that adapting to one stimulus does not decrease its suppressive potency [@Foley1997; @Freeman2002].
-This orthodoxy was recently challenged by a series of innovative studies showing that normalization can be 'reweighted' by recent history [@Westrick2016; @Aschner2018; @Yiltiz2020].
-Specifically, when pairs of stimuli are repeatedly presented together, their neural representations come to suppress each other more strongly.
-This suggests that, far from being fixed, normalization is a dynamic process that is continuously updated by the sensory environment.
-Here, our objectives were to determine if the timecourse of these changes can be measured non-invasively from the human brain, assess if they occur similarly in distinct suppressive pathways, and determine whether they differ across the population as a function of autistic traits.
-
-Plastic changes within the visual system occur over multiple timescales [see @Webster2015 for a recent review].
-In the retina, adaptation to complete darkness takes around 30 minutes [@Lamb2006], and has established physiological substrates (i.e.
-the regeneration rate of chemicals in different photoreceptor classes).
-Cortical forms of adaptation to cues such as stimulus contrast [@Blakemore1969], orientation [@Gibson1937] and motion [@Mather2008] can be observed within a few seconds, but also build up over durations on the order of several minutes [@Greenlee1991].
-A recent form of binocular plasticity [@Lunghi2011], in which one eye is patched and subsequently contributes more to binocular vision, requires more than an hour.
-Other types of adaptation have been identified with changes occurring over longer time periods, such as over several hours [@Kwon2009] or days [@Haak2014].
-Finally adaptation to specific combinations of orientation and colour [the @McCollough1965 effect] can persist for several weeks [@Jones1975], even with a brief induction period.
-Previous work on normalization reweighting has involved adapting sequences of around 40 -- 60s [@Aschner2018; @Yiltiz2020], though it is possible that reweighting might occur faster than this, consistent with other types of contrast adaptation.
-
-Normalization itself is not a single process.
-Multiple suppressive pathways have been identified in the visual system, including between stimuli differing in orientation [@Heeger1992; @Foley1994], eye-of-origin [@Legge1979; @Sengpiel1994] and spatial position [@Petrov2005; @Cannon1991].
-At present there is evidence of normalization reweighting between stimuli with orthogonal orientations [@Aschner2018], and adjacent spatial positions [@Yiltiz2020].
-We anticipated that interocular suppression should also be subject to reweighting, but that there might be differences in the dynamics across suppressive pathways.
-This is plausible, given that suppression within and between the eyes has different spatiotemporal tuning [@Meese2009], and dichoptic masking can be reduced by adapting to the mask [@Sengpiel2005; @Li2005; @Baker2007], unlike within-eye masking.
-Dynamic fluctuations in interocular suppression are a key feature of binocular rivalry [@Wilson2003; @Alais2010], for which autism-related differences have also been reported [@Robertson2013].
-By comparing monocular and dichoptic suppression, we are also able to isolate any contribution of early pre-cortical factors.
-This is because interocular suppression impacts in primary visual cortex, and therefore bypasses earlier retinal and subcortical stages of processing that may contribute to monocular suppression [@Li2005].
-
-Atypical sensory experience is widely reported by individuals on the autism spectrum [@MacLennan2022; @Simmons2009], but the causal mechanisms remain unclear.
-Typical issues include hypersensitivity to intense stimuli such as loud sounds, bright lights and strong odours or flavours.
-Yet fundamental measures of sensitivity such as visual acuity [@Tavassoli2011], contrast sensitivity [@Koh2010], and audiometric performance [@Rosenhall1999] are not consistently different from neurotypical controls.
-Theoretical accounts of sensory differences in autism have long proposed that the balance of inhibition and excitation may be disrupted [@Rubenstein2003; @Rosenberg2015], and there are isolated results that appear consistent with this.
-For example neural measures of surround suppression are weaker in autism [@Schallmo2020], binocular rivalry is slower [@Robertson2013] and orientation discrimination performance is better [@Dickinson2014].
-Conversely, other studies have failed to find group differences using paradigms that should be equally dependent on inhibition, such as orientation repulsion [@VandeCruys2018], repetition suppression [@Utzerath2018] and psychophysical measures of surround suppression [@Sandhu2020].
-The evidence for atypical inhibition in autism is therefore currently inconclusive.
-
-Our recent work has identified a potential autism-related difference in gain control using steady-state EEG methods.
-@Vilidaite2018 measured contrast response functions for flickering stimuli in a large group of neurotypical adults, who were grouped according to their autism quotient [AQ, see @Baron-Cohen2001] score.
-The responses were comparable between high and low AQ groups at the flicker frequency of the stimulus.
-However at the second harmonic frequency (twice the flicker frequency), the high AQ group showed weaker responses than the low AQ group.
-This effect was replicated in an independent sample of 12 adults with an autism diagnosis (compared with neurotypical controls).
-Because second harmonic responses are caused by nonlinear interactions in the visual system (they are absent in a linear system), and divisive suppression is a nonlinearity, this potentially implicates differences in suppression in autism.
-Furthermore, there appears to be a developmental trajectory, as autistic children tested as part of the same study [@Vilidaite2018] showed weaker responses at both the first and second harmonic frequencies.
-
-In this paper we perform a time-course analysis of a previously published EEG data set, and report two novel pre-registered experiments using EEG and MEG.
-Our data show that suppression increases substantially during the first 2-5 seconds following stimulus onset, for both monocular and dichoptic masks.
-Source localisation of MEG data indicate that the reweighting is present as early as primary visual cortex (V1).
-We also hypothesised that normalization reweighting might differ as a function of autistic traits.
-The relative novelty of the reweighting framework could explain why any differences have not previously been detected, and why the literature on inhibition in autism is relatively inconclusive.
-However we did not find convincing support for this hypothesis.
-
-# Results
-
 ```{r include=FALSE, results='hide'}
@@
 ```
-
-We began by reanalysing data from a steady-state visually evoked potential (SSVEP) experiment reported by @Vilidaite2018.
-Participants viewed arrays of flickering gratings of varying contrasts.
-In some conditions a single grating orientation was present flickering at 7Hz, whereas in other conditions a high contrast 'mask' was added at right angles to the target gratings, and flickering at 5Hz.
-The left panel of Figure \@ref(fig:Pilotdata)a shows contrast response functions with and without the mask - the presence of the mask reduces the 7Hz response to the target (blue squares are below the black circles; significant main effect of mask contrast, F(1,99) = `r round(maskinganova1$ANOVA$F[2],digits=2)`, \emph{p} < 0.001).
-Similarly, the right panel of Figure \@ref(fig:Pilotdata)a shows that the 5Hz response to the mask was itself suppressed by the presence of high contrast targets (main effect of target contrast on the mask response, F(`r round(maskinganova2$ANOVA$DFn*gg,digits=2)`,`r round(maskinganova2$ANOVA$DFd*gg,digits=2)`) = `r round(maskinganova2$ANOVA$F,digits=2)`, \emph{p} < 0.001; note that the data from the masking conditions were not reported by @Vilidaite2018).
-At both frequencies, responses were localised to the occipital pole (see insets).
-
-```{r Pilotdata, fig.cap="Summary of pilot analysis of data from Vilidiate et al.
-(2018).
-Panel (a) shows contrast response functions at the target frequency (7Hz, left) and the mask frequency (5Hz, right).
-Insets show the distribution of activity across the scalp, with points marking the electrodes over which signals were averaged (Oz, POz, O1 and O2).
-Panel (b) shows Fourier spectra for the single component stimuli and their combination (plaid).
-Note the strong second harmonic components at 14Hz and 10Hz.
-Panel (c) shows timecourses of frequency-locked responses to a single stimulus (black) and the plaid stimulus (blue), compared to baseline (grey).
-Panel (d) shows the timecourse of suppression at each frequency (7Hz, 5Hz, 14Hz, 10Hz) and their average (black curve).
-Points around y = 1.8 indicate a significantly increasing ratio.
-Error bars in panel (a) and shaded regions in panels (c,d) indicate ±1SE across N=100 participants, and grey rectangles indicate the timing of stimulus presentation.
-The larger symbols in panel (a) indicate the conditions used for subsequent analyses.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('Figures/VilidaiteData.pdf')
-
-```
-
-We then performed a timecourse analysis, in which we analysed each 11-second trial using a sliding 1-second time window.
-The top panel of Figure \@ref(fig:Pilotdata)c shows the response at the target frequency (7Hz) to a single stimulus of 32% contrast (black), and the response at 7Hz when the 32% contrast mask is added (blue).
-For comparison, a baseline timecourse is also shown (grey), which was the response at 7Hz when a 5Hz stimulus was shown (therefore controlling for attention, blinking etc.).
-Analogous responses are shown at three other frequencies - the mask frequency (5Hz), and the second harmonics of both target and mask frequencies (14Hz, 10Hz), at which strong responses were also found (see spectra in Figure \@ref(fig:Pilotdata)b).
-The reduction in signal strength when the mask component is added illustrates the masking effect.
-
-Taking the ratio of the two timecourses to calculate a masking index reveals that at 7Hz masking increases steeply during the first two seconds of stimulus presentation, and then plateaus for several seconds (blue trace in Figure \@ref(fig:Pilotdata)d).
-A similar pattern is observed at 5Hz (red trace in Figure \@ref(fig:Pilotdata)d), as well as at the second harmonics, with some variability in the timecourse across frequencies; for example at 5Hz suppression peaks at around 4 seconds.
-The black trace shows the average masking ratio across all four frequencies, which rises steeply for just over two seconds and then stays approximately constant until stimulus offset.
-We conducted cluster-corrected t-tests between ratios separated by `r timeoffset`ms, testing for an increase in suppression ratio across time (i.e.
-a one-sided test).
-Points at y = 1.8 in Figure \@ref(fig:Pilotdata)d indicate time points where the ratio is significantly increasing, and occur mostly during the first 2 seconds of stimulus presentation.
-
-Our initial reanalysis was promising, however the data were noisy despite the large sample size (of N=100), because each participant contributed only 8 trials (88 seconds) to each condition.
-We therefore preregistered two new experiments (see https://osf.io/4qudc) to investigate these effects in greater detail.
-These had a similar overall design to the @Vilidaite2018 study, with some small changes intended to optimise the study (see Methods).
-The key differences were that we used shorter trials (because there were few changes in the latter part of the trials shown in Figure \@ref(fig:Pilotdata)d), and also focussed all trials into a smaller number of conditions, such that each participant contributed 48 repetitions (288 seconds of data) to each of 4 conditions.
 
@@
 
-Figure \@ref(fig:EEGdata) summarises the results of our EEG experiment testing a further 100 adult participants.
-Averaged EEG waveforms showed a strong oscillatory component at each of the two stimulus flicker frequencies (Figure \@ref(fig:EEGdata)a), which slightly lagged the driving signal.
-Signals were well-isolated in the Fourier domain (Figure \@ref(fig:EEGdata)b), and localised to occipital electrodes.
-Responses at 7Hz were weaker in the two masking conditions, showing significant changes in response amplitude for both the monocular (\emph{t} = `r round(t7a$statistic,digits=2)`, \emph{df} = `r t7a$parameter`, \emph{p} < 0.001) and dichoptic (\emph{t} = `r round(t7b$statistic,digits=2)`, \emph{df} = `r t7b$parameter`, \emph{p} < 0.001) masks.
-Dichoptic masking was significantly stronger than monocular masking (\emph{t} = `r round(t7c$statistic,digits=2)`, \emph{df} = `r t7c$parameter`, \emph{p} < 0.001), and a similar pattern was evident at 5Hz.
-
-```{r EEGdata, fig.cap="Summary of EEG results for N=100 adult participants.
-Panel (a) shows scalp topographies and averaged waveforms for 5Hz (top) and 7Hz (bottom) stimuli.
-The black sine wave trace in each panel illustrates the driving contrast modulation, and black points on the scalp topographies indicate electrodes Oz, O1, O2 and POz.
-Panel (b) shows the Fourier amplitude spectrum for each condition, with clear peaks at 5Hz and 7Hz.
-Panels (c,d) show timecourses at each frequency for the baseline condition (black), and the monocular (blue) and dichoptic (red) masking conditions.
-Panels (e,f) show suppression ratios as a function of time for each mask type, with points around y = 0.8 indicating a significantly increasing ratio.
-Shaded regions in panels (c-f) span ±1SE across participants, and light grey rectangles indicate the period of stimulus presentation.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('Figures/EEGdata.pdf')
-
-```
-
-The timecourse at both flicker frequencies showed an initial onset transient, and was then relatively stable for the 6 seconds of stimulus presentation (Figure \@ref(fig:EEGdata)c,d).
-The ratio of target only to target + mask conditions increased over time (Figure \@ref(fig:EEGdata)e,f) for both mask types.
-At 5Hz the increase in masking continued over the first 5 seconds of stimulus presentation (Figure \@ref(fig:EEGdata)e; points at y = 0.8 indicate significantly increasing suppression), whereas at 7Hz the increase occurred primarily during the first second after onset (Figure \@ref(fig:EEGdata)f).
-These differences across frequency are consistent with the pilot data (see Figure \@ref(fig:Pilotdata)d).
-Both monocular and dichoptic masks produced similar timecourses of suppression.
-Overall, this second study confirmed that normalization increases during the first few seconds of a steady-state trial, and extends this finding to dichoptic mask arrangements.
-
 ```{r include=FALSE, results='hide'}
@@
 
-```{r MEGdata, fig.cap="Summary of MEG results for N=20 adults.
-Panel (a) shows average SSVEP response in source space, thresholded at SNR=2 (blue, left), and locations of the V1 ROI on the medial surface of both hemispheres (right, red).
-Panel (b) shows the Fourier spectra for the four experimental conditions, from the most responsive vertex in V1.
-Panels (c,d) show timecourses at 5Hz and 7Hz, and panels (e,f) show suppression ratios for the monocular and dichoptic conditions at each frequency, with points around y = 0.8 indicating a significantly increasing ratio.
-Shaded regions in panels (c-f) indicate ±1SE across participants, and light grey rectangles indicate the period of stimulus presentation.", fig.align="center", echo=FALSE}
-
-knitr::include_graphics('Figures/MEGdata.pdf')
-
-```
-
-Next we repeated the experiment on 20 participants using a 248-channel whole-head cryogenic MEG system.
-Half of the participants had a diagnosis of autism, and the remainder were age- and gender-matched controls.
-Source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm [@VanVeen1997] showed strong localisation of steady-state signals at the occipital pole (see Figure \@ref(fig:MEGdata)a), and in the Fourier domain (Figure \@ref(fig:MEGdata)b).
-Responses from the most responsive V1 vertex showed a similar timecourse to those of the EEG experiments at both frequencies (Figure \@ref(fig:MEGdata)c,d), and showed increasing suppression during the first few seconds of stimulus presentation (Figure \@ref(fig:MEGdata)e,f).
-The normalization reweighting effect was again clearest at 5Hz, especially for the dichoptic condition (red curve in Figure \@ref(fig:MEGdata)e).
-This confirms that the reweighting effects can occur as early as primary visual cortex, consistent with findings from neurophysiology [@Aschner2018].
-However the data are more variable than for our EEG experiments, and had fewer significant clusters, owing to the smaller sample size for this dataset.
-
 ```{r include=FALSE, results='hide'}
+
+# AQ analysis and figure plotting
 
@@
 
+# Abstract
+
+For decades, neural suppression in early visual cortex has been thought to be fixed.
+But recent work has challenged this assumption by showing that suppression can be \emph{reweighted} based on recent history; when pairs of stimuli are repeatedly presented together, suppression between them strengthens.
+Here we investigate the temporal dynamics of this process using a steady-state visual evoked potential (SSVEP) paradigm that provides a time-resolved, direct index of suppression between pairs of stimuli flickering at different frequencies (5 and 7Hz).
+Our initial analysis of an existing EEG dataset (N=100) indicated that suppression increases substantially during the first 2-5 seconds of stimulus presentation (with some variation across stimulation frequency).
+We then collected new EEG data (N=100) replicating this finding for both monocular and dichoptic mask arrangements in a preregistered study designed to measure reweighting.
+A third experiment (N=20) used source localized MEG, and found that these effects are apparent in primary visual cortex (V1), consistent with results from neurophysiological work.
+Because long-standing theories propose inhibition/excitation differences in autism, we also compared reweighting between individuals with high vs low autistic traits, and with and without an autism diagnosis, across our 3 data sets (total N=220).
+We find no compelling differences in reweighting that are associated with autism.
+Our results support the normalization reweighting model, and indicate that for prolonged stimulation, increases in suppression occur on the order of 2-5 seconds after stimulus onset.
+
+# Significance statement
+
+We investigated the timecourse of a novel form of neural plasticity, normalization reweighting, using steady-state EEG in humans.
+We find increases in suppression during the first 2-5 seconds of stimulation, with similar dynamics for monocular and dichoptic presentation.
+The effects are present in primary visual cortex, and were not mediated by autistic traits.
+These findings demonstrate that reweighting builds up rapidly after stimulus onset, consistent with a process that adjusts the sensory response to the local environment.
+Normalization reweighting also has potential as a biomarker of neural function both in humans and in animal models of disease.
+
+# Introduction
+
+Suppressive interactions between neurons are ubiquitous in the nervous system, with normalization considered a canonical neuronal computation [@Carandini2011].
+Yet for decades the strength of suppression was treated as fixed, due to the observation that adapting to one stimulus does not decrease its suppressive potency [@Foley1997; @Freeman2002].
+This orthodoxy has been challenged by a series of innovative studies showing that normalization can be 'reweighted' by recent history [@Westrick2016; @Aschner2018; @Yiltiz2020].
+When pairs of stimuli are repeatedly presented together, their neural representations come to suppress each other more strongly.
+Far from being fixed, normalization is therefore a dynamic process that is continuously updated by the sensory environment.
+Our objectives were to measure the timecourse of these changes non-invasively in the human brain, compare them across distinct suppressive pathways, and determine whether they differ as a function of autistic traits.
+
+Plastic changes within the visual system occur over multiple timescales [see @Webster2015 for a recent review].
+Cortical forms of adaptation to cues such as stimulus contrast [@Blakemore1969], orientation [@Gibson1937] and motion [@Mather2008] can be observed within a few seconds, but also build up over durations on the order of minutes [@Greenlee1991].
+Other types of adaptation have been identified where changes occur over longer time periods, such as several hours [@Kwon2009] or days [@Haak2014].
+Previous normalization reweighting studies involved adapting sequences of around 40 -- 60s [@Aschner2018; @Yiltiz2020], but in principle reweighting might occur faster than this, consistent with other types of contrast adaptation.
+
+Multiple suppressive pathways have been identified in the visual system, including between stimuli differing in orientation [@Heeger1992; @Foley1994], eye-of-origin [@Legge1979; @Sengpiel1994] and spatial position [@Petrov2005; @Cannon1991].
+At present there is evidence of normalization reweighting between stimuli with orthogonal orientations [@Aschner2018], and adjacent spatial positions [@Yiltiz2020].
+We anticipated that interocular suppression should also be subject to reweighting, but that there might be differences in the dynamics across suppressive pathways [e.g.
+@Meese2009; @Sengpiel2005; @Li2005].
+Comparing monocular and dichoptic suppression permits any contribution of early pre-cortical factors to be isolated.
+This is because interocular suppression impacts in primary visual cortex, and bypasses any retinal and subcortical stages of processing that contribute to monocular suppression [@Li2005].
+
+Atypical sensory experience, including hypersensitivity to loud sounds, bright lights and strong odours or flavours, is widely reported by individuals on the autism spectrum [@MacLennan2022; @Simmons2009], but the causal mechanisms remain unclear.
+Fundamental measures of sensitivity including visual acuity [@Tavassoli2011], contrast sensitivity [@Koh2010], and audiometric performance [@Rosenhall1999] are not consistently different from neurotypical controls.
+Theoretical accounts of sensory differences in autism have proposed that the balance of inhibition and excitation may be disrupted [@Rubenstein2003; @Rosenberg2015], yet the evidence is currently inconclusive [e.g.
+@Schallmo2020; @VandeCruys2018; @Sandhu2020].
+Our recent work identified an autism-related difference using steady-state EEG [@Vilidaite2018], in which nonlinear (second harmonic) responses were weaker, implicating atypical suppression in autism.
+
+Here we perform a time-course analysis of a previously published data set, and report two novel pre-registered experiments using EEG and MEG.
+Our data show that suppression increases substantially during the first 2-5 seconds following stimulus onset, for both monocular and dichoptic masks.
+Source localisation of MEG data indicate that the reweighting is present as early as primary visual cortex (V1).
+We also hypothesised that normalization reweighting might differ as a function of autistic traits, but did not find convincing support for this hypothesis.
+
+# Materials and Methods
+
+## Participants
+
+Experiment 1 was completed by 100 adult participants (32 male, 68 female; mean age 21.9) in early 2015, and first reported by @Vilidaite2018.
+Here we reanalysed the dataset, and report the results of masking conditions not previously published.
+Experiment 2 was completed by 100 adult participants (23 male, 74 female, 3 other/not stated; mean age 22.1) in early 2022.
+Experiment 3 was completed by 10 adults (2 male, 8 female) with a clinical diagnosis of autism, and 10 control participants who were closely matched for age (means of `r t_age$estimate[1]` and `r t_age$estimate[2]`, *t* = `r format(round(abs(t_age$statistic),digits=2))`, *df* = `r t_age$parameter`, *p* = `r format(round(abs(t_age$p.value),digits=2))`) and exactly matched for gender.
+Procedures in Experiments 1 and 2 were approved by the ethics committee of the Department of Psychology at the University of York.
+Procedures for Experiment 3 were approved by the ethics committee of the York Neuroimaging Centre.
+All participants provided written informed consent.
+
+## Apparatus and stimuli
+
+In Experiments 1 and 2, stimuli were presented using a ViewPixx 3D LCD display device (VPixx Technologies, Canada) with a resolution of 1920 $\times$ 1080 pixels and a refresh rate of 120Hz.
+The display was gamma corrected using a Minolta LS110 photometer.
+In Experiment 2, participants wore active stereo shutter glasses (NVidia 3D Vision 2) that were synchronised with the display using an infra-red signal.
+EEG data were collected using a 64-channel Waveguard cap, and were amplified and digitised at 1000Hz using an ANT Neuroscan system.
+Electrode impedance was maintained below 5k$\Omega$, and referenced to a whole-head average.
+
+In Experiment 3, stimuli were presented using a ProPixx DLP projector (VPixx Technologies) running at 120Hz.
+Stereo presentation was enabled using a circular polariser that was synchronised with the projector refresh, and participants wore passive polarised glasses during the experiment.
+DLP projectors are perfectly linear, so gamma correction was not required.
+Data were acquired using a refurbished 248-channel 4D Neuroimaging Magnes 3600 MEG scanner, recording at 1001Hz.
+Participant head shape was digitised using a Polhemus Fastrak device, and head position was recorded at the start and end of each block by passing current through 5 position coils placed at fiducial points on the head.
+We also obtained structural MRI scans using a 3 Tesla Siemens Magnetom Prisma scanner to aid in source localisation.
+Two participants were not available for MRI scans, so we used the MNI ICBM152 template brain [@Fonov2011] for these individuals.
+
+Stimuli were patches of sine wave grating with a diameter of 2 degrees, flickering sinusoidally (on/off flicker) at either 5Hz or 7Hz.
+In Experiment 1 the gratings had a spatial frequency of 0.5c/deg, and in Experiments 2 & 3 this was increased to 2c/deg.
+A symmetrical array of 36 individual patches tiled the display.
+In Experiment 1 the patch orientation was randomly selected on each trial, and all patches had the same orientation.
+In Experiments 2 & 3 each patch had a random orientation, which was intended to prevent any sequential effects between trials with similar orientations.
+The central patch was omitted and replaced by a fixation marker constructed from randomly overlaid squares.
+During each experiment, the fixation marker could be resampled on each trial with a probability of 0.5.
+Participants were instructed to monitor the fixation marker and count the number of times it changed throughout the experiment.
+This was intended to maintain attention towards the display and keep participants occupied.
+
+Participants also completed either the short AQ [@Hoekstra2011] in Experiment 1, or the full AQ [@Baron-Cohen2001] in Experiments 2 and 3.
+For comparison across experiments, we rescaled the short AQ to the same range as the full AQ (0-50).
+In Experiments 2 and 3, the sensory perception quotient (SPQ) questionnaire [@Tavassoli2014] was also completed.
+
+## Experimental design and statistical analysis
+
+In Experiment 1, target stimuli flickering at 7Hz were presented at a range of contrasts (1 - 64%).
+In half of the conditions a superimposed orthogonal mask of 32% contrast was presented simultaneously, flickering at 5Hz.
+Stimuli were displayed for trials of 11 seconds, with a 3 second inter-trial interval.
+The experiment consisted of 4 blocks of trials, each lasting around 10 minutes, and resulting in 8 repetitions of each condition.
+Participants viewed the display from 57cm, were comfortably seated in an upright position, and were able to rest between blocks.
+Low latency 8-bit digital triggers transmitted the trial onset and condition information directly to the EEG amplifier.
+
+The procedure for Experiment 2 was very similar, except that participants also wore stereo shutter glasses during the experiment.
+There were four conditions: (i) monocular presentation of a 5Hz stimulus of 48% contrast, (ii) monocular presentation of a 7Hz stimulus of 48% contrast, (iii) monocular presentation of both stimuli superimposed at right angles, and (iv) dichoptic presentation of both stimuli at right angles (i.e.
+one stimulus to the left eye, one to the right eye).
+Eye of presentation was pseudo-randomised to ensure equal numbers of left-eye and right-eye presentations.
+The trial duration was 6 seconds, with a 3 second inter-trial interval.
+Participants completed 3 blocks, each lasting around 10 minutes, resulting in a total of 48 repetitions of each condition.
+Experiment 3 was identical, except that the projector screen was viewed from a distance of 85cm.
+
+EEG data from Experiments 1 and 2 were first imported into Matlab using components of the EEGlab toolbox [@Delorme2004], and converted into a compressed ASCII format.
+Primary data analysis was then conducted using a bespoke _R_ script.
+In brief, we epoched each trial and extracted the average timecourse across four occipital electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}), and then calculated the Fourier transform of this average waveform.
+We excluded trials for which the Mahalanobis distance of the complex Fourier components exceeded 3 [for details see @Baker2021].
+This resulted in `r round(Pilotpercentexcluded,digits=2)`% of trials being excluded for Experiment 1, and `r round(EEGpercentexcluded,digits=2)`% of trials for Experiment 2.
+Next we averaged the waveforms across all remaining trials, and calculated the Fourier transform in a 1-second sliding window to generate timecourses for each participant.
+We divided the timecourse for the target-only condition by the timecourse for the target + mask condition to produce a suppression ratio.
+These were then converted to logarithmic (dB) units for averaging, calculation of standard errors, and statistical comparisons.
+For display purposes we smoothed the timecourses using a cubic spline function, however all statistical comparisons used the unsmoothed data.
+
+For Experiment 3, we performed source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm, implemented in Brainstorm [@Tadel2011].
+Structural MRI scans were processed using Freesurfer [@Dale1999] to generate a 3D mesh of the head and brain, and we calculated source weights for each block with reference to a 5-minute empty room recording, usually recorded on the day of the experiment.
+The matrix of source weights for each block was used in a custom Matlab script to extract signals from V1, identified using the probabilistic maps of @Wang2015.
+These signals were then imported into R for the main analysis, which was consistent with the EEG analysis described above.
+The outlier rejection procedure excluded `r round(MEGpercentexcluded,digits=2)`% of trials for Experiment 3.
+
+To make comparisons between groups of participants across time, we used a non-parametric cluster correction technique [@Maris2007] based on t-tests.
+Clusters were identified as temporally adjacent observations that were all statistically significant, and a summed t-value was calculated for each cluster.
+A null distribution was then generated by randomising group membership and recalculating the summed t-value for the largest cluster, and repeating this procedure `r nbootstraps` times.
+Clusters were considered significant if they fell outside of the 95% confidence limits of the null distribution.
+We adapted this approach to test for significantly increasing suppression by conducting one-way t-tests between time points separated by `r timeoffset`ms, and repeating the cluster correction procedure as described above.
+
+## Preregistration, data and code accessibility
+
+Following a preliminary analysis of the data from Experiment 1, we preregistered our hypotheses and analysis plan for Experiments 2 and 3 on the Open Science Framework website.
+The preregistration document, along with raw and processed data, and analysis scripts, are publicly available at the project repository: https://osf.io/ab3yv/
+
+# Results
+
+We began by reanalysing data from a steady-state visually evoked potential (SSVEP) experiment reported by @Vilidaite2018.
+Participants viewed arrays of flickering gratings of varying contrasts.
+In some conditions a single grating orientation was present flickering at 7Hz, whereas in other conditions a high contrast 'mask' was added at right angles to the target gratings, and flickering at 5Hz.
+The left panel of Figure \@ref(fig:Pilotdata)a shows contrast response functions with and without the mask - the presence of the mask reduces the 7Hz response to the target (blue squares are below the black circles; significant main effect of mask contrast, F(1,99) = `r round(maskinganova1$ANOVA$F[2],digits=2)`, \emph{p} < 0.001).
+Similarly, the right panel of Figure \@ref(fig:Pilotdata)a shows that the 5Hz response to the mask was itself suppressed by the presence of high contrast targets (main effect of target contrast on the mask response, F(`r round(maskinganova2$ANOVA$DFn*gg,digits=2)`,`r round(maskinganova2$ANOVA$DFd*gg,digits=2)`) = `r round(maskinganova2$ANOVA$F,digits=2)`, \emph{p} < 0.001; note that the data from the masking conditions were not reported by @Vilidaite2018).
+At both frequencies, responses were localised to the occipital pole (see insets).
+
+```{r Pilotdata, fig.cap="Summary of pilot analysis of data from Vilidiate et al.
+(2018).
+Panel (a) shows contrast response functions at the target frequency (7Hz, left) and the mask frequency (5Hz, right).
+Insets show the distribution of activity across the scalp, with points marking the electrodes over which signals were averaged (Oz, POz, O1 and O2).
+Panel (b) shows Fourier spectra for the single component stimuli and their combination (plaid).
+Note the strong second harmonic components at 14Hz and 10Hz.
+Panel (c) shows timecourses of frequency-locked responses to a single stimulus (black) and the plaid stimulus (blue), compared to baseline (grey).
+Panel (d) shows the timecourse of suppression at each frequency (7Hz, 5Hz, 14Hz, 10Hz) and their average (black curve).
+Points around y = 1.8 indicate a significantly increasing ratio.
+Error bars in panel (a) and shaded regions in panels (c,d) indicate ±1SE across N=100 participants, and grey rectangles indicate the timing of stimulus presentation.
+The larger symbols in panel (a) indicate the conditions used for subsequent analyses.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('Figures/VilidaiteData.pdf')
+
+```
+
+We then performed a timecourse analysis, in which we analysed each 11-second trial using a sliding 1-second time window.
+The top panel of Figure \@ref(fig:Pilotdata)c shows the response at the target frequency (7Hz) to a single stimulus of 32% contrast (black), and the response at 7Hz when the 32% contrast mask is added (blue).
+For comparison, a baseline timecourse is also shown (grey), which was the response at 7Hz when a 5Hz stimulus was shown (therefore controlling for attention, blinking etc.).
+Analogous responses are shown at three other frequencies - the mask frequency (5Hz), and the second harmonics of both target and mask frequencies (14Hz, 10Hz), at which strong responses were also found (see spectra in Figure \@ref(fig:Pilotdata)b).
+The reduction in signal strength when the mask component is added illustrates the masking effect.
+
+Taking the ratio of the two timecourses to calculate a masking index reveals that at 7Hz masking increases steeply during the first two seconds of stimulus presentation, and then plateaus for several seconds (blue trace in Figure \@ref(fig:Pilotdata)d).
+A similar pattern is observed at 5Hz (red trace in Figure \@ref(fig:Pilotdata)d), as well as at the second harmonics, with some variability in the timecourse across frequencies; for example, at 5Hz suppression peaks at around 4 seconds.
+The black trace shows the average masking ratio across all four frequencies, which rises steeply for just over two seconds and then stays approximately constant until stimulus offset.
+We conducted cluster-corrected t-tests between ratios separated by `r timeoffset`ms, testing for an increase in suppression ratio across time (i.e.
+a one-sided test).
+Points at y = 1.8 in Figure \@ref(fig:Pilotdata)d indicate time points where the ratio is significantly increasing, and occur mostly during the first 2 seconds of stimulus presentation.
+
+Our initial reanalysis was promising, however the data were noisy despite the large sample size (of N=100), because each participant contributed only 8 trials (88 seconds) to each condition.
+We therefore preregistered two new experiments (see https://osf.io/4qudc) to investigate these effects in greater detail.
+These had a similar overall design to the @Vilidaite2018 study, with some small changes intended to optimise the study (see Methods).
+The key differences were that we used shorter trials (because there were few changes in the latter part of the trials shown in Figure \@ref(fig:Pilotdata)d), and also focussed all trials into a smaller number of conditions, such that each participant contributed 48 repetitions (288 seconds of data) to each of 4 conditions.
+
+Figure \@ref(fig:EEGdata) summarises the results of our EEG experiment testing a further 100 adult participants.
+Averaged EEG waveforms showed a strong oscillatory component at each of the two stimulus flicker frequencies (Figure \@ref(fig:EEGdata)a), which slightly lagged the driving signal.
+Signals were well-isolated in the Fourier domain (Figure \@ref(fig:EEGdata)b), and localised to occipital electrodes.
+Responses at 7Hz were weaker in the two masking conditions, showing significant changes in response amplitude for both the monocular (\emph{t} = `r round(t7a$statistic,digits=2)`, \emph{df} = `r t7a$parameter`, \emph{p} < 0.001) and dichoptic (\emph{t} = `r round(t7b$statistic,digits=2)`, \emph{df} = `r t7b$parameter`, \emph{p} < 0.001) masks.
+Dichoptic masking was significantly stronger than monocular masking (\emph{t} = `r round(t7c$statistic,digits=2)`, \emph{df} = `r t7c$parameter`, \emph{p} < 0.001), and a similar pattern was evident at 5Hz.
+
+```{r EEGdata, fig.cap="Summary of EEG results for N=100 adult participants.
+Panel (a) shows scalp topographies and averaged waveforms for 5Hz (top) and 7Hz (bottom) stimuli.
+The black sine wave trace in each panel illustrates the driving contrast modulation, and black points on the scalp topographies indicate electrodes Oz, O1, O2 and POz.
+Panel (b) shows the Fourier amplitude spectrum for each condition, with clear peaks at 5Hz and 7Hz.
+Panels (c,d) show timecourses at each frequency for the baseline condition (black), and the monocular (blue) and dichoptic (red) masking conditions.
+Panels (e,f) show suppression ratios as a function of time for each mask type, with points around y = 0.8 indicating a significantly increasing ratio.
+Shaded regions in panels (c-f) span ±1SE across participants, and light grey rectangles indicate the period of stimulus presentation.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('Figures/EEGdata.pdf')
+
+```
+
+The timecourse at both flicker frequencies showed an initial onset transient, and was then relatively stable for the 6 seconds of stimulus presentation (Figure \@ref(fig:EEGdata)c,d).
+The ratio of target only to target + mask conditions increased over time (Figure \@ref(fig:EEGdata)e,f) for both mask types.
+At 5Hz the increase in masking continued over the first 5 seconds of stimulus presentation (Figure \@ref(fig:EEGdata)e; points at y = 0.8 indicate significantly increasing suppression), whereas at 7Hz the increase occurred primarily during the first second after onset (Figure \@ref(fig:EEGdata)f).
+These differences across frequency are consistent with the pilot data (see Figure \@ref(fig:Pilotdata)d).
+Both monocular and dichoptic masks produced similar timecourses of suppression.
+Overall, this second study confirmed that normalization increases during the first few seconds of a steady-state trial, and extends this finding to dichoptic mask arrangements.
+
+```{r MEGdata, fig.cap="Summary of MEG results for N=20 adults.
+Panel (a) shows average SSVEP response in source space, thresholded at SNR=2 (blue, left), and locations of the V1 ROI on the medial surface of both hemispheres (right, red).
+Panel (b) shows the Fourier spectra for the four experimental conditions, from the most responsive vertex in V1.
+Panels (c,d) show timecourses at 5Hz and 7Hz, and panels (e,f) show suppression ratios for the monocular and dichoptic conditions at each frequency, with points around y = 0.8 indicating a significantly increasing ratio.
+Shaded regions in panels (c-f) indicate ±1SE across participants, and light grey rectangles indicate the period of stimulus presentation.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('Figures/MEGdata.pdf')
+
+```
+
+Next we repeated the experiment on 20 participants using a 248-channel whole-head cryogenic MEG system.
+Half of the participants had a diagnosis of autism, and the remainder were age- and gender-matched controls.
+Source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm [@VanVeen1997] showed strong localisation of steady-state signals at the occipital pole (see Figure \@ref(fig:MEGdata)a), and in the Fourier domain (Figure \@ref(fig:MEGdata)b).
+Responses from the most responsive V1 vertex showed a similar timecourse to those of the EEG experiments at both frequencies (Figure \@ref(fig:MEGdata)c,d), and showed increasing suppression during the first few seconds of stimulus presentation (Figure \@ref(fig:MEGdata)e,f).
+The normalization reweighting effect was again clearest at 5Hz, especially for the dichoptic condition (red curve in Figure \@ref(fig:MEGdata)e).
+This confirms that the reweighting effects can occur as early as primary visual cortex, consistent with findings from neurophysiology [@Aschner2018].
+However the data are more variable than for our EEG experiments, and had fewer significant clusters, owing to the smaller sample size for this dataset.
+
 ```{r AQanalysis, fig.cap="Analysis of the effect of autistic traits on normalization reweighting.
@@
 We also compared suppression ratios calculated on Fourier components for the full trial, and found no significant effects of autism on suppression strength.
+For Experiment 1 we assessed the first and second harmonics separately, but also found no AQ-related differences.
 We therefore conclude that autism/AQ score is not associated with normalization reweighting, or the strength of suppression more generally.
@@
 
-Participants in Experiments 2 & 3 also completed the sensory perception quotient (SPQ) scale.
-SPQ scores showed significant negative correlation with AQ for both data sets (EEG data, *r* = `r round(corEEG$estimate,digits=2)`, *p* < `r ceiling(1000*corEEG$p.value)/1000`; MEG data, *r* = `r round(corMEG$estimate,digits=2)`, *p* = `r round(corMEG$p.value,digits=3)`) with effect sizes comparable to those reported previously [@Tavassoli2014].
+Autism is composed of a set of heterogenous symptoms and characteristics, and normalization reweighting may have a more specific relationship to some aspects of autism, rather than autism per se.
+For this reason, we also examined relationships with the sensory perception quotient (SPQ) to examine whether sensory experiences specifically were related to normalization reweighting.
+SPQ scores showed significant negative correlation with AQ for the data sets from Experiments 2 and 3 (EEG data, *r* = `r round(corEEG$estimate,digits=2)`, *p* < `r ceiling(1000*corEEG$p.value)/1000`; MEG data, *r* = `r round(corMEG$estimate,digits=2)`, *p* = `r round(corMEG$p.value,digits=3)`) with effect sizes comparable to those reported previously [@Tavassoli2014].
 We also conducted an exploratory analysis of the EEG data from Experiment 2, splitting participants by SPQ instead of AQ.
@@
 The idea that the dynamic balance of inhibition and excitation might be different in autism [@Rubenstein2003; @Rosenberg2015] has compelling face validity.
-For example individuals with autism often report difficulties with changes in their sensory environment, which might be due to gain control processes failing to adapt appropriately.
+For example, individuals with autism often report difficulties with changes in their sensory environment, which might be due to gain control processes failing to adapt appropriately.
 Indeed, there is experimental evidence of reduced adaptation across various domains [@Pellicano2007; @Turi2015], which is predicted by some autism models [@Pellicano2012].
@@
 
-# Methods
-
-## Participants
-
-Experiment 1 was completed by 100 adult participants (32 male, 68 female; mean age 21.9) in early 2015, and first reported by @Vilidaite2018.
-Here we reanalysed the dataset, and report the results of masking conditions not previously published.
-Experiment 2 was completed by 100 adult participants (23 male, 74 female, 3 other/not stated; mean age 22.1) in early 2022.
-Experiment 3 was completed by 10 adults (2 male, 8 female) with a clinical diagnosis of autism, and 10 control participants who were closely matched for age (means of `r t_age$estimate[1]` and `r t_age$estimate[2]`, *t* = `r format(round(abs(t_age$statistic),digits=2))`, *df* = `r t_age$parameter`, *p* = `r format(round(abs(t_age$p.value),digits=2))`) and exactly matched for gender.
-Procedures in Experiments 1 and 2 were approved by the ethics committee of the Department of Psychology at the University of York.
-Procedures for Experiment 3 were approved by the ethics committee of the York Neuroimaging Centre.
-All participants provided written informed consent.
-
-## Apparatus and stimuli
-
-In Experiments 1 and 2, stimuli were presented using a ViewPixx 3D LCD display device (VPixx Technologies, Canada) with a resolution of 1920 $\times$ 1080 pixels and a refresh rate of 120Hz.
-The display was gamma corrected using a Minolta LS110 photometer.
-In Experiment 2, participants wore active stereo shutter glasses (NVidia 3D Vision 2) that were synchronised with the display using an infra-red signal.
-EEG data were collected using a 64-channel Waveguard cap, and were amplified and digitised at 1000Hz using an ANT Neuroscan system.
-Electrode impedance was maintained below 5k$\Omega$, and referenced to a whole-head average.
-
-In Experiment 3, stimuli were presented using a ProPixx DLP projector (VPixx Technologies) running at 120Hz.
-Stereo presentation was enabled using a circular polariser that was synchronised with the projector refresh, and participants wore passive polarised glasses during the experiment.
-DLP projectors are perfectly linear, so gamma correction was not required.
-Data were acquired using a refurbished 248-channel 4D Neuroimaging Magnes 3600 MEG scanner, recording at 1001Hz.
-Participant head shape was digitised using a Polhemus Fastrak device, and head position was recorded at the start and end of each block by passing current through 5 position coils placed at fiducial points on the head.
-We also obtained structural MRI scans using a 3 Tesla Siemens Magnetom Prisma scanner to aid in source localisation.
-Two participants were not available for MRI scans, so we used the MNI ICBM152 template brain [@Fonov2011] for these individuals.
-
-Stimuli were patches of sine wave grating with a diameter of 2 degrees, flickering sinusoidally (on/off flicker) at either 5Hz or 7Hz.
-In Experiment 1 the gratings had a spatial frequency of 0.5c/deg, and in Experiments 2 & 3 this was increased to 2c/deg.
-A symmetrical array of 36 individual patches tiled the display.
-In Experiment 1 the patch orientation was randomly selected on each trial, and all patches had the same orientation.
-In Experiments 2 & 3 each patch had a random orientation, which was intended to prevent any sequential effects between trials with similar orientations.
-The central patch was omitted and replaced by a fixation marker constructed from randomly overlaid squares.
-During each experiment, the fixation marker could be resampled on each trial with a probability of 0.5.
-Participants were instructed to monitor the fixation marker and count the number of times it changed throughout the experiment.
-This was intended to maintain attention towards the display and keep participants occupied.
-
-Participants also completed either the short AQ [@Hoekstra2011] in Experiment 1, or the full AQ [@Baron-Cohen2001] in Experiments 2 and 3.
-For comparison across experiments, we rescaled the short AQ to the same range as the full AQ (0-50).
-In Experiments 2 and 3, the sensory perception quotient (SPQ) questionnaire [@Tavassoli2014] was also completed.
-
-## Procedures
-
-In Experiment 1, target stimuli flickering at 7Hz were presented at a range of contrasts (1 - 64%).
-In half of the conditions a superimposed orthogonal mask of 32% contrast was presented simultaneously, flickering at 5Hz.
-Stimuli were displayed for trials of 11 seconds, with a 3 second inter-trial interval.
-The experiment consisted of 4 blocks of trials, each lasting around 10 minutes, and resulting in 8 repetitions of each condition.
-Participants viewed the display from 57cm, were comfortably seated in an upright position, and were able to rest between blocks.
-Low latency 8-bit digital triggers transmitted the trial onset and condition information directly to the EEG amplifier.
-
-The procedure for Experiment 2 was very similar, except that participants also wore stereo shutter glasses during the experiment.
-There were four conditions: (i) monocular presentation of a 5Hz stimulus of 48% contrast, (ii) monocular presentation of a 7Hz stimulus of 48% contrast, (iii) monocular presentation of both stimuli superimposed at right angles, and (iv) dichoptic presentation of both stimuli at right angles (i.e.
-one stimulus to the left eye, one to the right eye).
-Eye of presentation was pseudo-randomised to ensure equal numbers of left-eye and right-eye presentations.
-The trial duration was 6 seconds, with a 3 second inter-trial interval.
-Participants completed 3 blocks, each lasting around 10 minutes, resulting in a total of 48 repetitions of each condition.
-Experiment 3 was identical, except that the projector screen was viewed from a distance of 85cm.
-
-## Data analysis
-
-EEG data from Experiments 1 and 2 were first imported into Matlab using components of the EEGlab toolbox [@Delorme2004], and converted into a compressed ASCII format.
-Primary data analysis was then conducted using a bespoke _R_ script.
-In brief, we epoched each trial and extracted the average timecourse across four occipital electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}), and then calculated the Fourier transform of this average waveform.
-We excluded trials for which the Mahalanobis distance of the complex Fourier components exceeded 3 [for details see @Baker2021].
-This resulted in `r round(Pilotpercentexcluded,digits=2)`% of trials being excluded for Experiment 1, and `r round(EEGpercentexcluded,digits=2)`% of trials for Experiment 2.
-Next we averaged the waveforms across all remaining trials, and calculated the Fourier transform in a 1-second sliding window to generate timecourses for each participant.
-We divided the timecourse for the target-only condition by the timecourse for the target + mask condition to produce a suppression ratio.
-These were then converted to logarithmic (dB) units for averaging, calculation of standard errors, and statistical comparisons.
-For display purposes we smoothed the timecourses using a cubic spline function, however all statistical comparisons used the unsmoothed data.
-
-For Experiment 3, we performed source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm, implemented in Brainstorm [@Tadel2011].
-Structural MRI scans were processed using Freesurfer [@Dale1999] to generate a 3D mesh of the head and brain, and we calculated source weights for each block with reference to a 5-minute empty room recording, usually recorded on the day of the experiment.
-The matrix of source weights for each block was used in a custom Matlab script to extract signals from V1, identified using the probabilistic maps of @Wang2015.
-These signals were then imported into R for the main analysis, which was consistent with the EEG analysis described above.
-The outlier rejection procedure excluded `r round(MEGpercentexcluded,digits=2)`% of trials for Experiment 3.
-
-To make comparisons between groups of participants across time, we used a non-parametric cluster correction technique [@Maris2007] based on t-tests.
-Clusters were identified as temporally adjacent observations that were all statistically significant, and a summed t-value was calculated for each cluster.
-A null distribution was then generated by randomising group membership and recalculating the summed t-value for the largest cluster, and repeating this procedure `r nbootstraps` times.
-Clusters were considered significant if they fell outside of the 95% confidence limits of the null distribution.
-We adapted this approach to test for significantly increasing suppression by conducting one-way t-tests between time points separated by `r timeoffset`ms, and repeating the cluster correction procedure as described above.
-
-## Preregistration, data and code availability
-
-Following a preliminary analysis of the data from Experiment 1, we preregistered our hypotheses and analysis plan for Experiments 2 and 3 on the Open Science Framework website.
-The preregistration document, along with raw and processed data, and analysis scripts, are publicly available at the project repository: https://osf.io/ab3yv/
-
 # Acknowledgements

### 2023-02-10 manuscript.tex
Bug fixes
Reformatted for journal submmission

@@
  {}
+\usepackage{lineno}
+\linenumbers
 \usepackage{calc}
@@
 Emily L. Williams, Hannah M. Hobson \& Alex R. Wade}
-\date{2022-09-30}
+\date{Department of Psychology, University of York, UK}
 
@@
 But recent work has challenged this assumption by showing that suppression can be \emph{reweighted} based on recent history; when pairs of stimuli are repeatedly presented together, suppression between them strengthens.
-Here we investigate the temporal dynamics of this process using a steady-state VEP paradigm that provides a time-resolved, direct index of suppression between pairs of stimuli flickering at different frequencies (5 and 7Hz).
+Here we investigate the temporal dynamics of this process using a steady-state visual evoked potential (SSVEP) paradigm that provides a time-resolved, direct index of suppression between pairs of stimuli flickering at different frequencies (5 and 7Hz).
 Our initial analysis of an existing EEG dataset (N=100) indicated that suppression increases substantially during the first 2-5 seconds of stimulus presentation (with some variation across stimulation frequency).
@@
 
+\hypertarget{significance-statement}{%
+\section{Significance statement}\label{significance-statement}}
+
+We investigated the timecourse of a novel form of neural plasticity, normalization reweighting, using steady-state EEG in humans.
+We find increases in suppression during the first 2-5 seconds of stimulation, with similar dynamics for monocular and dichoptic presentation.
+The effects are present in primary visual cortex, and were not mediated by autistic traits.
+These findings demonstrate that reweighting builds up rapidly after stimulus onset, consistent with a process that adjusts the sensory response to the local environment.
+Normalization reweighting also has potential as a biomarker of neural function both in humans and in animal models of disease.
+
 \hypertarget{introduction}{%
@@
 
-Suppressive interactions between neurons are ubiquitous in the nervous system, and normalization (or gain control) processes are considered a canonical neuronal computation (Carandini and Heeger, 2011).
-Yet for decades the strength of suppression was treated as fixed, largely due to the observation that adapting to one stimulus does not decrease its suppressive potency (Foley and Chen, 1997; Freeman et al., 2002).
-This orthodoxy was recently challenged by a series of innovative studies showing that normalization can be `reweighted' by recent history (Aschner et al., 2018; Westrick et al., 2016; Yiltiz et al., 2020).
-Specifically, when pairs of stimuli are repeatedly presented together, their neural representations come to suppress each other more strongly.
-This suggests that, far from being fixed, normalization is a dynamic process that is continuously updated by the sensory environment.
-Here, our objectives were to determine if the timecourse of these changes can be measured non-invasively from the human brain, assess if they occur similarly in distinct suppressive pathways, and determine whether they differ across the population as a function of autistic traits.
+Suppressive interactions between neurons are ubiquitous in the nervous system, with normalization considered a canonical neuronal computation (Carandini and Heeger, 2011).
+Yet for decades the strength of suppression was treated as fixed, due to the observation that adapting to one stimulus does not decrease its suppressive potency (Foley and Chen, 1997; Freeman et al., 2002).
+This orthodoxy has been challenged by a series of innovative studies showing that normalization can be `reweighted' by recent history (Aschner et al., 2018; Westrick et al., 2016; Yiltiz et al., 2020).
+When pairs of stimuli are repeatedly presented together, their neural representations come to suppress each other more strongly.
+Far from being fixed, normalization is therefore a dynamic process that is continuously updated by the sensory environment.
+Our objectives were to measure the timecourse of these changes non-invasively in the human brain, compare them across distinct suppressive pathways, and determine whether they differ as a function of autistic traits.
 
 Plastic changes within the visual system occur over multiple timescales (see Webster, 2015 for a recent review).
-In the retina, adaptation to complete darkness takes around 30 minutes (Lamb and Pugh, 2006), and has established physiological substrates (i.e.~the regeneration rate of chemicals in different photoreceptor classes).
-Cortical forms of adaptation to cues such as stimulus contrast (Blakemore and Campbell, 1969), orientation (Gibson and Radner, 1937) and motion (Mather et al., 2008) can be observed within a few seconds, but also build up over durations on the order of several minutes (Greenlee et al., 1991).
-A recent form of binocular plasticity (Lunghi et al., 2011), in which one eye is patched and subsequently contributes more to binocular vision, requires more than an hour.
-Other types of adaptation have been identified with changes occurring over longer time periods, such as over several hours (Kwon et al., 2009) or days (Haak et al., 2014).
-Finally adaptation to specific combinations of orientation and colour (the McCollough, 1965 effect) can persist for several weeks (Jones and Holding, 1975), even with a brief induction period.
-Previous work on normalization reweighting has involved adapting sequences of around 40 -- 60s (Aschner et al., 2018; Yiltiz et al., 2020), though it is possible that reweighting might occur faster than this, consistent with other types of contrast adaptation.
+Cortical forms of adaptation to cues such as stimulus contrast (Blakemore and Campbell, 1969), orientation (Gibson and Radner, 1937) and motion (Mather et al., 2008) can be observed within a few seconds, but also build up over durations on the order of minutes (Greenlee et al., 1991).
+Other types of adaptation have been identified where changes occur over longer time periods, such as several hours (Kwon et al., 2009) or days (Haak et al., 2014).
+Previous normalization reweighting studies involved adapting sequences of around 40 -- 60s (Aschner et al., 2018; Yiltiz et al., 2020), but in principle reweighting might occur faster than this, consistent with other types of contrast adaptation.
 
-Normalization itself is not a single process.
 Multiple suppressive pathways have been identified in the visual system, including between stimuli differing in orientation (Foley, 1994; Heeger, 1992), eye-of-origin (Legge, 1979; Sengpiel and Blakemore, 1994) and spatial position (Cannon and Fullenkamp, 1991; Petrov, 2005).
 At present there is evidence of normalization reweighting between stimuli with orthogonal orientations (Aschner et al., 2018), and adjacent spatial positions (Yiltiz et al., 2020).
-We anticipated that interocular suppression should also be subject to reweighting, but that there might be differences in the dynamics across suppressive pathways.
-This is plausible, given that suppression within and between the eyes has different spatiotemporal tuning (Meese and Baker, 2009), and dichoptic masking can be reduced by adapting to the mask (Baker et al., 2007; Li et al., 2005; Sengpiel and Vorobyov, 2005), unlike within-eye masking.
-Dynamic fluctuations in interocular suppression are a key feature of binocular rivalry (Alais et al., 2010; Wilson, 2003), for which autism-related differences have also been reported (Robertson et al., 2013).
-By comparing monocular and dichoptic suppression, we are also able to isolate any contribution of early pre-cortical factors.
-This is because interocular suppression impacts in primary visual cortex, and therefore bypasses earlier retinal and subcortical stages of processing that may contribute to monocular suppression (Li et al., 2005).
+We anticipated that interocular suppression should also be subject to reweighting, but that there might be differences in the dynamics across suppressive pathways (Li et al., 2005; e.g.
+Meese and Baker, 2009; Sengpiel and Vorobyov, 2005).
+Comparing monocular and dichoptic suppression permits any contribution of early pre-cortical factors to be isolated.
+This is because interocular suppression impacts in primary visual cortex, and bypasses any retinal and subcortical stages of processing that contribute to monocular suppression (Li et al., 2005).
 
-Atypical sensory experience is widely reported by individuals on the autism spectrum (MacLennan et al., 2022; Simmons et al., 2009), but the causal mechanisms remain unclear.
-Typical issues include hypersensitivity to intense stimuli such as loud sounds, bright lights and strong odours or flavours.
-Yet fundamental measures of sensitivity such as visual acuity (Tavassoli et al., 2011), contrast sensitivity (Koh et al., 2010), and audiometric performance (Rosenhall et al., 1999) are not consistently different from neurotypical controls.
-Theoretical accounts of sensory differences in autism have long proposed that the balance of inhibition and excitation may be disrupted (Rosenberg et al., 2015; Rubenstein and Merzenich, 2003), and there are isolated results that appear consistent with this.
-For example neural measures of surround suppression are weaker in autism (Schallmo et al., 2020), binocular rivalry is slower (Robertson et al., 2013) and orientation discrimination performance is better (Dickinson et al., 2014).
-Conversely, other studies have failed to find group differences using paradigms that should be equally dependent on inhibition, such as orientation repulsion (Van de Cruys et al., 2018), repetition suppression (Utzerath et al., 2018) and psychophysical measures of surround suppression (Sandhu et al., 2020).
-The evidence for atypical inhibition in autism is therefore currently inconclusive.
+Atypical sensory experience, including hypersensitivity to loud sounds, bright lights and strong odours or flavours, is widely reported by individuals on the autism spectrum (MacLennan et al., 2022; Simmons et al., 2009), but the causal mechanisms remain unclear.
+Fundamental measures of sensitivity including visual acuity (Tavassoli et al., 2011), contrast sensitivity (Koh et al., 2010), and audiometric performance (Rosenhall et al., 1999) are not consistently different from neurotypical controls.
+Theoretical accounts of sensory differences in autism have proposed that the balance of inhibition and excitation may be disrupted (Rosenberg et al., 2015; Rubenstein and Merzenich, 2003), yet the evidence is currently inconclusive (Sandhu et al., 2020; e.g.
+Schallmo et al., 2020; Van de Cruys et al., 2018).
+Our recent work identified an autism-related difference using steady-state EEG (Vilidaite et al., 2018), in which nonlinear (second harmonic) responses were weaker, implicating atypical suppression in autism.
 
-Our recent work has identified a potential autism-related difference in gain control using steady-state EEG methods.
-Vilidaite et al.
-(2018) measured contrast response functions for flickering stimuli in a large group of neurotypical adults, who were grouped according to their autism quotient (AQ, see Baron-Cohen et al., 2001) score.
-The responses were comparable between high and low AQ groups at the flicker frequency of the stimulus.
-However at the second harmonic frequency (twice the flicker frequency), the high AQ group showed weaker responses than the low AQ group.
-This effect was replicated in an independent sample of 12 adults with an autism diagnosis (compared with neurotypical controls).
-Because second harmonic responses are caused by nonlinear interactions in the visual system (they are absent in a linear system), and divisive suppression is a nonlinearity, this potentially implicates differences in suppression in autism.
-Furthermore, there appears to be a developmental trajectory, as autistic children tested as part of the same study (Vilidaite et al., 2018) showed weaker responses at both the first and second harmonic frequencies.
-
-In this paper we perform a time-course analysis of a previously published EEG data set, and report two novel pre-registered experiments using EEG and MEG.
+Here we perform a time-course analysis of a previously published data set, and report two novel pre-registered experiments using EEG and MEG.
 Our data show that suppression increases substantially during the first 2-5 seconds following stimulus onset, for both monocular and dichoptic masks.
 Source localisation of MEG data indicate that the reweighting is present as early as primary visual cortex (V1).
-We also hypothesised that normalization reweighting might differ as a function of autistic traits.
-The relative novelty of the reweighting framework could explain why any differences have not previously been detected, and why the literature on inhibition in autism is relatively inconclusive.
-However we did not find convincing support for this hypothesis.
+We also hypothesised that normalization reweighting might differ as a function of autistic traits, but did not find convincing support for this hypothesis.
+
+\hypertarget{materials-and-methods}{%
+\section{Materials and Methods}\label{materials-and-methods}}
+
+\hypertarget{participants}{%
+\subsection{Participants}\label{participants}}
+
+Experiment 1 was completed by 100 adult participants (32 male, 68 female; mean age 21.9) in early 2015, and first reported by Vilidaite et al.
+(2018).
+Here we reanalysed the dataset, and report the results of masking conditions not previously published.
+Experiment 2 was completed by 100 adult participants (23 male, 74 female, 3 other/not stated; mean age 22.1) in early 2022.
+Experiment 3 was completed by 10 adults (2 male, 8 female) with a clinical diagnosis of autism, and 10 control participants who were closely matched for age (means of 21.8 and 22, \emph{t} = 0.18, \emph{df} = 18, \emph{p} = 0.86) and exactly matched for gender.
+Procedures in Experiments 1 and 2 were approved by the ethics committee of the Department of Psychology at the University of York.
+Procedures for Experiment 3 were approved by the ethics committee of the York Neuroimaging Centre.
+All participants provided written informed consent.
+
+\hypertarget{apparatus-and-stimuli}{%
+\subsection{Apparatus and stimuli}\label{apparatus-and-stimuli}}
+
+In Experiments 1 and 2, stimuli were presented using a ViewPixx 3D LCD display device (VPixx Technologies, Canada) with a resolution of 1920 \(\times\) 1080 pixels and a refresh rate of 120Hz.
+The display was gamma corrected using a Minolta LS110 photometer.
+In Experiment 2, participants wore active stereo shutter glasses (NVidia 3D Vision 2) that were synchronised with the display using an infra-red signal.
+EEG data were collected using a 64-channel Waveguard cap, and were amplified and digitised at 1000Hz using an ANT Neuroscan system.
+Electrode impedance was maintained below 5k\(\Omega\), and referenced to a whole-head average.
+
+In Experiment 3, stimuli were presented using a ProPixx DLP projector (VPixx Technologies) running at 120Hz.
+Stereo presentation was enabled using a circular polariser that was synchronised with the projector refresh, and participants wore passive polarised glasses during the experiment.
+DLP projectors are perfectly linear, so gamma correction was not required.
+Data were acquired using a refurbished 248-channel 4D Neuroimaging Magnes 3600 MEG scanner, recording at 1001Hz.
+Participant head shape was digitised using a Polhemus Fastrak device, and head position was recorded at the start and end of each block by passing current through 5 position coils placed at fiducial points on the head.
+We also obtained structural MRI scans using a 3 Tesla Siemens Magnetom Prisma scanner to aid in source localisation.
+Two participants were not available for MRI scans, so we used the MNI ICBM152 template brain (Fonov et al., 2011) for these individuals.
+
+Stimuli were patches of sine wave grating with a diameter of 2 degrees, flickering sinusoidally (on/off flicker) at either 5Hz or 7Hz.
+In Experiment 1 the gratings had a spatial frequency of 0.5c/deg, and in Experiments 2 \& 3 this was increased to 2c/deg.
+A symmetrical array of 36 individual patches tiled the display.
+In Experiment 1 the patch orientation was randomly selected on each trial, and all patches had the same orientation.
+In Experiments 2 \& 3 each patch had a random orientation, which was intended to prevent any sequential effects between trials with similar orientations.
+The central patch was omitted and replaced by a fixation marker constructed from randomly overlaid squares.
+During each experiment, the fixation marker could be resampled on each trial with a probability of 0.5.
+Participants were instructed to monitor the fixation marker and count the number of times it changed throughout the experiment.
+This was intended to maintain attention towards the display and keep participants occupied.
+
+Participants also completed either the short AQ (Hoekstra et al., 2011) in Experiment 1, or the full AQ (Baron-Cohen et al., 2001) in Experiments 2 and 3.
+For comparison across experiments, we rescaled the short AQ to the same range as the full AQ (0-50).
+In Experiments 2 and 3, the sensory perception quotient (SPQ) questionnaire (Tavassoli et al., 2014) was also completed.
+
+\hypertarget{experimental-design-and-statistical-analysis}{%
+\subsection{Experimental design and statistical analysis}\label{experimental-design-and-statistical-analysis}}
+
+In Experiment 1, target stimuli flickering at 7Hz were presented at a range of contrasts (1 - 64\%).
+In half of the conditions a superimposed orthogonal mask of 32\% contrast was presented simultaneously, flickering at 5Hz.
+Stimuli were displayed for trials of 11 seconds, with a 3 second inter-trial interval.
+The experiment consisted of 4 blocks of trials, each lasting around 10 minutes, and resulting in 8 repetitions of each condition.
+Participants viewed the display from 57cm, were comfortably seated in an upright position, and were able to rest between blocks.
+Low latency 8-bit digital triggers transmitted the trial onset and condition information directly to the EEG amplifier.
+
+The procedure for Experiment 2 was very similar, except that participants also wore stereo shutter glasses during the experiment.
+There were four conditions: (i) monocular presentation of a 5Hz stimulus of 48\% contrast, (ii) monocular presentation of a 7Hz stimulus of 48\% contrast, (iii) monocular presentation of both stimuli superimposed at right angles, and (iv) dichoptic presentation of both stimuli at right angles (i.e.~one stimulus to the left eye, one to the right eye).
+Eye of presentation was pseudo-randomised to ensure equal numbers of left-eye and right-eye presentations.
+The trial duration was 6 seconds, with a 3 second inter-trial interval.
+Participants completed 3 blocks, each lasting around 10 minutes, resulting in a total of 48 repetitions of each condition.
+Experiment 3 was identical, except that the projector screen was viewed from a distance of 85cm.
+
+EEG data from Experiments 1 and 2 were first imported into Matlab using components of the EEGlab toolbox (Delorme and Makeig, 2004), and converted into a compressed ASCII format.
+Primary data analysis was then conducted using a bespoke \emph{R} script.
+In brief, we epoched each trial and extracted the average timecourse across four occipital electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}), and then calculated the Fourier transform of this average waveform.
+We excluded trials for which the Mahalanobis distance of the complex Fourier components exceeded 3 (for details see Baker, 2021).
+This resulted in 0.25\% of trials being excluded for Experiment 1, and 4.51\% of trials for Experiment 2.
+Next we averaged the waveforms across all remaining trials, and calculated the Fourier transform in a 1-second sliding window to generate timecourses for each participant.
+We divided the timecourse for the target-only condition by the timecourse for the target + mask condition to produce a suppression ratio.
+These were then converted to logarithmic (dB) units for averaging, calculation of standard errors, and statistical comparisons.
+For display purposes we smoothed the timecourses using a cubic spline function, however all statistical comparisons used the unsmoothed data.
+
+For Experiment 3, we performed source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm, implemented in Brainstorm (Tadel et al., 2011).
+Structural MRI scans were processed using Freesurfer (Dale et al., 1999) to generate a 3D mesh of the head and brain, and we calculated source weights for each block with reference to a 5-minute empty room recording, usually recorded on the day of the experiment.
+The matrix of source weights for each block was used in a custom Matlab script to extract signals from V1, identified using the probabilistic maps of Wang et al.
+(2015).
+These signals were then imported into R for the main analysis, which was consistent with the EEG analysis described above.
+The outlier rejection procedure excluded 2.47\% of trials for Experiment 3.
+
+To make comparisons between groups of participants across time, we used a non-parametric cluster correction technique (Maris and Oostenveld, 2007) based on t-tests.
+Clusters were identified as temporally adjacent observations that were all statistically significant, and a summed t-value was calculated for each cluster.
+A null distribution was then generated by randomising group membership and recalculating the summed t-value for the largest cluster, and repeating this procedure 1000 times.
+Clusters were considered significant if they fell outside of the 95\% confidence limits of the null distribution.
+We adapted this approach to test for significantly increasing suppression by conducting one-way t-tests between time points separated by 1000ms, and repeating the cluster correction procedure as described above.
+
+\hypertarget{preregistration-data-and-code-accessibility}{%
+\subsection{Preregistration, data and code accessibility}\label{preregistration-data-and-code-accessibility}}
+
+Following a preliminary analysis of the data from Experiment 1, we preregistered our hypotheses and analysis plan for Experiments 2 and 3 on the Open Science Framework website.
+The preregistration document, along with raw and processed data, and analysis scripts, are publicly available at the project repository: \url{https://osf.io/ab3yv/}
 
@@
 Taking the ratio of the two timecourses to calculate a masking index reveals that at 7Hz masking increases steeply during the first two seconds of stimulus presentation, and then plateaus for several seconds (blue trace in Figure \ref{fig:Pilotdata}d).
-A similar pattern is observed at 5Hz (red trace in Figure \ref{fig:Pilotdata}d), as well as at the second harmonics, with some variability in the timecourse across frequencies; for example at 5Hz suppression peaks at around 4 seconds.
+A similar pattern is observed at 5Hz (red trace in Figure \ref{fig:Pilotdata}d), as well as at the second harmonics, with some variability in the timecourse across frequencies; for example, at 5Hz suppression peaks at around 4 seconds.
 The black trace shows the average masking ratio across all four frequencies, which rises steeply for just over two seconds and then stays approximately constant until stimulus offset.
@@
 
-Participants in Experiments 2 \& 3 also completed the sensory perception quotient (SPQ) scale.
-SPQ scores showed significant negative correlation with AQ for both data sets (EEG data, \emph{r} = -0.35, \emph{p} \textless{} 0.001; MEG data, \emph{r} = -0.57, \emph{p} = 0.011) with effect sizes comparable to those reported previously (Tavassoli et al., 2014).
+Autism is composed of a set of heterogenous symptoms and characteristics, and normalization reweighting may have a more specific relationship to some aspects of autism, rather than autism per se.
+For this reason, we also examined relationships with the sensory perception quotient (SPQ) to examine whether sensory experiences specifically were related to normalization reweighting.
+SPQ scores showed significant negative correlation with AQ for the data sets from Experiments 2 and 3 (EEG data, \emph{r} = -0.35, \emph{p} \textless{} 0.001; MEG data, \emph{r} = -0.57, \emph{p} = 0.011) with effect sizes comparable to those reported previously (Tavassoli et al., 2014).
 We also conducted an exploratory analysis of the EEG data from Experiment 2, splitting participants by SPQ instead of AQ.
@@
 The idea that the dynamic balance of inhibition and excitation might be different in autism (Rosenberg et al., 2015; Rubenstein and Merzenich, 2003) has compelling face validity.
-For example individuals with autism often report difficulties with changes in their sensory environment, which might be due to gain control processes failing to adapt appropriately.
+For example, individuals with autism often report difficulties with changes in their sensory environment, which might be due to gain control processes failing to adapt appropriately.
 Indeed, there is experimental evidence of reduced adaptation across various domains (Pellicano et al., 2007; Turi et al., 2015), which is predicted by some autism models (Pellicano and Burr, 2012).
@@
 Our results support an emerging theory that suppression is a dynamic process that allows sensory systems to recalibrate according to their recent history.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-Experiment 1 was completed by 100 adult participants (32 male, 68 female; mean age 21.9) in early 2015, and first reported by Vilidaite et al.
-(2018).
-Here we reanalysed the dataset, and report the results of masking conditions not previously published.
-Experiment 2 was completed by 100 adult participants (23 male, 74 female, 3 other/not stated; mean age 22.1) in early 2022.
-Experiment 3 was completed by 10 adults (2 male, 8 female) with a clinical diagnosis of autism, and 10 control participants who were closely matched for age (means of 21.8 and 22, \emph{t} = 0.18, \emph{df} = 18, \emph{p} = 0.86) and exactly matched for gender.
-Procedures in Experiments 1 and 2 were approved by the ethics committee of the Department of Psychology at the University of York.
-Procedures for Experiment 3 were approved by the ethics committee of the York Neuroimaging Centre.
-All participants provided written informed consent.
-
-\hypertarget{apparatus-and-stimuli}{%
-\subsection{Apparatus and stimuli}\label{apparatus-and-stimuli}}
-
-In Experiments 1 and 2, stimuli were presented using a ViewPixx 3D LCD display device (VPixx Technologies, Canada) with a resolution of 1920 \(\times\) 1080 pixels and a refresh rate of 120Hz.
-The display was gamma corrected using a Minolta LS110 photometer.
-In Experiment 2, participants wore active stereo shutter glasses (NVidia 3D Vision 2) that were synchronised with the display using an infra-red signal.
-EEG data were collected using a 64-channel Waveguard cap, and were amplified and digitised at 1000Hz using an ANT Neuroscan system.
-Electrode impedance was maintained below 5k\(\Omega\), and referenced to a whole-head average.
-
-In Experiment 3, stimuli were presented using a ProPixx DLP projector (VPixx Technologies) running at 120Hz.
-Stereo presentation was enabled using a circular polariser that was synchronised with the projector refresh, and participants wore passive polarised glasses during the experiment.
-DLP projectors are perfectly linear, so gamma correction was not required.
-Data were acquired using a refurbished 248-channel 4D Neuroimaging Magnes 3600 MEG scanner, recording at 1001Hz.
-Participant head shape was digitised using a Polhemus Fastrak device, and head position was recorded at the start and end of each block by passing current through 5 position coils placed at fiducial points on the head.
-We also obtained structural MRI scans using a 3 Tesla Siemens Magnetom Prisma scanner to aid in source localisation.
-Two participants were not available for MRI scans, so we used the MNI ICBM152 template brain (Fonov et al., 2011) for these individuals.
-
-Stimuli were patches of sine wave grating with a diameter of 2 degrees, flickering sinusoidally (on/off flicker) at either 5Hz or 7Hz.
-In Experiment 1 the gratings had a spatial frequency of 0.5c/deg, and in Experiments 2 \& 3 this was increased to 2c/deg.
-A symmetrical array of 36 individual patches tiled the display.
-In Experiment 1 the patch orientation was randomly selected on each trial, and all patches had the same orientation.
-In Experiments 2 \& 3 each patch had a random orientation, which was intended to prevent any sequential effects between trials with similar orientations.
-The central patch was omitted and replaced by a fixation marker constructed from randomly overlaid squares.
-During each experiment, the fixation marker could be resampled on each trial with a probability of 0.5.
-Participants were instructed to monitor the fixation marker and count the number of times it changed throughout the experiment.
-This was intended to maintain attention towards the display and keep participants occupied.
-
-Participants also completed either the short AQ (Hoekstra et al., 2011) in Experiment 1, or the full AQ (Baron-Cohen et al., 2001) in Experiments 2 and 3.
-For comparison across experiments, we rescaled the short AQ to the same range as the full AQ (0-50).
-In Experiments 2 and 3, the sensory perception quotient (SPQ) questionnaire (Tavassoli et al., 2014) was also completed.
-
-\hypertarget{procedures}{%
-\subsection{Procedures}\label{procedures}}
-
-In Experiment 1, target stimuli flickering at 7Hz were presented at a range of contrasts (1 - 64\%).
-In half of the conditions a superimposed orthogonal mask of 32\% contrast was presented simultaneously, flickering at 5Hz.
-Stimuli were displayed for trials of 11 seconds, with a 3 second inter-trial interval.
-The experiment consisted of 4 blocks of trials, each lasting around 10 minutes, and resulting in 8 repetitions of each condition.
-Participants viewed the display from 57cm, were comfortably seated in an upright position, and were able to rest between blocks.
-Low latency 8-bit digital triggers transmitted the trial onset and condition information directly to the EEG amplifier.
-
-The procedure for Experiment 2 was very similar, except that participants also wore stereo shutter glasses during the experiment.
-There were four conditions: (i) monocular presentation of a 5Hz stimulus of 48\% contrast, (ii) monocular presentation of a 7Hz stimulus of 48\% contrast, (iii) monocular presentation of both stimuli superimposed at right angles, and (iv) dichoptic presentation of both stimuli at right angles (i.e.~one stimulus to the left eye, one to the right eye).
-Eye of presentation was pseudo-randomised to ensure equal numbers of left-eye and right-eye presentations.
-The trial duration was 6 seconds, with a 3 second inter-trial interval.
-Participants completed 3 blocks, each lasting around 10 minutes, resulting in a total of 48 repetitions of each condition.
-Experiment 3 was identical, except that the projector screen was viewed from a distance of 85cm.
-
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
-
-EEG data from Experiments 1 and 2 were first imported into Matlab using components of the EEGlab toolbox (Delorme and Makeig, 2004), and converted into a compressed ASCII format.
-Primary data analysis was then conducted using a bespoke \emph{R} script.
-In brief, we epoched each trial and extracted the average timecourse across four occipital electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}), and then calculated the Fourier transform of this average waveform.
-We excluded trials for which the Mahalanobis distance of the complex Fourier components exceeded 3 (for details see Baker, 2021).
-This resulted in 0.25\% of trials being excluded for Experiment 1, and 4.51\% of trials for Experiment 2.
-Next we averaged the waveforms across all remaining trials, and calculated the Fourier transform in a 1-second sliding window to generate timecourses for each participant.
-We divided the timecourse for the target-only condition by the timecourse for the target + mask condition to produce a suppression ratio.
-These were then converted to logarithmic (dB) units for averaging, calculation of standard errors, and statistical comparisons.
-For display purposes we smoothed the timecourses using a cubic spline function, however all statistical comparisons used the unsmoothed data.
-
-For Experiment 3, we performed source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm, implemented in Brainstorm (Tadel et al., 2011).
-Structural MRI scans were processed using Freesurfer (Dale et al., 1999) to generate a 3D mesh of the head and brain, and we calculated source weights for each block with reference to a 5-minute empty room recording, usually recorded on the day of the experiment.
-The matrix of source weights for each block was used in a custom Matlab script to extract signals from V1, identified using the probabilistic maps of Wang et al.
-(2015).
-These signals were then imported into R for the main analysis, which was consistent with the EEG analysis described above.
-The outlier rejection procedure excluded 2.47\% of trials for Experiment 3.
-
-To make comparisons between groups of participants across time, we used a non-parametric cluster correction technique (Maris and Oostenveld, 2007) based on t-tests.
-Clusters were identified as temporally adjacent observations that were all statistically significant, and a summed t-value was calculated for each cluster.
-A null distribution was then generated by randomising group membership and recalculating the summed t-value for the largest cluster, and repeating this procedure 1000 times.
-Clusters were considered significant if they fell outside of the 95\% confidence limits of the null distribution.
-We adapted this approach to test for significantly increasing suppression by conducting one-way t-tests between time points separated by 1000ms, and repeating the cluster correction procedure as described above.
-
-\hypertarget{preregistration-data-and-code-availability}{%
-\subsection{Preregistration, data and code availability}\label{preregistration-data-and-code-availability}}
-
-Following a preliminary analysis of the data from Experiment 1, we preregistered our hypotheses and analysis plan for Experiments 2 and 3 on the Open Science Framework website.
-The preregistration document, along with raw and processed data, and analysis scripts, are publicly available at the project repository: \url{https://osf.io/ab3yv/}
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-Alais2010}{}}%
-Alais D, Cass J, OShea RP, Blake R.
-2010.
-Visual sensitivity underlying changes in visual consciousness.
-\emph{Current Biology} \textbf{20}:1362--1367.
-doi:\href{https://doi.org/10.1016/j.cub.2010.06.015}{10.1016/j.cub.2010.06.015}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Aschner2018}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Dickinson2014}{}}%
-Dickinson A, Jones M, Milne E.
-2014.
-Oblique orientation discrimination thresholds are superior in those with a high level of autistic traits.
-\emph{Journal of Autism and Developmental Disorders} \textbf{44}:2844--2850.
-doi:\href{https://doi.org/10.1007/s10803-014-2147-1}{10.1007/s10803-014-2147-1}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Foley1994}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Jones1975}{}}%
-Jones PD, Holding DH.
-1975.
-Extremely long-term persistence of the McCollough effect.
-\emph{J Exp Psychol Hum Percept Perform} \textbf{1}:323--7.
-doi:\href{https://doi.org/10.1037//0096-1523.1.4.323}{10.1037//0096-1523.1.4.323}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Koh2010}{}}%
@@
 doi:\href{https://doi.org/10.1167/9.2.20}{10.1167/9.2.20}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Lamb2006}{}}%
-Lamb TD, Pugh EN Jr.
-2006.
-Phototransduction, dark adaptation, and rhodopsin regeneration the proctor lecture.
-\emph{Invest Ophthalmol Vis Sci} \textbf{47}:5137--52.
-doi:\href{https://doi.org/10.1167/iovs.06-0849}{10.1167/iovs.06-0849}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-McCollough1965}{}}%
-McCollough C.
-1965.
-Color adaptation of edge-detectors in the human visual system.
-\emph{Science} \textbf{149}:1115--6.
-doi:\href{https://doi.org/10.1126/science.149.3688.1115}{10.1126/science.149.3688.1115}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Meese2009}{}}%
@@
 doi:\href{https://doi.org/10.1523/jneurosci.2871-05.2005}{10.1523/jneurosci.2871-05.2005}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Robertson2013}{}}%
-Robertson CE, Kravitz DJ, Freyberg J, Baron-Cohen S, Baker CI.
-2013.
-Slower rate of binocular rivalry in autism.
-\emph{The Journal of Neuroscience} \textbf{33}:16983--16991.
-doi:\href{https://doi.org/10.1523/jneurosci.0448-13.2013}{10.1523/jneurosci.0448-13.2013}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Utzerath2018}{}}%
-Utzerath C, Schmits IC, Buitelaar J, Lange FP de.
-2018.
-Adolescents with autism show typical fMRI repetition suppression, but atypical surprise response.
-\emph{Cortex} \textbf{109}:25--34.
-doi:\href{https://doi.org/10.1016/j.cortex.2018.08.019}{10.1016/j.cortex.2018.08.019}
-
 \leavevmode\vadjust pre{\hypertarget{ref-VandeCruys2018}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-Wilson2003}{}}%
-Wilson HR.
-2003.
-Computational evidence for a rivalry hierarchy in vision.
-\emph{Proc Natl Acad Sci U S A} \textbf{100}:14499--503.
-doi:\href{https://doi.org/10.1073/pnas.2333622100}{10.1073/pnas.2333622100}
-
 \leavevmode\vadjust pre{\hypertarget{ref-Yiltiz2020}{}}%

### 2023-03-19 manuscript.Rmd
Minor edits for submission to JoV

@@
     keep_tex: yes
+    extra_dependencies: ["lineno"]
+  bookdown::word_document2:
+    fig_caption: yes
+    toc: no
   word_document: default
-  pdf_document:
-    toc: no
   html_document: default
@@
 ---
+
+\linenumbers
 
@@
 
-# Significance statement
-
-We investigated the timecourse of a novel form of neural plasticity, normalization reweighting, using steady-state EEG in humans.
-We find increases in suppression during the first 2-5 seconds of stimulation, with similar dynamics for monocular and dichoptic presentation.
-The effects are present in primary visual cortex, and were not mediated by autistic traits.
-These findings demonstrate that reweighting builds up rapidly after stimulus onset, consistent with a process that adjusts the sensory response to the local environment.
-Normalization reweighting also has potential as a biomarker of neural function both in humans and in animal models of disease.
-
 # Introduction
@@
 Procedures for Experiment 3 were approved by the ethics committee of the York Neuroimaging Centre.
-All participants provided written informed consent.
+All participants provided written informed consent, and procedures were consistent with the Declaration of Helsinki.
 

### 2023-03-19 manuscript.tex
Minor edits for submission to JoV

@@
  {}
-\usepackage{lineno}
-\linenumbers
 \usepackage{calc}
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\usepackage{lineno}
 \ifLuaTeX
@@
 
+\linenumbers
+
 \hypertarget{abstract}{%
@@
 Our results support the normalization reweighting model, and indicate that for prolonged stimulation, increases in suppression occur on the order of 2-5 seconds after stimulus onset.
-
-\hypertarget{significance-statement}{%
-\section{Significance statement}\label{significance-statement}}
-
-We investigated the timecourse of a novel form of neural plasticity, normalization reweighting, using steady-state EEG in humans.
-We find increases in suppression during the first 2-5 seconds of stimulation, with similar dynamics for monocular and dichoptic presentation.
-The effects are present in primary visual cortex, and were not mediated by autistic traits.
-These findings demonstrate that reweighting builds up rapidly after stimulus onset, consistent with a process that adjusts the sensory response to the local environment.
-Normalization reweighting also has potential as a biomarker of neural function both in humans and in animal models of disease.
 

### 2023-07-31 manuscript.Rmd
Implemented reviewer suggestions

@@
     extra_dependencies: ["lineno"]
-  bookdown::word_document2:
-    fig_caption: yes
-    toc: no
-  word_document: default
-  html_document: default
 bibliography: references.bib
-csl: elife.csl
+link-citations: true
+csl: journal-of-vision.csl
 ---
@@
 plotsmoothed <- 1 # either plot the raw data (0), or a smoothed spline (1)
+fixedphase <- 0 # option to use a fixed phase sinusoidal dot product instead of Fourier analysis for the timecourses
 useSPQ <- 0  # optionally do the median split by SPQ for the main EEG experiment
@@
 
-```{r include=FALSE, results='hide'}
+```{r analysepilotindividual, include=FALSE, results='hide'}
 
@@
 mindex <- (10*maskF) + 1
+tindex2 <- (10*targetF*2) + 1
+mindex2 <- (10*maskF*2) + 1
 duration <- 14
@@
 
-```{r include=FALSE, results='hide'}
+```{r analysepilotgroup, include=FALSE, results='hide'}
 
@@
     EEGspectra[s,cond,] <- spec[1:(20*10)]
-
+if (fixedphase==0){  # do normal Fourier analysis
 for (t in 1:(14000-binwidth)){
@@
   }
-}
+}}
+
+if (fixedphase==1){  # used fixed phase dot product with sinewave
+  # make a sine wave with the same phase as the EEG response
+  spec <- fft(temp)/length(temp)
+  synspec <- spec*0
+  synspec[(targetF*14) + 1] <- spec[(targetF*14) + 1]
+  sw1 <- Re(fft(synspec,inverse=TRUE))
+  sw1 <- sw1/max(sw1)
+  synspec <- spec*0
+  synspec[(maskF*14) + 1] <- spec[(maskF*14) + 1]
+  sw2 <- Re(fft(synspec,inverse=TRUE))  
+  sw2 <- sw2/max(sw2)
+  synspec <- spec*0
+  synspec[(2*targetF*14) + 1] <- spec[(2*targetF*14) + 1]
+  sw3 <- Re(fft(synspec,inverse=TRUE))
+  sw3 <- sw3/max(sw3)
+  synspec <- spec*0
+  synspec[(2*maskF*14) + 1] <- spec[(2*maskF*14) + 1]
+  sw4 <- Re(fft(synspec,inverse=TRUE)) 
+  sw4 <- sw4/max(sw4)
+
+for (t in 1:(14000-binwidth)){
+  EEGtimecourse[s,1,cond,t] <- mean(temp[t:(t+binwidth-1)] * sw1[t:(t+binwidth-1)]) + 0.1
+  EEGtimecourse[s,2,cond,t] <- mean(temp[t:(t+binwidth-1)] * sw2[t:(t+binwidth-1)]) + 0.1
+  EEGtimecourse[s,3,cond,t] <- mean(temp[t:(t+binwidth-1)] * sw3[t:(t+binwidth-1)]) + 0.1
+  EEGtimecourse[s,4,cond,t] <- mean(temp[t:(t+binwidth-1)] * sw4[t:(t+binwidth-1)]) + 0.1
+}}
+
   }
@@
 
-```{r include=FALSE, results='hide'}
+```{r plotpilotdata, include=FALSE, results='hide'}
 
@@
 }
+
+legend(2,1,c('Baseline','Target','Target+mask'),col=c('grey',colpal[1],colpal[2]),lty=1,lwd=2,box.lwd=2)
+
 text(10,0.95,'7Hz',cex=2)
@@
 spl5aL <- smooth.spline(times,EEGmeantimes[2,2,]-EEGSEtimes[2,2,],df=20)
-polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[1],border=NA)
+ # use of pmin function here crops the error region at the top of the graph 
+polygon(times[c(1:13000,13000:1)],c(pmin(spl5aU$y,1),spl5aL$y[13000:1]),col=colpal[1],border=NA)
 
@@
 
-  pdf('Figures/VilidaiteData.pdf', bg="transparent", height = 6, width = 16)
+ if (fixedphase==0){pdf('Figures/VilidaiteData.pdf', bg="transparent", height = 15, width = 6)}
+ if (fixedphase==1){pdf('Figures/VilidaiteDataFP.pdf', bg="transparent", height = 15, width = 6)}  
   par(mar=c(0.1,0.1,0.1,0.1))
@@
 
-  aspratio <- 6/16  # this is the aspect ratio of the output pdf
-  imwidth <- 0.25
-  xstart <- 0.02
-  ystart <- 0.58
+  aspratio <- 15/6  # this is the aspect ratio of the output pdf
+  imwidth <- 0.05
+  xstart <- 0.05
+  ystart <- 0.92
   rasterImage(e1,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth)
-  xstart <- 0.22
-  ystart <- 0.58
+  xstart <- 0.55
+  ystart <- 0.92
   rasterImage(e2,xstart,ystart,xstart+imwidth*aspratio,ystart+imwidth)
 
-  grid.picture(e3,x=0.225,y=0.7,width=0.4,height=1)
-  grid.picture(e5,x=0.225,y=0.25,width=0.4,height=1)
-
-  grid.picture(e6,x=0.5,y=0.85,width=0.1,height=1)
-  grid.picture(e7,x=0.5,y=0.625,width=0.1,height=1)
-  grid.picture(e8,x=0.5,y=0.375,width=0.1,height=1)
-  grid.picture(e9,x=0.5,y=0.15,width=0.1,height=1)
-  grid.picture(e4,x=0.77,y=0.5,width=0.45,height=1)
-
-  text(-0.02,0.98,'(a)',pos=4,cex=2)
-  text(-0.02,0.45,'(b)',pos=4,cex=2)
-  text(0.41,0.98,'(c)',pos=4,cex=2)
-  text(0.57,0.98,'(d)',pos=4,cex=2)
+  grid.picture(e3,x=0.5,y=0.91,width=1)
+  grid.picture(e5,x=0.5,y=0.74,width=1)
+
+  grid.picture(e6,x=0.25,y=0.57,width=0.5,height=1)
+  grid.picture(e7,x=0.75,y=0.57,width=0.5,height=1)
+  grid.picture(e8,x=0.25,y=0.42,width=0.5,height=1)
+  grid.picture(e9,x=0.75,y=0.42,width=0.5,height=1)
+
+  grid.picture(e4,x=0.5,y=2/12,width=1)
+
+  text(-0.055,1.02,'(a)',pos=4,cex=2)
+  text(-0.055,0.85,'(b)',pos=4,cex=2)
+  text(-0.055,0.67,'(c)',pos=4,cex=2)
+  text(-0.055,0.3,'(d)',pos=4,cex=2)
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r pilotstats, include=FALSE, results='hide'}
 
@@
 
+# calculate effect size
+
+baseline <- rowMeans((20*log10(abs(EEGtimecourse[,1,1,1001:2000])/abs(EEGtimecourse[,1,3,1001:2000])) + 20*log10(abs(EEGtimecourse[,2,2,1001:2000])/abs(EEGtimecourse[,2,3,1001:2000])) + 20*log10(abs(EEGtimecourse[,3,1,1001:2000])/abs(EEGtimecourse[,3,3,1001:2000])) + 20*log10(abs(EEGtimecourse[,4,2,1001:2000])/abs(EEGtimecourse[,4,3,1001:2000])))/4)
+
+laterepoch <- rowMeans((20*log10(abs(EEGtimecourse[,1,1,3001:4000])/abs(EEGtimecourse[,1,3,3001:4000])) + 20*log10(abs(EEGtimecourse[,2,2,3001:4000])/abs(EEGtimecourse[,2,3,3001:4000])) + 20*log10(abs(EEGtimecourse[,3,1,3001:4000])/abs(EEGtimecourse[,3,3,3001:4000])) + 20*log10(abs(EEGtimecourse[,4,2,3001:4000])/abs(EEGtimecourse[,4,3,3001:4000])))/4)
+
+diff <- laterepoch-baseline
+
+piloteffectsize <- mean(diff)/sd(diff)
+
 ```
 
-```{r include=FALSE, results='hide'}
+```{r analyseEEGindividual, include=FALSE, results='hide'}
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r analyseEEGgroup, include=FALSE, results='hide'}
 
@@
 
+if (fixedphase==0){
 fspec1 <- NULL
@@
     EEGtimecourse7Hz[s,cond,] <- fspec2
+}
+
+if (fixedphase==1){  # used fixed phase dot product with sinewave
+  # make a sine wave with the same phase as the EEG response
+  spec <- fft(temp)/length(temp)
+  synspec <- spec*0
+  synspec[(targetF*9) + 1] <- spec[(targetF*9) + 1]
+  sw1 <- Re(fft(synspec,inverse=TRUE))
+  sw1 <- sw1/max(sw1)
+  synspec <- spec*0
+  synspec[(maskF*9) + 1] <- spec[(maskF*9) + 1]
+  sw2 <- Re(fft(synspec,inverse=TRUE)) 
+  sw2 <- sw2/max(sw2)
+
+for (t in 1:(9000-binwidth)){
+  EEGtimecourse5Hz[s,cond,t] <- mean(temp[t:(t+binwidth-1)] * sw1[t:(t+binwidth-1)])
+  EEGtimecourse7Hz[s,cond,t] <- mean(temp[t:(t+binwidth-1)] * sw2[t:(t+binwidth-1)])
+}}
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r plotEEGdata, include=FALSE, results='hide'}
 
@@
 isincluded <- matrix(rep(1,4*dim(allspec)[1]),nrow=4,ncol=dim(allspec)[1])
+if (fixedphase==0){
 for (cond in 1:4){
@@
 }
+}
 
@@
 monratios <- abs(EEGtimecourse5Hz[which(includedboth==1),1,])/abs(EEGtimecourse5Hz[which(includedboth==1),3,])
-EEGmaskindex5[1,] <- colMeans(20*log10(monratios))
-EEGmaskindexSE5[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+monratios[which(monratios==0)] <- 0.001
+EEGmaskindex5[1,] <- colMeans(20*log10(monratios),na.rm=TRUE)
+EEGmaskindexSE5[1,] <- apply(20*log10(monratios),2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
 includedboth <- isincluded[1,]*isincluded[4,]
 dichratios <- abs(EEGtimecourse5Hz[which(includedboth==1),1,])/abs(EEGtimecourse5Hz[which(includedboth==1),4,])
-EEGmaskindex5[2,] <- colMeans(20*log10(dichratios))
-EEGmaskindexSE5[2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+dichratios[which(dichratios==0)] <- 0.001
+EEGmaskindex5[2,] <- colMeans(20*log10(dichratios),na.rm=TRUE)
+EEGmaskindexSE5[2,] <- apply(20*log10(dichratios),2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
 
@@
 
+earlydataM[is.na(earlydataM)] <- 0
+
 if (nbootstraps>0){clustoutM5 <- clustercorrect(earlydataM,latedataM,testtype=4,paired=TRUE)}
@@
 
+earlydataD[is.na(earlydataD)] <- 0
+
 if (nbootstraps>0){clustoutD5 <- clustercorrect(earlydataD,latedataD,testtype=4,paired=TRUE)}
@@
 monratios <- abs(EEGtimecourse7Hz[which(includedboth==1),2,])/abs(EEGtimecourse7Hz[which(includedboth==1),3,])
-EEGmaskindex7[1,] <- colMeans(20*log10(monratios))
-EEGmaskindexSE7[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+monratios[which(monratios==0)] <- 0.001
+EEGmaskindex7[1,] <- colMeans(20*log10(monratios),na.rm=TRUE)
+EEGmaskindexSE7[1,] <- apply(20*log10(monratios),2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
 includedboth <- isincluded[2,]*isincluded[4,]
 dichratios <- abs(EEGtimecourse7Hz[which(includedboth==1),2,])/abs(EEGtimecourse7Hz[which(includedboth==1),4,])
-EEGmaskindex7[2,] <- colMeans(20*log10(dichratios))
-EEGmaskindexSE7[2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+dichratios[which(dichratios==0)] <- 0.001
+EEGmaskindex7[2,] <- colMeans(20*log10(dichratios),na.rm=TRUE)
+EEGmaskindexSE7[2,] <- apply(20*log10(dichratios),2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
 
@@
 
+earlydataM[is.na(earlydataM)] <- 0
+
 if (nbootstraps>0){clustoutM7 <- clustercorrect(earlydataM,latedataM,testtype=4,paired=TRUE)}
@@
 
+earlydataD[is.na(earlydataD)] <- 0
+
 if (nbootstraps>0){clustoutD7 <- clustercorrect(earlydataD,latedataD,testtype=4,paired=TRUE)}
+
+EEGmaskindex5[which(is.na(EEGmaskindex5))] <- 0
+EEGmaskindex7[which(is.na(EEGmaskindex7))] <- 0
+EEGmaskindexSE5[which(is.na(EEGmaskindexSE5))] <- 0
+EEGmaskindexSE7[which(is.na(EEGmaskindexSE7))] <- 0
 
@@
 if (plotsmoothed==0){
-polygon(times[c(1:8000,8000:1)],c(EEGmeantime5Hz[1,]+EEGSEtime5Hz[1,],EEGmeantime5Hz[1,8000:1]-EEGSEtime5Hz[1,8000:1]),col=colpal[1],border=NA)
+polygon(times[c(1:8000,8000:1)],pmin(c(EEGmeantime5Hz[1,]+EEGSEtime5Hz[1,],EEGmeantime5Hz[1,8000:1]-EEGSEtime5Hz[1,8000:1]),plotlims[4]),col=colpal[1],border=NA)
 polygon(times[c(1:8000,8000:1)],c(EEGmeantime5Hz[3,]+EEGSEtime5Hz[3,],EEGmeantime5Hz[3,8000:1]-EEGSEtime5Hz[3,8000:1]),col=colpal[2],border=NA)
@@
 
-lines(times,EEGmeantime5Hz[1,],lwd=2,col=colpal[1])
+lines(times,pmin(EEGmeantime5Hz[1,],plotlims[4]),lwd=2,col=colpal[1])
 # lines(times,EEGmeantime5Hz[2,],lwd=2,col='green')
@@
 spl5aL <- smooth.spline(times,EEGmeantime5Hz[1,]-EEGSEtime5Hz[1,],df=20)
-polygon(times[c(1:8000,8000:1)],c(spl5aU$y,spl5aL$y[8000:1]),col=colpal[1],border=NA)
+polygon(times[c(1:8000,8000:1)],pmin(c(spl5aU$y,spl5aL$y[8000:1]),plotlims[4]), col=colpal[1],border=NA)
 
@@
 
-spl5a <- smooth.spline(times,EEGmeantime5Hz[1,],df=20)
+spl5a <- smooth.spline(times,pmin(EEGmeantime5Hz[1,],plotlims[4]),df=20)
 lines(spl5a$x,spl5a$y,col=colpal[1],lwd=2)
@@
 text(6,0.55,'5Hz',cex=2)
-  legend(1.25,0.2,c('Baseline','Monocular','Dichoptic'),lty=1,lwd=2,col=colpal[1:3],box.lwd=2)
+  legend(1.25,0.2,c('Target only','Monocular','Dichoptic'),lty=1,lwd=2,col=colpal[1:3],box.lwd=2)
 dev.off()
@@
 
-  pdf('Figures/EEGdata.pdf', bg="transparent", height = 6, width = 15)
+if (fixedphase==0){pdf('Figures/EEGdata.pdf', bg="transparent", height = 6, width = 15)}
+if (fixedphase==1){pdf('Figures/EEGdataFP.pdf', bg="transparent", height = 6, width = 15)}
   par(mar=c(0.1,0.1,0.1,0.1))
@@
 
-```{r include=FALSE, results='hide'}
+```{r EEGstats, include=FALSE, results='hide'}
 
@@
 
+# calculate effect size
+
+baseline <- rowMeans((20*log10(abs(EEGtimecourse5Hz[,1,1001:2000])/abs(EEGtimecourse5Hz[,3,1001:2000])) + 20*log10(abs(EEGtimecourse5Hz[,1,1001:2000])/abs(EEGtimecourse5Hz[,4,1001:2000])) + 20*log10(abs(EEGtimecourse7Hz[,2,1001:2000])/abs(EEGtimecourse7Hz[,3,1001:2000])) + 20*log10(abs(EEGtimecourse7Hz[,2,1001:2000])/abs(EEGtimecourse7Hz[,4,1001:2000])))/4)
+
+laterepoch <- rowMeans((20*log10(abs(EEGtimecourse5Hz[,1,3001:4000])/abs(EEGtimecourse5Hz[,3,3001:4000])) + 20*log10(abs(EEGtimecourse5Hz[,1,3001:4000])/abs(EEGtimecourse5Hz[,4,3001:4000])) + 20*log10(abs(EEGtimecourse7Hz[,2,3001:4000])/abs(EEGtimecourse7Hz[,3,3001:4000])) + 20*log10(abs(EEGtimecourse7Hz[,2,3001:4000])/abs(EEGtimecourse7Hz[,4,3001:4000])))/4)
+
+diff <- laterepoch-baseline
+
+EEGeffectsize <- mean(diff)/sd(diff)
+
 ```
 
-```{r include=FALSE, results='hide'}
+```{r analyseMEGgroup, include=FALSE, results='hide'}
 
@@
 
+if (fixedphase==0){            
         fspec1 <- NULL
@@
         MEGtimecourse7Hz[s,cond,] <- fspec2
+}
+
+if (fixedphase==1){  # used fixed phase dot product with sinewave
+  # make a sine wave with the same phase as the EEG response
+  spec <- fft(temp)/length(temp)
+  synspec <- spec*0
+  synspec[(targetF*8) + 1] <- spec[(targetF*8) + 1]
+  sw1 <- Re(fft(synspec,inverse=TRUE))
+  sw1 <- sw1/max(sw1)
+  synspec <- spec*0
+  synspec[(maskF*8) + 1] <- spec[(maskF*8) + 1]
+  sw2 <- Re(fft(synspec,inverse=TRUE))
+  sw2 <- sw2/max(sw2)
+
+for (t in 1:(9000-binwidth)){
+  MEGtimecourse5Hz[s,cond,t] <- mean(temp[t:(t+binwidth-1)] * sw1[t:(t+binwidth-1)])
+  MEGtimecourse7Hz[s,cond,t] <- mean(temp[t:(t+binwidth-1)] * sw2[t:(t+binwidth-1)])
+}}
 
@@
 
-```{r include=FALSE, results='hide'}
+```{r plotMEGdata, include=FALSE, results='hide'}
 
@@
 isincluded <- array(1, dim=c(4,dim(allspec)[1]))
+if (fixedphase==0){
     for (cond in 1:4){
@@
     }
+  }
 
@@
     monratios <- abs(MEGtimecourse5Hz[which(includedboth==1),1,])/abs(MEGtimecourse5Hz[which(includedboth==1),3,])
-    MEGmaskindex5[1,] <- colMeans(20*log10(monratios))
-    MEGmaskindexSE5[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+    MEGmaskindex5[1,] <- colMeans(20*log10(monratios),na.rm=TRUE)
+    MEGmaskindexSE5[1,] <- apply(20*log10(monratios),2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
     includedboth <- isincluded[1,]*isincluded[4,]
     dichratios <- abs(MEGtimecourse5Hz[which(includedboth==1),1,])/abs(MEGtimecourse5Hz[which(includedboth==1),4,])
-    MEGmaskindex5[2,] <- colMeans(20*log10(dichratios))
-    MEGmaskindexSE5[2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+    MEGmaskindex5[2,] <- colMeans(20*log10(dichratios),na.rm=TRUE)
+    MEGmaskindexSE5[2,] <- apply(20*log10(dichratios),2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
 
@@
 latedataD[1:dim(dichratios)[1],(dim(dichratios)[2])+(1-(timeoffset/2)):0] <- 0
+
+earlydataD[is.na(earlydataD)] <- 0
 
@@
 
+earlydataD[is.na(earlydataD)] <- 0
+
 if (nbootstraps>0){clustoutD7 <- clustercorrect(earlydataD,latedataD,testtype=4,paired=TRUE)}
+
+MEGmaskindex5[which(is.na(MEGmaskindex5))] <- 0
+MEGmaskindex7[which(is.na(MEGmaskindex7))] <- 0
+MEGmaskindexSE5[which(is.na(MEGmaskindexSE5))] <- 0
+MEGmaskindexSE7[which(is.na(MEGmaskindexSE7))] <- 0
 
@@
   text(6,2.8,'5Hz',cex=2)
-  legend(1.25,1,c('Baseline','Monocular','Dichoptic'),lty=1,lwd=2,col=colpal[1:3],box.lwd=2)
+  legend(1.25,1,c('Target only', 'Monocular','Dichoptic'), lty=1,lwd=2,col=colpal[1:3],box.lwd=2)
   dev.off()
@@
 
-  pdf('Figures/MEGdata.pdf', bg="transparent", height = 6, width = 15)
+if (fixedphase==0){pdf('Figures/MEGdata.pdf', bg="transparent", height = 6, width = 15)}
+if (fixedphase==1){pdf('Figures/MEGdataFP.pdf', bg="transparent", height = 6, width = 15)}
   par(mar=c(0.1,0.1,0.1,0.1))
@@
 
+# calculate effect size
+
+baseline <- rowMeans((20*log10(abs(MEGtimecourse5Hz[,1,1002:2003])/abs(MEGtimecourse5Hz[,3,1002:2003])) + 20*log10(abs(MEGtimecourse5Hz[,1,1002:2003])/abs(MEGtimecourse5Hz[,4,1002:2003])) + 20*log10(abs(MEGtimecourse7Hz[,2,1002:2003])/abs(MEGtimecourse7Hz[,3,1002:2003])) + 20*log10(abs(MEGtimecourse7Hz[,2,1002:2003])/abs(MEGtimecourse7Hz[,4,1002:2003])))/4)
+
+laterepoch <- rowMeans((20*log10(abs(MEGtimecourse5Hz[,1,3004:4005])/abs(MEGtimecourse5Hz[,3,3004:4005])) + 20*log10(abs(MEGtimecourse5Hz[,1,3004:4005])/abs(MEGtimecourse5Hz[,4,3004:4005])) + 20*log10(abs(MEGtimecourse7Hz[,2,3004:4005])/abs(MEGtimecourse7Hz[,3,3004:4005])) + 20*log10(abs(MEGtimecourse7Hz[,2,3004:4005])/abs(MEGtimecourse7Hz[,4,3004:4005])))/4)
+
+diff <- laterepoch-baseline
+
+MEGeffectsize <- mean(diff)/sd(diff)
+
 ```
 
-```{r include=FALSE, results='hide'}
+```{r runIManalysis, include=FALSE, results='hide'}
+
+# group level analysis of data from Vilidaite et al. (2018)
+
+samplerate <- 1000
+targetF <- 7
+maskF <- 5
+tindex <- (10*(targetF+maskF)) + 1
+duration <- 14
+
+binwidth <- 1000
+findex <- 1 + (targetF+maskF)*(binwidth/samplerate)
+
+condlist <- c(6,8,13)
+
+if (processdata>1){
+
+d <- dir(path = 'temp/VilidaiteProcessed', pattern = '*.RData', full.names=TRUE)
+
+# download any missing data files from osf
+if (length(d)<100){
+  pilotrepo <- pmatch('Processed pilot data',as.character(unlist(componentlist[,1])))
+  pilotfiles <- osf_ls_files(componentlist[pilotrepo,2],n_max=300)
+  for (s in 1:nrow(pilotfiles)){
+    if (!file.exists(paste0('temp/VilidaiteProcessed/',pilotfiles[s,1]))){
+      osf_download(pilotfiles[s,],'temp/VilidaiteProcessed/',progress=TRUE)
+    }
+  }
+}
+
+d <- dir(path = 'temp/VilidaiteProcessed', pattern = '*.RData', full.names=TRUE)
+
+EEGtimecourse <- array(0,dim=c(length(d),3,13000))
+# EEGspectra <- array(0,dim=c(length(d),3,20*10))
+EEGscalpresps <- array(0,dim=c(length(d),14,64))
+# EEGallconds <- array(0,dim=c(length(d),4,14))
+alltrialcounts <- array(0,dim=c(length(d),14,64))
+
+for (s in 1:length(d)){
+  load(d[s])
+  targetchannels <- match(targetelectrodes, electrodes) - 2
+  alltrialcounts[s,,] <- trialsincluded
+
+  for (cond in 1:3){
+    temp <- colMeans(meanwaveforms[condlist[cond],targetchannels,],na.rm=TRUE)
+    nainds <- which(is.na(temp))   # find occasional NaN values in the waveform
+    temp[nainds] <- 0   # replace with zeros
+
+for (t in 1:(14000-binwidth)){
+  spec <- fft(temp[t:(t+binwidth-1)])/binwidth
+  EEGtimecourse[s,cond,t] <- spec[findex]
+}
+}
+
+for (cond in 1:14){
+  for (ch in 1:64){
+     temp <- meanwaveforms[cond,ch,]
+    nainds <- which(is.na(temp))   # find occasional NaN values in the waveform
+    temp[nainds] <- 0   # replace with zeros
+   spec <- fft(temp[2501:12500])/10000
+   EEGscalpresps[s,cond,ch] <- spec[((targetF+maskF)*10)+1]
+
+  }
+}
+
+}
+
+save(file='temp/PilotIM.RData',list=c('EEGtimecourse','electrodes','EEGscalpresps','alltrialcounts'))
+
+}
+
+if (processdata>0){
+load('temp/PilotIM.RData')
+
+nsubjs <- dim(EEGtimecourse)[1]
+EEGmeantimes <- array(0,dim=c(3,13000))
+EEGSEtimes <- array(0,dim=c(3,13000))
+EEGmeanscalp <- abs(apply(abs(EEGscalpresps),2:3,mean))
+
+for (cond in 1:3){
+EEGmeantimes[cond,] <- apply(abs(EEGtimecourse[,cond,]),2,mean,na.rm=TRUE)
+EEGSEtimes[cond,] <- apply(abs(EEGtimecourse[,cond,]),2,sd,na.rm=TRUE)/sqrt(nsubjs)
+}
+
+EEGmaskindices <- colMeans(20*log10(abs(EEGtimecourse[,3,])/abs(EEGtimecourse[,2,])))
+EEGmaskSE <- apply(20*log10(abs(EEGtimecourse[,3,])/abs(EEGtimecourse[,2,])),2,sd)/sqrt(nsubjs)
+
+times <- (-999:12000)/1000
+
+postscript('pilotIM.ps', horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,12,-3,6)
+ticklocsx <- c(-1,seq(0,12,2))    # locations of tick marks on y axis
+ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = seq(0,12,2), side = 1, at=seq(0,12,2))
+mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="12Hz response", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,11,11,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))
+
+lines(c(-1,12),c(0,0),lty=2)
+
+if (plotsmoothed==0){
+
+  polygon(times[c(1:13000,13000:1)],c(EEGmaskindices+EEGmaskSE,EEGmaskindices[13000:1]-EEGmaskSE[13000:1]),col=colpal[1],border=NA)
+
+lines(times,EEGmaskindices,col=colpal[1],lwd=4)
+}
+
+if (plotsmoothed==1){
+
+  spl5aU <- smooth.spline(times,EEGmaskindices+EEGmaskSE,df=20)
+spl5aL <- smooth.spline(times,EEGmaskindices-EEGmaskSE,df=20)
+polygon(times[c(1:13000,13000:1)],c(spl5aU$y,spl5aL$y[13000:1]),col=colpal[1],border=NA)
+
+spl5a <- smooth.spline(times,EEGmaskindices,df=20)
+lines(spl5a$x,spl5a$y,col=colpal[1],lwd=6)
+}
+
+text(9,5.5,'Pilot EEG data',cex=1.5)
+dev.off()
+
+}
+
+duration <- 6
+
+if (processdata>1){
+
+d <- dir(path = 'temp/EEGprocessed', pattern = '*.RData', full.names=TRUE)
+
+# download any missing data files from osf
+if (length(d)<100){
+  EEGrepo <- pmatch('Processed EEG data',as.character(unlist(componentlist[,1])))
+  EEGfiles <- osf_ls_files(componentlist[EEGrepo,2],n_max=300)
+  for (s in 1:nrow(EEGfiles)){
+    if (!file.exists(paste0('temp/EEGprocessed/',EEGfiles[s,1]))){
+      osf_download(EEGfiles[s,],'temp/EEGprocessed/',progress=TRUE)
+    }
+  }
+}
+
+d <- dir(path = 'temp/EEGprocessed', pattern = '*.RData', full.names=TRUE)
+
+EEGtimecourse12Hz <- array(0,dim=c(length(d),4,8000))
+allwaves <- array(0,dim=c(length(d),4,9000))
+allheads12 <- array(0,dim=c(length(d),4,64))
+EEGtrialsincluded <- array(0,dim=c(length(d),4,64))
+
+for (s in 1:length(d)){
+  load(d[s])
+  targetchannels <- match(targetelectrodes, electrodes) - 2
+  EEGtrialsincluded[s,,] <- trialsincluded
+  for (cond in 1:4){
+    temp <- rowMeans(subjwaves[cond,,targetchannels],na.rm=TRUE)
+    nainds <- which(is.na(temp))   
+    temp[nainds] <- 0   # replace with zeros
+    allwaves[s,cond,] <- temp - mean(temp)
+
+fspec1 <- NULL
+for (t in 1:(9000-binwidth)){
+  spec <- fft(temp[t:(t+binwidth-1)])/binwidth
+  fspec1[t] <- spec[findex]
+}
+    EEGtimecourse12Hz[s,cond,] <- fspec1
+
+  for (ch in 1:64){
+    temp <- fft(subjwaves[cond,1501:7500,ch])/6000
+    allheads12[s,cond,ch] <- temp[1+(duration*(targetF+maskF))]
+
+  }
+  }
+
+}
+
+save(file='temp/EEGIM.RData',list=c('allheads12','allwaves','EEGtimecourse12Hz','electrodes','EEGtrialsincluded'))
+}
+
+if (processdata>0){
+load('temp/EEGIM.RData')
+
+nsubjs <- dim(EEGtimecourse12Hz)[1]    
+mon1 <- 20*log10(abs(EEGtimecourse12Hz[,3,])/abs(EEGtimecourse12Hz[,1,]))
+mon2 <- 20*log10(abs(EEGtimecourse12Hz[,3,])/abs(EEGtimecourse12Hz[,2,]))
+meanmon <- (mon1 + mon2)/2
+meanmon[which(is.infinite(meanmon))] <- 0
+EEGmaskindicesMon <- colMeans(meanmon)
+EEGmaskSEMon <- apply(meanmon,2,sd)/sqrt(nsubjs)
+
+dich1 <- 20*log10(abs(EEGtimecourse12Hz[,4,])/abs(EEGtimecourse12Hz[,1,]))
+dich2 <- 20*log10(abs(EEGtimecourse12Hz[,4,])/abs(EEGtimecourse12Hz[,2,]))
+meandich <- (dich1 + dich2)/2
+meandich[which(is.infinite(meandich))] <- 0
+EEGmaskindicesDich <- colMeans(meandich)
+EEGmaskSEDich <- apply(meandich,2,sd)/sqrt(nsubjs)
+
+times <- (-999:7000)/1000
+
+postscript('EEG_IM.ps', horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,7,-3,6)
+ticklocsx <- seq(-1,7,1)    # locations of tick marks on y axis
+ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = seq(-1,7,1), side = 1, at=seq(-1,7,1))
+mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="12Hz response", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,6,6,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))
+
+lines(c(-1,7),c(0,0),lty=2)
+
+if (plotsmoothed==0){
+
+  polygon(times[c(1:8000,8000:1)],c(EEGmaskindicesMon+EEGmaskSEMon,EEGmaskindicesMon[8000:1]-EEGmaskSEMon[8000:1]),col=colpal[2],border=NA)
+  polygon(times[c(1:8000,8000:1)],c(EEGmaskindicesDich+EEGmaskSEDich,EEGmaskindicesDich[8000:1]-EEGmaskSEDich[8000:1]),col=colpal[3],border=NA)
+
+lines(times,EEGmaskindicesMon,col=colpal[2],lwd=4)
+lines(times,EEGmaskindicesDich,col=colpal[3],lwd=4)
+}
+
+if (plotsmoothed==1){
+
+spl5aU <- smooth.spline(times,EEGmaskindicesMon+EEGmaskSEMon,df=20)
+spl5aL <- smooth.spline(times,EEGmaskindicesMon-EEGmaskSEMon,df=20)
+polygon(times[c(1:8000,8000:1)],c(spl5aU$y,spl5aL$y[8000:1]),col=colpal[2],border=NA)
+
+spl5aU <- smooth.spline(times,EEGmaskindicesDich+EEGmaskSEDich,df=20)
+spl5aL <- smooth.spline(times,EEGmaskindicesDich-EEGmaskSEDich,df=20)
+polygon(times[c(1:8000,8000:1)],c(spl5aU$y,spl5aL$y[8000:1]),col=colpal[3],border=NA)
+
+spl5a <- smooth.spline(times,EEGmaskindicesMon,df=20)
+lines(spl5a$x,spl5a$y,col=colpal[2],lwd=6)
+
+spl5a <- smooth.spline(times,EEGmaskindicesDich,df=20)
+lines(spl5a$x,spl5a$y,col=colpal[3],lwd=6)
+
+}
+text(5.5,5.5,'EEG data',cex=1.5)
+
+legend(1.5,-0.5,c('Monocular','Dichoptic'),lwd=4,col=colpal[c(2,3)],bty='n')
+
+dev.off()
+
+}
+
+samplerate <- 1001
+binwidth <- 1001
+findex <- 1 + (targetF+maskF)*(binwidth/samplerate)
+
+if (processdata>1){
+
+d <- dir(path = 'temp/MEGdata', pattern = '*.RData', full.names=TRUE)
+
+  # download any missing data files from osf
+if (length(d)<20){
+  MEGrepo <- pmatch('Processed MEG data',as.character(unlist(componentlist[,1])))
+  MEGfiles <- osf_ls_files(componentlist[MEGrepo,2],n_max=300)
+  for (s in 1:nrow(MEGfiles)){
+    if (!file.exists(paste0('temp/MEGdata/',MEGfiles[s,1]))){
+      osf_download(MEGfiles[s,],'temp/MEGdata/',progress=TRUE)
+    }
+  }
+}
+
+d <- dir(path = 'temp/MEGdata', pattern = '*.RData', full.names=TRUE)
+
+MEGtimecourse12Hz <- array(0,dim=c(length(d),4,8008))
+MEGsubjwaves <- array(0,dim=c(length(d),4,9009))
+allspec <- array(0,dim=c(length(d),4,(duration*20)))
+MEGtrialsincluded <- array(0,dim=c(length(d),4))
+
+for (s in 1:length(d)){
+  load(d[s])
+
+  for (cond in 1:4){
+
+     temp <- alltrials[cond,1:trialcounter[1,cond],]
+          spec12 <- NULL
+          for (t in 1:trialcounter[1,cond]){
+            spec <- fft(temp[t,1501:7506])/6006
+            spec12[t] <- spec[(targetF+maskF)*duration+1]
+          }
+        spec12[which(is.na(spec12))] <- 0
+
+      if (length(which(abs(spec12)>0))>2){  
+      tempxy <- data.frame(Re(spec12),Im(spec12))
+      D12 <- sqrt(mahalanobis(tempxy,colMeans(tempxy),cov(tempxy)))
+      i <- which(D12<3)
+      MEGtrialsincluded[s,cond] <- length(i)
+      temp <- colMeans(temp[i,])
+      MEGsubjwaves[s,cond,] <- temp
+      spec <- fft(temp[1501:7506])/6006
+      allspec[s,cond,] <- spec[1+(1:(duration*20))]
+
+        fspec1 <- NULL
+        fspec2 <- NULL
+        for (t in 1:(9009-binwidth)){
+          spec <- fft(temp[t:(t+binwidth-1)])/binwidth
+          fspec1[t] <- spec[findex]
+        }
+
+        MEGtimecourse12Hz[s,cond,] <- fspec1
+
+        }
+  }
+}
+
+save(file='temp/MEGIM.RData',list=c('MEGsubjwaves','MEGtimecourse12Hz','allspec','MEGtrialsincluded'))
+
+}
+
+if (processdata>0){
+load('temp/MEGIM.RData')
+
+nsubjs <- dim(MEGtimecourse12Hz)[1]    
+mon1 <- 20*log10(abs(MEGtimecourse12Hz[,3,])/abs(MEGtimecourse12Hz[,1,]))
+mon2 <- 20*log10(abs(MEGtimecourse12Hz[,3,])/abs(MEGtimecourse12Hz[,2,]))
+meanmon <- (mon1 + mon2)/2
+meanmon[which(is.infinite(meanmon))] <- 0
+MEGmaskindicesMon <- colMeans(meanmon)
+MEGmaskSEMon <- apply(meanmon,2,sd)/sqrt(nsubjs)
+
+dich1 <- 20*log10(abs(MEGtimecourse12Hz[,4,])/abs(MEGtimecourse12Hz[,1,]))
+dich2 <- 20*log10(abs(MEGtimecourse12Hz[,4,])/abs(MEGtimecourse12Hz[,2,]))
+meandich <- (dich1 + dich2)/2
+meandich[which(is.infinite(meandich))] <- 0
+MEGmaskindicesDich <- colMeans(meandich)
+MEGmaskSEDich <- apply(meandich,2,sd)/sqrt(nsubjs)
+
+times <- (-999:7008)/1000
+
+postscript('MEG_IM.ps', horizontal = FALSE, onefile = FALSE, paper = "special", height = 5, width = 5)
+
+plotlims <- c(-1,7,-3,6)
+ticklocsx <- seq(-1,7,1)    # locations of tick marks on y axis
+ticklocsy <- seq(-3,6,3)    # locations of tick marks on y axis
+plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=plotlims[1:2], ylim=plotlims[3:4])
+axis(1, at=ticklocsx, tck=0.01, lab=F, lwd=2)
+axis(2, at=ticklocsy, tck=0.01, lab=F, lwd=2)
+mtext(text = seq(-1,7,1), side = 1, at=seq(-1,7,1))
+mtext(text = c(expression(sqrt(2)/2),'1',expression(sqrt(2)),'2'), side = 2, at=ticklocsy, line=0.2, las=1)
+title(xlab="Time (s)", col.lab=rgb(0,0,0), line=1.2, cex.lab=1.5)    
+title(ylab="12Hz response", col.lab=rgb(0,0,0), line=1.5, cex.lab=1.5)
+
+polygon(c(0,6,6,0),c(-3.4,-3.4,-2.6,-2.6),border=NA,col=rgb(0.5,0.5,0.5))
+
+lines(c(-1,7),c(0,0),lty=2)
+
+if (plotsmoothed==0){
+
+  polygon(times[c(1:8008,8008:1)],c(MEGmaskindicesMon+MEGmaskSEMon,MEGmaskindicesMon[8008:1]-MEGmaskSEMon[8008:1]),col=colpal[2],border=NA)
+  polygon(times[c(1:8008,8008:1)],c(MEGmaskindicesDich+MEGmaskSEDich,MEGmaskindicesDich[8008:1]-MEGmaskSEDich[8008:1]),col=colpal[3],border=NA)
+
+lines(times,MEGmaskindicesMon,col=colpal[2],lwd=4)
+lines(times,MEGmaskindicesDich,col=colpal[3],lwd=4)
+}
+
+if (plotsmoothed==1){
+
+spl5aU <- smooth.spline(times,MEGmaskindicesMon+MEGmaskSEMon,df=20)
+spl5aL <- smooth.spline(times,MEGmaskindicesMon-MEGmaskSEMon,df=20)
+polygon(times[c(1:8008,8008:1)],c(spl5aU$y,spl5aL$y[8008:1]),col=colpal[2],border=NA)
+
+spl5aU <- smooth.spline(times,MEGmaskindicesDich+MEGmaskSEDich,df=20)
+spl5aL <- smooth.spline(times,MEGmaskindicesDich-MEGmaskSEDich,df=20)
+polygon(times[c(1:8008,8008:1)],c(spl5aU$y,spl5aL$y[8008:1]),col=colpal[3],border=NA)
+
+spl5a <- smooth.spline(times,MEGmaskindicesMon,df=20)
+lines(spl5a$x,spl5a$y,col=colpal[2],lwd=6)
+
+spl5a <- smooth.spline(times,MEGmaskindicesDich,df=20)
+lines(spl5a$x,spl5a$y,col=colpal[3],lwd=6)
+
+}
+text(5.5,5.5,'MEG data',cex=1.5)
+
+legend(1.5,-0.5,c('Monocular','Dichoptic'),lwd=4,col=colpal[c(2,3)],bty='n')
+
+dev.off()
+
+  PostScriptTrace(paste('pilotIM.ps',sep=''))
+  e1 <- readPicture('pilotIM.ps.xml')
+  for (n in 1:length(e1@paths)){
+    temp <- class(e1@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e1@paths[n]$path@rgb))<765){e1@paths[n]$path@rgb <- addalpha(e1@paths[n]$path@rgb,alpha=0.2)}}}
+
+  PostScriptTrace(paste('EEG_IM.ps',sep=''))
+  e2 <- readPicture('EEG_IM.ps.xml')
+  for (n in 1:length(e2@paths)){
+    temp <- class(e2@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e2@paths[n]$path@rgb))<765){e2@paths[n]$path@rgb <- addalpha(e2@paths[n]$path@rgb,alpha=0.2)}}}
+
+  PostScriptTrace(paste('MEG_IM.ps',sep=''))
+  e3 <- readPicture('MEG_IM.ps.xml')
+  for (n in 1:length(e3@paths)){
+    temp <- class(e3@paths[n]$path)[1]
+    if (pmatch(temp,"PictureFill",nomatch=0)){
+      if (sum(col2rgb(e3@paths[n]$path@rgb))<765){e3@paths[n]$path@rgb <- addalpha(e3@paths[n]$path@rgb,alpha=0.2)}}}
+
+if (fixedphase==0){pdf('Figures/IMfigure.pdf', bg="transparent", height = 5, width = 18)}
+
+  par(mar=c(0.1,0.1,0.1,0.1))
+  plot(x=NULL,y=NULL,axes=FALSE, ann=FALSE, xlim=c(0,1), ylim=c(0,1))
+
+  grid.picture(e1,x=1/6,y=1/2,width=0.33,height=1)
+  grid.picture(e2,x=3/6,y=1/2,width=0.33,height=1)
+  grid.picture(e3,x=5/6,y=1/2,width=0.33,height=1)
+
+  text(-0.04,0.97,'(a)',pos=4,cex=3)
+  text(0.32,0.97,'(b)',pos=4,cex=3)
+  text(0.68,0.97,'(c)',pos=4,cex=3)
+
+  dev.off()
+
+  file.remove(c('pilotIM.ps','EEG_IM.ps','MEG_IM.ps'))
+  file.remove(c('pilotIM.ps.xml','EEG_IM.ps.xml','MEG_IM.ps.xml'))
+
+}
+
+```
+
+```{r runAQanalysis, include=FALSE, results='hide'}
 
@@
   monratios <- (20*log10(monratios1) + 20*log10(monratios2) + 20*log10(monratios3) + 20*log10(monratios4))/4
-  PilotmaskindexL <- colMeans(monratios)
-  PilotmaskindexSEL <- apply(monratios,2,sd)/sqrt(sum(includedboth))
+  PilotmaskindexL <- colMeans(monratios,na.rm=TRUE)
+  PilotmaskindexSEL <- apply(monratios,2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
 
@@
   monratios <- (20*log10(monratios1) + 20*log10(monratios2) + 20*log10(monratios3) + 20*log10(monratios4))/4
-  PilotmaskindexH <- colMeans(monratios)
-  PilotmaskindexSEH <- apply(monratios,2,sd)/sqrt(sum(includedboth))
+  PilotmaskindexH <- colMeans(monratios,na.rm=TRUE)
+  PilotmaskindexSEH <- apply(monratios,2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
 
@@
   monratios <- abs(EEGtimecourse[which(includedboth==1),2,2,])/abs(EEGtimecourse[which(includedboth==1),2,3,])
-  Pilotmaskindex5L[1,] <- colMeans(20*log10(monratios))
-  PilotmaskindexSE5L[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+  Pilotmaskindex5L[1,] <- colMeans(20*log10(monratios),na.rm=TRUE)
+  PilotmaskindexSE5L[1,] <- apply(20*log10(monratios),2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
 
@@
   monratios <- abs(EEGtimecourse[which(includedboth==1),2,2,])/abs(EEGtimecourse[which(includedboth==1),2,3,])
-  Pilotmaskindex5H[1,] <- colMeans(20*log10(monratios))
-  PilotmaskindexSE5H[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+  Pilotmaskindex5H[1,] <- colMeans(20*log10(monratios),na.rm=TRUE)
+  PilotmaskindexSE5H[1,] <- apply(20*log10(monratios),2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
 
@@
   monratios <- abs(EEGtimecourse[which(includedboth==1),1,1,])/abs(EEGtimecourse[which(includedboth==1),1,3,])
-  Pilotmaskindex7L[1,] <- colMeans(20*log10(monratios))
-  PilotmaskindexSE7L[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+  Pilotmaskindex7L[1,] <- colMeans(20*log10(monratios),na.rm=TRUE)
+  PilotmaskindexSE7L[1,] <- apply(20*log10(monratios),2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
 
@@
   monratios <- abs(EEGtimecourse[which(includedboth==1),1,1,])/abs(EEGtimecourse[which(includedboth==1),1,3,])
-  Pilotmaskindex7H[1,] <- colMeans(20*log10(monratios))
-  PilotmaskindexSE7H[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+  Pilotmaskindex7H[1,] <- colMeans(20*log10(monratios),na.rm=TRUE)
+  PilotmaskindexSE7H[1,] <- apply(20*log10(monratios),2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
 
@@
   monratios <- (20*log10(monratios1) + 20*log10(monratios2))/2
-  EEGmaskindexL[1,] <- colMeans(monratios)
-  EEGmaskindexSEL[1,] <- apply(monratios,2,sd)/sqrt(sum(includedboth))
+  EEGmaskindexL[1,] <- colMeans(monratios,na.rm=TRUE)
+  EEGmaskindexSEL[1,] <- apply(monratios,2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
   includedboth <- isincluded[1,]*isincluded[4,]*islowAQ
@@
   dichratios <- (20*log10(dichratios1) + 20*log10(dichratios2))/2
-  EEGmaskindexL[2,] <- colMeans(dichratios)
-  EEGmaskindexSEL[2,] <- apply(dichratios,2,sd)/sqrt(sum(includedboth))
+  EEGmaskindexL[2,] <- colMeans(dichratios,na.rm=TRUE)
+  EEGmaskindexSEL[2,] <- apply(dichratios,2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
 
@@
   monratios <- (20*log10(monratios1) + 20*log10(monratios2))/2
-  EEGmaskindexH[1,] <- colMeans(monratios)
-  EEGmaskindexSEH[1,] <- apply(monratios,2,sd)/sqrt(sum(includedboth))
+  EEGmaskindexH[1,] <- colMeans(monratios,na.rm=TRUE)
+  EEGmaskindexSEH[1,] <- apply(monratios,2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
   includedboth <- isincluded[1,]*isincluded[4,]*ishighAQ
@@
   dichratios <- (20*log10(dichratios1) + 20*log10(dichratios2))/2
-  EEGmaskindexH[2,] <- colMeans(dichratios)
-  EEGmaskindexSEH[2,] <- apply(dichratios,2,sd)/sqrt(sum(includedboth))
+  EEGmaskindexH[2,] <- colMeans(dichratios,na.rm=TRUE)
+  EEGmaskindexSEH[2,] <- apply(dichratios,2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
 
@@
   monratios <- abs(EEGtimecourse5Hz[which(includedboth==1),1,])/abs(EEGtimecourse5Hz[which(includedboth==1),3,])
-  EEGmaskindex5L[1,] <- colMeans(20*log10(monratios))
-  EEGmaskindexSE5L[1,] <- apply(20*log10(monratios),2,sd)/sqrt(sum(includedboth))
+  EEGmaskindex5L[1,] <- colMeans(20*log10(monratios),na.rm=TRUE)
+  EEGmaskindexSE5L[1,] <- apply(20*log10(monratios),2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
   includedboth <- isincluded[1,]*isincluded[4,]*islowAQ
   dichratios <- abs(EEGtimecourse5Hz[which(includedboth==1),1,])/abs(EEGtimecourse5Hz[which(includedboth==1),4,])
-  EEGmaskindex5L[2,] <- colMeans(20*log10(dichratios))
-  EEGmaskindexSE5L[2,] <- apply(20*log10(dichratios),2,sd)/sqrt(sum(includedboth))
+  EEGmaskindex5L[2,] <- colMeans(20*log10(dichratios),na.rm=TRUE)
+  EEGmaskindexSE5L[2,] <- apply(20*log10(dichratios),2,sd,na.rm=TRUE)/sqrt(sum(includedboth))
 
@@
 
+  CgroupM[which(is.na(CgroupM))] <- 0
+  AgroupM[which(is.na(AgroupM))] <- 0
+  CgroupD[which(is.na(CgroupD))] <- 0
+  AgroupD[which(is.na(AgroupD))] <- 0
+
       if (nbootstraps>0){
@@
 
+    MEGmaskindexC[which(is.na(MEGmaskindexC))] <- 0
+    MEGmaskindexA[which(is.na(MEGmaskindexA))] <- 0
+    MEGmaskindexSEC[which(is.na(MEGmaskindexSEC))] <- 0
+    MEGmaskindexSEA[which(is.na(MEGmaskindexSEA))] <- 0
+
     if (plotsmoothed==0){
@@
     if (plotsmoothed==1){
+
       U <- smooth.spline(times,MEGmaskindexC[masktype,]+MEGmaskindexSEC[masktype,],df=20)
@@
 
-  pdf('Figures/AQfigure.pdf', bg="transparent", height = 10, width = 12)
+if (fixedphase==0){pdf('Figures/AQfigure.pdf', bg="transparent", height = 10, width = 12)}
+if (fixedphase==1){pdf('Figures/AQfigureFP.pdf', bg="transparent", height = 10, width = 12)}
+
   par(mar=c(0.1,0.1,0.1,0.1))
@@
 Suppressive interactions between neurons are ubiquitous in the nervous system, with normalization considered a canonical neuronal computation [@Carandini2011].
-Yet for decades the strength of suppression was treated as fixed, due to the observation that adapting to one stimulus does not decrease its suppressive potency [@Foley1997; @Freeman2002].
-This orthodoxy has been challenged by a series of innovative studies showing that normalization can be 'reweighted' by recent history [@Westrick2016; @Aschner2018; @Yiltiz2020].
-When pairs of stimuli are repeatedly presented together, their neural representations come to suppress each other more strongly.
-Far from being fixed, normalization is therefore a dynamic process that is continuously updated by the sensory environment.
-Our objectives were to measure the timecourse of these changes non-invasively in the human brain, compare them across distinct suppressive pathways, and determine whether they differ as a function of autistic traits.
+One consequence of normalization is that neurons tuned to different stimulus features modulate each others' firing, usually via a process of divisive suppression [@Heeger1992].
+For decades the strength of suppression was treated as fixed, due to the observation that adapting to one stimulus does not decrease its suppressive potency [@Foley1997; @Freeman2002].
+This orthodoxy has been challenged by a series of innovative studies proposing that normalization can be 'reweighted' by recent history [@Westrick2016; @Aschner2018; @Yiltiz2020].
+When pairs of stimuli are repeatedly presented together, their neural representations appear to suppress each other more strongly.
+Far from being fixed, normalization may therefore be a dynamic process that is continuously updated by the sensory environment.
+Our objectives were to measure the timecourse of changes in suppression non-invasively in the human brain, compare them across distinct anatomical pathways, and determine whether they differ as a function of autistic traits.
 
@@
 
-Multiple suppressive pathways have been identified in the visual system, including between stimuli differing in orientation [@Heeger1992; @Foley1994], eye-of-origin [@Legge1979; @Sengpiel1994] and spatial position [@Petrov2005; @Cannon1991].
+Multiple suppressive pathways have been identified in the visual system, including between stimuli differing in orientation [@Heeger1992; @Foley1994], eye-of-origin [@Legge1979; @Sengpiel1994; @Dougherty2019] and spatial position [@Petrov2005; @Cannon1991].
 At present there is evidence of normalization reweighting between stimuli with orthogonal orientations [@Aschner2018], and adjacent spatial positions [@Yiltiz2020].
@@
 Comparing monocular and dichoptic suppression permits any contribution of early pre-cortical factors to be isolated.
-This is because interocular suppression impacts in primary visual cortex, and bypasses any retinal and subcortical stages of processing that contribute to monocular suppression [@Li2005].
+This is because interocular suppression is generally thought to impact in primary visual cortex [though see @Dougherty2019], and bypasses any retinal and subcortical stages of processing that contribute to monocular suppression [@Li2005].
 
@@
 
+Following the suggestion of a reviewer, we conducted an alternative fixed-phase analysis, where the signal in each 1 second epoch was multiplied by a sine wave of appropriate frequency and phase instead of taking the Fourier transform.
+The results were similar to our main analysis, and can be viewed in the Figures subdirectory of the project code repository ([https://github.com/bakerdh/normreweight/tree/main/Figures files with the suffix 'FP'](https://github.com/bakerdh/normreweight/tree/main/Figures)).
+We also conducted simulations (also available in the code repository) to confirm that our analysis methods were not distorting the estimates of the suppression timecourse.
+In brief, although the 1 second sliding time window does blur the signals in time, these effects are largely negated by calculating the suppression ratio because the blur cancels out across the numerator and denominator.
+Overall these simulations give us confidence in the accuracy of our estimates of suppression dynamics.
+
 For Experiment 3, we performed source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm, implemented in Brainstorm [@Tadel2011].
@@
 Participants viewed arrays of flickering gratings of varying contrasts.
-In some conditions a single grating orientation was present flickering at 7Hz, whereas in other conditions a high contrast 'mask' was added at right angles to the target gratings, and flickering at 5Hz.
+In some conditions a single grating orientation was present flickering at 7Hz (the target), whereas in other conditions a high contrast 'mask' was added at right angles to the target gratings, and flickering at 5Hz.
 The left panel of Figure \@ref(fig:Pilotdata)a shows contrast response functions with and without the mask - the presence of the mask reduces the 7Hz response to the target (blue squares are below the black circles; significant main effect of mask contrast, F(1,99) = `r round(maskinganova1$ANOVA$F[2],digits=2)`, \emph{p} < 0.001).
@@
 
-```{r Pilotdata, fig.cap="Summary of pilot analysis of data from Vilidiate et al.
+```{r Pilotdata, out.width="40%", fig.cap="Summary of pilot analysis of data from Vilidiate et al.
 (2018).
@@
 Note the strong second harmonic components at 14Hz and 10Hz.
-Panel (c) shows timecourses of frequency-locked responses to a single stimulus (black) and the plaid stimulus (blue), compared to baseline (grey).
+Panel (c) shows timecourses of frequency-locked responses to a single stimulus (black) and the plaid stimulus (blue), compared to a baseline condition (grey) where no stimulus was shown at the target frequency.
 Panel (d) shows the timecourse of suppression at each frequency (7Hz, 5Hz, 14Hz, 10Hz) and their average (black curve).
-Points around y = 1.8 indicate a significantly increasing ratio.
+Points around y = 1.8 indicate a significantly increasing ratio (for the time window centred at each point).
 Error bars in panel (a) and shaded regions in panels (c,d) indicate ±1SE across N=100 participants, and grey rectangles indicate the timing of stimulus presentation.
@@
 
-knitr::include_graphics('Figures/VilidaiteData.pdf')
+if (fixedphase==0){knitr::include_graphics('Figures/VilidaiteData.pdf')}
+if (fixedphase==1){knitr::include_graphics('Figures/VilidaiteDataFP.pdf')}
 
@@
 The top panel of Figure \@ref(fig:Pilotdata)c shows the response at the target frequency (7Hz) to a single stimulus of 32% contrast (black), and the response at 7Hz when the 32% contrast mask is added (blue).
-For comparison, a baseline timecourse is also shown (grey), which was the response at 7Hz when a 5Hz stimulus was shown (therefore controlling for attention, blinking etc.).
+For comparison, a baseline timecourse is also shown (grey), which was the target response at 7Hz when a 5Hz mask stimulus was shown (therefore controlling for attention, blinking etc.).
 Analogous responses are shown at three other frequencies - the mask frequency (5Hz), and the second harmonics of both target and mask frequencies (14Hz, 10Hz), at which strong responses were also found (see spectra in Figure \@ref(fig:Pilotdata)b).
-The reduction in signal strength when the mask component is added illustrates the masking effect.
-
-Taking the ratio of the two timecourses to calculate a masking index reveals that at 7Hz masking increases steeply during the first two seconds of stimulus presentation, and then plateaus for several seconds (blue trace in Figure \@ref(fig:Pilotdata)d).
-A similar pattern is observed at 5Hz (red trace in Figure \@ref(fig:Pilotdata)d), as well as at the second harmonics, with some variability in the timecourse across frequencies; for example, at 5Hz suppression peaks at around 4 seconds.
+The reduction in signal strength when a second component is added at a different orientation and frequency illustrates the masking effect.
+Surprisingly there was sometimes substantial activity before and after the stimulus was presented, as is especially clear in the baseline condition shown by the grey curves in Figure \@ref(fig:Pilotdata)c.
+We think the most likely explanation for this is broadband noise from participant movement during the breaks between trials.
+Since it is approximately equal across conditions it appears to cancel out in the suppression ratios (Figure \@ref(fig:Pilotdata)d).
+
+Taking the ratio of the two timecourses (the target only timecourse and the target timecourse when a mask was present) to calculate a masking index reveals that for 7Hz targets masking increases steeply during the first two seconds of stimulus presentation, and then plateaus for several seconds (blue trace in Figure \@ref(fig:Pilotdata)d).
+A similar pattern is observed for the 5Hz mask (red trace in Figure \@ref(fig:Pilotdata)d), as well as at the second harmonics, with some variability in the timecourse across frequencies; for example, at 5Hz suppression peaks at around 4 seconds.
 The black trace shows the average masking ratio across all four frequencies, which rises steeply for just over two seconds and then stays approximately constant until stimulus offset.
@@
 a one-sided test).
-Points at y = 1.8 in Figure \@ref(fig:Pilotdata)d indicate time points where the ratio is significantly increasing, and occur mostly during the first 2 seconds of stimulus presentation.
+Points at y = 1.8 in Figure \@ref(fig:Pilotdata)d indicate time points where the ratio is significantly increasing (i.e.
+there is significantly more suppression 500ms after the time point than there was 500ms before it), and occur up until 2.27 seconds after stimulus presentation.
+We also calculated an overall effect size by comparing the amount of suppression during the first 1000ms following stimulus onset with that between 2000 and 3000ms, averaged across all temporal frequencies.
+This effect size (Cohen's *d* = `r round(piloteffectsize,digits=2)`) indicated a medium-sized effect.
 
@@
 Responses at 7Hz were weaker in the two masking conditions, showing significant changes in response amplitude for both the monocular (\emph{t} = `r round(t7a$statistic,digits=2)`, \emph{df} = `r t7a$parameter`, \emph{p} < 0.001) and dichoptic (\emph{t} = `r round(t7b$statistic,digits=2)`, \emph{df} = `r t7b$parameter`, \emph{p} < 0.001) masks.
-Dichoptic masking was significantly stronger than monocular masking (\emph{t} = `r round(t7c$statistic,digits=2)`, \emph{df} = `r t7c$parameter`, \emph{p} < 0.001), and a similar pattern was evident at 5Hz.
+Dichoptic masking was significantly stronger than monocular masking (\emph{t} = `r round(t7c$statistic,digits=2)`, \emph{df} = `r t7c$parameter`, \emph{p} < 0.001), and a similar pattern was evident at 5Hz (note that for this experiment, the terms 'target' and 'mask' are arbitrary, as each component was presented at a single contrast).
 
@@
 Panel (b) shows the Fourier amplitude spectrum for each condition, with clear peaks at 5Hz and 7Hz.
-Panels (c,d) show timecourses at each frequency for the baseline condition (black), and the monocular (blue) and dichoptic (red) masking conditions.
+Panels (c,d) show timecourses at each frequency for the target-only condition (black), and the monocular (blue) and dichoptic (red) masking conditions.
 Panels (e,f) show suppression ratios as a function of time for each mask type, with points around y = 0.8 indicating a significantly increasing ratio.
@@
 
-knitr::include_graphics('Figures/EEGdata.pdf')
+if (fixedphase==0){knitr::include_graphics('Figures/EEGdata.pdf')}
+if (fixedphase==1){knitr::include_graphics('Figures/EEGdataFP.pdf')}
 
@@
 The ratio of target only to target + mask conditions increased over time (Figure \@ref(fig:EEGdata)e,f) for both mask types.
-At 5Hz the increase in masking continued over the first 5 seconds of stimulus presentation (Figure \@ref(fig:EEGdata)e; points at y = 0.8 indicate significantly increasing suppression), whereas at 7Hz the increase occurred primarily during the first second after onset (Figure \@ref(fig:EEGdata)f).
+At 5Hz the increase in masking continued for as long as 5 seconds of stimulus presentation in the monocular condition (Figure \@ref(fig:EEGdata)e; points at y = 0.8 indicate significantly increasing suppression, which continue until 5.1s (mon) or 4.2s (dich)), whereas at 7Hz the increase occurred primarily during the first 1.5 seconds after onset (Figure \@ref(fig:EEGdata)f; substantial clusters up to 1.5s (mon) and 1.7s (dich)).
 These differences across frequency are consistent with the pilot data (see Figure \@ref(fig:Pilotdata)d).
 Both monocular and dichoptic masks produced similar timecourses of suppression.
+We calculated an overall effect size comparing suppression in the first 1000ms after stimulus onset to the time window from 3000-4000ms, pooling over frequency and mask type.
+This had a value of *d* = `r round(EEGeffectsize,digits=2)`.
 Overall, this second study confirmed that normalization increases during the first few seconds of a steady-state trial, and extends this finding to dichoptic mask arrangements.
@@
 
-knitr::include_graphics('Figures/MEGdata.pdf')
+if (fixedphase==0){knitr::include_graphics('Figures/MEGdata.pdf')}
+if (fixedphase==1){knitr::include_graphics('Figures/MEGdataFP.pdf')}
 
@@
 Responses from the most responsive V1 vertex showed a similar timecourse to those of the EEG experiments at both frequencies (Figure \@ref(fig:MEGdata)c,d), and showed increasing suppression during the first few seconds of stimulus presentation (Figure \@ref(fig:MEGdata)e,f).
-The normalization reweighting effect was again clearest at 5Hz, especially for the dichoptic condition (red curve in Figure \@ref(fig:MEGdata)e).
+The normalization reweighting effect was again clearest at 5Hz, especially for the dichoptic condition (red curve in Figure \@ref(fig:MEGdata)e), which increased until 2.5s.
 This confirms that the reweighting effects can occur as early as primary visual cortex, consistent with findings from neurophysiology [@Aschner2018].
-However the data are more variable than for our EEG experiments, and had fewer significant clusters, owing to the smaller sample size for this dataset.
+However the data are more variable than for our EEG experiments, and had fewer significant clusters, perhaps owing to a power reduction caused by the smaller sample size for this dataset and greater heterogeneity across frequency.
+When pooling effects over frequency and condition, the overall effect size (*d* = `r round(MEGeffectsize,digits=2)`) was near zero.
+
+Intermodulation responses, at sums and differences of different stimulation frequencies, are another marker of nonlinear interaction [@Regan1988; @Tsai2012; @Cunningham2017].
+We also calculated the timecourse of the sum intermodulation terms (at 12Hz) in our data sets (the difference terms at 2Hz were negligible).
+Figure \@ref(fig:IMplot) shows that for both EEG experiments, the intermodulation term increases during the first 1 second of stimulus presentation and then remains approximately constant.
+The intermodulation response in the MEG data was less clear, consistent with the spectra shown in Figure \@ref(fig:MEGdata)b.
+It seems unlikely that intermodulation terms are useful for monitoring the timecourse of normalization reweighting, and indeed they may derive from a nonlinear process other than suppression, such as exponentiation and signal combination [@Regan1988].
+Previous work has identified situations in which suppression is constant, but the intermodulation term changes substantially between conditions depending on the extent of signal pooling [@Cunningham2017].
+
+```{r IMplot, fig.cap="Timecourse of the sum intermodulation term at 12Hz across three experiments.
+In both EEG experiments, the intermodulation response increases during the first 1 second of stimulus presentation.
+Responses are calculated as a proportional increase relative to the target-only conditions (where the intermodulation response is absent), for direct comparison with the suppression ratios in Figures 1-3.
+Shaded regions indicate ±1SE.", fig.align="center", echo=FALSE}
+
+knitr::include_graphics('Figures/IMfigure.pdf')
+
+```
+
+To investigate whether normalization reweighting effects differ with respect to autistic traits, we then split each dataset (averaged across temporal frequency) using median AQ score (for the EEG experiments) or according to diagnostic group (autism vs controls) for the MEG data.
+Figure \@ref(fig:AQanalysis)a-c shows distributions of AQ scores for each experiment, and indicates for the pilot and EEG data which participants were in the high (purple) and low (green) AQ groups.
+The median AQ scores were `r round(median(pilotAQ),digits=0)` for the pilot data, and `r median(allAQ)` for the EEG data.
+In the MEG experiment, AQ scores for the autism group (mean `r round(mean(MEG_A),digits=1)`) and the control group (mean `r round(mean(MEG_C),digits=1)`) were significantly different (*t* = `r format(round(t$statistic,digits=2),nsmall=2)`, *df* = `r round(t$parameter,digits=1)`, *p* < 0.001), with minimal overlap (one participant with an autism diagnosis had an AQ score marginally lower than the highest AQ scores from the control group).
+These distributions are consistent with previous results for AQ [@Baron-Cohen2001].
 
@@
 
-knitr::include_graphics('Figures/AQfigure.pdf')
+if (fixedphase==0){knitr::include_graphics('Figures/AQfigure.pdf')}
+if (fixedphase==1){knitr::include_graphics('Figures/AQfigureFP.pdf')}
 
 ```
-
-To investigate whether normalization reweighting effects differ with respect to autistic traits, we then split each dataset (averaged across temporal frequency) using median AQ score (for the EEG experiments) or according to diagnostic group (autism vs controls) for the MEG data.
-Figure \@ref(fig:AQanalysis)a-c shows distributions of AQ scores for each experiment, and indicates for the pilot and EEG data which participants were in the high (purple) and low (green) AQ groups.
-The median AQ scores were `r round(median(pilotAQ),digits=0)` for the pilot data, and `r median(allAQ)` for the EEG data.
-In the MEG experiment, AQ scores for the autism group (mean `r round(mean(MEG_A),digits=1)`) and the control group (mean `r round(mean(MEG_C),digits=1)`) were significantly different (*t* = `r format(round(t$statistic,digits=2),nsmall=2)`, *df* = `r round(t$parameter,digits=1)`, *p* < 0.001), with minimal overlap (one participant with an autism diagnosis had an AQ score marginally lower than the highest AQ scores from the control group).
-These distributions are consistent with previous results for AQ [@Baron-Cohen2001].
 
@@
 Suppression increased significantly during the first 2-5 seconds of stimulus presentation, though with some variation across temporal frequency.
+Relative to the first 1 second of stimulus presentation, the increase in suppression after 3 seconds constituted an effect size of *d* = `r round(piloteffectsize,digits=2)` for the pilot data, *d* = `r round(EEGeffectsize,digits=2)` for our new EEG experiment, and *d* = `r round(MEGeffectsize,digits=2)` for our MEG experiment (pooled across temporal frequency and monocular and dichoptic conditions).
 Reweighting had a similar timecourse for monocular and dichoptic stimulus presentation, and was apparent as early as V1.
@@
 
-The relationship between normalization reweighting and other forms of visual plasticity is currently unclear.
+The relationship between normalization reweighting and other forms of visual plasticity and adaptation is currently unclear.
 One phenomenon that might be closely related to our dichoptic effect is the change in interocular suppression that occurs when one eye is patched for a period of time [@Lunghi2011].

### 2023-07-31 manuscript.tex
Implemented reviewer suggestions

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
+\urlstyle{same}
 \hypersetup{
@@
 
-Suppressive interactions between neurons are ubiquitous in the nervous system, with normalization considered a canonical neuronal computation (Carandini and Heeger, 2011).
-Yet for decades the strength of suppression was treated as fixed, due to the observation that adapting to one stimulus does not decrease its suppressive potency (Foley and Chen, 1997; Freeman et al., 2002).
-This orthodoxy has been challenged by a series of innovative studies showing that normalization can be `reweighted' by recent history (Aschner et al., 2018; Westrick et al., 2016; Yiltiz et al., 2020).
-When pairs of stimuli are repeatedly presented together, their neural representations come to suppress each other more strongly.
-Far from being fixed, normalization is therefore a dynamic process that is continuously updated by the sensory environment.
-Our objectives were to measure the timecourse of these changes non-invasively in the human brain, compare them across distinct suppressive pathways, and determine whether they differ as a function of autistic traits.
+Suppressive interactions between neurons are ubiquitous in the nervous system, with normalization considered a canonical neuronal computation (\protect\hyperlink{ref-Carandini2011}{Carandini \& Heeger, 2011}).
+One consequence of normalization is that neurons tuned to different stimulus features modulate each others' firing, usually via a process of divisive suppression (\protect\hyperlink{ref-Heeger1992}{Heeger, 1992}).
+For decades the strength of suppression was treated as fixed, due to the observation that adapting to one stimulus does not decrease its suppressive potency (\protect\hyperlink{ref-Foley1997}{Foley \& Chen, 1997}; \protect\hyperlink{ref-Freeman2002}{Freeman et al., 2002}).
+This orthodoxy has been challenged by a series of innovative studies proposing that normalization can be `reweighted' by recent history (\protect\hyperlink{ref-Aschner2018}{Aschner et al., 2018}; \protect\hyperlink{ref-Westrick2016}{Westrick et al., 2016}; \protect\hyperlink{ref-Yiltiz2020}{Yiltiz et al., 2020}).
+When pairs of stimuli are repeatedly presented together, their neural representations appear to suppress each other more strongly.
+Far from being fixed, normalization may therefore be a dynamic process that is continuously updated by the sensory environment.
+Our objectives were to measure the timecourse of changes in suppression non-invasively in the human brain, compare them across distinct anatomical pathways, and determine whether they differ as a function of autistic traits.
 
-Plastic changes within the visual system occur over multiple timescales (see Webster, 2015 for a recent review).
-Cortical forms of adaptation to cues such as stimulus contrast (Blakemore and Campbell, 1969), orientation (Gibson and Radner, 1937) and motion (Mather et al., 2008) can be observed within a few seconds, but also build up over durations on the order of minutes (Greenlee et al., 1991).
-Other types of adaptation have been identified where changes occur over longer time periods, such as several hours (Kwon et al., 2009) or days (Haak et al., 2014).
-Previous normalization reweighting studies involved adapting sequences of around 40 -- 60s (Aschner et al., 2018; Yiltiz et al., 2020), but in principle reweighting might occur faster than this, consistent with other types of contrast adaptation.
+Plastic changes within the visual system occur over multiple timescales (see \protect\hyperlink{ref-Webster2015}{Webster, 2015} for a recent review).
+Cortical forms of adaptation to cues such as stimulus contrast (\protect\hyperlink{ref-Blakemore1969}{Blakemore \& Campbell, 1969}), orientation (\protect\hyperlink{ref-Gibson1937}{Gibson \& Radner, 1937}) and motion (\protect\hyperlink{ref-Mather2008}{Mather et al., 2008}) can be observed within a few seconds, but also build up over durations on the order of minutes (\protect\hyperlink{ref-Greenlee1991}{Greenlee et al., 1991}).
+Other types of adaptation have been identified where changes occur over longer time periods, such as several hours (\protect\hyperlink{ref-Kwon2009}{Kwon et al., 2009}) or days (\protect\hyperlink{ref-Haak2014}{Haak et al., 2014}).
+Previous normalization reweighting studies involved adapting sequences of around 40 -- 60s (\protect\hyperlink{ref-Aschner2018}{Aschner et al., 2018}; \protect\hyperlink{ref-Yiltiz2020}{Yiltiz et al., 2020}), but in principle reweighting might occur faster than this, consistent with other types of contrast adaptation.
 
-Multiple suppressive pathways have been identified in the visual system, including between stimuli differing in orientation (Foley, 1994; Heeger, 1992), eye-of-origin (Legge, 1979; Sengpiel and Blakemore, 1994) and spatial position (Cannon and Fullenkamp, 1991; Petrov, 2005).
-At present there is evidence of normalization reweighting between stimuli with orthogonal orientations (Aschner et al., 2018), and adjacent spatial positions (Yiltiz et al., 2020).
-We anticipated that interocular suppression should also be subject to reweighting, but that there might be differences in the dynamics across suppressive pathways (Li et al., 2005; e.g.
-Meese and Baker, 2009; Sengpiel and Vorobyov, 2005).
+Multiple suppressive pathways have been identified in the visual system, including between stimuli differing in orientation (\protect\hyperlink{ref-Foley1994}{Foley, 1994}; \protect\hyperlink{ref-Heeger1992}{Heeger, 1992}), eye-of-origin (\protect\hyperlink{ref-Dougherty2019}{Dougherty et al., 2019}; \protect\hyperlink{ref-Legge1979}{Legge, 1979}; \protect\hyperlink{ref-Sengpiel1994}{Sengpiel \& Blakemore, 1994}) and spatial position (\protect\hyperlink{ref-Cannon1991}{Cannon \& Fullenkamp, 1991}; \protect\hyperlink{ref-Petrov2005}{Petrov, 2005}).
+At present there is evidence of normalization reweighting between stimuli with orthogonal orientations (\protect\hyperlink{ref-Aschner2018}{Aschner et al., 2018}), and adjacent spatial positions (\protect\hyperlink{ref-Yiltiz2020}{Yiltiz et al., 2020}).
+We anticipated that interocular suppression should also be subject to reweighting, but that there might be differences in the dynamics across suppressive pathways (\protect\hyperlink{ref-Li2005}{Li et al., 2005}; e.g.
+\protect\hyperlink{ref-Meese2009}{Meese \& Baker, 2009}; \protect\hyperlink{ref-Sengpiel2005}{Sengpiel \& Vorobyov, 2005}).
 Comparing monocular and dichoptic suppression permits any contribution of early pre-cortical factors to be isolated.
-This is because interocular suppression impacts in primary visual cortex, and bypasses any retinal and subcortical stages of processing that contribute to monocular suppression (Li et al., 2005).
+This is because interocular suppression is generally thought to impact in primary visual cortex (though see \protect\hyperlink{ref-Dougherty2019}{Dougherty et al., 2019}), and bypasses any retinal and subcortical stages of processing that contribute to monocular suppression (\protect\hyperlink{ref-Li2005}{Li et al., 2005}).
 
-Atypical sensory experience, including hypersensitivity to loud sounds, bright lights and strong odours or flavours, is widely reported by individuals on the autism spectrum (MacLennan et al., 2022; Simmons et al., 2009), but the causal mechanisms remain unclear.
-Fundamental measures of sensitivity including visual acuity (Tavassoli et al., 2011), contrast sensitivity (Koh et al., 2010), and audiometric performance (Rosenhall et al., 1999) are not consistently different from neurotypical controls.
-Theoretical accounts of sensory differences in autism have proposed that the balance of inhibition and excitation may be disrupted (Rosenberg et al., 2015; Rubenstein and Merzenich, 2003), yet the evidence is currently inconclusive (Sandhu et al., 2020; e.g.
-Schallmo et al., 2020; Van de Cruys et al., 2018).
-Our recent work identified an autism-related difference using steady-state EEG (Vilidaite et al., 2018), in which nonlinear (second harmonic) responses were weaker, implicating atypical suppression in autism.
+Atypical sensory experience, including hypersensitivity to loud sounds, bright lights and strong odours or flavours, is widely reported by individuals on the autism spectrum (\protect\hyperlink{ref-MacLennan2022}{MacLennan et al., 2022}; \protect\hyperlink{ref-Simmons2009}{Simmons et al., 2009}), but the causal mechanisms remain unclear.
+Fundamental measures of sensitivity including visual acuity (\protect\hyperlink{ref-Tavassoli2011}{Tavassoli et al., 2011}), contrast sensitivity (\protect\hyperlink{ref-Koh2010}{Koh et al., 2010}), and audiometric performance (\protect\hyperlink{ref-Rosenhall1999}{Rosenhall et al., 1999}) are not consistently different from neurotypical controls.
+Theoretical accounts of sensory differences in autism have proposed that the balance of inhibition and excitation may be disrupted (\protect\hyperlink{ref-Rosenberg2015}{Rosenberg et al., 2015}; \protect\hyperlink{ref-Rubenstein2003}{Rubenstein \& Merzenich, 2003}), yet the evidence is currently inconclusive (\protect\hyperlink{ref-Sandhu2020}{Sandhu et al., 2020}; e.g.
+\protect\hyperlink{ref-Schallmo2020}{Schallmo et al., 2020}; \protect\hyperlink{ref-VandeCruys2018}{Van de Cruys et al., 2018}).
+Our recent work identified an autism-related difference using steady-state EEG (\protect\hyperlink{ref-Vilidaite2018}{Vilidaite et al., 2018}), in which nonlinear (second harmonic) responses were weaker, implicating atypical suppression in autism.
 
@@
 Experiment 1 was completed by 100 adult participants (32 male, 68 female; mean age 21.9) in early 2015, and first reported by Vilidaite et al.
-(2018).
+(\protect\hyperlink{ref-Vilidaite2018}{2018}).
 Here we reanalysed the dataset, and report the results of masking conditions not previously published.
@@
 We also obtained structural MRI scans using a 3 Tesla Siemens Magnetom Prisma scanner to aid in source localisation.
-Two participants were not available for MRI scans, so we used the MNI ICBM152 template brain (Fonov et al., 2011) for these individuals.
+Two participants were not available for MRI scans, so we used the MNI ICBM152 template brain (\protect\hyperlink{ref-Fonov2011}{Fonov et al., 2011}) for these individuals.
 
@@
 
-Participants also completed either the short AQ (Hoekstra et al., 2011) in Experiment 1, or the full AQ (Baron-Cohen et al., 2001) in Experiments 2 and 3.
+Participants also completed either the short AQ (\protect\hyperlink{ref-Hoekstra2011}{Hoekstra et al., 2011}) in Experiment 1, or the full AQ (\protect\hyperlink{ref-Baron-Cohen2001}{Baron-Cohen et al., 2001}) in Experiments 2 and 3.
 For comparison across experiments, we rescaled the short AQ to the same range as the full AQ (0-50).
-In Experiments 2 and 3, the sensory perception quotient (SPQ) questionnaire (Tavassoli et al., 2014) was also completed.
+In Experiments 2 and 3, the sensory perception quotient (SPQ) questionnaire (\protect\hyperlink{ref-Tavassoli2014}{Tavassoli et al., 2014}) was also completed.
 
@@
 
-EEG data from Experiments 1 and 2 were first imported into Matlab using components of the EEGlab toolbox (Delorme and Makeig, 2004), and converted into a compressed ASCII format.
+EEG data from Experiments 1 and 2 were first imported into Matlab using components of the EEGlab toolbox (\protect\hyperlink{ref-Delorme2004}{Delorme \& Makeig, 2004}), and converted into a compressed ASCII format.
 Primary data analysis was then conducted using a bespoke \emph{R} script.
 In brief, we epoched each trial and extracted the average timecourse across four occipital electrodes (\emph{Oz}, \emph{POz}, \emph{O1} and \emph{O2}), and then calculated the Fourier transform of this average waveform.
-We excluded trials for which the Mahalanobis distance of the complex Fourier components exceeded 3 (for details see Baker, 2021).
+We excluded trials for which the Mahalanobis distance of the complex Fourier components exceeded 3 (for details see \protect\hyperlink{ref-Baker2021}{Baker, 2021}).
 This resulted in 0.25\% of trials being excluded for Experiment 1, and 4.51\% of trials for Experiment 2.
@@
 
-For Experiment 3, we performed source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm, implemented in Brainstorm (Tadel et al., 2011).
-Structural MRI scans were processed using Freesurfer (Dale et al., 1999) to generate a 3D mesh of the head and brain, and we calculated source weights for each block with reference to a 5-minute empty room recording, usually recorded on the day of the experiment.
+Following the suggestion of a reviewer, we conducted an alternative fixed-phase analysis, where the signal in each 1 second epoch was multiplied by a sine wave of appropriate frequency and phase instead of taking the Fourier transform.
+The results were similar to our main analysis, and can be viewed in the Figures subdirectory of the project code repository (\href{https://github.com/bakerdh/normreweight/tree/main/Figures}{https://github.com/bakerdh/normreweight/tree/main/Figures files with the suffix `FP'}).
+We also conducted simulations (also available in the code repository) to confirm that our analysis methods were not distorting the estimates of the suppression timecourse.
+In brief, although the 1 second sliding time window does blur the signals in time, these effects are largely negated by calculating the suppression ratio because the blur cancels out across the numerator and denominator.
+Overall these simulations give us confidence in the accuracy of our estimates of suppression dynamics.
+
+For Experiment 3, we performed source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm, implemented in Brainstorm (\protect\hyperlink{ref-Tadel2011}{Tadel et al., 2011}).
+Structural MRI scans were processed using Freesurfer (\protect\hyperlink{ref-Dale1999}{Dale et al., 1999}) to generate a 3D mesh of the head and brain, and we calculated source weights for each block with reference to a 5-minute empty room recording, usually recorded on the day of the experiment.
 The matrix of source weights for each block was used in a custom Matlab script to extract signals from V1, identified using the probabilistic maps of Wang et al.
-(2015).
+(\protect\hyperlink{ref-Wang2015}{2015}).
 These signals were then imported into R for the main analysis, which was consistent with the EEG analysis described above.
@@
 
-To make comparisons between groups of participants across time, we used a non-parametric cluster correction technique (Maris and Oostenveld, 2007) based on t-tests.
+To make comparisons between groups of participants across time, we used a non-parametric cluster correction technique (\protect\hyperlink{ref-Maris2007}{Maris \& Oostenveld, 2007}) based on t-tests.
 Clusters were identified as temporally adjacent observations that were all statistically significant, and a summed t-value was calculated for each cluster.
@@
 We began by reanalysing data from a steady-state visually evoked potential (SSVEP) experiment reported by Vilidaite et al.
-(2018).
+(\protect\hyperlink{ref-Vilidaite2018}{2018}).
 Participants viewed arrays of flickering gratings of varying contrasts.
-In some conditions a single grating orientation was present flickering at 7Hz, whereas in other conditions a high contrast `mask' was added at right angles to the target gratings, and flickering at 5Hz.
+In some conditions a single grating orientation was present flickering at 7Hz (the target), whereas in other conditions a high contrast `mask' was added at right angles to the target gratings, and flickering at 5Hz.
 The left panel of Figure \ref{fig:Pilotdata}a shows contrast response functions with and without the mask - the presence of the mask reduces the 7Hz response to the target (blue squares are below the black circles; significant main effect of mask contrast, F(1,99) = 26.52, \emph{p} \textless{} 0.001).
 Similarly, the right panel of Figure \ref{fig:Pilotdata}a shows that the 5Hz response to the mask was itself suppressed by the presence of high contrast targets (main effect of target contrast on the mask response, F(2.92,288.63) = 46.77, \emph{p} \textless{} 0.001; note that the data from the masking conditions were not reported by Vilidaite et al.
-(2018)).
+(\protect\hyperlink{ref-Vilidaite2018}{2018})).
 At both frequencies, responses were localised to the occipital pole (see insets).
@@
 
-{\centering \includegraphics{Figures/VilidaiteData}
+{\centering \includegraphics[width=0.4\linewidth]{Figures/VilidaiteData}
 
@@
 The top panel of Figure \ref{fig:Pilotdata}c shows the response at the target frequency (7Hz) to a single stimulus of 32\% contrast (black), and the response at 7Hz when the 32\% contrast mask is added (blue).
-For comparison, a baseline timecourse is also shown (grey), which was the response at 7Hz when a 5Hz stimulus was shown (therefore controlling for attention, blinking etc.).
+For comparison, a baseline timecourse is also shown (grey), which was the target response at 7Hz when a 5Hz mask stimulus was shown (therefore controlling for attention, blinking etc.).
 Analogous responses are shown at three other frequencies - the mask frequency (5Hz), and the second harmonics of both target and mask frequencies (14Hz, 10Hz), at which strong responses were also found (see spectra in Figure \ref{fig:Pilotdata}b).
-The reduction in signal strength when the mask component is added illustrates the masking effect.
+The reduction in signal strength when a second component is added at a different orientation and frequency illustrates the masking effect.
+Surprisingly there was sometimes substantial activity before and after the stimulus was presented, as is especially clear in the baseline condition shown by the grey curves in Figure \ref{fig:Pilotdata}c.~We think the most likely explanation for this is broadband noise from participant movement during the breaks between trials.
+Since it is approximately equal across conditions it appears to cancel out in the suppression ratios (Figure \ref{fig:Pilotdata}d).
 
-Taking the ratio of the two timecourses to calculate a masking index reveals that at 7Hz masking increases steeply during the first two seconds of stimulus presentation, and then plateaus for several seconds (blue trace in Figure \ref{fig:Pilotdata}d).
-A similar pattern is observed at 5Hz (red trace in Figure \ref{fig:Pilotdata}d), as well as at the second harmonics, with some variability in the timecourse across frequencies; for example, at 5Hz suppression peaks at around 4 seconds.
+Taking the ratio of the two timecourses (the target only timecourse and the target timecourse when a mask was present) to calculate a masking index reveals that for 7Hz targets masking increases steeply during the first two seconds of stimulus presentation, and then plateaus for several seconds (blue trace in Figure \ref{fig:Pilotdata}d).
+A similar pattern is observed for the 5Hz mask (red trace in Figure \ref{fig:Pilotdata}d), as well as at the second harmonics, with some variability in the timecourse across frequencies; for example, at 5Hz suppression peaks at around 4 seconds.
 The black trace shows the average masking ratio across all four frequencies, which rises steeply for just over two seconds and then stays approximately constant until stimulus offset.
 We conducted cluster-corrected t-tests between ratios separated by 1000ms, testing for an increase in suppression ratio across time (i.e.~a one-sided test).
-Points at y = 1.8 in Figure \ref{fig:Pilotdata}d indicate time points where the ratio is significantly increasing, and occur mostly during the first 2 seconds of stimulus presentation.
+Points at y = 1.8 in Figure \ref{fig:Pilotdata}d indicate time points where the ratio is significantly increasing (i.e.~there is significantly more suppression 500ms after the time point than there was 500ms before it), and occur up until 2.27 seconds after stimulus presentation.
+We also calculated an overall effect size by comparing the amount of suppression during the first 1000ms following stimulus onset with that between 2000 and 3000ms, averaged across all temporal frequencies.
+This effect size (Cohen's \emph{d} = 0.49) indicated a medium-sized effect.
 
@@
 These had a similar overall design to the Vilidaite et al.
-(2018) study, with some small changes intended to optimise the study (see Methods).
+(\protect\hyperlink{ref-Vilidaite2018}{2018}) study, with some small changes intended to optimise the study (see Methods).
 The key differences were that we used shorter trials (because there were few changes in the latter part of the trials shown in Figure \ref{fig:Pilotdata}d), and also focussed all trials into a smaller number of conditions, such that each participant contributed 48 repetitions (288 seconds of data) to each of 4 conditions.
@@
 Responses at 7Hz were weaker in the two masking conditions, showing significant changes in response amplitude for both the monocular (\emph{t} = 7.56, \emph{df} = 87, \emph{p} \textless{} 0.001) and dichoptic (\emph{t} = 11.35, \emph{df} = 87, \emph{p} \textless{} 0.001) masks.
-Dichoptic masking was significantly stronger than monocular masking (\emph{t} = 7.96, \emph{df} = 87, \emph{p} \textless{} 0.001), and a similar pattern was evident at 5Hz.
+Dichoptic masking was significantly stronger than monocular masking (\emph{t} = 7.96, \emph{df} = 87, \emph{p} \textless{} 0.001), and a similar pattern was evident at 5Hz (note that for this experiment, the terms `target' and `mask' are arbitrary, as each component was presented at a single contrast).
 
@@
 The ratio of target only to target + mask conditions increased over time (Figure \ref{fig:EEGdata}e,f) for both mask types.
-At 5Hz the increase in masking continued over the first 5 seconds of stimulus presentation (Figure \ref{fig:EEGdata}e; points at y = 0.8 indicate significantly increasing suppression), whereas at 7Hz the increase occurred primarily during the first second after onset (Figure \ref{fig:EEGdata}f).
+At 5Hz the increase in masking continued for as long as 5 seconds of stimulus presentation in the monocular condition (Figure \ref{fig:EEGdata}e; points at y = 0.8 indicate significantly increasing suppression, which continue until 5.1s (mon) or 4.2s (dich)), whereas at 7Hz the increase occurred primarily during the first 1.5 seconds after onset (Figure \ref{fig:EEGdata}f; substantial clusters up to 1.5s (mon) and 1.7s (dich)).
 These differences across frequency are consistent with the pilot data (see Figure \ref{fig:Pilotdata}d).
 Both monocular and dichoptic masks produced similar timecourses of suppression.
+We calculated an overall effect size comparing suppression in the first 1000ms after stimulus onset to the time window from 3000-4000ms, pooling over frequency and mask type.
+This had a value of \emph{d} = 0.33.
 Overall, this second study confirmed that normalization increases during the first few seconds of a steady-state trial, and extends this finding to dichoptic mask arrangements.
@@
 Half of the participants had a diagnosis of autism, and the remainder were age- and gender-matched controls.
-Source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm (Van Veen et al., 1997) showed strong localisation of steady-state signals at the occipital pole (see Figure \ref{fig:MEGdata}a), and in the Fourier domain (Figure \ref{fig:MEGdata}b).
+Source localisation using a linearly constrained minimum variance (LCMV) beamformer algorithm (\protect\hyperlink{ref-VanVeen1997}{Van Veen et al., 1997}) showed strong localisation of steady-state signals at the occipital pole (see Figure \ref{fig:MEGdata}a), and in the Fourier domain (Figure \ref{fig:MEGdata}b).
 Responses from the most responsive V1 vertex showed a similar timecourse to those of the EEG experiments at both frequencies (Figure \ref{fig:MEGdata}c,d), and showed increasing suppression during the first few seconds of stimulus presentation (Figure \ref{fig:MEGdata}e,f).
-The normalization reweighting effect was again clearest at 5Hz, especially for the dichoptic condition (red curve in Figure \ref{fig:MEGdata}e).
-This confirms that the reweighting effects can occur as early as primary visual cortex, consistent with findings from neurophysiology (Aschner et al., 2018).
-However the data are more variable than for our EEG experiments, and had fewer significant clusters, owing to the smaller sample size for this dataset.
+The normalization reweighting effect was again clearest at 5Hz, especially for the dichoptic condition (red curve in Figure \ref{fig:MEGdata}e), which increased until 2.5s.
+This confirms that the reweighting effects can occur as early as primary visual cortex, consistent with findings from neurophysiology (\protect\hyperlink{ref-Aschner2018}{Aschner et al., 2018}).
+However the data are more variable than for our EEG experiments, and had fewer significant clusters, perhaps owing to a power reduction caused by the smaller sample size for this dataset and greater heterogeneity across frequency.
+When pooling effects over frequency and condition, the overall effect size (\emph{d} = 0.03) was near zero.
+
+Intermodulation responses, at sums and differences of different stimulation frequencies, are another marker of nonlinear interaction (\protect\hyperlink{ref-Cunningham2017}{Cunningham et al., 2017}; \protect\hyperlink{ref-Regan1988}{Regan \& Regan, 1988}; \protect\hyperlink{ref-Tsai2012}{Tsai et al., 2012}).
+We also calculated the timecourse of the sum intermodulation terms (at 12Hz) in our data sets (the difference terms at 2Hz were negligible).
+Figure \ref{fig:IMplot} shows that for both EEG experiments, the intermodulation term increases during the first 1 second of stimulus presentation and then remains approximately constant.
+The intermodulation response in the MEG data was less clear, consistent with the spectra shown in Figure \ref{fig:MEGdata}b.
+It seems unlikely that intermodulation terms are useful for monitoring the timecourse of normalization reweighting, and indeed they may derive from a nonlinear process other than suppression, such as exponentiation and signal combination (\protect\hyperlink{ref-Regan1988}{Regan \& Regan, 1988}).
+Previous work has identified situations in which suppression is constant, but the intermodulation term changes substantially between conditions depending on the extent of signal pooling (\protect\hyperlink{ref-Cunningham2017}{Cunningham et al., 2017}).
+
+\begin{figure}
+
+{\centering \includegraphics{Figures/IMfigure}
+
+}
+
+\caption{Timecourse of the sum intermodulation term at 12Hz across three experiments.
+In both EEG experiments, the intermodulation response increases during the first 1 second of stimulus presentation.
+Responses are calculated as a proportional increase relative to the target-only conditions (where the intermodulation response is absent), for direct comparison with the suppression ratios in Figures 1-3.
+Shaded regions indicate ±1SE.}\label{fig:IMplot}
+\end{figure}
+
+To investigate whether normalization reweighting effects differ with respect to autistic traits, we then split each dataset (averaged across temporal frequency) using median AQ score (for the EEG experiments) or according to diagnostic group (autism vs controls) for the MEG data.
+Figure \ref{fig:AQanalysis}a-c shows distributions of AQ scores for each experiment, and indicates for the pilot and EEG data which participants were in the high (purple) and low (green) AQ groups.
+The median AQ scores were 14 for the pilot data, and 18 for the EEG data.
+In the MEG experiment, AQ scores for the autism group (mean 36.1) and the control group (mean 16.7) were significantly different (\emph{t} = 6.00, \emph{df} = 14.2, \emph{p} \textless{} 0.001), with minimal overlap (one participant with an autism diagnosis had an AQ score marginally lower than the highest AQ scores from the control group).
+These distributions are consistent with previous results for AQ (\protect\hyperlink{ref-Baron-Cohen2001}{Baron-Cohen et al., 2001}).
 
@@
 
-To investigate whether normalization reweighting effects differ with respect to autistic traits, we then split each dataset (averaged across temporal frequency) using median AQ score (for the EEG experiments) or according to diagnostic group (autism vs controls) for the MEG data.
-Figure \ref{fig:AQanalysis}a-c shows distributions of AQ scores for each experiment, and indicates for the pilot and EEG data which participants were in the high (purple) and low (green) AQ groups.
-The median AQ scores were 14 for the pilot data, and 18 for the EEG data.
-In the MEG experiment, AQ scores for the autism group (mean 36.1) and the control group (mean 16.7) were significantly different (\emph{t} = 6.00, \emph{df} = 14.2, \emph{p} \textless{} 0.001), with minimal overlap (one participant with an autism diagnosis had an AQ score marginally lower than the highest AQ scores from the control group).
-These distributions are consistent with previous results for AQ (Baron-Cohen et al., 2001).
-
-We compared the timecourse of suppression between groups using a nonparametric cluster correction approach (Maris and Oostenveld, 2007) to control the type I error rate.
+We compared the timecourse of suppression between groups using a nonparametric cluster correction approach (\protect\hyperlink{ref-Maris2007}{Maris \& Oostenveld, 2007}) to control the type I error rate.
 Significant clusters are indicated at y = 0.8 in panels d-h of Figure \ref{fig:AQanalysis}.
@@
 Suppression increased significantly during the first 2-5 seconds of stimulus presentation, though with some variation across temporal frequency.
+Relative to the first 1 second of stimulus presentation, the increase in suppression after 3 seconds constituted an effect size of \emph{d} = 0.49 for the pilot data, \emph{d} = 0.33 for our new EEG experiment, and \emph{d} = 0.03 for our MEG experiment (pooled across temporal frequency and monocular and dichoptic conditions).
 Reweighting had a similar timecourse for monocular and dichoptic stimulus presentation, and was apparent as early as V1.
@@
 These differences may be a consequence of visual channels with different temporal tuning interacting with the stimulation frequency, as well as any nonlinearities that govern suppression.
-Or there could be an asymmetry, whereby the relative temporal frequency between the two stimulus components affects the character of suppression (Liza and Ray, 2022).
+Or there could be an asymmetry, whereby the relative temporal frequency between the two stimulus components affects the character of suppression (\protect\hyperlink{ref-Liza2022}{Liza \& Ray, 2022}).
 We hope to be able to model these effects in the future, for example by using dynamic models of early vision that incorporate time-lagged gain control (e.g.
-Zhou et al., 2019).
+\protect\hyperlink{ref-Zhou2019}{Zhou et al., 2019}).
 
@@
 This is important, because the dichoptic arrangement bypasses early stages of processing before the cortex (e.g.~the retina and lateral geniculate nucleus).
-It suggests that the dynamic increases in suppression occur in the cortex, consistent with our MEG data that find evidence of reweighting in V1 (see Fig \ref{fig:MEGdata}), and with previous neurophysiological work (Aschner et al., 2018).
+It suggests that the dynamic increases in suppression occur in the cortex, consistent with our MEG data that find evidence of reweighting in V1 (see Fig \ref{fig:MEGdata}), and with previous neurophysiological work (\protect\hyperlink{ref-Aschner2018}{Aschner et al., 2018}).
 It is currently unclear whether these effects originate in V1, or might involve feedback from higher areas.
 The similarity between monocular and dichoptic effects also differs from work on adaptation to individual mask components.
-In both physiological (Li et al., 2005; Sengpiel and Vorobyov, 2005) and psychophysical (Baker et al., 2007) paradigms, adapting to a dichoptic mask reduces its potency, whereas adapting to a monocular mask has little or no effect.
+In both physiological (\protect\hyperlink{ref-Li2005}{Li et al., 2005}; \protect\hyperlink{ref-Sengpiel2005}{Sengpiel \& Vorobyov, 2005}) and psychophysical (\protect\hyperlink{ref-Baker2007}{Baker et al., 2007}) paradigms, adapting to a dichoptic mask reduces its potency, whereas adapting to a monocular mask has little or no effect.
 Normalization reweighting offers an explanation for why monocular masks presented in isolation do not adapt: if suppressive weights are determined by co-occurrence of stimuli, presentation of an isolated mask will have little effect.
 However this cannot explain the dichoptic adaptation effects without invoking additional binocular processes, such as competition between summing and differencing channels (e.g.
-May et al., 2012).
+\protect\hyperlink{ref-May2012}{May et al., 2012}).
 
-The relationship between normalization reweighting and other forms of visual plasticity is currently unclear.
-One phenomenon that might be closely related to our dichoptic effect is the change in interocular suppression that occurs when one eye is patched for a period of time (Lunghi et al., 2011).
+The relationship between normalization reweighting and other forms of visual plasticity and adaptation is currently unclear.
+One phenomenon that might be closely related to our dichoptic effect is the change in interocular suppression that occurs when one eye is patched for a period of time (\protect\hyperlink{ref-Lunghi2011}{Lunghi et al., 2011}).
 In the patching paradigm, the inputs to the two eyes are uncorrelated while one eye is patched, which the normalization reweighting model predicts should reduce suppression between the eyes.
@@
 It is difficult to distinguish these possibilities using paradigms that assess the balance between the two eyes, such as the binocular rivalry paradigm from the original Lunghi et al.
-(2011) study.
-However subsequent work has shown that patching increases the patched eye's response (Zhou et al., 2015), and reduces both dichoptic masking (Baldwin and Hess, 2018) and levels of the inhibitory neurotransmitter GABA (Lunghi et al., 2015).
+(\protect\hyperlink{ref-Lunghi2011}{2011}) study.
+However subsequent work has shown that patching increases the patched eye's response (\protect\hyperlink{ref-Zhou2015}{Zhou et al., 2015}), and reduces both dichoptic masking (\protect\hyperlink{ref-Baldwin2018}{Baldwin \& Hess, 2018}) and levels of the inhibitory neurotransmitter GABA (\protect\hyperlink{ref-Lunghi2015}{Lunghi et al., 2015}).
 All of these findings are consistent with a reweighting account.
@@
 For this reason, we also examined relationships with the sensory perception quotient (SPQ) to examine whether sensory experiences specifically were related to normalization reweighting.
-SPQ scores showed significant negative correlation with AQ for the data sets from Experiments 2 and 3 (EEG data, \emph{r} = -0.35, \emph{p} \textless{} 0.001; MEG data, \emph{r} = -0.57, \emph{p} = 0.011) with effect sizes comparable to those reported previously (Tavassoli et al., 2014).
+SPQ scores showed significant negative correlation with AQ for the data sets from Experiments 2 and 3 (EEG data, \emph{r} = -0.35, \emph{p} \textless{} 0.001; MEG data, \emph{r} = -0.57, \emph{p} = 0.011) with effect sizes comparable to those reported previously (\protect\hyperlink{ref-Tavassoli2014}{Tavassoli et al., 2014}).
 We also conducted an exploratory analysis of the EEG data from Experiment 2, splitting participants by SPQ instead of AQ.
@@
 We suspect that the increase in spatial frequency from 0.5 c/deg in the Vilidaite et al.
-(2018) study to 2 c/deg here is most likely responsible for the dramatically reduced second harmonic response.
+(\protect\hyperlink{ref-Vilidaite2018}{2018}) study to 2 c/deg here is most likely responsible for the dramatically reduced second harmonic response.
 
-The idea that the dynamic balance of inhibition and excitation might be different in autism (Rosenberg et al., 2015; Rubenstein and Merzenich, 2003) has compelling face validity.
+The idea that the dynamic balance of inhibition and excitation might be different in autism (\protect\hyperlink{ref-Rosenberg2015}{Rosenberg et al., 2015}; \protect\hyperlink{ref-Rubenstein2003}{Rubenstein \& Merzenich, 2003}) has compelling face validity.
 For example, individuals with autism often report difficulties with changes in their sensory environment, which might be due to gain control processes failing to adapt appropriately.
-Indeed, there is experimental evidence of reduced adaptation across various domains (Pellicano et al., 2007; Turi et al., 2015), which is predicted by some autism models (Pellicano and Burr, 2012).
-However this appears not to extend to changes in normalization reweighting, despite the link between reweighting and adaptation (Westrick et al., 2016).
+Indeed, there is experimental evidence of reduced adaptation across various domains (\protect\hyperlink{ref-Pellicano2007}{Pellicano et al., 2007}; \protect\hyperlink{ref-Turi2015}{Turi et al., 2015}), which is predicted by some autism models (\protect\hyperlink{ref-Pellicano2012}{Pellicano \& Burr, 2012}).
+However this appears not to extend to changes in normalization reweighting, despite the link between reweighting and adaptation (\protect\hyperlink{ref-Westrick2016}{Westrick et al., 2016}).
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Aschner2018}{}}%
-Aschner A, Solomon SG, Landy MS, Heeger DJ, Kohn A.
-2018.
+Aschner, A., Solomon, S.
+G., Landy, M.
+S., Heeger, D.
+J., \& Kohn, A.
+(2018).
 Temporal contingencies determine whether adaptation strengthens or weakens normalization.
-\emph{J Neurosci} \textbf{38}:10129--10142.
-doi:\href{https://doi.org/10.1523/JNEUROSCI.1131-18.2018}{10.1523/JNEUROSCI.1131-18.2018}
+\emph{J Neurosci}, \emph{38}(47), 10129--10142.
+\url{https://doi.org/10.1523/JNEUROSCI.1131-18.2018}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Baker2021}{}}%
-Baker DH.
-2021.
-Statistical analysis of periodic data in neuroscience.
-\emph{Neurons, Behavior, Data analysis, and Theory} \textbf{5}.
-doi:\href{https://doi.org/10.51628/001c.27680}{10.51628/001c.27680}
+Baker, D. H. (2021). Statistical analysis of periodic data in neuroscience. \emph{Neurons, Behavior, Data Analysis, and Theory}, \emph{5}(3). \url{https://doi.org/10.51628/001c.27680}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Baker2007}{}}%
-Baker DH, Meese TS, Summers RJ.
-2007.
+Baker, D.
+H., Meese, T.
+S., \& Summers, R.
+J.
+(2007).
 Psychophysical evidence for two routes to suppression before binocular summation of signals in human vision.
-\emph{Neuroscience} \textbf{146}:435--448.
-doi:\href{https://doi.org/10.1016/j.neuroscience.2007.01.030}{10.1016/j.neuroscience.2007.01.030}
+\emph{Neuroscience}, \emph{146}(1), 435--448.
+\url{https://doi.org/10.1016/j.neuroscience.2007.01.030}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Baldwin2018}{}}%
-Baldwin AS, Hess RF.
-2018.
+Baldwin, A.
+S., \& Hess, R.
+F.
+(2018).
 The mechanism of short-term monocular deprivation is not simple: Separate effects on parallel and cross-oriented dichoptic masking.
-\emph{Sci Rep} \textbf{8}:6191.
-doi:\href{https://doi.org/10.1038/s41598-018-24584-9}{10.1038/s41598-018-24584-9}
+\emph{Sci Rep}, \emph{8}(1), 6191.
+\url{https://doi.org/10.1038/s41598-018-24584-9}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Baron-Cohen2001}{}}%
-Baron-Cohen S, Wheelwright S, Skinner R, Martin J, Clubley E.
-2001.
+Baron-Cohen, S., Wheelwright, S., Skinner, R., Martin, J., \& Clubley, E.
+(2001).
 The autism-spectrum quotient (AQ): Evidence from asperger syndrome/high-functioning autism, males and females, scientists and mathematicians.
-\emph{J Autism Dev Disord} \textbf{31}:5--17.
-doi:\href{https://doi.org/10.1023/a:1005653411471}{10.1023/a:1005653411471}
+\emph{J Autism Dev Disord}, \emph{31}(1), 5--17.
+\url{https://doi.org/10.1023/a:1005653411471}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Blakemore1969}{}}%
-Blakemore C, Campbell FW.
-1969.
+Blakemore, C., \& Campbell, F.
+W.
+(1969).
 On the existence of neurones in the human visual system selectively sensitive to the orientation and size of retinal images.
-\emph{J Physiol} \textbf{203}:237--60.
-doi:\href{https://doi.org/10.1113/jphysiol.1969.sp008862}{10.1113/jphysiol.1969.sp008862}
+\emph{J Physiol}, \emph{203}(1), 237--260.
+\url{https://doi.org/10.1113/jphysiol.1969.sp008862}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Cannon1991}{}}%
-Cannon MW, Fullenkamp SC.
-1991.
+Cannon, M.
+W., \& Fullenkamp, S.
+C.
+(1991).
 Spatial interactions in apparent contrast: Inhibitory effects among grating patterns of different spatial frequencies, spatial positions and orientations.
-\emph{Vision Res} \textbf{31}:1985--98.
-doi:\href{https://doi.org/10.1016/0042-6989(91)90193-9}{10.1016/0042-6989(91)90193-9}
+\emph{Vision Res}, \emph{31}(11), 1985--1998.
+\url{https://doi.org/10.1016/0042-6989(91)90193-9}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Carandini2011}{}}%
-Carandini M, Heeger DJ. 2011. Normalization as a canonical neural computation. \emph{Nature Reviews Neuroscience} \textbf{13}:51--62. doi:\href{https://doi.org/10.1038/nrn3136}{10.1038/nrn3136}
+Carandini, M., \& Heeger, D. J. (2011). Normalization as a canonical neural computation. \emph{Nature Reviews Neuroscience}, \emph{13}(1), 51--62. \url{https://doi.org/10.1038/nrn3136}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Cunningham2017}{}}%
+Cunningham, D. G. M., Baker, D. H., \& Peirce, J. W. (2017). Measuring nonlinear signal combination using EEG. \emph{J Vis}, \emph{17}(5), 10. \url{https://doi.org/10.1167/17.5.10}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Dale1999}{}}%
-Dale AM, Fischl B, Sereno MI.
-1999.
+Dale, A.
+M., Fischl, B., \& Sereno, M.
+I.
+(1999).
 Cortical surface-based analysis.
@@
 Segmentation and surface reconstruction.
-\emph{Neuroimage} \textbf{9}:179--94.
-doi:\href{https://doi.org/10.1006/nimg.1998.0395}{10.1006/nimg.1998.0395}
+\emph{Neuroimage}, \emph{9}(2), 179--194.
+\url{https://doi.org/10.1006/nimg.1998.0395}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Delorme2004}{}}%
-Delorme A, Makeig S.
-2004.
+Delorme, A., \& Makeig, S.
+(2004).
 EEGLAB: An open source toolbox for analysis of single-trial EEG dynamics including independent component analysis.
-\emph{J Neurosci Methods} \textbf{134}:9--21.
-doi:\href{https://doi.org/10.1016/j.jneumeth.2003.10.009}{10.1016/j.jneumeth.2003.10.009}
+\emph{J Neurosci Methods}, \emph{134}(1), 9--21.
+\url{https://doi.org/10.1016/j.jneumeth.2003.10.009}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Dougherty2019}{}}%
+Dougherty, K., Schmid, M.
+C., \& Maier, A.
+(2019).
+Binocular response modulation in the lateral geniculate nucleus.
+\emph{J Comp Neurol}, \emph{527}(3), 522--534.
+\url{https://doi.org/10.1002/cne.24417}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Foley1994}{}}%
-Foley JM.
-1994.
+Foley, J.
+M.
+(1994).
 Human luminance pattern-vision mechanisms: Masking experiments require a new model.
-\emph{J Opt Soc Am A Opt Image Sci Vis} \textbf{11}:1710--9.
-doi:\href{https://doi.org/10.1364/josaa.11.001710}{10.1364/josaa.11.001710}
+\emph{J Opt Soc Am A Opt Image Sci Vis}, \emph{11}(6), 1710--1719.
+\url{https://doi.org/10.1364/josaa.11.001710}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Foley1997}{}}%
-Foley JM, Chen CC.
-1997.
+Foley, J.
+M., \& Chen, C.
+C.
+(1997).
 Analysis of the effect of pattern adaptation on pattern pedestal effects: A two-process model.
-\emph{Vision Res} \textbf{37}:2779--88.
-doi:\href{https://doi.org/10.1016/s0042-6989(97)00081-3}{10.1016/s0042-6989(97)00081-3}
+\emph{Vision Res}, \emph{37}(19), 2779--2788.
+\url{https://doi.org/10.1016/s0042-6989(97)00081-3}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Fonov2011}{}}%
-Fonov V, Evans AC, Botteron K, Almli CR, McKinstry RC, Collins DL, Brain Development Cooperative Group.
-2011.
+Fonov, V., Evans, A.
+C., Botteron, K., Almli, C.
+R., McKinstry, R.
+C., Collins, D.
+L., \& Brain Development Cooperative Group.
+(2011).
 Unbiased average age-appropriate atlases for pediatric studies.
-\emph{Neuroimage} \textbf{54}:313--27.
-doi:\href{https://doi.org/10.1016/j.neuroimage.2010.07.033}{10.1016/j.neuroimage.2010.07.033}
+\emph{Neuroimage}, \emph{54}(1), 313--327.
+\url{https://doi.org/10.1016/j.neuroimage.2010.07.033}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Freeman2002}{}}%
-Freeman TCB, Durand S, Kiper DC, Carandini M.
-2002.
+Freeman, T.
+C.
+B., Durand, S., Kiper, D.
+C., \& Carandini, M.
+(2002).
 Suppression without inhibition in visual cortex.
-\emph{Neuron} \textbf{35}:759--71.
-doi:\href{https://doi.org/10.1016/s0896-6273(02)00819-x}{10.1016/s0896-6273(02)00819-x}
+\emph{Neuron}, \emph{35}(4), 759--771.
+\url{https://doi.org/10.1016/s0896-6273(02)00819-x}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Gibson1937}{}}%
-Gibson JJ, Radner M.
-1937.
+Gibson, J.
+J., \& Radner, M.
+(1937).
 Adaptation, after-effect and contrast in the perception of tilted lines.
@@
 {Quantitative} studies.
-\emph{Journal of Experimental Psychology} \textbf{20}:453--467.
-doi:\href{https://doi.org/10.1037/h0059826}{10.1037/h0059826}
+\emph{Journal of Experimental Psychology}, \emph{20}(5), 453--467.
+\url{https://doi.org/10.1037/h0059826}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Greenlee1991}{}}%
-Greenlee MW, Georgeson MA, Magnussen S, Harris JP.
-1991.
+Greenlee, M.
+W., Georgeson, M.
+A., Magnussen, S., \& Harris, J.
+P.
+(1991).
 The time course of adaptation to spatial contrast.
-\emph{Vision Res} \textbf{31}:223--36.
-doi:\href{https://doi.org/10.1016/0042-6989(91)90113-j}{10.1016/0042-6989(91)90113-j}
+\emph{Vision Res}, \emph{31}(2), 223--236.
+\url{https://doi.org/10.1016/0042-6989(91)90113-j}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Haak2014}{}}%
-Haak KV, Fast E, Bao M, Lee M, Engel SA.
-2014.
+Haak, K.
+V., Fast, E., Bao, M., Lee, M., \& Engel, S.
+A.
+(2014).
 Four days of visual contrast deprivation reveals limits of neuronal adaptation.
-\emph{Curr Biol} \textbf{24}:2575--9.
-doi:\href{https://doi.org/10.1016/j.cub.2014.09.027}{10.1016/j.cub.2014.09.027}
+\emph{Curr Biol}, \emph{24}(21), 2575--2579.
+\url{https://doi.org/10.1016/j.cub.2014.09.027}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Heeger1992}{}}%
-Heeger DJ. 1992. Normalization of cell responses in cat striate cortex. \emph{Vis Neurosci} \textbf{9}:181--97. doi:\href{https://doi.org/10.1017/s0952523800009640}{10.1017/s0952523800009640}
+Heeger, D. J. (1992). Normalization of cell responses in cat striate cortex. \emph{Vis Neurosci}, \emph{9}(2), 181--197. \url{https://doi.org/10.1017/s0952523800009640}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Hoekstra2011}{}}%
-Hoekstra RA, Vinkhuyzen AAE, Wheelwright S, Bartels M, Boomsma DI, Baron-Cohen S, Posthuma D, Sluis S van der.
-2011.
+Hoekstra, R.
+A., Vinkhuyzen, A.
+A.
+E., Wheelwright, S., Bartels, M., Boomsma, D.
+I., Baron-Cohen, S., Posthuma, D., \& Sluis, S.
+van der.
+(2011).
 The construction and validation of an abridged version of the autism-spectrum quotient (AQ-short).
-\emph{J Autism Dev Disord} \textbf{41}:589--96.
-doi:\href{https://doi.org/10.1007/s10803-010-1073-0}{10.1007/s10803-010-1073-0}
+\emph{J Autism Dev Disord}, \emph{41}(5), 589--596.
+\url{https://doi.org/10.1007/s10803-010-1073-0}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Koh2010}{}}%
-Koh HC, Milne E, Dobkins K.
-2010.
+Koh, H.
+C., Milne, E., \& Dobkins, K.
+(2010).
 Spatial contrast sensitivity in adolescents with autism spectrum disorders.
-\emph{J Autism Dev Disord} \textbf{40}:978--87.
-doi:\href{https://doi.org/10.1007/s10803-010-0953-7}{10.1007/s10803-010-0953-7}
+\emph{J Autism Dev Disord}, \emph{40}(8), 978--987.
+\url{https://doi.org/10.1007/s10803-010-0953-7}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Kwon2009}{}}%
-Kwon M, Legge GE, Fang F, Cheong AMY, He S.
-2009.
+Kwon, M., Legge, G.
+E., Fang, F., Cheong, A.
+M.
+Y., \& He, S.
+(2009).
 Adaptive changes in visual cortex following prolonged contrast reduction.
-\emph{J Vis} \textbf{9}:20.1--16.
-doi:\href{https://doi.org/10.1167/9.2.20}{10.1167/9.2.20}
+\emph{J Vis}, \emph{9}(2), 20.1--16.
+\url{https://doi.org/10.1167/9.2.20}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Legge1979}{}}%
-Legge GE. 1979. Spatial frequency masking in human vision: Binocular interactions. \emph{J Opt Soc Am} \textbf{69}:838--47. doi:\href{https://doi.org/10.1364/josa.69.000838}{10.1364/josa.69.000838}
+Legge, G. E. (1979). Spatial frequency masking in human vision: Binocular interactions. \emph{J Opt Soc Am}, \emph{69}(6), 838--847. \url{https://doi.org/10.1364/josa.69.000838}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Li2005}{}}%
-Li B, Peterson MR, Thompson JK, Duong T, Freeman RD.
-2005.
+Li, B., Peterson, M.
+R., Thompson, J.
+K., Duong, T., \& Freeman, R.
+D.
+(2005).
 Cross-orientation suppression: Monoptic and dichoptic mechanisms are different.
-\emph{J Neurophysiol} \textbf{94}:1645--50.
-doi:\href{https://doi.org/10.1152/jn.00203.2005}{10.1152/jn.00203.2005}
+\emph{J Neurophysiol}, \emph{94}(2), 1645--1650.
+\url{https://doi.org/10.1152/jn.00203.2005}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Liza2022}{}}%
-Liza K, Ray S.
-2022.
+Liza, K., \& Ray, S.
+(2022).
 Local interactions between steady-state visually evoked potentials at nearby flickering frequencies.
-\emph{J Neurosci} \textbf{42}:3965--3974.
-doi:\href{https://doi.org/10.1523/JNEUROSCI.0180-22.2022}{10.1523/JNEUROSCI.0180-22.2022}
+\emph{J Neurosci}, \emph{42}(19), 3965--3974.
+\url{https://doi.org/10.1523/JNEUROSCI.0180-22.2022}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Lunghi2011}{}}%
-Lunghi C, Burr DC, Morrone C.
-2011.
+Lunghi, C., Burr, D.
+C., \& Morrone, C.
+(2011).
 Brief periods of monocular deprivation disrupt ocular balance in human adult visual cortex.
-\emph{Curr Biol} \textbf{21}:R538--9.
-doi:\href{https://doi.org/10.1016/j.cub.2011.06.004}{10.1016/j.cub.2011.06.004}
+\emph{Curr Biol}, \emph{21}(14), R538--9.
+\url{https://doi.org/10.1016/j.cub.2011.06.004}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Lunghi2015}{}}%
-Lunghi C, Emir UE, Morrone MC, Bridge H.
-2015.
+Lunghi, C., Emir, U.
+E., Morrone, M.
+C., \& Bridge, H.
+(2015).
 Short-term monocular deprivation alters GABA in the adult human visual cortex.
-\emph{Curr Biol} \textbf{25}:1496--501.
-doi:\href{https://doi.org/10.1016/j.cub.2015.04.021}{10.1016/j.cub.2015.04.021}
+\emph{Curr Biol}, \emph{25}(11), 1496--1501.
+\url{https://doi.org/10.1016/j.cub.2015.04.021}
 
 \leavevmode\vadjust pre{\hypertarget{ref-MacLennan2022}{}}%
-MacLennan K, O'Brien S, Tavassoli T.
-2022.
+MacLennan, K., O'Brien, S., \& Tavassoli, T.
+(2022).
 In our own words: The complex sensory experiences of autistic adults.
-\emph{J Autism Dev Disord} \textbf{52}:3061--3075.
-doi:\href{https://doi.org/10.1007/s10803-021-05186-3}{10.1007/s10803-021-05186-3}
+\emph{J Autism Dev Disord}, \emph{52}(7), 3061--3075.
+\url{https://doi.org/10.1007/s10803-021-05186-3}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Maris2007}{}}%
-Maris E, Oostenveld R.
-2007.
-Nonparametric statistical testing of EEG- and MEG-data.
-\emph{J Neurosci Methods} \textbf{164}:177--90.
-doi:\href{https://doi.org/10.1016/j.jneumeth.2007.03.024}{10.1016/j.jneumeth.2007.03.024}
+Maris, E., \& Oostenveld, R. (2007). Nonparametric statistical testing of EEG- and MEG-data. \emph{J Neurosci Methods}, \emph{164}(1), 177--190. \url{https://doi.org/10.1016/j.jneumeth.2007.03.024}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Mather2008}{}}%
-Mather G, Pavan A, Campana G, Casco C.
-2008.
-The motion aftereffect reloaded.
-\emph{Trends Cogn Sci} \textbf{12}:481--7.
-doi:\href{https://doi.org/10.1016/j.tics.2008.09.002}{10.1016/j.tics.2008.09.002}
+Mather, G., Pavan, A., Campana, G., \& Casco, C. (2008). The motion aftereffect reloaded. \emph{Trends Cogn Sci}, \emph{12}(12), 481--487. \url{https://doi.org/10.1016/j.tics.2008.09.002}
 
 \leavevmode\vadjust pre{\hypertarget{ref-May2012}{}}%
-May KA, Zhaoping L, Hibbard PB.
-2012.
+May, K.
+A., Zhaoping, L., \& Hibbard, P.
+B.
+(2012).
 Perceived direction of motion determined by adaptation to static binocular images.
-\emph{Curr Biol} \textbf{22}:28--32.
-doi:\href{https://doi.org/10.1016/j.cub.2011.11.025}{10.1016/j.cub.2011.11.025}
+\emph{Curr Biol}, \emph{22}(1), 28--32.
+\url{https://doi.org/10.1016/j.cub.2011.11.025}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Meese2009}{}}%
-Meese TS, Baker DH.
-2009.
+Meese, T.
+S., \& Baker, D.
+H.
+(2009).
 Cross-orientation masking is speed invariant between ocular pathways but speed dependent within them.
-\emph{Journal of Vision} \textbf{9}:2.
-doi:\href{https://doi.org/10.1167/9.5.2}{10.1167/9.5.2}
+\emph{Journal of Vision}, \emph{9}(5), 2.
+\url{https://doi.org/10.1167/9.5.2}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Pellicano2012}{}}%
-Pellicano E, Burr D.
-2012.
+Pellicano, E., \& Burr, D.
+(2012).
 When the world becomes 'too real': A bayesian explanation of autistic perception.
-\emph{Trends Cogn Sci} \textbf{16}:504--10.
-doi:\href{https://doi.org/10.1016/j.tics.2012.08.009}{10.1016/j.tics.2012.08.009}
+\emph{Trends Cogn Sci}, \emph{16}(10), 504--510.
+\url{https://doi.org/10.1016/j.tics.2012.08.009}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Pellicano2007}{}}%
-Pellicano E, Jeffery L, Burr D, Rhodes G.
-2007.
+Pellicano, E., Jeffery, L., Burr, D., \& Rhodes, G.
+(2007).
 Abnormal adaptive face-coding mechanisms in children with autism spectrum disorder.
-\emph{Curr Biol} \textbf{17}:1508--12.
-doi:\href{https://doi.org/10.1016/j.cub.2007.07.065}{10.1016/j.cub.2007.07.065}
+\emph{Curr Biol}, \emph{17}(17), 1508--1512.
+\url{https://doi.org/10.1016/j.cub.2007.07.065}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Petrov2005}{}}%
-Petrov Y.
-2005.
-Two distinct mechanisms of suppression in human vision.
-\emph{Journal of Neuroscience} \textbf{25}:8704--8707.
-doi:\href{https://doi.org/10.1523/jneurosci.2871-05.2005}{10.1523/jneurosci.2871-05.2005}
+Petrov, Y. (2005). Two distinct mechanisms of suppression in human vision. \emph{Journal of Neuroscience}, \emph{25}(38), 8704--8707. \url{https://doi.org/10.1523/jneurosci.2871-05.2005}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Regan1988}{}}%
+Regan, M.
+P., \& Regan, D.
+(1988).
+A frequency domain technique for characterizing nonlinearities in biological systems.
+\emph{Journal of Theoretical Biology}, \emph{133}(3), 293--317.
+https://doi.org/\url{https://doi.org/10.1016/S0022-5193(88)80323-0}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Rosenberg2015}{}}%
-Rosenberg A, Patterson JS, Angelaki DE.
-2015.
+Rosenberg, A., Patterson, J.
+S., \& Angelaki, D.
+E.
+(2015).
 A computational perspective on autism.
-\emph{Proc Natl Acad Sci U S A} \textbf{112}:9158--65.
-doi:\href{https://doi.org/10.1073/pnas.1510583112}{10.1073/pnas.1510583112}
+\emph{Proc Natl Acad Sci U S A}, \emph{112}(30), 9158--9165.
+\url{https://doi.org/10.1073/pnas.1510583112}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Rosenhall1999}{}}%
-Rosenhall U, Nordin V, Sandström M, Ahlsén G, Gillberg C.
-1999.
-Autism and hearing loss.
-\emph{J Autism Dev Disord} \textbf{29}:349--57.
-doi:\href{https://doi.org/10.1023/a:1023022709710}{10.1023/a:1023022709710}
+Rosenhall, U., Nordin, V., Sandström, M., Ahlsén, G., \& Gillberg, C. (1999). Autism and hearing loss. \emph{J Autism Dev Disord}, \emph{29}(5), 349--357. \url{https://doi.org/10.1023/a:1023022709710}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Rubenstein2003}{}}%
-Rubenstein JLR, Merzenich MM.
-2003.
+Rubenstein, J.
+L.
+R., \& Merzenich, M.
+M.
+(2003).
 Model of autism: Increased ratio of excitation/inhibition in key neural systems.
-\emph{Genes Brain Behav} \textbf{2}:255--67.
-doi:\href{https://doi.org/10.1034/j.1601-183x.2003.00037.x}{10.1034/j.1601-183x.2003.00037.x}
+\emph{Genes Brain Behav}, \emph{2}(5), 255--267.
+\url{https://doi.org/10.1034/j.1601-183x.2003.00037.x}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Sandhu2020}{}}%
-Sandhu TR, Reese G, Lawson RP.
-2020.
+Sandhu, T.
+R., Reese, G., \& Lawson, R.
+P.
+(2020).
 Preserved low-level visual gain control in autistic adults.
-\emph{Wellcome Open Research} \textbf{4}.
-doi:\href{https://doi.org/10.12688/wellcomeopenres.15615.1}{10.12688/wellcomeopenres.15615.1}
+\emph{Wellcome Open Research}, \emph{4}(208).
+\url{https://doi.org/10.12688/wellcomeopenres.15615.1}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Schallmo2020}{}}%
-Schallmo M-P, Kolodny T, Kale AM, Millin R, Flevaris AV, Edden RAE, Gerdts J, Bernier RA, Murray SO.
-2020.
+Schallmo, M.-P., Kolodny, T., Kale, A.
+M., Millin, R., Flevaris, A.
+V., Edden, R.
+A.
+E., Gerdts, J., Bernier, R.
+A., \& Murray, S.
+O.
+(2020).
 Weaker neural suppression in autism.
-\emph{Nat Commun} \textbf{11}:2675.
-doi:\href{https://doi.org/10.1038/s41467-020-16495-z}{10.1038/s41467-020-16495-z}
+\emph{Nat Commun}, \emph{11}(1), 2675.
+\url{https://doi.org/10.1038/s41467-020-16495-z}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Sengpiel1994}{}}%
-Sengpiel F, Blakemore C. 1994. Interocular control of neuronal responsiveness in cat visual cortex. \emph{Nature} \textbf{368}:847--50. doi:\href{https://doi.org/10.1038/368847a0}{10.1038/368847a0}
+Sengpiel, F., \& Blakemore, C. (1994). Interocular control of neuronal responsiveness in cat visual cortex. \emph{Nature}, \emph{368}(6474), 847--850. \url{https://doi.org/10.1038/368847a0}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Sengpiel2005}{}}%
-Sengpiel F, Vorobyov V.
-2005.
+Sengpiel, F., \& Vorobyov, V.
+(2005).
 Intracortical origins of interocular suppression in the visual cortex.
-\emph{J Neurosci} \textbf{25}:6394--400.
-doi:\href{https://doi.org/10.1523/JNEUROSCI.0862-05.2005}{10.1523/JNEUROSCI.0862-05.2005}
+\emph{J Neurosci}, \emph{25}(27), 6394--6400.
+\url{https://doi.org/10.1523/JNEUROSCI.0862-05.2005}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Simmons2009}{}}%
-Simmons DR, Robertson AE, McKay LS, Toal E, McAleer P, Pollick FE.
-2009.
+Simmons, D.
+R., Robertson, A.
+E., McKay, L.
+S., Toal, E., McAleer, P., \& Pollick, F.
+E.
+(2009).
 Vision in autism spectrum disorders.
-\emph{Vision Research} \textbf{49}:2705--2739.
-doi:\href{https://doi.org/10.1016/j.visres.2009.08.005}{10.1016/j.visres.2009.08.005}
+\emph{Vision Research}, \emph{49}(22), 2705--2739.
+\url{https://doi.org/10.1016/j.visres.2009.08.005}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Tadel2011}{}}%
-Tadel F, Baillet S, Mosher JC, Pantazis D, Leahy RM.
-2011.
+Tadel, F., Baillet, S., Mosher, J.
+C., Pantazis, D., \& Leahy, R.
+M.
+(2011).
 Brainstorm: A user-friendly application for MEG/EEG analysis.
-\emph{Comput Intell Neurosci} \textbf{2011}:879716.
-doi:\href{https://doi.org/10.1155/2011/879716}{10.1155/2011/879716}
+\emph{Comput Intell Neurosci}, \emph{2011}, 879716.
+\url{https://doi.org/10.1155/2011/879716}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Tavassoli2014}{}}%
-Tavassoli T, Hoekstra RA, Baron-Cohen S.
-2014.
+Tavassoli, T., Hoekstra, R.
+A., \& Baron-Cohen, S.
+(2014).
 The sensory perception quotient (SPQ): Development and validation of a new sensory questionnaire for adults with and without autism.
-\emph{Mol Autism} \textbf{5}:29.
-doi:\href{https://doi.org/10.1186/2040-2392-5-29}{10.1186/2040-2392-5-29}
+\emph{Mol Autism}, \emph{5}, 29.
+\url{https://doi.org/10.1186/2040-2392-5-29}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Tavassoli2011}{}}%
-Tavassoli T, Latham K, Bach M, Dakin SC, Baron-Cohen S.
-2011.
+Tavassoli, T., Latham, K., Bach, M., Dakin, S.
+C., \& Baron-Cohen, S.
+(2011).
 Psychophysical measures of visual acuity in autism spectrum conditions.
-\emph{Vision Research} \textbf{51}:1778--1780.
-doi:\href{https://doi.org/10.1016/j.visres.2011.06.004}{10.1016/j.visres.2011.06.004}
+\emph{Vision Research}, \emph{51}(15), 1778--1780.
+\url{https://doi.org/10.1016/j.visres.2011.06.004}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Tsai2012}{}}%
+Tsai, J.
+J., Wade, A.
+R., \& Norcia, A.
+M.
+(2012).
+Dynamics of normalization underlying masking in human visual cortex.
+\emph{J Neurosci}, \emph{32}(8), 2783--2789.
+\url{https://doi.org/10.1523/JNEUROSCI.4485-11.2012}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Turi2015}{}}%
-Turi M, Burr DC, Igliozzi R, Aagten-Murphy D, Muratori F, Pellicano E.
-2015.
+Turi, M., Burr, D.
+C., Igliozzi, R., Aagten-Murphy, D., Muratori, F., \& Pellicano, E.
+(2015).
 Children with autism spectrum disorder show reduced adaptation to number.
-\emph{Proc Natl Acad Sci U S A} \textbf{112}:7868--72.
-doi:\href{https://doi.org/10.1073/pnas.1504099112}{10.1073/pnas.1504099112}
+\emph{Proc Natl Acad Sci U S A}, \emph{112}(25), 7868--7872.
+\url{https://doi.org/10.1073/pnas.1504099112}
 
 \leavevmode\vadjust pre{\hypertarget{ref-VandeCruys2018}{}}%
-Van de Cruys S, Vanmarcke S, Steyaert J, Wagemans J.
-2018.
+Van de Cruys, S., Vanmarcke, S., Steyaert, J., \& Wagemans, J.
+(2018).
 Intact perceptual bias in autism contradicts the decreased normalization model.
-\emph{Scientific Reports} \textbf{8}.
-doi:\href{https://doi.org/10.1038/s41598-018-31042-z}{10.1038/s41598-018-31042-z}
+\emph{Scientific Reports}, \emph{8}(1).
+\url{https://doi.org/10.1038/s41598-018-31042-z}
 
 \leavevmode\vadjust pre{\hypertarget{ref-VanVeen1997}{}}%
-Van Veen BD, Drongelen W van, Yuchtman M, Suzuki A.
-1997.
+Van Veen, B.
+D., Drongelen, W.
+van, Yuchtman, M., \& Suzuki, A.
+(1997).
 Localization of brain electrical activity via linearly constrained minimum variance spatial filtering.
-\emph{IEEE Trans Biomed Eng} \textbf{44}:867--80.
-doi:\href{https://doi.org/10.1109/10.623056}{10.1109/10.623056}
+\emph{IEEE Trans Biomed Eng}, \emph{44}(9), 867--880.
+\url{https://doi.org/10.1109/10.623056}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Vilidaite2018}{}}%
-Vilidaite G, Norcia AM, West RJH, Elliott CJH, Pei F, Wade AR, Baker DH.
-2018.
+Vilidaite, G., Norcia, A.
+M., West, R.
+J.
+H., Elliott, C.
+J.
+H., Pei, F., Wade, A.
+R., \& Baker, D.
+H.
+(2018).
 Autism sensory dysfunction in an evolutionarily conserved system.
-\emph{Proc Biol Sci} \textbf{285}:20182255.
-doi:\href{https://doi.org/10.1098/rspb.2018.2255}{10.1098/rspb.2018.2255}
+\emph{Proc Biol Sci}, \emph{285}(1893), 20182255.
+\url{https://doi.org/10.1098/rspb.2018.2255}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Wang2015}{}}%
-Wang L, Mruczek REB, Arcaro MJ, Kastner S.
-2015.
+Wang, L., Mruczek, R.
+E.
+B., Arcaro, M.
+J., \& Kastner, S.
+(2015).
 Probabilistic maps of visual topography in human cortex.
-\emph{Cereb Cortex} \textbf{25}:3911--31.
-doi:\href{https://doi.org/10.1093/cercor/bhu277}{10.1093/cercor/bhu277}
+\emph{Cereb Cortex}, \emph{25}(10), 3911--3931.
+\url{https://doi.org/10.1093/cercor/bhu277}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Webster2015}{}}%
-Webster MA. 2015. Visual adaptation. \emph{Annu Rev Vis Sci} \textbf{1}:547--567. doi:\href{https://doi.org/10.1146/annurev-vision-082114-035509}{10.1146/annurev-vision-082114-035509}
+Webster, M. A. (2015). Visual adaptation. \emph{Annu Rev Vis Sci}, \emph{1}, 547--567. \url{https://doi.org/10.1146/annurev-vision-082114-035509}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Westrick2016}{}}%
-Westrick ZM, Heeger DJ, Landy MS.
-2016.
+Westrick, Z.
+M., Heeger, D.
+J., \& Landy, M.
+S.
+(2016).
 Pattern adaptation and normalization reweighting.
-\emph{Journal of Neuroscience} \textbf{36}:9805--9816.
-doi:\href{https://doi.org/10.1523/jneurosci.1067-16.2016}{10.1523/jneurosci.1067-16.2016}
+\emph{Journal of Neuroscience}, \emph{36}(38), 9805--9816.
+\url{https://doi.org/10.1523/jneurosci.1067-16.2016}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Yiltiz2020}{}}%
-Yiltiz H, Heeger DJ, Landy MS.
-2020.
-Contingent adaptation in masking and surround suppression.
-\emph{Vision Res} \textbf{166}:72--80.
-doi:\href{https://doi.org/10.1016/j.visres.2019.11.004}{10.1016/j.visres.2019.11.004}
+Yiltiz, H., Heeger, D. J., \& Landy, M. S. (2020). Contingent adaptation in masking and surround suppression. \emph{Vision Res}, \emph{166}, 72--80. \url{https://doi.org/10.1016/j.visres.2019.11.004}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Zhou2015}{}}%
-Zhou J, Baker DH, Simard M, Saint-Amour D, Hess RF.
-2015.
+Zhou, J., Baker, D.
+H., Simard, M., Saint-Amour, D., \& Hess, R.
+F.
+(2015).
 Short-term monocular patching boosts the patched eye's response in visual cortex.
-\emph{Restor Neurol Neurosci} \textbf{33}:381--7.
-doi:\href{https://doi.org/10.3233/RNN-140472}{10.3233/RNN-140472}
+\emph{Restor Neurol Neurosci}, \emph{33}(3), 381--387.
+\url{https://doi.org/10.3233/RNN-140472}
 
 \leavevmode\vadjust pre{\hypertarget{ref-Zhou2019}{}}%
-Zhou J, Benson NC, Kay K, Winawer J.
-2019.
+Zhou, J., Benson, N.
+C., Kay, K., \& Winawer, J.
+(2019).
 Predicting neuronal dynamics with a delayed gain control model.
-\emph{PLoS Comput Biol} \textbf{15}:e1007484.
-doi:\href{https://doi.org/10.1371/journal.pcbi.1007484}{10.1371/journal.pcbi.1007484}
+\emph{PLoS Comput Biol}, \emph{15}(11), e1007484.
+\url{https://doi.org/10.1371/journal.pcbi.1007484}
 

### 2023-07-31 additionalresources/csvconversionwrapper.m

@@ -1,0 +1,7 @@
+
+for s = 299:299
+    subj = num2str(s);
+    strcat('/Users/db900/Desktop/UG2021/P',subj,'/')
+d_EEG2CSV(strcat('/Users/db900/Desktop/UG2021/P',subj,'/'))
+
+end

### 2023-07-31 additionalresources/examplestim.m

@@ -1,0 +1,188 @@
+function examplestim
+
+clear
+close all;
+
+E.levelsC5 = [48 0 48 48]./100;
+E.levelsC7 = [0 48 48 48]./100;
+
+stimorient = 360.*(rand(36,1));
+
+ST.npixelsperdegree = 36;       % VPixx pixel resolution at 57cm
+
+ST.gratingsize = ST.npixelsperdegree*2;         %
+ST.gratingradiusfactor = ST.npixelsperdegree*2;  % previously 128
+ST.SF = 2;
+ST.ncycles = ST.SF*ST.gratingsize/ST.npixelsperdegree;
+
+screens=Screen('Screens');
+screenNumber=max(screens);
+rect = [1 1 1024 1024];
+[w, winRect] = Screen('OpenWindow',screenNumber,128,rect);
+ST.greylevel = 128;
+[width, height] = Screen('WindowSize', w);
+
+ndots = 250;
+doffset = 320;
+dotangle = rand(1,ndots).*2.*pi;
+dotradius = rand(1,ndots).*ST.npixelsperdegree/4;
+[ST.dotcoords(1,:) ST.dotcoords(2,:)] = pol2cart(dotangle, dotradius);
+ST.dotcoords(1,51:100) = ST.dotcoords(1,51:100)+doffset;
+ST.dotcoords(1,101:150) = ST.dotcoords(1,101:150)-doffset;
+ST.dotcoords(1,151:200) = ST.dotcoords(1,151:200)-doffset;
+ST.dotcoords(1,201:250) = ST.dotcoords(1,201:250)+doffset;
+ST.dotcoords(2,51:100) = ST.dotcoords(2,51:100)+doffset;
+ST.dotcoords(2,101:150) = ST.dotcoords(2,101:150)+doffset;
+ST.dotcoords(2,151:200) = ST.dotcoords(2,151:200)-doffset;
+ST.dotcoords(2,201:250) = ST.dotcoords(2,201:250)-doffset;
+
+ST.dotlevels = round(255*rand(3,ndots));
+
+ST.dotsize = 8;
+ST.centre = [width/2, height/2];
+
+gratingangle = [(0:90:330) (45:90:330) (0:90:330) (22.5:45:360) (0:45:315) (22.5:45:360)];
+gratingangle = pi.*gratingangle./180;
+gratingradius(1:4) = ST.gratingradiusfactor;
[…]

### 2023-07-31 additionalresources/mondichNRexpt.m

@@ -1,0 +1,744 @@
+function mondichNRexpt
+
+% normalization reweighting experiment with mon and dichoptic presentation
+% code based on surround suppression experiment from 2014
+% this version for ViewPixx, 36 pix/cm dot pitch
+% four conditions - 5Hz component, 7Hz component, both mon, dichoptic
+% DHB 1/3/20
+
+clear
+close all;
+
+pID = inputdlg('Enter participant ID number');
+E.subj = pID{1,1};
+useVP = 0;                  % hardware stereo doesn't seem to work in M16 mode
+atYNIC = 0;
+blockstorun = 3;
+
+E.nconds = 4;                           % 5Hz component, 7Hz component, mon combination, dich combination
+E.ntrials = 16;                         % total number of trials per condition in each block
+E.ntrialsperblock = E.nconds*E.ntrials;
+E.totalblocks = 3;
+E.totalreps = E.ntrials*E.totalblocks;
+
+E.levelsC5 = [48 0 48 48]./100;
+E.levelsC7 = [0 48 48 48]./100;
+
+W = what; E.exptpath = strcat(W.path,'/'); clear W;
+KbName('UnifyKeyNames');
+Screen('Preference', 'SkipSyncTests', 1);
+
+if atYNIC
+    ST.npixelsperdegree = 44;       % MEG projector pixel resolution at 85cm
+    addpath(strcat(E.exptpath,'/ppdev-mex-master'));
+else
+    ST.npixelsperdegree = 36;       % VPixx pixel resolution at 57cm
+end
+ST.gratingsize = ST.npixelsperdegree*2;         %
+ST.gratingradiusfactor = ST.npixelsperdegree*2;  % previously 128
+ST.SF = 2;
+ST.ncycles = ST.SF*ST.gratingsize/ST.npixelsperdegree;
+
+ST.duration = 6;
+ST.ITI = 3;         % always leave n seconds between trials
+ST.TFtarget = 5;
+ST.TFmask = 7;
+
+if (~exist(strcat(E.exptpath, 'Results/'),'dir'))
+    mkdir(strcat(E.exptpath, 'Results/'));
+end
+fname = strcat(E.exptpath, 'Results/', E.subj, 'trialorderNR.mat');
+if exist(fname)
+    load(fname);
+    save(strcat(E.exptpath, 'Results/', E.subj, 'trialorderNRold.mat'),'R','E');
+else
+    R.subj = E.subj;
[…]

### 2023-07-31 additionalresources/simulations.Rmd
Added simulations

---
title: "Additional simulations of timecourse analysis"
author: "Daniel Baker"
date: "2023-07-31"
output: pdf_document
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)

# set the initial parameters for the simulations
samplerate <- 1000
targetF <- 5
duration <- 6
binwidth <- 1000
tindex <- 1 + targetF*(binwidth/samplerate)

```

## Overview

At the suggestion of a reviewer, we conducted simulations to assess the temporal precision of our analysis methods. In particular, we wanted to check if the use of a `r binwidth/1000`-second sliding time window placed a limit on our estimates of the change in suppression strength. We began by generating two samples of a sine wave carrier at `r targetF` Hz. To simulate the onset transient often observed in steady-state data, we set the amplitude of the first 1000ms to be 1.4 times higher than the remainder of the waveform. To assess our methods for quantifying suppression, we generated two waveforms with amplitudes that differed by a factor of two. We also added white noise to each signal. The two signals are shown by the black and blue traces in the following plots:

```{r makestimulus}

times <- seq(1/1000,9,1/1000)-1.5
trigwaveform1 <- -cos(2 * targetF * times * pi)
trigwaveform1[1:1500] <- -1     # set the start to zero
trigwaveform1[7501:9000] <- -1  # set the end to zero

trigwaveform1 <- 0.1*abs(rnorm(9000))+((trigwaveform1 + 1)/2)
trigwaveform1[2501:8000] <- trigwaveform1[2501:8000] / 1.4

trigwaveform2 <- -cos(2 * targetF * times * pi)
trigwaveform2[1:1500] <- -1
trigwaveform2[7501:9000] <- -1

trigwaveform2 <- 0.1*abs(rnorm(9000))+((trigwaveform2 + 1)/4)
trigwaveform2[2501:8000] <- trigwaveform2[2501:8000] / 1.4

plot(times,trigwaveform1,type='l',ylim=c(0,1.3))

plot(times,trigwaveform2,type='l',col='blue',ylim=c(0,1.3))

```

Next we applied our timecourse analysis method in which the Fourier transform of the waveform was calculated in successive `r binwidth/1000`-second time windows, and the (absolute) amplitude at the carrier frequency (`r targetF` Hz) taken as the outcome. These timecourses are then plotted as the black and blue traces in the plot below. The onset transient is apparent, as is the difference in amplitude between the two signals:

```{r fouriermethod}

fspec1 <- NULL
fspec2 <- NULL
for (t in 1:(9000-binwidth)){
  spec <- fft(trigwaveform1[t:(t+binwidth-1)])/binwidth
  fspec1[t] <- spec[tindex]
  spec <- fft(trigwaveform2[t:(t+binwidth-1)])/binwidth
  fspec2[t] <- spec[tindex]
}

# adjust times so that the x-values correspond to the centre of the time window
plot(times[501:8500],abs(fspec1),type='l')
lines(times[501:8500],abs(fspec2),col='blue')

```

It is clear that the finite time-window produces a gradually ramped onset over a 1 second period. The final step was to determine the extent to which this affects the timecourse of the suppression ratios, which are defined here as the ratio of the two signals, with a small constant added to each to avoid division by zero during time points when the stimulus amplitude was low. The simulated suppression ratio is plotted below.

```{r ratio1}

plot(times[501:8500],abs(fspec1+0.01)/abs(fspec2+0.01),type='l')

```

The increase in suppression ratio over time is very abrupt, taking place over the course of 1 carrier cycle. This is much more rapid than the blurring from the sliding time window, most likely because the blur cancels out across the numerator and denominator of the ratio calculation.

Finally, we repeated the analysis using an alternative fixed-phase method. Here the stimulus was multiplied (dot product) with a pure sine wave within each time window (instead of taking the Fourier transform). This has the advantage of removing out-of-phase noise. It generates a similarly precise timecourse, though with a less pronounced 'ripple' artifact from the temporal windowing.

```{r fixedphasemethod}

# generate a pure sine wave of the correct phase
fullwave <- -cos(2 * targetF * times * pi)

samp1 <- NULL
samp2 <- NULL
for (t in 1:(9000-binwidth)){
  spec <- trigwaveform1[t:(t+binwidth-1)] * fullwave[t:(t+binwidth-1)]
  samp1[t] <- sum(spec)/binwidth
  spec <- trigwaveform2[t:(t+binwidth-1)] * fullwave[t:(t+binwidth-1)]
  samp2[t] <- sum(spec)/binwidth
}

plot(times[501:8500],abs(samp1),type='l')
lines(times[501:8500],abs(samp2),col='blue')

plot(times[501:8500],abs(samp1+0.01)/abs(samp2+0.01),type='l')

```

Overall, these simulations increase our confidence that we are able to resolve rapid increases in suppression should they exist. In our empirical data we find evidence for more gradual increases, often taking around 2-5 seconds to reach maximum levels of suppression (depending on temporal frequency). These appear not to be an artifact of our analysis method.

### 2023-07-31 manuscript.Rmd
Added simulations

@@
 
-processdata <- 0  # this flag determines the amount of processing, with 4 levels:
+processdata <- 1  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures

### 2023-07-31 manuscript.Rmd
Added code to download the processed intermodulation data if required

@@
 if (processdata>0){
+
+   if (!file.exists('temp/PilotIM.RData')){
+      hid <- pmatch('PilotIM.RData',as.character(unlist(osffiles[,1])))
+      osf_download(osffiles[hid,],'temp/',progress=TRUE)
+ }
 load('temp/PilotIM.RData')
@@
 if (processdata>0){
+
+     if (!file.exists('temp/EEGIM.RData')){
+      hid <- pmatch('EEGIM.RData',as.character(unlist(osffiles[,1])))
+      osf_download(osffiles[hid,],'temp/',progress=TRUE)
+ }
 load('temp/EEGIM.RData')
@@
 if (processdata>0){
+
+       if (!file.exists('temp/MEGIM.RData')){
+      hid <- pmatch('MEGIM.RData',as.character(unlist(osffiles[,1])))
+      osf_download(osffiles[hid,],'temp/',progress=TRUE)
+ }
 load('temp/MEGIM.RData')

### 2023-07-31 manuscript.Rmd
Testing build from processed individual data

@@
 
-processdata <- 1  # this flag determines the amount of processing, with 4 levels:
+processdata <- 2  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
@@
 Following the suggestion of a reviewer, we conducted an alternative fixed-phase analysis, where the signal in each 1 second epoch was multiplied by a sine wave of appropriate frequency and phase instead of taking the Fourier transform.
-The results were similar to our main analysis, and can be viewed in the Figures subdirectory of the project code repository ([https://github.com/bakerdh/normreweight/tree/main/Figures files with the suffix 'FP'](https://github.com/bakerdh/normreweight/tree/main/Figures)).
+The results were similar to our main analysis, and can be viewed in the Figures subdirectory of the project code repository ([https://github.com/bakerdh/normreweight/tree/main/Figures - see files with the suffix 'FP'](https://github.com/bakerdh/normreweight/tree/main/Figures)).
 We also conducted simulations (also available in the code repository) to confirm that our analysis methods were not distorting the estimates of the suppression timecourse.
@@
 This confirms that the reweighting effects can occur as early as primary visual cortex, consistent with findings from neurophysiology [@Aschner2018].
-However the data are more variable than for our EEG experiments, and had fewer significant clusters, perhaps owing to a power reduction caused by the smaller sample size for this dataset and greater heterogeneity across frequency.
+However the data are more variable than for our EEG experiments, and had fewer significant clusters, perhaps owing to a power reduction caused by the smaller sample size for this dataset and/or greater heterogeneity across frequency.
 When pooling effects over frequency and condition, the overall effect size (*d* = `r round(MEGeffectsize,digits=2)`) was near zero.

### 2023-07-31 manuscript.Rmd
Revert to processing level 1

@@
 
-processdata <- 2  # this flag determines the amount of processing, with 4 levels:
+processdata <- 1  # this flag determines the amount of processing, with 4 levels:
 # 0 - do no processing, generate the pdf using existing versions of all figures
